### 2018-10-07 paper/bin-love-after-gw170817.tex
Added structure for the paper

\documentclass[prd,twocolumn,nofootinbib,superscriptaddress,amsmath,amssymb]{revtex4-1}
\include{preamble}

\begin{document}

\title{Universal relations after GW170817}

\author{Frodo}
\affiliation{}

\author{Sam}
\affiliation{}

\author{Pippin}
\affiliation{}

\author{Merry}
\affiliation{}

\date{\today}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Begin Abstract %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

\end{abstract}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Begin Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}\label{sec:intro}

\subsection{Executive Summary}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Begin theory %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Neutron star tidal deformability}\label{sec:tidal}
We begin by reviewing how one can extract internal structure information of NSs via GW measurement.
In the presence of a neighboring tidal field $\mathcal{E}_{ij}$, such as the binary NS system found in GW170817, NSs tidally deform away from sphericity and acquire a non-vanishing quadrupole moment $Q_{ij}$ that is characterized by the \textit{tidal deformability} $\lambda$~\cite{Flanagan2008}:
This process is characterized by the \textit{tidal deformability}, $\lambda$~\cite{hinderer-love,Yagi2013}:
\begin{equation}
Q_{ij} = - \lambda \mathcal{E}_{ij}.
\end{equation}
Such tidal deformability can be made dimensionless as
\begin{equation}
\Lambda \equiv \frac{\lambda}{M^5},
\end{equation}
and can be calculated via the following expression~\cite{hinderer-love,damour-nagar,Yagi2013}:
\begin{align}
\begin{split}
\Lambda &= \frac{16}{15} (1-2\bar{C})^2[2+2\bar{C}(y_\R-1)-y_\R]\\
& \times \{2\bar{C}[6-3y_\R+3\bar{C}(5y_\R-8)]\\ 
&+4\bar{C}^3[13-11y_\R+\bar{C}(3y_\R-2)+2\bar{C}^2(1+y_\R)]\\ 
&+3(1-2\bar{C})^2[2-y_\R+2\bar{C}(y_\R-1)]\ln{(1-2\bar{C})}\}^{-1}.
\end{split}
\end{align}
Here $\bar{C} \equiv M / R$ is the stellar compactness with $M$ and $R$ representing the NS mass and radius. $y_\R \equiv y(R)$ with $y(r) \equiv r h'(r)/h(r)$, where a prime stands for taking a derivative with respect to the radial coordinate $r$. $h$ represents the quadrupolar part of the $(t,t)$ component of the metric perturbation that satisfies the following differential equation:
\begin{align}\label{eq:deq} 
\begin{split}
& h''+ \Big\{ \frac{2}{r} + \Big\lbrack \frac{2m}{r^2}+4 \pi r (p - \epsilon ) \Big\rbrack e^{\lambda} \Big\} h'\\
&+ \Big\{4 \pi \Big\lbrack 5 \epsilon + 9p + (p+ \epsilon) \frac{d \epsilon}{dp} \Big\rbrack e^{\lambda}- \frac{6}{r^2}e^{\lambda} - \Big(\frac{d \nu}{dr} \Big)^2 \Big\}h =0
\end{split}
\end{align}
with background metric coefficients $e^{\nu} = g_{tt}$ and $e^{\lambda} = (1-2m/r)^{-1} = g_{rr}$, while $p$ and $\epsilon$ represent pressure and energy density respectively.

The above differential equation can be solved as follows.
First, one needs to prepare unperturbed background solutions by choosing a specific EoS, or $p(\epsilon)$, and solve a set of Tolman-Oppenheimer-Volkoff (TOV) equations with a chosen central density (or pressure) and appropriate boundary conditions. The stellar radius is determined from $p(R)=0$ while the mass is determined by matching the interior solution to the Schwarzschild metric.
Having such solutions at hand, one then plugs them into Eq.~\eqref{eq:deq} and solve it with the boundary condition $y(0)=2$~\cite{hinderer-love}.

Because there are two NSs in a binary, two tidal deformabilities $\Lambda_1$ and $\Lambda_2$ associated with each star enter in the gravitational waveform.
However, extracting such parameters independently is challenging due to the strong correlation between them\footnote{One way to cure this problem is to use universal relations between them~\cite{Yagi:2015pkc,Yagi:2016qmr}.}. 
Thus, what one can measure is the dominant tidal parameter in the waveform, which corresponds to the weighted average tidal deformability given by~\cite{Flanagan2008}
\begin{equation}
\tilde{\Lambda} = \frac{16}{13} \frac{(1+12q) \Lambda_1+(12+q)q^4\Lambda_2}{(1+q)^5},
\end{equation}
where $q \equiv m_2/m_1$ is the mass ratio between two stars.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Begin EOS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Spectral representations of neutron star equations of state}\label{sec:eos}
The structure of a NS and its tidal interactions in a binary system rely heavily on the underlying EoS of nuclear matter.

%%%%%%%%%%%%%%%%%%%%%%%%% Begin universal relations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Universal relations}\label{sec:universal}

\subsection{I-Love-Q relations}\label{sec:ilq}

\subsection{Binary love relations}\label{sec:binary}

%%%%%%%%%%%%%%%%%%%%%%%%% Begin constraints %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Constraints on neutron star equation of state}\label{sec:constraints}

%%%%%%%%%%%%%%%%%%%%%%%%% Begin Discussion %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Discussion}\label{sec:conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%% Begin Acknowledgements %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgments}\label{acknowledgments}

%\appendix

%%%%%%%%%%%%%%%%%%%%%%%%% Begin Bibliography  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\clearpage
\bibliography{Zack}
%\bibliographystyle{IEEEtran}
%\onecolumngrid

\end{document}

### 2018-10-07 paper/go.sh

@@ -1,0 +1,14 @@
+#!/bin/bash
+echo "Compiling.."
+rm *blg *log *aux *Notes* *bbl output.text
+pdflatex --shell-escape bin-love-after-gw170817.tex > output.text
+echo "~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~" >> output.text
+pdflatex --shell-escape bin-love-after-gw170817.tex >> output.text
+echo "~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~" >> output.text
+bibtex bin-love-after-gw170817.aux >> output.text
+echo "~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~" >> output.text
+pdflatex --shell-escape bin-love-after-gw170817.tex >> output.text
+echo "~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~" >> output.text
+pdflatex --shell-escape bin-love-after-gw170817.tex >> output.text
+echo "Done. Enjoy your PDF!"
+evince bin-love-after-gw170817.pdf &

### 2018-11-15 paper/bin-love-after-gw170817.tex
rough first draft of the paper

@@
 
+\author{Gandalf}
+\affiliation{}
+
 \date{\today}
@@
 \begin{abstract}
-
+% Intro
+The thermodynamic relationship between pressure and density (the equation of state) of supranuclear matter, accessible primarily in neutron stars, is critical to the study of such stars, and is one of the largest uncertainties in nuclear physics to date.
+% How to probe
+The extraction of tidal deformabilities from the gravitational waveforms of binary neutron star merger events, such as GW170817, is a promising method of probing the nuclear structure.
+% What was done before - Binary Love
+Previous studies have shown that approximately equation of state insensitive ``binary Love universal relations" exist between symmetric and antisymmetric combinations of individual tidal deformabilities, which are difficult to be independently measured with second-generation gravitational wave interferometers.
+% What was done before - I-Love-Q
+Similarly, another set of equation of state independent relations exist between individual neutron star parameters: moment of inertia (I), tidal deformability (Love number), and quadrupole moment (Q) - known as the ``I-Love-Q universal relations."
+% What universal relations do
+Such universal relations allow the elimination of some tidal parameters from the list of model parameters, thus breaking degeneracies and ultimately reducing the uncertainty of the dominant tidal effect in parameter estimation.
+% What we will do
+In this document, we explain how one can reduce equation of state variation for both binary Love and I-Love-Q universal relations, which helps to reduce systematic errors on the tidal measurement of binary neutron star mergers.
+We achieve this  by restricting to only equations of state drawn within the 90\% posterior constraint on pressure as a function of density, as derived by the LIGO Collaboration.
+% What we found
+We find an improvement in binary Love universality by a factor of 25\% for stars with mass below 1.7 solar masses, and in I-Love-Q universality by a factor of 22\%\zc{check these numbers}.
+% Conclude
+We end by comparing systematic errors on tidal measurement due to the equation of state variation with statistical errors and comment on whether one can safely use these universal relations with future gravitational wave observations.
 \end{abstract}
@@
 \section{Introduction}\label{sec:intro}
+%Intro
+The dependance of pressure on density for supranuclear matter found primarily inside neutron stars (NSs) remains to be one of the largest mysteries in both nuclear physics and astrophysics.
+This internal structure of such stars, known as the equation of state (EoS), is exceedingly important, as it is the determining factor for many NS observables - such as the mass, the radius, and many more.
+Unfortunately, terrestrial experiments can only study the EoS up to the nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy}, making NSs ideal laboratories for constraining ultra dense nuclear matter.
+
+%Constraining the EoS
+Independent measurements of NS observables can be used to constrain the nuclear EoS.
+For example, electromagnetic observations of the mass-radius relationship of NSs have been used to place limits on NSs~\cite{guver,ozel-baym-guver,steiner-lattimer-brown,Lattimer2014,Ozel:2016oaf}.
+However, these implications suffer from large systematic errors due to astrophysical mismodeling.
+Alternatively, the emission of gravtiational waves (GWs) from binary NS merger events have proven to be a unique method of probing nuclear physics.
+During the early inspiral portion of the merger, the orbital separation is large enough that the effect of companion tidal fields is negligable. 
+As the separation decreases through GW emission, tidal forces are magnified and the NSs deform from sphericity, altering the orbital trajectories; a relic which is directly imprinted on the GW signal.
+This deformation is characterized by the \textit{tidal deformability} $\Lambda$ as the linear response of the NSs quadrupole moment $Q_{ij}$ to the neighboring tidal field $\varepsilon_{ij}$.
+
+%reparameterization of the template
+In the case of binary NSs, each star becomes deformed via the process highlighted above, resulting in two highly correlated tidal parameters $\Lambda_1$ and $\Lambda_2$ entering in the gravitational waveform.
+Due to high correlations between between the two paramters, independant extraction becomes very difficult at current interferometer sensitivities.\zc{cite?}
+Typically, these high correlations can be reduced by strategically reparameterizing the waveform template with new tidal parameters constructed from linear combinations of $\Lambda_1$ and $\Lambda_2$.
+For example, utilizing the parameters $\tilde{\Lambda}$ and $\delta \tilde{\Lambda}$~\cite{hinderer-love,Flanagan2008} which enter the GW waveform at different post-Newtonian (PN) orders (powers of the ratio between the orbital speed and the speed of light $v/c^{2n}$) partially mitigates these correlations.
+
+%Universal relations
+Unfortunately, current detectors are only sensitive enough to accurately measure the dominant tidal parameter, $\tilde{\Lambda}$, known as the chirp deformability.
+Previous work by Yagi \textit{et al.}~\cite{Yagi:binLove} resolved this issue by finding approximately EoS-insensitive ``binary Love universal relations" between symmetric and anti-symmetric combinations of tidal deformabilities $\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$.
+This allows one to further break degeneracies between tidal parameters, resulting in both (i) a decrease in uncertainty upon parameter extraction on the removal of one parameter from the model, and (ii) the ability to measure the secondary tidal parameter upon measurement of the first.
+This important work showed up to an order of magnitude improvement in parameter estimation through a simple Fisher analysis.
+Similar ``I-Love-Q" universal relations~\cite{Yagi:ILQ} have been found between individual NS observables: quadrupole moment , moment of inertia, and tidal deformability; similarly allowing the removal of tidal parameters from the model list, and allowing an automatic determination of one observable through the measurement of another.
+
+%How we improved this
+In this analysis, we aim to improve this important work by imposing the restrictions found on the EoS~\cite{LIGO:posterior} derived from the recent binary NS merger observation, GW170817~\cite{TheLIGOScientific:2017qsa}.
+By restricting to only EoSs which lie within the the 90\% credible region on pressure as a function of density found in~\cite{LIGO:posterior}, we repeat the analyses done in~\cite{Yagi:binLove,Yagi:ILQ} and show an increase in universality for both binary Love and I-Love-Q universal relations.
+Further, we estimate the viability of using improved universal relations on future GW detections by performing simple Fisher analyses to approximate when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in universal relations.
 
 \subsection{Executive Summary}
+%What we did
+In this paper we attempt to improve binary Love and I-Love-Q universal relations by imposing constraints on the EoS found by GW170817~\cite{LIGO:posterior,TheLIGOScientific:2017qsa}.
+First, we generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, where we (i) impose the restriction that they must lie within GW170817's 90\% credible region in pressure as a function of density, and (ii) don't impose any restrictions for comparison purposes.
+Next, we follow the important works of~\cite{Yagi:binLove} and~\cite{Yagi:ILQ} to show how the ``constrained" set of EoSs show improved universality from both the previous works, and the ``unconstrained" sample.
+Lasty, through a simple Fisher analysis, we consider the value in improving universal relations by approximating when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in universal relations.
+
+%Final Results
+Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of 25\% for stars with mass below 1.7 solar masses, and in I-Love-Q universality by a factor of 22\%.
+Unfortunately, due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the universal relations are far outweighed by the statistical errors accrued by extraction of high-order PN tidal parameters from GW waveforms.
+Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from parameter extraction for GW170817 as if it had been observed by future detectors aLIGO, a\texttt{++}, Voyager, ET, and CE\zc{cite these individually}.
+Here, $\sigma_1$ corresponds to the statistical error found from observing GW170817, and $\sigma_N$ represents the combined uncertainty after the detection of $N$ events (corresponding to the binary NS merger rate associated with each interferometer).
+These values are further tabulated in Table~\ref{tab:variances}.
+It can be seen from this figure that the statistical errors from parameter extraction become comparable the universal relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love universal relations will become viable.
+\begin{figure}
+\begin{center} 
+\includegraphics[width=\columnwidth]{stackedFisher.pdf}
+\end{center}
+\caption{
+\zc{Redo this image in xmgrace.}
+Estimated statistical uncertainties $\sigma_1$ (blue) in the extraction of $\tilde{\Lambda}$ from GW170817 (O2) as if it were observed with future interferometers aLIGO, a++, Voyager, CE, and ET as a function of SNR.
+This is compared to the combined uncertainty $\sigma_N$ (orange) from the observation of multiple events from a simulated population of size $N$ corresponding to the expected rate of binary NS observations for O2, aLIGO, a\texttt{++}, Voyager, CE, and ET over 2 observing runs: 2, 44, 355, 4818, 256620, and 1349917 respectively.
+It can be seen that the statistical errors in parameter extraction become comparable to the systematics from EoS variation in binary Love relations (magenta) for Voyager and on.
+Note the approximation for $\sigma_N$ under the O2 detector sensitivity is a poor estimate due to the small number of stacked events, $N_{\text{O2}}=2$, resulting in a high degree of randomness in population generation.
+These results are further tabulated in Table~\ref{tab:variances}.
+}
+\label{fig:stackedFisher}
+\end{figure}
+
+%outline
+The organization of this paper is outlined below.
+We begin with a complementary background and theory material in Sec.~\ref{sec:theory}.
+We continue in Sec.~\ref{sec:universal} by finding new and improved binary Love and I-Love-Q universal relations.
+We next examine these improved universal relations and question whether or not they are useful for future interferometers in Sec.~\ref{sec:observations}.
+We conclude in Sec.~\ref{sec:conclusion} by discussing our results and mentioning avenues of future work.
+Throughout this paper, we have adopted geometric units of $G=c=1$, unless otherwise stated.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Begin theory %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Neutron star tidal deformability}\label{sec:tidal}
-We begin by reviewing how one can extract internal structure information of NSs via GW measurement.
-In the presence of a neighboring tidal field $\mathcal{E}_{ij}$, such as the binary NS system found in GW170817, NSs tidally deform away from sphericity and acquire a non-vanishing quadrupole moment $Q_{ij}$ that is characterized by the \textit{tidal deformability} $\lambda$~\cite{Flanagan2008}:
-This process is characterized by the \textit{tidal deformability}, $\lambda$~\cite{hinderer-love,Yagi2013}:
+\section{Background and theory}\label{sec:theory}
+
+\subsection{Spectral representations of neutron star equations of state}\label{sec:eos}
+The structure of a NS and its tidal interactions in a binary system rely heavily on the underlying state function describing the relationship between pressure ($p$) and energy density ($\epsilon$), or equation of state, of nuclear matter.
+Given that all currently proposed EoSs utilize certain approximations, one method to study a wide range of physically realizeable EoSs is to parameterize them in a model-independent way.
+Spectral representations~\cite{Lindblom:2010bb,Lindblom:2012zi,Lindblom:2013kra,Lindblom:2018rfr,Abbott:2018exr} parameterize EoSs by performing spectral expansions on the adiabatic index $\Gamma(p)$\footnote{Another way of parameterizing EoSs is the piecewise polytropic formulation~\cite{Read2009,Lackey:2014fwa,Carney:2018sdv}.}:
 \begin{equation}
-Q_{ij} = - \lambda \mathcal{E}_{ij}.
+\Gamma(x) = \exp{\sum_k\gamma_k x^k},
 \end{equation}
-Such tidal deformability can be made dimensionless as
+where $x \equiv \log{p/p_0}$ for minimum pressure $p_0$.
+The equation of state is then determined by an integration of the differential equation:
 \begin{equation}
-\Lambda \equiv \frac{\lambda}{M^5},
+\frac{d \epsilon(p)}{dp}=\frac{\epsilon(p)+p}{p \Gamma(p)}.
+\end{equation}9
+Using this formalism, any valid EoS can be approximated through choice of 4 or more spectral coefficients $\gamma_k$, tabulated for several common EoSs in Table 1 of~\cite{Lindblom:2018rfr}.
+
+In the current analysis, we consider only EoSs which have been constrained by the recent binary neutron star merger event, GW170817.
+Important recent work~\cite{LIGO:posterior} uniformly sampled EoS parameters in order to derive a marginalized posterior on the pressure as a function of mass density, as seen in Fig.
+2 of~\cite{LIGO:posterior}.
+In our work, we similarly sample spectral coefficients within the ranges: $\gamma_0 \in \lbrack 0.2,2 \rbrack$, $\gamma_1 \in \lbrack -1.6,1.7 \rbrack$, $\gamma_2 \in \lbrack -0.6,0.6 \rbrack$, $\gamma_0 \in \lbrack -0.02,0.02 \rbrack$, and further restricting the adiabatic index to be $\Gamma \in \lbrack 0.6,4.5 \rbrack$, ensuring our parameterization exposes a wide range of viable EoSs~\cite{Lindblom:parameters}.
+In addition, we impose similar constraints as was done in~\cite{LIGO:posterior}: (i) causality within 10\%, and (ii) EoS priors must support NS masses up to $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations.
+We then utilize the posterior defined by GW170817 by rejecting any EoS sample which does not lie within the 90\% credible posterior region, resulting in a sample of 35 EoSs shown in Fig.~\ref{fig:eos}.
+Following~\cite{Read2009}, the parameterized high-density core EoSs generated above are matched to the low-density crust EoS Sly~\cite{Douchin:2001sv} at the density such that the pressures are equal.
+For comparison, we also include a second sample of randomly generated EoSs, without restricting to GW170817s posterior.
+\begin{figure}
+\begin{center} 
+\includegraphics[width=\columnwidth]{EoSs.pdf}
+\end{center}
+\caption{
+\zc{Redo this image in xmgrace.}Set of 35 randomly generated EoSs used in our analysis. 
+These were populated by uniformly sampling the spectral coefficient parameter space, then restricting to the 90\% credible level on EoS as derived by~\cite{LIGO:posterior}.
+}
+\label{fig:eos}
+\end{figure}
+
+\subsection{Tidal deformability}\label{tidal}
+Binary neutron star mergers, such as GW170817, provide valuable insight into the internal structure of such stars. 
+Namely, tidal effects which enter the gravitational waveform depend strongly on the EoS defining the NSs structure. 
+The ($l=2$ electric type) \emph{tidal deformability}, denoted as $\lambda$, has the largest impact on the waveform phase. 
+Consider a NS of mass $M$ in the presence of the tidal field $\varepsilon_{ij}$ of a companion star.
+In response, the NS will deform away from sphericity under the aquisition of quadrupole moment $Q_{ij}$, characterized by $\lambda$ as the linear response to $\varepsilon_{ij}$~\cite{Flanagan2008,hinderer-love,Yagi2013}:
+\begin{equation}
+Q_{ij}=-\lambda \varepsilon_{ij}.
 \end{equation}
-and can be calculated via the following expression~\cite{hinderer-love,damour-nagar,Yagi2013}:
+One can extract $\lambda$, or its dimensionless form $\Lambda \equiv \lambda/M^5$, via different asymptotic limits of the gravitational potential:
 \begin{align}
 \begin{split}
-\Lambda &= \frac{16}{15} (1-2\bar{C})^2[2+2\bar{C}(y_\R-1)-y_\R]\\
-& \times \{2\bar{C}[6-3y_\R+3\bar{C}(5y_\R-8)]\\ 
-&+4\bar{C}^3[13-11y_\R+\bar{C}(3y_\R-2)+2\bar{C}^2(1+y_\R)]\\ 
-&+3(1-2\bar{C})^2[2-y_\R+2\bar{C}(y_\R-1)]\ln{(1-2\bar{C})}\}^{-1}.
+\Phi=\frac{1+g_{tt}}{2}&=-\frac{M}{r} - \frac{3}{2}\frac{Q_{ij}}{r^3} \Bigg(\frac{x^i}{r} \frac{x^j}{r}-\frac{1}{3}\delta_{ij} \Bigg) + \mathcal{O} \Bigg( \frac{M^4}{r^4} \Bigg)\\
+&+ \frac{1}{2} \varepsilon_{ij} x^i x^j + \mathcal{O} \Bigg( \frac{r^3}{M^3} \Bigg).
 \end{split}
 \end{align}
-Here $\bar{C} \equiv M / R$ is the stellar compactness with $M$ and $R$ representing the NS mass and radius.
-$y_\R \equiv y(R)$ with $y(r) \equiv r h'(r)/h(r)$, where a prime stands for taking a derivative with respect to the radial coordinate $r$.
-$h$ represents the quadrupolar part of the $(t,t)$ component of the metric perturbation that satisfies the following differential equation:
-\begin{align}\label{eq:deq} 
-\begin{split}
-& h''+ \Big\{ \frac{2}{r} + \Big\lbrack \frac{2m}{r^2}+4 \pi r (p - \epsilon ) \Big\rbrack e^{\lambda} \Big\} h'\\
-&+ \Big\{4 \pi \Big\lbrack 5 \epsilon + 9p + (p+ \epsilon) \frac{d \epsilon}{dp} \Big\rbrack e^{\lambda}- \frac{6}{r^2}e^{\lambda} - \Big(\frac{d \nu}{dr} \Big)^2 \Big\}h =0
-\end{split}
-\end{align}
-with background metric coefficients $e^{\nu} = g_{tt}$ and $e^{\lambda} = (1-2m/r)^{-1} = g_{rr}$, while $p$ and $\epsilon$ represent pressure and energy density respectively.
+This process is described in more detail in~\cite{hinderer-love}.
 
-The above differential equation can be solved as follows.
-First, one needs to prepare unperturbed background solutions by choosing a specific EoS, or $p(\epsilon)$, and solve a set of Tolman-Oppenheimer-Volkoff (TOV) equations with a chosen central density (or pressure) and appropriate boundary conditions.
-The stellar radius is determined from $p(R)=0$ while the mass is determined by matching the interior solution to the Schwarzschild metric.
-Having such solutions at hand, one then plugs them into Eq.~\eqref{eq:deq} and solve it with the boundary condition $y(0)=2$~\cite{hinderer-love}.
+Next, we consider the case of two NSs in a binary, such as the system found in GW170817, where each star 
+individually experiences a neighboring tidal field.
+Thus each star possesses tidal deformabilities $\Lambda_1$ and $\Lambda_2$ entering the gravitational waveform.
+Due to strong correlations between these parameters, individual extraction is very difficult with current interferometer sensitivity limitations.
+However, the waveform templates can be strategically reparameterized to instead include independant linear combinations of $\Lambda_1$ and $\Lambda_2$ to mitigate correlations between them. 
+Any set of two independent functions may be used, for example: tidal parameters $\tilde{\Lambda}=\tilde{\Lambda}(\Lambda_1,\Lambda_2)$ and $\delta \tilde{\Lambda}=\delta \tilde{\Lambda}(\Lambda_1,\Lambda_2)$ enter the gravitational waveform at 5PN and 6PN orders respectively, thus partially breaking degeneracies.
+Here, $\tilde{\Lambda}$ is the weighted average tidal deformability, or chirp deformability due to its status as the primary tidal parameter in the waveform.
 
-Because there are two NSs in a binary, two tidal deformabilities $\Lambda_1$ and $\Lambda_2$ associated with each star enter in the gravitational waveform.
-However, extracting such parameters independently is challenging due to the strong correlation between them\footnote{One way to cure this problem is to use universal relations between them~\cite{Yagi:2015pkc,Yagi:2016qmr}.}.
-Thus, what one can measure is the dominant tidal parameter in the waveform, which corresponds to the weighted average tidal deformability given by~\cite{Flanagan2008}
+\subsection{EoS insensitive relations}\label{sec:eosInsensitive}
+Current gravitational wave interferometry is not yet sensitive enough to accurately extract both tidal parameters $\tilde{\Lambda}$ and $\delta\tilde{\Lambda}$.
+In a search to remedy this, important previous work by Yagi \textit{et al.}~\cite{Yagi:binLove} found that symmetric and antisymmetric combinations of tidal deformabilities:
 \begin{equation}
-\tilde{\Lambda} = \frac{16}{13} \frac{(1+12q) \Lambda_1+(12+q)q^4\Lambda_2}{(1+q)^5},
+\Lambda_s \equiv \frac{\Lambda_1 + \Lambda_2}{2}, \hspace{6mm} \Lambda_a \equiv \frac{\Lambda_1 - \Lambda_2}{2},
 \end{equation}
-where $q \equiv m_2/m_1$ is the mass ratio between two stars.
+display EoS-insensitive properties to a high degree, showing EoS variations up to 20\% for binaries with masses less than $1.7 \text{ M}_{\odot}$, for a representative set of 11 EoSs. 
+These relations, known as ``binary Love universal relations" allows one to break degeneracies between coupled tidal parameters.
+This is important for two reasons: (i) allows us to algebraically eliminate tidal parameters from the template parameter list, improving parameter estimation, and (ii) automatic measurement of second tidal parameter given observation of the first.
+It was shown through a simple Fisher analysis that the use of binary Love universal relations improved parameter extraction on $\tilde{\Lambda}$ by an order of magnitude.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Begin EOS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Spectral representations of neutron star equations of state}\label{sec:eos}
-The structure of a NS and its tidal interactions in a binary system rely heavily on the underlying EoS of nuclear matter.
-
+Similal universal relations have been found to exist between individual NS observables: moment of inertia (I), tidal deformability (Love), and quadrupole moment (Q), known as the ``I-Love-Q" universal relations~\cite{Yagi:ILQ}.
+These have been found to be EoS insensitive by up to 1\% for each of pair of observables.
+In this paper, we show improvement in both of these universal relations by restricting to EoSs drawn within GW170817s posterior on pressure as a function of density.
 %%%%%%%%%%%%%%%%%%%%%%%%% Begin universal relations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Universal relations}\label{sec:universal}
+In this section, we follow the analyses performed in~\cite{Yagi:binLove,Yagi:ILQ} with two new sets of 35 spectrally generated EoS: (i) those constrained by GW170817s 90\% credible region on pressure as a function of density as shown in Fig.~\ref{fig:eos}, and (ii) those unconstrained by any prior information.
+For the remainder of the paper, we refer to these distinct samples as ``constrained" and ``unconstrained."
 
 \subsection{I-Love-Q relations}\label{sec:ilq}
+Here we present our results on I-Love-Q universality as compared to Fig. 1 of Yagi \textit{et al.}~\cite{Yagi:ILQ}.
+Following this work, the data for each universal relation is fit to the following curve:
+\begin{equation}\label{eq:ILQfit}
+\ln{y_i}=a+b \ln{x_i} + c (\ln{x_i})^2 + d (\ln{x_i})^3 + e (\ln{x_i})^4,
+\end{equation}
+where the updated coefficients are given in Table~\ref{tab:ILQfit}.
+In particular, we focus only on the I-Love universal relation for brevity, noting that the remaining relations Q-Love and I-Q show similar results.
+
+\begin{table}[ht!]
+\centering
+\caption{
+Updated fit parameters for I-Love-Q universal relations, as given by the curve found in Eq.~\ref{eq:ILQfit}.
+}\label{tab:ILQfit}
+\begin{tabular}{ c  c | c c c c c } 
+ \hline
+ \hline
+ $y_i$ & $x_i$ & $a_i$ & $b_i$ & $c_i$ & $d_i$ & $e_i$ \\
+ \hline
+ $\bar{I}$ & $\Lambda$ & $1.49$ & $0.0632$ & $0.0212$ & $-5.47 \times 10^{-4}$ & $2.18 \times 10^{-6}$ \\
+ $\bar{I}$ & $\bar{Q}$ & $0.212$ & $0.0726$ & $0.0542$ & $-5.07 \times 10^{-3}$ & $1.60 \times 10^{-4}$ \\
+ $\bar{Q}$ & $\Lambda$ & $1.38$ & $0.590$ & $-0.0183$ & $0.0405$ & $-2.77 \times 10^{-3}$ \\ 
+ \hline
+ \hline
+\end{tabular}
+\end{table}
+
+Fig.~\ref{fig:ILQ} shows the improved I-Love universal relation between dimensionless moment of inertia $\bar{I} \equiv I/M^3$ and dimensionless tidal deformability $\Lambda$ for both constrained and unconstrained sets of EoSs.
+We observe that the maximum recorded EoS variation under the constrained set of EoSs is $0.43\%$, showing considerable improvement from the $0.88\%$ found in the case of unconstrained EoSs.
+Further, both EoS samples show improvement from the original result of $\approx 1\%$ displayed in~\cite{Yagi:ILQ}.
+\begin{figure*}
+\begin{center} 
+\includegraphics[width=\textwidth]{ILQ.pdf}
+\end{center}
+\caption{
+\zc{Redo this image in xmgrace.}
+I-Love universal relations shown for the constrained EoSs (left) and unconstrained EoSs (right).
+In this figure, the black line corresponds to the fit given by Eq.~\ref{eq:ILQfit}, while all other colors correspond to the 35 EoSs used in each case.
+The maximal EoS variation from the fit for unconstrained EoSs is $0.88\%$, which is comparable to the $1\%$ found in~\cite{Yagi:ILQ}.
+The constrained EoSs on the other hand, are universal to $0.43\%$, showing considerable improvement upon previous analyses.
+}
+\label{fig:ILQ}
+\end{figure*}
+
+These results indicate that universal relations can indeed be improved upon by constraining to only EoSs that agree with physical observations.
+Although the unconstrained EoSs show slightly smaller EoS variation than found in previous works, they are comparable in the sense that a wide range of EoSs were strategically picked in~\cite{Yagi:ILQ}, while the unconstrained set consists of a random sample which may or may not encompass everything considered previously.
+On the other hand, the constrained set of EoSs show significant improvement from that found in previous 
+works.
 
 \subsection{Binary love relations}\label{sec:binary}
+Next we consider improvements to the binary Love universal relations.
+Following Ref.~\cite{Yagi:binLove}, we fit the relation to the two-dimensional curve:
+\begin{equation}\label{eq:binLovefit}
+\Lambda_a=F_n(q) \frac{a+ \sum_{i=1}^3 \sum_{j=1}^2 b_{ij}q^j x^{i/5}}{a+ \sum_{i=1}^3 \sum_{j=1}^2 c_{ij}q^j x^{i/5}} \Lambda_s^{\alpha}
+\end{equation}
+where q is the mass ratio $q \equiv m_1/m_2$ with $m_1 \leq m_2$, and $F_n(q)$ being the Newtonian limit given by:
+\begin{equation}
+F_n(q) \equiv \frac{1-q^{10/(3-n)}}{1+q^{10/(3-n)}}.
+\end{equation}
+The updated fit parameters can be found in Table~\ref{tab:binLovefit}.
+Notice how, unlike the individual NS I-Love-Q universal relations, these relations also depend on the ratio of constituent masses in the binary system.
+\begin{table*}[ht!]
+\centering
+\caption{
+Updated fit parameters for the binary Love universal relations, as given by the curve found in Eq.~\ref{eq:binLovefit}.
+}\label{tab:binLovefit}
+\addtolength{\tabcolsep}{1pt} 
+\begin{tabular}{ c  c  c  c  c  c  c  c  c  c  c  c  c  c  c} 
+ \hline
+ \hline
+ $n$ & $\alpha$ & $a$ & $b_{11}$ & $b_{12}$ & $b_{21}$ & $b_{22}$ & $b_{31}$ & $b_{32}$ & $c_{11}$ & $c_{12}$ & $c_{21}$ & $c_{22}$ & $c_{31}$ & $c_{32}$\\
+ \hline
+ $0.743$ & $-1$ & $0.08684$ & $-2.594$ & $-0.6145$ & $9.659$ & $3.024$ & $-7.816$ & $17.5488$ & $-2.172$ & $-1.744$ & $3.609$ & $18.14$ & $11.45$ & $-29.90$\\
+\hline
+ \hline
+\end{tabular}
+\addtolength{\tabcolsep}{-1pt}
+\end{table*}
 
-%%%%%%%%%%%%%%%%%%%%%%%%% Begin constraints %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Constraints on neutron star equation of state}\label{sec:constraints}
+Fig.~\ref{fig:binLove} shows the improved binary Love universal relation for 3 different mass ratios: $q=0.9$, $q=0.75$, and $q=0.5$ for both constrained and unconstrained sets of EoSs.
+We observe that the maximum recorded EoS variation under the constrained set of EoSs is $23.65\%$, $9.76\%$, and $2.15\%$ for mass ratios of $q=0.9$, $q=0.75$, and $q=0.50$, respectively.
+This shows considerable improvement from the universalities of $\sim 50\%$, $\sim 20\%$, and $\sim 3\%$ found in Ref.~\cite{Yagi:binLove}.
+In addition, the unconstrained set of EoSs show similar universality to that recorded in Ref.~\cite{Yagi:binLove}.
+\begin{figure*}
+\begin{center} 
+\includegraphics[width=\textwidth]{binLove.pdf}
+\end{center}
+\caption{
+\zc{Redo this image in xmgrace.}
+Binary Love universal relations shown for the constrained EoSs (left) and unconstrained EoSs (right).
+In this figure, the solid black line corresponds to the fit given by Eq.~\ref{eq:binLovefit}, while the solid, dashed, and dotted colored lines represent the 35 EoSs for mass ratios of $q=0.9$, $q=0.75$, and $q=0.50$, respectively.
+The maximal EoS variation for each value of $q$ is $23.65\%$, $9.76\%$, and $2.15\%$ respectively, compared to $\sim 50\%$, $\sim 20\%$, and $\sim 3\%$ found in Ref.~\cite{Yagi:binLove}.
+These values are comparable to the maximal EoS variation for unconstrained EoSs as expected, found to be $41.66\%$, $12.64\%$, and $3.83\%$.
+}
+\label{fig:binLove}
+\end{figure*}
+
+We have now shown that binary NS merger observations can help improve universal relations - the question is: is it worth it?
+Current interferometer sensitivities are not yet small enough to accurately constrain $\tilde{\Lambda}$.
+For example, GW170817 was detected by LIGO observing run 2 (``O2")\zc{cite} and was able to constrain $\tilde{\Lambda}$ to a $90\%$ confidence interval of 325 (this relates to a standard deviation of $\sigma_{\tilde{\Lambda}}$=198) centered at $\tilde{\Lambda}=395$.
+This corresponds to statistical uncertainties on the order of $\sim 82\%$, which vastly dominates the error budget compared to the small systematic errors picked up by EoS variation in the universal relations, which can be seen in Fig.~\ref{fig:variances}.
+This implies that currently, improved universal relations will not make any difference in tidal parameter extraction.
+However, future detectors (for example aLIGO, a\texttt{++}, Voyager, CE, and ET) are planned with large reductions in sensitivity - both decreasing the statistical errors and allowing for a larger binary NS merger detection rate; further reducing uncertainties.
+In Sec.~\ref{sec:observations}, we analyze this further and discuss when improved universal relations will make a difference.
+\begin{figure}
+\begin{center} 
+\includegraphics[width=\columnwidth]{variances.png}
+\end{center}
+\caption{
+\zc{Ask Katerina for this data.
+Convert $\Lambda_s$ to $\tilde{\Lambda}$, then redo this image in xmgrace.
+Remove posterior eoss, Add a gridline at the maximum errors for both constrained and unconstrained, and maybe even show the relative errors as well?
+Probably remove the means as well.}
+Absolute difference from the fit on $\tilde{\Lambda}$ from EoS variation in the binary Love universal relations plotted with varying mass ratio $q$.
+Observe that the maximum systematic error attained for the constrained EoSs is $\sigma_{\tilde{\Lambda}}=10$ (this is found to be $20$ for the unconstrained EoSs).
+This is negligible compared to the statistical errors accrued on paramter extraction from GW170817.
+}
+\label{fig:variances}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%% Begin Future Observations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Impact on future observations}\label{sec:observations}
+In this section, we estimate the feasibility of ultilizing improved universal relations in future binary NS merger events.
+This estimate is aqcuired through a simple Fisher analysis~\cite{Finn:Fisher,Cutler:Fisher} which approximates the accuracy with which one can extract best-fit parameters $\theta^a$, given a prior template waveform.
+For the remainder of the paper, we consider a template parameter vector consisting of:
+\begin{equation}
+\theta^a=(\ln{A},\phi_c,t_c,\ln{\mathcal{M}},\ln{\mathcal{\eta}},\chi_s,\chi_a,\tilde{\Lambda},\delta \tilde{\Lambda}),
+\end{equation}
+where $A \equiv \sqrt{\frac{2 \eta}{3 \pi^{1/3}}}$ is a normalized amplitude factor, $\eta \equiv m_1 m_2/M^2$ is the symmetric mass ratio with $m_{1,2}$ and $M$ being the individual and total masses, $\mathcal{M}=M \eta^{3/5}$ is the chirp mass, and $\chi_{s,a}=\frac{1}{2}(\chi_1+\pm\chi_2)$ are the symmetric and antisymmetric total spins, where $\chi_{1,2}$ are the NSs individual spins.
+Following Refs.~\cite{Cutler:Fisher,Berti:Fisher,Poisson:Fisher}, this method relies on the crude assumption of Gaussian prior distributions\footnote{Typically, the more valid assumption is a uniform prior distribution; an improvement made in a more detailed Bayesian analysis.}.
+The resulting posterior distribution is Gaussian with root-mean-sqaure given by:
+\begin{equation}
+\Delta \theta^a=\sqrt{\Big( \tilde{\Gamma}^{-1}\Big)^{aa}}.
+\end{equation}
+Here, the Fisher matrix $\tilde{\Gamma}$ is defined by:
+\begin{equation}
+\tilde{\Gamma}_{ab} \equiv \Big( \frac{\partial h}{\partial \theta^a} \Big| \frac{\partial h}{\partial \theta^a}\Big) + \frac{1}{\sigma_{\theta^a}^2} \delta_{ab}
+\end{equation}
+where $h$ is the waveform template, $\sigma_{\theta^a}$ is the parameters' prior root-mean-square estimate, and the inner product is defined by:
+\begin{equation}
+(a|b) \equiv 2 \int^{\infty}_0\frac{\tilde{a}^*\tilde{b}+\tilde{b}^*\tilde{a}}{S_n(f)}df.
+\end{equation}
+Lastly, $S_n(f)$ is the spectral noise density for the given interferometer.
+
+We begin by authenticating this approach by applying a Fisher analysis to GW170817, as observed by LIGO with O2 detector sensitivity\zc{cite}.
+Further, we scale the luminosity distance such that $SNR=32.4$, as was found in GW170817.
+We also assume low spin priors $|\chi| \leq 0.05$, as well as $\tilde{\Lambda} \leq 3000$ and $|\delta \tilde{\Lambda}| \leq 500$~\cite{Wade:LambdaPriors}.
+The resulting posterior distribution on $\tilde{\Lambda}$ has a range of $\pm 276.99$ encompassing the $90\%$ credible levels.
+We compare these results with the Bayesian analysis performed in Ref.~\cite{TheLIGOScientific:2017qsa,Abbott2018}, finding close agreement with the resulting $90\%$ credible region of $70 \leq \tilde{\Lambda} \leq 720$.
+This confirms the approximate validity of this method, allowing a continuation of this analysis for future detectors.
+
+Next, we consider events identical to GW170817 detected on future design sensitivity upgrades and detectors aLIGO, a\texttt{++}, Voyager, CE, and ET\zc{cite} to determine if and when the statistical errors associated with parameter extraction of $\tilde{\Lambda}$ drop below the systematic EoS variation errors from using binary Love universal relations.
+The process we use for each detector sensitivity $S_n^{\text{det}}(f)$ is as follows:
+\begin{itemize}
+\item Perform a Fisher analysis as outlined above using $S_n^{\text{det}}(f)$, while restricting the luminosity distance $D_L$ such that $SNR_{\text{O2}}=32.4$ would be achieved on O2 sensitivity $S_n^{\text{O2}}(f)$.
+This results in statistical error $\sigma_1^{\text{det}}$ accrued in the extraction of $\tilde{\Lambda}$.
+\item Generate a population of $N_{\text{det}}$ events corresponding to the expected binary NS merger detection rate, following the distribution $f=3 SNR_{\text{th}}^3/SNR^4$~\cite{Shutz:SNR,Chen:SNR} with a network SNR threshold of 8.
+We approximate this to be proportional to the cube of SNR ratios over 2 observing runs: $N_{\text{det}} \sim N_{\text{O2}} (SNR_{\text{det}}/SNR_{\text{O2}})^3$, where $N_{\text{O2}}=2$, giving the rates shown in Table~\ref{tab:variances}.
+\item Compute the population standard deviation given by:
+\begin{equation}
+\frac{1}{(\sigma_N^{\text{det}})^2}=\sum_i^{N_{\text{det}}}\frac{1}{(\sigma_i^{\text{det}})^2},
+\end{equation}
+where $\sigma_i^{\text{det}}$ is computed by the relations $\sigma_i^{\text{det}} \times SNR_i^{\text{det}} = \sigma_1^{\text{det}} \times SNR_1^{\text{det}}$.
+\end{itemize}
+The results are compiled in Table~\ref{tab:variances}, and shown graphically in Fig.~\ref{fig:stackedFisher} where $\sigma_1$ and $\sigma_N$ are plotted as a function of $SNR_1$ (the SNR as if GW170817 were detected on a future detector) for 5 future detector sensitivities.
+
+\begin{table}[ht!]
+\centering
+\caption{
+Tabulated results for the estimated statistical errors on $\tilde{\Lambda}$ for the combined results of $N_{\text{det}}$ detections corresponding to the estimated binary NS merger detection rate.
+This is repeated for 5 future detector sensitivities: aLIGO, a\texttt{++}, Voyager, CE, and ET.
+Below, $SNR_1$ and $\sigma_1$ correspond to the approximate SNR and $\sigma_{\tilde{\Lambda}}$ of GW170817 had it been observed by the future interferometer, and $\sigma_N$ corresponds to the final uncertainty on $\tilde{\Lambda}$ after $N_{\text{det}}$ detections.
+It can be seen here that the statistical errors on $\tilde{\Lambda}$ become comparable with the systematics $\sigma_{\tilde{\Lambda}}=10$ from using improved binary Love relations from Voyager and on, indicating when it may be safe to utilize new universal relations.
+Note the approximation for $\sigma_N$ under the O2 detector sensitivity is a poor estimate due to the small number of stacked events, $N_{\text{O2}}=2$, resulting in a high degree of randomness in population generation.
+These results are shown graphically in Fig.~\ref{fig:stackedFisher}.
+}\label{tab:variances}
+\begin{tabular}{ c || c  c  c c } 
+\hline
+Detector & $N_{\text{det}}$ & $SNR_1$ & $\sigma_1$ & $\sigma_N$\\
+\hline
+\hline
+O2 & $2$ & $32.40$ & $168.40$ & $425.53$\\
+aLIGO & $44$ & $90.74$ & $75.44$ & $63.03$\\
+a\texttt{++} & $355$ & $180.95$ & $31.55$ & $24.22$\\
+Voyager & $4818$ & $428.89$ & $16.69$ & $7.78$\\
+CE & $256620$ & $1398.03$ & $4.85$ & $0.97$\\
+ET & $1349917$ & $2807.45$ & $6.26$ & $1.10$\\
+\hline
+\end{tabular}
+\end{table}
+
+Concluding, we find that the Voyager, ET, and CE detectors all exhibit enough uncertainty reduction that the systematics from using improved universal relations no longer become negligible in the error budget.
+This implies that the use and further improvement of universal relations is justified for future binary NS merger detections.
 
@@
 \section{Conclusion and Discussion}\label{sec:conclusion}
+The recent GW observation of binary NS merger GW170817 placed constraints on the supranuclear matter EoS for NSs.
+We take advantage of this by generating a restricted set of spectral EoSs which agree with this observation to reduce uncertainties upon the extraction of tidal parameters from future GW events.
+Important previous work by Yagi \text{et al.}~\cite{Yagi:ILQ,Yagi:binLove} found EoS-insensitive universal relations between symmetric and antisymmetric combinations of NS tidal deformabilities, which aid in the extraction of said tidal parameters.
+We find an improvement upon these universal relations by a factor of 25\% for stars with mass below 1.7 solar masses\zc{check this number} by restricting to the EoSs constrained by GW170817.
+Further, we analyze the impact of this improvement for future binary NS merger detections, as the current detector sensitivity is not yet small enough to accurately constrain $\tilde{\Lambda}$ enough for universal relations to make a difference.
+We find that future interferometers Voyager, CE, and ET all experience statistical uncertainties upon the extraction of $\tilde{\Lambda}$ small enough to become comparable to the systemtic errors injected by using the improved universal relations, as depicted in Fig.~\ref{fig:stackedFisher} and Table~\ref{tab:variances}.
+This indicates that the use and further improvement of universal relations is justified for future GW observations of binary NS merger events.
+
+Future work on this subject includes the possible constraint on the EoS through the observation of super-massive NSs combined with the results of GW170817.
+For example, recent millisecond pulsar discovery J1748-2021B~\cite{Freire:superMassiveNS} has mass $2.74 \pm 0.21$, with large error bars due to astronomical mismodeling.
+If verified, this provides a possible avenue of EoS constraint via considering only spectrally generated EoSs which support maximum NS mass in agreeance with J1748-2021B.
+\zc{Should we talk about this here? More future directions?}
 
@@
 \section*{Acknowledgments}\label{acknowledgments}
-
-%\appendix
+K.Y. would like to acknowledge networking support by the COST Action
+GWverse CA16104. \zc{everyone elses acknowledgments. Which grant am I funded by?}
 
@@
 \bibliography{Zack}
-%\bibliographystyle{IEEEtran}
-%\onecolumngrid
-
 \end{document}

### 2018-11-16 paper/bin-love-after-gw170817.tex
updates to paper draft

@@
 Unfortunately, due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the universal relations are far outweighed by the statistical errors accrued by extraction of high-order PN tidal parameters from GW waveforms.
-Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from parameter extraction for GW170817 as if it had been observed by future detectors aLIGO, a\texttt{++}, Voyager, ET, and CE\zc{cite these individually}.
-Here, $\sigma_1$ corresponds to the statistical error found from observing GW170817, and $\sigma_N$ represents the combined uncertainty after the detection of $N$ events (corresponding to the binary NS merger rate associated with each interferometer).
+Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from parameter extraction for GW170817 as if it had been observed by future detectors $A \equiv ($ O2, aLIGO, a\texttt{++}, Voyager, ET, CE$)$\zc{cite these individually}.
+Here, $\sigma^A_{\text{GW170817}}$ and $\rho^A_{\text{GW170817}}$ correspond to the statistical error and signal-to-noise-ratio found from observing GW170817 on detector $A$, and $\sigma^A_N$ represents the combined uncertainty after the detection of $N_A$ events (corresponding to the binary NS merger rate associated interferometer $A$).
 These values are further tabulated in Table~\ref{tab:variances}.
@@
 \zc{Redo this image in xmgrace.}
-Estimated statistical uncertainties $\sigma_1$ (blue) in the extraction of $\tilde{\Lambda}$ from GW170817 (O2) as if it were observed with future interferometers aLIGO, a++, Voyager, CE, and ET as a function of SNR.
-This is compared to the combined uncertainty $\sigma_N$ (orange) from the observation of multiple events from a simulated population of size $N$ corresponding to the expected rate of binary NS observations for O2, aLIGO, a\texttt{++}, Voyager, CE, and ET over 2 observing runs: 2, 44, 355, 4818, 256620, and 1349917 respectively.
+Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue) in the extraction of $\tilde{\Lambda}$ from GW170817 (O2) as if observed with future interferometers aLIGO, a++, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
+This is compared to the combined uncertainty $\sigma^A_N$ (orange) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the expected rate of binary NS observations for O2, aLIGO, a\texttt{++}, Voyager, CE, and ET-D over 1 observing run: 1, 22, 177, 2409, 128310, and 674958 respectively.
 It can be seen that the statistical errors in parameter extraction become comparable to the systematics from EoS variation in binary Love relations (magenta) for Voyager and on.
-Note the approximation for $\sigma_N$ under the O2 detector sensitivity is a poor estimate due to the small number of stacked events, $N_{\text{O2}}=2$, resulting in a high degree of randomness in population generation.
+Note the approximation for $\sigma^A_N$ under the O2 detector sensitivity is a poor estimate due to the small number of stacked events, $N_{\text{O2}}=1$, resulting in a high degree of randomness in population generation.
 These results are further tabulated in Table~\ref{tab:variances}.
@@
 These were populated by uniformly sampling the spectral coefficient parameter space, then restricting to the 90\% credible level on EoS as derived by~\cite{LIGO:posterior}.
+In addition, the following constraints were also applied: (i) the EoS must have a causal structure within 10\%, and (ii) the EoS must support maximum NS mass of at least $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations.
 }
@@
 
-\subsection{Tidal deformability}\label{tidal}
+\subsection{Neutron Star Tidal deformability}\label{tidal}
 Binary neutron star mergers, such as GW170817, provide valuable insight into the internal structure of such stars. 
@@
 \end{equation}
-One can extract $\lambda$, or its dimensionless form $\Lambda \equiv \lambda/M^5$, via different asymptotic limits of the gravitational potential:
+One can extract $Q_{ij}$ and $\varepsilon_{ij}$ -- and thus $\lambda$, or its dimensionless form $\Lambda \equiv \lambda/M^5$ -- via diffent asymptotic limits of the gravitational potential:
 \begin{align}
@@
 \end{align}
-This process is described in more detail in~\cite{hinderer-love}.
+The metric component $g_{tt}$ is determined by first constructing a spherically symmetric, non-spinning background solution, followed by the introduction of a perturbative tidal deformation.
+Next, the perturbed Einstein equations must be solved in the NSs interior given an EoS, then matched to the exterior Schwarzschild solution at the surface, modulo a constant.
+This process is described in more detail in Ref.~\cite{hinderer-love}.
+Further, the stellar mass and radius are determined from $p(R)=0$, and the above mentioned constant.
+Similarly, the moment of inertia is obtained from the asymptotic behavior of the $g_{t \phi}$ metric component.
 
@@
 However, the waveform templates can be strategically reparameterized to instead include independant linear combinations of $\Lambda_1$ and $\Lambda_2$ to mitigate correlations between them. 
-Any set of two independent functions may be used, for example: tidal parameters $\tilde{\Lambda}=\tilde{\Lambda}(\Lambda_1,\Lambda_2)$ and $\delta \tilde{\Lambda}=\delta \tilde{\Lambda}(\Lambda_1,\Lambda_2)$ enter the gravitational waveform at 5PN and 6PN orders respectively, thus partially breaking degeneracies.
-Here, $\tilde{\Lambda}$ is the weighted average tidal deformability, or chirp deformability due to its status as the primary tidal parameter in the waveform.
+Any set of two independent functions may be used, for example: tidal parameters $\tilde{\Lambda}=\tilde{\Lambda}(\Lambda_1,\Lambda_2)$ and $\delta \tilde{\Lambda}=\delta \tilde{\Lambda}(\Lambda_1,\Lambda_2)$~\cite{Wade:tidalCorrections} first enter the gravitational waveform at 5PN and 6PN orders respectively, thus partially breaking degeneracies.
+Here, $\tilde{\Lambda}$ is known as the mass weighted tidal deformability, or \emph{chirp deformability} due to its status as the dominant tidal parameter in the waveform.
 
@@
 \begin{equation}\label{eq:ILQfit}
-\ln{y_i}=a+b \ln{x_i} + c (\ln{x_i})^2 + d (\ln{x_i})^3 + e (\ln{x_i})^4,
+\ln{y_i}=a_i+b_i \ln{x_i} + c_i (\ln{x_i})^2 + d_i (\ln{x_i})^3 + e_i (\ln{x_i})^4,
 \end{equation}
@@
 \end{equation}
+In this analysis, we consider the ``PhenomD" waveform template~\cite{PhenomDI,PhenomDII} modified by tidal corrections shown in Ref.~\cite{Wade:tidalCorrections}.
 Lastly, $S_n(f)$ is the spectral noise density for the given interferometer.
@@
 We begin by authenticating this approach by applying a Fisher analysis to GW170817, as observed by LIGO with O2 detector sensitivity\zc{cite}.
-Further, we scale the luminosity distance such that $SNR=32.4$, as was found in GW170817.
+Further, we scale the luminosity distance such that the signal-to-noise-ratio ($SNR \equiv \rho$) is fixed to be $\rho=32.4$, as was found in GW170817.
 We also assume low spin priors $|\chi| \leq 0.05$, as well as $\tilde{\Lambda} \leq 3000$ and $|\delta \tilde{\Lambda}| \leq 500$~\cite{Wade:LambdaPriors}.
@@
 This confirms the approximate validity of this method, allowing a continuation of this analysis for future detectors.
+\begin{figure}
+\begin{center} 
+\includegraphics[width=\columnwidth]{sensitivities.pdf}
+\end{center}
+\caption{
+\zc{redo this image in xmgrace}
+Square root of of the spectral noise densities $\sqrt{S_n^A(f)}$ plotted for detectors ($A$): LIGO O2 (orange), aLIGO (green), a\texttt{++} (purple), Voyager (magenta), CE (red), and ET-D (blue) as interpolated from publicly available data\zc{cite}.
+Spectral noise densities are plotted from $f_{\text{min}}=(23,10,10,7,1,1) \text{ Hz}$, respectively, to $f_{\text{max}}=1649 \text{ Hz}$.
+Also shown is $2 \sqrt{f}$ multiplied by the amplitude of the PhenomD~\cite{PhenomDI,PhenomDII} waveform template, modified by tidal corrections from Ref.~\cite{Wade:tidalCorrections} used in our Fisher Analysis.
+}
+\label{fig:sensitivities}
+\end{figure}
 
-Next, we consider events identical to GW170817 detected on future design sensitivity upgrades and detectors aLIGO, a\texttt{++}, Voyager, CE, and ET\zc{cite} to determine if and when the statistical errors associated with parameter extraction of $\tilde{\Lambda}$ drop below the systematic EoS variation errors from using binary Love universal relations.
-The process we use for each detector sensitivity $S_n^{\text{det}}(f)$ is as follows:
+Next, we consider events identical to GW170817 detected on future design sensitivity upgrades and detectors $A \equiv ($O2, aLIGO, a\texttt{++}, Voyager, CE, ET-D$)$\zc{cite}, shown in Fig.~\ref{fig:sensitivities}, to determine if and when the statistical errors associated with parameter extraction of $\tilde{\Lambda}$ drop below the systematic EoS variation errors from using binary Love universal relations.
+The process we use for each detector sensitivity $S_n^A(f)$ is as follows:
 \begin{itemize}
-\item Perform a Fisher analysis as outlined above using $S_n^{\text{det}}(f)$, while restricting the luminosity distance $D_L$ such that $SNR_{\text{O2}}=32.4$ would be achieved on O2 sensitivity $S_n^{\text{O2}}(f)$.
-This results in statistical error $\sigma_1^{\text{det}}$ accrued in the extraction of $\tilde{\Lambda}$.
-\item Generate a population of $N_{\text{det}}$ events corresponding to the expected binary NS merger detection rate, following the distribution $f=3 SNR_{\text{th}}^3/SNR^4$~\cite{Shutz:SNR,Chen:SNR} with a network SNR threshold of 8.
-We approximate this to be proportional to the cube of SNR ratios over 2 observing runs: $N_{\text{det}} \sim N_{\text{O2}} (SNR_{\text{det}}/SNR_{\text{O2}})^3$, where $N_{\text{O2}}=2$, giving the rates shown in Table~\ref{tab:variances}.
+\item Perform a Fisher analysis as outlined above using $S_n^A(f)$, while restricting the luminosity distance $D_L$ such that $\rho^{\text{O2}}_{\text{GW170817}}=32.4$ would be achieved on O2 sensitivity $S_n^{\text{O2}}(f)$.
+This results in SNR $\rho^A_{\text{GW170817}}$ and statistical error $\sigma_\text{GW170817}^A$ accrued in the extraction of $\tilde{\Lambda}$ on detector $A$.
+\item Generate a population of $N_A$ events corresponding to the expected binary NS merger detection rate for detector $A$, following the distribution $f=3 \rho_{\text{th}}^3/\rho^4$~\cite{Shutz:SNR,Chen:SNR} with a network SNR threshold of $\rho_{\text{th}}=8$.
+We approximate this rate to be proportional to the cube of SNR ratios over 1 observing run: $N_A = N_{\text{O2}} (\rho^A_{\text{GW170817}}/\rho^{\text{O2}}_{\text{GW170817}})^3$, where $N_{\text{O2}}=1$, giving the rates shown inthe second column of Table~\ref{tab:variances}.
 \item Compute the population standard deviation given by:
 \begin{equation}
-\frac{1}{(\sigma_N^{\text{det}})^2}=\sum_i^{N_{\text{det}}}\frac{1}{(\sigma_i^{\text{det}})^2},
+\frac{1}{(\sigma_N^A)^2}=\sum_i^{N_A}\frac{1}{(\sigma_i^A)^2},
 \end{equation}
-where $\sigma_i^{\text{det}}$ is computed by the relations $\sigma_i^{\text{det}} \times SNR_i^{\text{det}} = \sigma_1^{\text{det}} \times SNR_1^{\text{det}}$.
+where $\sigma_i^A$ is computed by the relations $\sigma_i^A \times \rho_i^A = \sigma_{\text{GW170817}}^A \times \rho_{\text{GW170817}}^A$.
 \end{itemize}
-The results are compiled in Table~\ref{tab:variances}, and shown graphically in Fig.~\ref{fig:stackedFisher} where $\sigma_1$ and $\sigma_N$ are plotted as a function of $SNR_1$ (the SNR as if GW170817 were detected on a future detector) for 5 future detector sensitivities.
+The results are compiled in Table~\ref{tab:variances}, and shown graphically in Fig.~\ref{fig:stackedFisher} where $\sigma^A_{\text{GW170817}}$ and $\sigma^A_N$ are plotted as a function of $\rho^A_{\text{GW170817}}$ (the SNR as if GW170817 were detected on future detector $A$) for 5 future detector sensitivities.
 
@@
 \caption{
-Tabulated results for the estimated statistical errors on $\tilde{\Lambda}$ for the combined results of $N_{\text{det}}$ detections corresponding to the estimated binary NS merger detection rate.
+Tabulated results for the estimated statistical errors on $\tilde{\Lambda}$ for the combined results of $N_A$ detections corresponding to the estimated binary NS merger detection rate.
 This is repeated for 5 future detector sensitivities: aLIGO, a\texttt{++}, Voyager, CE, and ET.
-Below, $SNR_1$ and $\sigma_1$ correspond to the approximate SNR and $\sigma_{\tilde{\Lambda}}$ of GW170817 had it been observed by the future interferometer, and $\sigma_N$ corresponds to the final uncertainty on $\tilde{\Lambda}$ after $N_{\text{det}}$ detections.
+Below, $\rho^A_{\text{GW170817}}$ and $\sigma^A_{\text{GW170817}}$ correspond to the approximate SNR and $\sigma_{\tilde{\Lambda}}$ of GW170817 had it been observed by the future interferometer, and $\sigma^A_N$ corresponds to the final uncertainty on $\tilde{\Lambda}$ after $N_A$ detections on interferometer $A$.
 It can be seen here that the statistical errors on $\tilde{\Lambda}$ become comparable with the systematics $\sigma_{\tilde{\Lambda}}=10$ from using improved binary Love relations from Voyager and on, indicating when it may be safe to utilize new universal relations.
-Note the approximation for $\sigma_N$ under the O2 detector sensitivity is a poor estimate due to the small number of stacked events, $N_{\text{O2}}=2$, resulting in a high degree of randomness in population generation.
+Note the approximation for $\sigma^A_N$ under the O2 detector sensitivity is a poor estimate due to the small number of stacked events, $N_{\text{O2}}=1$, resulting in a high degree of randomness in population generation.
 These results are shown graphically in Fig.~\ref{fig:stackedFisher}.
@@
 \hline
-Detector & $N_{\text{det}}$ & $SNR_1$ & $\sigma_1$ & $\sigma_N$\\
+Detector ($A$) & $N_A$ & $\rho^A_{\text{GW170817}}$ & $\sigma^A_{\text{GW170817}}$ & $\sigma^A_N$\\
 \hline
 \hline
-O2 & $2$ & $32.40$ & $168.40$ & $425.53$\\
-aLIGO & $44$ & $90.74$ & $75.44$ & $63.03$\\
-a\texttt{++} & $355$ & $180.95$ & $31.55$ & $24.22$\\
-Voyager & $4818$ & $428.89$ & $16.69$ & $7.78$\\
-CE & $256620$ & $1398.03$ & $4.85$ & $0.97$\\
-ET & $1349917$ & $2807.45$ & $6.26$ & $1.10$\\
+O2 & $1$ & $32.40$ & $168.40$ & $314.90$\\
+aLIGO & $22$ & $90.74$ & $75.44$ & $70.37$\\
+a\texttt{++} & $177$ & $180.95$ & $31.55$ & $27.96$\\
+Voyager & $2409$ & $428.89$ & $16.69$ & $10.21$\\
+CE & $128310$ & $1398.03$ & $4.85$ & $1.39$\\
+ET-D & $674958$ & $2807.45$ & $6.26$ & $1.53$\\
 \hline
@@
 Further, we analyze the impact of this improvement for future binary NS merger detections, as the current detector sensitivity is not yet small enough to accurately constrain $\tilde{\Lambda}$ enough for universal relations to make a difference.
-We find that future interferometers Voyager, CE, and ET all experience statistical uncertainties upon the extraction of $\tilde{\Lambda}$ small enough to become comparable to the systemtic errors injected by using the improved universal relations, as depicted in Fig.~\ref{fig:stackedFisher} and Table~\ref{tab:variances}.
+We find that future interferometers Voyager, CE, and ET-D all experience statistical uncertainties upon the extraction of $\tilde{\Lambda}$ small enough to become comparable to the systemtic errors injected by using the improved universal relations, as depicted in Fig.~\ref{fig:stackedFisher} and Table~\ref{tab:variances}.
 This indicates that the use and further improvement of universal relations is justified for future GW observations of binary NS merger events.

### 2018-11-16 paper/bin-love-after-gw170817.tex
finished first rough draft of paper

@@
 By restricting to only EoSs which lie within the the 90\% credible region on pressure as a function of density found in~\cite{LIGO:posterior}, we repeat the analyses done in~\cite{Yagi:binLove,Yagi:ILQ} and show an increase in universality for both binary Love and I-Love-Q universal relations.
+In addition, we consider hybrid star EoSs seen in~\cite{Paschalidis2018}, which experience strong first-order transitions from hadronic matter to quark matter.
+These provide a departure from the nuclear matter relations considered here - providing valuable insight into them.
 Further, we estimate the viability of using improved universal relations on future GW detections by performing simple Fisher analyses to approximate when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in universal relations.
@@
 Next, we follow the important works of~\cite{Yagi:binLove} and~\cite{Yagi:ILQ} to show how the ``constrained" set of EoSs show improved universality from both the previous works, and the ``unconstrained" sample.
+In addition, we determine the degree to which hybrid star EoSs obey binary Love universal relations.
 Lasty, through a simple Fisher analysis, we consider the value in improving universal relations by approximating when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in universal relations.
@@
 Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of 25\% for stars with mass below 1.7 solar masses, and in I-Love-Q universality by a factor of 22\%.
+We also find that binaries consisting of one massive hybrid star, and one small-mass hadronic star do not agree with derived binary Love relations, due to the large separation in $\tilde{\Lambda}$ between the constituent stars.
 Unfortunately, due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the universal relations are far outweighed by the statistical errors accrued by extraction of high-order PN tidal parameters from GW waveforms.
@@
 We begin with a complementary background and theory material in Sec.~\ref{sec:theory}.
-We continue in Sec.~\ref{sec:universal} by finding new and improved binary Love and I-Love-Q universal relations.
+We continue in Sec.~\ref{sec:universal} by finding new and improved binary Love and I-Love-Q universal relations, and considering how well hybrid star EoSs agree with the binary Love relations.
 We next examine these improved universal relations and question whether or not they are useful for future interferometers in Sec.~\ref{sec:observations}.
@@
 Next we consider improvements to the binary Love universal relations.
-Following Ref.~\cite{Yagi:binLove}, we fit the relation to the two-dimensional curve:
+In particular, we consider two distinct classes of NSs: nuclear matter EoSs and hybrid quark-hadron star EoSs~\cite{Paschalidis2018,Alford:2017qgh,1971SvA....15..347S,Zdunik:2012dj,Alford:2013aca}.
+In the latter, the low-density nucleonic crust region of the EoS experiences a first-order phase transition into a high density quark matter core at a given transition pressure $P_{\text{tr}}$.
+In this document, we adopt the ACB models, in particular ACB5 as seen in Table II of Ref.~\cite{Paschalidis2018}.
+We begin in Sec.~\ref{sec:nuclear} by fitting new binary Love relations for nucleonic matter as was done in~\cite{Yagi:binLove}.
+This is followed in Sec.~\ref{sec:hybrid} by an analysis and discussion into how well hybrid stars agree with the improved binary Love relations
+
+\subsubsection{Nuclear matter stars}\label{sec:nuclear}
+Following Ref.~\cite{Yagi:binLove}, we fit the binary Love relations from the constrained EoSs to the two-dimensional curve:
 \begin{equation}\label{eq:binLovefit}
-\Lambda_a=F_n(q) \frac{a+ \sum_{i=1}^3 \sum_{j=1}^2 b_{ij}q^j x^{i/5}}{a+ \sum_{i=1}^3 \sum_{j=1}^2 c_{ij}q^j x^{i/5}} \Lambda_s^{\alpha}
+\Lambda_a=F_n(q) \frac{a+ \sum_{i=1}^3 \sum_{j=1}^2 b_{ij}q^j x^{i/5}}{a+ \sum_{i=1}^3 \sum_{j=1}^2 c_{ij}q^j x^{i/5}} \Lambda_s^{\alpha},
 \end{equation}
@@
 \end{figure*}
+
+\subsubsection{Hybrid quark-hadron stars}\label{sec:hybrid}
+Transitional quark-hadron matter stars undergo first-order phase transitions at pressure $P_{\text{tr}}$, where the hadronic branch departs into a quark-matter branch at a given mass transition.
+We focus on the ACB5 model, which observes a transition mass at $\sim 1.4 \text{ M}_{\odot}$~\cite{Paschalidis2018}.
+This results in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq 1.4 \text{ M}_{\odot}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote this as ``QS"), and (ii) small-mass ($M \leq 1.4 \text{ M}_{\odot}$) hadronic stars with no internal transition to quark matter (we denote this as ``HS").
+We consider 3 classes of binaries:
+\begin{itemize}
+\item QS/HS binary: consists of one massive hybrid star, and one small hadronic star,
+\item HS/HS binary: consists of two small-mass hadronic stars,
+\item QS/QS binary: consists of two massive hybrid stars.
+\end{itemize}
+
+To determine how each of class of binary NSs obey our improved binary Love universal relations, we pick a representative set of 10 binary pairs from each class.
+Binary Love values are then computed for each pair, then residuals from the binary Love curve found in Sec.~\ref{sec:nuclear} are determined and compared to that from the constrained set of EoSs.
+The results are shown in Fig.~\ref{fig:hybrid}.
+First, we observe that the HS/HS combination of stars gives consistent results to that found earlier -- as expected.
+Next, we see that QS/QS combinations agree moderately with previous relations\footnote{Note that these EoSs do not fit within GW170817's 90\% posterior on EoS - so we excpect deviations consistent with the ``unconstrained" set of EoSs, rather than the ``constraind" set.}, while QS/HS combinations disagree significantly.
+This can be explained by the large reduction in tidal deformability for hybrid stars, are shown in Fig.
+2 of Ref.~\cite{Paschalidis2018}: when one star lies on the hadronic branch while the other is on the quark branch, they each see vast differences in $\tilde{\Lambda}$ - disrupting the binary Love relations as found for stars on the hadronic branch.
+We conclude that quark-hadron stars may or may not obey these ``hadronic" universal relations, depending on the location of transition, and the difference between constituent masses in the binary.
+\begin{figure}
+\begin{center} 
+\includegraphics[width=\columnwidth]{hybrid.pdf}
+\end{center}
+\caption{
+\zc{Redo this image in xmgrace.}
+Fractional difference from the improved binary Love relations fit for a representative set of constrained nuclear matter EoSs (gray cirlces), and 30 selected NS binaries from the ACB5 hybrid EoS.
+In particular, these binary pairs are selected from each of the following categories: (i) binaries with which one massive star has a quark matter core, while the other is pure hadronic matter (i.e.
+small enough mass that the transition point has not yet been reached), denoted QS/HS (red triangles); (ii) binary with both small-mass hadron stars, denoted HS/HS (purple triangles); and (iii) binary with both large-mass stars with quark matter cores, denoted QS/QS (magenta triangles.
+}
+\label{fig:hybrid}
+\end{figure}
 
@@
 We find an improvement upon these universal relations by a factor of 25\% for stars with mass below 1.7 solar masses\zc{check this number} by restricting to the EoSs constrained by GW170817.
+In addition, we find that binaries consisting of one massive hyrid quark-hadron star, and one small-mass hadron star do not obey these universal relations -- explained by the large difference in $\tilde{\Lambda}$ displayed between the constituent stars.
 Further, we analyze the impact of this improvement for future binary NS merger detections, as the current detector sensitivity is not yet small enough to accurately constrain $\tilde{\Lambda}$ enough for universal relations to make a difference.
@@
 If verified, this provides a possible avenue of EoS constraint via considering only spectrally generated EoSs which support maximum NS mass in agreeance with J1748-2021B.
-\zc{Should we talk about this here? More future directions?}
+\zc{Should we talk about these here? More future directions?}
 

### 2018-11-21 paper/bin-love-after-gw170817.tex
finished XMgrace figures in paper draft

@@
 Unfortunately, current detectors are only sensitive enough to accurately measure the dominant tidal parameter, $\tilde{\Lambda}$, known as the chirp deformability.
-Previous work by Yagi \textit{et al.}~\cite{Yagi:binLove} resolved this issue by finding approximately EoS-insensitive ``binary Love universal relations" between symmetric and anti-symmetric combinations of tidal deformabilities $\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$.
+Previous work by Yagi and Yunes~\cite{Yagi:binLove} resolved this issue by finding approximately EoS-insensitive ``binary Love universal relations" between symmetric and anti-symmetric combinations of tidal deformabilities $\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$.
 This allows one to further break degeneracies between tidal parameters, resulting in both (i) a decrease in uncertainty upon parameter extraction on the removal of one parameter from the model, and (ii) the ability to measure the secondary tidal parameter upon measurement of the first.
@@
 \begin{center} 
-\includegraphics[width=\columnwidth]{stackedFisher.pdf}
+\includegraphics[width=\columnwidth]{stackedFisher.eps}
 \end{center}
 \caption{
-\zc{Redo this image in xmgrace.}
 Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue) in the extraction of $\tilde{\Lambda}$ from GW170817 (O2) as if observed with future interferometers aLIGO, a++, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
-This is compared to the combined uncertainty $\sigma^A_N$ (orange) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the expected rate of binary NS observations for O2, aLIGO, a\texttt{++}, Voyager, CE, and ET-D over 1 observing run: 1, 22, 177, 2409, 128310, and 674958 respectively.
-It can be seen that the statistical errors in parameter extraction become comparable to the systematics from EoS variation in binary Love relations (magenta) for Voyager and on.
+This is compared to the combined uncertainty $\sigma^A_N$ (red) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the expected rate of binary NS observations for O2, aLIGO, a\texttt{++}, Voyager, CE, and ET-D over 1 observing run: 1, 22, 177, 2409, 128310, and 674958 respectively.
+It can be seen that the statistical errors in parameter extraction become comparable to the systematics from EoS variation in binary Love relations (purple) for Voyager and on.
 Note the approximation for $\sigma^A_N$ under the O2 detector sensitivity is a poor estimate due to the small number of stacked events, $N_{\text{O2}}=1$, resulting in a high degree of randomness in population generation.
@@
 We then utilize the posterior defined by GW170817 by rejecting any EoS sample which does not lie within the 90\% credible posterior region, resulting in a sample of 35 EoSs shown in Fig.~\ref{fig:eos}.
-Following~\cite{Read2009}, the parameterized high-density core EoSs generated above are matched to the low-density crust EoS Sly~\cite{Douchin:2001sv} at the density such that the pressures are equal.
+Following~\cite{Read2009}, the parameterized high-density core EoSs generated above are matched to the low-density crust EoS Sly~\cite{Douchin:2001sv} at about half of the nuclear saturation density, $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$.
 For comparison, we also include a second sample of randomly generated EoSs, without restricting to GW170817s posterior.
@@
 \begin{center} 
-\includegraphics[width=\columnwidth]{EoSs.pdf}
+\includegraphics[width=\columnwidth]{EoSs.eps}
 \end{center}
 \caption{
-\zc{Redo this image in xmgrace.}Set of 35 randomly generated EoSs used in our analysis. 
-These were populated by uniformly sampling the spectral coefficient parameter space, then restricting to the 90\% credible level on EoS as derived by~\cite{LIGO:posterior}.
+Representative set of EoSs used in our analysis. 
+These were populated by uniformly sampling the spectral coefficient parameter space, then restricting to the 90\% credible level shown in cyan~\cite{LIGO:posterior}.
 In addition, the following constraints were also applied: (i) the EoS must have a causal structure within 10\%, and (ii) the EoS must support maximum NS mass of at least $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations.
+Finally, the high density core EoSs generated above were stitched to the low-density crust EoS of SLy~\cite{Douchin:2001sv} at $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$.
 }
@@
 Current gravitational wave interferometry is not yet sensitive enough to accurately extract both tidal parameters $\tilde{\Lambda}$ and $\delta\tilde{\Lambda}$.
-In a search to remedy this, important previous work by Yagi \textit{et al.}~\cite{Yagi:binLove} found that symmetric and antisymmetric combinations of tidal deformabilities:
+In a search to remedy this, important previous work by Yagi and Yunes~\cite{Yagi:binLove} found that symmetric and antisymmetric combinations of tidal deformabilities:
 \begin{equation}
@@
 \subsection{I-Love-Q relations}\label{sec:ilq}
-Here we present our results on I-Love-Q universality as compared to Fig. 1 of Yagi \textit{et al.}~\cite{Yagi:ILQ}.
+Here we present our results on I-Love-Q universality as compared to Fig. 1 of Yagi and Yunes~\cite{Yagi:ILQ}.
 Following this work, the data for each universal relation is fit to the following curve:
@@
 \begin{center} 
-\includegraphics[width=\textwidth]{ILQ.pdf}
+\includegraphics[width=\textwidth]{ILQ.eps}
 \end{center}
 \caption{
-\zc{Redo this image in xmgrace.}
 I-Love universal relations shown for the constrained EoSs (left) and unconstrained EoSs (right).
-In this figure, the black line corresponds to the fit given by Eq.~\ref{eq:ILQfit}, while all other colors correspond to the 35 EoSs used in each case.
+In these figures, the black dashed lines corresponds to the fit given by Eq.~\ref{eq:ILQfit}, while all other colors correspond to the 35 EoSs used in each case.
 The maximal EoS variation from the fit for unconstrained EoSs is $0.88\%$, which is comparable to the $1\%$ found in~\cite{Yagi:ILQ}.
@@
 \begin{center} 
-\includegraphics[width=\textwidth]{binLove.pdf}
+\includegraphics[width=\textwidth]{binLove.eps}
 \end{center}
 \caption{
-\zc{Redo this image in xmgrace.}
 Binary Love universal relations shown for the constrained EoSs (left) and unconstrained EoSs (right).
-In this figure, the solid black line corresponds to the fit given by Eq.~\ref{eq:binLovefit}, while the solid, dashed, and dotted colored lines represent the 35 EoSs for mass ratios of $q=0.9$, $q=0.75$, and $q=0.50$, respectively.
+In this figure, the dashed black line corresponds to the fit given by Eq.~\ref{eq:binLovefit}, while the dotted blue, dashed magenta, and solid green lines represent the 35 EoSs for mass ratios of $q=0.9$, $q=0.75$, and $q=0.50$, respectively.
 The maximal EoS variation for each value of $q$ is $23.65\%$, $9.76\%$, and $2.15\%$ respectively, compared to $\sim 50\%$, $\sim 20\%$, and $\sim 3\%$ found in Ref.~\cite{Yagi:binLove}.
@@
 \begin{center} 
-\includegraphics[width=\columnwidth]{hybrid.pdf}
+\includegraphics[width=\columnwidth]{hybrid.eps}
 \end{center}
 \caption{
-\zc{Redo this image in xmgrace.}
 Fractional difference from the improved binary Love relations fit for a representative set of constrained nuclear matter EoSs (gray cirlces), and 30 selected NS binaries from the ACB5 hybrid EoS.
 In particular, these binary pairs are selected from each of the following categories: (i) binaries with which one massive star has a quark matter core, while the other is pure hadronic matter (i.e.
-small enough mass that the transition point has not yet been reached), denoted QS/HS (red triangles); (ii) binary with both small-mass hadron stars, denoted HS/HS (purple triangles); and (iii) binary with both large-mass stars with quark matter cores, denoted QS/QS (magenta triangles.
+small enough mass that the transition point has not yet been reached), denoted QS/HS (green triangles); (ii) binary with both small-mass hadron stars, denoted HS/HS (red squares); and (iii) binary with both large-mass stars with quark matter cores, denoted QS/QS (magenta diamonds).
 }
@@
 \begin{center} 
-\includegraphics[width=\columnwidth]{sensitivities.pdf}
+\includegraphics[width=\columnwidth]{sensitivities.eps}
 \end{center}
 \caption{
-\zc{redo this image in xmgrace}
 Square root of of the spectral noise densities $\sqrt{S_n^A(f)}$ plotted for detectors ($A$): LIGO O2 (orange), aLIGO (green), a\texttt{++} (purple), Voyager (magenta), CE (red), and ET-D (blue) as interpolated from publicly available data\zc{cite}.
@@
 We take advantage of this by generating a restricted set of spectral EoSs which agree with this observation to reduce uncertainties upon the extraction of tidal parameters from future GW events.
-Important previous work by Yagi \text{et al.}~\cite{Yagi:ILQ,Yagi:binLove} found EoS-insensitive universal relations between symmetric and antisymmetric combinations of NS tidal deformabilities, which aid in the extraction of said tidal parameters.
+Important previous work by Yagi and Yunes~\cite{Yagi:ILQ,Yagi:binLove} found EoS-insensitive universal relations between symmetric and antisymmetric combinations of NS tidal deformabilities, which aid in the extraction of said tidal parameters.
 We find an improvement upon these universal relations by a factor of 25\% for stars with mass below 1.7 solar masses\zc{check this number} by restricting to the EoSs constrained by GW170817.

### 2018-11-26 paper/bin-love-after-gw170817.tex
added lots of stuff to the paper from last weeks meeting

@@
 Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue) in the extraction of $\tilde{\Lambda}$ from GW170817 (O2) as if observed with future interferometers aLIGO, a++, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
-This is compared to the combined uncertainty $\sigma^A_N$ (red) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the expected rate of binary NS observations for O2, aLIGO, a\texttt{++}, Voyager, CE, and ET-D over 1 observing run: 1, 22, 177, 2409, 128310, and 674958 respectively.
+This is compared to the combined uncertainty $\sigma^A_N$ (red) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper (teal), central (orange), and lower (magenta) limits of expected binary NS merger detection rates for O2, aLIGO, a\texttt{++}, Voyager, CE, and ET-D over 1 observation year.
 It can be seen that the statistical errors in parameter extraction become comparable to the systematics from EoS variation in binary Love relations (purple) for Voyager and on.
@@
 These values are comparable to the maximal EoS variation for unconstrained EoSs as expected, found to be $41.66\%$, $12.64\%$, and $3.83\%$.
+Additionally shown is the binary Love relations for hybrid stars (dash-dash-dotted curves) as discussed in Sec.~\label{sec:hybrid}.
+Observe the large deviations from the fit as the mass ratio $q$ increases, returning near the fit before the transitional pressure at large values of $\Lambda_s$.
 }
@@
 \subsubsection{Hybrid quark-hadron stars}\label{sec:hybrid}
+\begin{figure}
+\begin{center} 
+\includegraphics[width=\linewidth]{hybridML.eps}
+\end{center}
+\caption{
+$M-\tilde{\Lambda}$ relations for the ACB5 model hybrid star. 
+Note the strong phase transition into a quark-matter branch at $\sim 1.4 \text{ M}_{\odot}$.
+As described in the text, HS/HS and NS/NS binaries have individual masses chosen such that both stars are contained within one branch -- resulting in high $q$ values.
+Constrastingly, HS/NS binaries have individual masses chosen from each branch resulting in small $q-values$.
+}
+\label{fig:hybridML}
+\end{figure} 
 Transitional quark-hadron matter stars undergo first-order phase transitions at pressure $P_{\text{tr}}$, where the hadronic branch departs into a quark-matter branch at a given mass transition.
-We focus on the ACB5 model, which observes a transition mass at $\sim 1.4 \text{ M}_{\odot}$~\cite{Paschalidis2018}.
-This results in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq 1.4 \text{ M}_{\odot}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote this as ``QS"), and (ii) small-mass ($M \leq 1.4 \text{ M}_{\odot}$) hadronic stars with no internal transition to quark matter (we denote this as ``HS").
+We focus on the ACB5 model shown in Fig.~\ref{fig:hybridML}, which observes a transition mass at $\sim 1.4 \text{ M}_{\odot}$~\cite{Paschalidis2018}.
+This results in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq 1.4 \text{ M}_{\odot}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote this as ``HS"), and (ii) small-mass ($M \leq 1.4 \text{ M}_{\odot}$) hadronic stars with no internal transition to quark matter (we denote this as ``NS").
 We consider 3 classes of binaries:
 \begin{itemize}
-\item QS/HS binary: consists of one massive hybrid star, and one small hadronic star,
-\item HS/HS binary: consists of two small-mass hadronic stars,
-\item QS/QS binary: consists of two massive hybrid stars.
+\item HS/NS binary: consists of one massive hybrid star, and one small hadronic neutron star,
+\item NS/NS binary: consists of two small-mass hadronic neutron stars,
+\item HS/HS binary: consists of two massive hybrid stars.
 \end{itemize}
@@
 The results are shown in Fig.~\ref{fig:hybrid}.
-First, we observe that the HS/HS combination of stars gives consistent results to that found earlier -- as expected.
-Next, we see that QS/QS combinations agree moderately with previous relations\footnote{Note that these EoSs do not fit within GW170817's 90\% posterior on EoS - so we excpect deviations consistent with the ``unconstrained" set of EoSs, rather than the ``constraind" set.}, while QS/HS combinations disagree significantly.
+First, we observe that the NS/NS combination of stars gives consistent results to that found earlier -- as expected.
+Next, we see that HS/HS combinations agree moderately with previous relations\footnote{Note that these EoSs do not fit within GW170817's 90\% posterior on EoS - so we excpect deviations consistent with the ``unconstrained" set of EoSs, rather than the ``constraind" set.}, while HS/NS combinations disagree significantly.
 This can be explained by the large reduction in tidal deformability for hybrid stars, are shown in Fig.
 2 of Ref.~\cite{Paschalidis2018}: when one star lies on the hadronic branch while the other is on the quark branch, they each see vast differences in $\tilde{\Lambda}$ - disrupting the binary Love relations as found for stars on the hadronic branch.
+In addition, the discrepancy can be seen in Fig.~\ref{fig:binLove} where the binary Love relations for the ACB5 EoS is shown in relation to the constrained nuclear matter EoSs.
+Observe how the residuals from the fit are quite good for low pressures (large $\Lambda_s$) when the the binaries consist of a NS/NS combination, before reaching the transitional pressure when the deviations become increasingly large for HS/HS and HS/NS binaries.
 We conclude that quark-hadron stars may or may not obey these ``hadronic" universal relations, depending on the location of transition, and the difference between constituent masses in the binary.
@@
 In particular, these binary pairs are selected from each of the following categories: (i) binaries with which one massive star has a quark matter core, while the other is pure hadronic matter (i.e.
-small enough mass that the transition point has not yet been reached), denoted QS/HS (green triangles); (ii) binary with both small-mass hadron stars, denoted HS/HS (red squares); and (iii) binary with both large-mass stars with quark matter cores, denoted QS/QS (magenta diamonds).
+small enough mass that the transition point has not yet been reached), denoted HS/NS (green triangles); (ii) binary with both small-mass hadron stars, denoted NS/NS (red squares); and (iii) binary with both large-mass stars with quark matter cores, denoted HS/HS (magenta diamonds).
 }
@@
 \item Generate a population of $N_A$ events corresponding to the expected binary NS merger detection rate for detector $A$, following the distribution $f=3 \rho_{\text{th}}^3/\rho^4$~\cite{Shutz:SNR,Chen:SNR} with a network SNR threshold of $\rho_{\text{th}}=8$.
-We approximate this rate to be proportional to the cube of SNR ratios over 1 observing run: $N_A = N_{\text{O2}} (\rho^A_{\text{GW170817}}/\rho^{\text{O2}}_{\text{GW170817}})^3$, where $N_{\text{O2}}=1$, giving the rates shown inthe second column of Table~\ref{tab:variances}.
+This is calculated for the upper, central, and lower limits of the local binary NS coalescence rate density $R=1540^{+3200}_{-1220} \text{ Gpc}^{-3}\text{yr}^{-1}$~\cite{Abbott2017}, giving the rates shown in the second column of Table~\ref{tab:variances}.
 \item Compute the population standard deviation given by:
@@
 
-\begin{table}[ht!]
+\begin{table*}[ht!]
 \centering
 \caption{
-Tabulated results for the estimated statistical errors on $\tilde{\Lambda}$ for the combined results of $N_A$ detections corresponding to the estimated binary NS merger detection rate.
+Tabulated results for the estimated statistical errors on $\tilde{\Lambda}$ for the combined results of $N_A$ detections corresponding to the estimated upper, central, and lower limits of the binary NS merger detection rate $R$.
 This is repeated for 5 future detector sensitivities: aLIGO, a\texttt{++}, Voyager, CE, and ET.
@@
 }\label{tab:variances}
-\begin{tabular}{ c || c  c  c c } 
+\begin{tabular}{ c || c c c c c c c c} 
 \hline
-Detector ($A$) & $N_A$ & $\rho^A_{\text{GW170817}}$ & $\sigma^A_{\text{GW170817}}$ & $\sigma^A_N$\\
+Detector ($A$) & $N_A (\text{Lower})$ & $N_A (\text{Central})$ & $N_A (\text{Upper})$ & $\rho^A_{\text{GW170817}}$ & $\sigma^A_{\text{GW170817}}$ & $\sigma^A_N (\text{Lower})$ & $\sigma^A_N (\text{Central})$ & $\sigma^A_N (\text{Large})$\\
 \hline
 \hline
-O2 & $1$ & $32.40$ & $168.40$ & $314.90$\\
-aLIGO & $22$ & $90.74$ & $75.44$ & $70.37$\\
-a\texttt{++} & $177$ & $180.95$ & $31.55$ & $27.96$\\
-Voyager & $2409$ & $428.89$ & $16.69$ & $10.21$\\
-CE & $128310$ & $1398.03$ & $4.85$ & $1.39$\\
-ET-D & $674958$ & $2807.45$ & $6.26$ & $1.53$\\
+O2 & $1$ & $1$ & $1$ & $32.40$ & $168.40$ & $558.18$ & $393.24$ & $279.44$\\
+aLIGO & $23$ & $112$ & $344$ & $90.74$ & $75.44$ & $117.022$ & $42.89$ & $24.27$\\
+a\texttt{++} & $208$ & $1004$ & $3091$ & $180.95$ & $31.55$ & $27.62$ & $13.36$ & $7.36$\\
+Voyager & $3854$ & $1.85 \times 10^4$ & $5.71 \times 10^4$ & $428.89$ & $16.69$ & $8.57$ & $3.78$ & $2.16$\\
+ET-D & $1.35\times 10^7$ & $6.50\times 10^7$ & $2.00\times 10^8$ & $2807.45$ & $6.26$ & $0.78$ & $0.35$ & $0.20$\\
+CE & $3.98\times 10^5$ & $1.91\times 10^6$ & $5.89\times 10^6$ & $1398.03$ & $4.85$ & $0.34$ & $0.16$ & $0.10$\\
 \hline
 \end{tabular}
-\end{table}
+\end{table*}
 
@@
 If verified, this provides a possible avenue of EoS constraint via considering only spectrally generated EoSs which support maximum NS mass in agreeance with J1748-2021B.
-\zc{Should we talk about these here? More future directions?}
+\zc{Should we talk about this here?}
+In addition, separate binary Love universal relations for hybrid star binaries should be investigated.
 

### 2018-11-27 paper/bin-love-after-gw170817.tex
added comments

--- 2018-11-21 paper/bin-love-after-gw170817.tex
@@
 \include{preamble}
+
+\definecolor{red(ncs)}{rgb}{0.77, 0.01, 0.2}
+\newcommand{\ny}[1]{\textcolor{blue}{NY: #1} }
 
@@
 \frac{d \epsilon(p)}{dp}=\frac{\epsilon(p)+p}{p \Gamma(p)}.
-\end{equation}9
+\end{equation}
 Using this formalism, any valid EoS can be approximated through choice of 4 or more spectral coefficients $\gamma_k$, tabulated for several common EoSs in Table 1 of~\cite{Lindblom:2018rfr}.
@@
 For comparison, we also include a second sample of randomly generated EoSs, without restricting to GW170817s posterior.
+{\ny{It would be good to make this figure a double pane one, so that you can show the constrained set and the unconstrained set side-by-side.}}
 \begin{figure}
@@
 
+{\ny{Let me play devil's advocate and explain things I could potentially be worried about.
+\begin{itemize}
+\item The constrained and the unconstrained data set of I-Love that you are fitting, do they have the same number of data points?
+If not, how do you know your fits and the comparisons are reliable to variation on the data set?
+You can study this by re-doing this analysis with the same amount of data in both sets of EoSs and then repeating the analysis with twice the amount of data to see how the results change.
+\item  The unconstrained set does not contain the same EoSs as the constrained set plus additional ones that are ruled out.
+This makes comparison of the sets a bit more difficult, because they are randomly sampled.
+How do you know your comparisons are robust to the number of EoSs you have randomly chosen without your probability distribution?
+You can study this by re-doing this analysis with twice the number of drawn EoSs to see how the results change.
+\item In the constrained set, there seems to be 3 EoSs that have the ``largest'' difference.
+What makes these EoSs special?
+Do they have anything in common?
+Same question for the unconstrained data set, but there are 2 special ones this time.
+\end{itemize}
+}}
 Fig.~\ref{fig:ILQ} shows the improved I-Love universal relation between dimensionless moment of inertia $\bar{I} \equiv I/M^3$ and dimensionless tidal deformability $\Lambda$ for both constrained and unconstrained sets of EoSs.
@@
 Further, both EoS samples show improvement from the original result of $\approx 1\%$ displayed in~\cite{Yagi:ILQ}.
+
+{\ny{This comment is related to the list above, but I'm worried about how robust these numbers quoted above to *2* sig figs are...}}
+
 \begin{figure*}
@@
 
+{\ny{I think it would be worth studying whether there is a better fitting function that one can use for the constrained set.
+The functional form in Eq.
+(6) does not limit properly to the Newtonian result or to the relativistic result.
+But we do know how I-Love for example scales in the Newtonian limit, so could we e.g.
+peel off the asymptotic behavior analytically, and then correct this with a fitting function?
+This is similar to what Kent and I did in the past in a paper (in the binary love actually) and also similar to the way EoB works.}}
+
 \subsection{Binary love relations}\label{sec:binary}
@@
 This is followed in Sec.~\ref{sec:hybrid} by an analysis and discussion into how well hybrid stars agree with the improved binary Love relations
+
+{\ny{Why do we consider hybrid stars only in this subsection? Why not also include these in the I-Love studies?}}
 
@@
 
+{\ny{I have very similar comments here to those I listed in the I-Love relation section.}}
+
 \subsubsection{Hybrid quark-hadron stars}\label{sec:hybrid}
@@
 \end{itemize}
+
+{\ny{The comparison below is a bit misleading because all you have shown is that the fitting coefficients for the standard stars do not work when dealing with mixed stars.
+I think it would be interesting to see how the binary love relations look when you include hybrid systems (something like Fig.
+5 but for QS/QS and for QS/HS).
+Also I think it would be interesting to either (i) redo the fits including the QS/QS and QS/HS data and or (ii) produce different fits for those families, and then you can compare either of these to a wide set of systems to determine the validity of the fit.}}
 

### 2018-11-28 paper/bin-love-after-gw170817.tex
Comments by Katerina

@@
 \newcommand{\ny}[1]{\textcolor{blue}{NY: #1} }
+\newcommand{\kc}[1]{\textcolor{red}{KC: #1} }
 
@@
 We then utilize the posterior defined by GW170817 by rejecting any EoS sample which does not lie within the 90\% credible posterior region, resulting in a sample of 35 EoSs shown in Fig.~\ref{fig:eos}.
+\kc{Why aren't we directly using the gamma's that Carl provided?}
 Following~\cite{Read2009}, the parameterized high-density core EoSs generated above are matched to the low-density crust EoS Sly~\cite{Douchin:2001sv} at about half of the nuclear saturation density, $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$.
@@
 
+\kc{why not study the I-Q relation too?}
 \subsection{Binary love relations}\label{sec:binary}
@@
 Observe that the maximum systematic error attained for the constrained EoSs is $\sigma_{\tilde{\Lambda}}=10$ (this is found to be $20$ for the unconstrained EoSs).
-This is negligible compared to the statistical errors accrued on paramter extraction from GW170817.
+This is negligible compared to the statistical errors accrued on paramter extraction from GW170817.\kc{Similar to an earlier comment, I think we should use the "posterior" EoSs since they were directly computed from the data.}
 }

### 2018-11-28 paper/bin-love-after-gw170817.tex
commiting paper updates before pulling Katerinas update

--- 2018-11-27 paper/bin-love-after-gw170817.tex
@@
 }\label{tab:variances}
-\begin{tabular}{ c || c c c c c c c c} 
-\hline
-Detector ($A$) & $N_A (\text{Lower})$ & $N_A (\text{Central})$ & $N_A (\text{Upper})$ & $\rho^A_{\text{GW170817}}$ & $\sigma^A_{\text{GW170817}}$ & $\sigma^A_N (\text{Lower})$ & $\sigma^A_N (\text{Central})$ & $\sigma^A_N (\text{Large})$\\
-\hline
-\hline
-O2 & $1$ & $1$ & $1$ & $32.40$ & $168.40$ & $558.18$ & $393.24$ & $279.44$\\
-aLIGO & $23$ & $112$ & $344$ & $90.74$ & $75.44$ & $117.022$ & $42.89$ & $24.27$\\
-a\texttt{++} & $208$ & $1004$ & $3091$ & $180.95$ & $31.55$ & $27.62$ & $13.36$ & $7.36$\\
-Voyager & $3854$ & $1.85 \times 10^4$ & $5.71 \times 10^4$ & $428.89$ & $16.69$ & $8.57$ & $3.78$ & $2.16$\\
-ET-D & $1.35\times 10^7$ & $6.50\times 10^7$ & $2.00\times 10^8$ & $2807.45$ & $6.26$ & $0.78$ & $0.35$ & $0.20$\\
-CE & $3.98\times 10^5$ & $1.91\times 10^6$ & $5.89\times 10^6$ & $1398.03$ & $4.85$ & $0.34$ & $0.16$ & $0.10$\\
-\hline
+%\begin{tabular}{ c || c c c c c c c c} 
+%\hline
+%Detector ($A$) & $N_A (\text{Lower})$ & $N_A (\text{Central})$ & $N_A (\text{Upper})$ & $\rho^A_{\text{GW170817}}$ & $\sigma^A_{\text{GW170817}}$ & $\sigma^A_N (\text{Lower})$ & $\sigma^A_N (\text{Central})$ & $\sigma^A_N (\text{Upper})$\\
+%\hline
+%\hline
+%O2 & $1$ & $1$ & $1$ & $32.40$ & $168.40$ & $558.18$ & $393.24$ & $279.44$\\
+%aLIGO & $23$ & $112$ & $344$ & $90.74$ & $75.44$ & $117.022$ & $42.89$ & $24.27$\\
+%a\texttt{++} & $208$ & $1004$ & $3091$              & $180.95$ & $31.55$ &               $27.62$ & $13.36$ & $7.36$\\
+%Voyager & $3854$ & $1.85 \times 10^4$ & $5.71 \times 10^4$ &              $428.89$ & $16.69$              & $8.57$ & $3.78$ & $2.16$\\
+%ET-D & $3.98\times 10^5$ & $1.91\times 10^6$ & $5.89\times 10^6$ &                  $2807.45$ & $6.26$ &               $0.78$ & $0.35$ & $0.20$\\
+%CE & $1.35\times 10^7$ & $6.50\times 10^7$ & $2.00\times 10^8$ &                 $1398.03$ & $4.85$ &                 $0.34$ & $0.16$ & $0.10$\\
+%\hline
+%\end{tabular}
+\begin{tabular}{|c|@{\extracolsep{4pt}}c@{\extracolsep{0pt}}|c|@{\extracolsep{4pt}}C{1.7cm}@{\extracolsep{-2pt}}|C{1.7cm}|@{\extracolsep{-2pt}}C{1.7cm}@{\extracolsep{2pt}}|c|@{\extracolsep{0pt}}c@{\extracolsep{0pt}}|c|}
+\cline{1-1}\cline{2-3}\cline{4-9}
+    \multicolumn{1}{|c|}{\bfseries Detectors (A)} & \multicolumn{2}{|c|}{\bfseries GW170817} & \multicolumn{6}{|c|}{\bfseries Multiple events} \\
+\cline{1-1}\cline{2-3}\cline{4-9}
+\noalign{\smallskip}
+\cline{2-3}\cline{4-6}\cline{7-9}
+\multicolumn{1}{c}{} & \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \multicolumn{3}{|c|}{} & \multicolumn{3}{|c|}{}
+\\[-1em]
+\multicolumn{1}{c}{}  &  \multicolumn{1}{|c|}{\multirow{2}{*}{$\rho^A_{\text{GW170817}}$}}  &  \multirow{ 2}{*}{$\sigma^A_{\text{GW170817}}$}  &  \multicolumn{3}{|c|}{$N_A$}  &  \multicolumn{3}{|c|}{$\sigma^A_N$}  \\
+\cline{4-6}\cline{7-9}
+\multicolumn{1}{c}{}  &  \multicolumn{1}{|c|}{}  &  \multicolumn{1}{c|}{}  &  \multicolumn{1}{|c|}{Low}  &  \multicolumn{1}{c|}{Central} &  \multicolumn{1}{c|}{High}  & \multicolumn{1}{|c|}{Low}  &  \multicolumn{1}{c|}{Central} &  \multicolumn{1}{c|}{High}\\
+\cline{2-3}\cline{4-6}\cline{7-9}
+\noalign{\smallskip}
+\noalign{\smallskip}
+\cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
+ O2  & \multicolumn{1}{|c|}{$32.40$}  & $168.40$ &  \multicolumn{1}{|c|}{$1$} & $1$ & $1$ & \multicolumn{1}{|c|}{$558.18$} & $393.24$ & $279.44$\\
+\cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
+ aLIGO  & \multicolumn{1}{|c|}{$90.74$}  & $75.44$ &  \multicolumn{1}{|c|}{$23$} & $112$ & $344$ & \multicolumn{1}{|c|}{$117.022$} & $42.89$ & $24.27$\\
+\cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
+ a\texttt{++}  & \multicolumn{1}{|c|}{$180.95$}  & $31.55$ &  \multicolumn{1}{|c|}{$208$} & $1004$ & $3091$ & \multicolumn{1}{|c|}{$27.62$} & $13.36$ & $7.36$\\
+\cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
+
+\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{}
+\\[-1em]
+
+ Voyager  & \multicolumn{1}{|c|}{$428.89$}  & $16.69$ &  \multicolumn{1}{|c|}{$3854$} & $1.85 \times 10^4$ & $5.71 \times 10^4$ & \multicolumn{1}{|c|}{$8.57$} & $3.78$ & $2.16$\\
+\cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
+
+\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{}
+\\[-1em]
+
+ ET-D  & \multicolumn{1}{|c|}{$2807.45$}  & $6.26$ &  \multicolumn{1}{|c|}{$3.98 \times 10^5$} & $1.91 \times 10^6$ & $5.89 \times 10^6$ & \multicolumn{1}{|c|}{$0.78$} & $0.35$ & $0.20$\\
+\cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
+
+\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{}
+\\[-1em]
+
+ CE  & \multicolumn{1}{|c|}{$1398.03$}  & $4.85$ &  \multicolumn{1}{|c|}{$1.35 \times 10^7$} & $6.50 \times 10^7$ & $2.00 \times 10^8$ & \multicolumn{1}{|c|}{$0.34$} & $0.16$ & $0.10$\\
+\cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
 \end{tabular}

### 2018-11-28 paper/bin-love-after-gw170817.tex
resolving conflict

@@
 \include{preamble}
-
-\definecolor{red(ncs)}{rgb}{0.77, 0.01, 0.2}
-\newcommand{\ny}[1]{\textcolor{blue}{NY: #1} }
-\newcommand{\kc}[1]{\textcolor{red}{KC: #1} }
 
@@
 These values are comparable to the maximal EoS variation for unconstrained EoSs as expected, found to be $41.66\%$, $12.64\%$, and $3.83\%$.
-Additionally shown is the binary Love relations for hybrid stars (dash-dash-dotted curves) as discussed in Sec.~\label{sec:hybrid}.
+Additionally shown is the binary Love relations for hybrid stars ACB5 and ACB7 (dash-dash-dotted curves) as discussed in Sec.~\ref{sec:hybrid}.
 Observe the large deviations from the fit as the mass ratio $q$ increases, returning near the fit before the transitional pressure at large values of $\Lambda_s$.
@@
 \caption{
-$M-\tilde{\Lambda}$ relations for the ACB5 model hybrid star. 
+$M-\tilde{\Lambda}$ relations for the ACB5 and ACB7 model hybrid stars. 
 Note the strong phase transition into a quark-matter branch at $\sim 1.4 \text{ M}_{\odot}$.
 As described in the text, HS/HS and NS/NS binaries have individual masses chosen such that both stars are contained within one branch -- resulting in high $q$ values.
-Constrastingly, HS/NS binaries have individual masses chosen from each branch resulting in small $q-values$.
+Constrastingly, HS/NS binaries have individual masses chosen from each branch resulting in small $q$-values.
 }
@@
 Transitional quark-hadron matter stars undergo first-order phase transitions at pressure $P_{\text{tr}}$, where the hadronic branch departs into a quark-matter branch at a given mass transition.
-We focus on the ACB5 model shown in Fig.~\ref{fig:hybridML}, which observes a transition mass at $\sim 1.4 \text{ M}_{\odot}$~\cite{Paschalidis2018}.
-This results in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq 1.4 \text{ M}_{\odot}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote this as ``HS"), and (ii) small-mass ($M \leq 1.4 \text{ M}_{\odot}$) hadronic stars with no internal transition to quark matter (we denote this as ``NS").
+We focus on the ACB5 and ACB7 models shown in Fig.~\ref{fig:hybridML}, which observe transition masses at $\sim 1.4 \text{ M}_{\odot}$~\cite{Paschalidis2018}.
+These result in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq 1.4 \text{ M}_{\odot}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote this as ``HS"), and (ii) small-mass ($M \leq 1.4 \text{ M}_{\odot}$) hadronic stars with no internal transition to quark matter (we denote this as ``NS").
 We consider 3 classes of binaries:
@@
 2 of Ref.~\cite{Paschalidis2018}: when one star lies on the hadronic branch while the other is on the quark branch, they each see vast differences in $\tilde{\Lambda}$ - disrupting the binary Love relations as found for stars on the hadronic branch.
-In addition, the discrepancy can be seen in Fig.~\ref{fig:binLove} where the binary Love relations for the ACB5 EoS is shown in relation to the constrained nuclear matter EoSs.
+In addition, the discrepancy can be seen in Fig.~\ref{fig:binLove} where the binary Love relations for the ACB5 and ACB7 EoSs are shown in relation to the constrained and unconstrained nuclear matter EoSs.
 Observe how the residuals from the fit are quite good for low pressures (large $\Lambda_s$) when the the binaries consist of a NS/NS combination, before reaching the transitional pressure when the deviations become increasingly large for HS/HS and HS/NS binaries.
@@
 We find an improvement upon these universal relations by a factor of 25\% for stars with mass below 1.7 solar masses\zc{check this number} by restricting to the EoSs constrained by GW170817.
+We also find an increase in I-Love-Q universality by a factor of 23\%.
 In addition, we find that binaries consisting of one massive hyrid quark-hadron star, and one small-mass hadron star do not obey these universal relations -- explained by the large difference in $\tilde{\Lambda}$ displayed between the constituent stars.

### 2018-12-18 paper/bin-love-after-gw170817.tex
lots of new updates and new analyses added to the paper, corresponding to past comments :)

--- 2018-11-28 paper/bin-love-after-gw170817.tex
@@
 \include{preamble}
-
-\definecolor{red(ncs)}{rgb}{0.77, 0.01, 0.2}
-\newcommand{\ny}[1]{\textcolor{blue}{NY: #1} }
 
@@
 
-\author{Frodo}
-\affiliation{}
+\author{Zachary Carson}
+\affiliation{%
+ Department of Physics, University of Virginia, Charlottesville, Virginia 22904, USA
+}%
 
-\author{Sam}
-\affiliation{}
+\author{Katerina Chatziioannou}
+\affiliation{%
+ Canadian Institute for Theoretical Astrophysics, 60 St. George Street, Toronto, Ontario, M5S 3H8, Canada
+}%
+\affiliation{%
+ Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY 10010
+}%
 
-\author{Pippin}
-\affiliation{}
+\author{Carl-Johan Haster}
+\affiliation{%
+ Canadian Institute for Theoretical Astrophysics, 60 St. George Street, Toronto, Ontario, M5S 3H8, Canada
+}%
+\affiliation{%
+ Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY 10010
+}%
 
-\author{Merry}
-\affiliation{}
+\author{Nicol\`as Yunes}
+\affiliation{%
+ Department of Physics, Montana State University, Bozeman, MT 59717, USA.
+}%
+\affiliation{%
+ Department of Physics and MIT Kavli Institute,
+}%
 
-\author{Gandalf}
-\affiliation{}
+\author{Kent Yagi}
+\affiliation{%
+ Department of Physics, University of Virginia, Charlottesville, Virginia 22904, USA
+}%
 
@@
 In this document, we explain how one can reduce equation of state variation for both binary Love and I-Love-Q universal relations, which helps to reduce systematic errors on the tidal measurement of binary neutron star mergers.
-We achieve this  by restricting to only equations of state drawn within the 90\% posterior constraint on pressure as a function of density, as derived by the LIGO Collaboration.
+We achieve this  by restricting to only equations of state drawn from the 90\% posterior constraint on pressure as a function of density, as derived by the LIGO Collaboration.
 % What we found
-We find an improvement in binary Love universality by a factor of 25\% for stars with mass below 1.7 solar masses, and in I-Love-Q universality by a factor of 22\%\zc{check these numbers}.
+We find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with a mass ratio of 0.75, and in I-Love-Q universality by factors of $\sim 50$\%.
 % Conclude
@@
 %Intro
-The dependance of pressure on density for supranuclear matter found primarily inside neutron stars (NSs) remains to be one of the largest mysteries in both nuclear physics and astrophysics.
+The dependence of pressure on density for supranuclear matter found primarily inside neutron stars (NSs) remains to be one of the largest mysteries in both nuclear physics and astrophysics.
 This internal structure of such stars, known as the equation of state (EoS), is exceedingly important, as it is the determining factor for many NS observables - such as the mass, the radius, and many more.
@@
 However, these implications suffer from large systematic errors due to astrophysical mismodeling.
-Alternatively, the emission of gravtiational waves (GWs) from binary NS merger events have proven to be a unique method of probing nuclear physics.
-During the early inspiral portion of the merger, the orbital separation is large enough that the effect of companion tidal fields is negligable. 
+Alternatively, the emission of gravitational waves (GWs) from binary NS merger events have proven to be a unique method of probing nuclear physics.
+During the early inspiral portion of the merger, the orbital separation is large enough that the effect of companion tidal fields is negligible. 
 As the separation decreases through GW emission, tidal forces are magnified and the NSs deform from sphericity, altering the orbital trajectories; a relic which is directly imprinted on the GW signal.
@@
 In the case of binary NSs, each star becomes deformed via the process highlighted above, resulting in two highly correlated tidal parameters $\Lambda_1$ and $\Lambda_2$ entering in the gravitational waveform.
-Due to high correlations between between the two paramters, independant extraction becomes very difficult at current interferometer sensitivities.\zc{cite?}
+Due to high correlations between between the two parameters, independent extraction becomes very difficult at current interferometer sensitivities.\zc{cite?}
 Typically, these high correlations can be reduced by strategically reparameterizing the waveform template with new tidal parameters constructed from linear combinations of $\Lambda_1$ and $\Lambda_2$.
@@
 In this paper we attempt to improve binary Love and I-Love-Q universal relations by imposing constraints on the EoS found by GW170817~\cite{LIGO:posterior,TheLIGOScientific:2017qsa}.
-First, we generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, where we (i) impose the restriction that they must lie within GW170817's 90\% credible region in pressure as a function of density, and (ii) don't impose any restrictions for comparison purposes.
-Next, we follow the important works of~\cite{Yagi:binLove} and~\cite{Yagi:ILQ} to show how the ``constrained" set of EoSs show improved universality from both the previous works, and the ``unconstrained" sample.
+First, we generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, where we (i) impose the restriction that they must be drawn from GW170817s 90\% credible posterior in pressure as a function of density, and (ii) don't impose any restrictions for comparison purposes.
+Next, we follow the important works of~\cite{Yagi:binLove} and~\cite{Yagi:ILQ} to show how the ``constrained" set of EoSs show improved universality from both the previous works, and the ``unconstrained" sample, shown by Fig.~\ref{fig:ILQ}.
 In addition, we determine the degree to which hybrid star EoSs obey binary Love universal relations.
-Lasty, through a simple Fisher analysis, we consider the value in improving universal relations by approximating when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in universal relations.
+Finally, through a simple Fisher analysis, we consider the value in improving universal relations by approximating when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in universal relations.
 
 %Final Results
-Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of 25\% for stars with mass below 1.7 solar masses, and in I-Love-Q universality by a factor of 22\%.
+Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with mass ratios of $0.75$, and in I-Love-Q universality by factors of $\sim50$\%, tabulated in Tab.~\ref{tab:maxVar}.
 We also find that binaries consisting of one massive hybrid star, and one small-mass hadronic star do not agree with derived binary Love relations, due to the large separation in $\tilde{\Lambda}$ between the constituent stars.
@@
 It can be seen that the statistical errors in parameter extraction become comparable to the systematics from EoS variation in binary Love relations (purple) for Voyager and on.
-Note the approximation for $\sigma^A_N$ under the O2 detector sensitivity is a poor estimate due to the small number of stacked events, $N_{\text{O2}}=1$, resulting in a high degree of randomness in population generation.
+Note there is no simulated populations of events under the O2 design sensitivity - due to there only being a single event during the observing period.
 These results are further tabulated in Table~\ref{tab:variances}.
@@
 We begin with a complementary background and theory material in Sec.~\ref{sec:theory}.
-We continue in Sec.~\ref{sec:universal} by finding new and improved binary Love and I-Love-Q universal relations, and considering how well hybrid star EoSs agree with the binary Love relations.
+We continue in Sec.~\ref{sec:universal} by finding new and improved binary Love and I-Love-Q universal relations, and considering how well hybrid star EoSs agree with the universal relations.
 We next examine these improved universal relations and question whether or not they are useful for future interferometers in Sec.~\ref{sec:observations}.
@@
 The structure of a NS and its tidal interactions in a binary system rely heavily on the underlying state function describing the relationship between pressure ($p$) and energy density ($\epsilon$), or equation of state, of nuclear matter.
-Given that all currently proposed EoSs utilize certain approximations, one method to study a wide range of physically realizeable EoSs is to parameterize them in a model-independent way.
+Given that all currently proposed EoSs utilize certain approximations, one method to study a wide range of physically realizable EoSs is to parameterize them in a model-independent way.
 Spectral representations~\cite{Lindblom:2010bb,Lindblom:2012zi,Lindblom:2013kra,Lindblom:2018rfr,Abbott:2018exr} parameterize EoSs by performing spectral expansions on the adiabatic index $\Gamma(p)$\footnote{Another way of parameterizing EoSs is the piecewise polytropic formulation~\cite{Read2009,Lackey:2014fwa,Carney:2018sdv}.}:
@@
 
-In the current analysis, we consider only EoSs which have been constrained by the recent binary neutron star merger event, GW170817.
-Important recent work~\cite{LIGO:posterior} uniformly sampled EoS parameters in order to derive a marginalized posterior on the pressure as a function of mass density, as seen in Fig.
+In the current analysis, we consider EoSs which have been constrained by the recent binary neutron star merger event, GW170817.
+Important recent work~\cite{LIGO:posterior} sampled EoS parameters in order to derive a marginalized posterior on the pressure as a function of mass density, as seen in Fig.
 2 of~\cite{LIGO:posterior}.
-In our work, we similarly sample spectral coefficients within the ranges: $\gamma_0 \in \lbrack 0.2,2 \rbrack$, $\gamma_1 \in \lbrack -1.6,1.7 \rbrack$, $\gamma_2 \in \lbrack -0.6,0.6 \rbrack$, $\gamma_0 \in \lbrack -0.02,0.02 \rbrack$, and further restricting the adiabatic index to be $\Gamma \in \lbrack 0.6,4.5 \rbrack$, ensuring our parameterization exposes a wide range of viable EoSs~\cite{Lindblom:parameters}.
-In addition, we impose similar constraints as was done in~\cite{LIGO:posterior}: (i) causality within 10\%, and (ii) EoS priors must support NS masses up to $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations.
-We then utilize the posterior defined by GW170817 by rejecting any EoS sample which does not lie within the 90\% credible posterior region, resulting in a sample of 35 EoSs shown in Fig.~\ref{fig:eos}.
+The spectral coefficients were sampled within the ranges: $\gamma_0 \in \lbrack 0.2,2 \rbrack$, $\gamma_1 \in \lbrack -1.6,1.7 \rbrack$, $\gamma_2 \in \lbrack -0.6,0.6 \rbrack$, $\gamma_0 \in \lbrack -0.02,0.02 \rbrack$, and further restricted the adiabatic index to be $\Gamma \in \lbrack 0.6,4.5 \rbrack$, ensuring the parameterization exposed a wide range of viable EoSs~\cite{Lindblom:parameters}.
+Additional constraints imposed upon the generated EoSs were as follows~\cite{LIGO:posterior}: (i) causality within 10\%, and (ii) EoS priors must support NS masses up to $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations.
+We utilize a random set of 100 of the above posterior samples defined by GW170817, furthermore referenced as the ``constrained EoSs", as shown in Fig.~\ref{fig:eos}.\zc{Carl, can you describe how you generated these?
+They aren't the \emph{actual} posteriors, are they?}
 Following~\cite{Read2009}, the parameterized high-density core EoSs generated above are matched to the low-density crust EoS Sly~\cite{Douchin:2001sv} at about half of the nuclear saturation density, $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$.
-For comparison, we also include a second sample of randomly generated EoSs, without restricting to GW170817s posterior.
-{\ny{It would be good to make this figure a double pane one, so that you can show the constrained set and the unconstrained set side-by-side.}}
+For comparison, we also include a second sample of 100 ``unconstrained" EoSs, randomly sampled in the pressure-density plane to be unrestricted by GW170817s posterior.
+
+In addition, we investigate 10 transitional quark-hadron matter stars, which undergo first-order phase transitions at pressure $P_{\text{tr}}$, where the hadronic branch departs into a quark-matter branch at a given mass transition~\cite{Paschalidis2018,Alford:2017qgh,1971SvA....15..347S,Zdunik:2012dj,Alford:2013aca}.
+In particular, we focus on the ACS and ACB models described in Ref.~\cite{Paschalidis2018}, shown in Fig.~\ref{fig:hybridML}.
+These result in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq \text{ M}_{\text{tr}}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote this as ``HS"), and (ii) small-mass ($M \leq \text{ M}_{\text{tr}}$) hadronic stars with no internal transition to quark matter (we denote this as ``NS").
+
 \begin{figure}
@@
 \caption{
-Representative set of EoSs used in our analysis. 
-These were populated by uniformly sampling the spectral coefficient parameter space, then restricting to the 90\% credible level shown in cyan~\cite{LIGO:posterior}.
-In addition, the following constraints were also applied: (i) the EoS must have a causal structure within 10\%, and (ii) the EoS must support maximum NS mass of at least $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations.
+Small representative sets of the constrained (left) and unconstrained (right) EoSs used in this analysis. 
+The constrained EoSs were populated by randomly selecting 100 posterior samples obtained from the GW170817 90\% credible level shown in cyan~\cite{LIGO:posterior}.
+Additionally, 100 unconstrained EoSs were generated by randomly sampling spectral coefficients of physically valid EoSs, with no further constrained applied.
+The following constraints were also applied to both sets of EoSs: (i) the EoS must have a causal structure within 10\%, and (ii) the EoS must support maximum NS mass of at least $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations.
 Finally, the high density core EoSs generated above were stitched to the low-density crust EoS of SLy~\cite{Douchin:2001sv} at $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$.
@@
 \label{fig:eos}
+\end{figure}
+
+\begin{figure}
+\begin{center} 
+\includegraphics[width=\linewidth]{hybridML.eps}
+\end{center}
+\caption{
+$M-\Lambda$ relations for the ACS and ACB class model hybrid stars. 
+Observe the transitional points where the NS transitions from the hadronic branch into a quark-matter branch.
+As described in the text, HS/HS and NS/NS binaries have individual masses chosen such that both stars are contained within one branch -- resulting in high $q$ values.
+Constrastingly, HS/NS binaries have individual masses chosen from each branch resulting in small $q$-values.
+}
+\label{fig:hybridML}
 \end{figure}
@@
 Consider a NS of mass $M$ in the presence of the tidal field $\varepsilon_{ij}$ of a companion star.
-In response, the NS will deform away from sphericity under the aquisition of quadrupole moment $Q_{ij}$, characterized by $\lambda$ as the linear response to $\varepsilon_{ij}$~\cite{Flanagan2008,hinderer-love,Yagi2013}:
+In response, the NS will deform away from sphericity under the acquisition of quadrupole moment $Q_{ij}$, characterized by $\lambda$ as the linear response to $\varepsilon_{ij}$~\cite{Flanagan2008,hinderer-love,Yagi2013}:
 \begin{equation}
@@
 Due to strong correlations between these parameters, individual extraction is very difficult with current interferometer sensitivity limitations.
-However, the waveform templates can be strategically reparameterized to instead include independant linear combinations of $\Lambda_1$ and $\Lambda_2$ to mitigate correlations between them. 
+However, the waveform templates can be strategically reparameterized to instead include independent linear combinations of $\Lambda_1$ and $\Lambda_2$ to mitigate correlations between them. 
 Any set of two independent functions may be used, for example: tidal parameters $\tilde{\Lambda}=\tilde{\Lambda}(\Lambda_1,\Lambda_2)$ and $\delta \tilde{\Lambda}=\delta \tilde{\Lambda}(\Lambda_1,\Lambda_2)$~\cite{Wade:tidalCorrections} first enter the gravitational waveform at 5PN and 6PN orders respectively, thus partially breaking degeneracies.
@@
 
-Similal universal relations have been found to exist between individual NS observables: moment of inertia (I), tidal deformability (Love), and quadrupole moment (Q), known as the ``I-Love-Q" universal relations~\cite{Yagi:ILQ}.
+Similar universal relations have been found to exist between individual NS observables: moment of inertia (I), tidal deformability (Love), and quadrupole moment (Q), known as the ``I-Love-Q" universal relations~\cite{Yagi:ILQ}.
 These have been found to be EoS insensitive by up to 1\% for each of pair of observables.
-In this paper, we show improvement in both of these universal relations by restricting to EoSs drawn within GW170817s posterior on pressure as a function of density.
+In this paper, we show improvement in both of these universal relations by restricting to EoSs sampled from GW170817s posterior on pressure as a function of density.
 %%%%%%%%%%%%%%%%%%%%%%%%% Begin universal relations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Universal relations}\label{sec:universal}
-In this section, we follow the analyses performed in~\cite{Yagi:binLove,Yagi:ILQ} with two new sets of 35 spectrally generated EoS: (i) those constrained by GW170817s 90\% credible region on pressure as a function of density as shown in Fig.~\ref{fig:eos}, and (ii) those unconstrained by any prior information.
-For the remainder of the paper, we refer to these distinct samples as ``constrained" and ``unconstrained."
+In this section, we follow the analyses performed in~\cite{Yagi:binLove,Yagi:ILQ} with two new sets of 100 spectrally generated EoS: (i) posterior samples randomly selected from GW170817s 90\% posterior on on pressure as a function of density as shown in the left panel of Fig.~\ref{fig:eos}, and (ii) those unconstrained by any prior EoS information, as shown in the right panel of Fig.~\ref{fig:eos}.
 
@@
 Here we present our results on I-Love-Q universality as compared to Fig. 1 of Yagi and Yunes~\cite{Yagi:ILQ}.
-Following this work, the data for each universal relation is fit to the following curve:
+In particular, we consider two distinct classes of NSs: nuclear matter EoSs and hybrid quark-hadron star EoSs as described in Sec.~\ref{sec:theory}.
+We begin in Sec.~\ref{sec:ilq-nuc} by fitting the new I-Love-Q universal relations using the constrained set of EoSs.
+This is followed in Sec.~\ref{sec:ilq-hyb} by an analysis and discussion into how well hybrid stars agree with the improved binary Love relations.
+
+\subsubsection{Nuclear matter stars}\label{sec:ilq-nuc}
+Following the work of Ref.~\cite{Yagi:ILQ}, the data for each universal relation is first fit to the following curve:
 \begin{equation}\label{eq:ILQfit}
@@
 where the updated coefficients are given in Table~\ref{tab:ILQfit}.
-In particular, we focus only on the I-Love universal relation for brevity, noting that the remaining relations Q-Love and I-Q show similar results.
+Additionally, we offer an improvement to the functional form of the I-Love-Q fitting curve. 
+Namely, we use the Newtonian relationships between various observables as a controlling factor in the fit~\cite{Yagi:ILQ}:
+\begin{equation}\label{eq:Newtonian}
+\bar{I}^{\text{N}} = C_{\bar{I}\Lambda}\Lambda^{2/5}, \hspace{3mm} \bar{Q}^{\text{N}} = C_{\bar{Q}\Lambda}\Lambda^{1/5}, \hspace{3mm} \bar{I}^{\text{N}} = C_{\bar{I}\bar{Q}}\bar{Q}^{2}.
+\end{equation}
+This is appended to an expansion in $\Lambda^{-1/5} \propto C$ (or $\bar{Q}^{-1/5}$), where $C=M/R$ is the compactness of the star.
+This results in the following overall fitting relation:
+\begin{equation}\label{eq:ILQfitNew}
+y=C_{yx} x^{\alpha} \frac{1+\sum_{i=1}^3 a_i x^{-i/5}}{1+\sum_{i=1}^3 b_i x^{-i/5}},
+\end{equation}
+where $y$ and $x$ correspond to NS observables $\bar{I}$, $\bar{Q}$, and $\Lambda$, and $\alpha$ is given by $2/5$, $1/5$, and $2$ for the $\bar{I}-\Lambda$, $\bar{Q}-\Lambda$, and $\bar{I}-\bar{Q}$ relations, respectively.
+The new fitting coefficients are presented in Table~\ref{tab:ILQfitNew}.
+While the two above fits both result in fits with similar $R^2$ values of $\sim 0.9999995$ for the data presented, the lattter one has the advantage that it properly limits to the Newtonian case as $\Lambda \rightarrow \infty$~\cite{Yagi:binLove}.
 
-\begin{table}[ht!]
+\begin{table*}
 \centering
 \caption{
-Updated fit parameters for I-Love-Q universal relations, as given by the curve found in Eq.~\ref{eq:ILQfit}.
+Updated fit parameters for the I-Love-Q universal relations, fitted to the constrained EoS data by the curve found in Eq.~\ref{eq:ILQfit}.
 }\label{tab:ILQfit}
@@
  \hline
- $\bar{I}$ & $\Lambda$ & $1.49$ & $0.0632$ & $0.0212$ & $-5.47 \times 10^{-4}$ & $2.18 \times 10^{-6}$ \\
- $\bar{I}$ & $\bar{Q}$ & $0.212$ & $0.0726$ & $0.0542$ & $-5.07 \times 10^{-3}$ & $1.60 \times 10^{-4}$ \\
- $\bar{Q}$ & $\Lambda$ & $1.38$ & $0.590$ & $-0.0183$ & $0.0405$ & $-2.77 \times 10^{-3}$ \\ 
+ $\bar{I}$ & $\Lambda$ & $1.4934168$ & $0.0640972$ & $0.0208513$ & $-5.018022 \times 10^{-4}$ & $3.1638958 \times 10^{-7}$ \\
+ $\bar{Q}$ & $\Lambda$ & $0.2092931$ & $0.0740442$ & $-0.0538210$ & $-5.018022 \times 10^{-3}$ & $1.576165 \times 10^{-4}$ \\ 
+  $\bar{I}$ & $\bar{Q}$ & $1.3832702$ & $0.0.5931020$ & $-0.0216132$ & $0.0419044$ & $-2.9676365 \times 10^{-3}$ \\
+ \hline
+ \hline
+\end{tabular}
+\end{table*}
+
+\begin{table*}
+\centering
+\caption{
+I-Love-Q universal relations fit parameters for the constrained EoS data using the improved fitting relations found in Eq.~\ref{eq:ILQfitNew}.
+This fitting relation, unlike previous versions, properly limits to the Newtonian case as $\Lambda \rightarrow \infty$.
+}\label{tab:ILQfitNew}
+\begin{tabular}{ c  c  | c c c c c c c c} 
+ \hline
+ \hline
+ $y$ & $x$ & $\alpha$ & $C_{yx}$ & $a_1$ & $a_2$ & $a_3$ & $b_1$ & $b_2$ & $b_3$ \\
+ \hline
+ $\bar{I}$ & $\Lambda$ & $2/5$ & $0.5313031$ & $1.2868285$ & $0.0988787$ & $-2.3001034$ & $-1.3465945$ & $0.3857349$ & $-0.0287014$\\
+ $\bar{Q}$ & $\Lambda$ & $1/5$ & $3.5554627$ & $-2.1218079$ & $2.7237378$ & $-1.4906808$ & $0.8643535$ & $-0.1427541$ & $-1.3973147$\\
+ $\bar{I}$ & $\bar{Q}$ & $2$ & $0.0089212$ & $10.5910815$ & $-37.4581345$ & $43.1831156$ & $-2.3610288$ & $1.9674667$ & $-0.5678018$\\
+\hline
+\hline
+\end{tabular}
+\end{table*}
+
+Fig.~\ref{fig:ILQ} shows the improved I-Love universal relations between the dimensionless moment of inertia $\bar{I} \equiv I/M^3$, the dimensionless quadrupole moment $\bar{Q} \equiv Q/M^3$, and the dimensionless tidal deformability $\Lambda$ for both the constrained and unconstrained sets of EoSs (each with individual fits pertaining to only that set of EoSs).
+We observe that the constrained EoSs show considerable improvement from both the results of previous works~\cite{Yagi:ILQ}, and from the unconstrained EoSs.
+This is further validated in Tab.~\ref{tab:maxVar}, where the maximal EoS variation from each fit is tabulated; comparing the results of previous works to the unconstrained, and constrained sets of EoSs.
+Observe how the constrained EoSs outperform both other cases by a considerable amount for each I-Love-Q universal relation.
+
+\begin{figure*}
+\begin{center} 
+\includegraphics[width=.32\textwidth]{IL.eps}
+\includegraphics[width=.32\textwidth]{QL.eps}
+\includegraphics[width=.32\textwidth]{IQ.eps}
+\end{center}
+\caption{
+Individual I-Love universal relations $\bar{I}-\Lambda$ (left), $\bar{Q}-\Lambda$ (center), and $\bar{I}-\bar{Q}$ (right), shown for both the constrained EoSs (solid green) and unconstrained EoSs (dotted maroon).
+In these figures, the black dashed lines corresponds to the fits given by Eq.~\ref{eq:ILQfitNew} (note: each panel contains individual fits for the constrained and unconstrained EoSs, indistinguishable on such a large scale).
+Observe how the fractional difference from the fits, shown in the bottom panels, is greatly suppressed for the constrained case, compared to both the unconstrained case, and results from previous works~\cite{Yagi:ILQ}.
+The maximal EoS variation from the fits for the unconstrained and constrained sets of EoSs are compared in Tab.~\ref{tab:maxVar}.
+Additionally shown in this figure is the fractional difference from the nuclear matter fits for the 10 hybrid star EoSs (dashed green).
+}
+\label{fig:ILQ}
+\end{figure*}
+
+\begin{table}
+\centering
+\caption{
+Comparison between the universal relations (both I-Love-Q and binary Love) maximal EoS variability for the results of previous works~\cite{Yagi:ILQ,Yagi:binLove}, and the unconstrained and constrained sets of EoSs analyzed here.
+The maximum EoS variation, given by the largest fractional difference from the fits as shown in Figs.~\ref{fig:ILQ} and~\ref{fig:binLove}, sees a considerable improvement for the constrained set of EoSs, compared to the unconstrained set as well as previous works.
+Additionally, notice how the maximal EoS variation for the unconstrained set of EoSs is slightly higher than that found in Refs.~\cite{Yagi:ILQ,Yagi:binLove} - due to the effects of large random sampling taking into account more sources of uncertainty.\zc{Kent do you know the IQ max EoS variation?
+It's not quoted or shown in the paper}
+}\label{tab:maxVar}
+\begin{tabular}{ c  || c c c } 
+ \hline
+ \hline
+ \textbf{Universal} & \multicolumn{3}{c}{\textbf{Maximal EoS Variability}} \\
+ \cline{2-4}
+ \textbf{Relation} & \multicolumn{1}{c|}{\emph{Previous}} & \multicolumn{1}{c|}{\emph{Unconstrained}} & \emph{Constrained}\\
+ \hline
+ $\bar{I}-\Lambda$ & $\sim 0.005$ & $0.0076725$ & $0.0031383$\\
+ $\bar{Q}-\Lambda$ & $\sim 0.009$ & $0.012617$ & $0.0046612$\\
+ $\bar{I}-\bar{Q}$ & ? & $0.014895$ & $0.0057157$\\
+ \hline
+ $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.50$} & \multirow{2}{*}{$0.5723891$} & \multirow{2}{*}{$0.2140192$}\\
+ $(q=0.90)$ & & &\\
+ \cline{1-1}
+ $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.20$} & \multirow{2}{*}{$0.2447418$} & \multirow{2}{*}{$0.0828446$}\\
+  $(q=0.7)$ & & &\\
+  \cline{1-1}
+ $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.025$} & \multirow{2}{*}{$0.0384088$} & \multirow{2}{*}{$0.0182308$}\\
+  $(q=0.50)$ & & &\\
+  \cline{1-1}
 \hline
@@
 
-{\ny{Let me play devil's advocate and explain things I could potentially be worried about.
-\begin{itemize}
-\item The constrained and the unconstrained data set of I-Love that you are fitting, do they have the same number of data points?
-If not, how do you know your fits and the comparisons are reliable to variation on the data set?
-You can study this by re-doing this analysis with the same amount of data in both sets of EoSs and then repeating the analysis with twice the amount of data to see how the results change.
-\item  The unconstrained set does not contain the same EoSs as the constrained set plus additional ones that are ruled out.
-This makes comparison of the sets a bit more difficult, because they are randomly sampled.
-How do you know your comparisons are robust to the number of EoSs you have randomly chosen without your probability distribution?
-You can study this by re-doing this analysis with twice the number of drawn EoSs to see how the results change.
-\item In the constrained set, there seems to be 3 EoSs that have the ``largest'' difference.
-What makes these EoSs special?
-Do they have anything in common?
-Same question for the unconstrained data set, but there are 2 special ones this time.
-\end{itemize}
-}}
-Fig.~\ref{fig:ILQ} shows the improved I-Love universal relation between dimensionless moment of inertia $\bar{I} \equiv I/M^3$ and dimensionless tidal deformability $\Lambda$ for both constrained and unconstrained sets of EoSs.
-We observe that the maximum recorded EoS variation under the constrained set of EoSs is $0.43\%$, showing considerable improvement from the $0.88\%$ found in the case of unconstrained EoSs.
-Further, both EoS samples show improvement from the original result of $\approx 1\%$ displayed in~\cite{Yagi:ILQ}.
+These results indicate that universal relations can indeed be greatly improved upon by constraining to only EoSs which agree with physical observations.
+In addition, we confirm the validity of this method by noting that the unconstrained EoSs observe more EoS variability than that found in Ref~\cite{Yagi:ILQ} due to the nature of large random sampling taking into account more sources of uncertainty than previously studied.
+On the other hand, the constrained set of EoSs show significant improvement from that found in previous works.
 
-{\ny{This comment is related to the list above, but I'm worried about how robust these numbers quoted above to *2* sig figs are...}}
+\subsubsection{Hybrid quark-hadron stars}\label{sec:ilq-hyb}
+In this section, we investigate the I-Love-Q universality of hybrid stars, and their compatibility with the nuclear matter counterparts.
+We consider three different sets of data to be fit to Eq.~\ref{eq:ILQfitNew}:
+\begin{enumerate}
+\item Complete set of 100 constrained EoSs combined with the 10 hybrid star EoSs,
+\item Complete set of 100 constrained EoSs alone,
+\item Complete set of 10 hybrid star EoSs alone.
+\end{enumerate}
+Following this, we compute the fractional difference from the fits for all three cases for the 10 hybrid star EoSs.
+The fractional differences for the second case fit (fit to only the constrained EoSs) is shown by the dashed green lines in Fig.~\ref{fig:ILQ} for example.
+To compare the three different fits, Tab.~\ref{tab:hybridCompare} displays the maximal EoS variation in the $I-\Lambda$ relation for both the constrained and hybrid star EoSs in each case.
 
-\begin{figure*}
-\begin{center} 
-\includegraphics[width=\textwidth]{ILQ.eps}
-\end{center}
+\begin{table}
+\centering
 \caption{
-I-Love universal relations shown for the constrained EoSs (left) and unconstrained EoSs (right).
-In these figures, the black dashed lines corresponds to the fit given by Eq.~\ref{eq:ILQfit}, while all other colors correspond to the 35 EoSs used in each case.
-The maximal EoS variation from the fit for unconstrained EoSs is $0.88\%$, which is comparable to the $1\%$ found in~\cite{Yagi:ILQ}.
-The constrained EoSs on the other hand, are universal to $0.43\%$, showing considerable improvement upon previous analyses.
-}
-\label{fig:ILQ}
-\end{figure*}
+Comparison between the $I-\Lambda$ maximal EoS variability for the constrained EoSs and the hybrid EoSs for three different cases of fitting data to Eq.~\ref{eq:ILQfitNew}: (1) fit to the combined data of constrained and hybrid EoS, (2) fit to the constrained EoS data alone, and (3) fit to the hybrid EoS data alone.
+Observe how for all 3 cases, the hybrid EoSs are only universal up to a minimum of $\sim1$\%, while in each case the constrained EoSs outperform the hybrid ones.
+The second case is demonstrated in Fig.~\ref{fig:ILQ}.
+}\label{tab:hybridCompare}
+\begin{tabular}{ c  || c c } 
+ \hline
+ \hline
+ \textbf{Fitting} & \multicolumn{2}{c}{\textbf{Maximal EoS Variability}} \\
+ \cline{2-3}
+ \textbf{Case} &  \multicolumn{1}{c|}{\emph{Constrained}} & \emph{Hybrid}\\
+ \hline
+ \emph{Combined} &  \multirow{2}{*}{$0.0044066$} & \multirow{2}{*}{$0.0136338$}\\
+ \emph{(Case 1)} & &\\
+ \cline{1-1}
+ \emph{Constrained only} & \multirow{2}{*}{$0.0031383$} & \multirow{2}{*}{$0.0173574$}\\
+  \emph{(Case 2)} & &\\
+  \cline{1-1}
+ \emph{Hybrid only} & \multirow{2}{*}{$0.0084002$} & \multirow{2}{*}{$0.0101741$}\\
+  \emph{(Case 3)} & &\\
+  \cline{1-1}
+\hline
+\hline
+\end{tabular}
+\end{table}
 
-These results indicate that universal relations can indeed be improved upon by constraining to only EoSs that agree with physical observations.
-Although the unconstrained EoSs show slightly smaller EoS variation than found in previous works, they are comparable in the sense that a wide range of EoSs were strategically picked in~\cite{Yagi:ILQ}, while the unconstrained set consists of a random sample which may or may not encompass everything considered previously.
-On the other hand, the constrained set of EoSs show significant improvement from that found in previous 
-works.
-
-{\ny{I think it would be worth studying whether there is a better fitting function that one can use for the constrained set.
-The functional form in Eq.
-(6) does not limit properly to the Newtonian result or to the relativistic result.
-But we do know how I-Love for example scales in the Newtonian limit, so could we e.g.
-peel off the asymptotic behavior analytically, and then correct this with a fitting function?
-This is similar to what Kent and I did in the past in a paper (in the binary love actually) and also similar to the way EoB works.}}
+Observe how the hybrid star EoSs do obey the I-Love-Q universal relations up to $\sim1.7$\%, slightly higher than that found here for nuclear matter EoSs, as well as that found in previous works~\cite{Yagi:ILQ}.
+Further, we observe that the universality can not be improved by much through the introduction of new fits, only bringing the max EoS variation down to $\sim1$\% for the fits constructed with only hybrid star EoSs.
+Concluding, we claim that hybrid star EoSs \emph{do} obey the I-Love-Q universal relations computed through nuclear EoS data, with the exception that the universality goes up to $\sim1.7$\%.
 
@@
 Next we consider improvements to the binary Love universal relations.
-In particular, we consider two distinct classes of NSs: nuclear matter EoSs and hybrid quark-hadron star EoSs~\cite{Paschalidis2018,Alford:2017qgh,1971SvA....15..347S,Zdunik:2012dj,Alford:2013aca}.
-In the latter, the low-density nucleonic crust region of the EoS experiences a first-order phase transition into a high density quark matter core at a given transition pressure $P_{\text{tr}}$.
-In this document, we adopt the ACB models, in particular ACB5 as seen in Table II of Ref.~\cite{Paschalidis2018}.
-We begin in Sec.~\ref{sec:nuclear} by fitting new binary Love relations for nucleonic matter as was done in~\cite{Yagi:binLove}.
-This is followed in Sec.~\ref{sec:hybrid} by an analysis and discussion into how well hybrid stars agree with the improved binary Love relations
+Similar to Sec.~\ref{sec:ilq}, we consider two classes of NSs: nuclear matter EoSs and hybrid quark-hadron star EoSs~\cite{Paschalidis2018,Alford:2017qgh,1971SvA....15..347S,Zdunik:2012dj,Alford:2013aca}.
+We begin in Sec.~\ref{sec:binLove-nuclear} by fitting new binary Love relations for nucleonic matter as was done in~\cite{Yagi:binLove}.
+This is followed in Sec.~\ref{sec:binLove-hybrid} by an analysis and discussion into different fits incorporating hybrid star EoSs.
 
-{\ny{Why do we consider hybrid stars only in this subsection? Why not also include these in the I-Love studies?}}
-
-\subsubsection{Nuclear matter stars}\label{sec:nuclear}
+\subsubsection{Nuclear matter stars}\label{sec:binLove-nuclear}
 Following Ref.~\cite{Yagi:binLove}, we fit the binary Love relations from the constrained EoSs to the two-dimensional curve:
 \begin{equation}\label{eq:binLovefit}
-\Lambda_a=F_n(q) \frac{a+ \sum_{i=1}^3 \sum_{j=1}^2 b_{ij}q^j x^{i/5}}{a+ \sum_{i=1}^3 \sum_{j=1}^2 c_{ij}q^j x^{i/5}} \Lambda_s^{\alpha},
+\Lambda_a=F_n(q) \frac{1+ \sum_{i=1}^3 \sum_{j=1}^2 b_{ij}q^j x^{i/5}}{1 + \sum_{i=1}^3 \sum_{j=1}^2 c_{ij}q^j x^{i/5}} \Lambda_s^{\alpha},
 \end{equation}
@@
 Notice how, unlike the individual NS I-Love-Q universal relations, these relations also depend on the ratio of constituent masses in the binary system.
-\begin{table*}[ht!]
+\begin{table*}
 \centering
@@
 Updated fit parameters for the binary Love universal relations, as given by the curve found in Eq.~\ref{eq:binLovefit}.
+The bottom row corresponds to separate fits corresponding to the hybrid star branch of the hybrid EoSs.
 }\label{tab:binLovefit}
 \addtolength{\tabcolsep}{1pt} 
-\begin{tabular}{ c  c  c  c  c  c  c  c  c  c  c  c  c  c  c} 
+\begin{tabular}{c | c  c  c  c  c  c  c  c } 
  \hline
  \hline
- $n$ & $\alpha$ & $a$ & $b_{11}$ & $b_{12}$ & $b_{21}$ & $b_{22}$ & $b_{31}$ & $b_{32}$ & $c_{11}$ & $c_{12}$ & $c_{21}$ & $c_{22}$ & $c_{31}$ & $c_{32}$\\
+ Fit & $n$ & $\alpha$ & $b_{11}$ & $b_{12}$ & $b_{21}$ & $b_{22}$ & $b_{31}$ & $b_{32}$\\
  \hline
- $0.743$ & $-1$ & $0.08684$ & $-2.594$ & $-0.6145$ & $9.659$ & $3.024$ & $-7.816$ & $17.5488$ & $-2.172$ & $-1.744$ & $3.609$ & $18.14$ & $11.45$ & $-29.90$\\
+ NS & $0.743$ & $-1$ & $-14.3953859$ & $14.4524099$ & $31.3639705$ & $-32.2487464$ & $-22.4377209$ & $20.3458458$\\
+ HS & $0.743$ & $-1$ & $343.0432419$ & $-382.6204995$ & $519.4578954$ & $-594.3272852$ & $811.6275273$ & $-867.6333691$\\
+\hline
+ \hline
+ \noalign{\smallskip}
+
+ & & & $c_{11}$ & $c_{12}$ & $c_{21}$ & $c_{22}$ & $c_{31}$ & $c_{32}$\\
+ \hline
+ NS & & & $-15.2461132$ & $15.3712170$ & $37.3335552$ & $-43.1985996$ & $-29.9331083$ & $35.1806737$\\
+ HS & & & $82.5971248$ & $-97.7858530$ & $242.2411803$ & $-262.9050666$ & $244.8665753$ & $-268.8024651$\\
  \hline
@@
 Fig.~\ref{fig:binLove} shows the improved binary Love universal relation for 3 different mass ratios: $q=0.9$, $q=0.75$, and $q=0.5$ for both constrained and unconstrained sets of EoSs.
-We observe that the maximum recorded EoS variation under the constrained set of EoSs is $23.65\%$, $9.76\%$, and $2.15\%$ for mass ratios of $q=0.9$, $q=0.75$, and $q=0.50$, respectively.
-This shows considerable improvement from the universalities of $\sim 50\%$, $\sim 20\%$, and $\sim 3\%$ found in Ref.~\cite{Yagi:binLove}.
-In addition, the unconstrained set of EoSs show similar universality to that recorded in Ref.~\cite{Yagi:binLove}.
-\begin{figure*}
+Observe how once again, the constrained set of EoSs show a considerable improvement upon both the unconstrained set of EoSs, as well as the results found in previous works~\cite{Yagi:binLove}.
+Additionally, the unconstrained set of EoSs show similar, yet slightly larger EoS variation due to the random sampling.
+Once again, the maximum EoS variability is tabulated in Tab.~\ref{tab:maxVar} for each value of mass ratio.
+
+\begin{figure}
 \begin{center} 
-\includegraphics[width=\textwidth]{binLove.eps}
+\includegraphics[width=\linewidth]{binLove.eps}
 \end{center}
 \caption{
-Binary Love universal relations shown for the constrained EoSs (left) and unconstrained EoSs (right).
-In this figure, the dashed black line corresponds to the fit given by Eq.~\ref{eq:binLovefit}, while the dotted blue, dashed magenta, and solid green lines represent the 35 EoSs for mass ratios of $q=0.9$, $q=0.75$, and $q=0.50$, respectively.
-The maximal EoS variation for each value of $q$ is $23.65\%$, $9.76\%$, and $2.15\%$ respectively, compared to $\sim 50\%$, $\sim 20\%$, and $\sim 3\%$ found in Ref.~\cite{Yagi:binLove}.
-These values are comparable to the maximal EoS variation for unconstrained EoSs as expected, found to be $41.66\%$, $12.64\%$, and $3.83\%$.
-Additionally shown is the binary Love relations for hybrid stars (dash-dash-dotted curves) as discussed in Sec.~\label{sec:hybrid}.
+Binary Love universal relations shown for the constrained EoSs (dotted maroon) and unconstrained EoSs (solid green) for various values of mass ratio: $q=0.9$, $q=0.75$, and $q=0.50$.
+In this figure, the top panel displays the universal relations with fits given by Eq.~\ref{eq:binLovefit} shown by dashed black lines, while the bottom 3 panels correspond to the EoS variation for each mass ratio.
+Observe how the the constrained set of EoSs show a reduction in EoS variation for both the unconstrained set, and from the results shown in Ref.~\cite{Yagi:binLove}.
+The max EoS variability for each case is tabulated and compared in Tab.~\ref{tab:maxVar}.
+Additionally shown is the binary Love relations for the 10 hybrid star EoSs (dashed green curves) as discussed in Sec.~\ref{sec:binLove-hybrid}.
 Observe the large deviations from the fit as the mass ratio $q$ increases, returning near the fit before the transitional pressure at large values of $\Lambda_s$.
@@
 \label{fig:binLove}
-\end{figure*}
+\end{figure}
 
-{\ny{I have very similar comments here to those I listed in the I-Love relation section.}}
-
-\subsubsection{Hybrid quark-hadron stars}\label{sec:hybrid}
-\begin{figure}
-\begin{center} 
-\includegraphics[width=\linewidth]{hybridML.eps}
-\end{center}
-\caption{
-$M-\tilde{\Lambda}$ relations for the ACB5 model hybrid star. 
-Note the strong phase transition into a quark-matter branch at $\sim 1.4 \text{ M}_{\odot}$.
-As described in the text, HS/HS and NS/NS binaries have individual masses chosen such that both stars are contained within one branch -- resulting in high $q$ values.
-Constrastingly, HS/NS binaries have individual masses chosen from each branch resulting in small $q-values$.
-}
-\label{fig:hybridML}
-\end{figure} 
-Transitional quark-hadron matter stars undergo first-order phase transitions at pressure $P_{\text{tr}}$, where the hadronic branch departs into a quark-matter branch at a given mass transition.
-We focus on the ACB5 model shown in Fig.~\ref{fig:hybridML}, which observes a transition mass at $\sim 1.4 \text{ M}_{\odot}$~\cite{Paschalidis2018}.
-This results in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq 1.4 \text{ M}_{\odot}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote this as ``HS"), and (ii) small-mass ($M \leq 1.4 \text{ M}_{\odot}$) hadronic stars with no internal transition to quark matter (we denote this as ``NS").
+\subsubsection{Hybrid quark-hadron stars}\label{sec:binLove-hybrid}
+As described in Sec.~\ref{sec:theory}, transitional quark-hadron matter stars undergo first-order phase transitions at pressure $P_{\text{tr}}$, where the hadronic branch departs into a quark-matter branch at a given mass transition.
+These transitions result in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq M_{\text{tr}}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote this as ``HS"), and (ii) small-mass ($M \leq M_{\text{tr}}$) hadronic stars with no internal transition to quark matter (we denote this as ``NS").
 We consider 3 classes of binaries:
@@
 
-{\ny{The comparison below is a bit misleading because all you have shown is that the fitting coefficients for the standard stars do not work when dealing with mixed stars.
-I think it would be interesting to see how the binary love relations look when you include hybrid systems (something like Fig.
-5 but for QS/QS and for QS/HS).
-Also I think it would be interesting to either (i) redo the fits including the QS/QS and QS/HS data and or (ii) produce different fits for those families, and then you can compare either of these to a wide set of systems to determine the validity of the fit.}}
-
-To determine how each of class of binary NSs obey our improved binary Love universal relations, we pick a representative set of 10 binary pairs from each class.
-Binary Love values are then computed for each pair, then residuals from the binary Love curve found in Sec.~\ref{sec:nuclear} are determined and compared to that from the constrained set of EoSs.
+To determine how each of class of binary NSs obey our improved binary Love universal relations, we pick a representative set of 10 binary pairs from each class, for the ACB5 hybrid EoS, with a transition at $1.4 \text{ M}_{\odot}$.
+Binary Love values are then computed for each pair, then residuals from the binary Love curve found in Sec.~\ref{sec:binLove-nuclear} are determined and compared to that from the constrained set of EoSs.
 The results are shown in Fig.~\ref{fig:hybrid}.
 First, we observe that the NS/NS combination of stars gives consistent results to that found earlier -- as expected.
-Next, we see that HS/HS combinations agree moderately with previous relations\footnote{Note that these EoSs do not fit within GW170817's 90\% posterior on EoS - so we excpect deviations consistent with the ``unconstrained" set of EoSs, rather than the ``constraind" set.}, while HS/NS combinations disagree significantly.
+Next, we see that HS/HS combinations agree moderately with previous relations\footnote{Note that these EoSs do not fit within GW170817s 90\% posterior on EoS - so we expect deviations consistent with the ``unconstrained" set of EoSs, rather than the ``constrained" set.}, while HS/NS combinations disagree significantly.
 This can be explained by the large reduction in tidal deformability for hybrid stars, are shown in Fig.
 2 of Ref.~\cite{Paschalidis2018}: when one star lies on the hadronic branch while the other is on the quark branch, they each see vast differences in $\tilde{\Lambda}$ - disrupting the binary Love relations as found for stars on the hadronic branch.
-In addition, the discrepancy can be seen in Fig.~\ref{fig:binLove} where the binary Love relations for the ACB5 EoS is shown in relation to the constrained nuclear matter EoSs.
-Observe how the residuals from the fit are quite good for low pressures (large $\Lambda_s$) when the the binaries consist of a NS/NS combination, before reaching the transitional pressure when the deviations become increasingly large for HS/HS and HS/NS binaries.
-We conclude that quark-hadron stars may or may not obey these ``hadronic" universal relations, depending on the location of transition, and the difference between constituent masses in the binary.
+
 \begin{figure}
@@
 \caption{
-Fractional difference from the improved binary Love relations fit for a representative set of constrained nuclear matter EoSs (gray cirlces), and 30 selected NS binaries from the ACB5 hybrid EoS.
+Fractional difference from the improved binary Love relations fit for a representative set of constrained nuclear matter EoSs (gray circles), and 30 selected NS binaries from the ACB5 hybrid EoS.
 In particular, these binary pairs are selected from each of the following categories: (i) binaries with which one massive star has a quark matter core, while the other is pure hadronic matter (i.e.
@@
 
+This discrepancy between hybrid and hadronic matter EoSs can be seen in Fig.~\ref{fig:binLove}, where the binary Love relations for the 10 hybrid star EoSs are shown in relation to the constrained and unconstrained nuclear matter EoSs.
+Observe how the residuals from the fit are quite good for low pressures (large $\Lambda_s$) when the the binaries consist of a NS/NS combination, before reaching the transitional pressure when the deviations become increasingly large ($\sim160$\% for $q=0.90$, $\sim37$\% for $q=0.75$, and $\sim6$\% for $q=0.50$) for HS/HS and HS/NS binaries.
+
+To further investigate this phenomena, we consider binary Love fits to the HS branches, or NS branches \emph{individually}.
+It was found that by trying to fit binary Love relations to the full hybrid star EoSs failed, due to the difference in transitional masses $M_{\text{tr}}$.
+To compensate for these differences, we separate the two branches into the NS (hadronic matter) and HS (hybrid matter) branches.
+We first observe that the NS branch obeys the ``hadronic" binary Love relations derived earlier in Sec.~\ref{sec:binLove-nuclear} within the variability found earlier, indicating no further need for additional fits.
+However, the HS branch does not, suggesting the need for a new ``hybrid" binary love fit pertaining to this branch.
+We begin by fitting the binary Love relations to the new HS branch, resulting in the fit coefficients found in the bottom row of Tab.~\ref{tab:binLovefit}.
+We urge caution with the use of these fits, as the small sample size (10 EoSs) as well as the occurrence of hybrid matter transitions only being available for certain mass ratios on certain EoSs, results in a less accurate fit than the nuclear-matter counterpart.
+Similar to before, the fractional difference from the fit for each HS branch is computed, resulting in a maximum variability of $18.488$\% for $q=0.90$.
+This result is strongly consistent with the results found for the nuclear matter fits of Sec.~\ref{sec:binLove-nuclear}.
+
+We conclude this section with the observation that the hybrid star EoSs do \emph{not} conform to the fits performed on nuclear matter EoSs.
+This is not surprising, as the hybrid branch of the EoSs give inconsistent results between $\Lambda_1$ and $\Lambda_2$ with different masses; an issue not present for the single-star I-Love-Q relations.
+By separating the two branches of the hybrid EoSs, we find a new ``hybrid" branch binary Love fit which gives consistent results to that found for the nuclear matter fits.
+
+\subsubsection{Error Marginalization}
 We have now shown that binary NS merger observations can help improve universal relations - the question is: is it worth it?
 Current interferometer sensitivities are not yet small enough to accurately constrain $\tilde{\Lambda}$.
-For example, GW170817 was detected by LIGO observing run 2 (``O2")\zc{cite} and was able to constrain $\tilde{\Lambda}$ to a $90\%$ confidence interval of 325 (this relates to a standard deviation of $\sigma_{\tilde{\Lambda}}$=198) centered at $\tilde{\Lambda}=395$.
-This corresponds to statistical uncertainties on the order of $\sim 82\%$, which vastly dominates the error budget compared to the small systematic errors picked up by EoS variation in the universal relations, which can be seen in Fig.~\ref{fig:variances}.
-This implies that currently, improved universal relations will not make any difference in tidal parameter extraction.
+For example, GW170817 was detected by LIGO observing run 2 (``O2")\zc{cite} and was able to constrain $\tilde{\Lambda}$ to a $90\%$ confidence interval of 325 (this relates to a standard deviation of $\sigma_{\tilde{\Lambda}}=198$) centered at $\tilde{\Lambda}=395$.
+This corresponds to statistical uncertainties on the order of $\sim 82\%$, which vastly dominates the error budget compared to the small systematic errors picked up by EoS variation in the universal relations, which can be seen in Fig.~\ref{fig:residuals}.
+This implies that currently, improved universal relations will only make a negligible difference in tidal parameter extraction.
+
+In this section, we investigate the residuals in $\tilde{\Lambda}(\Lambda_a,\Lambda_s,q)$ in order to marginalize over the intrinsic error in the binary Love universal relations.
+In particular, we restrict our focus to only the constrained set of EoSs.
+Residuals in $\tilde\Lambda$ are computed as $\tilde{\Lambda}^{\text{fit}}-\tilde{\Lambda}^{\text{true}}$, where $\tilde{\Lambda}^{\text{true}}=\tilde{\Lambda}(\Lambda_a,\Lambda_s,q)$ corresponds to the true value predicted by the sample EoSs, and $\tilde{\Lambda}^{\text{fit}}=\tilde{\Lambda}(\Lambda_a^{\text{fit}}(\Lambda_s,q),\Lambda_s,q)$ corresponds to the value obtained through the universal relations found in Sec.~\ref{sec:binLove-nuclear}.
+Following Ref.~\cite{Katerina:residuals}, we assume the residuals in $\tilde{\Lambda}$ observe a Gaussian distribution with mean and standard deviation given by:
+\begin{align}
+\mu_{\tilde{\Lambda}}(\Lambda_s,q) &=\frac{\mu_{\Lambda_s}(\Lambda_s)+\mu_{q}(q)}{2},\\ 
+\sigma_{\tilde{\Lambda}} &=\sqrt{\sigma_{\Lambda_s}^2(\Lambda_s) + \sigma_{q}^2(q)}. 
+\end{align}
+Similar to Ref.~\cite{Katerina:residuals}, we fit the individual components to be:
+\begin{align}
+\mu_{\Lambda_s}(x) &= \mu_1 x + \mu_2, \label{eq:margFit1}\\ 
+\mu_{q}(x) &= \mu_3 x^2 + \mu_4 x + \mu_5, \label{eq:margFit2}\\ 
+\sigma_{\Lambda_s}(x) &= \sigma_1 x^{7/2} + \sigma_2 x^{5/2} + \sigma_3 x^{3/2} +  \sigma_4 x^{1/2} + \sigma_5, \label{eq:margFit3}\\ 
+\sigma_{q}(x) &= \sigma_6 x^3 + \sigma_7 x^2 + \sigma_8 x + \sigma_9. \label{eq:margFit4}
+\end{align}
+The fitting parameters $\mu_i$ and $\sigma_i$ are tabulated in Table~\ref{tab:marginalized}.
+
+\begin{table}
+\centering
+\caption{
+Coefficients to the fits given by Eqs.(~\ref{eq:margFit1})-(\ref{eq:margFit4}) for the relative error on $\tilde{\Lambda}$ in the improved binary Love universal relations presented in this paper.
+}\label{tab:marginalized}
+\addtolength{\tabcolsep}{1pt} 
+\begin{tabular}{ c | c || c | c}
+\hline 
+\noalign{\smallskip}
+$\mu_1$ & $-8.7169662 \times 10^{-5}$ & $\sigma_1$ & $3.3497867 \times 10^{-11}$\\
+$\mu_2$ & $0.0185324$ & $\sigma_2$ & $-2.3026166 \times 10^{-7}$\\
+$\mu_3$ & $-3.2611497$ & $\sigma_3$ & $3.8180750 \times 10^{-4}$\\
+$\mu_4$ & $5.0680859$ & $\sigma_4$ & $0.0444373$\\
+$\mu_5$ & $-1.9040182$ & $\sigma_5$ & $-0.0126140$\\
+ &  & $\sigma_6$ & $181.8712429$\\
+ &  & $\sigma_7$ & $-419.0842028$\\
+ &  & $\sigma_8$ & $299.5608266$\\
+  &  & $\sigma_9$ & $-62.1555049$\\
+ \noalign{\smallskip}
+ \hline
+\end{tabular}
+\addtolength{\tabcolsep}{-1pt}
+\end{table}
+
+Figure~\ref{fig:residuals} displays the Gaussian distribution of $\tilde\Lambda$ residuals for both the constrained, and unconstrained sets of EoSs for comparison.
+Observe how the standard deviations $\sigma=7.666$ and $\sigma=40.887$ show a large decrease between the unconstrained and constrained sets of EoSs.
+In addition, we find the 90th, 99th, and 100th percentiles on $\tilde\Lambda$ to be $P_{90}=12.014$, $P_{99}=29.710$, and $P_{100}=62.240$ for the constrained EoSs.
+Because the un-binned residuals seen in Fig.~\ref{fig:residuals} are dominated by the low-error regions of parameter space ($\Lambda_s \rightarrow 0$ and $q \rightarrow 1$) shown by the fits of Tab.~\ref{tab:marginalized}, we consider the 90th for the remainder of the analysis.
+We take this value of $P_{90}=12.014$ to be the systematic measurement error introduced by using the improved binary Love universal relations on the parameter extraction of $\tilde\Lambda$.
+Currently, the statistical error of $198$ on $\tilde\Lambda$ from GW170817 dominate the error budget compared to the systematic error of $12.014$.
+This means that, for the current ``O2" detector sensitivity, the use of improved binary Love universal relations will only make a negligible difference on the extraction of $\tilde\Lambda$.
 However, future detectors (for example aLIGO, a\texttt{++}, Voyager, CE, and ET) are planned with large reductions in sensitivity - both decreasing the statistical errors and allowing for a larger binary NS merger detection rate; further reducing uncertainties.
-In Sec.~\ref{sec:observations}, we analyze this further and discuss when improved universal relations will make a difference.
+In Sec.~\ref{sec:observations}, we analyze this further and discuss when the systematic errors from universal relations become comparable to the statistical errors.
+
 \begin{figure}
 \begin{center} 
-\includegraphics[width=\columnwidth]{variances.png}
+\includegraphics[width=\columnwidth]{residuals.pdf}
 \end{center}
 \caption{
-\zc{Ask Katerina for this data.
-Convert $\Lambda_s$ to $\tilde{\Lambda}$, then redo this image in xmgrace.
-Remove posterior eoss, Add a gridline at the maximum errors for both constrained and unconstrained, and maybe even show the relative errors as well?
-Probably remove the means as well.}
-Absolute difference from the fit on $\tilde{\Lambda}$ from EoS variation in the binary Love universal relations plotted with varying mass ratio $q$.
-Observe that the maximum systematic error attained for the constrained EoSs is $\sigma_{\tilde{\Lambda}}=10$ (this is found to be $20$ for the unconstrained EoSs).
-This is negligible compared to the statistical errors accrued on paramter extraction from GW170817.
+Residuals on $\tilde\Lambda$ computed as $\tilde{\Lambda}^{\text{fit}}-\tilde{\Lambda}^{\text{true}}$ for the binary Love relations modeled in Sec.~\ref{sec:binLove-nuclear} for both constrained and unconstrained sets of EoSs.
+These residuals obey Gaussian distributions centered at $\mu=-1.8133 \times 10^{-4}$ and $\mu=4.2258 \times 10^{-3}$ with standard deviations of $\sigma=7.6664$ and $\sigma=40.8866$ for the constrained and unconstrained sets of EoSs, respectively.
+These uncertainties correspond roughly to the systematic errors introduced on the parameter extraction of $\tilde{\Lambda}$ upon the use of binary Love universal relations.
+However, to take into account the systematic errors found in high-error regions of the parameter space, we instead set the systematic error to be the 90th percentile, $P_{90}=12.014$.
+Observe that the systematic errors from using the improved (constrained) binary Love universal relations are negligible compared to the statistical errors accrued on parameter extraction from GW170817, found to be $\sigma_{\tilde{\Lambda}}=198$.
 }
-\label{fig:variances}
+\label{fig:residuals}
 \end{figure}
@@
 \section{Impact on future observations}\label{sec:observations}
-In this section, we estimate the feasibility of ultilizing improved universal relations in future binary NS merger events.
-This estimate is aqcuired through a simple Fisher analysis~\cite{Finn:Fisher,Cutler:Fisher} which approximates the accuracy with which one can extract best-fit parameters $\theta^a$, given a prior template waveform.
+In this section, we estimate the feasibility of utilizing improved universal relations in future binary NS merger events.
+This estimate is acquired through a simple Fisher analysis~\cite{Finn:Fisher,Cutler:Fisher} which approximates the accuracy with which one can extract best-fit parameters $\theta^a$, given a prior template waveform.
 For the remainder of the paper, we consider a template parameter vector consisting of:
-\begin{equation}
+\begin{equation}\label{eq:template}
 \theta^a=(\ln{A},\phi_c,t_c,\ln{\mathcal{M}},\ln{\mathcal{\eta}},\chi_s,\chi_a,\tilde{\Lambda},\delta \tilde{\Lambda}),
 \end{equation}
-where $A \equiv \sqrt{\frac{2 \eta}{3 \pi^{1/3}}}$ is a normalized amplitude factor, $\eta \equiv m_1 m_2/M^2$ is the symmetric mass ratio with $m_{1,2}$ and $M$ being the individual and total masses, $\mathcal{M}=M \eta^{3/5}$ is the chirp mass, and $\chi_{s,a}=\frac{1}{2}(\chi_1+\pm\chi_2)$ are the symmetric and antisymmetric total spins, where $\chi_{1,2}$ are the NSs individual spins.
+where $A \equiv \sqrt{\frac{2 \eta}{3 \pi^{1/3}}}$ is a normalized amplitude factor, $\eta \equiv m_1 m_2/M^2$ is the symmetric mass ratio with $m_{1,2}$ and $M$ being the individual and total masses, $\mathcal{M}=M \eta^{3/5}$ is the chirp mass, and $\chi_{s,a}=\frac{1}{2}(\chi_1\pm\chi_2)$ are the symmetric and antisymmetric total spins, where $\chi_{1,2}$ are the NSs individual spins.
 Following Refs.~\cite{Cutler:Fisher,Berti:Fisher,Poisson:Fisher}, this method relies on the crude assumption of Gaussian prior distributions\footnote{Typically, the more valid assumption is a uniform prior distribution; an improvement made in a more detailed Bayesian analysis.}.
-The resulting posterior distribution is Gaussian with root-mean-sqaure given by:
+The resulting posterior distribution is Gaussian with root-mean-square given by:
 \begin{equation}
@@
 
-\begin{table*}[ht!]
+\begin{table*}
 \centering
@@
 Below, $\rho^A_{\text{GW170817}}$ and $\sigma^A_{\text{GW170817}}$ correspond to the approximate SNR and $\sigma_{\tilde{\Lambda}}$ of GW170817 had it been observed by the future interferometer, and $\sigma^A_N$ corresponds to the final uncertainty on $\tilde{\Lambda}$ after $N_A$ detections on interferometer $A$.
-It can be seen here that the statistical errors on $\tilde{\Lambda}$ become comparable with the systematics $\sigma_{\tilde{\Lambda}}=10$ from using improved binary Love relations from Voyager and on, indicating when it may be safe to utilize new universal relations.
-Note the approximation for $\sigma^A_N$ under the O2 detector sensitivity is a poor estimate due to the small number of stacked events, $N_{\text{O2}}=1$, resulting in a high degree of randomness in population generation.
+It can be seen here that the statistical errors on $\tilde{\Lambda}$ become comparable with the systematics (set to be $P_{90}=12.014$) from using improved binary Love relations from Voyager and on, indicating when it may be safe to utilize new universal relations.
+Note the approximation for $\sigma^A_N$ under the O2 detector sensitivity is left blank due to the singularity of the detected event.
 These results are shown graphically in Fig.~\ref{fig:stackedFisher}.
@@
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
- O2  & \multicolumn{1}{|c|}{$32.40$}  & $168.40$ &  \multicolumn{1}{|c|}{$1$} & $1$ & $1$ & \multicolumn{1}{|c|}{$558.18$} & $393.24$ & $279.44$\\
+ O2  & \multicolumn{1}{|c|}{$32.40$}  & $168.40$ &  \multicolumn{1}{|c|}{--} & -- & -- & \multicolumn{1}{|c|}{--} & -- & --\\
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
@@
 
-Concluding, we find that the Voyager, ET, and CE detectors all exhibit enough uncertainty reduction that the systematics from using improved universal relations no longer become negligible in the error budget.
+Concluding, we find that the Voyager, ET, and CE detectors all exhibit enough uncertainty reduction that the systematics on $\tilde\Lambda$ introduced from using improved universal relations (found to be $12.014$) no longer become negligible in the error budget.
 This implies that the use and further improvement of universal relations is justified for future binary NS merger detections.
+Further, we investigate the dependence of the measurement accuracy of $\tilde\Lambda$ on the binary NS mass ratio $q$ for fixed chirp mass $\mathcal{M}=1.88\text{ M}_{\odot}$ in Appendix~\ref{app:measurement}.
 
@@
 Important previous work by Yagi and Yunes~\cite{Yagi:ILQ,Yagi:binLove} found EoS-insensitive universal relations between symmetric and antisymmetric combinations of NS tidal deformabilities, which aid in the extraction of said tidal parameters.
-We find an improvement upon these universal relations by a factor of 25\% for stars with mass below 1.7 solar masses\zc{check this number} by restricting to the EoSs constrained by GW170817.
-In addition, we find that binaries consisting of one massive hyrid quark-hadron star, and one small-mass hadron star do not obey these universal relations -- explained by the large difference in $\tilde{\Lambda}$ displayed between the constituent stars.
+We find an improvement upon these universal relations by a factor of $\sim 59$\% for stars with mass ratios of $0.75$ by restricting to the EoS posterior samples from GW170817s 90\% credible region on pressure as a function of density.
+Similarly, we find an increase in I-Love-Q universality by a factors of $\sim 50$\%.
+In addition, we find that binaries consisting of one massive hybrid quark-hadron star, and one small-mass hadron star do not obey these universal relations -- explained by the large difference in $\tilde{\Lambda}$ displayed between the constituent stars.
+To improve on this, we construct new ``hybrid matter binary Love relations", applied to only the hybrid branches of the transitional EoSs.
+This results in EoS variability similar to that found for the nuclear matter fits.
 Further, we analyze the impact of this improvement for future binary NS merger detections, as the current detector sensitivity is not yet small enough to accurately constrain $\tilde{\Lambda}$ enough for universal relations to make a difference.
-We find that future interferometers Voyager, CE, and ET-D all experience statistical uncertainties upon the extraction of $\tilde{\Lambda}$ small enough to become comparable to the systemtic errors injected by using the improved universal relations, as depicted in Fig.~\ref{fig:stackedFisher} and Table~\ref{tab:variances}.
+We find that future interferometers Voyager, CE, and ET-D all experience statistical uncertainties upon the extraction of $\tilde{\Lambda}$ small enough to become comparable to the systematic errors injected through the use of improved universal relations (found to be $12.014$), as depicted in Fig.~\ref{fig:stackedFisher} and Table~\ref{tab:variances}.
+Finally, in Appendix~\ref{app:measurement} we investigate the effect of NS binary mass ratio q on the measurement accuracy of $\tilde\Lambda$.
+We find that second generation interferometers lose accuracy as one increases the mass ratio, while third generation detectors observe a large increase of accuracy due to the correlations between $\tilde\Lambda$ and $\delta\tilde\Lambda$.
 This indicates that the use and further improvement of universal relations is justified for future GW observations of binary NS merger events.
 
-Future work on this subject includes the possible constraint on the EoS through the observation of super-massive NSs combined with the results of GW170817.
-For example, recent millisecond pulsar discovery J1748-2021B~\cite{Freire:superMassiveNS} has mass $2.74 \pm 0.21$, with large error bars due to astronomical mismodeling.
-If verified, this provides a possible avenue of EoS constraint via considering only spectrally generated EoSs which support maximum NS mass in agreeance with J1748-2021B.
-\zc{Should we talk about this here?}
-In addition, separate binary Love universal relations for hybrid star binaries should be investigated.
+\zc{Discuss with group on possible avenues of future work.}
 
@@
 \section*{Acknowledgments}\label{acknowledgments}
-K.Y. would like to acknowledge networking support by the COST Action
-GWverse CA16104. \zc{everyone elses acknowledgments. Which grant am I funded by?}
+K.Y. would like to acknowledge networking support by the COST Action GWverse CA16104.
+
+%%%%%%%%%%%%%%%%%%%%%%%%% Begin Appendix A: measurement accuracy as a functino of q %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\appendix
+\section{Measurement accuracy as a function of binary mass ratio}\label{app:measurement}
+In this appendix, we discuss the effects of the binary NS mass ratio on the measurement accuracy of $\tilde\Lambda$ for various interferometers. 
+The left panel of Fig.~\ref{fig:massVariation} displays an approximation of the $\tilde\Lambda$ measurement accuracy as a function of increasing mass ratio $q$ (for a fixed chirp mass of $\mathcal{M}=1.188 \text{ M}_{\odot}$ corresponding to GW170817), using the Fisher analysis techniques described in Sec.~\ref{sec:observations}.
+We observe two points of interest about these trends: (i) the second generation detectors (O2, aLIGO, a\texttt{++}, and Voyager) typically become less accurate as the mass ratio approaches unity, (ii) the third generation detectors (CE and ET) observe the opposite behavior-- a fast growth in accuracy as the mass ratio increases.
+For the remainder of this appendix, we attempt to explain the opposing behaviors of the second and third generation interferometers on the extraction of $\tilde\Lambda$.
+
+\begin{figure*}
+\begin{center} 
+\includegraphics[width=.3\textwidth]{massVariation1.eps}
+\includegraphics[width=.3\textwidth]{massVariation2.eps}
+\includegraphics[width=.3\textwidth]{massVariation3.eps}
+\end{center}
+\caption{
+Measurement accuracy of $\tilde\Lambda$ as a function of increasing mass ratio $q$ for interferometer sensitivities O2, aLIGO, a\texttt{++}, Voyager, CE, and ET.
+Evaluated at a fixed chirp mass of $\mathcal{M}=1.188\text{ M}_{\odot}$ corresponding to GW170817, this is repeated for three cases: (i) (left) with correlations between all template waveform parameters $\theta^a$ intact; (ii) (center) with the correlations between $\tilde\Lambda$ and $\delta\tilde\Lambda$ removed; and (iii) (right) with correlations between all parameters removed.
+The removal of parameter correlations is approximated by setting certain Fisher matrix elements to 0, as described in Appendix.~\ref{app:measurement}.
+Observe how the left panel shows strong disagreement between second and third generation detectors, while the right panel shows identical behavior.
+This indicates that parameter correlations between $\tilde\Lambda$ and higher PN order parameter $\delta\tilde\Lambda$ to be the culprit in such a disagreement.
+}
+\label{fig:massVariation}
+\end{figure*}
+
+We begin by considering the correlations between individual template parameters and $\tilde\Lambda$, given in Eq.~\ref{eq:template}.
+A simple approximation on the amplitude of these correlations can be performed by assuming all other correlations are non-existing.
+Correlations between parameters $\tilde\Lambda$ and $\theta^a$ alone is achieved by setting all off-diagonal Fisher matrix elements to $0$, except for the $(i,j)$ components such that both $i$ and $j$ correspond to the $\tilde\Lambda$ and $\theta^a$ parameters.
+We follow this process for each parameter in turn, and display the results in Fig.~\ref{fig:correlations} for each interferometer.
+This figure, showing only the relative differences between correlations of different parameters $\theta^a$ and $\tilde\Lambda$, reveals a few things.
+First, the coalescence time $t_c$ is highly correlated with $\tilde\Lambda$ equally for each interferometer, an unsurprising fact due to the high 4PN order at which the parameter enters the waveform.
+Secondly, correlations with 6PN tidal parameter $\delta\tilde\Lambda$ shows high correlations with $\tilde\Lambda$ for only the third generation detectors.
+This can be explained by the high PN order at which $\delta\tilde\Lambda$ enters the waveform, an effect that only the most sensitive of detectors can probe.
+
+\begin{figure}
+\begin{center} 
+\begin{overpic}[width=\columnwidth]{correlations.eps}
+\put(121,13){\fontsize{7pt}{7pt}\selectfont $\mathcal{M}$}
+\end{overpic}
+\end{center}
+\caption{
+Measurement accuracy of $\tilde\Lambda$ upon the consideration of correlations between \emph{only} $\tilde\Lambda$ and other individual template parameters $\theta^a$ shown in Eq.~\ref{eq:template}.
+This process, repeated for 6 interferometer design sensitivities O2, aLIGO, a\texttt{++}, Voyager, CE, and ET, is approximated by setting all off-diagonal Fisher matrix elements to 0 except for the $(i,j)$ components such that both $i$ and $j$ correspond to the $\tilde\Lambda$ and $\theta^a$ parameters.
+Observe how correlations with 4PN parameter $t_c$ (coalescence time) remain to be highly correlated with $\tilde\Lambda$ among all 6 interferometers.
+However, correlations between 6PN tidal parameter $\delta\tilde\Lambda$ and $\tilde\Lambda$ only begin to make a strong impact for third generation detectors.
+This is due to the small effect that $\delta\tilde\Lambda$ has on the waveform, only to be distinguished by the most sensitive detectors.
+}
+\label{fig:correlations}
+\end{figure}
+
+Following this conclusion on the difference of correlations between tidal parameters $\tilde\Lambda$ and $\delta\tilde\Lambda$ for second and third generation detectors, we attempt to describe the opposing behaviors of measurement accuracy between the two.
+Shown in the center panel of Fig.~\ref{fig:massVariation}, we approximate the measurement accuracy of $\tilde\Lambda$ with the correlations between $\delta\tilde\Lambda$ and $\tilde\Lambda$ removed, through a process similar to that described above.
+Notice how the trends between detector generations become more similar -- implying that the correlations between tidal parameters may be the cause.
+This is confirmed by the right panel of Fig.~\ref{fig:massVariation} where all parameter correlations have been removed from the Fisher matrix.
+We see that this results in identical behaviors between all 6 representative interferometers, leading us to conclude that the discrepancy between interferometers comes from the degeneracies between different parameters in the gravitational waveform, namely the 6PN tidal parameter $\delta\tilde\Lambda$ which is only detectable by the highly sensitive third generation detectors CE and ET.
 
 %%%%%%%%%%%%%%%%%%%%%%%%% Begin Bibliography  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\clearpage
+\clearpage
 \bibliography{Zack}

### 2018-12-18 paper/bin-love-after-gw170817.tex
small changes from Kents email

@@
 The maximum EoS variation, given by the largest fractional difference from the fits as shown in Figs.~\ref{fig:ILQ} and~\ref{fig:binLove}, sees a considerable improvement for the constrained set of EoSs, compared to the unconstrained set as well as previous works.
-Additionally, notice how the maximal EoS variation for the unconstrained set of EoSs is slightly higher than that found in Refs.~\cite{Yagi:ILQ,Yagi:binLove} - due to the effects of large random sampling taking into account more sources of uncertainty.\zc{Kent do you know the IQ max EoS variation?
-It's not quoted or shown in the paper}
+Additionally, notice how the maximal EoS variation for the unconstrained set of EoSs is slightly higher than that found in Refs.~\cite{Yagi:ILQ,Yagi:binLove} - due to the effects of large random sampling taking into account more sources of uncertainty.
 }\label{tab:maxVar}
@@
  \hline
- $\bar{I}-\Lambda$ & $\sim 0.005$ & $0.0076725$ & $0.0031383$\\
- $\bar{Q}-\Lambda$ & $\sim 0.009$ & $0.012617$ & $0.0046612$\\
- $\bar{I}-\bar{Q}$ & ? & $0.014895$ & $0.0057157$\\
+ $\bar{I}-\Lambda$ &  $0.0059$ & $0.0076725$ & $0.0031383$\\
+ $\bar{Q}-\Lambda$ & $0.0010$ & $0.012617$ & $0.0046612$\\
+ $\bar{I}-\bar{Q}$ & $0.012$ & $0.014895$ & $0.0057157$\\
  \hline
@@
 Binary Love universal relations shown for the constrained EoSs (dotted maroon) and unconstrained EoSs (solid green) for various values of mass ratio: $q=0.9$, $q=0.75$, and $q=0.50$.
-In this figure, the top panel displays the universal relations with fits given by Eq.~\ref{eq:binLovefit} shown by dashed black lines, while the bottom 3 panels correspond to the EoS variation for each mass ratio.
+In this figure, the top panel displays the universal relations with fits given by Eq.~\ref{eq:binLovefit} shown by dashed black lines (note there are 2 fits for each mass ratio, corresponding to the constrained and unconstrained sets of EoSs), while the bottom 3 panels correspond to the EoS variation for each mass ratio.
 Observe how the the constrained set of EoSs show a reduction in EoS variation for both the unconstrained set, and from the results shown in Ref.~\cite{Yagi:binLove}.
 The max EoS variability for each case is tabulated and compared in Tab.~\ref{tab:maxVar}.
-Additionally shown is the binary Love relations for the 10 hybrid star EoSs (dashed green curves) as discussed in Sec.~\ref{sec:binLove-hybrid}.
+Additionally shown is the binary Love relations for the 10 hybrid star EoSs (dashed bright green curves), as well as the HS fits (dot-dashed blue curves) discussed in Sec.~\ref{sec:binLove-hybrid}.
 Observe the large deviations from the fit as the mass ratio $q$ increases, returning near the fit before the transitional pressure at large values of $\Lambda_s$.
+This is shown in the bottom three panels as the fractional difference from the NS fit for comparison, while the HS fits show similar EoS variability to the constrained EoSs.
 }
@@
 We begin by fitting the binary Love relations to the new HS branch, resulting in the fit coefficients found in the bottom row of Tab.~\ref{tab:binLovefit}.
+The fits are displayed in the top panel of Fig.~\ref{fig:binLove} as dot-dashed blue curves, showing a good relationship with the hybrid star branch.
 We urge caution with the use of these fits, as the small sample size (10 EoSs) as well as the occurrence of hybrid matter transitions only being available for certain mass ratios on certain EoSs, results in a less accurate fit than the nuclear-matter counterpart.

### 2018-12-20 paper/bin-love-after-gw170817.tex
fixed figure 2

@@
 This is compared to the combined uncertainty $\sigma^A_N$ (red) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper (teal), central (orange), and lower (magenta) limits of expected binary NS merger detection rates for O2, aLIGO, a\texttt{++}, Voyager, CE, and ET-D over 1 observation year.
-It can be seen that the statistical errors in parameter extraction become comparable to the systematics from EoS variation in binary Love relations (purple) for Voyager and on.
+It can be seen that the statistical errors in parameter extraction become comparable to the systematics from EoS variation in binary Love relations (purple shaded region) for Voyager and on.
 Note there is no simulated populations of events under the O2 design sensitivity - due to there only being a single event during the observing period.
@@
 \caption{
-Small representative sets of the constrained (left) and unconstrained (right) EoSs used in this analysis. 
+Small representative sets of the unconstrained (dotted) and constrained (solid) EoSs used in this analysis. 
 The constrained EoSs were populated by randomly selecting 100 posterior samples obtained from the GW170817 90\% credible level shown in cyan~\cite{LIGO:posterior}.

### 2018-12-27 paper/bin-love-after-gw170817.tex
comments on abstract

@@
 
-\title{Universal relations after GW170817}
+\title{Universal relations after GW170817\kc{Here and elsewhere: I suggest we use the term "EoS-insensitive" instead of "universal" relations}}
 
@@
 \author{Katerina Chatziioannou}
-\affiliation{%
- Canadian Institute for Theoretical Astrophysics, 60 St. George Street, Toronto, Ontario, M5S 3H8, Canada
-}%
+%\affiliation{%
+% Canadian Institute for Theoretical Astrophysics, 60 St. George Street, Toronto, Ontario, M5S 3H8, Canada
+%}%
 \affiliation{%
@@
 % Intro
-The thermodynamic relationship between pressure and density (the equation of state) of supranuclear matter, accessible primarily in neutron stars, is critical to the study of such stars, and is one of the largest uncertainties in nuclear physics to date.
+The thermodynamic relationship between pressure and density (the equation of state) of \kc{cold} supranuclear matter, accessible primarily in neutron stars\kc{this statement makes nuclear experiment people not happy}, is critical to the study of such stars, and is one of the largest uncertainties in nuclear physics to date.
 % How to probe
@@
 % What was done before - I-Love-Q
-Similarly, another set of equation of state independent relations exist between individual neutron star parameters: moment of inertia (I), tidal deformability (Love number), and quadrupole moment (Q) - known as the ``I-Love-Q universal relations."
+Similarly, another set of equation of state \sout{independent}\kc{insensitive} relations exist between individual neutron star parameters: moment of inertia (I), tidal deformability (Love number), and quadrupole moment (Q) - known as the ``I-Love-Q universal relations."
 % What universal relations do
-Such universal relations allow the elimination of some tidal parameters from the list of model parameters, thus breaking degeneracies and ultimately reducing the uncertainty of the dominant tidal effect in parameter estimation.
+Such universal relations\kc{so far we have said "EoS-insensitive", "EoS-independent", and "universal".
+We should pick a name and stick with it.
+I suggest "EoS-insensitive"} allow the elimination of some tidal parameters from the list of model parameters, thus breaking degeneracies and ultimately reducing the uncertainty of the dominant tidal effect in parameter estimation\kc{You mean $\tilde{\Lambda}$?
+In our paper with Carl and Aaron we showed that the binary Love relation doesn't affect the $\tilde{\Lambda}$ measurement much.}.
 % What we will do
-In this document, we explain how one can reduce equation of state variation for both binary Love and I-Love-Q universal relations, which helps to reduce systematic errors on the tidal measurement of binary neutron star mergers.
+\kc{Add a sentence saying that even the more precise relations have some EoS variation which can cause a systematic error which can be marginalized over}
+In this document, we explain how one can reduce equation of state variation for both binary Love and I-Love-Q universal relations, which helps to reduce systematic errors on the tidal measurement of binary neutron star mergers\kc{but we show that the systematic effects of these relations is very small until next-G detectors.}.
 We achieve this  by restricting to only equations of state drawn from the 90\% posterior constraint on pressure as a function of density, as derived by the LIGO Collaboration.
@@
 % Conclude
-We end by comparing systematic errors on tidal measurement due to the equation of state variation with statistical errors and comment on whether one can safely use these universal relations with future gravitational wave observations.
+We end by comparing systematic errors on tidal measurement due to the equation of state variation with statistical errors and comment on whether one can safely use these universal relations with future gravitational wave observations.\kc{We should give the answer to this here: Yes!}
 \end{abstract}

### 2018-12-27 paper/bin-love-after-gw170817.tex
comments on intro

@@
 %Intro
-The dependence of pressure on density for supranuclear matter found primarily inside neutron stars (NSs) remains to be one of the largest mysteries in both nuclear physics and astrophysics.
+The dependence of pressure on density for \kc{cold} supranuclear matter found primarily inside neutron stars (NSs) remains to be one of the largest mysteries in both nuclear physics and astrophysics.
 This internal structure of such stars, known as the equation of state (EoS), is exceedingly important, as it is the determining factor for many NS observables - such as the mass, the radius, and many more.
-Unfortunately, terrestrial experiments can only study the EoS up to the nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy}, making NSs ideal laboratories for constraining ultra dense nuclear matter.
+Unfortunately, terrestrial experiments can only study the EoS up to the nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy}, making NSs ideal laboratories for constraining ultra dense nuclear matter\kc{heavy ion collisions supposedly go to higher densities, but they are T-dependent}.
 
@@
 Independent measurements of NS observables can be used to constrain the nuclear EoS.
-For example, electromagnetic observations of the mass-radius relationship of NSs have been used to place limits on NSs~\cite{guver,ozel-baym-guver,steiner-lattimer-brown,Lattimer2014,Ozel:2016oaf}.
-However, these implications suffer from large systematic errors due to astrophysical mismodeling.
+For example, electromagnetic observations of the mass-radius relationship of NSs have been used to place limits on NSs\kc{limits on what?}~\cite{guver,ozel-baym-guver,steiner-lattimer-brown,Lattimer2014,Ozel:2016oaf}.
+However, these implications \kc{potentially} suffer from large systematic errors due to uncertainties in the astrophysical modeling \kc{of...}.
 Alternatively, the emission of gravitational waves (GWs) from binary NS merger events have proven to be a unique method of probing nuclear physics.
@@
 As the separation decreases through GW emission, tidal forces are magnified and the NSs deform from sphericity, altering the orbital trajectories; a relic which is directly imprinted on the GW signal.
-This deformation is characterized by the \textit{tidal deformability} $\Lambda$ as the linear response of the NSs quadrupole moment $Q_{ij}$ to the neighboring tidal field $\varepsilon_{ij}$.
+This deformation is characterized by the \textit{tidal deformability} $\Lambda$ as the linear response of the NSs quadrupole moment $Q_{ij}$ to the neighboring tidal field $\varepsilon_{ij}$~\cite{hinderer-love,Flanagan2008}.
 
 %reparameterization of the template
-In the case of binary NSs, each star becomes deformed via the process highlighted above, resulting in two highly correlated tidal parameters $\Lambda_1$ and $\Lambda_2$ entering in the gravitational waveform.
-Due to high correlations between between the two parameters, independent extraction becomes very difficult at current interferometer sensitivities.\zc{cite?}
+In the case of binary NSs, each star becomes deformed via the process highlighted above, resulting in two highly correlated tidal parameters $\Lambda_1$ and $\Lambda_2$ entering in the gravitational waveform\cite{Flanagan2008,Vines:2011ud}.
+Due to high correlations between between the two parameters, independent extraction becomes very difficult at current interferometer sensitivities~\cite{Wade:tidalCorrections}.
 Typically, these high correlations can be reduced by strategically reparameterizing the waveform template with new tidal parameters constructed from linear combinations of $\Lambda_1$ and $\Lambda_2$.
-For example, utilizing the parameters $\tilde{\Lambda}$ and $\delta \tilde{\Lambda}$~\cite{hinderer-love,Flanagan2008} which enter the GW waveform at different post-Newtonian (PN) orders (powers of the ratio between the orbital speed and the speed of light $v/c^{2n}$) partially mitigates these correlations.
+For example, utilizing the parameters $\tilde{\Lambda}$ and $\delta \tilde{\Lambda}$~\cite{Favata:2013rwa,Wade:tidalCorrections} which enter the GW waveform at different post-Newtonian (PN) orders (powers of the ratio between the orbital speed and the speed of light $v/c^{2n}$) partially mitigates these correlations.
 
 %Universal relations
-Unfortunately, current detectors are only sensitive enough to accurately measure the dominant tidal parameter, $\tilde{\Lambda}$, known as the chirp deformability.
+Unfortunately, current detectors are only sensitive enough to accurately measure the dominant tidal parameter, $\tilde{\Lambda}$, known as the chirp deformability\kc{That's the first time I hear this term!}.
 Previous work by Yagi and Yunes~\cite{Yagi:binLove} resolved this issue by finding approximately EoS-insensitive ``binary Love universal relations" between symmetric and anti-symmetric combinations of tidal deformabilities $\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$.
-This allows one to further break degeneracies between tidal parameters, resulting in both (i) a decrease in uncertainty upon parameter extraction on the removal of one parameter from the model, and (ii) the ability to measure the secondary tidal parameter upon measurement of the first.
-This important work showed up to an order of magnitude improvement in parameter estimation through a simple Fisher analysis.
+This allows one to further break degeneracies between tidal parameters, resulting in both (i) a decrease in uncertainty upon parameter extraction on the removal of one parameter from the model\kc{decrease in uncertainty in which parameter?}, and (ii) the ability to measure the secondary tidal parameter upon measurement of the first~\cite{Katerina:residuals}.
+Use of this relations leads to up to an order of magnitude improvement in parameter estimation \kc{of what?} through a simple Fisher analysis~\cite{Yagi:binLove}, also confirmed with the detailed analysis of~\cite{Katerina:residuals}.
 Similar ``I-Love-Q" universal relations~\cite{Yagi:ILQ} have been found between individual NS observables: quadrupole moment , moment of inertia, and tidal deformability; similarly allowing the removal of tidal parameters from the model list, and allowing an automatic determination of one observable through the measurement of another.
 
+\kc{Say here that these relations are tuned to many EoS models and have intrinsic uncertainties. }
 %How we improved this

### 2018-12-28 paper/bin-love-after-gw170817.tex
comments on intro

@@
 \subsection{Executive Summary}
+\kc{The paper is fairly short, is the summary here necessary?}
+
 %What we did
@@
 We also find that binaries consisting of one massive hybrid star, and one small-mass hadronic star do not agree with derived binary Love relations, due to the large separation in $\tilde{\Lambda}$ between the constituent stars.
-Unfortunately, due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the universal relations are far outweighed by the statistical errors accrued by extraction of high-order PN tidal parameters from GW waveforms.
-Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from parameter extraction for GW170817 as if it had been observed by future detectors $A \equiv ($ O2, aLIGO, a\texttt{++}, Voyager, ET, CE$)$\zc{cite these individually}.
-Here, $\sigma^A_{\text{GW170817}}$ and $\rho^A_{\text{GW170817}}$ correspond to the statistical error and signal-to-noise-ratio found from observing GW170817 on detector $A$, and $\sigma^A_N$ represents the combined uncertainty after the detection of $N_A$ events (corresponding to the binary NS merger rate associated interferometer $A$).
+Unfortunately\kc{??}, due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the universal relations are far outweighed by the statistical errors accrued by extraction of high-order PN tidal parameters from GW waveforms.
+Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from parameter extraction for GW170817 as if it had been observed by future detectors $A \equiv ($ O2, aLIGO, a\texttt{++}, Voyager, ET, CE$)$\zc{cite these individually}\kc{a\texttt{++} should be A\texttt{+}}.
+Here, $\sigma^A_{\text{GW170817}}$ and $\rho^A_{\text{GW170817}}$ correspond to the statistical error and signal-to-noise-ratio found from observing GW170817 on detector $A$, and $\sigma^A_N$ represents the combined uncertainty after the detection of $N_A$ events (corresponding to the binary NS merger rate associated interferometer $A$)\kc{How are we combining the uncertainty on $\tilde{\Lambda}$ when each event will have a different $\tilde{\Lambda}$?}.
 These values are further tabulated in Table~\ref{tab:variances}.
-It can be seen from this figure that the statistical errors from parameter extraction become comparable the universal relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love universal relations will become viable.
+It can be seen from this figure that the statistical errors from parameter extraction become comparable the universal relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love universal relations will become viable\kc{viable?
+you mean necessary?}.
 \begin{figure}
@@
 Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue) in the extraction of $\tilde{\Lambda}$ from GW170817 (O2) as if observed with future interferometers aLIGO, a++, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
-This is compared to the combined uncertainty $\sigma^A_N$ (red) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper (teal), central (orange), and lower (magenta) limits of expected binary NS merger detection rates for O2, aLIGO, a\texttt{++}, Voyager, CE, and ET-D over 1 observation year.
+This is compared to the combined uncertainty $\sigma^A_N$ (red) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper (teal), central (orange), and lower (magenta) limits of expected binary NS merger detection rates for O2, aLIGO, a\texttt{++}, Voyager, CE, and ET-D over 1 observation year \kc{Instead of points, it might be clearer to show this with shaded regions from the upper to the lower rate.}.
 It can be seen that the statistical errors in parameter extraction become comparable to the systematics from EoS variation in binary Love relations (purple shaded region) for Voyager and on.

### 2018-12-28 paper/bin-love-after-gw170817.tex
sec 2

@@
 The structure of a NS and its tidal interactions in a binary system rely heavily on the underlying state function describing the relationship between pressure ($p$) and energy density ($\epsilon$), or equation of state, of nuclear matter.
-Given that all currently proposed EoSs utilize certain approximations, one method to study a wide range of physically realizable EoSs is to parameterize them in a model-independent way.
+Given that all currently proposed EoSs utilize certain approximations\kc{cite reviews by Baym and Oertel}, one method to study a wide range of physically realizable EoSs is to parameterize them in a model-independent\kc{how is this model-independent?} way.
 Spectral representations~\cite{Lindblom:2010bb,Lindblom:2012zi,Lindblom:2013kra,Lindblom:2018rfr,Abbott:2018exr} parameterize EoSs by performing spectral expansions on the adiabatic index $\Gamma(p)$\footnote{Another way of parameterizing EoSs is the piecewise polytropic formulation~\cite{Read2009,Lackey:2014fwa,Carney:2018sdv}.}:
@@
 In the current analysis, we consider EoSs which have been constrained by the recent binary neutron star merger event, GW170817.
-Important recent work~\cite{LIGO:posterior} sampled EoS parameters in order to derive a marginalized posterior on the pressure as a function of mass density, as seen in Fig.
+Important recent work~\cite{LIGO:posterior,Carney:2018sdv} sampled EoS parameters in order to derive a marginalized posterior on the pressure as a function of mass density, as seen in Fig.
 2 of~\cite{LIGO:posterior}.
 The spectral coefficients were sampled within the ranges: $\gamma_0 \in \lbrack 0.2,2 \rbrack$, $\gamma_1 \in \lbrack -1.6,1.7 \rbrack$, $\gamma_2 \in \lbrack -0.6,0.6 \rbrack$, $\gamma_0 \in \lbrack -0.02,0.02 \rbrack$, and further restricted the adiabatic index to be $\Gamma \in \lbrack 0.6,4.5 \rbrack$, ensuring the parameterization exposed a wide range of viable EoSs~\cite{Lindblom:parameters}.
-Additional constraints imposed upon the generated EoSs were as follows~\cite{LIGO:posterior}: (i) causality within 10\%, and (ii) EoS priors must support NS masses up to $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations.
+Additional constraints imposed upon the generated EoSs were as follows~\cite{LIGO:posterior}: (i) causality within 10\%, and (ii) EoS priors must support NS masses up to $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations\kc{cite}.
 We utilize a random set of 100 of the above posterior samples defined by GW170817, furthermore referenced as the ``constrained EoSs", as shown in Fig.~\ref{fig:eos}.\zc{Carl, can you describe how you generated these?
-They aren't the \emph{actual} posteriors, are they?}
+They aren't the \emph{actual} posteriors, are they?}\kc{Yeah they are}
 Following~\cite{Read2009}, the parameterized high-density core EoSs generated above are matched to the low-density crust EoS Sly~\cite{Douchin:2001sv} at about half of the nuclear saturation density, $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$.

### 2018-12-28 paper/bin-love-after-gw170817.tex
sec 3

@@
 \section{Universal relations}\label{sec:universal}
-In this section, we follow the analyses performed in~\cite{Yagi:binLove,Yagi:ILQ} with two new sets of 100 spectrally generated EoS: (i) posterior samples randomly selected from GW170817s 90\% posterior on on pressure as a function of density as shown in the left panel of Fig.~\ref{fig:eos}, and (ii) those unconstrained by any prior EoS information, as shown in the right panel of Fig.~\ref{fig:eos}.
+In this section, we follow the analyses performed in~\cite{Yagi:binLove,Yagi:ILQ} with two new sets of 100 spectrally generated EoS: (i) posterior samples randomly selected from GW170817s 90\% posterior on on pressure as a function of density as shown in the left panel of Fig.~\ref{fig:eos}, and (ii) those unconstrained by any prior EoS information, as shown in the right panel of Fig.~\ref{fig:eos}.\kc{only one panel}
 
@@
 The new fitting coefficients are presented in Table~\ref{tab:ILQfitNew}.
-While the two above fits both result in fits with similar $R^2$ values of $\sim 0.9999995$ for the data presented, the lattter one has the advantage that it properly limits to the Newtonian case as $\Lambda \rightarrow \infty$~\cite{Yagi:binLove}.
+While the two above fits both result in fits with similar $R^2$\kc{define} values of $\sim 0.9999995$ for the data presented, the lattter one has the advantage that it properly limits to the Newtonian case as $\Lambda \rightarrow \infty$~\cite{Yagi:binLove}.
 

### 2019-01-02 paper/bin-love-after-gw170817.tex
Added C-Love section to the paper

--- 2018-12-28 paper/bin-love-after-gw170817.tex
@@
 
-\title{Universal relations after GW170817\kc{Here and elsewhere: I suggest we use the term "EoS-insensitive" instead of "universal" relations}}
+\title{Universal relations after GW170817}
 
@@
 \author{Katerina Chatziioannou}
-%\affiliation{%
-% Canadian Institute for Theoretical Astrophysics, 60 St. George Street, Toronto, Ontario, M5S 3H8, Canada
-%}%
+\affiliation{%
+ Canadian Institute for Theoretical Astrophysics, 60 St. George Street, Toronto, Ontario, M5S 3H8, Canada
+}%
 \affiliation{%
@@
 % Intro
-The thermodynamic relationship between pressure and density (the equation of state) of \kc{cold} supranuclear matter, accessible primarily in neutron stars\kc{this statement makes nuclear experiment people not happy}, is critical to the study of such stars, and is one of the largest uncertainties in nuclear physics to date.
+The thermodynamic relationship between pressure and density (the equation of state) of supranuclear matter, accessible primarily in neutron stars, is critical to the study of such stars, and is one of the largest uncertainties in nuclear physics to date.
 % How to probe
@@
 % What was done before - I-Love-Q
-Similarly, another set of equation of state \sout{independent}\kc{insensitive} relations exist between individual neutron star parameters: moment of inertia (I), tidal deformability (Love number), and quadrupole moment (Q) - known as the ``I-Love-Q universal relations."
+Similarly, another set of equation of state independent relations exist between individual neutron star parameters: moment of inertia (I), tidal deformability (Love number), quadrupole moment (Q), and compactness (C) - known as the ``I-Love-Q" and ``C-Love" universal relations.
 % What universal relations do
-Such universal relations\kc{so far we have said "EoS-insensitive", "EoS-independent", and "universal".
-We should pick a name and stick with it.
-I suggest "EoS-insensitive"} allow the elimination of some tidal parameters from the list of model parameters, thus breaking degeneracies and ultimately reducing the uncertainty of the dominant tidal effect in parameter estimation\kc{You mean $\tilde{\Lambda}$?
-In our paper with Carl and Aaron we showed that the binary Love relation doesn't affect the $\tilde{\Lambda}$ measurement much.}.
+Such universal relations allow the elimination of some tidal parameters from the list of model parameters, thus breaking degeneracies and ultimately reducing the uncertainty of the dominant tidal effect in parameter estimation.
 % What we will do
-\kc{Add a sentence saying that even the more precise relations have some EoS variation which can cause a systematic error which can be marginalized over}
-In this document, we explain how one can reduce equation of state variation for both binary Love and I-Love-Q universal relations, which helps to reduce systematic errors on the tidal measurement of binary neutron star mergers\kc{but we show that the systematic effects of these relations is very small until next-G detectors.}.
+In this document, we explain how one can reduce equation of state variation for binary Love, I-Love-Q, and C-Love universal relations, which helps to reduce systematic errors on the tidal measurement of binary neutron star mergers.
 We achieve this  by restricting to only equations of state drawn from the 90\% posterior constraint on pressure as a function of density, as derived by the LIGO Collaboration.
 % What we found
-We find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with a mass ratio of 0.75, and in I-Love-Q universality by factors of $\sim 50$\%.
+We find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with a mass ratio of 0.75, in C-Love universality by a factor of $\sim 67\%$, and in I-Love-Q universality by factors of $\sim 50$\%.
 % Conclude
-We end by comparing systematic errors on tidal measurement due to the equation of state variation with statistical errors and comment on whether one can safely use these universal relations with future gravitational wave observations.\kc{We should give the answer to this here: Yes!}
+We end by comparing systematic errors on tidal measurement due to the equation of state variation with statistical errors and comment on whether one can safely use these universal relations with future gravitational wave observations.
 \end{abstract}
@@
 %Intro
-The dependence of pressure on density for \kc{cold} supranuclear matter found primarily inside neutron stars (NSs) remains to be one of the largest mysteries in both nuclear physics and astrophysics.
+The dependence of pressure on density for supranuclear matter found primarily inside neutron stars (NSs) remains to be one of the largest mysteries in both nuclear physics and astrophysics.
 This internal structure of such stars, known as the equation of state (EoS), is exceedingly important, as it is the determining factor for many NS observables - such as the mass, the radius, and many more.
-Unfortunately, terrestrial experiments can only study the EoS up to the nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy}, making NSs ideal laboratories for constraining ultra dense nuclear matter\kc{heavy ion collisions supposedly go to higher densities, but they are T-dependent}.
+Unfortunately, terrestrial experiments can only study the EoS up to the nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy}, making NSs ideal laboratories for constraining ultra dense nuclear matter.
 
@@
 Independent measurements of NS observables can be used to constrain the nuclear EoS.
-For example, electromagnetic observations of the mass-radius relationship of NSs have been used to place limits on NSs\kc{limits on what?}~\cite{guver,ozel-baym-guver,steiner-lattimer-brown,Lattimer2014,Ozel:2016oaf}.
-However, these implications \kc{potentially} suffer from large systematic errors due to uncertainties in the astrophysical modeling \kc{of...}.
+For example, electromagnetic observations of the mass-radius relationship of NSs have been used to place limits on NSs~\cite{guver,ozel-baym-guver,steiner-lattimer-brown,Lattimer2014,Ozel:2016oaf}.
+However, these implications suffer from large systematic errors due to astrophysical mismodeling.
 Alternatively, the emission of gravitational waves (GWs) from binary NS merger events have proven to be a unique method of probing nuclear physics.
@@
 As the separation decreases through GW emission, tidal forces are magnified and the NSs deform from sphericity, altering the orbital trajectories; a relic which is directly imprinted on the GW signal.
-This deformation is characterized by the \textit{tidal deformability} $\Lambda$ as the linear response of the NSs quadrupole moment $Q_{ij}$ to the neighboring tidal field $\varepsilon_{ij}$~\cite{hinderer-love,Flanagan2008}.
+This deformation is characterized by the \textit{tidal deformability} $\Lambda$ as the linear response of the NSs quadrupole moment $Q_{ij}$ to the neighboring tidal field $\varepsilon_{ij}$.
 
 %reparameterization of the template
-In the case of binary NSs, each star becomes deformed via the process highlighted above, resulting in two highly correlated tidal parameters $\Lambda_1$ and $\Lambda_2$ entering in the gravitational waveform\cite{Flanagan2008,Vines:2011ud}.
-Due to high correlations between between the two parameters, independent extraction becomes very difficult at current interferometer sensitivities~\cite{Wade:tidalCorrections}.
+In the case of binary NSs, each star becomes deformed via the process highlighted above, resulting in two highly correlated tidal parameters $\Lambda_1$ and $\Lambda_2$ entering in the gravitational waveform.
+Due to high correlations between between the two parameters, independent extraction becomes very difficult at current interferometer sensitivities.\zc{cite?}
 Typically, these high correlations can be reduced by strategically reparameterizing the waveform template with new tidal parameters constructed from linear combinations of $\Lambda_1$ and $\Lambda_2$.
-For example, utilizing the parameters $\tilde{\Lambda}$ and $\delta \tilde{\Lambda}$~\cite{Favata:2013rwa,Wade:tidalCorrections} which enter the GW waveform at different post-Newtonian (PN) orders (powers of the ratio between the orbital speed and the speed of light $v/c^{2n}$) partially mitigates these correlations.
+For example, utilizing the parameters $\tilde{\Lambda}$ and $\delta \tilde{\Lambda}$~\cite{hinderer-love,Flanagan2008} which enter the GW waveform at different post-Newtonian (PN) orders (powers of the ratio between the orbital speed and the speed of light $v/c^{2n}$) partially mitigates these correlations.
 
 %Universal relations
-Unfortunately, current detectors are only sensitive enough to accurately measure the dominant tidal parameter, $\tilde{\Lambda}$, known as the chirp deformability\kc{That's the first time I hear this term!}.
+Unfortunately, current detectors are only sensitive enough to accurately measure the dominant tidal parameter, $\tilde{\Lambda}$, known as the chirp deformability.
 Previous work by Yagi and Yunes~\cite{Yagi:binLove} resolved this issue by finding approximately EoS-insensitive ``binary Love universal relations" between symmetric and anti-symmetric combinations of tidal deformabilities $\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$.
-This allows one to further break degeneracies between tidal parameters, resulting in both (i) a decrease in uncertainty upon parameter extraction on the removal of one parameter from the model\kc{decrease in uncertainty in which parameter?}, and (ii) the ability to measure the secondary tidal parameter upon measurement of the first~\cite{Katerina:residuals}.
-Use of this relations leads to up to an order of magnitude improvement in parameter estimation \kc{of what?} through a simple Fisher analysis~\cite{Yagi:binLove}, also confirmed with the detailed analysis of~\cite{Katerina:residuals}.
-Similar ``I-Love-Q" universal relations~\cite{Yagi:ILQ} have been found between individual NS observables: quadrupole moment , moment of inertia, and tidal deformability; similarly allowing the removal of tidal parameters from the model list, and allowing an automatic determination of one observable through the measurement of another.
+This allows one to further break degeneracies between tidal parameters, resulting in both (i) a decrease in uncertainty upon parameter extraction on the removal of one parameter from the model, and (ii) the ability to measure the secondary tidal parameter upon measurement of the first.
+This important work showed up to an order of magnitude improvement in parameter estimation through a simple Fisher analysis.
+Similar ``I-Love-Q" and ``C-Love" universal relations~\cite{Yagi:ILQ} have been found between individual NS observables: quadrupole moment , moment of inertia, tidal deformability, and compactness; similarly allowing the removal of tidal parameters from the model list, and allowing an automatic determination of one observable through the measurement of another.
 
-\kc{Say here that these relations are tuned to many EoS models and have intrinsic uncertainties. }
 %How we improved this
@@
 \subsection{Executive Summary}
-\kc{The paper is fairly short, is the summary here necessary?}
-
 %What we did
@@
 First, we generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, where we (i) impose the restriction that they must be drawn from GW170817s 90\% credible posterior in pressure as a function of density, and (ii) don't impose any restrictions for comparison purposes.
-Next, we follow the important works of~\cite{Yagi:binLove} and~\cite{Yagi:ILQ} to show how the ``constrained" set of EoSs show improved universality from both the previous works, and the ``unconstrained" sample, shown by Fig.~\ref{fig:ILQ}.
-In addition, we determine the degree to which hybrid star EoSs obey binary Love universal relations.
+Next, we follow the important works of~\cite{Yagi:binLove} and~\cite{Yagi:ILQ} to show how the ``constrained" set of EoSs show improved universality (binary Love, I-Love-Q, and C-Love) from both the previous works, and the ``unconstrained" sample, shown by Fig.~\ref{fig:ILQ}.
+In addition, we determine the degree to which hybrid star EoSs obey such universal relations.
 Finally, through a simple Fisher analysis, we consider the value in improving universal relations by approximating when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in universal relations.
@@
 %Final Results
-Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with mass ratios of $0.75$, and in I-Love-Q universality by factors of $\sim50$\%, tabulated in Tab.~\ref{tab:maxVar}.
+Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with mass ratios of $0.75$, in C-Love universality by a factor of $\sim 67\%$, and in I-Love-Q universality by factors of $\sim50$\%, tabulated in Tab.~\ref{tab:maxVar}.
 We also find that binaries consisting of one massive hybrid star, and one small-mass hadronic star do not agree with derived binary Love relations, due to the large separation in $\tilde{\Lambda}$ between the constituent stars.
-Unfortunately\kc{??}, due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the universal relations are far outweighed by the statistical errors accrued by extraction of high-order PN tidal parameters from GW waveforms.
-Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from parameter extraction for GW170817 as if it had been observed by future detectors $A \equiv ($ O2, aLIGO, a\texttt{++}, Voyager, ET, CE$)$\zc{cite these individually}\kc{a\texttt{++} should be A\texttt{+}}.
-Here, $\sigma^A_{\text{GW170817}}$ and $\rho^A_{\text{GW170817}}$ correspond to the statistical error and signal-to-noise-ratio found from observing GW170817 on detector $A$, and $\sigma^A_N$ represents the combined uncertainty after the detection of $N_A$ events (corresponding to the binary NS merger rate associated interferometer $A$)\kc{How are we combining the uncertainty on $\tilde{\Lambda}$ when each event will have a different $\tilde{\Lambda}$?}.
+Unfortunately, due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the universal relations are far outweighed by the statistical errors accrued by extraction of high-order PN tidal parameters from GW waveforms.
+Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from parameter extraction for GW170817 as if it had been observed by future detectors $A \equiv ($ O2, aLIGO, a\texttt{++}, Voyager, ET, CE$)$\zc{cite these individually}.
+Here, $\sigma^A_{\text{GW170817}}$ and $\rho^A_{\text{GW170817}}$ correspond to the statistical error and signal-to-noise-ratio found from observing GW170817 on detector $A$, and $\sigma^A_N$ represents the combined uncertainty after the detection of $N_A$ events (corresponding to the binary NS merger rate associated interferometer $A$).
 These values are further tabulated in Table~\ref{tab:variances}.
-It can be seen from this figure that the statistical errors from parameter extraction become comparable the universal relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love universal relations will become viable\kc{viable?
-you mean necessary?}.
+It can be seen from this figure that the statistical errors from parameter extraction become comparable the universal relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love universal relations will become viable.
 \begin{figure}
@@
 Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue) in the extraction of $\tilde{\Lambda}$ from GW170817 (O2) as if observed with future interferometers aLIGO, a++, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
-This is compared to the combined uncertainty $\sigma^A_N$ (red) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper (teal), central (orange), and lower (magenta) limits of expected binary NS merger detection rates for O2, aLIGO, a\texttt{++}, Voyager, CE, and ET-D over 1 observation year \kc{Instead of points, it might be clearer to show this with shaded regions from the upper to the lower rate.}.
+This is compared to the combined uncertainty $\sigma^A_N$ (red) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper (teal), central (orange), and lower (magenta) limits of expected binary NS merger detection rates for O2, aLIGO, a\texttt{++}, Voyager, CE, and ET-D over 1 observation year.
 It can be seen that the statistical errors in parameter extraction become comparable to the systematics from EoS variation in binary Love relations (purple shaded region) for Voyager and on.
@@
 We begin with a complementary background and theory material in Sec.~\ref{sec:theory}.
-We continue in Sec.~\ref{sec:universal} by finding new and improved binary Love and I-Love-Q universal relations, and considering how well hybrid star EoSs agree with the universal relations.
+We continue in Sec.~\ref{sec:universal} by finding new and improved binary Love, I-Love-Q, and C-Love universal relations, and considering how well hybrid star EoSs agree with the universal relations.
 We next examine these improved universal relations and question whether or not they are useful for future interferometers in Sec.~\ref{sec:observations}.
@@
 where $y$ and $x$ correspond to NS observables $\bar{I}$, $\bar{Q}$, and $\Lambda$, and $\alpha$ is given by $2/5$, $1/5$, and $2$ for the $\bar{I}-\Lambda$, $\bar{Q}-\Lambda$, and $\bar{I}-\bar{Q}$ relations, respectively.
-The new fitting coefficients are presented in Table~\ref{tab:ILQfitNew}.
+The new fitting coefficients are presented in Tab.~\ref{tab:ILQfitNew}.
 While the two above fits both result in fits with similar $R^2$ values of $\sim 0.9999995$ for the data presented, the lattter one has the advantage that it properly limits to the Newtonian case as $\Lambda \rightarrow \infty$~\cite{Yagi:binLove}.
@@
 \caption{
-I-Love-Q universal relations fit parameters for the constrained EoS data using the improved fitting relations found in Eq.~\ref{eq:ILQfitNew}.
+I-Love-Q and C-Love universal relations fit parameters for the constrained EoS data using the improved fitting relations found in Eq.~\ref{eq:ILQfitNew}.
 This fitting relation, unlike previous versions, properly limits to the Newtonian case as $\Lambda \rightarrow \infty$.
@@
  $\bar{I}$ & $\bar{Q}$ & $2$ & $0.0089212$ & $10.5910815$ & $-37.4581345$ & $43.1831156$ & $-2.3610288$ & $1.9674667$ & $-0.5678018$\\
+ $\bar{C}$ & $\Lambda$ & $-1/5$ & $0.2495709$ & $-919.5651942$ & $330.2848184$ & $-857.1842107$ & $-383.5404843$ & $192.4933832$ & $-811.1425435$\\
 \hline
@@
 \caption{
-Comparison between the universal relations (both I-Love-Q and binary Love) maximal EoS variability for the results of previous works~\cite{Yagi:ILQ,Yagi:binLove}, and the unconstrained and constrained sets of EoSs analyzed here.
+Comparison between the universal relations (I-Love-Q, C-Love, and binary Love) maximal EoS variability for the results of previous works~\cite{Yagi:ILQ,Yagi:binLove}, and the unconstrained and constrained sets of EoSs analyzed here.
 The maximum EoS variation, given by the largest fractional difference from the fits as shown in Figs.~\ref{fig:ILQ} and~\ref{fig:binLove}, sees a considerable improvement for the constrained set of EoSs, compared to the unconstrained set as well as previous works.
@@
  $\bar{I}-\Lambda$ &  $0.0059$ & $0.0076725$ & $0.0031383$\\
- $\bar{Q}-\Lambda$ & $0.0010$ & $0.012617$ & $0.0046612$\\
+ $\bar{Q}-\Lambda$ & $0.010$ & $0.012617$ & $0.0046612$\\
  $\bar{I}-\bar{Q}$ & $0.012$ & $0.014895$ & $0.0057157$\\
+ \hline
+ $\bar{C}-\Lambda$ & $0.065$ & $0.071975$ & $0.021688$\\
  \hline
@@
 Concluding, we claim that hybrid star EoSs \emph{do} obey the I-Love-Q universal relations computed through nuclear EoS data, with the exception that the universality goes up to $\sim1.7$\%.
+
+\subsection{C-Love Relations}\label{sec:clove}
+In this section we consider approximate C-Love universal relations between NS compactness $\bar{C} \equiv M/R$ and unitless tidal deformability $\Lambda$, as discussed by Yagi and Yunes~\cite{Yagi:binLove}.
+Similar to the previous section, we consider two classes of stars: nuclear matter EoSs and hybrid quark-hadron star EoSs.
+
+\subsubsection{Nuclear matter stars}\label{sec:clove-nuc}
+Following Ref.~\cite{Yagi:binLove}, we begin by fitting the data for each set of EoSs to the simple curve:
+\begin{equation}
+\bar{C} = \sum^2_{k=0} a_k (\ln{\Lambda})^k.
+\end{equation}
+Doing so yields $a_0 = 0.3616998$, $a_1 = -0.0354818$, and $a_2 = 0.0006193849$, similar to what was found in Ref.~\cite{Yagi:binLove}.
+Additionally we offer an improvement to the fits as was done in Sec.~\ref{sec:ilq}. 
+We consider the fitting function found in Eq.~\ref{eq:ILQfitNew}, with the controlling factor given by:
+\begin{equation}
+\bar{C}^N=C_{\bar{C}\Lambda}\Lambda^{-1/5}.
+\end{equation}
+The new fitting coefficients are displayed in Tab.~\ref{tab:ILQfitNew}, alongside the previously found I-Love-Q relations.
+
+Figure~\ref{fig:clove} presents the C-Love universal relations for both the constrained and unconstrained sets of EoSs, along with the relative fractional difference from the fits. 
+Observe how the constrained EoSs show a large suppression in EoS variability compared to both the unconstrained EoSs, as well as that found in previous works~\cite{Yagi:binLove}.
+The maximal EoS variation is compared between the above three cases in Tab.~\ref{tab:maxVar}.
+\begin{figure}
+\begin{center} 
+\includegraphics[width=1\columnwidth]{CL.eps}
+\end{center}
+\caption{
+Similar to Fig.~\ref{fig:ILQ} but for C-Love universal relations.
+In this figure, we similarly construct fits to  Eq.~\ref{eq:ILQfitNew}, properly limiting to the newtonian case $\bar{C} \sim \Lambda^{-1/5}$.
+Observe how, as before, the fractional difference from the fits is greatly suppressed for the constrained case, compared to both the unconstrained case, and results from previous works~\cite{Yagi:binLove}.
+The maximal EoS variation from the fits for the unconstrained and constrained sets of EoSs are compared in Tab.~\ref{tab:maxVar}.
+Additionally shown in this figure is the hybrid star C-Love relations along with their fractional difference from the constrained EoS fits (dashed green).
+}
+\label{fig:clove}
+\end{figure}
+
+These results, similar to that found in Sec.~\ref{sec:ilq}, show the considerable improvement found in using constrained EoSs over any unconstrained set.
+We also note that the unconstrained EoSs display slightly larger EoS variability than found in Ref.~\cite{Yagi:binLove}, due to the large random sampling as discussed previously in Sec.~\ref{sec:ilq}.
+
+\subsubsection{Hybrid quark-hadron stars}\label{sec:clove-hyb}
+In this section, we consider the effect of hybrid star EoSs on the C-Love universal relation.
+Much like Sec.~\ref{sec:ilq-hyb}, we perform 3 separate fits (constrained and hybrid EoSs combined, constrained EoSs only, and hybrid EoSs only) and compare the maximal EoS variation for each class of EoSs.
+
+Table~\ref{tab:hybridCompareClove} compares the maximal EoS variability for the constrained and hybrid star EoSs under the fitting conditions for each case described above. 
+We observe very similar behavior to that described in Sec.~\ref{sec:ilq-hyb}, in which the maximal EoS variation for hybrid stars only fluctuate slightly ($\sim 4.5\% - 7\%$) for each case.
+From this, we similarly conclude that hybrid stars do obey the C-Love universal relation derived with nuclear matter stars, with the caveat that the maximum universality increases to $\sim 7.1\%$.
+This is exemplified in Fig.~\ref{fig:clove} by the dashed green curves.
+
+\begin{table}
+\centering
+\caption{
+Similar to Tab.~\ref{tab:hybridCompare} but for the C-Love universal relation.
+Observe how for all 3 cases, the hybrid EoSs are only universal up to a minimum of $\sim1$\%, while in each case the constrained EoSs outperform the hybrid ones.
+The second case is demonstrated in Fig.~\ref{fig:clove}.
+}\label{tab:hybridCompareClove}
+\begin{tabular}{ c  || c c } 
+ \hline
+ \hline
+ \textbf{Fitting} & \multicolumn{2}{c}{\textbf{Maximal EoS Variability}} \\
+ \cline{2-3}
+ \textbf{Case} &  \multicolumn{1}{c|}{\emph{Constrained}} & \emph{Hybrid}\\
+ \hline
+ \emph{Combined} &  \multirow{2}{*}{$0.0368589$} & \multirow{2}{*}{$0.0553262$}\\
+ \emph{(Case 1)} & &\\
+ \cline{1-1}
+ \emph{Constrained only} & \multirow{2}{*}{$0.0.0216879$} & \multirow{2}{*}{$0.0.0719104$}\\
+  \emph{(Case 2)} & &\\
+  \cline{1-1}
+ \emph{Hybrid only} & \multirow{2}{*}{$0.0.0578764$} & \multirow{2}{*}{$0.0.0447799$}\\
+  \emph{(Case 3)} & &\\
+  \cline{1-1}
+\hline
+\hline
+\end{tabular}
+\end{table}
 
@@
 Observe how the standard deviations $\sigma=7.666$ and $\sigma=40.887$ show a large decrease between the unconstrained and constrained sets of EoSs.
-In addition, we find the 90th, 99th, and 100th percentiles on $\tilde\Lambda$ to be $P_{90}=12.014$, $P_{99}=29.710$, and $P_{100}=62.240$ for the constrained EoSs.
+In addition, we find the 90th, 99th, and 100th percentiles on $\tilde\Lambda$ to be $P_{90}=12.014$, $P_{99}=29.710$, and $P_{100}=62.240$ for the constrained EoSs, computed directly from the data rather than the fitted models.
 Because the un-binned residuals seen in Fig.~\ref{fig:residuals} are dominated by the low-error regions of parameter space ($\Lambda_s \rightarrow 0$ and $q \rightarrow 1$) shown by the fits of Tab.~\ref{tab:marginalized}, we consider the 90th for the remainder of the analysis.
@@
 Residuals on $\tilde\Lambda$ computed as $\tilde{\Lambda}^{\text{fit}}-\tilde{\Lambda}^{\text{true}}$ for the binary Love relations modeled in Sec.~\ref{sec:binLove-nuclear} for both constrained and unconstrained sets of EoSs.
-These residuals obey Gaussian distributions centered at $\mu=-1.8133 \times 10^{-4}$ and $\mu=4.2258 \times 10^{-3}$ with standard deviations of $\sigma=7.6664$ and $\sigma=40.8866$ for the constrained and unconstrained sets of EoSs, respectively.
+These residuals obey Gaussian distributions (displayed here as dashed lines) centered at $\mu=-1.8133 \times 10^{-4}$ and $\mu=4.2258 \times 10^{-3}$ with standard deviations of $\sigma=7.6664$ and $\sigma=40.8866$ for the constrained and unconstrained sets of EoSs, respectively.
 These uncertainties correspond roughly to the systematic errors introduced on the parameter extraction of $\tilde{\Lambda}$ upon the use of binary Love universal relations.
@@
 \item Generate a population of $N_A$ events corresponding to the expected binary NS merger detection rate for detector $A$, following the distribution $f=3 \rho_{\text{th}}^3/\rho^4$~\cite{Shutz:SNR,Chen:SNR} with a network SNR threshold of $\rho_{\text{th}}=8$.
-This is calculated for the upper, central, and lower limits of the local binary NS coalescence rate density $R=1540^{+3200}_{-1220} \text{ Gpc}^{-3}\text{yr}^{-1}$~\cite{Abbott2017}, giving the rates shown in the second column of Table~\ref{tab:variances}.
+This is calculated for the upper, central, and lower limits of the local binary NS coalescence rate density $\mathcal{R}=1540^{+3200}_{-1220} \text{ Gpc}^{-3}\text{yr}^{-1}$~\cite{Abbott2017}, giving the rates shown in the second column of Table~\ref{tab:variances}.
 \item Compute the population standard deviation given by:
@@
 \caption{
-Tabulated results for the estimated statistical errors on $\tilde{\Lambda}$ for the combined results of $N_A$ detections corresponding to the estimated upper, central, and lower limits of the binary NS merger detection rate $R$.
+Tabulated results for the estimated statistical errors on $\tilde{\Lambda}$ for the combined results of $N_A$ detections corresponding to the estimated upper, central, and lower limits of the binary NS merger detection rate $\mathcal{R}$.
 This is repeated for 5 future detector sensitivities: aLIGO, a\texttt{++}, Voyager, CE, and ET.
@@
 We find an improvement upon these universal relations by a factor of $\sim 59$\% for stars with mass ratios of $0.75$ by restricting to the EoS posterior samples from GW170817s 90\% credible region on pressure as a function of density.
-Similarly, we find an increase in I-Love-Q universality by a factors of $\sim 50$\%.
-In addition, we find that binaries consisting of one massive hybrid quark-hadron star, and one small-mass hadron star do not obey these universal relations -- explained by the large difference in $\tilde{\Lambda}$ displayed between the constituent stars.
+Similarly, we find an increase in C-Love and I-Love-Q universality by a factors of $\sim 76$\% and $\sim 50$\%, respectively.
+Additionally, we find that hybrid quark-hadron star EoSs \emph{do} obey the I-Love-Q and C-Love universality, albeit with a slightly higher maximum EoS variability as displayed in Tabs.~\ref{tab:hybridCompare} and ~\ref{tab:hybridCompareClove}.
+In addition, we find that binaries consisting of one massive hybrid quark-hadron star, and one small-mass hadron star do not obey the binary Love universal relations -- explained by the large difference in $\tilde{\Lambda}$ displayed between the constituent stars.
 To improve on this, we construct new ``hybrid matter binary Love relations", applied to only the hybrid branches of the transitional EoSs.

### 2019-01-02 paper/bin-love-after-gw170817.tex
added C-Love section to paper

--- 2018-12-28 paper/bin-love-after-gw170817.tex
@@
 % What was done before - I-Love-Q
-Similarly, another set of equation of state \sout{independent}\kc{insensitive} relations exist between individual neutron star parameters: moment of inertia (I), tidal deformability (Love number), and quadrupole moment (Q) - known as the ``I-Love-Q universal relations."
+Similarly, another set of equation of state independent relations exist between individual neutron star parameters: moment of inertia (I), tidal deformability (Love number), quadrupole moment (Q), and compactness (C) - known as the ``I-Love-Q" and ``C-Love" universal relations.
 % What universal relations do
@@
 % What we found
-We find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with a mass ratio of 0.75, and in I-Love-Q universality by factors of $\sim 50$\%.
+We find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with a mass ratio of 0.75, in C-Love universality by a factor of $\sim 67\%$, and in I-Love-Q universality by factors of $\sim 50$\%.
 % Conclude
@@
 Use of this relations leads to up to an order of magnitude improvement in parameter estimation \kc{of what?} through a simple Fisher analysis~\cite{Yagi:binLove}, also confirmed with the detailed analysis of~\cite{Katerina:residuals}.
-Similar ``I-Love-Q" universal relations~\cite{Yagi:ILQ} have been found between individual NS observables: quadrupole moment , moment of inertia, and tidal deformability; similarly allowing the removal of tidal parameters from the model list, and allowing an automatic determination of one observable through the measurement of another.
+Similar ``I-Love-Q" and ``C-Love" universal relations~\cite{Yagi:ILQ} have been found between individual NS observables: quadrupole moment , moment of inertia, tidal deformability, and compactness; similarly allowing the removal of tidal parameters from the model list, and allowing an automatic determination of one observable through the measurement of another.
 
@@
 First, we generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, where we (i) impose the restriction that they must be drawn from GW170817s 90\% credible posterior in pressure as a function of density, and (ii) don't impose any restrictions for comparison purposes.
-Next, we follow the important works of~\cite{Yagi:binLove} and~\cite{Yagi:ILQ} to show how the ``constrained" set of EoSs show improved universality from both the previous works, and the ``unconstrained" sample, shown by Fig.~\ref{fig:ILQ}.
+Next, we follow the important works of~\cite{Yagi:binLove} and~\cite{Yagi:ILQ} to show how the ``constrained" set of EoSs show improved universality (binary Love, I-Love-Q, and C-Love) from both the previous works, and the ``unconstrained" sample, shown by Fig.~\ref{fig:ILQ}.
 In addition, we determine the degree to which hybrid star EoSs obey binary Love universal relations.
@@
 %Final Results
-Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with mass ratios of $0.75$, and in I-Love-Q universality by factors of $\sim50$\%, tabulated in Tab.~\ref{tab:maxVar}.
+Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with mass ratios of $0.75$, in C-Love universality by a factor of $\sim 67\%$, and in I-Love-Q universality by factors of $\sim50$\%, tabulated in Tab.~\ref{tab:maxVar}.
+Additionally, we find that hybrid quark-hadron stars do obey the I-Love-Q and C-Love universal relations, with sightly increased EoS variability.
 We also find that binaries consisting of one massive hybrid star, and one small-mass hadronic star do not agree with derived binary Love relations, due to the large separation in $\tilde{\Lambda}$ between the constituent stars.
@@
 
-Similar universal relations have been found to exist between individual NS observables: moment of inertia (I), tidal deformability (Love), and quadrupole moment (Q), known as the ``I-Love-Q" universal relations~\cite{Yagi:ILQ}.
-These have been found to be EoS insensitive by up to 1\% for each of pair of observables.
+Similar universal relations have been found to exist between individual NS observables: moment of inertia (I), tidal deformability (Love), quadrupole moment (Q), and compactness (C), known as the ``I-Love-Q" and ``C-Love" universal relations~\cite{Yagi:ILQ, Yagi:binLove}.
+These have been found to be EoS insensitive by up to 1\% and 6.5\% respectively.
 In this paper, we show improvement in both of these universal relations by restricting to EoSs sampled from GW170817s posterior on pressure as a function of density.

### 2019-01-06 paper/bin-love-after-gw170817.tex
C-Love universality

@@
 
-\title{Universal relations after GW170817\kc{Here and elsewhere: I suggest we use the term "EoS-insensitive" instead of "universal" relations}}
+\title{EoS-insensitive relations after GW170817}
 
@@
 % Intro
-The thermodynamic relationship between pressure and density (the equation of state) of \kc{cold} supranuclear matter, accessible primarily in neutron stars\kc{this statement makes nuclear experiment people not happy}, is critical to the study of such stars, and is one of the largest uncertainties in nuclear physics to date.
+The thermodynamic relationship between pressure and density (the equation of state, or EoS) of cold supranuclear matter, accessible in neutron stars, is critical to the study of such stars, and is one of the largest uncertainties in nuclear physics to date.
 % How to probe
@@
 % What was done before - Binary Love
-Previous studies have shown that approximately equation of state insensitive ``binary Love universal relations" exist between symmetric and antisymmetric combinations of individual tidal deformabilities, which are difficult to be independently measured with second-generation gravitational wave interferometers.
+Previous studies have shown that approximately EoS-insensitive ``binary Love universal relations" exist between symmetric and antisymmetric combinations of individual tidal deformabilities, which are difficult to be independently measured with second-generation gravitational wave interferometers.
 % What was done before - I-Love-Q
-Similarly, another set of equation of state independent relations exist between individual neutron star parameters: moment of inertia (I), tidal deformability (Love number), quadrupole moment (Q), and compactness (C) - known as the ``I-Love-Q" and ``C-Love" universal relations.
+Similarly, another set of EoS-insensitive relations exist between individual neutron star parameters: moment of inertia (I), tidal deformability (Love number), quadrupole moment (Q), and compactness (C) - known as the ``I-Love-Q" and ``C-Love" universal relations.
 % What universal relations do
-Such universal relations\kc{so far we have said "EoS-insensitive", "EoS-independent", and "universal".
-We should pick a name and stick with it.
-I suggest "EoS-insensitive"} allow the elimination of some tidal parameters from the list of model parameters, thus breaking degeneracies and ultimately reducing the uncertainty of the dominant tidal effect in parameter estimation\kc{You mean $\tilde{\Lambda}$?
+Such EoS-insensitive relations allow the elimination of some tidal parameters from the list of model parameters, thus breaking degeneracies and ultimately reducing the uncertainty of the dominant tidal effect in parameter estimation\kc{You mean $\tilde{\Lambda}$?
 In our paper with Carl and Aaron we showed that the binary Love relation doesn't affect the $\tilde{\Lambda}$ measurement much.}.
@@
 \kc{Add a sentence saying that even the more precise relations have some EoS variation which can cause a systematic error which can be marginalized over}
-In this document, we explain how one can reduce equation of state variation for both binary Love and I-Love-Q universal relations, which helps to reduce systematic errors on the tidal measurement of binary neutron star mergers\kc{but we show that the systematic effects of these relations is very small until next-G detectors.}.
+In this document, we explain how one can reduce equation of state variation for I-Love-Q, C-Love, and binary Love EoS-insensitive relations, which helps to reduce systematic errors on the tidal measurement of binary neutron star mergers.
+However, we show that the systematic effects of these relations is very small until next-generation detectors. 
 We achieve this  by restricting to only equations of state drawn from the 90\% posterior constraint on pressure as a function of density, as derived by the LIGO Collaboration.
@@
 % Conclude
-We end by comparing systematic errors on tidal measurement due to the equation of state variation with statistical errors and comment on whether one can safely use these universal relations with future gravitational wave observations.\kc{We should give the answer to this here: Yes!}
+We end by comparing systematic errors on tidal measurement due to the equation of state variation with statistical errors and comment on whether one can safely use these EoS-insensitive relations with future gravitational wave observations.
+We conclude that the systematic errors injected from the use of improved EoS-insensitive relations become comparable to the statistical errors for future design upgrade Voyager.
 \end{abstract}
@@
 %Intro
-The dependence of pressure on density for \kc{cold} supranuclear matter found primarily inside neutron stars (NSs) remains to be one of the largest mysteries in both nuclear physics and astrophysics.
+The dependence of pressure on density for cold supranuclear matter found inside neutron stars (NSs) remains to be one of the largest mysteries in both nuclear physics and astrophysics.
 This internal structure of such stars, known as the equation of state (EoS), is exceedingly important, as it is the determining factor for many NS observables - such as the mass, the radius, and many more.
@@
 Independent measurements of NS observables can be used to constrain the nuclear EoS.
-For example, electromagnetic observations of the mass-radius relationship of NSs have been used to place limits on NSs\kc{limits on what?}~\cite{guver,ozel-baym-guver,steiner-lattimer-brown,Lattimer2014,Ozel:2016oaf}.
-However, these implications \kc{potentially} suffer from large systematic errors due to uncertainties in the astrophysical modeling \kc{of...}.
+For example, electromagnetic observations of the mass-radius relationship of NSs have been used to place limits on the NS EoS~\cite{guver,ozel-baym-guver,steiner-lattimer-brown,Lattimer2014,Ozel:2016oaf}.
+However, these implications potentially suffer from large systematic errors due to astrophysical mismodeling uncertainties\kc{of...}.
 Alternatively, the emission of gravitational waves (GWs) from binary NS merger events have proven to be a unique method of probing nuclear physics.
@@
 %Universal relations
-Unfortunately, current detectors are only sensitive enough to accurately measure the dominant tidal parameter, $\tilde{\Lambda}$, known as the chirp deformability\kc{That's the first time I hear this term!}.
-Previous work by Yagi and Yunes~\cite{Yagi:binLove} resolved this issue by finding approximately EoS-insensitive ``binary Love universal relations" between symmetric and anti-symmetric combinations of tidal deformabilities $\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$.
-This allows one to further break degeneracies between tidal parameters, resulting in both (i) a decrease in uncertainty upon parameter extraction on the removal of one parameter from the model\kc{decrease in uncertainty in which parameter?}, and (ii) the ability to measure the secondary tidal parameter upon measurement of the first~\cite{Katerina:residuals}.
-Use of this relations leads to up to an order of magnitude improvement in parameter estimation \kc{of what?} through a simple Fisher analysis~\cite{Yagi:binLove}, also confirmed with the detailed analysis of~\cite{Katerina:residuals}.
-Similar ``I-Love-Q" and ``C-Love" universal relations~\cite{Yagi:ILQ} have been found between individual NS observables: quadrupole moment , moment of inertia, tidal deformability, and compactness; similarly allowing the removal of tidal parameters from the model list, and allowing an automatic determination of one observable through the measurement of another.
+Unfortunately, current detectors are only sensitive enough to accurately measure the dominant tidal parameter, $\tilde{\Lambda}$.
+Previous work by Yagi and Yunes~\cite{Yagi:binLove} resolved this issue by finding approximately EoS-insensitive ``binary Love universal relations" between symmetric and anti-symmetric combinations of tidal deformabilities $\Lambda_{s,a}=\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$.
+This allows one to further break degeneracies between tidal parameters, resulting in both (i) a decrease in uncertainty upon parameter extraction of $\Lambda_s$ on the removal of parameter $\Lambda_a$ from the model, and (ii) the ability to measure the secondary tidal parameter upon measurement of the first~\cite{Katerina:residuals}.
+Use of these relations leads to up to an order of magnitude improvement in parameter estimation of $\Lambda_s$ through a simple Fisher analysis~\cite{Yagi:binLove}, also confirmed with the detailed analysis of~\cite{Katerina:residuals}.
+Similar ``I-Love-Q" and ``C-Love" EoS-insensitive relations~\cite{Yagi:ILQ} have been found between individual NS observables: quadrupole moment , moment of inertia, tidal deformability, and compactness; similarly allowing the removal of tidal parameters from the model list, and allowing an automatic determination of one observable through the measurement of another.
+However, these EoS-insensitive relations have been tuned to a collection of EoS models, and each have intrinsic uncertainties associated with their use.
 
-\kc{Say here that these relations are tuned to many EoS models and have intrinsic uncertainties. }
 %How we improved this
 In this analysis, we aim to improve this important work by imposing the restrictions found on the EoS~\cite{LIGO:posterior} derived from the recent binary NS merger observation, GW170817~\cite{TheLIGOScientific:2017qsa}.
-By restricting to only EoSs which lie within the the 90\% credible region on pressure as a function of density found in~\cite{LIGO:posterior}, we repeat the analyses done in~\cite{Yagi:binLove,Yagi:ILQ} and show an increase in universality for both binary Love and I-Love-Q universal relations.
+By restricting to only EoSs which lie within the the 90\% credible region on pressure as a function of density found in~\cite{LIGO:posterior}, we repeat the analyses done in~\cite{Yagi:binLove,Yagi:ILQ} and show an increase in universality for I-Love-Q, C-Love, and binary Love EoS-insensitive relations.
 In addition, we consider hybrid star EoSs seen in~\cite{Paschalidis2018}, which experience strong first-order transitions from hadronic matter to quark matter.
 These provide a departure from the nuclear matter relations considered here - providing valuable insight into them.
-Further, we estimate the viability of using improved universal relations on future GW detections by performing simple Fisher analyses to approximate when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in universal relations.
+Further, we estimate the viability of using improved EoS-insensitive relations on future GW detections by performing simple Fisher analyses to approximate when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in EoS-insensitive relations.
 
@@
 %What we did
-In this paper we attempt to improve binary Love and I-Love-Q universal relations by imposing constraints on the EoS found by GW170817~\cite{LIGO:posterior,TheLIGOScientific:2017qsa}.
+In this paper we attempt to improve I-Love-Q, C-Love, and binary Love EoS-insensitive relations by imposing constraints on the EoS found by GW170817~\cite{LIGO:posterior,TheLIGOScientific:2017qsa}.
 First, we generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, where we (i) impose the restriction that they must be drawn from GW170817s 90\% credible posterior in pressure as a function of density, and (ii) don't impose any restrictions for comparison purposes.
 Next, we follow the important works of~\cite{Yagi:binLove} and~\cite{Yagi:ILQ} to show how the ``constrained" set of EoSs show improved universality (binary Love, I-Love-Q, and C-Love) from both the previous works, and the ``unconstrained" sample, shown by Fig.~\ref{fig:ILQ}.
-In addition, we determine the degree to which hybrid star EoSs obey binary Love universal relations.
-Finally, through a simple Fisher analysis, we consider the value in improving universal relations by approximating when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in universal relations.
+In addition, we determine the degree to which hybrid star EoSs obey binary Love EoS-insensitive relations.
+Finally, through a simple Fisher analysis, we consider the value in improving EoS-insensitive relations by approximating when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in EoS-insensitive relations.
 
@@
 Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with mass ratios of $0.75$, in C-Love universality by a factor of $\sim 67\%$, and in I-Love-Q universality by factors of $\sim50$\%, tabulated in Tab.~\ref{tab:maxVar}.
-Additionally, we find that hybrid quark-hadron stars do obey the I-Love-Q and C-Love universal relations, with sightly increased EoS variability.
+Additionally, we find that hybrid quark-hadron stars do obey the I-Love-Q and C-Love EoS-insensitive relations, with sightly increased EoS variability.
 We also find that binaries consisting of one massive hybrid star, and one small-mass hadronic star do not agree with derived binary Love relations, due to the large separation in $\tilde{\Lambda}$ between the constituent stars.
-Unfortunately\kc{??}, due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the universal relations are far outweighed by the statistical errors accrued by extraction of high-order PN tidal parameters from GW waveforms.
-Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from parameter extraction for GW170817 as if it had been observed by future detectors $A \equiv ($ O2, aLIGO, a\texttt{++}, Voyager, ET, CE$)$\zc{cite these individually}\kc{a\texttt{++} should be A\texttt{+}}.
-Here, $\sigma^A_{\text{GW170817}}$ and $\rho^A_{\text{GW170817}}$ correspond to the statistical error and signal-to-noise-ratio found from observing GW170817 on detector $A$, and $\sigma^A_N$ represents the combined uncertainty after the detection of $N_A$ events (corresponding to the binary NS merger rate associated interferometer $A$)\kc{How are we combining the uncertainty on $\tilde{\Lambda}$ when each event will have a different $\tilde{\Lambda}$?}.
+Due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the EoS-insensitive relations are far outweighed by the statistical errors accrued by extraction of high-order PN tidal parameters from GW waveforms.
+Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from parameter extraction for GW170817 as if it had been observed by future detectors $A \equiv ($ O2, aLIGO, A\texttt{+}, Voyager, ET, CE$)$\zc{cite these individually}.
+Here, $\sigma^A_{\text{GW170817}}$ and $\rho^A_{\text{GW170817}}$ correspond to the statistical error and signal-to-noise-ratio found from observing GW170817 on detector $A$, and $\sigma^A_N$ represents the combined uncertainty after the detection of $N_A$ events (corresponding to the binary NS merger rate associated interferometer $A$).
 These values are further tabulated in Table~\ref{tab:variances}.
-It can be seen from this figure that the statistical errors from parameter extraction become comparable the universal relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love universal relations will become viable\kc{viable?
-you mean necessary?}.
+It can be seen from this figure that the statistical errors from parameter extraction become comparable the EoS-insensitive relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love EoS-insensitive relations will become necessary.
 \begin{figure}
@@
 \caption{
-Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue) in the extraction of $\tilde{\Lambda}$ from GW170817 (O2) as if observed with future interferometers aLIGO, a++, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
-This is compared to the combined uncertainty $\sigma^A_N$ (red) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper (teal), central (orange), and lower (magenta) limits of expected binary NS merger detection rates for O2, aLIGO, a\texttt{++}, Voyager, CE, and ET-D over 1 observation year \kc{Instead of points, it might be clearer to show this with shaded regions from the upper to the lower rate.}.
+Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue circle) in the extraction of $\tilde{\Lambda}$ from GW170817 (O2) as if observed with future interferometers aLIGO, A\texttt{+}, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
+This is compared to the combined uncertainty $\sigma^A_N$ (turqoise shaded region) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper and lower limits of expected binary NS merger detection rates for O2, aLIGO, A\texttt{+}, Voyager, CE, and ET-D over 1 observation year.
 It can be seen that the statistical errors in parameter extraction become comparable to the systematics from EoS variation in binary Love relations (purple shaded region) for Voyager and on.
@@
 We begin with a complementary background and theory material in Sec.~\ref{sec:theory}.
-We continue in Sec.~\ref{sec:universal} by finding new and improved binary Love, I-Love-Q, and C-Love universal relations, and considering how well hybrid star EoSs agree with the universal relations.
-We next examine these improved universal relations and question whether or not they are useful for future interferometers in Sec.~\ref{sec:observations}.
+We continue in Sec.~\ref{sec:universal} by finding new and improved binary Love, I-Love-Q, and C-Love EoS-insensitive relations, and considering how well hybrid star EoSs agree with the EoS-insensitive relations.
+We next examine these improved EoS-insensitive relations and question whether or not they are useful for future interferometers in Sec.~\ref{sec:observations}.
 We conclude in Sec.~\ref{sec:conclusion} by discussing our results and mentioning avenues of future work.
@@
 The structure of a NS and its tidal interactions in a binary system rely heavily on the underlying state function describing the relationship between pressure ($p$) and energy density ($\epsilon$), or equation of state, of nuclear matter.
-Given that all currently proposed EoSs utilize certain approximations\kc{cite reviews by Baym and Oertel}, one method to study a wide range of physically realizable EoSs is to parameterize them in a model-independent\kc{how is this model-independent?} way.
+Given that all currently proposed EoSs utilize certain approximations\kc{cite reviews by Baym and Oertel}, one method to study a wide range of physically realizable EoSs is to parameterize them in a model-independent way\kc{how is this model-independant?}.
 Spectral representations~\cite{Lindblom:2010bb,Lindblom:2012zi,Lindblom:2013kra,Lindblom:2018rfr,Abbott:2018exr} parameterize EoSs by performing spectral expansions on the adiabatic index $\Gamma(p)$\footnote{Another way of parameterizing EoSs is the piecewise polytropic formulation~\cite{Read2009,Lackey:2014fwa,Carney:2018sdv}.}:
@@
 Additional constraints imposed upon the generated EoSs were as follows~\cite{LIGO:posterior}: (i) causality within 10\%, and (ii) EoS priors must support NS masses up to $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations\kc{cite}.
-We utilize a random set of 100 of the above posterior samples defined by GW170817, furthermore referenced as the ``constrained EoSs", as shown in Fig.~\ref{fig:eos}.\zc{Carl, can you describe how you generated these?
-They aren't the \emph{actual} posteriors, are they?}\kc{Yeah they are}
+We utilize a random set of 100 of the above posterior samples defined by GW170817, furthermore referenced as the ``constrained EoSs", as shown in Fig.~\ref{fig:eos}.
 Following~\cite{Read2009}, the parameterized high-density core EoSs generated above are matched to the low-density crust EoS Sly~\cite{Douchin:2001sv} at about half of the nuclear saturation density, $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$.
@@
 This is important for two reasons: (i) allows us to algebraically eliminate tidal parameters from the template parameter list, improving parameter estimation, and (ii) automatic measurement of second tidal parameter given observation of the first.
-It was shown through a simple Fisher analysis that the use of binary Love universal relations improved parameter extraction on $\tilde{\Lambda}$ by an order of magnitude.
+It was shown through a simple Fisher analysis that the use of binary Love EoS-insensitive relations improved parameter extraction on $\tilde{\Lambda}$ by an order of magnitude.
 
-Similar universal relations have been found to exist between individual NS observables: moment of inertia (I), tidal deformability (Love), quadrupole moment (Q), and compactness (C), known as the ``I-Love-Q" and ``C-Love" universal relations~\cite{Yagi:ILQ, Yagi:binLove}.
+Similar EoS-insensitive relations have been found to exist between individual NS observables: moment of inertia (I), tidal deformability (Love), quadrupole moment (Q), and compactness (C), known as the ``I-Love-Q" and ``C-Love" EoS-insensitive relations~\cite{Yagi:ILQ, Yagi:binLove}.
 These have been found to be EoS insensitive by up to 1\% and 6.5\% respectively.
-In this paper, we show improvement in both of these universal relations by restricting to EoSs sampled from GW170817s posterior on pressure as a function of density.
+In this paper, we show improvement in both of these EoS-insensitive relations by restricting to EoSs sampled from GW170817s posterior on pressure as a function of density.
 %%%%%%%%%%%%%%%%%%%%%%%%% Begin universal relations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Universal relations}\label{sec:universal}
-In this section, we follow the analyses performed in~\cite{Yagi:binLove,Yagi:ILQ} with two new sets of 100 spectrally generated EoS: (i) posterior samples randomly selected from GW170817s 90\% posterior on on pressure as a function of density as shown in the left panel of Fig.~\ref{fig:eos}, and (ii) those unconstrained by any prior EoS information, as shown in the right panel of Fig.~\ref{fig:eos}.\kc{only one panel}
+\section{EoS-insensitive relations}\label{sec:universal}
+In this section, we follow the analyses performed in~\cite{Yagi:binLove,Yagi:ILQ} with two new sets of 100 spectrally generated EoS: (i) posterior samples randomly selected from GW170817s 90\% posterior on on pressure as a function of density as shown by the solid green curves in Fig.~\ref{fig:eos}, and (ii) those unconstrained by any prior EoS information, as shown by the dotted maroon curves in Fig.~\ref{fig:eos}.
 
@@
 In particular, we consider two distinct classes of NSs: nuclear matter EoSs and hybrid quark-hadron star EoSs as described in Sec.~\ref{sec:theory}.
-We begin in Sec.~\ref{sec:ilq-nuc} by fitting the new I-Love-Q universal relations using the constrained set of EoSs.
+We begin in Sec.~\ref{sec:ilq-nuc} by fitting the new I-Love-Q EoS-insensitive relations using the constrained set of EoSs.
 This is followed in Sec.~\ref{sec:ilq-hyb} by an analysis and discussion into how well hybrid stars agree with the improved binary Love relations.
@@
 \subsubsection{Nuclear matter stars}\label{sec:ilq-nuc}
-Following the work of Ref.~\cite{Yagi:ILQ}, the data for each universal relation is first fit to the following curve:
+Following the work of Ref.~\cite{Yagi:ILQ}, the data for each EoS-insensitive relation is first fit to the following curve:
 \begin{equation}\label{eq:ILQfit}
@@
 The new fitting coefficients are presented in Table~\ref{tab:ILQfitNew}.
-While the two above fits both result in fits with similar $R^2$\kc{define} values of $\sim 0.9999995$ for the data presented, the lattter one has the advantage that it properly limits to the Newtonian case as $\Lambda \rightarrow \infty$~\cite{Yagi:binLove}.
+While the two above fits both result in fits with similar $R^2$ (Coefficient of determination, defined as $R^2=\sum_i(f_i-\bar{y})^2/\sum_i(y_i-\bar{y})^2$, where $\bar{y}$ is the mean data value, and $f_i$, $y_i$ are the modeled and actual data values) values of $\sim 0.9999995$ for the data presented, the lattter one has the advantage that it properly limits to the Newtonian case as $\Lambda \rightarrow \infty$~\cite{Yagi:binLove}.
 
@@
 \caption{
-Updated fit parameters for the I-Love-Q universal relations, fitted to the constrained EoS data by the curve found in Eq.~\ref{eq:ILQfit}.
+Updated fit parameters for the I-Love-Q EoS-insensitive relations, fitted to the constrained EoS data by the curve found in Eq.~\ref{eq:ILQfit}.
 }\label{tab:ILQfit}
@@
  $\bar{Q}$ & $\Lambda$ & $0.2092931$ & $0.0740442$ & $-0.0538210$ & $-5.018022 \times 10^{-3}$ & $1.576165 \times 10^{-4}$ \\ 
-  $\bar{I}$ & $\bar{Q}$ & $1.3832702$ & $0.0.5931020$ & $-0.0216132$ & $0.0419044$ & $-2.9676365 \times 10^{-3}$ \\
+  $\bar{I}$ & $\bar{Q}$ & $1.3832702$ & $0.5931020$ & $-0.0216132$ & $0.0419044$ & $-2.9676365 \times 10^{-3}$ \\
  \hline
@@
 \caption{
-I-Love-Q and C-Love universal relations fit parameters for the constrained EoS data using the improved fitting relations found in Eq.~\ref{eq:ILQfitNew}.
+I-Love-Q and C-Love EoS-insensitive relations fit parameters for the constrained EoS data using the improved fitting relations found in Eq.~\ref{eq:ILQfitNew}.
 This fitting relation, unlike previous versions, properly limits to the Newtonian case as $\Lambda \rightarrow \infty$.
@@
 
-Fig.~\ref{fig:ILQ} shows the improved I-Love universal relations between the dimensionless moment of inertia $\bar{I} \equiv I/M^3$, the dimensionless quadrupole moment $\bar{Q} \equiv Q/M^3$, and the dimensionless tidal deformability $\Lambda$ for both the constrained and unconstrained sets of EoSs (each with individual fits pertaining to only that set of EoSs).
+Fig.~\ref{fig:ILQ} shows the improved I-Love EoS-insensitive relations between the dimensionless moment of inertia $\bar{I} \equiv I/M^3$, the dimensionless quadrupole moment $\bar{Q} \equiv Q/M^3$, and the dimensionless tidal deformability $\Lambda$ for both the constrained and unconstrained sets of EoSs (each with individual fits pertaining to only that set of EoSs).
 We observe that the constrained EoSs show considerable improvement from both the results of previous works~\cite{Yagi:ILQ}, and from the unconstrained EoSs.
 This is further validated in Tab.~\ref{tab:maxVar}, where the maximal EoS variation from each fit is tabulated; comparing the results of previous works to the unconstrained, and constrained sets of EoSs.
-Observe how the constrained EoSs outperform both other cases by a considerable amount for each I-Love-Q universal relation.
+Observe how the constrained EoSs outperform both other cases by a considerable amount for each I-Love-Q EoS-insensitive relation.
 
@@
 \caption{
-Individual I-Love universal relations $\bar{I}-\Lambda$ (left), $\bar{Q}-\Lambda$ (center), and $\bar{I}-\bar{Q}$ (right), shown for both the constrained EoSs (solid green) and unconstrained EoSs (dotted maroon).
+Individual I-Love EoS-insensitive relations $\bar{I}-\Lambda$ (left), $\bar{Q}-\Lambda$ (center), and $\bar{I}-\bar{Q}$ (right), shown for both the constrained EoSs (solid green) and unconstrained EoSs (dotted maroon).
 In these figures, the black dashed lines corresponds to the fits given by Eq.~\ref{eq:ILQfitNew} (note: each panel contains individual fits for the constrained and unconstrained EoSs, indistinguishable on such a large scale).
@@
 \caption{
-Comparison between the universal relations (I-Love-Q, C-Love, and binary Love) maximal EoS variability for the results of previous works~\cite{Yagi:ILQ,Yagi:binLove}, and the unconstrained and constrained sets of EoSs analyzed here.
+Comparison between the EoS-insensitive relations (I-Love-Q, C-Love, and binary Love) maximal EoS variability for the results of previous works~\cite{Yagi:ILQ,Yagi:binLove}, and the unconstrained and constrained sets of EoSs analyzed here.
 The maximum EoS variation, given by the largest fractional difference from the fits as shown in Figs.~\ref{fig:ILQ} and~\ref{fig:binLove}, sees a considerable improvement for the constrained set of EoSs, compared to the unconstrained set as well as previous works.
@@
  \hline
- \textbf{Universal} & \multicolumn{3}{c}{\textbf{Maximal EoS Variability}} \\
+ \textbf{EoS-insensitive} & \multicolumn{3}{c}{\textbf{Maximal EoS Variability}} \\
  \cline{2-4}
@@
 
-These results indicate that universal relations can indeed be greatly improved upon by constraining to only EoSs which agree with physical observations.
+These results indicate that EoS-insensitive relations can indeed be greatly improved upon by constraining to only EoSs which agree with physical observations.
 In addition, we confirm the validity of this method by noting that the unconstrained EoSs observe more EoS variability than that found in Ref~\cite{Yagi:ILQ} due to the nature of large random sampling taking into account more sources of uncertainty than previously studied.
@@
 
-Observe how the hybrid star EoSs do obey the I-Love-Q universal relations up to $\sim1.7$\%, slightly higher than that found here for nuclear matter EoSs, as well as that found in previous works~\cite{Yagi:ILQ}.
+Observe how the hybrid star EoSs do obey the I-Love-Q EoS-insensitive relations up to $\sim1.7$\%, slightly higher than that found here for nuclear matter EoSs, as well as that found in previous works~\cite{Yagi:ILQ}.
 Further, we observe that the universality can not be improved by much through the introduction of new fits, only bringing the max EoS variation down to $\sim1$\% for the fits constructed with only hybrid star EoSs.
-Concluding, we claim that hybrid star EoSs \emph{do} obey the I-Love-Q universal relations computed through nuclear EoS data, with the exception that the universality goes up to $\sim1.7$\%.
+Concluding, we claim that hybrid star EoSs \emph{do} obey the I-Love-Q EoS-insensitive relations computed through nuclear EoS data, with the exception that the universality goes up to $\sim1.7$\%.
 
 \subsection{C-Love Relations}\label{sec:clove}
-In this section we consider approximate C-Love universal relations between NS compactness $\bar{C} \equiv M/R$ and unitless tidal deformability $\Lambda$, as discussed by Yagi and Yunes~\cite{Yagi:binLove}.
+In this section we consider approximate C-Love EoS-insensitive relations between NS compactness $\bar{C} \equiv M/R$ and unitless tidal deformability $\Lambda$, as discussed by Yagi and Yunes~\cite{Yagi:binLove}.
 Similar to the previous section, we consider two classes of stars: nuclear matter EoSs and hybrid quark-hadron star EoSs.
@@
 
-Figure~\ref{fig:clove} presents the C-Love universal relations for both the constrained and unconstrained sets of EoSs, along with the relative fractional difference from the fits. 
+Figure~\ref{fig:clove} presents the C-Love EoS-insensitive relations for both the constrained and unconstrained sets of EoSs, along with the relative fractional difference from the fits. 
 Observe how the constrained EoSs show a large suppression in EoS variability compared to both the unconstrained EoSs, as well as that found in previous works~\cite{Yagi:binLove}.
@@
 \caption{
-Similar to Fig.~\ref{fig:ILQ} but for C-Love universal relations.
+Similar to Fig.~\ref{fig:ILQ} but for C-Love EoS-insensitive relations.
 In this figure, we similarly construct fits to  Eq.~\ref{eq:ILQfitNew}, properly limiting to the newtonian case $\bar{C} \sim \Lambda^{-1/5}$.
@@
 \subsubsection{Hybrid quark-hadron stars}\label{sec:clove-hyb}
-In this section, we consider the effect of hybrid star EoSs on the C-Love universal relation.
+In this section, we consider the effect of hybrid star EoSs on the C-Love EoS-insensitive relation.
 Much like Sec.~\ref{sec:ilq-hyb}, we perform 3 separate fits (constrained and hybrid EoSs combined, constrained EoSs only, and hybrid EoSs only) and compare the maximal EoS variation for each class of EoSs.
@@
 We observe very similar behavior to that described in Sec.~\ref{sec:ilq-hyb}, in which the maximal EoS variation for hybrid stars only fluctuate slightly ($\sim 4.5\% - 7\%$) for each case.
-From this, we similarly conclude that hybrid stars do obey the C-Love universal relation derived with nuclear matter stars, with the caveat that the maximum universality increases to $\sim 7.1\%$.
+From this, we similarly conclude that hybrid stars do obey the C-Love EoS-insensitive relation derived with nuclear matter stars, with the caveat that the maximum universality increases to $\sim 7.1\%$.
 This is exemplified in Fig.~\ref{fig:clove} by the dashed green curves.
@@
 \caption{
-Similar to Tab.~\ref{tab:hybridCompare} but for the C-Love universal relation.
+Similar to Tab.~\ref{tab:hybridCompare} but for the C-Love EoS-insensitive relation.
 Observe how for all 3 cases, the hybrid EoSs are only universal up to a minimum of $\sim1$\%, while in each case the constrained EoSs outperform the hybrid ones.
@@
  \cline{1-1}
- \emph{Constrained only} & \multirow{2}{*}{$0.0.0216879$} & \multirow{2}{*}{$0.0.0719104$}\\
+ \emph{Constrained only} & \multirow{2}{*}{$0.0216879$} & \multirow{2}{*}{$0.0719104$}\\
   \emph{(Case 2)} & &\\
   \cline{1-1}
- \emph{Hybrid only} & \multirow{2}{*}{$0.0.0578764$} & \multirow{2}{*}{$0.0.0447799$}\\
+ \emph{Hybrid only} & \multirow{2}{*}{$0.0578764$} & \multirow{2}{*}{$0.0447799$}\\
   \emph{(Case 3)} & &\\
@@
 \subsection{Binary love relations}\label{sec:binary}
-Next we consider improvements to the binary Love universal relations.
+Next we consider improvements to the binary Love EoS-insensitive relations.
 Similar to Sec.~\ref{sec:ilq}, we consider two classes of NSs: nuclear matter EoSs and hybrid quark-hadron star EoSs~\cite{Paschalidis2018,Alford:2017qgh,1971SvA....15..347S,Zdunik:2012dj,Alford:2013aca}.
@@
 The updated fit parameters can be found in Table~\ref{tab:binLovefit}.
-Notice how, unlike the individual NS I-Love-Q universal relations, these relations also depend on the ratio of constituent masses in the binary system.
+Notice how, unlike the individual NS I-Love-Q EoS-insensitive relations, these relations also depend on the ratio of constituent masses in the binary system.
 \begin{table*}
@@
 \caption{
-Updated fit parameters for the binary Love universal relations, as given by the curve found in Eq.~\ref{eq:binLovefit}.
+Updated fit parameters for the binary Love EoS-insensitive relations, as given by the curve found in Eq.~\ref{eq:binLovefit}.
 The bottom row corresponds to separate fits corresponding to the hybrid star branch of the hybrid EoSs.
@@
 
-Fig.~\ref{fig:binLove} shows the improved binary Love universal relation for 3 different mass ratios: $q=0.9$, $q=0.75$, and $q=0.5$ for both constrained and unconstrained sets of EoSs.
+Fig.~\ref{fig:binLove} shows the improved binary Love EoS-insensitive relation for 3 different mass ratios: $q=0.9$, $q=0.75$, and $q=0.5$ for both constrained and unconstrained sets of EoSs.
 Observe how once again, the constrained set of EoSs show a considerable improvement upon both the unconstrained set of EoSs, as well as the results found in previous works~\cite{Yagi:binLove}.
@@
 \caption{
-Binary Love universal relations shown for the constrained EoSs (dotted maroon) and unconstrained EoSs (solid green) for various values of mass ratio: $q=0.9$, $q=0.75$, and $q=0.50$.
-In this figure, the top panel displays the universal relations with fits given by Eq.~\ref{eq:binLovefit} shown by dashed black lines (note there are 2 fits for each mass ratio, corresponding to the constrained and unconstrained sets of EoSs), while the bottom 3 panels correspond to the EoS variation for each mass ratio.
+Binary Love EoS-insensitive relations shown for the constrained EoSs (dotted maroon) and unconstrained EoSs (solid green) for various values of mass ratio: $q=0.9$, $q=0.75$, and $q=0.50$.
+In this figure, the top panel displays the EoS-insensitive relations with fits given by Eq.~\ref{eq:binLovefit} shown by dashed black lines (note there are 2 fits for each mass ratio, corresponding to the constrained and unconstrained sets of EoSs), while the bottom 3 panels correspond to the EoS variation for each mass ratio.
 Observe how the the constrained set of EoSs show a reduction in EoS variation for both the unconstrained set, and from the results shown in Ref.~\cite{Yagi:binLove}.
@@
 
-To determine how each of class of binary NSs obey our improved binary Love universal relations, we pick a representative set of 10 binary pairs from each class, for the ACB5 hybrid EoS, with a transition at $1.4 \text{ M}_{\odot}$.
+To determine how each of class of binary NSs obey our improved binary Love EoS-insensitive relations, we pick a representative set of 10 binary pairs from each class, for the ACB5 hybrid EoS, with a transition at $1.4 \text{ M}_{\odot}$.
 Binary Love values are then computed for each pair, then residuals from the binary Love curve found in Sec.~\ref{sec:binLove-nuclear} are determined and compared to that from the constrained set of EoSs.
@@
 \subsubsection{Error Marginalization}
-We have now shown that binary NS merger observations can help improve universal relations - the question is: is it worth it?
+We have now shown that binary NS merger observations can help improve EoS-insensitive relations - the question is: is it worth it?
 Current interferometer sensitivities are not yet small enough to accurately constrain $\tilde{\Lambda}$.
 For example, GW170817 was detected by LIGO observing run 2 (``O2")\zc{cite} and was able to constrain $\tilde{\Lambda}$ to a $90\%$ confidence interval of 325 (this relates to a standard deviation of $\sigma_{\tilde{\Lambda}}=198$) centered at $\tilde{\Lambda}=395$.
-This corresponds to statistical uncertainties on the order of $\sim 82\%$, which vastly dominates the error budget compared to the small systematic errors picked up by EoS variation in the universal relations, which can be seen in Fig.~\ref{fig:residuals}.
-This implies that currently, improved universal relations will only make a negligible difference in tidal parameter extraction.
+This corresponds to statistical uncertainties on the order of $\sim 82\%$, which vastly dominates the error budget compared to the small systematic errors picked up by EoS variation in the EoS-insensitive relations, which can be seen in Fig.~\ref{fig:residuals}.
+This implies that currently, improved EoS-insensitive relations will only make a negligible difference in tidal parameter extraction.
 
-In this section, we investigate the residuals in $\tilde{\Lambda}(\Lambda_a,\Lambda_s,q)$ in order to marginalize over the intrinsic error in the binary Love universal relations.
+In this section, we investigate the residuals in $\tilde{\Lambda}(\Lambda_a,\Lambda_s,q)$ in order to marginalize over the intrinsic error in the binary Love EoS-insensitive relations.
 In particular, we restrict our focus to only the constrained set of EoSs.
-Residuals in $\tilde\Lambda$ are computed as $\tilde{\Lambda}^{\text{fit}}-\tilde{\Lambda}^{\text{true}}$, where $\tilde{\Lambda}^{\text{true}}=\tilde{\Lambda}(\Lambda_a,\Lambda_s,q)$ corresponds to the true value predicted by the sample EoSs, and $\tilde{\Lambda}^{\text{fit}}=\tilde{\Lambda}(\Lambda_a^{\text{fit}}(\Lambda_s,q),\Lambda_s,q)$ corresponds to the value obtained through the universal relations found in Sec.~\ref{sec:binLove-nuclear}.
+Residuals in $\tilde\Lambda$ are computed as $\tilde{\Lambda}^{\text{fit}}-\tilde{\Lambda}^{\text{true}}$, where $\tilde{\Lambda}^{\text{true}}=\tilde{\Lambda}(\Lambda_a,\Lambda_s,q)$ corresponds to the true value predicted by the sample EoSs, and $\tilde{\Lambda}^{\text{fit}}=\tilde{\Lambda}(\Lambda_a^{\text{fit}}(\Lambda_s,q),\Lambda_s,q)$ corresponds to the value obtained through the EoS-insensitive relations found in Sec.~\ref{sec:binLove-nuclear}.
 Following Ref.~\cite{Katerina:residuals}, we assume the residuals in $\tilde{\Lambda}$ observe a Gaussian distribution with mean and standard deviation given by:
@@
 \caption{
-Coefficients to the fits given by Eqs.(~\ref{eq:margFit1})-(\ref{eq:margFit4}) for the relative error on $\tilde{\Lambda}$ in the improved binary Love universal relations presented in this paper.
+Coefficients to the fits given by Eqs.(~\ref{eq:margFit1})-(\ref{eq:margFit4}) for the relative error on $\tilde{\Lambda}$ in the improved binary Love EoS-insensitive relations presented in this paper.
 }\label{tab:marginalized}
@@
 Because the un-binned residuals seen in Fig.~\ref{fig:residuals} are dominated by the low-error regions of parameter space ($\Lambda_s \rightarrow 0$ and $q \rightarrow 1$) shown by the fits of Tab.~\ref{tab:marginalized}, we consider the 90th for the remainder of the analysis.
-We take this value of $P_{90}=12.014$ to be the systematic measurement error introduced by using the improved binary Love universal relations on the parameter extraction of $\tilde\Lambda$.
+We take this value of $P_{90}=12.014$ to be the systematic measurement error introduced by using the improved binary Love EoS-insensitive relations on the parameter extraction of $\tilde\Lambda$.
 Currently, the statistical error of $198$ on $\tilde\Lambda$ from GW170817 dominate the error budget compared to the systematic error of $12.014$.
-This means that, for the current ``O2" detector sensitivity, the use of improved binary Love universal relations will only make a negligible difference on the extraction of $\tilde\Lambda$.
-However, future detectors (for example aLIGO, a\texttt{++}, Voyager, CE, and ET) are planned with large reductions in sensitivity - both decreasing the statistical errors and allowing for a larger binary NS merger detection rate; further reducing uncertainties.
-In Sec.~\ref{sec:observations}, we analyze this further and discuss when the systematic errors from universal relations become comparable to the statistical errors.
+This means that, for the current ``O2" detector sensitivity, the use of improved binary Love EoS-insensitive relations will only make a negligible difference on the extraction of $\tilde\Lambda$.
+However, future detectors (for example aLIGO, A\texttt{+}, Voyager, CE, and ET) are planned with large reductions in sensitivity - both decreasing the statistical errors and allowing for a larger binary NS merger detection rate; further reducing uncertainties.
+In Sec.~\ref{sec:observations}, we analyze this further and discuss when the systematic errors from EoS-insensitive relations become comparable to the statistical errors.
 
@@
 These residuals obey Gaussian distributions centered at $\mu=-1.8133 \times 10^{-4}$ and $\mu=4.2258 \times 10^{-3}$ with standard deviations of $\sigma=7.6664$ and $\sigma=40.8866$ for the constrained and unconstrained sets of EoSs, respectively.
-These uncertainties correspond roughly to the systematic errors introduced on the parameter extraction of $\tilde{\Lambda}$ upon the use of binary Love universal relations.
+These uncertainties correspond roughly to the systematic errors introduced on the parameter extraction of $\tilde{\Lambda}$ upon the use of binary Love EoS-insensitive relations.
 However, to take into account the systematic errors found in high-error regions of the parameter space, we instead set the systematic error to be the 90th percentile, $P_{90}=12.014$.
-Observe that the systematic errors from using the improved (constrained) binary Love universal relations are negligible compared to the statistical errors accrued on parameter extraction from GW170817, found to be $\sigma_{\tilde{\Lambda}}=198$.
+Observe that the systematic errors from using the improved (constrained) binary Love EoS-insensitive relations are negligible compared to the statistical errors accrued on parameter extraction from GW170817, found to be $\sigma_{\tilde{\Lambda}}=198$.
 }
@@
 \section{Impact on future observations}\label{sec:observations}
-In this section, we estimate the feasibility of utilizing improved universal relations in future binary NS merger events.
+In this section, we estimate the feasibility of utilizing improved EoS-insensitive relations in future binary NS merger events.
 This estimate is acquired through a simple Fisher analysis~\cite{Finn:Fisher,Cutler:Fisher} which approximates the accuracy with which one can extract best-fit parameters $\theta^a$, given a prior template waveform.
@@
 \caption{
-Square root of of the spectral noise densities $\sqrt{S_n^A(f)}$ plotted for detectors ($A$): LIGO O2 (orange), aLIGO (green), a\texttt{++} (purple), Voyager (magenta), CE (red), and ET-D (blue) as interpolated from publicly available data\zc{cite}.
+Square root of of the spectral noise densities $\sqrt{S_n^A(f)}$ plotted for detectors ($A$): LIGO O2 (orange), aLIGO (green), A\texttt{+} (purple), Voyager (magenta), CE (red), and ET-D (blue) as interpolated from publicly available data\zc{cite}.
 Spectral noise densities are plotted from $f_{\text{min}}=(23,10,10,7,1,1) \text{ Hz}$, respectively, to $f_{\text{max}}=1649 \text{ Hz}$.
@@
 
-Next, we consider events identical to GW170817 detected on future design sensitivity upgrades and detectors $A \equiv ($O2, aLIGO, a\texttt{++}, Voyager, CE, ET-D$)$\zc{cite}, shown in Fig.~\ref{fig:sensitivities}, to determine if and when the statistical errors associated with parameter extraction of $\tilde{\Lambda}$ drop below the systematic EoS variation errors from using binary Love universal relations.
+Next, we consider events identical to GW170817 detected on future design sensitivity upgrades and detectors $A \equiv ($O2, aLIGO, A\texttt{+}, Voyager, CE, ET-D$)$\zc{cite}, shown in Fig.~\ref{fig:sensitivities}, to determine if and when the statistical errors associated with parameter extraction of $\tilde{\Lambda}$ drop below the systematic EoS variation errors from using binary Love EoS-insensitive relations.
 The process we use for each detector sensitivity $S_n^A(f)$ is as follows:
@@
 Tabulated results for the estimated statistical errors on $\tilde{\Lambda}$ for the combined results of $N_A$ detections corresponding to the estimated upper, central, and lower limits of the binary NS merger detection rate $R$.
-This is repeated for 5 future detector sensitivities: aLIGO, a\texttt{++}, Voyager, CE, and ET.
+This is repeated for 5 future detector sensitivities: aLIGO, A\texttt{+}, Voyager, CE, and ET.
 Below, $\rho^A_{\text{GW170817}}$ and $\sigma^A_{\text{GW170817}}$ correspond to the approximate SNR and $\sigma_{\tilde{\Lambda}}$ of GW170817 had it been observed by the future interferometer, and $\sigma^A_N$ corresponds to the final uncertainty on $\tilde{\Lambda}$ after $N_A$ detections on interferometer $A$.
-It can be seen here that the statistical errors on $\tilde{\Lambda}$ become comparable with the systematics (set to be $P_{90}=12.014$) from using improved binary Love relations from Voyager and on, indicating when it may be safe to utilize new universal relations.
+It can be seen here that the statistical errors on $\tilde{\Lambda}$ become comparable with the systematics (set to be $P_{90}=12.014$) from using improved binary Love relations from Voyager and on, indicating when it may be safe to utilize new EoS-insensitive relations.
 Note the approximation for $\sigma^A_N$ under the O2 detector sensitivity is left blank due to the singularity of the detected event.
@@
 %aLIGO & $23$ & $112$ & $344$ & $90.74$ & $75.44$ & $117.022$ & $42.89$ & $24.27$\\
-%a\texttt{++} & $208$ & $1004$ & $3091$              & $180.95$ & $31.55$ &               $27.62$ & $13.36$ & $7.36$\\
+%A\texttt{+} & $208$ & $1004$ & $3091$              & $180.95$ & $31.55$ &               $27.62$ & $13.36$ & $7.36$\\
 %Voyager & $3854$ & $1.85 \times 10^4$ & $5.71 \times 10^4$ &              $428.89$ & $16.69$              & $8.57$ & $3.78$ & $2.16$\\
@@
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
- a\texttt{++}  & \multicolumn{1}{|c|}{$180.95$}  & $31.55$ &  \multicolumn{1}{|c|}{$208$} & $1004$ & $3091$ & \multicolumn{1}{|c|}{$27.62$} & $13.36$ & $7.36$\\
+ A\texttt{+}  & \multicolumn{1}{|c|}{$180.95$}  & $31.55$ &  \multicolumn{1}{|c|}{$208$} & $1004$ & $3091$ & \multicolumn{1}{|c|}{$27.62$} & $13.36$ & $7.36$\\
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
@@
 
-Concluding, we find that the Voyager, ET, and CE detectors all exhibit enough uncertainty reduction that the systematics on $\tilde\Lambda$ introduced from using improved universal relations (found to be $12.014$) no longer become negligible in the error budget.
-This implies that the use and further improvement of universal relations is justified for future binary NS merger detections.
+Concluding, we find that the Voyager, ET, and CE detectors all exhibit enough uncertainty reduction that the systematics on $\tilde\Lambda$ introduced from using improved EoS-insensitive relations (found to be $12.014$) no longer become negligible in the error budget.
+This implies that the use and further improvement of EoS-insensitive relations is justified for future binary NS merger detections.
 Further, we investigate the dependence of the measurement accuracy of $\tilde\Lambda$ on the binary NS mass ratio $q$ for fixed chirp mass $\mathcal{M}=1.88\text{ M}_{\odot}$ in Appendix~\ref{app:measurement}.
@@
 We take advantage of this by generating a restricted set of spectral EoSs which agree with this observation to reduce uncertainties upon the extraction of tidal parameters from future GW events.
-Important previous work by Yagi and Yunes~\cite{Yagi:ILQ,Yagi:binLove} found EoS-insensitive universal relations between symmetric and antisymmetric combinations of NS tidal deformabilities, which aid in the extraction of said tidal parameters.
-We find an improvement upon these universal relations by a factor of $\sim 59$\% for stars with mass ratios of $0.75$ by restricting to the EoS posterior samples from GW170817s 90\% credible region on pressure as a function of density.
+Important previous work by Yagi and Yunes~\cite{Yagi:ILQ,Yagi:binLove} found EoS-insensitive relations between symmetric and antisymmetric combinations of NS tidal deformabilities, which aid in the extraction of said tidal parameters.
+We find an improvement upon these EoS-insensitive relations by a factor of $\sim 59$\% for stars with mass ratios of $0.75$ by restricting to the EoS posterior samples from GW170817s 90\% credible region on pressure as a function of density.
 Similarly, we find an increase in C-Love and I-Love-Q universality by a factors of $\sim 76$\% and $\sim 50$\%, respectively.
 Additionally, we find that hybrid quark-hadron star EoSs \emph{do} obey the I-Love-Q and C-Love universality, albeit with a slightly higher maximum EoS variability as displayed in Tabs.~\ref{tab:hybridCompare} and ~\ref{tab:hybridCompareClove}.
-In addition, we find that binaries consisting of one massive hybrid quark-hadron star, and one small-mass hadron star do not obey the binary Love universal relations -- explained by the large difference in $\tilde{\Lambda}$ displayed between the constituent stars.
+In addition, we find that binaries consisting of one massive hybrid quark-hadron star, and one small-mass hadron star do not obey the binary Love EoS-insensitive relations -- explained by the large difference in $\tilde{\Lambda}$ displayed between the constituent stars.
 To improve on this, we construct new ``hybrid matter binary Love relations", applied to only the hybrid branches of the transitional EoSs.
 This results in EoS variability similar to that found for the nuclear matter fits.
-Further, we analyze the impact of this improvement for future binary NS merger detections, as the current detector sensitivity is not yet small enough to accurately constrain $\tilde{\Lambda}$ enough for universal relations to make a difference.
-We find that future interferometers Voyager, CE, and ET-D all experience statistical uncertainties upon the extraction of $\tilde{\Lambda}$ small enough to become comparable to the systematic errors injected through the use of improved universal relations (found to be $12.014$), as depicted in Fig.~\ref{fig:stackedFisher} and Table~\ref{tab:variances}.
+Further, we analyze the impact of this improvement for future binary NS merger detections, as the current detector sensitivity is not yet small enough to accurately constrain $\tilde{\Lambda}$ enough for EoS-insensitive relations to make a difference.
+We find that future interferometers Voyager, CE, and ET-D all experience statistical uncertainties upon the extraction of $\tilde{\Lambda}$ small enough to become comparable to the systematic errors injected through the use of improved EoS-insensitive relations (found to be $12.014$), as depicted in Fig.~\ref{fig:stackedFisher} and Table~\ref{tab:variances}.
 Finally, in Appendix~\ref{app:measurement} we investigate the effect of NS binary mass ratio q on the measurement accuracy of $\tilde\Lambda$.
 We find that second generation interferometers lose accuracy as one increases the mass ratio, while third generation detectors observe a large increase of accuracy due to the correlations between $\tilde\Lambda$ and $\delta\tilde\Lambda$.
-This indicates that the use and further improvement of universal relations is justified for future GW observations of binary NS merger events.
+This indicates that the use and further improvement of EoS-insensitive relations is justified for future GW observations of binary NS merger events.
 
@@
 The left panel of Fig.~\ref{fig:massVariation} displays an approximation of the $\tilde\Lambda$ measurement accuracy as a function of increasing mass ratio $q$ (for a fixed chirp mass of $\mathcal{M}=1.188 \text{ M}_{\odot}$ corresponding to GW170817), using the Fisher analysis techniques described in Sec.~\ref{sec:observations}.
-We observe two points of interest about these trends: (i) the second generation detectors (O2, aLIGO, a\texttt{++}, and Voyager) typically become less accurate as the mass ratio approaches unity, (ii) the third generation detectors (CE and ET) observe the opposite behavior-- a fast growth in accuracy as the mass ratio increases.
+We observe two points of interest about these trends: (i) the second generation detectors (O2, aLIGO, A\texttt{+}, and Voyager) typically become less accurate as the mass ratio approaches unity, (ii) the third generation detectors (CE and ET) observe the opposite behavior-- a fast growth in accuracy as the mass ratio increases.
 For the remainder of this appendix, we attempt to explain the opposing behaviors of the second and third generation interferometers on the extraction of $\tilde\Lambda$.
@@
 \caption{
-Measurement accuracy of $\tilde\Lambda$ as a function of increasing mass ratio $q$ for interferometer sensitivities O2, aLIGO, a\texttt{++}, Voyager, CE, and ET.
+Measurement accuracy of $\tilde\Lambda$ as a function of increasing mass ratio $q$ for interferometer sensitivities O2, aLIGO, A\texttt{+}, Voyager, CE, and ET.
 Evaluated at a fixed chirp mass of $\mathcal{M}=1.188\text{ M}_{\odot}$ corresponding to GW170817, this is repeated for three cases: (i) (left) with correlations between all template waveform parameters $\theta^a$ intact; (ii) (center) with the correlations between $\tilde\Lambda$ and $\delta\tilde\Lambda$ removed; and (iii) (right) with correlations between all parameters removed.
@@
 Measurement accuracy of $\tilde\Lambda$ upon the consideration of correlations between \emph{only} $\tilde\Lambda$ and other individual template parameters $\theta^a$ shown in Eq.~\ref{eq:template}.
-This process, repeated for 6 interferometer design sensitivities O2, aLIGO, a\texttt{++}, Voyager, CE, and ET, is approximated by setting all off-diagonal Fisher matrix elements to 0 except for the $(i,j)$ components such that both $i$ and $j$ correspond to the $\tilde\Lambda$ and $\theta^a$ parameters.
+This process, repeated for 6 interferometer design sensitivities O2, aLIGO, A\texttt{+}, Voyager, CE, and ET, is approximated by setting all off-diagonal Fisher matrix elements to 0 except for the $(i,j)$ components such that both $i$ and $j$ correspond to the $\tilde\Lambda$ and $\theta^a$ parameters.
 Observe how correlations with 4PN parameter $t_c$ (coalescence time) remain to be highly correlated with $\tilde\Lambda$ among all 6 interferometers.

### 2019-01-14 paper/bin-love-after-gw170817.tex
Updated paper draft with lambda_0 extraction efficiencies, R-Love URs, waveform mismodeling with 6PN vs NRTidal, new method on stacking uncertainties/ estimating number events, and more.

@@
 For example, utilizing the parameters $\tilde{\Lambda}$ and $\delta \tilde{\Lambda}$~\cite{Favata:2013rwa,Wade:tidalCorrections} which enter the GW waveform at different post-Newtonian (PN) orders (powers of the ratio between the orbital speed and the speed of light $v/c^{2n}$) partially mitigates these correlations.
+Similarly, the waveform may be parameterized by mass-independant tidal parameters $\lambda_0$ and $\lambda_1$, derived through a Taylor expansion about $m_0=1.4 \text{ M}_{\odot}$ of individual, unitful tidal deformability $\lambda \approx \lambda_0+\lambda+1(m_1-1.4 \text{ M}_{\odot})/\text{M}_{\odot}$~\cite{delPozzo:TaylorTidal}.
+Use of this set of tidal parameters allows one to effectively combine multiple events with varying mass and $\tilde\Lambda$ components, not possible in the former parameterization of $\tilde{\Lambda}$ and $\delta \tilde{\Lambda}$
 
 %Universal relations
-Unfortunately, current detectors are only sensitive enough to accurately measure the dominant tidal parameter, $\tilde{\Lambda}$.
+Unfortunately, current detectors are only sensitive enough to accurately measure the dominant tidal parameter, $\lambda_0$.
 Previous work by Yagi and Yunes~\cite{Yagi:binLove} resolved this issue by finding approximately EoS-insensitive ``binary Love universal relations" between symmetric and anti-symmetric combinations of tidal deformabilities $\Lambda_{s,a}=\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$.
@@
 By restricting to only EoSs which lie within the the 90\% credible region on pressure as a function of density found in~\cite{LIGO:posterior}, we repeat the analyses done in~\cite{Yagi:binLove,Yagi:ILQ} and show an increase in universality for I-Love-Q, C-Love, and binary Love EoS-insensitive relations.
+We also investigate the relationship between the NS radius and its tidal deformability, or the R-Love relations, determining if the uncertainties can be reduced.
 In addition, we consider hybrid star EoSs seen in~\cite{Paschalidis2018}, which experience strong first-order transitions from hadronic matter to quark matter.
@@
 Further, we estimate the viability of using improved EoS-insensitive relations on future GW detections by performing simple Fisher analyses to approximate when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in EoS-insensitive relations.
+To estimate the effect of waveform mismodeling, we additionally consider two different tidal corrections to the injected PhenomD~\cite{PhenomDI,PhenomDII} waveform: 6PN~\cite{Wade:tidalCorrections} and NRTidal~\cite{Samajdar:NRTidal}
 
@@
 Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with mass ratios of $0.75$, in C-Love universality by a factor of $\sim 67\%$, and in I-Love-Q universality by factors of $\sim50$\%, tabulated in Tab.~\ref{tab:maxVar}.
+We also present new R-Love relations displaying the relationship between NS radius and tidal deformability, showing maximum EoS variability of $18.88\%$ from the fit discussed in Sec.~\ref{sec:clove}.
 Additionally, we find that hybrid quark-hadron stars do obey the I-Love-Q and C-Love EoS-insensitive relations, with sightly increased EoS variability.
@@
 Due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the EoS-insensitive relations are far outweighed by the statistical errors accrued by extraction of high-order PN tidal parameters from GW waveforms.
-Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from parameter extraction for GW170817 as if it had been observed by future detectors $A \equiv ($ O2, aLIGO, A\texttt{+}, Voyager, ET, CE$)$\zc{cite these individually}.
+Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from parameter extraction for GW170817 as if it had been observed by future detectors $A \equiv ($ O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, ET~\cite{ET}, CE~\cite{Ap_Voyager_CE}$)$.
 Here, $\sigma^A_{\text{GW170817}}$ and $\rho^A_{\text{GW170817}}$ correspond to the statistical error and signal-to-noise-ratio found from observing GW170817 on detector $A$, and $\sigma^A_N$ represents the combined uncertainty after the detection of $N_A$ events (corresponding to the binary NS merger rate associated interferometer $A$).
@@
 It can be seen from this figure that the statistical errors from parameter extraction become comparable the EoS-insensitive relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love EoS-insensitive relations will become necessary.
+Also shown in the figure is the same measurement uncertainties upon the injection of the PhenomD + NRTidal waveform, rather than the PhenomD + 6PN tidal correction to demonstrate the effect of waveform mismodeling.
 \begin{figure}
@@
 \caption{
-Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue circle) in the extraction of $\tilde{\Lambda}$ from GW170817 (O2) as if observed with future interferometers aLIGO, A\texttt{+}, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
+Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue circle) in the extraction of $\lambda_0$ from GW170817 (O2) as if observed with future interferometers aLIGO, A\texttt{+}, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
 This is compared to the combined uncertainty $\sigma^A_N$ (turqoise shaded region) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper and lower limits of expected binary NS merger detection rates for O2, aLIGO, A\texttt{+}, Voyager, CE, and ET-D over 1 observation year.
@@
 These results are further tabulated in Table~\ref{tab:variances}.
+Additionally shown in the figure are the estimated statistical uncertainties on the extraction of $\lambda_0$ upon the injection of the PhenomD + NRTidal correction waveform (IMRD + NRTidal), rather than the PhenomD + 6PN tidal correction (IMRD + 6PN), in order to demonstrate the waveform mismodeling uncertainties.
+The single-detection uncertainties are shown in unfilled blue circles, while the combined detection uncertaintied are outlined in dashed maroon.
 }
@@
 \caption{
-I-Love-Q and C-Love EoS-insensitive relations fit parameters for the constrained EoS data using the improved fitting relations found in Eq.~\ref{eq:ILQfitNew}.
+I-Love-Q, C-Love, and R-Love EoS-insensitive relations fit parameters for the constrained EoS data using the improved fitting relations found in Eq.~\ref{eq:ILQfitNew}.
 This fitting relation, unlike previous versions, properly limits to the Newtonian case as $\Lambda \rightarrow \infty$.
@@
  $\bar{C}$ & $\Lambda$ & $-1/5$ & $0.2495709$ & $-919.5651942$ & $330.2848184$ & $-857.1842107$ & $-383.5404843$ & $192.4933832$ & $-811.1425435$\\
+ $R$ & $\Lambda$ & $0.6731380$\footnote{Here $\alpha=(n-1)/10$, with $n=7.7313801$ being the fitting coefficient.} & $0.0754339$ & $-12.7153380$ & $58.8217867$ & $-50.3212157$ & $-2.6960056$ & $2.7769172$ & $-1.1317519$\\
 \hline
@@
 \caption{
-Comparison between the EoS-insensitive relations (I-Love-Q, C-Love, and binary Love) maximal EoS variability for the results of previous works~\cite{Yagi:ILQ,Yagi:binLove}, and the unconstrained and constrained sets of EoSs analyzed here.
-The maximum EoS variation, given by the largest fractional difference from the fits as shown in Figs.~\ref{fig:ILQ} and~\ref{fig:binLove}, sees a considerable improvement for the constrained set of EoSs, compared to the unconstrained set as well as previous works.
+Comparison between the EoS-insensitive relations (I-Love-Q, C-Love, R-Love, and binary Love) maximal EoS variability for the results of previous works~\cite{Yagi:ILQ,Yagi:binLove}, and the unconstrained and constrained sets of EoSs analyzed here.
+The maximum EoS variation, given by the largest fractional difference from the fits as shown in Figs.~\ref{fig:ILQ},~\ref{fig:clove},~\ref{fig:rlove} and~\ref{fig:binLove}, sees a considerable improvement for the constrained set of EoSs, compared to the unconstrained set as well as previous works.
 Additionally, notice how the maximal EoS variation for the unconstrained set of EoSs is slightly higher than that found in Refs.~\cite{Yagi:ILQ,Yagi:binLove} - due to the effects of large random sampling taking into account more sources of uncertainty.
@@
  $\bar{C}-\Lambda$ & $0.065$ & $0.071975$ & $0.021688$\\
+ $R-\Lambda$ & \zc{Anyone?} & $0.497685$ & $0.188783$\\
  \hline
@@
 In this section we consider approximate C-Love EoS-insensitive relations between NS compactness $\bar{C} \equiv M/R$ and unitless tidal deformability $\Lambda$, as discussed by Yagi and Yunes~\cite{Yagi:binLove}.
+In addition, we show the R-Love relations, giving the relationship between NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
 Similar to the previous section, we consider two classes of stars: nuclear matter EoSs and hybrid quark-hadron star EoSs.
@@
 \begin{equation}
-\bar{C}^N=C_{\bar{C}\Lambda}\Lambda^{-1/5}.
+\bar{C}^N=C_{\bar{C}\Lambda}\Lambda^{-1/5}.\label{eq:cloveFit}
 \end{equation}
@@
 
+In addition, Fig.~\ref{fig:rlove} displays the relationship between NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
+As can be seen with the unconstrained EoSs, previously this relation was not very universal, and gave large uncertainties ($\sim50\%$ on the mapping from tidal deformability to radius.
+On the other hand, EoSs constrained by GW170817 observe a large decrease in EoS variability to $\sim20\%$.
+Similar to the fits performed for the I-Love-Q and C-Love universal relations, we fit the R-Love relations to Eq.~\ref{eq:ILQfitNew} with a newtonian control factor the same as used in the C-Love case seen in Eq.~\ref{eq:cloveFit}, where the NS mass is substituted with the polytropic form $M\propto R^{(3-n)/(1-n)}$\zc{Anyone have a cite for this?}.
+Absorbing the proprtionality constant into $C_{R\Lambda}$ results in:
+\begin{equation}
+R^N \approx C_{R\Lambda}\Lambda^{(n-1)/10}
+\end{equation}
+for polytropic index $n$, taken to be an additional fitting constant.
+The results of this fit are displayed in Tab.~\ref{tab:ILQfitNew}, and the maximal EoS variability is again shown in Tab.~\ref{tab:maxVar}.
+\begin{figure}
+\begin{center} 
+\includegraphics[width=1\columnwidth]{RL.eps}
+\end{center}
+\caption{
+Similar to Fig.~\ref{fig:clove} but for the R-Love relationships between the NS radius and tidal deformability.
+In this figure, we also construct fits to  Eq.~\ref{eq:ILQfitNew}, limiting to the newtonian case $\bar{R} \sim M\Lambda^{1/5}$, with $M\sim R^{(3-n)/(1-n)}$ for polytropic index $n$.
+Observe how the fractional difference from the fit is reduced significantly between the unconstrained and constrained sets of EoSs, shown by the comparisons in Tab.~\ref{tab:maxVar}.
+Also shown in this figure is the hybrid star R-Love relations along with their fractional difference from the constrained EoS fits (dashed green).
+}
+\label{fig:rlove}
+\end{figure}
+
 These results, similar to that found in Sec.~\ref{sec:ilq}, show the considerable improvement found in using constrained EoSs over any unconstrained set.
@@
 This is exemplified in Fig.~\ref{fig:clove} by the dashed green curves.
+We observe similar results for the case of R-Love relations, as seen by the dashed green curves in Fig.~\ref{fig:rlove}.
+Here, the hybrid stars show a maximal fractional difference of $30.82\%$ when compared to the constrained EoS fits - a value much smaller than the unconstrained EoSs variation.
 
@@
 Fig.~\ref{fig:binLove} shows the improved binary Love EoS-insensitive relation for 3 different mass ratios: $q=0.9$, $q=0.75$, and $q=0.5$ for both constrained and unconstrained sets of EoSs.
+In this figure we show the absolute difference from the fit, rather than the fractional difference, so one can see which regions of $\Lambda_s$ display the largest actual difference.
 Observe how once again, the constrained set of EoSs show a considerable improvement upon both the unconstrained set of EoSs, as well as the results found in previous works~\cite{Yagi:binLove}.
 Additionally, the unconstrained set of EoSs show similar, yet slightly larger EoS variation due to the random sampling.
-Once again, the maximum EoS variability is tabulated in Tab.~\ref{tab:maxVar} for each value of mass ratio.
+Once again, the maximum EoS variability (in terms of fractional difference from the fit for comparison purposes) is tabulated in Tab.~\ref{tab:maxVar} for each value of mass ratio.
 
@@
 \begin{center} 
-\includegraphics[width=\linewidth]{binLove.eps}
+\includegraphics[width=\linewidth]{binLoveAbsolute.eps}%{binLove.eps}
 \end{center}
@@
 Binary Love EoS-insensitive relations shown for the constrained EoSs (dotted maroon) and unconstrained EoSs (solid green) for various values of mass ratio: $q=0.9$, $q=0.75$, and $q=0.50$.
-In this figure, the top panel displays the EoS-insensitive relations with fits given by Eq.~\ref{eq:binLovefit} shown by dashed black lines (note there are 2 fits for each mass ratio, corresponding to the constrained and unconstrained sets of EoSs), while the bottom 3 panels correspond to the EoS variation for each mass ratio.
-Observe how the the constrained set of EoSs show a reduction in EoS variation for both the unconstrained set, and from the results shown in Ref.~\cite{Yagi:binLove}.
-The max EoS variability for each case is tabulated and compared in Tab.~\ref{tab:maxVar}.
+In this figure, the top panel displays the EoS-insensitive relations with fits given by Eq.~\ref{eq:binLovefit} shown by dashed black lines (note there are 2 fits for each mass ratio, corresponding to the constrained and unconstrained sets of EoSs), while the bottom 3 panels correspond to the absolute EoS variation for each mass ratio.
+Observe how the constrained set of EoSs show a reduction in EoS variation for both the unconstrained set, and from the results shown in Ref.~\cite{Yagi:binLove}.
+The maximal EoS variability (shown as a the fractional difference for comparison purposes) for each case is tabulated and compared in Tab.~\ref{tab:maxVar}.
 Additionally shown is the binary Love relations for the 10 hybrid star EoSs (dashed bright green curves), as well as the HS fits (dot-dashed blue curves) discussed in Sec.~\ref{sec:binLove-hybrid}.
 Observe the large deviations from the fit as the mass ratio $q$ increases, returning near the fit before the transitional pressure at large values of $\Lambda_s$.
-This is shown in the bottom three panels as the fractional difference from the NS fit for comparison, while the HS fits show similar EoS variability to the constrained EoSs.
+This is shown in the bottom three panels as the absolute difference from the NS fit for comparison, while the HS fits show similar EoS variability to the constrained EoSs.
 }
@@
 Current interferometer sensitivities are not yet small enough to accurately constrain $\tilde{\Lambda}$.
-For example, GW170817 was detected by LIGO observing run 2 (``O2")\zc{cite} and was able to constrain $\tilde{\Lambda}$ to a $90\%$ confidence interval of 325 (this relates to a standard deviation of $\sigma_{\tilde{\Lambda}}=198$) centered at $\tilde{\Lambda}=395$.
-This corresponds to statistical uncertainties on the order of $\sim 82\%$, which vastly dominates the error budget compared to the small systematic errors picked up by EoS variation in the EoS-insensitive relations, which can be seen in Fig.~\ref{fig:residuals}.
+For example, GW170817 was detected by LIGO observing run 2 (``O2")~\cite{aLIGO} and was able to constrain $\tilde{\Lambda}$ to a $90\%$ confidence interval of 325 (this relates to a standard deviation of $\sigma_{\tilde{\Lambda}}=198$) centered at $\tilde{\Lambda}=395$.
+This corresponds to statistical uncertainties on the order of $\sim 82\%$, which vastly dominates the error budget compared to the small systematic errors picked up by EoS variation in the EoS-insensitive relations.
 This implies that currently, improved EoS-insensitive relations will only make a negligible difference in tidal parameter extraction.
 
-In this section, we investigate the residuals in $\tilde{\Lambda}(\Lambda_a,\Lambda_s,q)$ in order to marginalize over the intrinsic error in the binary Love EoS-insensitive relations.
+In Sec.~\ref{sec:observations}, we compare the statistical errors on the parameter extraction of tidal parameters to the systematic errors introduced by using improved binary Love relations, computed in the current section.
+This is repeated for 5 future detectors, where multiple event detections become important.
+Because future events occur with weighted tidal parameters $\tilde\Lambda$ which are unknown at this time, we can not accurately combine the uncertainties on $\tilde\Lambda$ for multiple events.
+To remedy this, we re-parameterize the waveform and consider the $\lambda_0$ and $\lambda_1$ tidal coefficients produced by Taylor expanding unitful tidal deformability $\lambda \equiv \Lambda m^5$ about $m_0=1.4\text{ M}_{\odot}$:
+\begin{equation}
+\lambda \approx \lambda_0 + \lambda_1 (m-1.4 \text{M}_{\odot})/\text{M}_{\odot},
+\end{equation}
+as discussed in Ref.~\cite{delPozzo:TaylorTidal}.
+The new tidal parameters $\lambda_0$ and $\lambda_1$ do not depend on mass, and therefore are identical for every future binary NS merger, and thus may be combined in uncertainty.
+For this reason, we consider the new tidal parameters $\lambda_0$ and $\lambda_1$ for the remainder of the investigation.
+
+In this section, we investigate the residuals in $\lambda_0(\Lambda_a,\Lambda_s,q)$ in order to marginalize over the intrinsic error in the binary Love EoS-insensitive relations.
 In particular, we restrict our focus to only the constrained set of EoSs.
-Residuals in $\tilde\Lambda$ are computed as $\tilde{\Lambda}^{\text{fit}}-\tilde{\Lambda}^{\text{true}}$, where $\tilde{\Lambda}^{\text{true}}=\tilde{\Lambda}(\Lambda_a,\Lambda_s,q)$ corresponds to the true value predicted by the sample EoSs, and $\tilde{\Lambda}^{\text{fit}}=\tilde{\Lambda}(\Lambda_a^{\text{fit}}(\Lambda_s,q),\Lambda_s,q)$ corresponds to the value obtained through the EoS-insensitive relations found in Sec.~\ref{sec:binLove-nuclear}.
-Following Ref.~\cite{Katerina:residuals}, we assume the residuals in $\tilde{\Lambda}$ observe a Gaussian distribution with mean and standard deviation given by:
+Residuals in $\lambda_0$ are computed as $\lambda_0^{\text{fit}}-\lambda_0^{\text{true}}$, where $\lambda_0^{\text{true}}=\lambda_0(\Lambda_a,\Lambda_s,q)$ corresponds to the true value predicted by the sample EoSs, and $\lambda_0^{\text{fit}}=\lambda_0(\Lambda_a^{\text{fit}}(\Lambda_s,q),\Lambda_s,q)$ corresponds to the value obtained through the EoS-insensitive relations found in Sec.~\ref{sec:binLove-nuclear}.
+Following Ref.~\cite{Katerina:residuals}, we assume the residuals in $\lambda_0$ observe a Gaussian distribution with mean and standard deviation given by:
 \begin{align}
-\mu_{\tilde{\Lambda}}(\Lambda_s,q) &=\frac{\mu_{\Lambda_s}(\Lambda_s)+\mu_{q}(q)}{2},\\ 
-\sigma_{\tilde{\Lambda}} &=\sqrt{\sigma_{\Lambda_s}^2(\Lambda_s) + \sigma_{q}^2(q)}. 
+\mu_{\lambda_0}(\Lambda_s,q) &=\frac{\mu_{\Lambda_s}(\Lambda_s)+\mu_{q}(q)}{2},\\ 
+\sigma_{\lambda_0} &=\sqrt{\sigma_{\Lambda_s}^2(\Lambda_s) + \sigma_{q}^2(q)}. 
 \end{align}
@@
 \mu_{q}(x) &= \mu_3 x^2 + \mu_4 x + \mu_5, \label{eq:margFit2}\\ 
-\sigma_{\Lambda_s}(x) &= \sigma_1 x^{7/2} + \sigma_2 x^{5/2} + \sigma_3 x^{3/2} +  \sigma_4 x^{1/2} + \sigma_5, \label{eq:margFit3}\\ 
-\sigma_{q}(x) &= \sigma_6 x^3 + \sigma_7 x^2 + \sigma_8 x + \sigma_9. \label{eq:margFit4}
+\sigma_{\Lambda_s}(x) &= \sigma_1 x^{5/2} + \sigma_2 x^{3/2} +  \sigma_3 x^{1/2} + \sigma_4, \label{eq:margFit3}\\ 
+\sigma_{q}(x) &= \sigma_5 x^3 + \sigma_6 x^2 + \sigma_7 x + \sigma_8. \label{eq:margFit4}
 \end{align}
 The fitting parameters $\mu_i$ and $\sigma_i$ are tabulated in Table~\ref{tab:marginalized}.
+Figure~\ref{fig:qLsResiduals} shows the $\lambda_0$ residuals binned in both q and $\Lambda_s$, highlighting the error weights across the $(q,\Lambda_s)$ parameter space.
+Observe how $q\sim0.5$ and $\Lambda_s\sim2000$ observe the highest errors, while the low and high values of $q$ and $\Lambda_s$ see minimal uncertainties.
 
@@
 \caption{
-Coefficients to the fits given by Eqs.(~\ref{eq:margFit1})-(\ref{eq:margFit4}) for the relative error on $\tilde{\Lambda}$ in the improved binary Love EoS-insensitive relations presented in this paper.
+Coefficients to the fits given by Eqs. (\ref{eq:margFit1})-(\ref{eq:margFit4}) for the relative error on $\lambda_0$ in the improved binary Love EoS-insensitive relations presented in this paper.
 }\label{tab:marginalized}
@@
 \noalign{\smallskip}
-$\mu_1$ & $-8.7169662 \times 10^{-5}$ & $\sigma_1$ & $3.3497867 \times 10^{-11}$\\
-$\mu_2$ & $0.0185324$ & $\sigma_2$ & $-2.3026166 \times 10^{-7}$\\
-$\mu_3$ & $-3.2611497$ & $\sigma_3$ & $3.8180750 \times 10^{-4}$\\
-$\mu_4$ & $5.0680859$ & $\sigma_4$ & $0.0444373$\\
-$\mu_5$ & $-1.9040182$ & $\sigma_5$ & $-0.0126140$\\
- &  & $\sigma_6$ & $181.8712429$\\
- &  & $\sigma_7$ & $-419.0842028$\\
- &  & $\sigma_8$ & $299.5608266$\\
-  &  & $\sigma_9$ & $-62.1555049$\\
+$\mu_1$ & $-1.0158750\times10^{-29}$ & $\sigma_1$ & $-1.1953582\times10^{-33}$\\
+$\mu_2$ & $5.3758312\times10^{-27}$ & $\sigma_2$ & $4.0560936\times10^{-30}$\\
+$\mu_3$ & $-6.8500063\times10^{-25}$ & $\sigma_3$ & $5.6991756\times10^{-27}$\\
+$\mu_4$ & $1.0235088\times10^{-24}$ & $\sigma_4$ & $-1.3342207\times10^{-26}$\\
+$\mu_5$ & $-3.6802625\times10^{-25}$ & $\sigma_5$ & $7.1682441\times10^{-24}$\\
+ &  & $\sigma_6$ & $-1.5947653\times10^{-23}$\\
+ &  & $\sigma_7$ & $1.0979389\times10^{-23}$\\
+ &  & $\sigma_8$ & $-2.1389918\times10^{-24}$\\
  \noalign{\smallskip}
@@
 
-Figure~\ref{fig:residuals} displays the Gaussian distribution of $\tilde\Lambda$ residuals for both the constrained, and unconstrained sets of EoSs for comparison.
-Observe how the standard deviations $\sigma=7.666$ and $\sigma=40.887$ show a large decrease between the unconstrained and constrained sets of EoSs.
-In addition, we find the 90th, 99th, and 100th percentiles on $\tilde\Lambda$ to be $P_{90}=12.014$, $P_{99}=29.710$, and $P_{100}=62.240$ for the constrained EoSs.
-Because the un-binned residuals seen in Fig.~\ref{fig:residuals} are dominated by the low-error regions of parameter space ($\Lambda_s \rightarrow 0$ and $q \rightarrow 1$) shown by the fits of Tab.~\ref{tab:marginalized}, we consider the 90th for the remainder of the analysis.
-We take this value of $P_{90}=12.014$ to be the systematic measurement error introduced by using the improved binary Love EoS-insensitive relations on the parameter extraction of $\tilde\Lambda$.
-Currently, the statistical error of $198$ on $\tilde\Lambda$ from GW170817 dominate the error budget compared to the systematic error of $12.014$.
+Figure~\ref{fig:residuals} displays the Gaussian distribution of $\lambda_0$ residuals for both the constrained, and unconstrained sets of EoSs for comparison.
+Observe how the standard deviations $\sigma=1.52\times10^{-25} \text{ s}^5$ and $\sigma=12.21\times10^{-25} \text{ s}^5$ show a large decrease between the unconstrained and constrained sets of EoSs.
+In addition, we find the 90th, 99th, and 100th percentiles on $\lambda_0$ to be $P_{90}=2.06\times10^{-25} \text{ s}^5$, $P_{99}=6.61\times10^{-25} \text{ s}^5$, and $P_{100}=17.36\times10^{-25} \text{ s}^5$ for the constrained EoSs.
+Because the un-binned residuals seen in Fig.~\ref{fig:residuals} are dominated by the low-error regions of parameter space ($\Lambda_s \rightarrow 0$, $\Lambda_s \rightarrow \infty$, $q \rightarrow 0$ and $q \rightarrow 1$) shown by Fig.~\ref{fig:qLsResiduals}, we consider the 90th percentile error for the remainder of the analysis, in order to further take into account the high-error regions of the parameter space ($\Lambda_s \sim 2000$, $q\sim0.5$).
+We take this value of $P_{90}=2.06\times10^{-25} \text{ s}^5$ to be the systematic measurement error introduced by using the improved binary Love EoS-insensitive relations on the parameter extraction of $\lambda_0$, indicated by the dashed indigo line in Fig.~\ref{fig:stackedFisher}.
+Similarly, we derive the systematic measurement error on $\tilde\Lambda$ to be $12.01$, shown in Fig.~\ref{fig:singleFisherLt}.
+Currently, the statistical error of $26.53 \times 10^{-25} \text{ s}^5$ on $\lambda_0$ from GW170817 dominate the error budget compared to the systematic error of $2.06\times10^{-25} \text{ s}^5$, as seen in Fig.~\ref{fig:stackedFisher}.
 This means that, for the current ``O2" detector sensitivity, the use of improved binary Love EoS-insensitive relations will only make a negligible difference on the extraction of $\tilde\Lambda$.
@@
 \begin{center} 
+\includegraphics[width=\columnwidth]{qResiduals.eps}
+\includegraphics[width=\columnwidth]{LsResiduals.eps}
+\end{center}
+\caption{
+$\lambda_0$ residuals binned in $q$ (top) and $\Lambda_s$ (bottom), highlighting the different error weights across the entire $(q,\Lambda_s)$ parameter space.
+In this figure, the violet circles indicate the standard deviation of each bin in $q$-space ($\Lambda_s$-space), while the black dashed lines represent the best fit given by Eqs.
+(\ref{eq:margFit3})-(\ref{eq:margFit4}).
+Observe how the error is maximal for $q\sim0.5$ and $\Lambda_s\sim2000$, while it becomes minimal for both low and high values of $q$ and $\Lambda_s$.
+}
+\label{fig:qLsResiduals}
+\end{figure}
+
+\begin{figure}
+\begin{center} 
 \includegraphics[width=\columnwidth]{residuals.pdf}
@@
 \caption{
-Residuals on $\tilde\Lambda$ computed as $\tilde{\Lambda}^{\text{fit}}-\tilde{\Lambda}^{\text{true}}$ for the binary Love relations modeled in Sec.~\ref{sec:binLove-nuclear} for both constrained and unconstrained sets of EoSs.
-These residuals obey Gaussian distributions centered at $\mu=-1.8133 \times 10^{-4}$ and $\mu=4.2258 \times 10^{-3}$ with standard deviations of $\sigma=7.6664$ and $\sigma=40.8866$ for the constrained and unconstrained sets of EoSs, respectively.
-These uncertainties correspond roughly to the systematic errors introduced on the parameter extraction of $\tilde{\Lambda}$ upon the use of binary Love EoS-insensitive relations.
-However, to take into account the systematic errors found in high-error regions of the parameter space, we instead set the systematic error to be the 90th percentile, $P_{90}=12.014$.
-Observe that the systematic errors from using the improved (constrained) binary Love EoS-insensitive relations are negligible compared to the statistical errors accrued on parameter extraction from GW170817, found to be $\sigma_{\tilde{\Lambda}}=198$.
+Residuals on $\lambda_0$ computed as $\lambda_0^{\text{fit}}-\lambda_0^{\text{true}}$ for the binary Love relations modeled in Sec.~\ref{sec:binLove-nuclear} for both constrained and unconstrained sets of EoSs.
+These residuals obey Gaussian distributions centered at $\mu=-2.39 \times 10^{-27} \text{ s}^5$ and $\mu=4.22 \times 10^{-27} \text{ s}^5$ with standard deviations of $\sigma=1.52\times10^{-25} \text{ s}^5$ and $\sigma=12.21\times10^{-25} \text{ s}^5$ for the constrained and unconstrained sets of EoSs, respectively.
+These uncertainties correspond roughly to the systematic errors introduced on the parameter extraction of $\lambda_0$ upon the use of binary Love EoS-insensitive relations.
+However, to take into account the systematic errors found in high-error regions of the parameter space, we instead set the systematic error to be the 90th percentile, $P_{90}=2.06\times10^{-25} \text{ s}^5$.
+Observe that the systematic errors from using the improved (constrained) binary Love EoS-insensitive relations are negligible compared to the statistical errors accrued on parameter extraction from GW170817, found to be $\sigma_{\lambda_0}=26.53 \times 10^{-25} \text{ s}^5$.
 }
@@
 \begin{equation}\label{eq:template}
-\theta^a=(\ln{A},\phi_c,t_c,\ln{\mathcal{M}},\ln{\mathcal{\eta}},\chi_s,\chi_a,\tilde{\Lambda},\delta \tilde{\Lambda}),
+\theta^a=(\ln{A},\phi_c,t_c,\ln{\mathcal{M}},\ln{\mathcal{\eta}},\chi_s,\chi_a,\lambda_0, \lambda_1),
 \end{equation}
@@
 \end{equation}
-In this analysis, we consider the ``PhenomD" waveform template~\cite{PhenomDI,PhenomDII} modified by tidal corrections shown in Ref.~\cite{Wade:tidalCorrections}.
-Lastly, $S_n(f)$ is the spectral noise density for the given interferometer.
 
-We begin by authenticating this approach by applying a Fisher analysis to GW170817, as observed by LIGO with O2 detector sensitivity\zc{cite}.
+In this analysis, we consider the ``PhenomD" (IMRD) waveform template~\cite{PhenomDI,PhenomDII} modified by two different tidal corrections: the 6PN tidal correction shown in Ref.~\cite{Wade:tidalCorrections} (IMRD + 6PN), and the NRTidal correction shown in Ref.~\cite{Samajdar:NRTidal} (IMRD + NRTidal).
+Comparing the two tidal corrections to the IMRD waveform returns an estimate on the magnitude of waveform mismodeling systematics.
+Lastly, we consider the spectral noise density $S_n^A(f)$ for 6 different interferometer designs: $A \equiv ($O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, CE~\cite{ET}, ET-D~\cite{Ap_Voyager_CE}$)$ in order to compare the statistical errors accrued on parameter extraction using future upgraded detectors.
+
+We begin by authenticating this approach by applying a Fisher analysis (IMRD + 6PN waveform injection) to GW170817, as observed by LIGO with O2 detector sensitivity~\cite{aLIGO}.
+Because only 1 event was detected, we utilize $\tilde\Lambda$ and $\delta\tilde\Lambda$ as the tidal parameters for comparison purposes.
 Further, we scale the luminosity distance such that the signal-to-noise-ratio ($SNR \equiv \rho$) is fixed to be $\rho=32.4$, as was found in GW170817.
@@
 \caption{
-Square root of of the spectral noise densities $\sqrt{S_n^A(f)}$ plotted for detectors ($A$): LIGO O2 (orange), aLIGO (green), A\texttt{+} (purple), Voyager (magenta), CE (red), and ET-D (blue) as interpolated from publicly available data\zc{cite}.
+Square root of of the spectral noise densities $\sqrt{S_n^A(f)}$ plotted for detectors ($A$): LIGO O2 (orange), aLIGO (green), A\texttt{+} (purple), Voyager (magenta), CE (red), and ET-D (blue) as interpolated from publicly available data.
 Spectral noise densities are plotted from $f_{\text{min}}=(23,10,10,7,1,1) \text{ Hz}$, respectively, to $f_{\text{max}}=1649 \text{ Hz}$.
-Also shown is $2 \sqrt{f}$ multiplied by the amplitude of the PhenomD~\cite{PhenomDI,PhenomDII} waveform template, modified by tidal corrections from Ref.~\cite{Wade:tidalCorrections} used in our Fisher Analysis.
+Also shown is $2 \sqrt{f}$ multiplied by the amplitude of the PhenomD~\cite{PhenomDI,PhenomDII} waveform template, modified by two different tidal corrections used in our Fisher analyses: the 6PN tidal correction from Ref.~\cite{Wade:tidalCorrections}, as well as the NRTidal tidal correction found in Ref.~\cite{Samajdar:NRTidal} (this makes a negligable difference in the above figure).
 }
@@
 
-Next, we consider events identical to GW170817 detected on future design sensitivity upgrades and detectors $A \equiv ($O2, aLIGO, A\texttt{+}, Voyager, CE, ET-D$)$\zc{cite}, shown in Fig.~\ref{fig:sensitivities}, to determine if and when the statistical errors associated with parameter extraction of $\tilde{\Lambda}$ drop below the systematic EoS variation errors from using binary Love EoS-insensitive relations.
+Next, we consider events identical to GW170817 detected on future design sensitivity upgrades and detectors $A \equiv ($O2, aLIGO, A\texttt{+}, Voyager, CE, ET-D$)$, shown in Fig.~\ref{fig:sensitivities}, to determine if and when the statistical errors associated with parameter extraction of $\lambda_0$ drop below the systematic EoS variation errors from using binary Love EoS-insensitive relations.
 The process we use for each detector sensitivity $S_n^A(f)$ is as follows:
@@
 \item Perform a Fisher analysis as outlined above using $S_n^A(f)$, while restricting the luminosity distance $D_L$ such that $\rho^{\text{O2}}_{\text{GW170817}}=32.4$ would be achieved on O2 sensitivity $S_n^{\text{O2}}(f)$.
-This results in SNR $\rho^A_{\text{GW170817}}$ and statistical error $\sigma_\text{GW170817}^A$ accrued in the extraction of $\tilde{\Lambda}$ on detector $A$.
+Here we assume low spin priors $|\chi| \leq 0.05$, as well as $0 \leq \lambda_0 \leq 5 \times 10^{-23} \text{ s}^5$ and $-5 \times 10^{-18} \text{ s}^4\text{ M}_{\odot} \leq \lambda_1 \leq 0$~\cite{delPozzo:TaylorTidal}.
+This results in SNR $\rho^A_{\text{GW170817}}$ and statistical error $\sigma_\text{GW170817}^A$ accrued in the extraction of $\lambda_0$ on detector $A$.
 \item Generate a population of $N_A$ events corresponding to the expected binary NS merger detection rate for detector $A$, following the distribution $f=3 \rho_{\text{th}}^3/\rho^4$~\cite{Shutz:SNR,Chen:SNR} with a network SNR threshold of $\rho_{\text{th}}=8$.
-This is calculated for the upper, central, and lower limits of the local binary NS coalescence rate density $R=1540^{+3200}_{-1220} \text{ Gpc}^{-3}\text{yr}^{-1}$~\cite{Abbott2017}, giving the rates shown in the second column of Table~\ref{tab:variances}.
-\item Compute the population standard deviation given by:
+The number of events $N_A$ is calculated by taking into account the BNS merger rate history throughout all redshift values within detector As' horizon distance $z_h$, as shown by Eq.
+(10) of Ref.~\cite{Cutler:BNSmerger}:
 \begin{equation}
-\frac{1}{(\sigma_N^A)^2}=\sum_i^{N_A}\frac{1}{(\sigma_i^A)^2},
+N_A=\Delta \tau_0 \int\limits^{z_{h}}_0 4 \pi \lbrack  a_0r_1(z)\rbrack^2 \mathcal{R} r(z) \frac{d \tau}{dz} dz.
 \end{equation}
-where $\sigma_i^A$ is computed by the relations $\sigma_i^A \times \rho_i^A = \sigma_{\text{GW170817}}^A \times \rho_{\text{GW170817}}^A$.
+Here, $a_0r_1(z)$, $\frac{d\tau}{dz}$, and $r(z)$ for our chosen cosmology are given by:
+\begin{equation}
+a_0r_1(z) = \frac{1}{H_0}\int\limits^z_0 \frac{dz'}{\sqrt{(1-\Omega_{\Lambda})(1+z')^3+\Omega_{\Lambda}}},
+\end{equation}
+\begin{equation}
+\frac{d\tau}{dz} = \frac{1}{H_0} \frac{1}{1+z}\frac{1}{\sqrt{(1-\Omega_{\Lambda})(1+z')^3+\Omega_{\Lambda}}},
+\end{equation}
+\begin{equation}
+r(z) = \left\{
+\begin{array}{ll}
+      1+2z & z \leq 1 \\
+      \frac{3}{4}(5-z) & 1\leq z\leq 5 \\
+      0 & z\geq 5\\ 
+\end{array} 
+\right.
+\end{equation}
+
+where $H_0 = 70 \text{km s}^{-1}\text{Mpc}^{-1}$ is the local Hubble constant, and $\Omega_{\Lambda}=0.67$ is the universe's vacuum energy density.
+Here we choose an observing period $\Delta \tau = 1$ year, and calculate the detection rate for the upper, central, and lower limits of the local binary NS coalescence rate density $\mathcal{R}=1540^{+3200}_{-1220} \text{ Gpc}^{-3}\text{yr}^{-1}$~\cite{Abbott2017}, giving the rates shown in the second column of Table~\ref{tab:variances}.
+\item Compute the overall population standard deviation, taking into account sources at varying redshifts as done in Eq. (3) of Ref.~\cite{Takahiro}:
+\begin{equation}
+\sigma_{N_A}^{-2}=\Delta \tau \int\limits^{z_h}_04 \pi \lbrack a_0 r_1(z)\rbrack^2 \mathcal{R}r(z)\frac{d\tau}{dz}\sigma^A_i(z)^{-2}dz
+\end{equation}
+where $\sigma_i^A(z)$ is computed by the relations $\sigma_i^A \times \rho_i^A = \sigma_{\text{GW170817}}^A \times \rho_{\text{GW170817}}^A$.
 \end{itemize}
-The results are compiled in Table~\ref{tab:variances}, and shown graphically in Fig.~\ref{fig:stackedFisher} where $\sigma^A_{\text{GW170817}}$ and $\sigma^A_N$ are plotted as a function of $\rho^A_{\text{GW170817}}$ (the SNR as if GW170817 were detected on future detector $A$) for 5 future detector sensitivities.
+
+The results for this process upon the injection of the IMRD + 6PN waveform are compiled in Table~\ref{tab:variances}, and shown graphically in Fig.~\ref{fig:stackedFisher} where $\sigma^A_{\text{GW170817}}$ and $\sigma^A_N$ are plotted as a function of $\rho^A_{\text{GW170817}}$ (the SNR as if GW170817 were detected on future detector $A$) for 5 future detector sensitivities.
+For reference, Fig.~\ref{fig:singleFisherLt} also displays the estimated $\tilde\Lambda$ extraction efficiency for \emph{one} event on each detector; as these events can not be combined like was done in the case of $\lambda_0$.
+Observe how this figure shows similar results on $\tilde\Lambda$ to that found on $\lambda_0$ for the case of one event - that is, future detectors ET and CE both observe statistical errors on $\tilde\Lambda$ dropping below the systematic binary Love errors for a single event.
+\begin{figure}
+\begin{center} 
+\includegraphics[width=\columnwidth]{singleFisherLt.eps}
+\end{center}
+\caption{
+Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue) in the extraction of $\tilde\Lambda$ from GW170817 (O2) as if observed with future interferometers aLIGO, A\texttt{+}, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
+Also shown is the systematic error on $\tilde\Lambda$ (indigo) derived using the same method used to compute the systematic error on $\lambda_0$.
+This is similar to Fig.~\ref{fig:stackedFisher} where the extraction efficiency of $\lambda_0$ was plotted.
+However, in this case multiple events can \emph{not} be combined due to the variation in mass and therefore $\tilde\Lambda$ among events.
+}
+\label{fig:singleFisherLt}
+\end{figure}
 
@@
 \caption{
-Tabulated results for the estimated statistical errors on $\tilde{\Lambda}$ for the combined results of $N_A$ detections corresponding to the estimated upper, central, and lower limits of the binary NS merger detection rate $R$.
+Tabulated results for the estimated statistical errors on $\lambda_0$ for the combined results of $N_A$ detections corresponding to the estimated upper, central, and lower limits of the binary NS merger detection rate $R$.
 This is repeated for 5 future detector sensitivities: aLIGO, A\texttt{+}, Voyager, CE, and ET.
-Below, $\rho^A_{\text{GW170817}}$ and $\sigma^A_{\text{GW170817}}$ correspond to the approximate SNR and $\sigma_{\tilde{\Lambda}}$ of GW170817 had it been observed by the future interferometer, and $\sigma^A_N$ corresponds to the final uncertainty on $\tilde{\Lambda}$ after $N_A$ detections on interferometer $A$.
-It can be seen here that the statistical errors on $\tilde{\Lambda}$ become comparable with the systematics (set to be $P_{90}=12.014$) from using improved binary Love relations from Voyager and on, indicating when it may be safe to utilize new EoS-insensitive relations.
+Below, $\rho^A_{\text{GW170817}}$ and $\sigma^A_{\text{GW170817}}$ correspond to the approximate SNR and $\sigma_{\lambda_0}$ of GW170817 had it been observed by the future interferometer, and $\sigma^A_N$ corresponds to the final uncertainty on $\lambda_0$ after $N_A$ detections on interferometer $A$.
+It can be seen here that the statistical errors on $\lambda_0$ become comparable with the systematics (set to be $P_{90}=12.014$) from using improved binary Love relations from Voyager and on, indicating when it may be safe to utilize new EoS-insensitive relations.
 Note the approximation for $\sigma^A_N$ under the O2 detector sensitivity is left blank due to the singularity of the detected event.
@@
 }\label{tab:variances}
-%\begin{tabular}{ c || c c c c c c c c} 
-%\hline
-%Detector ($A$) & $N_A (\text{Lower})$ & $N_A (\text{Central})$ & $N_A (\text{Upper})$ & $\rho^A_{\text{GW170817}}$ & $\sigma^A_{\text{GW170817}}$ & $\sigma^A_N (\text{Lower})$ & $\sigma^A_N (\text{Central})$ & $\sigma^A_N (\text{Upper})$\\
-%\hline
-%\hline
-%O2 & $1$ & $1$ & $1$ & $32.40$ & $168.40$ & $558.18$ & $393.24$ & $279.44$\\
-%aLIGO & $23$ & $112$ & $344$ & $90.74$ & $75.44$ & $117.022$ & $42.89$ & $24.27$\\
-%A\texttt{+} & $208$ & $1004$ & $3091$              & $180.95$ & $31.55$ &               $27.62$ & $13.36$ & $7.36$\\
-%Voyager & $3854$ & $1.85 \times 10^4$ & $5.71 \times 10^4$ &              $428.89$ & $16.69$              & $8.57$ & $3.78$ & $2.16$\\
-%ET-D & $3.98\times 10^5$ & $1.91\times 10^6$ & $5.89\times 10^6$ &                  $2807.45$ & $6.26$ &               $0.78$ & $0.35$ & $0.20$\\
-%CE & $1.35\times 10^7$ & $6.50\times 10^7$ & $2.00\times 10^8$ &                 $1398.03$ & $4.85$ &                 $0.34$ & $0.16$ & $0.10$\\
-%\hline
-%\end{tabular}
 \begin{tabular}{|c|@{\extracolsep{4pt}}c@{\extracolsep{0pt}}|c|@{\extracolsep{4pt}}C{1.7cm}@{\extracolsep{-2pt}}|C{1.7cm}|@{\extracolsep{-2pt}}C{1.7cm}@{\extracolsep{2pt}}|c|@{\extracolsep{0pt}}c@{\extracolsep{0pt}}|c|}
@@
 \\[-1em]
-\multicolumn{1}{c}{}  &  \multicolumn{1}{|c|}{\multirow{2}{*}{$\rho^A_{\text{GW170817}}$}}  &  \multirow{ 2}{*}{$\sigma^A_{\text{GW170817}}$}  &  \multicolumn{3}{|c|}{$N_A$}  &  \multicolumn{3}{|c|}{$\sigma^A_N$}  \\
+\multicolumn{1}{c}{}  &  \multicolumn{1}{|c|}{\multirow{2}{*}{$\rho^A_{\text{GW170817}}$}}  &  \multirow{ 2}{*}{\large $\frac{\sigma^A_{\text{GW170817}}}{10^{-25}}$}  &  \multicolumn{3}{|c|}{$N_A$}  &  \multicolumn{3}{|c|}{$\sigma^A_N / 10^{-25}$}  \\
 \cline{4-6}\cline{7-9}
@@
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
- O2  & \multicolumn{1}{|c|}{$32.40$}  & $168.40$ &  \multicolumn{1}{|c|}{--} & -- & -- & \multicolumn{1}{|c|}{--} & -- & --\\
+ O2  & \multicolumn{1}{|c|}{$32.40$}  & $26.53$ &  \multicolumn{1}{|c|}{--} & -- & -- & \multicolumn{1}{|c|}{--} & -- & --\\
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
- aLIGO  & \multicolumn{1}{|c|}{$90.74$}  & $75.44$ &  \multicolumn{1}{|c|}{$23$} & $112$ & $344$ & \multicolumn{1}{|c|}{$117.022$} & $42.89$ & $24.27$\\
+ aLIGO  & \multicolumn{1}{|c|}{$90.74$}  & $17.10$ &  \multicolumn{1}{|c|}{$20$} & $98$ & $304$ & \multicolumn{1}{|c|}{$28.51$} & $12.99$ & $7.32$\\
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
- A\texttt{+}  & \multicolumn{1}{|c|}{$180.95$}  & $31.55$ &  \multicolumn{1}{|c|}{$208$} & $1004$ & $3091$ & \multicolumn{1}{|c|}{$27.62$} & $13.36$ & $7.36$\\
+ A\texttt{+}  & \multicolumn{1}{|c|}{$180.95$}  & $7.12$ &  \multicolumn{1}{|c|}{163} & 786 & 2,419 & \multicolumn{1}{|c|}{$9.19$} & $3.85$ & $2.13$\\
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
@@
 
- Voyager  & \multicolumn{1}{|c|}{$428.89$}  & $16.69$ &  \multicolumn{1}{|c|}{$3854$} & $1.85 \times 10^4$ & $5.71 \times 10^4$ & \multicolumn{1}{|c|}{$8.57$} & $3.78$ & $2.16$\\
+ Voyager  & \multicolumn{1}{|c|}{$428.89$}  & $3.94$ &  \multicolumn{1}{|c|}{2,191} & 10,544 & 32,454 & \multicolumn{1}{|c|}{$3.27$} & $1.49$ & $0.83$\\
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
@@
 
- ET-D  & \multicolumn{1}{|c|}{$2807.45$}  & $6.26$ &  \multicolumn{1}{|c|}{$3.98 \times 10^5$} & $1.91 \times 10^6$ & $5.89 \times 10^6$ & \multicolumn{1}{|c|}{$0.78$} & $0.35$ & $0.20$\\
+ ET-D  & \multicolumn{1}{|c|}{$1398.03$}  & $1.07$ &  \multicolumn{1}{|c|}{71,536} & 344,270 & 1,059,638 & \multicolumn{1}{|c|}{$0.60$} & $0.27$ & $0.15$\\
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
@@
 
- CE  & \multicolumn{1}{|c|}{$1398.03$}  & $4.85$ &  \multicolumn{1}{|c|}{$1.35 \times 10^7$} & $6.50 \times 10^7$ & $2.00 \times 10^8$ & \multicolumn{1}{|c|}{$0.34$} & $0.16$ & $0.10$\\
+ CE  & \multicolumn{1}{|c|}{$2807.45$}  & $1.20$ &  \multicolumn{1}{|c|}{295,200} & 1,420,650 & 4,372,653 & \multicolumn{1}{|c|}{$0.58$} & $0.26$ & $0.14$\\
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
@@
 
-Concluding, we find that the Voyager, ET, and CE detectors all exhibit enough uncertainty reduction that the systematics on $\tilde\Lambda$ introduced from using improved EoS-insensitive relations (found to be $12.014$) no longer become negligible in the error budget.
-This implies that the use and further improvement of EoS-insensitive relations is justified for future binary NS merger detections.
+Next, we repeat the process upon the injection of the IMRD + NRTidal waveform in order to demonstrate the effect of waveform mismodeling.
+The results are shown in Fig.~\ref{fig:stackedFisher} by blue outlined circles (single detection uncertainties) and the outlined dashed maroon region (combined uncertainties from multiple detections).
+Observe the noticeable difference between the extraction efficiencies for the two different tidal corrections - highlighting the need for further waveform modeling for future interferometers.
+
+Concluding, we find that the Voyager, ET, and CE detectors all exhibit enough uncertainty reduction that the systematics on $\lambda_0$ introduced from using improved EoS-insensitive relations (found to be $12.014$) no longer become negligible in the error budget.
+This was also shown for the case of $\tilde\Lambda$, only taking into account single observed events, where ET and CE detectors both observe comparable statistical and systematic errors on $\tilde\Lambda$.
+This implies that the use and further improvement of EoS-insensitive relations is not only justified, but necessary, for future binary NS merger detections.
 Further, we investigate the dependence of the measurement accuracy of $\tilde\Lambda$ on the binary NS mass ratio $q$ for fixed chirp mass $\mathcal{M}=1.88\text{ M}_{\odot}$ in Appendix~\ref{app:measurement}.
@@
 Similarly, we find an increase in C-Love and I-Love-Q universality by a factors of $\sim 76$\% and $\sim 50$\%, respectively.
+We also show new R-Love relations relating the NS radius to its tidal deformability, displaying a maximum of $18.88\%$ EoS variability from the fit discussed in Sec.~\ref{sec:clove}.
 Additionally, we find that hybrid quark-hadron star EoSs \emph{do} obey the I-Love-Q and C-Love universality, albeit with a slightly higher maximum EoS variability as displayed in Tabs.~\ref{tab:hybridCompare} and ~\ref{tab:hybridCompareClove}.
@@
 We find that future interferometers Voyager, CE, and ET-D all experience statistical uncertainties upon the extraction of $\tilde{\Lambda}$ small enough to become comparable to the systematic errors injected through the use of improved EoS-insensitive relations (found to be $12.014$), as depicted in Fig.~\ref{fig:stackedFisher} and Table~\ref{tab:variances}.
+Additionally, we considered the effect of waveform mismodeling by comparing Fisher analyses using two different tidal corrections to the PhenomD waveform: 6PN and NRTidal.
+Doing so revealed a noticeable difference between the extraction uncertainties derived under injection of each waveform - indicating the need for further waveform modeling.
 Finally, in Appendix~\ref{app:measurement} we investigate the effect of NS binary mass ratio q on the measurement accuracy of $\tilde\Lambda$.

### 2019-01-15 paper/bin-love-after-gw170817.tex
new updates and cleaning to paper draft

@@
 % What was done before - Binary Love
-Previous studies have shown that approximately EoS-insensitive ``binary Love universal relations" exist between symmetric and antisymmetric combinations of individual tidal deformabilities, which are difficult to be independently measured with second-generation gravitational wave interferometers.
+Previous studies have shown that approximately EoS-insensitive ``binary Love EoS insensitive relations" exist between symmetric and antisymmetric combinations of individual tidal deformabilities, which are difficult to be independently measured with second-generation gravitational wave interferometers.
 % What was done before - I-Love-Q
-Similarly, another set of EoS-insensitive relations exist between individual neutron star parameters: moment of inertia (I), tidal deformability (Love number), quadrupole moment (Q), and compactness (C) - known as the ``I-Love-Q" and ``C-Love" universal relations.
+Similarly, another set of EoS-insensitive relations exist between individual neutron star parameters: moment of inertia (I), tidal deformability (Love number), quadrupole moment (Q), and compactness (C) - known as the ``I-Love-Q" and ``C-Love" EoS insensitive relations.
 % What universal relations do
-Such EoS-insensitive relations allow the elimination of some tidal parameters from the list of model parameters, thus breaking degeneracies and ultimately reducing the uncertainty of the dominant tidal effect in parameter estimation\kc{You mean $\tilde{\Lambda}$?
-In our paper with Carl and Aaron we showed that the binary Love relation doesn't affect the $\tilde{\Lambda}$ measurement much.}.
+Such EoS-insensitive relations allow the elimination of some tidal parameters from the list of model parameters, thus breaking degeneracies and ultimately reducing parameter extraction uncertainties.
 % What we will do
-\kc{Add a sentence saying that even the more precise relations have some EoS variation which can cause a systematic error which can be marginalized over}
+However, even the most precise of EoS insensitive relations carry EoS variation which inject systematic errors into the parameter extraction process.
 In this document, we explain how one can reduce equation of state variation for I-Love-Q, C-Love, and binary Love EoS-insensitive relations, which helps to reduce systematic errors on the tidal measurement of binary neutron star mergers.
@@
 This internal structure of such stars, known as the equation of state (EoS), is exceedingly important, as it is the determining factor for many NS observables - such as the mass, the radius, and many more.
-Unfortunately, terrestrial experiments can only study the EoS up to the nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy}, making NSs ideal laboratories for constraining ultra dense nuclear matter\kc{heavy ion collisions supposedly go to higher densities, but they are T-dependent}.
+Unfortunately, terrestrial experiments can only study the EoS to around the nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy} (although some temperature-dependent heavy-ion collision experiments may probe higher densities \zc{Katerina do you know of any papers on this?}), making NSs ideal laboratories for constraining ultra dense nuclear matter.
 
@@
 For example, electromagnetic observations of the mass-radius relationship of NSs have been used to place limits on the NS EoS~\cite{guver,ozel-baym-guver,steiner-lattimer-brown,Lattimer2014,Ozel:2016oaf}.
-However, these implications potentially suffer from large systematic errors due to astrophysical mismodeling uncertainties\kc{of...}.
+However, these implications potentially suffer from large systematic errors due to various x-ray burst astrophysical mismodeling uncertainties.
 Alternatively, the emission of gravitational waves (GWs) from binary NS merger events have proven to be a unique method of probing nuclear physics.
@@
 For example, utilizing the parameters $\tilde{\Lambda}$ and $\delta \tilde{\Lambda}$~\cite{Favata:2013rwa,Wade:tidalCorrections} which enter the GW waveform at different post-Newtonian (PN) orders (powers of the ratio between the orbital speed and the speed of light $v/c^{2n}$) partially mitigates these correlations.
-Similarly, the waveform may be parameterized by mass-independant tidal parameters $\lambda_0$ and $\lambda_1$, derived through a Taylor expansion about $m_0=1.4 \text{ M}_{\odot}$ of individual, unitful tidal deformability $\lambda \approx \lambda_0+\lambda+1(m_1-1.4 \text{ M}_{\odot})/\text{M}_{\odot}$~\cite{delPozzo:TaylorTidal}.
+Similarly, the waveform may be parameterized by mass-independent tidal parameters $\lambda_0$ and $\lambda_1$, derived through a Taylor expansion about $m_0=1.4 \text{ M}_{\odot}$ of individual, unitful tidal deformability $\lambda \approx \lambda_0+\lambda+1(m_1-1.4 \text{ M}_{\odot})/\text{M}_{\odot}$~\cite{delPozzo:TaylorTidal}.
 Use of this set of tidal parameters allows one to effectively combine multiple events with varying mass and $\tilde\Lambda$ components, not possible in the former parameterization of $\tilde{\Lambda}$ and $\delta \tilde{\Lambda}$
@@
 \subsection{Executive Summary}
-\kc{The paper is fairly short, is the summary here necessary?}
-
+\zc{Me and Kent discussed whether or not we should include this section or not, and we decided like having the quick summary for busy readers - especially with the increasing number of figs and tables (8 tables, 14 figures so far).
+We can discuss this further if anyone doesn't want it included :)}
 %What we did
@@
 Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue circle) in the extraction of $\lambda_0$ from GW170817 (O2) as if observed with future interferometers aLIGO, A\texttt{+}, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
-This is compared to the combined uncertainty $\sigma^A_N$ (turqoise shaded region) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper and lower limits of expected binary NS merger detection rates for O2, aLIGO, A\texttt{+}, Voyager, CE, and ET-D over 1 observation year.
+This is compared to the combined uncertainty $\sigma^A_N$ (turquoise shaded region) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper and lower limits of expected binary NS merger detection rates for O2, aLIGO, A\texttt{+}, Voyager, CE, and ET-D over 1 observation year.
 It can be seen that the statistical errors in parameter extraction become comparable to the systematics from EoS variation in binary Love relations (purple shaded region) for Voyager and on.
@@
 Additionally shown in the figure are the estimated statistical uncertainties on the extraction of $\lambda_0$ upon the injection of the PhenomD + NRTidal correction waveform (IMRD + NRTidal), rather than the PhenomD + 6PN tidal correction (IMRD + 6PN), in order to demonstrate the waveform mismodeling uncertainties.
-The single-detection uncertainties are shown in unfilled blue circles, while the combined detection uncertaintied are outlined in dashed maroon.
+The single-detection uncertainties are shown in unfilled blue circles, while the combined detection uncertainties are outlined in dashed maroon.
 }
@@
 The structure of a NS and its tidal interactions in a binary system rely heavily on the underlying state function describing the relationship between pressure ($p$) and energy density ($\epsilon$), or equation of state, of nuclear matter.
-Given that all currently proposed EoSs utilize certain approximations\kc{cite reviews by Baym and Oertel}, one method to study a wide range of physically realizable EoSs is to parameterize them in a model-independent way\kc{how is this model-independant?}.
+Given that all currently proposed EoSs utilize certain approximations~\cite{Oertel:Review,Baym:Review}, one method to study a wide range of physically realizable EoSs is to parameterize them such that any realistic EoS can be represented with a small number of parameters.
 Spectral representations~\cite{Lindblom:2010bb,Lindblom:2012zi,Lindblom:2013kra,Lindblom:2018rfr,Abbott:2018exr} parameterize EoSs by performing spectral expansions on the adiabatic index $\Gamma(p)$\footnote{Another way of parameterizing EoSs is the piecewise polytropic formulation~\cite{Read2009,Lackey:2014fwa,Carney:2018sdv}.}:
@@
 The spectral coefficients were sampled within the ranges: $\gamma_0 \in \lbrack 0.2,2 \rbrack$, $\gamma_1 \in \lbrack -1.6,1.7 \rbrack$, $\gamma_2 \in \lbrack -0.6,0.6 \rbrack$, $\gamma_0 \in \lbrack -0.02,0.02 \rbrack$, and further restricted the adiabatic index to be $\Gamma \in \lbrack 0.6,4.5 \rbrack$, ensuring the parameterization exposed a wide range of viable EoSs~\cite{Lindblom:parameters}.
-Additional constraints imposed upon the generated EoSs were as follows~\cite{LIGO:posterior}: (i) causality within 10\%, and (ii) EoS priors must support NS masses up to $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations\kc{cite}.
+Additional constraints imposed upon the generated EoSs were as follows~\cite{LIGO:posterior}: (i) causality within 10\%, and (ii) EoS priors must support NS masses up to $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations~\cite{Zhao:massiveNS}.
 We utilize a random set of 100 of the above posterior samples defined by GW170817, furthermore referenced as the ``constrained EoSs", as shown in Fig.~\ref{fig:eos}.
@@
 \end{equation}
-One can extract $Q_{ij}$ and $\varepsilon_{ij}$ -- and thus $\lambda$, or its dimensionless form $\Lambda \equiv \lambda/M^5$ -- via diffent asymptotic limits of the gravitational potential:
+One can extract $Q_{ij}$ and $\varepsilon_{ij}$ -- and thus $\lambda$, or its dimensionless form $\Lambda \equiv \lambda/M^5$ -- via different asymptotic limits of the gravitational potential:
 \begin{align}
@@
 display EoS-insensitive properties to a high degree, showing EoS variations up to 20\% for binaries with masses less than $1.7 \text{ M}_{\odot}$, for a representative set of 11 EoSs. 
-These relations, known as ``binary Love universal relations" allows one to break degeneracies between coupled tidal parameters.
+These relations, known as ``binary Love EoS insensitive relations" allows one to break degeneracies between coupled tidal parameters.
 This is important for two reasons: (i) allows us to algebraically eliminate tidal parameters from the template parameter list, improving parameter estimation, and (ii) automatic measurement of second tidal parameter given observation of the first.
@@
 \begin{equation}\label{eq:Newtonian}
-\bar{I}^{\text{N}} = C_{\bar{I}\Lambda}\Lambda^{2/5}, \hspace{3mm} \bar{Q}^{\text{N}} = C_{\bar{Q}\Lambda}\Lambda^{1/5}, \hspace{3mm} \bar{I}^{\text{N}} = C_{\bar{I}\bar{Q}}\bar{Q}^{2}.
+\bar{I}^{\text{N}} = K_{\bar{I}\Lambda}\Lambda^{2/5}, \hspace{3mm} \bar{Q}^{\text{N}} = K_{\bar{Q}\Lambda}\Lambda^{1/5}, \hspace{3mm} \bar{I}^{\text{N}} = K_{\bar{I}\bar{Q}}\bar{Q}^{2}.
 \end{equation}
@@
 \begin{equation}\label{eq:ILQfitNew}
-y=C_{yx} x^{\alpha} \frac{1+\sum_{i=1}^3 a_i x^{-i/5}}{1+\sum_{i=1}^3 b_i x^{-i/5}},
+y=K_{yx} x^{\alpha} \frac{1+\sum_{i=1}^3 a_i x^{-i/5}}{1+\sum_{i=1}^3 b_i x^{-i/5}},
 \end{equation}
@@
  \hline
- $y$ & $x$ & $\alpha$ & $C_{yx}$ & $a_1$ & $a_2$ & $a_3$ & $b_1$ & $b_2$ & $b_3$ \\
+ $y$ & $x$ & $\alpha$ & $K_{yx}$ & $a_1$ & $a_2$ & $a_3$ & $b_1$ & $b_2$ & $b_3$ \\
  \hline
@@
  $\bar{I}$ & $\bar{Q}$ & $2$ & $0.0089212$ & $10.5910815$ & $-37.4581345$ & $43.1831156$ & $-2.3610288$ & $1.9674667$ & $-0.5678018$\\
- $\bar{C}$ & $\Lambda$ & $-1/5$ & $0.2495709$ & $-919.5651942$ & $330.2848184$ & $-857.1842107$ & $-383.5404843$ & $192.4933832$ & $-811.1425435$\\
- $R$ & $\Lambda$ & $0.6731380$\footnote{Here $\alpha=(n-1)/10$, with $n=7.7313801$ being the fitting coefficient.} & $0.0754339$ & $-12.7153380$ & $58.8217867$ & $-50.3212157$ & $-2.6960056$ & $2.7769172$ & $-1.1317519$\\
+ $C$ & $\Lambda$ & $-1/5$ & $0.2495709$ & $-919.5651942$ & $330.2848184$ & $-857.1842107$ & $-383.5404843$ & $192.4933832$ & $-811.1425435$\\
+ $R$ & $\Lambda$ & $-1/40$ & $8.5752160$ & $-10.5478546$ & $17.3202891$ & $-29.7572150$ & $-9.9777952$ & $21.9091242$ & $-31.7691648$\\
 \hline
@@
  \hline
- $\bar{C}-\Lambda$ & $0.065$ & $0.071975$ & $0.021688$\\
- $R-\Lambda$ & \zc{Anyone?} & $0.497685$ & $0.188783$\\
+ $C-\Lambda$ & $0.065$ & $0.071975$ & $0.021688$\\
+ $R-\Lambda$ & -- & $0.498269$ & $0.17922$\\
  \hline
@@
 \subsection{C-Love Relations}\label{sec:clove}
-In this section we consider approximate C-Love EoS-insensitive relations between NS compactness $\bar{C} \equiv M/R$ and unitless tidal deformability $\Lambda$, as discussed by Yagi and Yunes~\cite{Yagi:binLove}.
+In this section we consider approximate C-Love EoS-insensitive relations between NS compactness $C \equiv M/R$ and unitless tidal deformability $\Lambda$, as discussed by Yagi and Yunes~\cite{Yagi:binLove}.
 In addition, we show the R-Love relations, giving the relationship between NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
@@
 \begin{equation}
-\bar{C} = \sum^2_{k=0} a_k (\ln{\Lambda})^k.
+C = \sum^2_{k=0} a_k (\ln{\Lambda})^k.
 \end{equation}
@@
 \begin{equation}
-\bar{C}^N=C_{\bar{C}\Lambda}\Lambda^{-1/5}.\label{eq:cloveFit}
+C^N=K_{C\Lambda}\Lambda^{-1/5}.\label{eq:cloveFit}
 \end{equation}
@@
 \begin{center} 
-\includegraphics[width=1\columnwidth]{CL.eps}
+\includegraphics[width=.86\columnwidth]{CL.eps}
 \end{center}
@@
 Similar to Fig.~\ref{fig:ILQ} but for C-Love EoS-insensitive relations.
-In this figure, we similarly construct fits to  Eq.~\ref{eq:ILQfitNew}, properly limiting to the newtonian case $\bar{C} \sim \Lambda^{-1/5}$.
+In this figure, we similarly construct fits to  Eq.~\ref{eq:ILQfitNew}, properly limiting to the Newtonian case $C \sim \Lambda^{-1/5}$.
 Observe how, as before, the fractional difference from the fits is greatly suppressed for the constrained case, compared to both the unconstrained case, and results from previous works~\cite{Yagi:binLove}.
@@
 In addition, Fig.~\ref{fig:rlove} displays the relationship between NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
-As can be seen with the unconstrained EoSs, previously this relation was not very universal, and gave large uncertainties ($\sim50\%$ on the mapping from tidal deformability to radius.
-On the other hand, EoSs constrained by GW170817 observe a large decrease in EoS variability to $\sim20\%$.
-Similar to the fits performed for the I-Love-Q and C-Love universal relations, we fit the R-Love relations to Eq.~\ref{eq:ILQfitNew} with a newtonian control factor the same as used in the C-Love case seen in Eq.~\ref{eq:cloveFit}, where the NS mass is substituted with the polytropic form $M\propto R^{(3-n)/(1-n)}$\zc{Anyone have a cite for this?}.
-Absorbing the proprtionality constant into $C_{R\Lambda}$ results in:
+Similar to the fits performed for the I-Love-Q and C-Love EoS insensitive relations, we fit the R-Love relations to Eq.~\ref{eq:ILQfitNew} with a Newtonian control factor the same as used in the C-Love case seen in Eq.~\ref{eq:cloveFit}, where the NS mass is substituted with the polytropic form $M\propto R^{(3-n)/(1-n)}$~\cite{Shapiro:MRpolytrope}.
+Noting that most physical EoSs obey approximate polytropic indices between $0.50$ and $1.00$, as shown in Ref.~\cite{Yagi:binLove}, we choose a central value of $n=0.75$ for use in this analysis, resulting in $M\propto R^9$.
+Absorbing the proportionality constant into $K_{R\Lambda}$ gives the approximate Newtonian relationship as:
 \begin{equation}
-R^N \approx C_{R\Lambda}\Lambda^{(n-1)/10}
+R^N \approx K_{R\Lambda}\Lambda^{-1/40}.
 \end{equation}
-for polytropic index $n$, taken to be an additional fitting constant.
 The results of this fit are displayed in Tab.~\ref{tab:ILQfitNew}, and the maximal EoS variability is again shown in Tab.~\ref{tab:maxVar}.
+As can be seen with the unconstrained EoSs, previously this relation was not very universal, and gave large uncertainties ($\sim50\%$) on the mapping from tidal deformability to radius.
+Now, however, upon the restriction to soft EoSs conforming to GW170817 observe a large decrease in EoS variability to $\sim20\%$, making these relations EoS insensitive to some degree (on the same scale as the binary Love EoS insensitive relations).
 \begin{figure}
@@
 Similar to Fig.~\ref{fig:clove} but for the R-Love relationships between the NS radius and tidal deformability.
-In this figure, we also construct fits to  Eq.~\ref{eq:ILQfitNew}, limiting to the newtonian case $\bar{R} \sim M\Lambda^{1/5}$, with $M\sim R^{(3-n)/(1-n)}$ for polytropic index $n$.
+In this figure, we also construct fits to  Eq.~\ref{eq:ILQfitNew}, limiting to the Newtonian case $\bar{R} \sim M\Lambda^{1/5}$, with $M\sim R^{(3-n)/(1-n)}$ for polytropic index $n$.
 Observe how the fractional difference from the fit is reduced significantly between the unconstrained and constrained sets of EoSs, shown by the comparisons in Tab.~\ref{tab:maxVar}.
@@
 In addition, we find the 90th, 99th, and 100th percentiles on $\lambda_0$ to be $P_{90}=2.06\times10^{-25} \text{ s}^5$, $P_{99}=6.61\times10^{-25} \text{ s}^5$, and $P_{100}=17.36\times10^{-25} \text{ s}^5$ for the constrained EoSs.
-Because the un-binned residuals seen in Fig.~\ref{fig:residuals} are dominated by the low-error regions of parameter space ($\Lambda_s \rightarrow 0$, $\Lambda_s \rightarrow \infty$, $q \rightarrow 0$ and $q \rightarrow 1$) shown by Fig.~\ref{fig:qLsResiduals}, we consider the 90th percentile error for the remainder of the analysis, in order to further take into account the high-error regions of the parameter space ($\Lambda_s \sim 2000$, $q\sim0.5$).
+Because the un-binned residuals seen in Fig.~\ref{fig:residuals} are dominated by the low-error regions of parameter space ($\Lambda_s \rightarrow 0$, $\Lambda_s \rightarrow \infty$, $q \rightarrow 0$ and $q \rightarrow 1$) shown by Fig.~\ref{fig:qLsResiduals}, we consider the 90th percentile error (indicated by the dashed green line in Fig.~\ref{fig:qLsResiduals}) for the remainder of the analysis, in order to further take into account the high-error regions of the parameter space ($\Lambda_s \sim 2000$, $q\sim0.5$).
 We take this value of $P_{90}=2.06\times10^{-25} \text{ s}^5$ to be the systematic measurement error introduced by using the improved binary Love EoS-insensitive relations on the parameter extraction of $\lambda_0$, indicated by the dashed indigo line in Fig.~\ref{fig:stackedFisher}.
@@
 Observe how the error is maximal for $q\sim0.5$ and $\Lambda_s\sim2000$, while it becomes minimal for both low and high values of $q$ and $\Lambda_s$.
+Also shown in the figure is the 90th percentile of the un-binned residuals seen in Fig.~\ref{fig:residuals}, taken to be the overall systematic uncertainty introduced by using binary Love EoS insensitive relations.
 }
@@
 Spectral noise densities are plotted from $f_{\text{min}}=(23,10,10,7,1,1) \text{ Hz}$, respectively, to $f_{\text{max}}=1649 \text{ Hz}$.
-Also shown is $2 \sqrt{f}$ multiplied by the amplitude of the PhenomD~\cite{PhenomDI,PhenomDII} waveform template, modified by two different tidal corrections used in our Fisher analyses: the 6PN tidal correction from Ref.~\cite{Wade:tidalCorrections}, as well as the NRTidal tidal correction found in Ref.~\cite{Samajdar:NRTidal} (this makes a negligable difference in the above figure).
+Also shown is $2 \sqrt{f}$ multiplied by the amplitude of the PhenomD~\cite{PhenomDI,PhenomDII} waveform template.
 }
@@
 \item Perform a Fisher analysis as outlined above using $S_n^A(f)$, while restricting the luminosity distance $D_L$ such that $\rho^{\text{O2}}_{\text{GW170817}}=32.4$ would be achieved on O2 sensitivity $S_n^{\text{O2}}(f)$.
-Here we assume low spin priors $|\chi| \leq 0.05$, as well as $0 \leq \lambda_0 \leq 5 \times 10^{-23} \text{ s}^5$ and $-5 \times 10^{-18} \text{ s}^4\text{ M}_{\odot} \leq \lambda_1 \leq 0$~\cite{delPozzo:TaylorTidal}.
+Here we assume low spin priors $|\chi| \leq 0.05$, as well as $0 \text{ s}^5 \leq \lambda_0 \leq 5 \times 10^{-23} \text{ s}^5$ and $-5 \times 10^{-18} \text{ s}^4\text{ M}_{\odot} \leq \lambda_1 \leq 0 \text{ s}^4\text{ M}_{\odot}$~\cite{delPozzo:TaylorTidal}.
 This results in SNR $\rho^A_{\text{GW170817}}$ and statistical error $\sigma_\text{GW170817}^A$ accrued in the extraction of $\lambda_0$ on detector $A$.
@@
 where $\sigma_i^A(z)$ is computed by the relations $\sigma_i^A \times \rho_i^A = \sigma_{\text{GW170817}}^A \times \rho_{\text{GW170817}}^A$.
+\item \zc{These bullet points are getting kind of long and detailed. They (at least the low-level version of them) could go in a new appendix section - let me know what everyone thinks :)}
 \end{itemize}
@@
 
-Concluding, we find that the Voyager, ET, and CE detectors all exhibit enough uncertainty reduction that the systematics on $\lambda_0$ introduced from using improved EoS-insensitive relations (found to be $12.014$) no longer become negligible in the error budget.
+Concluding, we find that the Voyager, ET, and CE detectors all exhibit enough uncertainty reduction that the systematics on $\lambda_0$ introduced from using improved EoS-insensitive relations (found to be $2.06 \times 10^{-25}\text{ s}^5$) no longer become negligible in the error budget.
 This was also shown for the case of $\tilde\Lambda$, only taking into account single observed events, where ET and CE detectors both observe comparable statistical and systematic errors on $\tilde\Lambda$.
@@
 
-\zc{Discuss with group on possible avenues of future work.}
+Future work on this subject entails an investigation into the improvement of alternative EoS insensitive relations, such as the multipole Love relations between various $l$-th order electric, magnetic, and shape tidal deformabilities as discussed in Ref.~\cite{Yagi:Multipole}.
+Additionally, Lackey \emph{et al}. presented surrogate models of non-spinning effective-one-body waveform models with the the use of universal relations in Refs.~\cite{Lackey:Surrogate, Lackey:EOB}.
+By reducing the number of required waveform model parameters, surrogate models aid in the extraction of NS observables from GW detections.
+The improvement of multipole love EoS insensitive relations can then be used to increase the accuracy of surrogate models.
 
@@
 
-\begin{figure*}
+\begin{figure}
 \begin{center} 
@@
 Measurement accuracy of $\tilde\Lambda$ as a function of increasing mass ratio $q$ for interferometer sensitivities O2, aLIGO, A\texttt{+}, Voyager, CE, and ET.
-Evaluated at a fixed chirp mass of $\mathcal{M}=1.188\text{ M}_{\odot}$ corresponding to GW170817, this is repeated for three cases: (i) (left) with correlations between all template waveform parameters $\theta^a$ intact; (ii) (center) with the correlations between $\tilde\Lambda$ and $\delta\tilde\Lambda$ removed; and (iii) (right) with correlations between all parameters removed.
+Evaluated at a fixed chirp mass of $\mathcal{M}=1.188\text{ M}_{\odot}$ corresponding to GW170817, this is repeated for three cases: (i) (top) with correlations between all template waveform parameters $\theta^a$ intact; (ii) (center) with the correlations between $\tilde\Lambda$ and $\delta\tilde\Lambda$ removed; and (iii) (bottom) with correlations between all parameters removed.
 The removal of parameter correlations is approximated by setting certain Fisher matrix elements to 0, as described in Appendix.~\ref{app:measurement}.
@@
 \label{fig:massVariation}
-\end{figure*}
+\end{figure}
 

### 2019-01-15 paper/go.sh

@@ -1,6 +1,5 @@
 #!/bin/bash
 echo "Compiling.."
-rm *blg *log *aux *Notes* *bbl output.text
 pdflatex --shell-escape bin-love-after-gw170817.tex > output.text
 echo "~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~" >> output.text
 pdflatex --shell-escape bin-love-after-gw170817.tex >> output.text
@@ -10,5 +9,6 @@ echo "~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~" >> out
 pdflatex --shell-escape bin-love-after-gw170817.tex >> output.text
 echo "~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~" >> output.text
 pdflatex --shell-escape bin-love-after-gw170817.tex >> output.text
+rm *blg *log *aux *Notes* *bbl output.text *out
 echo "Done. Enjoy your PDF!"
 evince bin-love-after-gw170817.pdf &

### 2019-01-15 paper/bin-love-after-gw170817.tex
added a few comments up to Sec B

@@
 This internal structure of such stars, known as the equation of state (EoS), is exceedingly important, as it is the determining factor for many NS observables - such as the mass, the radius, and many more.
-Unfortunately, terrestrial experiments can only study the EoS to around the nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy} (although some temperature-dependent heavy-ion collision experiments may probe higher densities \zc{Katerina do you know of any papers on this?}), making NSs ideal laboratories for constraining ultra dense nuclear matter.
+Unfortunately, terrestrial experiments can only study the EoS to around the nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy} (although some temperature-dependent heavy-ion collision experiments may probe higher densities \zc{Katerina do you know of any papers on this?} {\ny{Look up the PREX and CREX experiments at JLab (a good author is Horowitz, e.g.
+Abrahamyan:2012gp, Horowitz:2012tj, Horowitz:2013wha)}}), making NSs ideal laboratories for constraining ultra dense nuclear matter.
 
@@
 We can discuss this further if anyone doesn't want it included :)}
+{\ny{I'm ok with keeping this, but let's get the science finished first.}}
 %What we did
@@
 \end{equation}
-Using this formalism, any valid EoS can be approximated through choice of 4 or more spectral coefficients $\gamma_k$, tabulated for several common EoSs in Table 1 of~\cite{Lindblom:2018rfr}.
+Using this formalism, any valid EoS can be approximated through the choice of 4 or more spectral coefficients $\gamma_k$, tabulated for several common EoSs in Table 1 of~\cite{Lindblom:2018rfr}.
 
@@
 Current gravitational wave interferometry is not yet sensitive enough to accurately extract both tidal parameters $\tilde{\Lambda}$ and $\delta\tilde{\Lambda}$.
-In a search to remedy this, important previous work by Yagi and Yunes~\cite{Yagi:binLove} found that symmetric and antisymmetric combinations of tidal deformabilities:
+In a search to remedy this, Yagi and Yunes~\cite{Yagi:binLove} found that symmetric and antisymmetric combinations of tidal deformabilities:
 \begin{equation}
@@
 display EoS-insensitive properties to a high degree, showing EoS variations up to 20\% for binaries with masses less than $1.7 \text{ M}_{\odot}$, for a representative set of 11 EoSs. 
-These relations, known as ``binary Love EoS insensitive relations" allows one to break degeneracies between coupled tidal parameters.
+These ``binary Love relations" allow one to break degeneracies between coupled tidal parameters.
 This is important for two reasons: (i) allows us to algebraically eliminate tidal parameters from the template parameter list, improving parameter estimation, and (ii) automatic measurement of second tidal parameter given observation of the first.
@@
 
-Similar EoS-insensitive relations have been found to exist between individual NS observables: moment of inertia (I), tidal deformability (Love), quadrupole moment (Q), and compactness (C), known as the ``I-Love-Q" and ``C-Love" EoS-insensitive relations~\cite{Yagi:ILQ, Yagi:binLove}.
+Similar EoS-insensitive relations have been found to exist between individual NS observables: moment of inertia (I), tidal deformability (Love), quadrupole moment (Q), and compactness (C), known as the ``I-Love-Q" and ``C-Love" relations~\cite{Yagi:ILQ, Yagi:binLove}.
 These have been found to be EoS insensitive by up to 1\% and 6.5\% respectively.
@@
 In particular, we consider two distinct classes of NSs: nuclear matter EoSs and hybrid quark-hadron star EoSs as described in Sec.~\ref{sec:theory}.
-We begin in Sec.~\ref{sec:ilq-nuc} by fitting the new I-Love-Q EoS-insensitive relations using the constrained set of EoSs.
+We begin in Sec.~\ref{sec:ilq-nuc} by fitting the new I-Love-Q relations using the constrained set of EoSs.
 This is followed in Sec.~\ref{sec:ilq-hyb} by an analysis and discussion into how well hybrid stars agree with the improved binary Love relations.
+
+{\ny{Overall, let's not call these relations ``I-Love-Q EOS insensitive relations'' or ``binary love EOS insensitive relations.''  It's much better to be brief and simply call them I-Love-Q relations and Binary Love relations (like is done in the literature).
+It should be clear when we define them that they are EOS insensitive}}
 
@@
 
-Fig.~\ref{fig:ILQ} shows the improved I-Love EoS-insensitive relations between the dimensionless moment of inertia $\bar{I} \equiv I/M^3$, the dimensionless quadrupole moment $\bar{Q} \equiv Q/M^3$, and the dimensionless tidal deformability $\Lambda$ for both the constrained and unconstrained sets of EoSs (each with individual fits pertaining to only that set of EoSs).
+Fig.~\ref{fig:ILQ} shows the improved I-Love EoS-insensitive relations between the dimensionless moment of inertia $\bar{I} \equiv I/M^3$, the dimensionless quadrupole moment $\bar{Q} \equiv Q/M^3$, and the dimensionless tidal deformability $\Lambda$ for both the constrained and unconstrained sets of EoSs (each with individual fits pertaining to only that set of EoSs {\ny{I think we should here say which fit we are using (I think you are using the new one.)}}).
 We observe that the constrained EoSs show considerable improvement from both the results of previous works~\cite{Yagi:ILQ}, and from the unconstrained EoSs.
@@
 Further, we observe that the universality can not be improved by much through the introduction of new fits, only bringing the max EoS variation down to $\sim1$\% for the fits constructed with only hybrid star EoSs.
-Concluding, we claim that hybrid star EoSs \emph{do} obey the I-Love-Q EoS-insensitive relations computed through nuclear EoS data, with the exception that the universality goes up to $\sim1.7$\%.
+Concluding, we claim that hybrid star EoSs \emph{do} obey the I-Love-Q EoS-insensitive relations computed through nuclear EoS data, but the lack of universality goes up to $\sim1.7$\%.
+
+{\ny{This is a bit strange, but probably still correct. But ``this'' I mean the fact that when you fit only to the hybrid stars you do not get better than $1\%$ universality. Why is this?}}
+
+{\ny{UP TO HERE}}
 

### 2019-01-16 paper/bin-love-after-gw170817.tex
added comments

@@
 % What was done before - Binary Love
-Previous studies have shown that approximately EoS-insensitive ``binary Love EoS insensitive relations" exist between symmetric and antisymmetric combinations of individual tidal deformabilities, which are difficult to be independently measured with second-generation gravitational wave interferometers.
+Previous studies have shown that approximately EoS-insensitive ``binary Love relations" exist between symmetric and antisymmetric combinations of individual tidal deformabilities, which are difficult to be independently measured with second-generation gravitational wave interferometers.
 % What was done before - I-Love-Q
-Similarly, another set of EoS-insensitive relations exist between individual neutron star parameters: moment of inertia (I), tidal deformability (Love number), quadrupole moment (Q), and compactness (C) - known as the ``I-Love-Q" and ``C-Love" EoS insensitive relations.
+Similarly, another set of EoS-insensitive relations exist between individual neutron star parameters: moment of inertia (I), tidal deformability (Love number), quadrupole moment (Q), and compactness (C) - known as the ``I-Love-Q" and ``C-Love" relations.
 % What universal relations do
@@
 However, even the most precise of EoS insensitive relations carry EoS variation which inject systematic errors into the parameter extraction process.
-In this document, we explain how one can reduce equation of state variation for I-Love-Q, C-Love, and binary Love EoS-insensitive relations, which helps to reduce systematic errors on the tidal measurement of binary neutron star mergers.
+In this document, we explain how one can reduce equation of state variation for I-Love-Q, C-Love, and binary Love relations, which helps to reduce systematic errors on the tidal measurement of binary neutron star mergers.
 However, we show that the systematic effects of these relations is very small until next-generation detectors. 
@@
 %Intro
+
+{\ny{Just some general comments so that we don't forget:
+\begin{itemize}
+\item The EoS-insensitive relations are called ``binary Love'', ``I-Love-Q'', ``C-Love'' and ``R-Love.'' There is no need to call them ``binary Love EoS-insensitive relations.'' That's too verbose and not what they are called in the literature.
+I am ok with describing these relations as EoS-insensitive instead of approximately universal, but let's not change the names.
+\item There is some serious tidying up that needs to be done to all of the text.
+Specifically, there are missing prepositions, like ``the'', in lots of places that makes the reading a bit choppy and we can improve.
+Zack, when you have a chance, please do a detail read through and fix the flow as much as you can.
+\item Eventually, we need to discuss the abstract and the intro in more detail. 
+\item Let's not forget to check the acknowledgements for funding sources. 
+\item Let's do a spell check. 
+\item Let's remove all commented out text.  
+\end{itemize}
+}}
 The dependence of pressure on density for cold supranuclear matter found inside neutron stars (NSs) remains to be one of the largest mysteries in both nuclear physics and astrophysics.
@@
 Use of these relations leads to up to an order of magnitude improvement in parameter estimation of $\Lambda_s$ through a simple Fisher analysis~\cite{Yagi:binLove}, also confirmed with the detailed analysis of~\cite{Katerina:residuals}.
-Similar ``I-Love-Q" and ``C-Love" EoS-insensitive relations~\cite{Yagi:ILQ} have been found between individual NS observables: quadrupole moment , moment of inertia, tidal deformability, and compactness; similarly allowing the removal of tidal parameters from the model list, and allowing an automatic determination of one observable through the measurement of another.
+Similar ``I-Love-Q" and ``C-Love" relations~\cite{Yagi:ILQ} have been found between individual NS observables: quadrupole moment , moment of inertia, tidal deformability, and compactness; similarly allowing the removal of tidal parameters from the model list, and allowing an automatic determination of one observable through the measurement of another.
 However, these EoS-insensitive relations have been tuned to a collection of EoS models, and each have intrinsic uncertainties associated with their use.
@@
 In this analysis, we aim to improve this important work by imposing the restrictions found on the EoS~\cite{LIGO:posterior} derived from the recent binary NS merger observation, GW170817~\cite{TheLIGOScientific:2017qsa}.
-By restricting to only EoSs which lie within the the 90\% credible region on pressure as a function of density found in~\cite{LIGO:posterior}, we repeat the analyses done in~\cite{Yagi:binLove,Yagi:ILQ} and show an increase in universality for I-Love-Q, C-Love, and binary Love EoS-insensitive relations.
+By restricting to only EoSs which lie within the the 90\% credible region on pressure as a function of density found in~\cite{LIGO:posterior}, we repeat the analyses done in~\cite{Yagi:binLove,Yagi:ILQ} and show an increase in universality for I-Love-Q, C-Love, and binary Love relations.
 We also investigate the relationship between the NS radius and its tidal deformability, or the R-Love relations, determining if the uncertainties can be reduced.
@@
 %What we did
-In this paper we attempt to improve I-Love-Q, C-Love, and binary Love EoS-insensitive relations by imposing constraints on the EoS found by GW170817~\cite{LIGO:posterior,TheLIGOScientific:2017qsa}.
+In this paper we attempt to improve I-Love-Q, C-Love, and binary Love relations by imposing constraints on the EoS found by GW170817~\cite{LIGO:posterior,TheLIGOScientific:2017qsa}.
 First, we generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, where we (i) impose the restriction that they must be drawn from GW170817s 90\% credible posterior in pressure as a function of density, and (ii) don't impose any restrictions for comparison purposes.
 Next, we follow the important works of~\cite{Yagi:binLove} and~\cite{Yagi:ILQ} to show how the ``constrained" set of EoSs show improved universality (binary Love, I-Love-Q, and C-Love) from both the previous works, and the ``unconstrained" sample, shown by Fig.~\ref{fig:ILQ}.
-In addition, we determine the degree to which hybrid star EoSs obey binary Love EoS-insensitive relations.
+In addition, we determine the degree to which hybrid star EoSs obey binary Love relations.
 Finally, through a simple Fisher analysis, we consider the value in improving EoS-insensitive relations by approximating when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in EoS-insensitive relations.
@@
 We also present new R-Love relations displaying the relationship between NS radius and tidal deformability, showing maximum EoS variability of $18.88\%$ from the fit discussed in Sec.~\ref{sec:clove}.
-Additionally, we find that hybrid quark-hadron stars do obey the I-Love-Q and C-Love EoS-insensitive relations, with sightly increased EoS variability.
+Additionally, we find that hybrid quark-hadron stars do obey the I-Love-Q and C-Love relations, with sightly increased EoS variability.
 We also find that binaries consisting of one massive hybrid star, and one small-mass hadronic star do not agree with derived binary Love relations, due to the large separation in $\tilde{\Lambda}$ between the constituent stars.
@@
 These values are further tabulated in Table~\ref{tab:variances}.
-It can be seen from this figure that the statistical errors from parameter extraction become comparable the EoS-insensitive relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love EoS-insensitive relations will become necessary.
+It can be seen from this figure that the statistical errors from parameter extraction become comparable the EoS-insensitive relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love relations will become necessary.
 Also shown in the figure is the same measurement uncertainties upon the injection of the PhenomD + NRTidal waveform, rather than the PhenomD + 6PN tidal correction to demonstrate the effect of waveform mismodeling.
@@
 We begin with a complementary background and theory material in Sec.~\ref{sec:theory}.
-We continue in Sec.~\ref{sec:universal} by finding new and improved binary Love, I-Love-Q, and C-Love EoS-insensitive relations, and considering how well hybrid star EoSs agree with the EoS-insensitive relations.
+We continue in Sec.~\ref{sec:universal} by finding new and improved binary Love, I-Love-Q, and C-Love relations, and considering how well hybrid star EoSs agree with the EoS-insensitive relations.
 We next examine these improved EoS-insensitive relations and question whether or not they are useful for future interferometers in Sec.~\ref{sec:observations}.
@@
 This is important for two reasons: (i) allows us to algebraically eliminate tidal parameters from the template parameter list, improving parameter estimation, and (ii) automatic measurement of second tidal parameter given observation of the first.
-It was shown through a simple Fisher analysis that the use of binary Love EoS-insensitive relations improved parameter extraction on $\tilde{\Lambda}$ by an order of magnitude.
+It was shown through a simple Fisher analysis that the use of binary Love relations improved parameter extraction on $\tilde{\Lambda}$ by an order of magnitude.
 
@@
 
-{\ny{Overall, let's not call these relations ``I-Love-Q EOS insensitive relations'' or ``binary love EOS insensitive relations.''  It's much better to be brief and simply call them I-Love-Q relations and Binary Love relations (like is done in the literature).
+{\ny{Overall, let's not call these relations ``I-Love-Q relations'' or ``binary love relations.''  It's much better to be brief and simply call them I-Love-Q relations and Binary Love relations (like is done in the literature).
 It should be clear when we define them that they are EOS insensitive}}
@@
 \caption{
-Updated fit parameters for the I-Love-Q EoS-insensitive relations, fitted to the constrained EoS data by the curve found in Eq.~\ref{eq:ILQfit}.
+Updated fit parameters for the I-Love-Q relations, fitted to the constrained EoS data by the curve found in Eq.~\ref{eq:ILQfit}.
 }\label{tab:ILQfit}
@@
 \caption{
-I-Love-Q, C-Love, and R-Love EoS-insensitive relations fit parameters for the constrained EoS data using the improved fitting relations found in Eq.~\ref{eq:ILQfitNew}.
+I-Love-Q, C-Love, and R-Love relations fit parameters for the constrained EoS data using the improved fitting relations found in Eq.~\ref{eq:ILQfitNew}.
 This fitting relation, unlike previous versions, properly limits to the Newtonian case as $\Lambda \rightarrow \infty$.
@@
 
-Fig.~\ref{fig:ILQ} shows the improved I-Love EoS-insensitive relations between the dimensionless moment of inertia $\bar{I} \equiv I/M^3$, the dimensionless quadrupole moment $\bar{Q} \equiv Q/M^3$, and the dimensionless tidal deformability $\Lambda$ for both the constrained and unconstrained sets of EoSs (each with individual fits pertaining to only that set of EoSs {\ny{I think we should here say which fit we are using (I think you are using the new one.)}}).
+Fig.~\ref{fig:ILQ} shows the improved I-Love relations between the dimensionless moment of inertia $\bar{I} \equiv I/M^3$, the dimensionless quadrupole moment $\bar{Q} \equiv Q/M^3$, and the dimensionless tidal deformability $\Lambda$ for both the constrained and unconstrained sets of EoSs (each with individual fits pertaining to only that set of EoSs {\ny{I think we should here say which fit we are using (I think you are using the new one.)}}).
 We observe that the constrained EoSs show considerable improvement from both the results of previous works~\cite{Yagi:ILQ}, and from the unconstrained EoSs.
 This is further validated in Tab.~\ref{tab:maxVar}, where the maximal EoS variation from each fit is tabulated; comparing the results of previous works to the unconstrained, and constrained sets of EoSs.
-Observe how the constrained EoSs outperform both other cases by a considerable amount for each I-Love-Q EoS-insensitive relation.
+Observe how the constrained EoSs outperform both other cases by a considerable amount for each I-Love-Q relation.
 
@@
 \caption{
-Individual I-Love EoS-insensitive relations $\bar{I}-\Lambda$ (left), $\bar{Q}-\Lambda$ (center), and $\bar{I}-\bar{Q}$ (right), shown for both the constrained EoSs (solid green) and unconstrained EoSs (dotted maroon).
+Individual I-Love relations $\bar{I}-\Lambda$ (left), $\bar{Q}-\Lambda$ (center), and $\bar{I}-\bar{Q}$ (right), shown for both the constrained EoSs (solid green) and unconstrained EoSs (dotted maroon).
 In these figures, the black dashed lines corresponds to the fits given by Eq.~\ref{eq:ILQfitNew} (note: each panel contains individual fits for the constrained and unconstrained EoSs, indistinguishable on such a large scale).
@@
 Additionally shown in this figure is the fractional difference from the nuclear matter fits for the 10 hybrid star EoSs (dashed green).
+{\ny{These figures are all too heavy and they make the scrolling of the pdf difficult.
+Can you downgrade their resolution or save them as pdf please?}}
 }
@@
 
-Observe how the hybrid star EoSs do obey the I-Love-Q EoS-insensitive relations up to $\sim1.7$\%, slightly higher than that found here for nuclear matter EoSs, as well as that found in previous works~\cite{Yagi:ILQ}.
+Observe how the hybrid star EoSs do obey the I-Love-Q relations up to $\sim1.7$\%, slightly higher than that found here for nuclear matter EoSs, as well as that found in previous works~\cite{Yagi:ILQ}.
 Further, we observe that the universality can not be improved by much through the introduction of new fits, only bringing the max EoS variation down to $\sim1$\% for the fits constructed with only hybrid star EoSs.
-Concluding, we claim that hybrid star EoSs \emph{do} obey the I-Love-Q EoS-insensitive relations computed through nuclear EoS data, but the lack of universality goes up to $\sim1.7$\%.
-
-{\ny{This is a bit strange, but probably still correct. But ``this'' I mean the fact that when you fit only to the hybrid stars you do not get better than $1\%$ universality. Why is this?}}
-
-{\ny{UP TO HERE}}
+Concluding, we claim that hybrid star EoSs \emph{do} obey the I-Love-Q relations computed through nuclear EoS data, but the lack of universality goes up to $\sim1.7$\%.
+
+{\ny{This is a bit strange, but probably still correct.
+But ``this'' I mean the fact that when you fit only to the hybrid stars you do not get better than $1\%$ universality.
+If I look at the hybrid curves alone, they look like the same simple lines as in the neutron star case (but of course a $1\%$ difference wouldn't show on this scale).
+Why is it that we can lower fractional difference in the NS case but not in the hybrid case?}}
+
+{\ny{Can I see the relative fractional different between each fit and the data for hybrid stars only?
+(ie.
+the analogous thing to the green dashed lines of the figure below, but also with the fits to the total set, to just the hybrids and to just the neutron stars.) I wonder whether there is any improvement at all when you fit just to hybrid stars or whether there are any features.}}
 
 \subsection{C-Love Relations}\label{sec:clove}
-In this section we consider approximate C-Love EoS-insensitive relations between NS compactness $C \equiv M/R$ and unitless tidal deformability $\Lambda$, as discussed by Yagi and Yunes~\cite{Yagi:binLove}.
+In this section we consider approximately EoS-insensitive C-Love relations between NS compactness $C \equiv M/R$ and unitless tidal deformability $\Lambda$, as discussed by Yagi and Yunes~\cite{Yagi:binLove}.
 In addition, we show the R-Love relations, giving the relationship between NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
@@
 
-Figure~\ref{fig:clove} presents the C-Love EoS-insensitive relations for both the constrained and unconstrained sets of EoSs, along with the relative fractional difference from the fits. 
+Figure~\ref{fig:clove} presents the C-Love relations for both the constrained and unconstrained sets of EoSs, along with the relative fractional difference from the fits. 
 Observe how the constrained EoSs show a large suppression in EoS variability compared to both the unconstrained EoSs, as well as that found in previous works~\cite{Yagi:binLove}.
@@
 \caption{
-Similar to Fig.~\ref{fig:ILQ} but for C-Love EoS-insensitive relations.
+Similar to Fig.~\ref{fig:ILQ} but for C-Love relations.
 In this figure, we similarly construct fits to  Eq.~\ref{eq:ILQfitNew}, properly limiting to the Newtonian case $C \sim \Lambda^{-1/5}$.
@@
 In addition, Fig.~\ref{fig:rlove} displays the relationship between NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
-Similar to the fits performed for the I-Love-Q and C-Love EoS insensitive relations, we fit the R-Love relations to Eq.~\ref{eq:ILQfitNew} with a Newtonian control factor the same as used in the C-Love case seen in Eq.~\ref{eq:cloveFit}, where the NS mass is substituted with the polytropic form $M\propto R^{(3-n)/(1-n)}$~\cite{Shapiro:MRpolytrope}.
+Similar to the fits performed for the I-Love-Q and C-Love relations, we fit the R-Love relations to Eq.~\ref{eq:ILQfitNew} with a Newtonian control factor the same as used in the C-Love case seen in Eq.~\ref{eq:cloveFit}, where the NS mass is substituted with the polytropic form $M\propto R^{(3-n)/(1-n)}$~\cite{Shapiro:MRpolytrope}.
 Noting that most physical EoSs obey approximate polytropic indices between $0.50$ and $1.00$, as shown in Ref.~\cite{Yagi:binLove}, we choose a central value of $n=0.75$ for use in this analysis, resulting in $M\propto R^9$.
@@
 As can be seen with the unconstrained EoSs, previously this relation was not very universal, and gave large uncertainties ($\sim50\%$) on the mapping from tidal deformability to radius.
-Now, however, upon the restriction to soft EoSs conforming to GW170817 observe a large decrease in EoS variability to $\sim20\%$, making these relations EoS insensitive to some degree (on the same scale as the binary Love EoS insensitive relations).
+Now, however, upon the restriction to soft EoSs conforming to GW170817 observe a large decrease in EoS variability to $\sim20\%$, making these relations EoS insensitive to some degree (on the same scale as the binary Love relations).
 \begin{figure}
@@
 \subsubsection{Hybrid quark-hadron stars}\label{sec:clove-hyb}
-In this section, we consider the effect of hybrid star EoSs on the C-Love EoS-insensitive relation.
+In this section, we consider the effect of hybrid star EoSs on the C-Love relation.
 Much like Sec.~\ref{sec:ilq-hyb}, we perform 3 separate fits (constrained and hybrid EoSs combined, constrained EoSs only, and hybrid EoSs only) and compare the maximal EoS variation for each class of EoSs.
@@
 We observe very similar behavior to that described in Sec.~\ref{sec:ilq-hyb}, in which the maximal EoS variation for hybrid stars only fluctuate slightly ($\sim 4.5\% - 7\%$) for each case.
-From this, we similarly conclude that hybrid stars do obey the C-Love EoS-insensitive relation derived with nuclear matter stars, with the caveat that the maximum universality increases to $\sim 7.1\%$.
+From this, we similarly conclude that hybrid stars do obey the C-Love relation derived with nuclear matter stars, with the caveat that the maximum universality increases to $\sim 7.1\%$.
 This is exemplified in Fig.~\ref{fig:clove} by the dashed green curves.
@@
 
+{\ny{let's in general drop the sig figs everywhere, e.g. in 30.82 percent.}}
+
 \begin{table}
@@
 \caption{
-Similar to Tab.~\ref{tab:hybridCompare} but for the C-Love EoS-insensitive relation.
+Similar to Tab.~\ref{tab:hybridCompare} but for the C-Love relation.
 Observe how for all 3 cases, the hybrid EoSs are only universal up to a minimum of $\sim1$\%, while in each case the constrained EoSs outperform the hybrid ones.
@@
 \subsection{Binary love relations}\label{sec:binary}
-Next we consider improvements to the binary Love EoS-insensitive relations.
+Next we consider improvements to the binary Love relations.
 Similar to Sec.~\ref{sec:ilq}, we consider two classes of NSs: nuclear matter EoSs and hybrid quark-hadron star EoSs~\cite{Paschalidis2018,Alford:2017qgh,1971SvA....15..347S,Zdunik:2012dj,Alford:2013aca}.
@@
 The updated fit parameters can be found in Table~\ref{tab:binLovefit}.
-Notice how, unlike the individual NS I-Love-Q EoS-insensitive relations, these relations also depend on the ratio of constituent masses in the binary system.
+Notice how, unlike the individual NS I-Love-Q relations, these relations also depend on the ratio of constituent masses in the binary system.
 \begin{table*}
@@
 \caption{
-Updated fit parameters for the binary Love EoS-insensitive relations, as given by the curve found in Eq.~\ref{eq:binLovefit}.
+Updated fit parameters for the binary Love relations, as given by the curve found in Eq.~\ref{eq:binLovefit}.
 The bottom row corresponds to separate fits corresponding to the hybrid star branch of the hybrid EoSs.
@@
 
-Fig.~\ref{fig:binLove} shows the improved binary Love EoS-insensitive relation for 3 different mass ratios: $q=0.9$, $q=0.75$, and $q=0.5$ for both constrained and unconstrained sets of EoSs.
+{\ny{Overall, if you start a sentence, you should spell out Figure or Section or Equation.}}
+
+Fig.~\ref{fig:binLove} shows the improved binary Love relation for 3 different mass ratios: $q=0.9$, $q=0.75$, and $q=0.5$ for both constrained and unconstrained sets of EoSs.
 In this figure we show the absolute difference from the fit, rather than the fractional difference, so one can see which regions of $\Lambda_s$ display the largest actual difference.
@@
 
+{\ny{I get why you are plotting the absolute difference but 
+\begin{itemize}
+\item[(i)] everywhere else in the paper you are plotting the relative fractional difference, so a reader that doesn't pay much attention (and say misses the 1 sentence in the paragraph above -- by the way, I think the caption is wrong and should say the absolute difference instead of the fractional difference, no?
+--) will look at the axis and say: Wow!
+100\% error...that's bad!.
+This is a problem, I don't have a solution for it (except for reverting to relative fractional differences) but it should not be ignored.
+\item[(ii)] it is hard to see easily what this error means in terms of EoS-variability.
+Say for example we pick the q=0.9 hybrid star case at Lambdas of 100.
+I can easily read that there is EoS variability of about 20.
+But to see if this 20 is a lot or a little, I have to compare with the top figure, from which I get that Lambdaa is about 60 or 70 (if I use a ruler on my computer screen).
+Now I have to take these two approximate numbers and compare them, but because they are approximate, it's hard to see whether this is a 30 per cent difference, a 50 percent difference or what.
+\end{itemize}
+}}
+
+{\ny{I must have missed something. Why do the unconstrained magenta lines extend way passed the constrained green lines? I didn't see this discussed anywhere.}}
+
 \begin{figure}
@@
 \caption{
-Binary Love EoS-insensitive relations shown for the constrained EoSs (dotted maroon) and unconstrained EoSs (solid green) for various values of mass ratio: $q=0.9$, $q=0.75$, and $q=0.50$.
+Binary Love relations shown for the constrained EoSs (dotted maroon) and unconstrained EoSs (solid green) for various values of mass ratio: $q=0.9$, $q=0.75$, and $q=0.50$.
 In this figure, the top panel displays the EoS-insensitive relations with fits given by Eq.~\ref{eq:binLovefit} shown by dashed black lines (note there are 2 fits for each mass ratio, corresponding to the constrained and unconstrained sets of EoSs), while the bottom 3 panels correspond to the absolute EoS variation for each mass ratio.
@@
 These transitions result in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq M_{\text{tr}}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote this as ``HS"), and (ii) small-mass ($M \leq M_{\text{tr}}$) hadronic stars with no internal transition to quark matter (we denote this as ``NS").
+{\ny{ooohh...I'm not sure I like the acronyms here.
+NS typically stands for ``neutron star'' of standard type, like what you would construct from an APR EoS.
+But here by NS you mean a low-mass neutron star specifically.
+Let's pick a better acronym.}}
 We consider 3 classes of binaries:
@@
 
-To determine how each of class of binary NSs obey our improved binary Love EoS-insensitive relations, we pick a representative set of 10 binary pairs from each class, for the ACB5 hybrid EoS, with a transition at $1.4 \text{ M}_{\odot}$.
+To determine how each of class of binary NSs obey our improved binary Love relations, we pick a representative set of 10 binary pairs from each class, for the ACB5 hybrid EoS, with a transition at $1.4 \text{ M}_{\odot}$.
 Binary Love values are then computed for each pair, then residuals from the binary Love curve found in Sec.~\ref{sec:binLove-nuclear} are determined and compared to that from the constrained set of EoSs.
@@
 2 of Ref.~\cite{Paschalidis2018}: when one star lies on the hadronic branch while the other is on the quark branch, they each see vast differences in $\tilde{\Lambda}$ - disrupting the binary Love relations as found for stars on the hadronic branch.
+{\ny{Sorry, I don't get it.
+Why does seeing ``a vast difference in Lambda tilde'' explain the loss of universality?
+We have cases with small enough q that show much more universality than what we find for the same value of q in the HS/NS case.
+I guess what I am saying is that we should explore this more from a theory side to try to provide an explanation, or we should say nothing (or say we don't know why this is the case).}}
 
@@
 Observe how the residuals from the fit are quite good for low pressures (large $\Lambda_s$) when the the binaries consist of a NS/NS combination, before reaching the transitional pressure when the deviations become increasingly large ($\sim160$\% for $q=0.90$, $\sim37$\% for $q=0.75$, and $\sim6$\% for $q=0.50$) for HS/HS and HS/NS binaries.
+{\ny{Why is there a hump for the HS cases in green in Fig.
+7?}}
 
@@
 By separating the two branches of the hybrid EoSs, we find a new ``hybrid" branch binary Love fit which gives consistent results to that found for the nuclear matter fits.
+{\ny{But wait, the Newtonian limit is not valid for this hybrid branch, since you are not allowed to go to low enough central densities, right?
+If so, what are you using for the controlling factor?
+I found the description in the 2 paragraphs above a bit muddled and short.
+It is not exactly clear to me what the message you were trying to send was.}}
 
 \subsubsection{Error Marginalization}
+
+{\ny{This section seems out of place here, as it really matters for the next section. We shoudl consider re-structuring.}}
+
 We have now shown that binary NS merger observations can help improve EoS-insensitive relations - the question is: is it worth it?
@@
 
-In this section, we investigate the residuals in $\lambda_0(\Lambda_a,\Lambda_s,q)$ in order to marginalize over the intrinsic error in the binary Love EoS-insensitive relations.
+In this section, we investigate the residuals in $\lambda_0(\Lambda_a,\Lambda_s,q)$ in order to marginalize over the intrinsic error in the binary Love relations.
 In particular, we restrict our focus to only the constrained set of EoSs.
@@
 \caption{
-Coefficients to the fits given by Eqs. (\ref{eq:margFit1})-(\ref{eq:margFit4}) for the relative error on $\lambda_0$ in the improved binary Love EoS-insensitive relations presented in this paper.
+Coefficients to the fits given by Eqs. (\ref{eq:margFit1})-(\ref{eq:margFit4}) for the relative error on $\lambda_0$ in the improved binary Love relations presented in this paper.
 }\label{tab:marginalized}
@@
 Because the un-binned residuals seen in Fig.~\ref{fig:residuals} are dominated by the low-error regions of parameter space ($\Lambda_s \rightarrow 0$, $\Lambda_s \rightarrow \infty$, $q \rightarrow 0$ and $q \rightarrow 1$) shown by Fig.~\ref{fig:qLsResiduals}, we consider the 90th percentile error (indicated by the dashed green line in Fig.~\ref{fig:qLsResiduals}) for the remainder of the analysis, in order to further take into account the high-error regions of the parameter space ($\Lambda_s \sim 2000$, $q\sim0.5$).
-We take this value of $P_{90}=2.06\times10^{-25} \text{ s}^5$ to be the systematic measurement error introduced by using the improved binary Love EoS-insensitive relations on the parameter extraction of $\lambda_0$, indicated by the dashed indigo line in Fig.~\ref{fig:stackedFisher}.
+We take this value of $P_{90}=2.06\times10^{-25} \text{ s}^5$ to be the systematic measurement error introduced by using the improved binary Love relations on the parameter extraction of $\lambda_0$, indicated by the dashed indigo line in Fig.~\ref{fig:stackedFisher}.
 Similarly, we derive the systematic measurement error on $\tilde\Lambda$ to be $12.01$, shown in Fig.~\ref{fig:singleFisherLt}.
 Currently, the statistical error of $26.53 \times 10^{-25} \text{ s}^5$ on $\lambda_0$ from GW170817 dominate the error budget compared to the systematic error of $2.06\times10^{-25} \text{ s}^5$, as seen in Fig.~\ref{fig:stackedFisher}.
-This means that, for the current ``O2" detector sensitivity, the use of improved binary Love EoS-insensitive relations will only make a negligible difference on the extraction of $\tilde\Lambda$.
+This means that, for the current ``O2" detector sensitivity, the use of improved binary Love relations will only make a negligible difference on the extraction of $\tilde\Lambda$.
 However, future detectors (for example aLIGO, A\texttt{+}, Voyager, CE, and ET) are planned with large reductions in sensitivity - both decreasing the statistical errors and allowing for a larger binary NS merger detection rate; further reducing uncertainties.
@@
 Observe how the error is maximal for $q\sim0.5$ and $\Lambda_s\sim2000$, while it becomes minimal for both low and high values of $q$ and $\Lambda_s$.
-Also shown in the figure is the 90th percentile of the un-binned residuals seen in Fig.~\ref{fig:residuals}, taken to be the overall systematic uncertainty introduced by using binary Love EoS insensitive relations.
+Also shown in the figure is the 90th percentile of the un-binned residuals seen in Fig.~\ref{fig:residuals}, taken to be the overall systematic uncertainty introduced by using binary Love relations.
 }
@@
 These residuals obey Gaussian distributions centered at $\mu=-2.39 \times 10^{-27} \text{ s}^5$ and $\mu=4.22 \times 10^{-27} \text{ s}^5$ with standard deviations of $\sigma=1.52\times10^{-25} \text{ s}^5$ and $\sigma=12.21\times10^{-25} \text{ s}^5$ for the constrained and unconstrained sets of EoSs, respectively.
-These uncertainties correspond roughly to the systematic errors introduced on the parameter extraction of $\lambda_0$ upon the use of binary Love EoS-insensitive relations.
+These uncertainties correspond roughly to the systematic errors introduced on the parameter extraction of $\lambda_0$ upon the use of binary Love relations.
 However, to take into account the systematic errors found in high-error regions of the parameter space, we instead set the systematic error to be the 90th percentile, $P_{90}=2.06\times10^{-25} \text{ s}^5$.
-Observe that the systematic errors from using the improved (constrained) binary Love EoS-insensitive relations are negligible compared to the statistical errors accrued on parameter extraction from GW170817, found to be $\sigma_{\lambda_0}=26.53 \times 10^{-25} \text{ s}^5$.
+Observe that the systematic errors from using the improved (constrained) binary Love relations are negligible compared to the statistical errors accrued on parameter extraction from GW170817, found to be $\sigma_{\lambda_0}=26.53 \times 10^{-25} \text{ s}^5$.
 }
@@
 
-Next, we consider events identical to GW170817 detected on future design sensitivity upgrades and detectors $A \equiv ($O2, aLIGO, A\texttt{+}, Voyager, CE, ET-D$)$, shown in Fig.~\ref{fig:sensitivities}, to determine if and when the statistical errors associated with parameter extraction of $\lambda_0$ drop below the systematic EoS variation errors from using binary Love EoS-insensitive relations.
+Next, we consider events identical to GW170817 detected on future design sensitivity upgrades and detectors $A \equiv ($O2, aLIGO, A\texttt{+}, Voyager, CE, ET-D$)$, shown in Fig.~\ref{fig:sensitivities}, to determine if and when the statistical errors associated with parameter extraction of $\lambda_0$ drop below the systematic EoS variation errors from using binary Love relations.
 The process we use for each detector sensitivity $S_n^A(f)$ is as follows:
@@
 where $H_0 = 70 \text{km s}^{-1}\text{Mpc}^{-1}$ is the local Hubble constant, and $\Omega_{\Lambda}=0.67$ is the universe's vacuum energy density.
-Here we choose an observing period $\Delta \tau = 1$ year, and calculate the detection rate for the upper, central, and lower limits of the local binary NS coalescence rate density $\mathcal{R}=1540^{+3200}_{-1220} \text{ Gpc}^{-3}\text{yr}^{-1}$~\cite{Abbott2017}, giving the rates shown in the second column of Table~\ref{tab:variances}.
+Here we choose an observing period $\Delta \tau = 1$ year {\ny{Should this be tau 0?}}, and calculate the detection rate for the upper, central, and lower limits of the local binary NS coalescence rate density $\mathcal{R}=1540^{+3200}_{-1220} \text{ Gpc}^{-3}\text{yr}^{-1}$~\cite{Abbott2017}, giving the rates shown in the second column of Table~\ref{tab:variances}.
 \item Compute the overall population standard deviation, taking into account sources at varying redshifts as done in Eq. (3) of Ref.~\cite{Takahiro}:
@@
 \end{itemize}
+
+{\ny{I think you need more detail because I didn't understand how you computed the combined statistical error.
+Perhaps you could give a concrete example of 1 iteration of the method, say if N = 2.
+This could make it much clearer and yes, you could move all of this to an appendix.
+}}
 
@@
 
+{\ny{Super confused about Fig. 1...}}
+
 Concluding, we find that the Voyager, ET, and CE detectors all exhibit enough uncertainty reduction that the systematics on $\lambda_0$ introduced from using improved EoS-insensitive relations (found to be $2.06 \times 10^{-25}\text{ s}^5$) no longer become negligible in the error budget.
@@
 Additionally, we find that hybrid quark-hadron star EoSs \emph{do} obey the I-Love-Q and C-Love universality, albeit with a slightly higher maximum EoS variability as displayed in Tabs.~\ref{tab:hybridCompare} and ~\ref{tab:hybridCompareClove}.
-In addition, we find that binaries consisting of one massive hybrid quark-hadron star, and one small-mass hadron star do not obey the binary Love EoS-insensitive relations -- explained by the large difference in $\tilde{\Lambda}$ displayed between the constituent stars.
+In addition, we find that binaries consisting of one massive hybrid quark-hadron star, and one small-mass hadron star do not obey the binary Love relations -- explained by the large difference in $\tilde{\Lambda}$ displayed between the constituent stars.
 To improve on this, we construct new ``hybrid matter binary Love relations", applied to only the hybrid branches of the transitional EoSs.
@@
 By reducing the number of required waveform model parameters, surrogate models aid in the extraction of NS observables from GW detections.
-The improvement of multipole love EoS insensitive relations can then be used to increase the accuracy of surrogate models.
+The improvement of multipole love relations can then be used to increase the accuracy of surrogate models.
 

### 2019-01-20 paper/bin-love-after-gw170817.tex
minore comments

@@
 Unfortunately, terrestrial experiments can only study the EoS to around the nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy} (although some temperature-dependent heavy-ion collision experiments may probe higher densities \zc{Katerina do you know of any papers on this?} {\ny{Look up the PREX and CREX experiments at JLab (a good author is Horowitz, e.g.
-Abrahamyan:2012gp, Horowitz:2012tj, Horowitz:2013wha)}}), making NSs ideal laboratories for constraining ultra dense nuclear matter.
+Abrahamyan:2012gp, Horowitz:2012tj, Horowitz:2013wha)}} \kc{these are neutron skin measurement papers, not heavy ion collisions.
+look at~\cite{Danielewicz:2002pu} }), making NSs ideal laboratories for constraining ultra dense nuclear matter.
 
@@
 Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with mass ratios of $0.75$, in C-Love universality by a factor of $\sim 67\%$, and in I-Love-Q universality by factors of $\sim50$\%, tabulated in Tab.~\ref{tab:maxVar}.
-We also present new R-Love relations displaying the relationship between NS radius and tidal deformability, showing maximum EoS variability of $18.88\%$ from the fit discussed in Sec.~\ref{sec:clove}.
+We also present new R-Love relations displaying the relationship between NS radius and tidal deformability, showing maximum EoS variability of $18.88\%$\kc{This needs to be expressed in terms of error in the radius, ie.
+in km} from the fit discussed in Sec.~\ref{sec:clove}.
 Additionally, we find that hybrid quark-hadron stars do obey the I-Love-Q and C-Love relations, with sightly increased EoS variability.
@@
 Finally, the high density core EoSs generated above were stitched to the low-density crust EoS of SLy~\cite{Douchin:2001sv} at $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$.
-}
+\kc{The axis should stop where the 170817 data stops}}
 \label{fig:eos}
@@
 
+\kc{Wait wait wait. Why $\lambda_0$? When we do PE, we do it in terms of $\Lambda_1$ and $\Lambda_2$. So it is these residuals (or equivalently $\Lambda_a$) we need in order to marginalize.}
 In this section, we investigate the residuals in $\lambda_0(\Lambda_a,\Lambda_s,q)$ in order to marginalize over the intrinsic error in the binary Love relations.
@@
 
+\kc{me too}
+
 Concluding, we find that the Voyager, ET, and CE detectors all exhibit enough uncertainty reduction that the systematics on $\lambda_0$ introduced from using improved EoS-insensitive relations (found to be $2.06 \times 10^{-25}\text{ s}^5$) no longer become negligible in the error budget.

### 2019-01-20 paper/bin-love-after-gw170817.tex
comment on radius

@@
 
+\kc{The R-Love fit is not a new relation, it is the same as C-Love.
+So instead of refitting you should just reexpress the C(Love) fit as R=m/C(Love).
+The errors you are finding here are way larger than error I've been finding from simply using C(Love) to compute the radius, and this might be the reason.}
 In addition, Fig.~\ref{fig:rlove} displays the relationship between NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
@@
 Also shown in this figure is the hybrid star R-Love relations along with their fractional difference from the constrained EoS fits (dashed green).
+\kc{The radius needs to be in km in both panels (not fractional error).}
 }

### 2019-01-27 paper/bin-love-after-gw170817.tex
more updates on the paper, as well as addressing Nicos comments

--- 2019-01-16 paper/bin-love-after-gw170817.tex
@@
 \item Eventually, we need to discuss the abstract and the intro in more detail. 
-\item Let's not forget to check the acknowledgements for funding sources. 
+\item Let's not forget to check the acknowledgments for funding sources. 
 \item Let's do a spell check. 
@@
 This internal structure of such stars, known as the equation of state (EoS), is exceedingly important, as it is the determining factor for many NS observables - such as the mass, the radius, and many more.
-Unfortunately, terrestrial experiments can only study the EoS to around the nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy} (although some temperature-dependent heavy-ion collision experiments may probe higher densities \zc{Katerina do you know of any papers on this?} {\ny{Look up the PREX and CREX experiments at JLab (a good author is Horowitz, e.g.
-Abrahamyan:2012gp, Horowitz:2012tj, Horowitz:2013wha)}}), making NSs ideal laboratories for constraining ultra dense nuclear matter.
+Unfortunately, terrestrial experiments can only study the EoS to around the nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy} (although some temperature-dependent heavy-ion collision experiments may probe higher densities~\cite{Abrahamyan:2012gp,Horowitz:2012tj,Horowitz:2013wha}), making NSs ideal laboratories for constraining ultra dense nuclear matter.
 
@@
 Unfortunately, current detectors are only sensitive enough to accurately measure the dominant tidal parameter, $\lambda_0$.
-Previous work by Yagi and Yunes~\cite{Yagi:binLove} resolved this issue by finding approximately EoS-insensitive ``binary Love universal relations" between symmetric and anti-symmetric combinations of tidal deformabilities $\Lambda_{s,a}=\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$.
+Previous work by Yagi and Yunes~\cite{Yagi:binLove} resolved this issue by finding approximately EoS-insensitive ``binary Love relations" between symmetric and anti-symmetric combinations of tidal deformabilities $\Lambda_{s,a}=\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$.
 This allows one to further break degeneracies between tidal parameters, resulting in both (i) a decrease in uncertainty upon parameter extraction of $\Lambda_s$ on the removal of parameter $\Lambda_a$ from the model, and (ii) the ability to measure the secondary tidal parameter upon measurement of the first~\cite{Katerina:residuals}.
@@
 Similar ``I-Love-Q" and ``C-Love" relations~\cite{Yagi:ILQ} have been found between individual NS observables: quadrupole moment , moment of inertia, tidal deformability, and compactness; similarly allowing the removal of tidal parameters from the model list, and allowing an automatic determination of one observable through the measurement of another.
-However, these EoS-insensitive relations have been tuned to a collection of EoS models, and each have intrinsic uncertainties associated with their use.
+However, these relations have been tuned to a collection of EoS models, and each have intrinsic uncertainties associated with their use.
 
@@
 These provide a departure from the nuclear matter relations considered here - providing valuable insight into them.
-Further, we estimate the viability of using improved EoS-insensitive relations on future GW detections by performing simple Fisher analyses to approximate when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in EoS-insensitive relations.
+Further, we estimate the viability of using improved EoS-insensitive relations on future GW detections by performing simple Fisher analyses to approximate when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in the relations.
 To estimate the effect of waveform mismodeling, we additionally consider two different tidal corrections to the injected PhenomD~\cite{PhenomDI,PhenomDII} waveform: 6PN~\cite{Wade:tidalCorrections} and NRTidal~\cite{Samajdar:NRTidal}
@@
 In addition, we determine the degree to which hybrid star EoSs obey binary Love relations.
-Finally, through a simple Fisher analysis, we consider the value in improving EoS-insensitive relations by approximating when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in EoS-insensitive relations.
+Finally, through a simple Fisher analysis, we consider the value in improving EoS-insensitive relations by approximating when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in the relations.
 
@@
 \caption{
-Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue circle) in the extraction of $\lambda_0$ from GW170817 (O2) as if observed with future interferometers aLIGO, A\texttt{+}, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
-This is compared to the combined uncertainty $\sigma^A_N$ (turquoise shaded region) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper and lower limits of expected binary NS merger detection rates for O2, aLIGO, A\texttt{+}, Voyager, CE, and ET-D over 1 observation year.
-It can be seen that the statistical errors in parameter extraction become comparable to the systematics from EoS variation in binary Love relations (purple shaded region) for Voyager and on.
-Note there is no simulated populations of events under the O2 design sensitivity - due to there only being a single event during the observing period.
+Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue circles) in the extraction of $\lambda_0$ from GW170817 (O2 detector sensitivity) as if it were observed with future interferometers aLIGO, A\texttt{+}, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
+This is compared to the combined uncertainty $\sigma^A_N$ (turquoise shaded region) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper and lower limits of the expected binary NS merger detection rates for O2, aLIGO, A\texttt{+}, Voyager, CE, and ET-D over 1 observation year.
+It can be seen that the statistical errors in the parameter extraction become comparable to the systematics from EoS variation in improved binary Love relations (indigo dashed line) for Voyager CE, and ET.
 These results are further tabulated in Table~\ref{tab:variances}.
-Additionally shown in the figure are the estimated statistical uncertainties on the extraction of $\lambda_0$ upon the injection of the PhenomD + NRTidal correction waveform (IMRD + NRTidal), rather than the PhenomD + 6PN tidal correction (IMRD + 6PN), in order to demonstrate the waveform mismodeling uncertainties.
-The single-detection uncertainties are shown in unfilled blue circles, while the combined detection uncertainties are outlined in dashed maroon.
+Additionally shown in the figure are the estimated statistical uncertainties on the extraction of $\lambda_0$ upon the injection of the PhenomD + NRTidal correction waveform (IMRD + NRTidal), rather than the PhenomD + 6PN tidal correction (IMRD + 6PN), in order to demonstrate the effect of waveform mismodeling uncertainties.
+The single-detection uncertainties are shown by unfilled blue circles, while the combined detection uncertainties are outlined by dashed maroon.
 }
@@
 We continue in Sec.~\ref{sec:universal} by finding new and improved binary Love, I-Love-Q, and C-Love relations, and considering how well hybrid star EoSs agree with the EoS-insensitive relations.
-We next examine these improved EoS-insensitive relations and question whether or not they are useful for future interferometers in Sec.~\ref{sec:observations}.
+We next examine these improved relations and question whether or not they are useful for future interferometers in Sec.~\ref{sec:observations}.
 We conclude in Sec.~\ref{sec:conclusion} by discussing our results and mentioning avenues of future work.
@@
 \subsection{Spectral representations of neutron star equations of state}\label{sec:eos}
-The structure of a NS and its tidal interactions in a binary system rely heavily on the underlying state function describing the relationship between pressure ($p$) and energy density ($\epsilon$), or equation of state, of nuclear matter.
+The structure of a NS and its tidal interactions in a binary system rely heavily on the underlying state function (or equation of state) describing the relationship between pressure ($p$) and energy density ($\epsilon$) of nuclear matter.
 Given that all currently proposed EoSs utilize certain approximations~\cite{Oertel:Review,Baym:Review}, one method to study a wide range of physically realizable EoSs is to parameterize them such that any realistic EoS can be represented with a small number of parameters.
@@
 \end{equation}
-where $x \equiv \log{p/p_0}$ for minimum pressure $p_0$.
+where $x \equiv \log{p/p_0}$ for a minimum pressure $p_0$.
 The equation of state is then determined by an integration of the differential equation:
@@
 In particular, we focus on the ACS and ACB models described in Ref.~\cite{Paschalidis2018}, shown in Fig.~\ref{fig:hybridML}.
-These result in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq \text{ M}_{\text{tr}}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote this as ``HS"), and (ii) small-mass ($M \leq \text{ M}_{\text{tr}}$) hadronic stars with no internal transition to quark matter (we denote this as ``NS").
+These result in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq \text{ M}_{\text{tr}}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote this as ``HS"), and (ii) low-mass ($M \leq \text{ M}_{\text{tr}}$) hadronic stars with no internal transition to quark matter (we denote this as ``NS").
 
@@
 The constrained EoSs were populated by randomly selecting 100 posterior samples obtained from the GW170817 90\% credible level shown in cyan~\cite{LIGO:posterior}.
-Additionally, 100 unconstrained EoSs were generated by randomly sampling spectral coefficients of physically valid EoSs, with no further constrained applied.
-The following constraints were also applied to both sets of EoSs: (i) the EoS must have a causal structure within 10\%, and (ii) the EoS must support maximum NS mass of at least $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations.
+Additionally, 100 unconstrained EoSs were generated by randomly sampling spectral coefficients of physically valid EoSs, with no further constraints applied.
+The following restrictions were also applied to both sets of EoSs: (i) the EoS must have a causal structure within 10\%, and (ii) the EoS must support maximum NS mass of at least $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations.
 Finally, the high density core EoSs generated above were stitched to the low-density crust EoS of SLy~\cite{Douchin:2001sv} at $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$.
@@
 
-Next, we consider the case of two NSs in a binary, such as the system found in GW170817, where each star 
-individually experiences a neighboring tidal field.
+Next we consider binary NS systems, as was found in GW170817, where each star individually experiences a neighboring tidal field.
 Thus each star possesses tidal deformabilities $\Lambda_1$ and $\Lambda_2$ entering the gravitational waveform.
@@
 Any set of two independent functions may be used, for example: tidal parameters $\tilde{\Lambda}=\tilde{\Lambda}(\Lambda_1,\Lambda_2)$ and $\delta \tilde{\Lambda}=\delta \tilde{\Lambda}(\Lambda_1,\Lambda_2)$~\cite{Wade:tidalCorrections} first enter the gravitational waveform at 5PN and 6PN orders respectively, thus partially breaking degeneracies.
-Here, $\tilde{\Lambda}$ is known as the mass weighted tidal deformability, or \emph{chirp deformability} due to its status as the dominant tidal parameter in the waveform.
+Here, $\tilde{\Lambda}$ is known as the mass weighted tidal deformability and is the dominant tidal parameter in the waveform.
 
@@
 These ``binary Love relations" allow one to break degeneracies between coupled tidal parameters.
-This is important for two reasons: (i) allows us to algebraically eliminate tidal parameters from the template parameter list, improving parameter estimation, and (ii) automatic measurement of second tidal parameter given observation of the first.
-It was shown through a simple Fisher analysis that the use of binary Love relations improved parameter extraction on $\tilde{\Lambda}$ by an order of magnitude.
+This is important for two reasons: (i) they allow one to algebraically eliminate tidal parameters from the template parameter list, improving overall parameter estimation, and (ii) they allow the automatic measurement of a second tidal parameter given observation of the first.
+It was shown through a simple Fisher analysis that the use of binary Love relations improved parameter extraction on $\tilde{\Lambda}$ by up to an order of magnitude.
 
@@
 These have been found to be EoS insensitive by up to 1\% and 6.5\% respectively.
-In this paper, we show improvement in both of these EoS-insensitive relations by restricting to EoSs sampled from GW170817s posterior on pressure as a function of density.
+In this paper, we show improvement in all of these relations by restricting to EoSs sampled from GW170817s posterior on pressure as a function of density.
 %%%%%%%%%%%%%%%%%%%%%%%%% Begin universal relations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{I-Love-Q relations}\label{sec:ilq}
-Here we present our results on I-Love-Q universality as compared to Fig. 1 of Yagi and Yunes~\cite{Yagi:ILQ}.
+Here we present our results on I-Love-Q universality as compared to Fig. 1 of Ref.~\cite{Yagi:ILQ}.
 In particular, we consider two distinct classes of NSs: nuclear matter EoSs and hybrid quark-hadron star EoSs as described in Sec.~\ref{sec:theory}.
@@
 This is followed in Sec.~\ref{sec:ilq-hyb} by an analysis and discussion into how well hybrid stars agree with the improved binary Love relations.
-
-{\ny{Overall, let's not call these relations ``I-Love-Q relations'' or ``binary love relations.''  It's much better to be brief and simply call them I-Love-Q relations and Binary Love relations (like is done in the literature).
-It should be clear when we define them that they are EOS insensitive}}
 
@@
 \end{equation}
-This is appended to an expansion in $\Lambda^{-1/5} \propto C$ (or $\bar{Q}^{-1/5}$), where $C=M/R$ is the compactness of the star.
+This is appended to an expansion in $\Lambda^{-1/5} \propto C$, where $C=M/R$ is the compactness of the star.
 This results in the following overall fitting relation:
@@
 The new fitting coefficients are presented in Table~\ref{tab:ILQfitNew}.
-While the two above fits both result in fits with similar $R^2$ (Coefficient of determination, defined as $R^2=\sum_i(f_i-\bar{y})^2/\sum_i(y_i-\bar{y})^2$, where $\bar{y}$ is the mean data value, and $f_i$, $y_i$ are the modeled and actual data values) values of $\sim 0.9999995$ for the data presented, the lattter one has the advantage that it properly limits to the Newtonian case as $\Lambda \rightarrow \infty$~\cite{Yagi:binLove}.
+While the two above curves both result in fits with similar $R^2$ values (Coefficient of determination, defined as $R^2=\sum_i(f_i-\bar{y})^2/\sum_i(y_i-\bar{y})^2$, where $\bar{y}$ is the mean data value, and $f_i$, $y_i$ are the modeled and actual data values) of $\sim 0.9999995$ for the data presented, the latter has the advantage that it properly limits to the Newtonian case as $\Lambda \rightarrow \infty$~\cite{Yagi:binLove}.
 
@@
  \hline
- $\bar{I}$ & $\Lambda$ & $1.4934168$ & $0.0640972$ & $0.0208513$ & $-5.018022 \times 10^{-4}$ & $3.1638958 \times 10^{-7}$ \\
- $\bar{Q}$ & $\Lambda$ & $0.2092931$ & $0.0740442$ & $-0.0538210$ & $-5.018022 \times 10^{-3}$ & $1.576165 \times 10^{-4}$ \\ 
-  $\bar{I}$ & $\bar{Q}$ & $1.3832702$ & $0.5931020$ & $-0.0216132$ & $0.0419044$ & $-2.9676365 \times 10^{-3}$ \\
+ $\bar{I}$ & $\Lambda$ & $1.493$ & $0.06410$ & $0.02085$ & $-5.018 \times 10^{-4}$ & $3.16 \times 10^{-7}$ \\
+ $\bar{Q}$ & $\Lambda$ & $0.2093$ & $0.07404$ & $-0.05382$ & $-5.018 \times 10^{-3}$ & $1.576 \times 10^{-4}$ \\ 
+  $\bar{I}$ & $\bar{Q}$ & $1.383$ & $0.5931$ & $-0.02161$ & $0.04190$ & $-2.968 \times 10^{-3}$ \\
  \hline
@@
  \hline
- $\bar{I}$ & $\Lambda$ & $2/5$ & $0.5313031$ & $1.2868285$ & $0.0988787$ & $-2.3001034$ & $-1.3465945$ & $0.3857349$ & $-0.0287014$\\
- $\bar{Q}$ & $\Lambda$ & $1/5$ & $3.5554627$ & $-2.1218079$ & $2.7237378$ & $-1.4906808$ & $0.8643535$ & $-0.1427541$ & $-1.3973147$\\
- $\bar{I}$ & $\bar{Q}$ & $2$ & $0.0089212$ & $10.5910815$ & $-37.4581345$ & $43.1831156$ & $-2.3610288$ & $1.9674667$ & $-0.5678018$\\
- $C$ & $\Lambda$ & $-1/5$ & $0.2495709$ & $-919.5651942$ & $330.2848184$ & $-857.1842107$ & $-383.5404843$ & $192.4933832$ & $-811.1425435$\\
- $R$ & $\Lambda$ & $-1/40$ & $8.5752160$ & $-10.5478546$ & $17.3202891$ & $-29.7572150$ & $-9.9777952$ & $21.9091242$ & $-31.7691648$\\
+ $\bar{I}$ & $\Lambda$ & $2/5$ & $0.5313$ & $1.287$ & $0.09888$ & $-2.300$ & $-1.347$ & $0.3857$ & $-0.02870$\\
+ $\bar{Q}$ & $\Lambda$ & $1/5$ & $3.555$ & $-2.122$ & $2.72$ & $-1.491$ & $0.8644$ & $-0.1428$ & $-1.397$\\
+ $\bar{I}$ & $\bar{Q}$ & $2$ & $0.008921$ & $10.59$ & $-37.46$ & $43.18$ & $-2.361$ & $1.967$ & $-0.5678$\\
+ $C$ & $\Lambda$ & $-1/5$ & $0.2496$ & $-919.6$ & $330.3$ & $-857.2$ & $-383.5$ & $192.5$ & $-811.1$\\
+ $R$ & $\Lambda$ & $-1/40$ & $8.575$ & $-10.55$ & $17.32$ & $-29.76$ & $-9.978$ & $21.91$ & $-31.77$\\
 \hline
@@
 
-Fig.~\ref{fig:ILQ} shows the improved I-Love relations between the dimensionless moment of inertia $\bar{I} \equiv I/M^3$, the dimensionless quadrupole moment $\bar{Q} \equiv Q/M^3$, and the dimensionless tidal deformability $\Lambda$ for both the constrained and unconstrained sets of EoSs (each with individual fits pertaining to only that set of EoSs {\ny{I think we should here say which fit we are using (I think you are using the new one.)}}).
-We observe that the constrained EoSs show considerable improvement from both the results of previous works~\cite{Yagi:ILQ}, and from the unconstrained EoSs.
-This is further validated in Tab.~\ref{tab:maxVar}, where the maximal EoS variation from each fit is tabulated; comparing the results of previous works to the unconstrained, and constrained sets of EoSs.
+Figure~\ref{fig:ILQ} shows the improved I-Love relations between the dimensionless moment of inertia $\bar{I} \equiv I/M^3$, the dimensionless quadrupole moment $\bar{Q} \equiv Q/M^3$, and the dimensionless tidal deformability $\Lambda$ for both the constrained and unconstrained sets of EoSs.
+Here, each category of EoS are fit individually using the curve found in Eq.~\ref{eq:ILQfitNew}.
+We observe that the constrained EoSs show considerable improvement from the unconstrained EoSs.
+Additionally, we note a large improvement from the results of previous works~\cite{Yagi:ILQ}, validated in Tab.~\ref{tab:maxVar}, where the maximal EoS variation from each fit is tabulated; comparing the results of previous works to the unconstrained and constrained sets of EoSs.
 Observe how the constrained EoSs outperform both other cases by a considerable amount for each I-Love-Q relation.
@@
 \begin{center} 
-\includegraphics[width=.32\textwidth]{IL.eps}
-\includegraphics[width=.32\textwidth]{QL.eps}
-\includegraphics[width=.32\textwidth]{IQ.eps}
+\includegraphics[width=.32\textwidth]{IL.pdf}
+\includegraphics[width=.32\textwidth]{QL.pdf}
+\includegraphics[width=.32\textwidth]{IQ.pdf}
 \end{center}
@@
 Additionally shown in this figure is the fractional difference from the nuclear matter fits for the 10 hybrid star EoSs (dashed green).
-{\ny{These figures are all too heavy and they make the scrolling of the pdf difficult.
-Can you downgrade their resolution or save them as pdf please?}}
 }
@@
 Comparison between the EoS-insensitive relations (I-Love-Q, C-Love, R-Love, and binary Love) maximal EoS variability for the results of previous works~\cite{Yagi:ILQ,Yagi:binLove}, and the unconstrained and constrained sets of EoSs analyzed here.
-The maximum EoS variation, given by the largest fractional difference from the fits as shown in Figs.~\ref{fig:ILQ},~\ref{fig:clove},~\ref{fig:rlove} and~\ref{fig:binLove}, sees a considerable improvement for the constrained set of EoSs, compared to the unconstrained set as well as previous works.
-Additionally, notice how the maximal EoS variation for the unconstrained set of EoSs is slightly higher than that found in Refs.~\cite{Yagi:ILQ,Yagi:binLove} - due to the effects of large random sampling taking into account more sources of uncertainty.
+The maximum EoS variation, given by the largest fractional difference from the fits as shown in Figs.~\ref{fig:ILQ},~\ref{fig:clove},~\ref{fig:rlove} and~\ref{fig:binLove}, observes a considerable improvement for the constrained set of EoSs, compared to the unconstrained set as well as that found in previous works.
+Additionally, note how the maximal EoS variation for the unconstrained set of EoSs is slightly larger than that found in Refs.~\cite{Yagi:ILQ,Yagi:binLove} - due to the effects of large random sampling taking into account more sources of uncertainty.
 }\label{tab:maxVar}
@@
  \hline
- $\bar{I}-\Lambda$ &  $0.0059$ & $0.0076725$ & $0.0031383$\\
- $\bar{Q}-\Lambda$ & $0.010$ & $0.012617$ & $0.0046612$\\
- $\bar{I}-\bar{Q}$ & $0.012$ & $0.014895$ & $0.0057157$\\
- \hline
- $C-\Lambda$ & $0.065$ & $0.071975$ & $0.021688$\\
- $R-\Lambda$ & -- & $0.498269$ & $0.17922$\\
- \hline
- $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.50$} & \multirow{2}{*}{$0.5723891$} & \multirow{2}{*}{$0.2140192$}\\
+ $\bar{I}-\Lambda$ &  $0.0059$ & $0.007673$ & $0.003138$\\
+ $\bar{Q}-\Lambda$ & $0.010$ & $0.01262$ & $0.004661$\\
+ $\bar{I}-\bar{Q}$ & $0.012$ & $0.01490$ & $0.005716$\\
+ \hline
+ $C-\Lambda$ & $0.065$ & $0.07198$ & $0.02169$\\
+ $R-\Lambda$ & -- & $0.4983$ & $0.1792$\\
+ \hline
+ $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.50$} & \multirow{2}{*}{$0.5724$} & \multirow{2}{*}{$0.2140$}\\
  $(q=0.90)$ & & &\\
  \cline{1-1}
- $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.20$} & \multirow{2}{*}{$0.2447418$} & \multirow{2}{*}{$0.0828446$}\\
+ $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.20$} & \multirow{2}{*}{$0.2447$} & \multirow{2}{*}{$0.08284$}\\
   $(q=0.7)$ & & &\\
   \cline{1-1}
- $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.025$} & \multirow{2}{*}{$0.0384088$} & \multirow{2}{*}{$0.0182308$}\\
+ $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.025$} & \multirow{2}{*}{$0.03841$} & \multirow{2}{*}{$0.01823$}\\
   $(q=0.50)$ & & &\\
@@
 
-These results indicate that EoS-insensitive relations can indeed be greatly improved upon by constraining to only EoSs which agree with physical observations.
-In addition, we confirm the validity of this method by noting that the unconstrained EoSs observe more EoS variability than that found in Ref~\cite{Yagi:ILQ} due to the nature of large random sampling taking into account more sources of uncertainty than previously studied.
+These results indicate that EoS-insensitive relations can indeed be greatly improved upon by restricting to EoSs in agreeance with physical observations.
+In addition, we confirm the validity of this method by noting that the unconstrained EoSs observe more EoS variability than that found in Ref.~\cite{Yagi:ILQ} due to the nature of large random sampling taking into account more sources of uncertainty than previously studied.
 On the other hand, the constrained set of EoSs show significant improvement from that found in previous works.
@@
 \subsubsection{Hybrid quark-hadron stars}\label{sec:ilq-hyb}
-In this section, we investigate the I-Love-Q universality of hybrid stars, and their compatibility with the nuclear matter counterparts.
-We consider three different sets of data to be fit to Eq.~\ref{eq:ILQfitNew}:
+In this section, we investigate the I-Love-Q universality of hybrid stars, and their compatibility with their nuclear matter counterparts.
+We consider three different sets of data to be fit by Eq.~\ref{eq:ILQfitNew}:
 \begin{enumerate}
@@
 Following this, we compute the fractional difference from the fits for all three cases for the 10 hybrid star EoSs.
-The fractional differences for the second case fit (fit to only the constrained EoSs) is shown by the dashed green lines in Fig.~\ref{fig:ILQ} for example.
+The fractional differences for the second case (fit to only the constrained EoSs) is shown by the dashed green lines in Fig.~\ref{fig:ILQ} for example.
 To compare the three different fits, Tab.~\ref{tab:hybridCompare} displays the maximal EoS variation in the $I-\Lambda$ relation for both the constrained and hybrid star EoSs in each case.
@@
  \hline
- \emph{Combined} &  \multirow{2}{*}{$0.0044066$} & \multirow{2}{*}{$0.0136338$}\\
+ \emph{Combined} &  \multirow{2}{*}{$0.004407$} & \multirow{2}{*}{$0.01363$}\\
  \emph{(Case 1)} & &\\
  \cline{1-1}
- \emph{Constrained only} & \multirow{2}{*}{$0.0031383$} & \multirow{2}{*}{$0.0173574$}\\
+ \emph{Constrained only} & \multirow{2}{*}{$0.003138$} & \multirow{2}{*}{$0.01736$}\\
   \emph{(Case 2)} & &\\
   \cline{1-1}
- \emph{Hybrid only} & \multirow{2}{*}{$0.0084002$} & \multirow{2}{*}{$0.0101741$}\\
+ \emph{Hybrid only} & \multirow{2}{*}{$0.008400$} & \multirow{2}{*}{$0.01017$}\\
   \emph{(Case 3)} & &\\
@@
 
-Observe how the hybrid star EoSs do obey the I-Love-Q relations up to $\sim1.7$\%, slightly higher than that found here for nuclear matter EoSs, as well as that found in previous works~\cite{Yagi:ILQ}.
+Observe how the hybrid star EoSs obey the I-Love-Q relations in each case by up to $\sim1.7$\%, slightly higher than that found for nuclear matter EoSs in previous works~\cite{Yagi:ILQ}.
 Further, we observe that the universality can not be improved by much through the introduction of new fits, only bringing the max EoS variation down to $\sim1$\% for the fits constructed with only hybrid star EoSs.
-Concluding, we claim that hybrid star EoSs \emph{do} obey the I-Love-Q relations computed through nuclear EoS data, but the lack of universality goes up to $\sim1.7$\%.
+Concluding, we claim that hybrid star EoSs \emph{do} obey the I-Love-Q relations computed through nuclear EoS data, with a decrease in universality to $\sim1.7$\%.
 
@@
 Why is it that we can lower fractional difference in the NS case but not in the hybrid case?}}
-
+{\zc{Nico, I think the reason for this is because there is nothing ``constrained" about the hybrid stars - these are basically ``unconstrained" EoSs so we can't really reduce the fractional difference any more.}}
 {\ny{Can I see the relative fractional different between each fit and the data for hybrid stars only?
@@
 the analogous thing to the green dashed lines of the figure below, but also with the fits to the total set, to just the hybrids and to just the neutron stars.) I wonder whether there is any improvement at all when you fit just to hybrid stars or whether there are any features.}}
+{\zc{Nico, Yes of course!
+I've added a new figure (for example only - this can be removed later) - Fig.~\ref{fig:example} showing the fractional difference for hybrid stars only for the three cases shown in the text.
+Looking at the figures, they don't change much at all in shape for the first two cases - just a minor vertical shift.
+The third case (fits to hybrids only) looks different but not by much.}}
+\begin{figure}
+\begin{center} 
+\includegraphics[width=\columnwidth]{compareHybrid.pdf}
+\end{center}
+\caption{
+\zc{Example figure applying to Nicos comment on the differences between the three different cases of Hybrid star fits: Case I - Complete set of 100 constrained EoSs combined
+with the 10 hybrid star EoSs, Case II - Complete set of 100 constrained EoSs alone, Case III - Complete set of 10 hybrid star EoSs alone.}
+}
+\label{fig:example}
+\end{figure}
 
@@
 \end{equation}
-Doing so yields $a_0 = 0.3616998$, $a_1 = -0.0354818$, and $a_2 = 0.0006193849$, similar to what was found in Ref.~\cite{Yagi:binLove}.
-Additionally we offer an improvement to the fits as was done in Sec.~\ref{sec:ilq}. 
-We consider the fitting function found in Eq.~\ref{eq:ILQfitNew}, with the controlling factor given by:
+Doing so yields $a_0 = 0.3617$, $a_1 = -0.03548$, and $a_2 = 0.0006194$, similar to that found in Ref.~\cite{Yagi:binLove}.
+Additionally we offer an improvement to the fits as was done in Sec.~\ref{sec:ilq}, by considering the fitting function found in Eq.~\ref{eq:ILQfitNew}, with the controlling factor given by:
 \begin{equation}
@@
 Figure~\ref{fig:clove} presents the C-Love relations for both the constrained and unconstrained sets of EoSs, along with the relative fractional difference from the fits. 
-Observe how the constrained EoSs show a large suppression in EoS variability compared to both the unconstrained EoSs, as well as that found in previous works~\cite{Yagi:binLove}.
+Observe how the constrained EoSs show a large suppression in EoS variability compared to the unconstrained EoSs, as well as to that found in previous works~\cite{Yagi:binLove}.
 The maximal EoS variation is compared between the above three cases in Tab.~\ref{tab:maxVar}.
@@
 
-In addition, Fig.~\ref{fig:rlove} displays the relationship between NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
-Similar to the fits performed for the I-Love-Q and C-Love relations, we fit the R-Love relations to Eq.~\ref{eq:ILQfitNew} with a Newtonian control factor the same as used in the C-Love case seen in Eq.~\ref{eq:cloveFit}, where the NS mass is substituted with the polytropic form $M\propto R^{(3-n)/(1-n)}$~\cite{Shapiro:MRpolytrope}.
+Additionally, Fig.~\ref{fig:rlove} displays the relationship between NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
+Similar to the fits performed for the I-Love-Q and C-Love relations, we fit the R-Love relations to Eq.~\ref{eq:ILQfitNew}.
+In this case, we utilize the same Newtonian control factor found in Eq.~\ref{eq:cloveFit} for the C-Love relations, substituting the NS mass with the polytropic form $M\propto R^{(3-n)/(1-n)}$~\cite{Shapiro:MRpolytrope}.
 Noting that most physical EoSs obey approximate polytropic indices between $0.50$ and $1.00$, as shown in Ref.~\cite{Yagi:binLove}, we choose a central value of $n=0.75$ for use in this analysis, resulting in $M\propto R^9$.
@@
 The results of this fit are displayed in Tab.~\ref{tab:ILQfitNew}, and the maximal EoS variability is again shown in Tab.~\ref{tab:maxVar}.
-As can be seen with the unconstrained EoSs, previously this relation was not very universal, and gave large uncertainties ($\sim50\%$) on the mapping from tidal deformability to radius.
-Now, however, upon the restriction to soft EoSs conforming to GW170817 observe a large decrease in EoS variability to $\sim20\%$, making these relations EoS insensitive to some degree (on the same scale as the binary Love relations).
+Previously, this relation observed large relative uncertainties on the order of $\sim50\%$ on the mapping from tidal deformability to radius, as can be seen by the unconstrained EoSs in Fig.~\ref{fig:rlove}.
+However, upon the restriction to soft EoSs conforming to GW170817, we observe a large suppression in EoS variability to the order of $\sim20\%$.
+This results in new EoS-insensitive relations, with relative uncertainties on the same scale as found in the binary Love relations discussed below in Sec.~\ref{sec:binary}.
 \begin{figure}
@@
 \caption{
-Similar to Fig.~\ref{fig:clove} but for the R-Love relationships between the NS radius and tidal deformability.
-In this figure, we also construct fits to  Eq.~\ref{eq:ILQfitNew}, limiting to the Newtonian case $\bar{R} \sim M\Lambda^{1/5}$, with $M\sim R^{(3-n)/(1-n)}$ for polytropic index $n$.
+Similar to Fig.~\ref{fig:clove} but for the R-Love relationship between the NS radius and tidal deformability.
+In this figure, we also construct fits to  Eq.~\ref{eq:ILQfitNew}, limiting to the Newtonian case $R \sim M\Lambda^{1/5}$, with $M\sim R^{(3-n)/(1-n)}$ for polytropic index $n$.
 Observe how the fractional difference from the fit is reduced significantly between the unconstrained and constrained sets of EoSs, shown by the comparisons in Tab.~\ref{tab:maxVar}.
@@
 
-These results, similar to that found in Sec.~\ref{sec:ilq}, show the considerable improvement found in using constrained EoSs over any unconstrained set.
+The results for the C-Love and R-Love relations, similar to that found in Sec.~\ref{sec:ilq}, show the considerable improvement found in using constrained EoSs over any unconstrained set.
 We also note that the unconstrained EoSs display slightly larger EoS variability than found in Ref.~\cite{Yagi:binLove}, due to the large random sampling as discussed previously in Sec.~\ref{sec:ilq}.
@@
 \subsubsection{Hybrid quark-hadron stars}\label{sec:clove-hyb}
-In this section, we consider the effect of hybrid star EoSs on the C-Love relation.
+In this section, we consider the effect of hybrid star EoSs on the C-Love and R-Love relations.
 Much like Sec.~\ref{sec:ilq-hyb}, we perform 3 separate fits (constrained and hybrid EoSs combined, constrained EoSs only, and hybrid EoSs only) and compare the maximal EoS variation for each class of EoSs.
@@
 We observe similar results for the case of R-Love relations, as seen by the dashed green curves in Fig.~\ref{fig:rlove}.
-Here, the hybrid stars show a maximal fractional difference of $30.82\%$ when compared to the constrained EoS fits - a value much smaller than the unconstrained EoSs variation.
-
-{\ny{let's in general drop the sig figs everywhere, e.g. in 30.82 percent.}}
+Here, the hybrid stars show a maximal fractional difference of $30.82\%$ from the constrained EoS fits, still much smaller than the unconstrained EoSs variation.
 
@@
  \hline
- \emph{Combined} &  \multirow{2}{*}{$0.0368589$} & \multirow{2}{*}{$0.0553262$}\\
+ \emph{Combined} &  \multirow{2}{*}{$0.03686$} & \multirow{2}{*}{$0.05533$}\\
  \emph{(Case 1)} & &\\
  \cline{1-1}
- \emph{Constrained only} & \multirow{2}{*}{$0.0216879$} & \multirow{2}{*}{$0.0719104$}\\
+ \emph{Constrained only} & \multirow{2}{*}{$0.02169$} & \multirow{2}{*}{$0.07191$}\\
   \emph{(Case 2)} & &\\
   \cline{1-1}
- \emph{Hybrid only} & \multirow{2}{*}{$0.0578764$} & \multirow{2}{*}{$0.0447799$}\\
+ \emph{Hybrid only} & \multirow{2}{*}{$0.05788$} & \multirow{2}{*}{$0.04478$}\\
   \emph{(Case 3)} & &\\
@@
 Similar to Sec.~\ref{sec:ilq}, we consider two classes of NSs: nuclear matter EoSs and hybrid quark-hadron star EoSs~\cite{Paschalidis2018,Alford:2017qgh,1971SvA....15..347S,Zdunik:2012dj,Alford:2013aca}.
-We begin in Sec.~\ref{sec:binLove-nuclear} by fitting new binary Love relations for nucleonic matter as was done in~\cite{Yagi:binLove}.
-This is followed in Sec.~\ref{sec:binLove-hybrid} by an analysis and discussion into different fits incorporating hybrid star EoSs.
+We begin in Sec.~\ref{sec:binLove-nuclear} by fitting new binary Love relations to the nucleonic matter EoSs as was done in~\cite{Yagi:binLove}.
+This is followed in Sec.~\ref{sec:binLove-hybrid} by an analysis and discussion into different fits which incorporate hybrid star EoSs.
 
 \subsubsection{Nuclear matter stars}\label{sec:binLove-nuclear}
-Following Ref.~\cite{Yagi:binLove}, we fit the binary Love relations from the constrained EoSs to the two-dimensional curve:
+Following Ref.~\cite{Yagi:binLove}, we fit the binary Love relations to the constrained and unconstrained EoSs using the two-dimensional curve:
 \begin{equation}\label{eq:binLovefit}
-\Lambda_a=F_n(q) \frac{1+ \sum_{i=1}^3 \sum_{j=1}^2 b_{ij}q^j x^{i/5}}{1 + \sum_{i=1}^3 \sum_{j=1}^2 c_{ij}q^j x^{i/5}} \Lambda_s^{\alpha},
-\end{equation}
-where q is the mass ratio $q \equiv m_1/m_2$ with $m_1 \leq m_2$, and $F_n(q)$ being the Newtonian limit given by:
+\Lambda_a=F_n(q) \frac{1+ \sum_{i=1}^3 \sum_{j=1}^2 b_{ij}q^j x^{i/5}}{1 + \sum_{i=1}^3 \sum_{j=1}^2 c_{ij}q^j x^{i/5}} \Lambda_s^{\alpha}.
+\end{equation}
+Here, q is the mass ratio $q \equiv m_1/m_2$ with $m_1 \leq m_2$, and $F_n(q)$ is the Newtonian-limiting control factor given by:
 \begin{equation}
@@
 \end{equation}
-The updated fit parameters can be found in Table~\ref{tab:binLovefit}.
+The updated fit parameters for the constrained set of EoSs can be found in Table~\ref{tab:binLovefit}.
 Notice how, unlike the individual NS I-Love-Q relations, these relations also depend on the ratio of constituent masses in the binary system.
@@
 \addtolength{\tabcolsep}{1pt} 
-\begin{tabular}{c | c  c  c  c  c  c  c  c } 
- \hline
- \hline
- Fit & $n$ & $\alpha$ & $b_{11}$ & $b_{12}$ & $b_{21}$ & $b_{22}$ & $b_{31}$ & $b_{32}$\\
- \hline
- NS & $0.743$ & $-1$ & $-14.3953859$ & $14.4524099$ & $31.3639705$ & $-32.2487464$ & $-22.4377209$ & $20.3458458$\\
- HS & $0.743$ & $-1$ & $343.0432419$ & $-382.6204995$ & $519.4578954$ & $-594.3272852$ & $811.6275273$ & $-867.6333691$\\
-\hline
- \hline
- \noalign{\smallskip}
-
- & & & $c_{11}$ & $c_{12}$ & $c_{21}$ & $c_{22}$ & $c_{31}$ & $c_{32}$\\
- \hline
- NS & & & $-15.2461132$ & $15.3712170$ & $37.3335552$ & $-43.1985996$ & $-29.9331083$ & $35.1806737$\\
- HS & & & $82.5971248$ & $-97.7858530$ & $242.2411803$ & $-262.9050666$ & $244.8665753$ & $-268.8024651$\\
+\begin{tabular}{c | c  c  c  c  c  c  c  c c c c c c c} 
+ \hline
+ \hline
+ Fit & $n$ & $\alpha$ & $b_{11}$ & $b_{12}$ & $b_{21}$ & $b_{22}$ & $b_{31}$ & $b_{32}$ & $c_{11}$ & $c_{12}$ & $c_{21}$ & $c_{22}$ & $c_{31}$ & $c_{32}$\\
+ \hline
+ NS & $0.743$ & $-1$ & $-14.40$ & $14.45$ & $31.36$ & $-32.25$ & $-22.44$ & $20.35$ & $-15.25$ & $15.37$ & $37.33$ & $-43.20$ & $-29.93$ & $35.18$\\
+ HS & $0.743$ & $-1$ & $343.0$ & $-382.6$ & $519.5$ & $-594.3$ & $811.6$ & $-867.6$ & $82.60$ & $-97.79$ & $242.2$ & $-262.9$ & $244.9$ & $-268.8$\\
  \hline
@@
 
-{\ny{Overall, if you start a sentence, you should spell out Figure or Section or Equation.}}
-
-Fig.~\ref{fig:binLove} shows the improved binary Love relation for 3 different mass ratios: $q=0.9$, $q=0.75$, and $q=0.5$ for both constrained and unconstrained sets of EoSs.
-In this figure we show the absolute difference from the fit, rather than the fractional difference, so one can see which regions of $\Lambda_s$ display the largest actual difference.
+Figure~\ref{fig:binLove} shows the improved binary Love relation for 3 different mass ratios: $q=0.9$, $q=0.75$, and $q=0.5$ for both the constrained and unconstrained sets of EoSs.
+%In this figure we show the absolute difference from the fit, rather than the fractional difference, so one can see which regions of $\Lambda_s$ display the largest actual difference.
+\zc{need to decide if using fractional or actual here}
 Observe how once again, the constrained set of EoSs show a considerable improvement upon both the unconstrained set of EoSs, as well as the results found in previous works~\cite{Yagi:binLove}.
-Additionally, the unconstrained set of EoSs show similar, yet slightly larger EoS variation due to the random sampling.
+Additionally, the unconstrained set of EoSs show similar, yet slightly larger EoS variation than was previously found in Ref.~\cite{Yagi:binLove} due to the random sampling taken into account in this analysis.
 Once again, the maximum EoS variability (in terms of fractional difference from the fit for comparison purposes) is tabulated in Tab.~\ref{tab:maxVar} for each value of mass ratio.
@@
 }}
+{\zc{I agree completely - and I think we should discuss over Skype what should be done for this plot (Both versions (absolute and fractional) are loaded in the images folder, just comment out the image name in the figure to change it.)
+Also, the caption is correct - It says that the absolute differences are shown in the plot, while fractional ones are listed in Table III (in order to easily compare to other universal relations and to previous works.)}}
 
 {\ny{I must have missed something. Why do the unconstrained magenta lines extend way passed the constrained green lines? I didn't see this discussed anywhere.}}
-
+{\zc{This is because I've cut all the EoSs off at masses of 1 M$_{\odot}$, and typically the unconstrained EoSs (maroon) have larger ranges of $\Lambda$ than the unconstrained ones.
+So when we take $\Lambda_1+\Lambda_2$, we end up getting higher values of $\Lambda_s$ for the unconstrained EoSs than we do for the constrained ones.}}
 \begin{figure}
@@
 \subsubsection{Hybrid quark-hadron stars}\label{sec:binLove-hybrid}
-As described in Sec.~\ref{sec:theory}, transitional quark-hadron matter stars undergo first-order phase transitions at pressure $P_{\text{tr}}$, where the hadronic branch departs into a quark-matter branch at a given mass transition.
-These transitions result in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq M_{\text{tr}}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote this as ``HS"), and (ii) small-mass ($M \leq M_{\text{tr}}$) hadronic stars with no internal transition to quark matter (we denote this as ``NS").
+As described in Sec.~\ref{sec:theory}, transitional quark-hadron matter stars undergo first-order phase transitions at pressure $P_{\text{tr}}$, where the hadronic branch departs into a quark-matter branch at the corresponding transitional mass $M_{\text{tr}}$.
+These transitions result in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq M_{\text{tr}}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote this as ``HS"), and (ii) low-mass ($M \leq M_{\text{tr}}$) hadronic stars with no internal transition to quark matter (we denote this as ``NS").
 {\ny{ooohh...I'm not sure I like the acronyms here.
@@
 Let's pick a better acronym.}}
-We consider 3 classes of binaries:
+{\zc{We can discuss this over Skype - me and Kent like ``NS" because the low-mass branch of the hybrid star EoS \emph{is} actually a nuclear matter ``NS" EoS - these hybrid stars are derived by introducing a transition to standard NS EoSs.}}
+We consider 3 classes of binary systems in this analysis:
 \begin{itemize}
@@
 
-To determine how each of class of binary NSs obey our improved binary Love relations, we pick a representative set of 10 binary pairs from each class, for the ACB5 hybrid EoS, with a transition at $1.4 \text{ M}_{\odot}$.
-Binary Love values are then computed for each pair, then residuals from the binary Love curve found in Sec.~\ref{sec:binLove-nuclear} are determined and compared to that from the constrained set of EoSs.
+To determine how each of class of binary NS systems obey our improved binary Love relations, we pick a representative set of 10 binary pairs from each class from the ACB5 hybrid EoS, with a transition at $M_{\text{tr}} \approx 1.4 \text{ M}_{\odot}$.
+Binary Love values are computed for each pair, and fractional residuals from the binary Love curve found in Sec.~\ref{sec:binLove-nuclear} are determined and compared to the values from the constrained set of EoSs.
 The results are shown in Fig.~\ref{fig:hybrid}.
-First, we observe that the NS/NS combination of stars gives consistent results to that found earlier -- as expected.
-Next, we see that HS/HS combinations agree moderately with previous relations\footnote{Note that these EoSs do not fit within GW170817s 90\% posterior on EoS - so we expect deviations consistent with the ``unconstrained" set of EoSs, rather than the ``constrained" set.}, while HS/NS combinations disagree significantly.
-This can be explained by the large reduction in tidal deformability for hybrid stars, are shown in Fig.
-2 of Ref.~\cite{Paschalidis2018}: when one star lies on the hadronic branch while the other is on the quark branch, they each see vast differences in $\tilde{\Lambda}$ - disrupting the binary Love relations as found for stars on the hadronic branch.
+First, we note that the NS/NS combination of stars gives consistent results to that found earlier -- as expected.
+Next, we observe that HS/HS combinations agree moderately with previous relations\footnote{Note that these EoSs do not fit within GW170817s 90\% posterior on EoS - so we expect deviations consistent with the ``unconstrained" set of EoSs, rather than the ``constrained" set.}, while HS/NS combinations disagree significantly.
+This can be explained by the large reduction in tidal deformability proceeding the transition pressure for hybrid stars, as shown in Fig.~\ref{fig:hybrid}.
+When one star lies on the hadronic-matter branch while the other is on the quark-matter branch, 
+the difference between tidal deformabilities becomes larger than expected for pure hadronic-matter stars.
+This results in a large deviation in the NS binary Love relations $\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$, disrupting the overall universality.
 {\ny{Sorry, I don't get it.
-Why does seeing ``a vast difference in Lambda tilde'' explain the loss of universality?
+Why does seeing ``a large difference in Lambda tilde'' explain the loss of universality?
 We have cases with small enough q that show much more universality than what we find for the same value of q in the HS/NS case.
 I guess what I am saying is that we should explore this more from a theory side to try to provide an explanation, or we should say nothing (or say we don't know why this is the case).}}
+{\zc{Nico, sorry this was a bad explanation on my part.
+when the two stars each see a large jump in $\Lambda$, the differences and sums of tidal deformabilities also see a big jump, and they ``jump off" the universal line as can be seen by the dashed bright green lines in fig.~\ref{fig:binLove}.
+I've rewritten this sentence to (hopefully) make more sense.}}
 
@@
 In particular, these binary pairs are selected from each of the following categories: (i) binaries with which one massive star has a quark matter core, while the other is pure hadronic matter (i.e.
-small enough mass that the transition point has not yet been reached), denoted HS/NS (green triangles); (ii) binary with both small-mass hadron stars, denoted NS/NS (red squares); and (iii) binary with both large-mass stars with quark matter cores, denoted HS/HS (magenta diamonds).
+small enough mass that the transition point has not yet been reached), denoted HS/NS (green triangles); (ii) binaries with two small-mass hadron stars, denoted NS/NS (red squares); and (iii) binaries with two large-mass stars with quark matter cores, denoted HS/HS (magenta diamonds).
 }
@@
 
-This discrepancy between hybrid and hadronic matter EoSs can be seen in Fig.~\ref{fig:binLove}, where the binary Love relations for the 10 hybrid star EoSs are shown in relation to the constrained and unconstrained nuclear matter EoSs.
-Observe how the residuals from the fit are quite good for low pressures (large $\Lambda_s$) when the the binaries consist of a NS/NS combination, before reaching the transitional pressure when the deviations become increasingly large ($\sim160$\% for $q=0.90$, $\sim37$\% for $q=0.75$, and $\sim6$\% for $q=0.50$) for HS/HS and HS/NS binaries.
+This discrepancy between the hybrid and hadronic matter EoSs can be seen in Fig.~\ref{fig:binLove}, where the binary Love relations for the 10 hybrid star EoSs are shown alongside the constrained and unconstrained nuclear matter EoSs.
+Observe how the residuals from the fit are quite good at low pressures (large $\Lambda_s$) where the the binaries consist of NS/NS combinations, before reaching the transitional pressure where the deviations become increasingly large ($\sim160$\% for $q=0.90$, $\sim37$\% for $q=0.75$, and $\sim6$\% for $q=0.50$) for HS/HS and HS/NS binaries.
 {\ny{Why is there a hump for the HS cases in green in Fig.
-7?}}
-
-To further investigate this phenomena, we consider binary Love fits to the HS branches, or NS branches \emph{individually}.
-It was found that by trying to fit binary Love relations to the full hybrid star EoSs failed, due to the difference in transitional masses $M_{\text{tr}}$.
+7?}}{\zc{The hump comes from the transition between NS and HS branches, as I describe in my above comment.
+If you are referring to the bottom panels of Fig 7, this hump is because I display the fractional difference of the \emph{HS} EoSs from the \emph{NS} fits - to show how badly they fit (although that is not as visible now that we are plotting absolute difference.
+Instead, I could plot their fractional difference from their own "HS" fits too.
+We can discuss this.}}
+
+To further investigate this phenomena, we consider binary Love fits to the HS or NS branches \emph{individually}.
+It was found that the binary Love relations failed to properly fit to the collection of full hybrid star EoSs, due to the varying transitional masses $M_{\text{tr}}$ across the various EoSs.
 To compensate for these differences, we separate the two branches into the NS (hadronic matter) and HS (hybrid matter) branches.
-We first observe that the NS branch obeys the ``hadronic" binary Love relations derived earlier in Sec.~\ref{sec:binLove-nuclear} within the variability found earlier, indicating no further need for additional fits.
-However, the HS branch does not, suggesting the need for a new ``hybrid" binary love fit pertaining to this branch.
-We begin by fitting the binary Love relations to the new HS branch, resulting in the fit coefficients found in the bottom row of Tab.~\ref{tab:binLovefit}.
-The fits are displayed in the top panel of Fig.~\ref{fig:binLove} as dot-dashed blue curves, showing a good relationship with the hybrid star branch.
-We urge caution with the use of these fits, as the small sample size (10 EoSs) as well as the occurrence of hybrid matter transitions only being available for certain mass ratios on certain EoSs, results in a less accurate fit than the nuclear-matter counterpart.
-Similar to before, the fractional difference from the fit for each HS branch is computed, resulting in a maximum variability of $18.488$\% for $q=0.90$.
+We first observe that the NS branches obey the ``hadronic" binary Love relations derived in Sec.~\ref{sec:binLove-nuclear} within the same EoS variability, indicating no further need for additional fits.
+However, the HS branches do not follow the same relations, suggesting the need for a new ``hybrid binary love fit" pertaining to this branch alone.
+We begin by fitting the binary Love curve in Eq.~\ref{eq:binLovefit} to the HS branches, resulting in the fit coefficients tabulated in the bottom row of Tab.~\ref{tab:binLovefit}.
+We note here that the Newtonian limit for this fit is not physical for quark-star matter, which does not reach low enough central densities.
+Attempts were made to remedy this by allowing the polytropic index $n$ to be either $0$ or a free fitting parameter, both of which failed.
+We instead leave the fits as they are, with the disclaimer that they do not properly limit to the Newtonian case.
+The fits are displayed in the top panel of Fig.~\ref{fig:binLove} as dot-dashed blue curves, showing a good relationship with the hybrid star branches used in the analysis.
+We urge caution with the use of these fits, as the limited sample size of 10 EoSs results in a less accurate fit than its nuclear-matter counterpart.
+Similar to the previous section, the fractional difference from the fit for each HS branch is computed, resulting in a maximum EoS variability of $18.49$\% for $q=0.90$.
 This result is strongly consistent with the results found for the nuclear matter fits of Sec.~\ref{sec:binLove-nuclear}.
@@
 We conclude this section with the observation that the hybrid star EoSs do \emph{not} conform to the fits performed on nuclear matter EoSs.
-This is not surprising, as the hybrid branch of the EoSs give inconsistent results between $\Lambda_1$ and $\Lambda_2$ with different masses; an issue not present for the single-star I-Love-Q relations.
+This is not surprising, as the hybrid branch of the EoSs forces inconsistent results between $\Lambda_1$ and $\Lambda_2$ with different masses; an issue not present for the single-star I-Love-Q relations.
 By separating the two branches of the hybrid EoSs, we find a new ``hybrid" branch binary Love fit which gives consistent results to that found for the nuclear matter fits. 
@@
 It is not exactly clear to me what the message you were trying to send was.}}
-
-\subsubsection{Error Marginalization}
-
-{\ny{This section seems out of place here, as it really matters for the next section. We shoudl consider re-structuring.}}
+{\zc{You're right - I tried to change this by using leaving the polytropic index (n) as an additional fitting parameter.
+Doing this gives n=1.7, and all other parameters $>10^7$.
+The fit looks good but I'm skeptical about those fit values.
+Additionally, if I set n=0, the fits diverge.
+Instead, I wrote a few sentences in the paper saying how it doesn't properly limit to the Newtonian case, and how we tried to remedy it.
+I'm welcome to any suggestions!}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%% Begin Future Observations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Impact on future observations}\label{sec:observations}
 
@@
 Current interferometer sensitivities are not yet small enough to accurately constrain $\tilde{\Lambda}$.
-For example, GW170817 was detected by LIGO observing run 2 (``O2")~\cite{aLIGO} and was able to constrain $\tilde{\Lambda}$ to a $90\%$ confidence interval of 325 (this relates to a standard deviation of $\sigma_{\tilde{\Lambda}}=198$) centered at $\tilde{\Lambda}=395$.
+For example, GW170817 was detected by LIGO observing run 2 (``O2")~\cite{aLIGO} and was able to constrain $\tilde{\Lambda}$ to a $90\%$ confidence interval of 325 (or $\sigma_{\tilde{\Lambda}}=198$) centered at $\mu_{\tilde{\Lambda}}=395$.
 This corresponds to statistical uncertainties on the order of $\sim 82\%$, which vastly dominates the error budget compared to the small systematic errors picked up by EoS variation in the EoS-insensitive relations.
-This implies that currently, improved EoS-insensitive relations will only make a negligible difference in tidal parameter extraction.
-
-In Sec.~\ref{sec:observations}, we compare the statistical errors on the parameter extraction of tidal parameters to the systematic errors introduced by using improved binary Love relations, computed in the current section.
+This implies that currently, the use of improved EoS-insensitive relations will only make a negligible difference on the extraction of tidal parameters.
+
+In Sec.~\ref{sec:marginalization}, we first compute the systematic errors introduced by using the improved binary Love relations derived earlier.
+In Sec.~\ref{sec:futureObservations}, we compare the statistical errors on the parameter extraction of tidal parameters to the above-mentioned systematic errors.
 This is repeated for 5 future detectors, where multiple event detections become important.
 Because future events occur with weighted tidal parameters $\tilde\Lambda$ which are unknown at this time, we can not accurately combine the uncertainties on $\tilde\Lambda$ for multiple events.
-To remedy this, we re-parameterize the waveform and consider the $\lambda_0$ and $\lambda_1$ tidal coefficients produced by Taylor expanding unitful tidal deformability $\lambda \equiv \Lambda m^5$ about $m_0=1.4\text{ M}_{\odot}$:
+To remedy this, we re-parameterize the waveform and instead consider the $\lambda_0$ and $\lambda_1$ tidal coefficients produced by Taylor expanding the unitful tidal deformability $\lambda \equiv \Lambda m^5$ about $m_0=1.4\text{ M}_{\odot}$:
 \begin{equation}
@@
 as discussed in Ref.~\cite{delPozzo:TaylorTidal}.
-The new tidal parameters $\lambda_0$ and $\lambda_1$ do not depend on mass, and therefore are identical for every future binary NS merger, and thus may be combined in uncertainty.
-For this reason, we consider the new tidal parameters $\lambda_0$ and $\lambda_1$ for the remainder of the investigation.
-
-In this section, we investigate the residuals in $\lambda_0(\Lambda_a,\Lambda_s,q)$ in order to marginalize over the intrinsic error in the binary Love relations.
+The new tidal parameters $\lambda_0$ and $\lambda_1$ do not depend on mass, thus are identical for every future binary NS merger, and may be combined in uncertainty.
+Under this reasoning, we consider the new tidal parameters $\lambda_0$ and $\lambda_1$ for the remainder of the investigation.
+
+\subsection{Error Marginalization}\label{sec:marginalization}
+
+In this section, we investigate the residuals on $\lambda_0(\Lambda_a,\Lambda_s,q)$ in order to marginalize over the intrinsic error in the binary Love relations.
 In particular, we restrict our focus to only the constrained set of EoSs.
-Residuals in $\lambda_0$ are computed as $\lambda_0^{\text{fit}}-\lambda_0^{\text{true}}$, where $\lambda_0^{\text{true}}=\lambda_0(\Lambda_a,\Lambda_s,q)$ corresponds to the true value predicted by the sample EoSs, and $\lambda_0^{\text{fit}}=\lambda_0(\Lambda_a^{\text{fit}}(\Lambda_s,q),\Lambda_s,q)$ corresponds to the value obtained through the EoS-insensitive relations found in Sec.~\ref{sec:binLove-nuclear}.
-Following Ref.~\cite{Katerina:residuals}, we assume the residuals in $\lambda_0$ observe a Gaussian distribution with mean and standard deviation given by:
+Residuals on $\lambda_0$ are computed as $\lambda_0^{\text{fit}}-\lambda_0^{\text{true}}$, where $\lambda_0^{\text{true}}=\lambda_0(\Lambda_a,\Lambda_s,q)$ corresponds to the true values predicted by the sample EoSs, and $\lambda_0^{\text{fit}}=\lambda_0(\Lambda_a^{\text{fit}}(\Lambda_s,q),\Lambda_s,q)$ corresponds to the values obtained through the EoS-insensitive relations found in Sec.~\ref{sec:binLove-nuclear}.
+Following Ref.~\cite{Katerina:residuals}, we assume the residuals on $\lambda_0$ observe a Gaussian distribution with mean and standard deviation given by:
 \begin{align}
@@
 \end{align}
-Similar to Ref.~\cite{Katerina:residuals}, we fit the individual components to be:
+Similar to Ref.~\cite{Katerina:residuals}, we fit the individual components to the following power functions:
 \begin{align}
@@
 \end{align}
-The fitting parameters $\mu_i$ and $\sigma_i$ are tabulated in Table~\ref{tab:marginalized}.
-Figure~\ref{fig:qLsResiduals} shows the $\lambda_0$ residuals binned in both q and $\Lambda_s$, highlighting the error weights across the $(q,\Lambda_s)$ parameter space.
-Observe how $q\sim0.5$ and $\Lambda_s\sim2000$ observe the highest errors, while the low and high values of $q$ and $\Lambda_s$ see minimal uncertainties.
+The fitting parameters $\mu_i$ and $\sigma_i$ are tabulated in Tab.~\ref{tab:marginalized}, and Fig.~\ref{fig:qLsResiduals} shows the $\lambda_0$ residuals binned in both q and $\Lambda_s$, highlighting the error weights across the $(q,\Lambda_s)$ parameter space.
+Observe how $q\sim0.5$ and $\Lambda_s\sim2000$ obtain the highest errors, while the low and high values of $q$ and $\Lambda_s$ have minimal uncertainties.
 
@@
 \noalign{\smallskip}
-$\mu_1$ & $-1.0158750\times10^{-29}$ & $\sigma_1$ & $-1.1953582\times10^{-33}$\\
-$\mu_2$ & $5.3758312\times10^{-27}$ & $\sigma_2$ & $4.0560936\times10^{-30}$\\
-$\mu_3$ & $-6.8500063\times10^{-25}$ & $\sigma_3$ & $5.6991756\times10^{-27}$\\
-$\mu_4$ & $1.0235088\times10^{-24}$ & $\sigma_4$ & $-1.3342207\times10^{-26}$\\
-$\mu_5$ & $-3.6802625\times10^{-25}$ & $\sigma_5$ & $7.1682441\times10^{-24}$\\
- &  & $\sigma_6$ & $-1.5947653\times10^{-23}$\\
- &  & $\sigma_7$ & $1.0979389\times10^{-23}$\\
- &  & $\sigma_8$ & $-2.1389918\times10^{-24}$\\
+$\mu_1$ & $-1.016\times10^{-29}$ & $\sigma_1$ & $-1.195\times10^{-33}$\\
+$\mu_2$ & $5.376\times10^{-27}$ & $\sigma_2$ & $4.056\times10^{-30}$\\
+$\mu_3$ & $-6.850\times10^{-25}$ & $\sigma_3$ & $5.699\times10^{-27}$\\
+$\mu_4$ & $1.024\times10^{-24}$ & $\sigma_4$ & $-1.334\times10^{-26}$\\
+$\mu_5$ & $-3.680\times10^{-25}$ & $\sigma_5$ & $7.168\times10^{-24}$\\
+ &  & $\sigma_6$ & $-1.595\times10^{-23}$\\
+ &  & $\sigma_7$ & $1.098\times10^{-23}$\\
+ &  & $\sigma_8$ & $-2.139\times10^{-24}$\\
  \noalign{\smallskip}
@@
 
-Figure~\ref{fig:residuals} displays the Gaussian distribution of $\lambda_0$ residuals for both the constrained, and unconstrained sets of EoSs for comparison.
-Observe how the standard deviations $\sigma=1.52\times10^{-25} \text{ s}^5$ and $\sigma=12.21\times10^{-25} \text{ s}^5$ show a large decrease between the unconstrained and constrained sets of EoSs.
-In addition, we find the 90th, 99th, and 100th percentiles on $\lambda_0$ to be $P_{90}=2.06\times10^{-25} \text{ s}^5$, $P_{99}=6.61\times10^{-25} \text{ s}^5$, and $P_{100}=17.36\times10^{-25} \text{ s}^5$ for the constrained EoSs.
-Because the un-binned residuals seen in Fig.~\ref{fig:residuals} are dominated by the low-error regions of parameter space ($\Lambda_s \rightarrow 0$, $\Lambda_s \rightarrow \infty$, $q \rightarrow 0$ and $q \rightarrow 1$) shown by Fig.~\ref{fig:qLsResiduals}, we consider the 90th percentile error (indicated by the dashed green line in Fig.~\ref{fig:qLsResiduals}) for the remainder of the analysis, in order to further take into account the high-error regions of the parameter space ($\Lambda_s \sim 2000$, $q\sim0.5$).
+Figure~\ref{fig:residuals} displays the un-binned Gaussian distribution of $\lambda_0$ residuals for both the constrained, and unconstrained sets of EoSs for comparison.
+Observe how the standard deviations $\sigma=1.52\times10^{-25} \text{ s}^5$ and $\sigma=12.21\times10^{-25} \text{ s}^5$ show a large decrease from the unconstrained to the constrained sets of EoSs.
+Additionally, we find the 90th, 99th, and 100th percentiles on $\lambda_0$ to be $P_{90}=2.06\times10^{-25} \text{ s}^5$, $P_{99}=6.61\times10^{-25} \text{ s}^5$, and $P_{100}=17.36\times10^{-25} \text{ s}^5$ for the constrained EoSs.
+Because the un-binned residuals seen in Fig.~\ref{fig:residuals} are dominated by the low-error regions of the parameter space ($\Lambda_s \rightarrow 0$, $\Lambda_s \rightarrow \infty$, $q \rightarrow 0$ and $q \rightarrow 1$) shown by Fig.~\ref{fig:qLsResiduals}, we consider the 90th percentile error (indicated by the dashed green line in Fig.~\ref{fig:qLsResiduals}) for the remainder of the analysis, in order to further take into account the high-error regions of the parameter space ($\Lambda_s \sim 2000$, $q\sim0.5$).
 We take this value of $P_{90}=2.06\times10^{-25} \text{ s}^5$ to be the systematic measurement error introduced by using the improved binary Love relations on the parameter extraction of $\lambda_0$, indicated by the dashed indigo line in Fig.~\ref{fig:stackedFisher}.
 Similarly, we derive the systematic measurement error on $\tilde\Lambda$ to be $12.01$, shown in Fig.~\ref{fig:singleFisherLt}.
-Currently, the statistical error of $26.53 \times 10^{-25} \text{ s}^5$ on $\lambda_0$ from GW170817 dominate the error budget compared to the systematic error of $2.06\times10^{-25} \text{ s}^5$, as seen in Fig.~\ref{fig:stackedFisher}.
+Currently, the statistical error of $26.53 \times 10^{-25} \text{ s}^5$ on $\lambda_0$ from GW170817 dominates the error budget compared to the systematic error of $2.06\times10^{-25} \text{ s}^5$, as seen in Fig.~\ref{fig:stackedFisher}.
 This means that, for the current ``O2" detector sensitivity, the use of improved binary Love relations will only make a negligible difference on the extraction of $\tilde\Lambda$.
-However, future detectors (for example aLIGO, A\texttt{+}, Voyager, CE, and ET) are planned with large reductions in sensitivity - both decreasing the statistical errors and allowing for a larger binary NS merger detection rate; further reducing uncertainties.
+However, future detectors (for example aLIGO, A\texttt{+}, Voyager, CE, and ET) are planned with large reductions in sensitivity - both decreasing the statistical errors and allowing for a larger binary NS merger detection rate; further reducing the statistical uncertainties.
 In Sec.~\ref{sec:observations}, we analyze this further and discuss when the systematic errors from EoS-insensitive relations become comparable to the statistical errors.
@@
 \end{center}
-\caption{
-$\lambda_0$ residuals binned in $q$ (top) and $\Lambda_s$ (bottom), highlighting the different error weights across the entire $(q,\Lambda_s)$ parameter space.
+\caption{$\lambda_0$ residuals binned in $q$ (top) and $\Lambda_s$ (bottom), highlighting the different error weights across the entire $(q,\Lambda_s)$ parameter space.
 In this figure, the violet circles indicate the standard deviation of each bin in $q$-space ($\Lambda_s$-space), while the black dashed lines represent the best fit given by Eqs.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%% Begin Future Observations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Impact on future observations}\label{sec:observations}
-In this section, we estimate the feasibility of utilizing improved EoS-insensitive relations in future binary NS merger events.
+\subsection{Future Observations}\label{sec:futureObservations}
+In this section, we estimate the feasibility of utilizing the improved EoS-insensitive relations in future binary NS merger events.
 This estimate is acquired through a simple Fisher analysis~\cite{Finn:Fisher,Cutler:Fisher} which approximates the accuracy with which one can extract best-fit parameters $\theta^a$, given a prior template waveform.
@@
 
-Next, we consider events identical to GW170817 detected on future design sensitivity upgrades and detectors $A \equiv ($O2, aLIGO, A\texttt{+}, Voyager, CE, ET-D$)$, shown in Fig.~\ref{fig:sensitivities}, to determine if and when the statistical errors associated with parameter extraction of $\lambda_0$ drop below the systematic EoS variation errors from using binary Love relations.
-The process we use for each detector sensitivity $S_n^A(f)$ is as follows:
-\begin{itemize}
-\item Perform a Fisher analysis as outlined above using $S_n^A(f)$, while restricting the luminosity distance $D_L$ such that $\rho^{\text{O2}}_{\text{GW170817}}=32.4$ would be achieved on O2 sensitivity $S_n^{\text{O2}}(f)$.
+Next, we consider events identical to GW170817 detected on future design sensitivity upgrades and detectors $A \equiv ($O2, aLIGO, A\texttt{+}, Voyager, CE, ET-D$)$, shown in Fig.~\ref{fig:sensitivities}.
+Further, we consider the combined statistical uncertainties of $N_A$ events detected over 1 year on detector $A$, determined by integrating the local binary NS (BNS) merger rate over redshifts up to the horizon redshift of each detector.
 Here we assume low spin priors $|\chi| \leq 0.05$, as well as $0 \text{ s}^5 \leq \lambda_0 \leq 5 \times 10^{-23} \text{ s}^5$ and $-5 \times 10^{-18} \text{ s}^4\text{ M}_{\odot} \leq \lambda_1 \leq 0 \text{ s}^4\text{ M}_{\odot}$~\cite{delPozzo:TaylorTidal}.
-This results in SNR $\rho^A_{\text{GW170817}}$ and statistical error $\sigma_\text{GW170817}^A$ accrued in the extraction of $\lambda_0$ on detector $A$.
-\item Generate a population of $N_A$ events corresponding to the expected binary NS merger detection rate for detector $A$, following the distribution $f=3 \rho_{\text{th}}^3/\rho^4$~\cite{Shutz:SNR,Chen:SNR} with a network SNR threshold of $\rho_{\text{th}}=8$.
-The number of events $N_A$ is calculated by taking into account the BNS merger rate history throughout all redshift values within detector As' horizon distance $z_h$, as shown by Eq.
-(10) of Ref.~\cite{Cutler:BNSmerger}:
-\begin{equation}
-N_A=\Delta \tau_0 \int\limits^{z_{h}}_0 4 \pi \lbrack  a_0r_1(z)\rbrack^2 \mathcal{R} r(z) \frac{d \tau}{dz} dz.
-\end{equation}
-Here, $a_0r_1(z)$, $\frac{d\tau}{dz}$, and $r(z)$ for our chosen cosmology are given by:
-\begin{equation}
-a_0r_1(z) = \frac{1}{H_0}\int\limits^z_0 \frac{dz'}{\sqrt{(1-\Omega_{\Lambda})(1+z')^3+\Omega_{\Lambda}}},
-\end{equation}
-\begin{equation}
-\frac{d\tau}{dz} = \frac{1}{H_0} \frac{1}{1+z}\frac{1}{\sqrt{(1-\Omega_{\Lambda})(1+z')^3+\Omega_{\Lambda}}},
-\end{equation}
-\begin{equation}
-r(z) = \left\{
-\begin{array}{ll}
-      1+2z & z \leq 1 \\
-      \frac{3}{4}(5-z) & 1\leq z\leq 5 \\
-      0 & z\geq 5\\ 
-\end{array} 
-\right.
-\end{equation}
-
-where $H_0 = 70 \text{km s}^{-1}\text{Mpc}^{-1}$ is the local Hubble constant, and $\Omega_{\Lambda}=0.67$ is the universe's vacuum energy density.
-Here we choose an observing period $\Delta \tau = 1$ year {\ny{Should this be tau 0?}}, and calculate the detection rate for the upper, central, and lower limits of the local binary NS coalescence rate density $\mathcal{R}=1540^{+3200}_{-1220} \text{ Gpc}^{-3}\text{yr}^{-1}$~\cite{Abbott2017}, giving the rates shown in the second column of Table~\ref{tab:variances}.
-\item Compute the overall population standard deviation, taking into account sources at varying redshifts as done in Eq. (3) of Ref.~\cite{Takahiro}:
-\begin{equation}
-\sigma_{N_A}^{-2}=\Delta \tau \int\limits^{z_h}_04 \pi \lbrack a_0 r_1(z)\rbrack^2 \mathcal{R}r(z)\frac{d\tau}{dz}\sigma^A_i(z)^{-2}dz
-\end{equation}
-where $\sigma_i^A(z)$ is computed by the relations $\sigma_i^A \times \rho_i^A = \sigma_{\text{GW170817}}^A \times \rho_{\text{GW170817}}^A$.
-\item \zc{These bullet points are getting kind of long and detailed. They (at least the low-level version of them) could go in a new appendix section - let me know what everyone thinks :)}
-\end{itemize}
-
-{\ny{I think you need more detail because I didn't understand how you computed the combined statistical error.
-Perhaps you could give a concrete example of 1 iteration of the method, say if N = 2.
-This could make it much clearer and yes, you could move all of this to an appendix.
-}}
+The process we utilize to compute single and combined statistical uncertainties for each detector sensitivity $S_n^A(f)$ is detailed in App.~\ref{app:stackingProcedure}.
+From this, we determine if and when the statistical errors associated with the parameter extraction of $\lambda_0$ drop below the systematic EoS variation errors from using binary Love relations.
 
@@
 \caption{
-Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue) in the extraction of $\tilde\Lambda$ from GW170817 (O2) as if observed with future interferometers aLIGO, A\texttt{+}, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
-Also shown is the systematic error on $\tilde\Lambda$ (indigo) derived using the same method used to compute the systematic error on $\lambda_0$.
-This is similar to Fig.~\ref{fig:stackedFisher} where the extraction efficiency of $\lambda_0$ was plotted.
-However, in this case multiple events can \emph{not} be combined due to the variation in mass and therefore $\tilde\Lambda$ among events.
+Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ in the extraction of $\tilde\Lambda$ from GW170817 (O2) as if observed with future interferometers aLIGO, A\texttt{+}, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
+Also shown is the systematic error on $\tilde\Lambda$ derived using the same method used to compute the systematic error on $\lambda_0$.
+This is similar to Fig.~\ref{fig:stackedFisher} where the extraction efficiency of $\lambda_0$ was plotted, however, in this case multiple events can \emph{not} be combined due to the variation in mass and therefore $\tilde\Lambda$ among events.
 }
@@
 \caption{
-Tabulated results for the estimated statistical errors on $\lambda_0$ for the combined results of $N_A$ detections corresponding to the estimated upper, central, and lower limits of the binary NS merger detection rate $R$.
+Tabulated results for the estimated statistical errors on $\lambda_0$ for the combined results of $N_A$ detections corresponding to the estimated upper, central, and lower limits of the binary NS merger detection rate $\mathcal{R}$.
 This is repeated for 5 future detector sensitivities: aLIGO, A\texttt{+}, Voyager, CE, and ET.
-Below, $\rho^A_{\text{GW170817}}$ and $\sigma^A_{\text{GW170817}}$ correspond to the approximate SNR and $\sigma_{\lambda_0}$ of GW170817 had it been observed by the future interferometer, and $\sigma^A_N$ corresponds to the final uncertainty on $\lambda_0$ after $N_A$ detections on interferometer $A$.
+Below, $\rho^A_{\text{GW170817}}$ and $\sigma^A_{\text{GW170817}}$ correspond to the approximate SNR and $\sigma_{\lambda_0}$ of GW170817 had it been observed by the future interferometer, and $\sigma^A_N$ corresponds to the overall uncertainty on $\lambda_0$ after $N_A$ detections on interferometer $A$.
 It can be seen here that the statistical errors on $\lambda_0$ become comparable with the systematics (set to be $P_{90}=12.014$) from using improved binary Love relations from Voyager and on, indicating when it may be safe to utilize new EoS-insensitive relations.
-Note the approximation for $\sigma^A_N$ under the O2 detector sensitivity is left blank due to the singularity of the detected event.
-These results are shown graphically in Fig.~\ref{fig:stackedFisher}.
+Note that the approximation for $\sigma^A_N$ under the O2 detector sensitivity is left blank due to the singularity of the detected event.
+These results are also shown graphically in Fig.~\ref{fig:stackedFisher}.
 }\label{tab:variances}
@@
 Next, we repeat the process upon the injection of the IMRD + NRTidal waveform in order to demonstrate the effect of waveform mismodeling.
-The results are shown in Fig.~\ref{fig:stackedFisher} by blue outlined circles (single detection uncertainties) and the outlined dashed maroon region (combined uncertainties from multiple detections).
+The results are shown in Fig.~\ref{fig:stackedFisher} as blue outlined circles (single detection uncertainties) and the outlined dashed maroon region (combined uncertainties from multiple detections).
 Observe the noticeable difference between the extraction efficiencies for the two different tidal corrections - highlighting the need for further waveform modeling for future interferometers.
@@
 {\ny{Super confused about Fig. 1...}}
+{\zc{Yes, there is a \emph{lot} of info in this figure.
+The filled blue circles are the statistical uncertainties on $\lambda_0$ for GW170817 as if it had been detected on Detector A=(O2, aLIGO, A+, Voyager, ET, CE), where the x-axis corresponds to the SNR on that detector as if it found GW170817.
+The filled turquoise region is the combined statistical uncertainty on the detection of $N_A$ events on each detector A, computed using the bulleted process above (moved to the appendix).
+There is some height to this shaded region because I consider the the upper and lower error bars of the local BNS merger rate $\mathcal{R}$ - giving us a range of $N_A$'s to consider for each detector.
+We can talk more about this over Skype.}}
 
@@
 This implies that the use and further improvement of EoS-insensitive relations is not only justified, but necessary, for future binary NS merger detections.
-Further, we investigate the dependence of the measurement accuracy of $\tilde\Lambda$ on the binary NS mass ratio $q$ for fixed chirp mass $\mathcal{M}=1.88\text{ M}_{\odot}$ in Appendix~\ref{app:measurement}.
+Additionally, we find that the effect of waveform mismodeling is indeed important for future observations as the statistical errors continue to decrease.
+Further, we investigate the dependence of the measurement accuracy on $\tilde\Lambda$ on the binary NS mass ratio $q$ for fixed chirp mass $\mathcal{M}=1.88\text{ M}_{\odot}$ in Appendix~\ref{app:measurement}.
 
@@
 The recent GW observation of binary NS merger GW170817 placed constraints on the supranuclear matter EoS for NSs.
-We take advantage of this by generating a restricted set of spectral EoSs which agree with this observation to reduce uncertainties upon the extraction of tidal parameters from future GW events.
+We take advantage of this by generating a restricted set of spectral EoSs which agree with this observation in order to reduce the uncertainties upon the extraction of tidal parameters from future GW events.
 Important previous work by Yagi and Yunes~\cite{Yagi:ILQ,Yagi:binLove} found EoS-insensitive relations between symmetric and antisymmetric combinations of NS tidal deformabilities, which aid in the extraction of said tidal parameters.
 We find an improvement upon these EoS-insensitive relations by a factor of $\sim 59$\% for stars with mass ratios of $0.75$ by restricting to the EoS posterior samples from GW170817s 90\% credible region on pressure as a function of density.
-Similarly, we find an increase in C-Love and I-Love-Q universality by a factors of $\sim 76$\% and $\sim 50$\%, respectively.
-We also show new R-Love relations relating the NS radius to its tidal deformability, displaying a maximum of $18.88\%$ EoS variability from the fit discussed in Sec.~\ref{sec:clove}.
-Additionally, we find that hybrid quark-hadron star EoSs \emph{do} obey the I-Love-Q and C-Love universality, albeit with a slightly higher maximum EoS variability as displayed in Tabs.~\ref{tab:hybridCompare} and ~\ref{tab:hybridCompareClove}.
+Similarly, we find an increase in C-Love and I-Love-Q universality by factors of $\sim 76$\% and $\sim 50$\%, respectively.
+We also show new R-Love EoS-insensitive relations relating the NS radius to its tidal deformability, displaying a maximum of $18.88\%$ EoS variability from the fit discussed in Sec.~\ref{sec:clove}.
+Additionally, we find that hybrid quark-hadron star EoSs \emph{do} obey the I-Love-Q and C-Love universality, albeit with slightly higher maximum EoS variabilities as displayed in Tabs.~\ref{tab:hybridCompare} and ~\ref{tab:hybridCompareClove}.
 In addition, we find that binaries consisting of one massive hybrid quark-hadron star, and one small-mass hadron star do not obey the binary Love relations -- explained by the large difference in $\tilde{\Lambda}$ displayed between the constituent stars.
 To improve on this, we construct new ``hybrid matter binary Love relations", applied to only the hybrid branches of the transitional EoSs.
-This results in EoS variability similar to that found for the nuclear matter fits.
-Further, we analyze the impact of this improvement for future binary NS merger detections, as the current detector sensitivity is not yet small enough to accurately constrain $\tilde{\Lambda}$ enough for EoS-insensitive relations to make a difference.
-We find that future interferometers Voyager, CE, and ET-D all experience statistical uncertainties upon the extraction of $\tilde{\Lambda}$ small enough to become comparable to the systematic errors injected through the use of improved EoS-insensitive relations (found to be $12.014$), as depicted in Fig.~\ref{fig:stackedFisher} and Table~\ref{tab:variances}.
+This results in a maximal EoS variability similar to that found for the nuclear matter fits.
+Further, we analyze the impact of this improvement for future binary NS merger detections, as the current detectors are not yet sensitive enough to accurately constrain $\tilde{\Lambda}$ for the improved EoS-insensitive relations to make a difference.
+We find that future interferometers Voyager, CE, and ET-D all experience statistical uncertainties upon the extraction of $\tilde{\Lambda}$ small enough to become comparable to the systematic errors injected through the use of improved EoS-insensitive relations, as depicted in Fig.~\ref{fig:stackedFisher} and Table~\ref{tab:variances}.
 Additionally, we considered the effect of waveform mismodeling by comparing Fisher analyses using two different tidal corrections to the PhenomD waveform: 6PN and NRTidal.
@@
 Finally, in Appendix~\ref{app:measurement} we investigate the effect of NS binary mass ratio q on the measurement accuracy of $\tilde\Lambda$.
-We find that second generation interferometers lose accuracy as one increases the mass ratio, while third generation detectors observe a large increase of accuracy due to the correlations between $\tilde\Lambda$ and $\delta\tilde\Lambda$.
+We find that the second generation interferometers lose accuracy as one increases the mass ratio, while the third generation detectors observe a large increase in accuracy due to the correlations between $\tilde\Lambda$ and $\delta\tilde\Lambda$.
 This indicates that the use and further improvement of EoS-insensitive relations is justified for future GW observations of binary NS merger events.
@@
 By reducing the number of required waveform model parameters, surrogate models aid in the extraction of NS observables from GW detections.
-The improvement of multipole love relations can then be used to increase the accuracy of surrogate models.
+The improvement in the multipole love relations can then be used to increase the accuracy of surrogate models.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%% Begin Appendix A: Stacked events process %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\appendix
+\section{Computation of statistical uncertainties}\label{app:stackingProcedure}
+
+In this appendix, we detail the process used to compute the statistical uncertainties on the extraction of $\lambda_0$ from the gravitational waveform.
+This is accomplished with a simple Fisher analysis described in Sec.~\ref{sec:futureObservations}, where we first consider single-events identical to GW170817 as if they were detected on future detectors $A \equiv ($ O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, ET~\cite{ET}, CE~\cite{Ap_Voyager_CE}$)$.
+We conclude by simulating a population of $N_A$ events for each interferometer, approximating the number of events detected on detector $A$ over an observing period of one year.
+This is used to combine the statistical uncertainties, resulting in an approximation on the overall measurement accuracy of $\lambda_0$, which is compared to the systematic errors computed in Sec.~\ref{sec:marginalization}.
+The process used to achieve this is outlined below:
+
+\begin{enumerate}
+\item[(i)] Perform a Fisher analysis as outlined in Sec.~\ref{sec:futureObservations} using detector sensitivity $S_n^A(f)$, while restricting the luminosity distance $D_L$ such that an SNR of $\rho^{\text{O2}}_{\text{GW170817}}=32.4$ would be achieved on O2 sensitivity $S_n^{\text{O2}}(f)$.
+Here we assume low spin priors $|\chi| \leq 0.05$, as well as $0 \text{ s}^5 \leq \lambda_0 \leq 5 \times 10^{-23} \text{ s}^5$ and $-5 \times 10^{-18} \text{ s}^4\text{ M}_{\odot} \leq \lambda_1 \leq 0 \text{ s}^4\text{ M}_{\odot}$~\cite{delPozzo:TaylorTidal}.
+This results in a SNR $\rho^A_{\text{GW170817}}$ and a single-event statistical error $\sigma_\text{GW170817}^A$ accrued in the extraction of $\lambda_0$ on detector $A$.
+
+\item[(ii)] Generate a population of $N_A$ events corresponding to the expected binary NS merger detection rate for detector $A$, following the probability distribution~\cite{Shutz:SNR,Chen:SNR}:
+\begin{equation}\label{eq:population}
+f(\rho)=3 \rho_{\text{th}}^3/\rho^4
+\end{equation}
+with a network SNR threshold of $\rho_{\text{th}}=8$.
+The number of events $N_A$ is calculated by taking into account the BNS merger rate history throughout all redshift values within detector As' horizon distance $z_h$, as shown by Eq.
+(10) of Ref.~\cite{Cutler:BNSmerger}:
+\begin{equation}
+N_A=\Delta \tau_0 \int\limits^{z_{h}}_0 4 \pi \lbrack  a_0r_1(z)\rbrack^2 \mathcal{R} r(z) \frac{d \tau}{dz} dz.
+\end{equation}
+Here, $a_0r_1(z)$, $\frac{d\tau}{dz}$, and $r(z)$ for our chosen cosmology are given by:
+\begin{equation}
+a_0r_1(z) = \frac{1}{H_0}\int\limits^z_0 \frac{dz'}{\sqrt{(1-\Omega_{\Lambda})(1+z')^3+\Omega_{\Lambda}}},
+\end{equation}
+\begin{equation}
+\frac{d\tau}{dz} = \frac{1}{H_0} \frac{1}{1+z}\frac{1}{\sqrt{(1-\Omega_{\Lambda})(1+z')^3+\Omega_{\Lambda}}},
+\end{equation}
+\begin{equation}
+r(z) = \left\{
+\begin{array}{ll}
+      1+2z & z \leq 1 \\
+      \frac{3}{4}(5-z) & 1\leq z\leq 5 \\
+      0 & z\geq 5\\ 
+\end{array} 
+\right.
+\end{equation}
+
+where $H_0 = 70 \text{km s}^{-1}\text{Mpc}^{-1}$ is the local Hubble constant, and $\Omega_{\Lambda}=0.67$ is the universe's vacuum energy density.
+Here we choose an observing period $\Delta \tau_0 = 1$ year, and calculate the detection rate for the upper, central, and lower limits of the local binary NS coalescence rate density $\mathcal{R}=1540^{+3200}_{-1220} \text{ Gpc}^{-3}\text{yr}^{-1}$~\cite{Abbott2017}, giving the rates $N_A$ shown in the second column of Table~\ref{tab:variances}, as well as the turquoise shaded region in Fig.~\ref{fig:stackedFisher}.
+
+\item[(iii)] Compute the combined population standard deviation $\sigma_{N_A}$, taking into account sources at varying redshifts as was done in Eq. (3) of Ref.~\cite{Takahiro}:
+\begin{equation}
+\sigma_{N_A}^{-2}=\Delta \tau \int\limits^{z_h}_04 \pi \lbrack a_0 r_1(z)\rbrack^2 \mathcal{R}r(z)\frac{d\tau}{dz}\sigma^A_i(z)^{-2}dz.
+\end{equation}
+Here, we compute the populations' single-event uncertainties $\sigma_i^A(z)$ via the simple SNR scaling factor: 
+\begin{equation}
+\frac{\rho_i^A}{\rho_{\text{GW170817}}^A} = \frac{\sigma_{\text{GW170817}}^A}{\sigma_i^A},
+\end{equation}
+where $\rho_i^A$ is the SNR of simulated event $i$ computed from Eq.~\ref{eq:population}, and $\rho_{\text{GW170817}}^A$ and $\sigma_{\text{GW170817}}^A$ are the known SNR and uncertainties of the GW170817 event from step (i).
+\end{enumerate}
+
 %%%%%%%%%%%%%%%%%%%%%%%%% Begin Appendix A: measurement accuracy as a functino of q %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
 \section{Measurement accuracy as a function of binary mass ratio}\label{app:measurement}
-In this appendix, we discuss the effects of the binary NS mass ratio on the measurement accuracy of $\tilde\Lambda$ for various interferometers. 
-The left panel of Fig.~\ref{fig:massVariation} displays an approximation of the $\tilde\Lambda$ measurement accuracy as a function of increasing mass ratio $q$ (for a fixed chirp mass of $\mathcal{M}=1.188 \text{ M}_{\odot}$ corresponding to GW170817), using the Fisher analysis techniques described in Sec.~\ref{sec:observations}.
-We observe two points of interest about these trends: (i) the second generation detectors (O2, aLIGO, A\texttt{+}, and Voyager) typically become less accurate as the mass ratio approaches unity, (ii) the third generation detectors (CE and ET) observe the opposite behavior-- a fast growth in accuracy as the mass ratio increases.
+In this appendix, we discuss the effects of the binary NS mass ratio $q$ on the measurement accuracy of $\tilde\Lambda$ for various interferometers. 
+The top panel of Fig.~\ref{fig:massVariation} displays an approximation of the $\tilde\Lambda$ measurement accuracy as a function of increasing mass ratio $q$ (for a fixed chirp mass of $\mathcal{M}=1.188 \text{ M}_{\odot}$ corresponding to GW170817), using the Fisher analysis techniques described in Sec.~\ref{sec:observations}.
+We observe two points of interest about these trends: (i) the second generation detectors (O2, aLIGO, A\texttt{+}, and Voyager) typically become less accurate as the mass ratio approaches unity, and (ii) the third generation detectors (CE and ET) observe the opposite behavior-- a fast growth in accuracy as the mass ratio increases.
 For the remainder of this appendix, we attempt to explain the opposing behaviors of the second and third generation interferometers on the extraction of $\tilde\Lambda$.
@@
 The removal of parameter correlations is approximated by setting certain Fisher matrix elements to 0, as described in Appendix.~\ref{app:measurement}.
-Observe how the left panel shows strong disagreement between second and third generation detectors, while the right panel shows identical behavior.
-This indicates that parameter correlations between $\tilde\Lambda$ and higher PN order parameter $\delta\tilde\Lambda$ to be the culprit in such a disagreement.
+Observe how the top panel shows strong disagreement between second and third generation detectors, while the bottom panel shows identical behavior.
+This indicates that parameter correlations between $\tilde\Lambda$ and higher PN order parameter $\delta\tilde\Lambda$ is the culprit in such a disagreement.
 }
@@
 We begin by considering the correlations between individual template parameters and $\tilde\Lambda$, given in Eq.~\ref{eq:template}.
-A simple approximation on the amplitude of these correlations can be performed by assuming all other correlations are non-existing.
-Correlations between parameters $\tilde\Lambda$ and $\theta^a$ alone is achieved by setting all off-diagonal Fisher matrix elements to $0$, except for the $(i,j)$ components such that both $i$ and $j$ correspond to the $\tilde\Lambda$ and $\theta^a$ parameters.
+A simple approximation for the amplitude of these correlations can be performed by assuming that all of the other correlations are non-existing.
+Individual correlations between parameters $\tilde\Lambda$ and $\theta^a$ is achieved by setting all of the off-diagonal Fisher matrix elements to $0$, except for the $(i,j)$ components such that both $i$ and $j$ correspond to the $\tilde\Lambda$ and $\theta^a$ parameters.
 We follow this process for each parameter in turn, and display the results in Fig.~\ref{fig:correlations} for each interferometer.
@@
 Following this conclusion on the difference of correlations between tidal parameters $\tilde\Lambda$ and $\delta\tilde\Lambda$ for second and third generation detectors, we attempt to describe the opposing behaviors of measurement accuracy between the two.
-Shown in the center panel of Fig.~\ref{fig:massVariation}, we approximate the measurement accuracy of $\tilde\Lambda$ with the correlations between $\delta\tilde\Lambda$ and $\tilde\Lambda$ removed, through a process similar to that described above.
-Notice how the trends between detector generations become more similar -- implying that the correlations between tidal parameters may be the cause.
-This is confirmed by the right panel of Fig.~\ref{fig:massVariation} where all parameter correlations have been removed from the Fisher matrix.
+Shown in the center panel of Fig.~\ref{fig:massVariation}, we approximate the measurement accuracy on $\tilde\Lambda$ with the correlations between $\delta\tilde\Lambda$ and $\tilde\Lambda$ removed, through a process similar to that described above.
+Notice how the trends between detector generations become more similar -- implying that the correlations between tidal parameters may be the cause of the opposing behaviors.
+This is confirmed by the bottom panel of Fig.~\ref{fig:massVariation} where all parameter correlations have been removed from the Fisher matrix.
 We see that this results in identical behaviors between all 6 representative interferometers, leading us to conclude that the discrepancy between interferometers comes from the degeneracies between different parameters in the gravitational waveform, namely the 6PN tidal parameter $\delta\tilde\Lambda$ which is only detectable by the highly sensitive third generation detectors CE and ET.

### 2019-01-27 paper/go.sh

@@ -9,6 +9,6 @@ echo "~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~" >> out
 pdflatex --shell-escape bin-love-after-gw170817.tex >> output.text
 echo "~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~" >> output.text
 pdflatex --shell-escape bin-love-after-gw170817.tex >> output.text
-rm *blg *log *aux *Notes* *bbl output.text *out
+#rm *blg *log *aux *Notes* *bbl output.text *out
 echo "Done. Enjoy your PDF!"
 evince bin-love-after-gw170817.pdf &

### 2019-01-27 paper/bin-love-after-gw170817.tex

@@
 This internal structure of such stars, known as the equation of state (EoS), is exceedingly important, as it is the determining factor for many NS observables - such as the mass, the radius, and many more.
-Unfortunately, terrestrial experiments can only study the EoS to around the nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy} (although some temperature-dependent heavy-ion collision experiments may probe higher densities~\cite{Abrahamyan:2012gp,Horowitz:2012tj,Horowitz:2013wha}), making NSs ideal laboratories for constraining ultra dense nuclear matter.
+Unfortunately, terrestrial experiments can only study the EoS to around the nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy} (although some temperature-dependent heavy-ion collision experiments may probe higher densities~\cite{Abrahamyan:2012gp,Horowitz:2012tj,Horowitz:2013wha}\kc{these are neutron skin measurement papers, not heavy ion collisions.
+look at~\cite{Danielewicz:2002pu} })), making NSs ideal laboratories for constraining ultra dense nuclear matter.
 
@@
 
-Additionally, Fig.~\ref{fig:rlove} displays the relationship between NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
+\kc{The R-Love fit is not a new relation, it is the same as C-Love.
+So instead of refitting you should just reexpress the C(Love) fit as R=m/C(Love).
+The errors you are finding here are way larger than error I've been finding from simply using C(Love) to compute the radius, and this might be the reason.}
+In addition, Fig.~\ref{fig:rlove} displays the relationship between NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
 Similar to the fits performed for the I-Love-Q and C-Love relations, we fit the R-Love relations to Eq.~\ref{eq:ILQfitNew}.
@@
 In this section, we investigate the residuals on $\lambda_0(\Lambda_a,\Lambda_s,q)$ in order to marginalize over the intrinsic error in the binary Love relations.
+\kc{Wait wait wait. Why $\lambda_0$? When we do PE, we do it in terms of $\Lambda_1$ and $\Lambda_2$. So it is these residuals (or equivalently $\Lambda_a$) we need in order to marginalize.}
 In particular, we restrict our focus to only the constrained set of EoSs.

### 2019-01-31 paper/bin-love-after-gw170817.tex
addressing comments

--- 2019-01-27 paper/bin-love-after-gw170817.tex
@@
 This internal structure of such stars, known as the equation of state (EoS), is exceedingly important, as it is the determining factor for many NS observables - such as the mass, the radius, and many more.
-Unfortunately, terrestrial experiments can only study the EoS to around the nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy} (although some temperature-dependent heavy-ion collision experiments may probe higher densities~\cite{Abrahamyan:2012gp,Horowitz:2012tj,Horowitz:2013wha}), making NSs ideal laboratories for constraining ultra dense nuclear matter.
+Unfortunately, terrestrial experiments can only study the EoS to around the nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy} (although some temperature-dependent heavy-ion collision experiments may probe higher densities~\cite{Danielewicz:2002pu}), making NSs ideal laboratories for constraining ultra dense nuclear matter.
 
@@
 Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with mass ratios of $0.75$, in C-Love universality by a factor of $\sim 67\%$, and in I-Love-Q universality by factors of $\sim50$\%, tabulated in Tab.~\ref{tab:maxVar}.
-We also present new R-Love relations displaying the relationship between NS radius and tidal deformability, showing maximum EoS variability of $18.88\%$ from the fit discussed in Sec.~\ref{sec:clove}.
+We also present the relationship between the NS radius and tidal deformability, computed directly from the C-Love relations, showing maximum EoS variability of $358.9 \text{ km}$ from the fit discussed in Sec.~\ref{sec:clove}.
 Additionally, we find that hybrid quark-hadron stars do obey the I-Love-Q and C-Love relations, with sightly increased EoS variability.
@@
 The following restrictions were also applied to both sets of EoSs: (i) the EoS must have a causal structure within 10\%, and (ii) the EoS must support maximum NS mass of at least $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations.
-Finally, the high density core EoSs generated above were stitched to the low-density crust EoS of SLy~\cite{Douchin:2001sv} at $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$.
-}
+Finally, the high density core EoSs generated above were stitched to the low-density crust EoS of SLy~\cite{Douchin:2001sv} at $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$.}
 \label{fig:eos}
@@
 \caption{
-I-Love-Q, C-Love, and R-Love relations fit parameters for the constrained EoS data using the improved fitting relations found in Eq.~\ref{eq:ILQfitNew}.
+I-Love-Q and C-Love, relations fit parameters for the constrained EoS data using the improved fitting relations found in Eq.~\ref{eq:ILQfitNew}.
 This fitting relation, unlike previous versions, properly limits to the Newtonian case as $\Lambda \rightarrow \infty$.
@@
  $C$ & $\Lambda$ & $-1/5$ & $0.2496$ & $-919.6$ & $330.3$ & $-857.2$ & $-383.5$ & $192.5$ & $-811.1$\\
- $R$ & $\Lambda$ & $-1/40$ & $8.575$ & $-10.55$ & $17.32$ & $-29.76$ & $-9.978$ & $21.91$ & $-31.77$\\
 \hline
@@
 Comparison between the EoS-insensitive relations (I-Love-Q, C-Love, R-Love, and binary Love) maximal EoS variability for the results of previous works~\cite{Yagi:ILQ,Yagi:binLove}, and the unconstrained and constrained sets of EoSs analyzed here.
-The maximum EoS variation, given by the largest fractional difference from the fits as shown in Figs.~\ref{fig:ILQ},~\ref{fig:clove},~\ref{fig:rlove} and~\ref{fig:binLove}, observes a considerable improvement for the constrained set of EoSs, compared to the unconstrained set as well as that found in previous works.
+The maximum EoS variation, given by the largest fractional difference (the R-Love variability is shown as the absolute difference in m here) from the fits as shown in Figs.~\ref{fig:ILQ},~\ref{fig:clove},~\ref{fig:rlove} and~\ref{fig:binLove}, observes a considerable improvement for the constrained set of EoSs, compared to the unconstrained set as well as that found in previous works.
 Additionally, note how the maximal EoS variation for the unconstrained set of EoSs is slightly larger than that found in Refs.~\cite{Yagi:ILQ,Yagi:binLove} - due to the effects of large random sampling taking into account more sources of uncertainty.
@@
  $C-\Lambda$ & $0.065$ & $0.07198$ & $0.02169$\\
- $R-\Lambda$ & -- & $0.4983$ & $0.1792$\\
+ $R-\Lambda$ & -- & $358.9 \text{ m}$ & $881.4 \text{ m}$\\
  \hline
@@
 In this section we consider approximately EoS-insensitive C-Love relations between NS compactness $C \equiv M/R$ and unitless tidal deformability $\Lambda$, as discussed by Yagi and Yunes~\cite{Yagi:binLove}.
-In addition, we show the R-Love relations, giving the relationship between NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
-Similar to the previous section, we consider two classes of stars: nuclear matter EoSs and hybrid quark-hadron star EoSs.
+Additionally in this section, we compute the relationship between the NS radius and tidal deformability from the C-Love relations.
+This allows one to compare the approximate uncertainty on NS radius computed from the C-Love relations for both the constrained and unconstrained sets of EoSs. 
+Similar to the previous section, we consider two classes of stars in this section: nuclear matter EoSs and hybrid quark-hadron star EoSs.
 
@@
 
-Additionally, Fig.~\ref{fig:rlove} displays the relationship between NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
-Similar to the fits performed for the I-Love-Q and C-Love relations, we fit the R-Love relations to Eq.~\ref{eq:ILQfitNew}.
-In this case, we utilize the same Newtonian control factor found in Eq.~\ref{eq:cloveFit} for the C-Love relations, substituting the NS mass with the polytropic form $M\propto R^{(3-n)/(1-n)}$~\cite{Shapiro:MRpolytrope}.
-Noting that most physical EoSs obey approximate polytropic indices between $0.50$ and $1.00$, as shown in Ref.~\cite{Yagi:binLove}, we choose a central value of $n=0.75$ for use in this analysis, resulting in $M\propto R^9$.
-Absorbing the proportionality constant into $K_{R\Lambda}$ gives the approximate Newtonian relationship as:
-\begin{equation}
-R^N \approx K_{R\Lambda}\Lambda^{-1/40}.
-\end{equation}
-The results of this fit are displayed in Tab.~\ref{tab:ILQfitNew}, and the maximal EoS variability is again shown in Tab.~\ref{tab:maxVar}.
-Previously, this relation observed large relative uncertainties on the order of $\sim50\%$ on the mapping from tidal deformability to radius, as can be seen by the unconstrained EoSs in Fig.~\ref{fig:rlove}.
-However, upon the restriction to soft EoSs conforming to GW170817, we observe a large suppression in EoS variability to the order of $\sim20\%$.
-This results in new EoS-insensitive relations, with relative uncertainties on the same scale as found in the binary Love relations discussed below in Sec.~\ref{sec:binary}.
+In addition, Fig.~\ref{fig:rlove} displays the relationship between the NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
+This relationship is computed directly from the C-Love relations discussed above as $R(\Lambda)=m/C(\Lambda)$ for observed mass $m=1.48\text{ M}_{\odot}$ from GW170817.
+We also present the uncertainty on a NS radius measurement using the C-Love relations in the bottom panel of Fig.~\ref{fig:rlove}, defined as the absolute difference from the fits.
+We observe a large suppression in the radius measurement accuracy from the unconstrained set of EoSs to the constrained set, tabulated in Tab.~\ref{tab:maxVar} as the maximal EoS measurement uncertainty.
+
 \begin{figure}
@@
 Similar to Fig.~\ref{fig:clove} but for the R-Love relationship between the NS radius and tidal deformability.
-In this figure, we also construct fits to  Eq.~\ref{eq:ILQfitNew}, limiting to the Newtonian case $R \sim M\Lambda^{1/5}$, with $M\sim R^{(3-n)/(1-n)}$ for polytropic index $n$.
-Observe how the fractional difference from the fit is reduced significantly between the unconstrained and constrained sets of EoSs, shown by the comparisons in Tab.~\ref{tab:maxVar}.
-Also shown in this figure is the hybrid star R-Love relations along with their fractional difference from the constrained EoS fits (dashed green).
+This relationship is computed directly from the C-Love relations, and estimates the uncertainty on the NS radius as computed through the C-Love relations.
+Observe how the absolute difference from the fit is reduced significantly between the unconstrained and constrained sets of EoSs, shown by the comparisons in Tab.~\ref{tab:maxVar}.
 }
@@
 \subsubsection{Hybrid quark-hadron stars}\label{sec:clove-hyb}
-In this section, we consider the effect of hybrid star EoSs on the C-Love and R-Love relations.
+In this section, we consider the effect of hybrid star EoSs on the C-Love relation.
 Much like Sec.~\ref{sec:ilq-hyb}, we perform 3 separate fits (constrained and hybrid EoSs combined, constrained EoSs only, and hybrid EoSs only) and compare the maximal EoS variation for each class of EoSs.
@@
 This is exemplified in Fig.~\ref{fig:clove} by the dashed green curves.
-We observe similar results for the case of R-Love relations, as seen by the dashed green curves in Fig.~\ref{fig:rlove}.
-Here, the hybrid stars show a maximal fractional difference of $30.82\%$ from the constrained EoS fits, still much smaller than the unconstrained EoSs variation.
 
@@
 
-In this section, we investigate the residuals on $\lambda_0(\Lambda_a,\Lambda_s,q)$ in order to marginalize over the intrinsic error in the binary Love relations.
+In this section, we investigate the residuals on $\Lambda_a(\Lambda_s,q)$ in order to marginalize over the intrinsic error found in the binary Love EoS-insensitive relations.
 In particular, we restrict our focus to only the constrained set of EoSs.
-Residuals on $\lambda_0$ are computed as $\lambda_0^{\text{fit}}-\lambda_0^{\text{true}}$, where $\lambda_0^{\text{true}}=\lambda_0(\Lambda_a,\Lambda_s,q)$ corresponds to the true values predicted by the sample EoSs, and $\lambda_0^{\text{fit}}=\lambda_0(\Lambda_a^{\text{fit}}(\Lambda_s,q),\Lambda_s,q)$ corresponds to the values obtained through the EoS-insensitive relations found in Sec.~\ref{sec:binLove-nuclear}.
-Following Ref.~\cite{Katerina:residuals}, we assume the residuals on $\lambda_0$ observe a Gaussian distribution with mean and standard deviation given by:
+Residuals in $\Lambda_a$ are computed as $\Lambda_a^{\text{relation}}(\Lambda_s,q)-\Lambda_a^{\text{true}}$, where $\Lambda_a^{\text{true}}$ corresponds to the true value predicted by the sample EoSs, and $\Lambda_a^{\text{relation}}(\Lambda_s,q)$ corresponds to the value obtained through the EoS-insensitive relations found in Sec.~\ref{sec:binLove-nuclear}.
+We follow this up by converting the $\Lambda_a$ residuals into $\lambda_0$, allowing us to approximate the overall systematic errors on $\lambda_0$ from using the improved binary Love relations.
+
+Following Ref.~\cite{Katerina:residuals}, we assume the residuals on $\Lambda_a$ observe a Gaussian distribution with mean and standard deviation given by:
 \begin{align}
-\mu_{\lambda_0}(\Lambda_s,q) &=\frac{\mu_{\Lambda_s}(\Lambda_s)+\mu_{q}(q)}{2},\\ 
-\sigma_{\lambda_0} &=\sqrt{\sigma_{\Lambda_s}^2(\Lambda_s) + \sigma_{q}^2(q)}. 
+\mu_{\Lambda_a}(\Lambda_s,q) &=\frac{\mu_{\Lambda_s}(\Lambda_s)+\mu_{q}(q)}{2},\\ 
+\sigma_{\Lambda_a} &=\sqrt{\sigma_{\Lambda_s}^2(\Lambda_s) + \sigma_{q}^2(q)}. 
 \end{align}
@@
 \mu_{q}(x) &= \mu_3 x^2 + \mu_4 x + \mu_5, \label{eq:margFit2}\\ 
-\sigma_{\Lambda_s}(x) &= \sigma_1 x^{5/2} + \sigma_2 x^{3/2} +  \sigma_3 x^{1/2} + \sigma_4, \label{eq:margFit3}\\ 
-\sigma_{q}(x) &= \sigma_5 x^3 + \sigma_6 x^2 + \sigma_7 x + \sigma_8. \label{eq:margFit4}
+\sigma_{\Lambda_s}(x) &= \sigma_1 x^{5/2} + \sigma_2 x^{3/2} + \sigma_3 x \sigma_4 x^{1/2} + \sigma_5, \label{eq:margFit3}\\ 
+\sigma_{q}(x) &= \sigma_6 x^3 + \sigma_7 x^2 + \sigma_8 x + \sigma_9. \label{eq:margFit4}
 \end{align}
-The fitting parameters $\mu_i$ and $\sigma_i$ are tabulated in Tab.~\ref{tab:marginalized}, and Fig.~\ref{fig:qLsResiduals} shows the $\lambda_0$ residuals binned in both q and $\Lambda_s$, highlighting the error weights across the $(q,\Lambda_s)$ parameter space.
-Observe how $q\sim0.5$ and $\Lambda_s\sim2000$ obtain the highest errors, while the low and high values of $q$ and $\Lambda_s$ have minimal uncertainties.
+The fitting parameters $\mu_i$ and $\sigma_i$ are tabulated in Table~\ref{tab:marginalized}.
 
@@
 \caption{
-Coefficients to the fits given by Eqs. (\ref{eq:margFit1})-(\ref{eq:margFit4}) for the relative error on $\lambda_0$ in the improved binary Love relations presented in this paper.
+Coefficients to the fits given by Eqs.(~\ref{eq:margFit1})-(\ref{eq:margFit4}) for the relative error on $\Lambda_a$ in the improved binary Love EoS-insensitive relations presented in this paper.
 }\label{tab:marginalized}
@@
 \noalign{\smallskip}
-$\mu_1$ & $-1.016\times10^{-29}$ & $\sigma_1$ & $-1.195\times10^{-33}$\\
-$\mu_2$ & $5.376\times10^{-27}$ & $\sigma_2$ & $4.056\times10^{-30}$\\
-$\mu_3$ & $-6.850\times10^{-25}$ & $\sigma_3$ & $5.699\times10^{-27}$\\
-$\mu_4$ & $1.024\times10^{-24}$ & $\sigma_4$ & $-1.334\times10^{-26}$\\
-$\mu_5$ & $-3.680\times10^{-25}$ & $\sigma_5$ & $7.168\times10^{-24}$\\
- &  & $\sigma_6$ & $-1.595\times10^{-23}$\\
- &  & $\sigma_7$ & $1.098\times10^{-23}$\\
- &  & $\sigma_8$ & $-2.139\times10^{-24}$\\
+$\mu_1$ & $3.509 \times 10^{-3}$ & $\sigma_1$ & $-2.074 \times 10^{-7}$\\
+$\mu_2$ & $9.351 \times 10^{-1}$ & $\sigma_2$ & $-1.492 \times 10^{-3}$\\
+$\mu_3$ & $-18.07$ & $\sigma_3$ & $-4.891 \times 10^{-2}$\\
+$\mu_4$ & $27.56$ & $\sigma_4$ & $8.207 \times 10^{-1}$\\
+$\mu_5$ & $-10.10$ & $\sigma_5$ & $-1.308$\\
+ &  & $\sigma_6$ & $-63.76$\\
+ &  & $\sigma_7$ & $11.14$\\
+ &  & $\sigma_8$ & $75.25$\\
+ &  & $\sigma_8$ & $-23.69$\\
  \noalign{\smallskip}
@@
 
+Now that we have obtained the residuals on $\Lambda_a$, we must convert them into the new tidal parameter $\lambda_0$, in order to compute and easily compare the systematic errors to the statistical errors on $\lambda_0$, found in Sec.~\ref{sec:futureObservations}.
+Figure~\ref{fig:qLsResiduals} shows the standard deviations of these residuals (converted into $\lambda_0$) binned in both $q$ and $\Lambda_s$ as was done above. 
+To estimate the overall systematic errors on $\lambda_0$ accrued upon the use of the improved binary Love relations, we combine the errors in both $q$ and $\Lambda_s$.
 Figure~\ref{fig:residuals} displays the un-binned Gaussian distribution of $\lambda_0$ residuals for both the constrained, and unconstrained sets of EoSs for comparison.
@@
 {\ny{Super confused about Fig. 1...}}
+\kc{me too}
 {\zc{Yes, there is a \emph{lot} of info in this figure.
@@
 Similarly, we find an increase in C-Love and I-Love-Q universality by factors of $\sim 76$\% and $\sim 50$\%, respectively.
-We also show new R-Love EoS-insensitive relations relating the NS radius to its tidal deformability, displaying a maximum of $18.88\%$ EoS variability from the fit discussed in Sec.~\ref{sec:clove}.
+We also show the relation between the NS radius and its tidal deformability, computed directly from the C-Love relations.
+We find this relation to display a maximum error of $358.9\text{ m}$ from the fit discussed in Sec.~\ref{sec:clove}.
 Additionally, we find that hybrid quark-hadron star EoSs \emph{do} obey the I-Love-Q and C-Love universality, albeit with slightly higher maximum EoS variabilities as displayed in Tabs.~\ref{tab:hybridCompare} and ~\ref{tab:hybridCompareClove}.

### 2019-02-06 paper/bin-love-after-gw170817.tex
added responses to comments.

--- 2019-01-27 paper/bin-love-after-gw170817.tex
@@
 
-{\ny{This is a bit strange, but probably still correct.
-But ``this'' I mean the fact that when you fit only to the hybrid stars you do not get better than $1\%$ universality.
-If I look at the hybrid curves alone, they look like the same simple lines as in the neutron star case (but of course a $1\%$ difference wouldn't show on this scale).
-Why is it that we can lower fractional difference in the NS case but not in the hybrid case?}}
-{\zc{Nico, I think the reason for this is because there is nothing ``constrained" about the hybrid stars - these are basically ``unconstrained" EoSs so we can't really reduce the fractional difference any more.}}
 {\ny{Can I see the relative fractional different between each fit and the data for hybrid stars only?
@@
 The third case (fits to hybrids only) looks different but not by much.}}
+{\ny{Ok, this makes more sense to me now.
+The universality does increase, but only by a small amount (which you did say before -- something like from 1.7 to 1 per cent.).
+Ok, we can remove these figures and these comments if you'd like.
+}}
 \begin{figure}
@@
 So instead of refitting you should just reexpress the C(Love) fit as R=m/C(Love).
-The errors you are finding here are way larger than error I've been finding from simply using C(Love) to compute the radius, and this might be the reason.}
+The errors you are finding here are way larger than error I've been finding from simply using C(Love) to compute the radius, and this might be the reason.} {\ny{That's a good idea.
+But it is not immediately obvious that this will help.
+Kent and I have found that when you look at relations between dimensionless quantities, then the universality is typically stronger than when you use dimensionful quantities (incidentally, this is why the Doneva paper about rapidly-rotating I-Love-Q is wrong, as pointed out by Haris and George).}}
 In addition, Fig.~\ref{fig:rlove} displays the relationship between NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
@@
 So when we take $\Lambda_1+\Lambda_2$, we end up getting higher values of $\Lambda_s$ for the unconstrained EoSs than we do for the constrained ones.}}
+{\ny{Ahh...yes, makes sense. Please add a sentence or two about this in the text.}}
 \begin{figure}
@@
 This results in a large deviation in the NS binary Love relations $\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$, disrupting the overall universality.
-{\ny{Sorry, I don't get it.
-Why does seeing ``a large difference in Lambda tilde'' explain the loss of universality?
-We have cases with small enough q that show much more universality than what we find for the same value of q in the HS/NS case.
-I guess what I am saying is that we should explore this more from a theory side to try to provide an explanation, or we should say nothing (or say we don't know why this is the case).}}
-{\zc{Nico, sorry this was a bad explanation on my part.
-when the two stars each see a large jump in $\Lambda$, the differences and sums of tidal deformabilities also see a big jump, and they ``jump off" the universal line as can be seen by the dashed bright green lines in fig.~\ref{fig:binLove}.
-I've rewritten this sentence to (hopefully) make more sense.}}
 
@@
 Instead, I could plot their fractional difference from their own "HS" fits too.
-We can discuss this.}}
+We can discuss this.}} {\ny{I was referring to the hump in the top panel (ie.
+in the R-Love relation).
+It'd be good to add a sentence to the text that points this hump out and explains it as you did above.}}
 
@@
 Instead, I wrote a few sentences in the paper saying how it doesn't properly limit to the Newtonian case, and how we tried to remedy it.
-I'm welcome to any suggestions!}}
+I'm welcome to any suggestions!}} {\ny{Hmmm....ok.}}
 
@@
 We can talk more about this over Skype.}}
-
-\kc{me too}
+{\ny{I'm happier with this rewrite (makes more sense to me now).}}
 

### 2019-02-06 paper/bin-love-after-gw170817.tex
minor

--- 2019-01-31 paper/bin-love-after-gw170817.tex
@@
 We observe a large suppression in the radius measurement accuracy from the unconstrained set of EoSs to the constrained set, tabulated in Tab.~\ref{tab:maxVar} as the maximal EoS measurement uncertainty.
+{\ny{That's a good idea.
+But it is not immediately obvious that this will help.
+Kent and I have found that when you look at relations between dimensionless quantities, then the universality is typically stronger than when you use dimensionful quantities (incidentally, this is why the Doneva paper about rapidly-rotating I-Love-Q is wrong, as pointed out by Haris and George).}}
 
@@
 Figure~\ref{fig:binLove} shows the improved binary Love relation for 3 different mass ratios: $q=0.9$, $q=0.75$, and $q=0.5$ for both the constrained and unconstrained sets of EoSs.
-%In this figure we show the absolute difference from the fit, rather than the fractional difference, so one can see which regions of $\Lambda_s$ display the largest actual difference.
 \zc{need to decide if using fractional or actual here}
@@
 We can talk more about this over Skype.}}
+{\ny{I'm happier with this rewrite (makes more sense to me now).}}
 

### 2019-02-07 paper/bin-love-after-gw170817.tex
removed comments and fixed Fig 1

@@
 \subsection{Executive Summary}
-\zc{Me and Kent discussed whether or not we should include this section or not, and we decided like having the quick summary for busy readers - especially with the increasing number of figs and tables (8 tables, 14 figures so far).
-We can discuss this further if anyone doesn't want it included :)}
-{\ny{I'm ok with keeping this, but let's get the science finished first.}}
 %What we did
@@
 \caption{
-Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue circles) in the extraction of $\lambda_0$ from GW170817 (O2 detector sensitivity) as if it were observed with future interferometers aLIGO, A\texttt{+}, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
-This is compared to the combined uncertainty $\sigma^A_N$ (turquoise shaded region) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper and lower limits of the expected binary NS merger detection rates for O2, aLIGO, A\texttt{+}, Voyager, CE, and ET-D over 1 observation year.
-It can be seen that the statistical errors in the parameter extraction become comparable to the systematics from EoS variation in improved binary Love relations (indigo dashed line) for Voyager CE, and ET.
+Estimated statistical uncertainties on the extraction of $\lambda_0$ observed from interferometers $A=$(O2, aLIGO, A\texttt{+}, Voyager, CE, ET-D$)$ as a function of the signal-to-noise-ratio.
+In this figure, the filled blue circles denote the single-event statistical uncertainties $\sigma^A_{\text{GW170817}}$ of GW170817 as if it were observed on detector $A$.
+Also shown by the turquoise shaded region is combined uncertainty $\sigma^A_N$  from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper and lower limits of the expected binary NS merger detection rates for O2, aLIGO, A\texttt{+}, Voyager, CE, and ET-D over 1 observation year.
+It can be seen that the statistical errors in the parameter extraction become comparable to the systematics from EoS variation in the improved binary Love relations (indicated by the horizontal indigo dashed line) for Voyager, CE, and ET.
 These results are further tabulated in Table~\ref{tab:variances}.
 Additionally shown in the figure are the estimated statistical uncertainties on the extraction of $\lambda_0$ upon the injection of the PhenomD + NRTidal correction waveform (IMRD + NRTidal), rather than the PhenomD + 6PN tidal correction (IMRD + 6PN), in order to demonstrate the effect of waveform mismodeling uncertainties.
-The single-detection uncertainties are shown by unfilled blue circles, while the combined detection uncertainties are outlined by dashed maroon.
+The single-detection uncertainties are shown by unfilled maroon circles, while the combined detection uncertainties are outlined by dashed maroon.
 }
@@
 
-{\ny{Can I see the relative fractional different between each fit and the data for hybrid stars only?
-(ie.
-the analogous thing to the green dashed lines of the figure below, but also with the fits to the total set, to just the hybrids and to just the neutron stars.) I wonder whether there is any improvement at all when you fit just to hybrid stars or whether there are any features.}}
-{\zc{Nico, Yes of course!
-I've added a new figure (for example only - this can be removed later) - Fig.~\ref{fig:example} showing the fractional difference for hybrid stars only for the three cases shown in the text.
-Looking at the figures, they don't change much at all in shape for the first two cases - just a minor vertical shift.
-The third case (fits to hybrids only) looks different but not by much.}}
-{\ny{Ok, this makes more sense to me now.
-The universality does increase, but only by a small amount (which you did say before -- something like from 1.7 to 1 per cent.).
-Ok, we can remove these figures and these comments if you'd like.
-}}
-\begin{figure}
-\begin{center} 
-\includegraphics[width=\columnwidth]{compareHybrid.pdf}
-\end{center}
-\caption{
-\zc{Example figure applying to Nicos comment on the differences between the three different cases of Hybrid star fits: Case I - Complete set of 100 constrained EoSs combined
-with the 10 hybrid star EoSs, Case II - Complete set of 100 constrained EoSs alone, Case III - Complete set of 10 hybrid star EoSs alone.}
-}
-\label{fig:example}
-\end{figure}
-
 \subsection{C-Love Relations}\label{sec:clove}
@@
 We observe a large suppression in the radius measurement accuracy from the unconstrained set of EoSs to the constrained set, tabulated in Tab.~\ref{tab:maxVar} as the maximal EoS measurement uncertainty.
-{\ny{That's a good idea.
-But it is not immediately obvious that this will help.
-Kent and I have found that when you look at relations between dimensionless quantities, then the universality is typically stronger than when you use dimensionful quantities (incidentally, this is why the Doneva paper about rapidly-rotating I-Love-Q is wrong, as pointed out by Haris and George).}}
 
@@
 Figure~\ref{fig:binLove} shows the improved binary Love relation for 3 different mass ratios: $q=0.9$, $q=0.75$, and $q=0.5$ for both the constrained and unconstrained sets of EoSs.
-\zc{need to decide if using fractional or actual here}
 Observe how once again, the constrained set of EoSs show a considerable improvement upon both the unconstrained set of EoSs, as well as the results found in previous works~\cite{Yagi:binLove}.
@@
 
-{\ny{I get why you are plotting the absolute difference but 
-\begin{itemize}
-\item[(i)] everywhere else in the paper you are plotting the relative fractional difference, so a reader that doesn't pay much attention (and say misses the 1 sentence in the paragraph above -- by the way, I think the caption is wrong and should say the absolute difference instead of the fractional difference, no?
---) will look at the axis and say: Wow!
-100\% error...that's bad!.
-This is a problem, I don't have a solution for it (except for reverting to relative fractional differences) but it should not be ignored.
-\item[(ii)] it is hard to see easily what this error means in terms of EoS-variability.
-Say for example we pick the q=0.9 hybrid star case at Lambdas of 100.
-I can easily read that there is EoS variability of about 20.
-But to see if this 20 is a lot or a little, I have to compare with the top figure, from which I get that Lambdaa is about 60 or 70 (if I use a ruler on my computer screen).
-Now I have to take these two approximate numbers and compare them, but because they are approximate, it's hard to see whether this is a 30 per cent difference, a 50 percent difference or what.
-\end{itemize}
-}}
-{\zc{I agree completely - and I think we should discuss over Skype what should be done for this plot (Both versions (absolute and fractional) are loaded in the images folder, just comment out the image name in the figure to change it.)
-Also, the caption is correct - It says that the absolute differences are shown in the plot, while fractional ones are listed in Table III (in order to easily compare to other universal relations and to previous works.)}}
-
-{\ny{I must have missed something. Why do the unconstrained magenta lines extend way passed the constrained green lines? I didn't see this discussed anywhere.}}
-{\zc{This is because I've cut all the EoSs off at masses of 1 M$_{\odot}$, and typically the unconstrained EoSs (maroon) have larger ranges of $\Lambda$ than the unconstrained ones.
-So when we take $\Lambda_1+\Lambda_2$, we end up getting higher values of $\Lambda_s$ for the unconstrained EoSs than we do for the constrained ones.}}
-{\ny{Ahh...yes, makes sense. Please add a sentence or two about this in the text.}}
 \begin{figure}
@@
 These transitions result in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq M_{\text{tr}}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote this as ``HS"), and (ii) low-mass ($M \leq M_{\text{tr}}$) hadronic stars with no internal transition to quark matter (we denote this as ``NS").
-{\ny{ooohh...I'm not sure I like the acronyms here.
-NS typically stands for ``neutron star'' of standard type, like what you would construct from an APR EoS.
-But here by NS you mean a low-mass neutron star specifically.
-Let's pick a better acronym.}}
-{\zc{We can discuss this over Skype - me and Kent like ``NS" because the low-mass branch of the hybrid star EoS \emph{is} actually a nuclear matter ``NS" EoS - these hybrid stars are derived by introducing a transition to standard NS EoSs.}}
 We consider 3 classes of binary systems in this analysis:
@@
 Observe how the residuals from the fit are quite good at low pressures (large $\Lambda_s$) where the the binaries consist of NS/NS combinations, before reaching the transitional pressure where the deviations become increasingly large ($\sim160$\% for $q=0.90$, $\sim37$\% for $q=0.75$, and $\sim6$\% for $q=0.50$) for HS/HS and HS/NS binaries.
-{\ny{Why is there a hump for the HS cases in green in Fig.
-7?}}{\zc{The hump comes from the transition between NS and HS branches, as I describe in my above comment.
-If you are referring to the bottom panels of Fig 7, this hump is because I display the fractional difference of the \emph{HS} EoSs from the \emph{NS} fits - to show how badly they fit (although that is not as visible now that we are plotting absolute difference.
-Instead, I could plot their fractional difference from their own "HS" fits too.
-We can discuss this.}} {\ny{I was referring to the hump in the top panel (ie.
-in the R-Love relation).
-It'd be good to add a sentence to the text that points this hump out and explains it as you did above.}}
 
@@
 By separating the two branches of the hybrid EoSs, we find a new ``hybrid" branch binary Love fit which gives consistent results to that found for the nuclear matter fits.
-{\ny{But wait, the Newtonian limit is not valid for this hybrid branch, since you are not allowed to go to low enough central densities, right?
-If so, what are you using for the controlling factor?
-I found the description in the 2 paragraphs above a bit muddled and short.
-It is not exactly clear to me what the message you were trying to send was.}}
-{\zc{You're right - I tried to change this by using leaving the polytropic index (n) as an additional fitting parameter.
-Doing this gives n=1.7, and all other parameters $>10^7$.
-The fit looks good but I'm skeptical about those fit values.
-Additionally, if I set n=0, the fits diverge.
-Instead, I wrote a few sentences in the paper saying how it doesn't properly limit to the Newtonian case, and how we tried to remedy it.
-I'm welcome to any suggestions!}} {\ny{Hmmm....ok.}}
 
@@
 
-{\ny{Super confused about Fig. 1...}}
-\kc{me too}
-{\zc{Yes, there is a \emph{lot} of info in this figure.
-The filled blue circles are the statistical uncertainties on $\lambda_0$ for GW170817 as if it had been detected on Detector A=(O2, aLIGO, A+, Voyager, ET, CE), where the x-axis corresponds to the SNR on that detector as if it found GW170817.
-The filled turquoise region is the combined statistical uncertainty on the detection of $N_A$ events on each detector A, computed using the bulleted process above (moved to the appendix).
-There is some height to this shaded region because I consider the the upper and lower error bars of the local BNS merger rate $\mathcal{R}$ - giving us a range of $N_A$'s to consider for each detector.
-We can talk more about this over Skype.}}
-{\ny{I'm happier with this rewrite (makes more sense to me now).}}
-
 Concluding, we find that the Voyager, ET, and CE detectors all exhibit enough uncertainty reduction that the systematics on $\lambda_0$ introduced from using improved EoS-insensitive relations (found to be $2.06 \times 10^{-25}\text{ s}^5$) no longer become negligible in the error budget.

### 2019-02-09 paper/bin-love-after-gw170817.tex
converted unitful to unitless lambda0

@@
 For example, utilizing the parameters $\tilde{\Lambda}$ and $\delta \tilde{\Lambda}$~\cite{Favata:2013rwa,Wade:tidalCorrections} which enter the GW waveform at different post-Newtonian (PN) orders (powers of the ratio between the orbital speed and the speed of light $v/c^{2n}$) partially mitigates these correlations.
-Similarly, the waveform may be parameterized by mass-independent tidal parameters $\lambda_0$ and $\lambda_1$, derived through a Taylor expansion about $m_0=1.4 \text{ M}_{\odot}$ of individual, unitful tidal deformability $\lambda \approx \lambda_0+\lambda+1(m_1-1.4 \text{ M}_{\odot})/\text{M}_{\odot}$~\cite{delPozzo:TaylorTidal}.
+Similarly, the waveform may be parameterized by mass-independent tidal parameters $\lambda_0$ and $\lambda_1$, derived through a Taylor expansion about $m_0=1.4 \text{ M}_{\odot}$ of tidal deformability $\Lambda \approx \lambda_0+\lambda+1(1-\frac{m}{m_0})$~\cite{delPozzo:TaylorTidal,Yagi:binLove}.
 Use of this set of tidal parameters allows one to effectively combine multiple events with varying mass and $\tilde\Lambda$ components, not possible in the former parameterization of $\tilde{\Lambda}$ and $\delta \tilde{\Lambda}$
@@
 %Universal relations
-Unfortunately, current detectors are only sensitive enough to accurately measure the dominant tidal parameter, $\lambda_0$.
+Unfortunately, current detectors are only sensitive enough to accurately measure the dominant tidal parameter, $\lambda_0$ (also known as $\Lambda_{1.4}$, the tidal deformability at $1.4 \text{ M}_{\odot}$).
 Previous work by Yagi and Yunes~\cite{Yagi:binLove} resolved this issue by finding approximately EoS-insensitive ``binary Love relations" between symmetric and anti-symmetric combinations of tidal deformabilities $\Lambda_{s,a}=\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$.
@@
 Due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the EoS-insensitive relations are far outweighed by the statistical errors accrued by extraction of high-order PN tidal parameters from GW waveforms.
-Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from parameter extraction for GW170817 as if it had been observed by future detectors $A \equiv ($ O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, ET~\cite{ET}, CE~\cite{Ap_Voyager_CE}$)$.
+Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from the parameter extraction of $\lambda_0$ (the tidal deformability at $1.4 \text{ M}_{\odot}$) for GW170817 as if it had been observed by future detectors $A \equiv ($ O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, ET~\cite{ET}, CE~\cite{Ap_Voyager_CE}$)$.
 Here, $\sigma^A_{\text{GW170817}}$ and $\rho^A_{\text{GW170817}}$ correspond to the statistical error and signal-to-noise-ratio found from observing GW170817 on detector $A$, and $\sigma^A_N$ represents the combined uncertainty after the detection of $N_A$ events (corresponding to the binary NS merger rate associated interferometer $A$).
@@
 \caption{
-Estimated statistical uncertainties on the extraction of $\lambda_0$ observed from interferometers $A=$(O2, aLIGO, A\texttt{+}, Voyager, CE, ET-D$)$ as a function of the signal-to-noise-ratio.
+Estimated statistical uncertainties on the extraction of the tidal deformability at $1.4 \text{ M}_{\odot}$, $\lambda_0$, observed from interferometers $A=$(O2, aLIGO, A\texttt{+}, Voyager, CE, ET-D$)$ as a function of the signal-to-noise-ratio.
 In this figure, the filled blue circles denote the single-event statistical uncertainties $\sigma^A_{\text{GW170817}}$ of GW170817 as if it were observed on detector $A$.
@@
 Because future events occur with weighted tidal parameters $\tilde\Lambda$ which are unknown at this time, we can not accurately combine the uncertainties on $\tilde\Lambda$ for multiple events.
-To remedy this, we re-parameterize the waveform and instead consider the $\lambda_0$ and $\lambda_1$ tidal coefficients produced by Taylor expanding the unitful tidal deformability $\lambda \equiv \Lambda m^5$ about $m_0=1.4\text{ M}_{\odot}$:
-\begin{equation}
-\lambda \approx \lambda_0 + \lambda_1 (m-1.4 \text{M}_{\odot})/\text{M}_{\odot},
-\end{equation}
-as discussed in Ref.~\cite{delPozzo:TaylorTidal}.
+To remedy this, we re-parameterize the waveform and instead consider the $\lambda_0$ and $\lambda_1$ tidal coefficients produced by Taylor expanding the dimensionless tidal deformability $\Lambda$ about the ``canonical" reference mass of $m_0=1.4\text{ M}_{\odot}$~\cite{delPozzo:TaylorTidal,Yagi:binLove}:
+\begin{equation}
+\lambda \approx \lambda_0 + \lambda_1 (1-\frac{m}{m_0}),
+\end{equation}
+where $\lambda_0$ and $\lambda_1$ are the tidal deformability and its slope at $1.4 \text{ M}_{\odot}$\footnote{$\lambda_0$ is commonly known as $\Lambda_{1.4}$.}. 
 The new tidal parameters $\lambda_0$ and $\lambda_1$ do not depend on mass, thus are identical for every future binary NS merger, and may be combined in uncertainty.
@@
 Figure~\ref{fig:residuals} displays the un-binned Gaussian distribution of $\lambda_0$ residuals for both the constrained, and unconstrained sets of EoSs for comparison.
-Observe how the standard deviations $\sigma=1.52\times10^{-25} \text{ s}^5$ and $\sigma=12.21\times10^{-25} \text{ s}^5$ show a large decrease from the unconstrained to the constrained sets of EoSs.
-Additionally, we find the 90th, 99th, and 100th percentiles on $\lambda_0$ to be $P_{90}=2.06\times10^{-25} \text{ s}^5$, $P_{99}=6.61\times10^{-25} \text{ s}^5$, and $P_{100}=17.36\times10^{-25} \text{ s}^5$ for the constrained EoSs.
+Observe how the standard deviations $\sigma=9.764$ and $\sigma=78.28$ show a large decrease from the unconstrained to the constrained sets of EoSs.
+Additionally, we find the 90th, 99th, and 100th percentiles on $\lambda_0$ to be $P_{90}=13.19$, $P_{99}=42.38$, and $P_{100}=111.32$ for the constrained EoSs.
 Because the un-binned residuals seen in Fig.~\ref{fig:residuals} are dominated by the low-error regions of the parameter space ($\Lambda_s \rightarrow 0$, $\Lambda_s \rightarrow \infty$, $q \rightarrow 0$ and $q \rightarrow 1$) shown by Fig.~\ref{fig:qLsResiduals}, we consider the 90th percentile error (indicated by the dashed green line in Fig.~\ref{fig:qLsResiduals}) for the remainder of the analysis, in order to further take into account the high-error regions of the parameter space ($\Lambda_s \sim 2000$, $q\sim0.5$).
-We take this value of $P_{90}=2.06\times10^{-25} \text{ s}^5$ to be the systematic measurement error introduced by using the improved binary Love relations on the parameter extraction of $\lambda_0$, indicated by the dashed indigo line in Fig.~\ref{fig:stackedFisher}.
+We take this value of $P_{90}=13.19$ to be the systematic measurement error introduced by using the improved binary Love relations on the parameter extraction of $\lambda_0$, indicated by the dashed indigo line in Fig.~\ref{fig:stackedFisher}.
 Similarly, we derive the systematic measurement error on $\tilde\Lambda$ to be $12.01$, shown in Fig.~\ref{fig:singleFisherLt}.
-Currently, the statistical error of $26.53 \times 10^{-25} \text{ s}^5$ on $\lambda_0$ from GW170817 dominates the error budget compared to the systematic error of $2.06\times10^{-25} \text{ s}^5$, as seen in Fig.~\ref{fig:stackedFisher}.
+Currently, the statistical error of $170.1$ on $\lambda_0$ from GW170817 dominates the error budget compared to the systematic error of $13.19$, as seen in Fig.~\ref{fig:stackedFisher}.
 This means that, for the current ``O2" detector sensitivity, the use of improved binary Love relations will only make a negligible difference on the extraction of $\tilde\Lambda$.
@@
 Residuals on $\lambda_0$ computed as $\lambda_0^{\text{fit}}-\lambda_0^{\text{true}}$ for the binary Love relations modeled in Sec.~\ref{sec:binLove-nuclear} for both constrained and unconstrained sets of EoSs.
-These residuals obey Gaussian distributions centered at $\mu=-2.39 \times 10^{-27} \text{ s}^5$ and $\mu=4.22 \times 10^{-27} \text{ s}^5$ with standard deviations of $\sigma=1.52\times10^{-25} \text{ s}^5$ and $\sigma=12.21\times10^{-25} \text{ s}^5$ for the constrained and unconstrained sets of EoSs, respectively.
+These residuals obey Gaussian distributions centered at $\mu=-0.1530$ and $\mu=0.2710$ with standard deviations of $\sigma=9.764$ and $\sigma=78.28$ for the constrained and unconstrained sets of EoSs, respectively.
 These uncertainties correspond roughly to the systematic errors introduced on the parameter extraction of $\lambda_0$ upon the use of binary Love relations.
-However, to take into account the systematic errors found in high-error regions of the parameter space, we instead set the systematic error to be the 90th percentile, $P_{90}=2.06\times10^{-25} \text{ s}^5$.
-Observe that the systematic errors from using the improved (constrained) binary Love relations are negligible compared to the statistical errors accrued on parameter extraction from GW170817, found to be $\sigma_{\lambda_0}=26.53 \times 10^{-25} \text{ s}^5$.
+However, to take into account the systematic errors found in high-error regions of the parameter space, we instead set the systematic error to be the 90th percentile, $P_{90}=13.19$.
+Observe that the systematic errors from using the improved (constrained) binary Love relations are negligible compared to the statistical errors accrued on parameter extraction from GW170817, found to be $\sigma_{\lambda_0}=170.1$.
 }
@@
 Further, we consider the combined statistical uncertainties of $N_A$ events detected over 1 year on detector $A$, determined by integrating the local binary NS (BNS) merger rate over redshifts up to the horizon redshift of each detector.
-Here we assume low spin priors $|\chi| \leq 0.05$, as well as $0 \text{ s}^5 \leq \lambda_0 \leq 5 \times 10^{-23} \text{ s}^5$ and $-5 \times 10^{-18} \text{ s}^4\text{ M}_{\odot} \leq \lambda_1 \leq 0 \text{ s}^4\text{ M}_{\odot}$~\cite{delPozzo:TaylorTidal}.
+Here we assume low spin priors $|\chi| \leq 0.05$, as well as $0 \leq \lambda_0 \leq 3207$ and $-4490 \leq \lambda_1 \leq 0$~\cite{delPozzo:TaylorTidal}\footnote{These are converted from the dimensional forms found in Ref.~\cite{delPozzo:TaylorTidal} into their corresponding dimensionless forms.}.
 The process we utilize to compute single and combined statistical uncertainties for each detector sensitivity $S_n^A(f)$ is detailed in App.~\ref{app:stackingProcedure}.
@@
 \caption{
-Tabulated results for the estimated statistical errors on $\lambda_0$ for the combined results of $N_A$ detections corresponding to the estimated upper, central, and lower limits of the binary NS merger detection rate $\mathcal{R}$.
+Tabulated results for the estimated statistical errors on the tidal deformability at $1.4\text{ M}_{\odot}$, $\lambda_0$, for the combined results of $N_A$ detections corresponding to the estimated upper, central, and lower limits of the binary NS merger detection rate $\mathcal{R}$.
 This is repeated for 5 future detector sensitivities: aLIGO, A\texttt{+}, Voyager, CE, and ET.
 Below, $\rho^A_{\text{GW170817}}$ and $\sigma^A_{\text{GW170817}}$ correspond to the approximate SNR and $\sigma_{\lambda_0}$ of GW170817 had it been observed by the future interferometer, and $\sigma^A_N$ corresponds to the overall uncertainty on $\lambda_0$ after $N_A$ detections on interferometer $A$.
-It can be seen here that the statistical errors on $\lambda_0$ become comparable with the systematics (set to be $P_{90}=12.014$) from using improved binary Love relations from Voyager and on, indicating when it may be safe to utilize new EoS-insensitive relations.
+It can be seen here that the statistical errors on $\lambda_0$ become comparable with the systematics (set to be $P_{90}=13.19$) from using improved binary Love relations from Voyager and on, indicating when it may be safe to utilize new EoS-insensitive relations.
 Note that the approximation for $\sigma^A_N$ under the O2 detector sensitivity is left blank due to the singularity of the detected event.
@@
 \\[-1em]
-\multicolumn{1}{c}{}  &  \multicolumn{1}{|c|}{\multirow{2}{*}{$\rho^A_{\text{GW170817}}$}}  &  \multirow{ 2}{*}{\large $\frac{\sigma^A_{\text{GW170817}}}{10^{-25}}$}  &  \multicolumn{3}{|c|}{$N_A$}  &  \multicolumn{3}{|c|}{$\sigma^A_N / 10^{-25}$}  \\
+\multicolumn{1}{c}{}  &  \multicolumn{1}{|c|}{\multirow{2}{*}{$\rho^A_{\text{GW170817}}$}}  &  \multirow{ 2}{*}{$\sigma^A_{\text{GW170817}}$}  &  \multicolumn{3}{|c|}{$N_A$}  &  \multicolumn{3}{|c|}{$\sigma^A_N$}  \\
 \cline{4-6}\cline{7-9}
@@
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
- O2  & \multicolumn{1}{|c|}{$32.40$}  & $26.53$ &  \multicolumn{1}{|c|}{--} & -- & -- & \multicolumn{1}{|c|}{--} & -- & --\\
+ O2  & \multicolumn{1}{|c|}{$32.40$}  & $170.13$ &  \multicolumn{1}{|c|}{--} & -- & -- & \multicolumn{1}{|c|}{--} & -- & --\\
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
- aLIGO  & \multicolumn{1}{|c|}{$90.74$}  & $17.10$ &  \multicolumn{1}{|c|}{$20$} & $98$ & $304$ & \multicolumn{1}{|c|}{$28.51$} & $12.99$ & $7.32$\\
+ aLIGO  & \multicolumn{1}{|c|}{$90.74$}  & $109.7$ &  \multicolumn{1}{|c|}{$20$} & $98$ & $304$ & \multicolumn{1}{|c|}{$182.8$} & $83.31$ & $46.95$\\
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
- A\texttt{+}  & \multicolumn{1}{|c|}{$180.95$}  & $7.12$ &  \multicolumn{1}{|c|}{163} & 786 & 2,419 & \multicolumn{1}{|c|}{$9.19$} & $3.85$ & $2.13$\\
+ A\texttt{+}  & \multicolumn{1}{|c|}{$180.95$}  & $45.64$ &  \multicolumn{1}{|c|}{163} & 786 & 2,419 & \multicolumn{1}{|c|}{$58.94$} & $24.69$ & $13.66$\\
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
@@
 
- Voyager  & \multicolumn{1}{|c|}{$428.89$}  & $3.94$ &  \multicolumn{1}{|c|}{2,191} & 10,544 & 32,454 & \multicolumn{1}{|c|}{$3.27$} & $1.49$ & $0.83$\\
+ Voyager  & \multicolumn{1}{|c|}{$428.89$}  & $25.26$ &  \multicolumn{1}{|c|}{2,191} & 10,544 & 32,454 & \multicolumn{1}{|c|}{$20.97$} & $9.556$ & $5.323$\\
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
@@
 
- ET-D  & \multicolumn{1}{|c|}{$1398.03$}  & $1.07$ &  \multicolumn{1}{|c|}{71,536} & 344,270 & 1,059,638 & \multicolumn{1}{|c|}{$0.60$} & $0.27$ & $0.15$\\
+ ET-D  & \multicolumn{1}{|c|}{$1398.03$}  & $6.871$ &  \multicolumn{1}{|c|}{71,536} & 344,270 & 1,059,638 & \multicolumn{1}{|c|}{$3.848$} & $1.732$ & $0.9621$\\
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
@@
 
- CE  & \multicolumn{1}{|c|}{$2807.45$}  & $1.20$ &  \multicolumn{1}{|c|}{295,200} & 1,420,650 & 4,372,653 & \multicolumn{1}{|c|}{$0.58$} & $0.26$ & $0.14$\\
+ CE  & \multicolumn{1}{|c|}{$2807.45$}  & $7.664$ &  \multicolumn{1}{|c|}{295,200} & 1,420,650 & 4,372,653 & \multicolumn{1}{|c|}{$3.720$} & $1.668$ & $0.8979$\\
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
@@
 
-Concluding, we find that the Voyager, ET, and CE detectors all exhibit enough uncertainty reduction that the systematics on $\lambda_0$ introduced from using improved EoS-insensitive relations (found to be $2.06 \times 10^{-25}\text{ s}^5$) no longer become negligible in the error budget.
+Concluding, we find that the Voyager, ET, and CE detectors all exhibit enough uncertainty reduction that the systematics on $\lambda_0$ introduced from using improved EoS-insensitive relations (found to be $13.19$) no longer become negligible in the error budget.
 This was also shown for the case of $\tilde\Lambda$, only taking into account single observed events, where ET and CE detectors both observe comparable statistical and systematic errors on $\tilde\Lambda$.
@@
 \item[(i)] Perform a Fisher analysis as outlined in Sec.~\ref{sec:futureObservations} using detector sensitivity $S_n^A(f)$, while restricting the luminosity distance $D_L$ such that an SNR of $\rho^{\text{O2}}_{\text{GW170817}}=32.4$ would be achieved on O2 sensitivity $S_n^{\text{O2}}(f)$.
-Here we assume low spin priors $|\chi| \leq 0.05$, as well as $0 \text{ s}^5 \leq \lambda_0 \leq 5 \times 10^{-23} \text{ s}^5$ and $-5 \times 10^{-18} \text{ s}^4\text{ M}_{\odot} \leq \lambda_1 \leq 0 \text{ s}^4\text{ M}_{\odot}$~\cite{delPozzo:TaylorTidal}.
+Here we assume low spin priors $|\chi| \leq 0.05$, as well as $0 \leq \lambda_0 \leq 3207$ and $-4490 \leq \lambda_1 \leq 0$~\cite{delPozzo:TaylorTidal} (These are converted from their corresponding dimensional forms).
 This results in a SNR $\rho^A_{\text{GW170817}}$ and a single-event statistical error $\sigma_\text{GW170817}^A$ accrued in the extraction of $\lambda_0$ on detector $A$.

### 2019-02-09 paper/bin-love-after-gw170817.tex
Switched some figures to absolute differences

@@
 Comparison between the EoS-insensitive relations (I-Love-Q, C-Love, R-Love, and binary Love) maximal EoS variability for the results of previous works~\cite{Yagi:ILQ,Yagi:binLove}, and the unconstrained and constrained sets of EoSs analyzed here.
-The maximum EoS variation, given by the largest fractional difference (the R-Love variability is shown as the absolute difference in m here) from the fits as shown in Figs.~\ref{fig:ILQ},~\ref{fig:clove},~\ref{fig:rlove} and~\ref{fig:binLove}, observes a considerable improvement for the constrained set of EoSs, compared to the unconstrained set as well as that found in previous works.
+The maximum EoS variation, given by the largest fractional difference (the absolute difference is also shown in parenthesis for the C-Love, R-Love, and binary Love fits) from the fits as shown in Figs.~\ref{fig:ILQ},~\ref{fig:clove},~\ref{fig:rlove} and~\ref{fig:binLove}, observes a considerable improvement for the constrained set of EoSs, compared to the unconstrained set as well as that found in previous works.
 Additionally, note how the maximal EoS variation for the unconstrained set of EoSs is slightly larger than that found in Refs.~\cite{Yagi:ILQ,Yagi:binLove} - due to the effects of large random sampling taking into account more sources of uncertainty.
@@
  \hline
- $C-\Lambda$ & $0.065$ & $0.07198$ & $0.02169$\\
- $R-\Lambda$ & -- & $358.9 \text{ m}$ & $881.4 \text{ m}$\\
- \hline
- $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.50$} & \multirow{2}{*}{$0.5724$} & \multirow{2}{*}{$0.2140$}\\
- $(q=0.90)$ & & &\\
+ \noalign{\smallskip}
+\noalign{\smallskip}
+ \noalign{\smallskip}
+\noalign{\smallskip}
+\hline
+ \hline
+ \textbf{EoS-insensitive} & \multicolumn{3}{c}{\textbf{Maximal EoS Variability}} \\
+ \cline{2-4}
+ \textbf{Relation} & \multicolumn{1}{c|}{\emph{Previous}} & \multicolumn{1}{c|}{\emph{Unconstrained}} & \emph{Constrained}\\
+ \hline
+ \multirow{2}{*}{$C-\Lambda$} & $0.065$ & $0.07198$ & $0.02169$\\
+ & (--) & ($0.01837$) & ($0.006582$)\\
+  \hline
+ \multirow{2}{*}{$R-\Lambda$} & -- & $0.02172$ & $0.05649$\\
+ & (--) & ($358.9 \text{ m}$) & ($881.4 \text{ m}$)\\
+ \hline
+ $\Lambda_a-\Lambda_s$ & $\sim0.50$ & $0.5724$ & $0.2140$\\
+ $q=0.90$ & (--) & ($190.1$) & ($37.23$) \\
  \cline{1-1}
- $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.20$} & \multirow{2}{*}{$0.2447$} & \multirow{2}{*}{$0.08284$}\\
-  $(q=0.7)$ & & &\\
+ $\Lambda_a-\Lambda_s$ & $\sim0.20$ & $0.2447$ & $0.08284$\\
+  $q=0.7$ & (--) & ($320.4$) & ($51.62$) \\
   \cline{1-1}
- $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.025$} & \multirow{2}{*}{$0.03841$} & \multirow{2}{*}{$0.01823$}\\
-  $(q=0.50)$ & & &\\
+ $\Lambda_a-\Lambda_s$ & $\sim0.025$ & $0.03841$ & $0.01823$\\
+  $q=0.50$ & (--) & ($244.1$) & ($28.96$) \\
   \cline{1-1}
@@
 \begin{center} 
-\includegraphics[width=.86\columnwidth]{CL.eps}
+\includegraphics[width=\columnwidth]{CL.eps}
 \end{center}
@@
 \begin{center} 
-\includegraphics[width=1\columnwidth]{RL.eps}
+\includegraphics[width=\columnwidth]{RL.eps}
 \end{center}

### 2019-02-09 paper/bin-love-after-gw170817.tex
removed BL hybrid star section and discussed why it didnt work and how well improve on it in future works

@@
 Next we consider improvements to the binary Love relations.
-Similar to Sec.~\ref{sec:ilq}, we consider two classes of NSs: nuclear matter EoSs and hybrid quark-hadron star EoSs~\cite{Paschalidis2018,Alford:2017qgh,1971SvA....15..347S,Zdunik:2012dj,Alford:2013aca}.
-We begin in Sec.~\ref{sec:binLove-nuclear} by fitting new binary Love relations to the nucleonic matter EoSs as was done in~\cite{Yagi:binLove}.
-This is followed in Sec.~\ref{sec:binLove-hybrid} by an analysis and discussion into different fits which incorporate hybrid star EoSs.
-
-\subsubsection{Nuclear matter stars}\label{sec:binLove-nuclear}
-Following Ref.~\cite{Yagi:binLove}, we fit the binary Love relations to the constrained and unconstrained EoSs using the two-dimensional curve:
+Similar to Sec.~\ref{sec:ilq}, we consider two distinct classes of NSs: nuclear matter EoSs and hybrid quark-hadron star EoSs~\cite{Paschalidis2018,Alford:2017qgh,1971SvA....15..347S,Zdunik:2012dj,Alford:2013aca}.
+Following Ref.~\cite{Yagi:binLove}, we begin by fitting the binary Love relations to the constrained and unconstrained sets of EoSs using the two-dimensional curve:
 \begin{equation}\label{eq:binLovefit}
@@
 Updated fit parameters for the binary Love relations, as given by the curve found in Eq.~\ref{eq:binLovefit}.
-The bottom row corresponds to separate fits corresponding to the hybrid star branch of the hybrid EoSs.
 }\label{tab:binLovefit}
 \addtolength{\tabcolsep}{1pt} 
-\begin{tabular}{c | c  c  c  c  c  c  c  c c c c c c c} 
- \hline
- \hline
- Fit & $n$ & $\alpha$ & $b_{11}$ & $b_{12}$ & $b_{21}$ & $b_{22}$ & $b_{31}$ & $b_{32}$ & $c_{11}$ & $c_{12}$ & $c_{21}$ & $c_{22}$ & $c_{31}$ & $c_{32}$\\
- \hline
- NS & $0.743$ & $-1$ & $-14.40$ & $14.45$ & $31.36$ & $-32.25$ & $-22.44$ & $20.35$ & $-15.25$ & $15.37$ & $37.33$ & $-43.20$ & $-29.93$ & $35.18$\\
- HS & $0.743$ & $-1$ & $343.0$ & $-382.6$ & $519.5$ & $-594.3$ & $811.6$ & $-867.6$ & $82.60$ & $-97.79$ & $242.2$ & $-262.9$ & $244.9$ & $-268.8$\\
+\begin{tabular}{c  c  c  c  c  c  c  c c c c c c c} 
+ \hline
+ \hline
+$n$ & $\alpha$ & $b_{11}$ & $b_{12}$ & $b_{21}$ & $b_{22}$ & $b_{31}$ & $b_{32}$ & $c_{11}$ & $c_{12}$ & $c_{21}$ & $c_{22}$ & $c_{31}$ & $c_{32}$\\
+\hline
+$0.743$ & $-1$ & $-14.40$ & $14.45$ & $31.36$ & $-32.25$ & $-22.44$ & $20.35$ & $-15.25$ & $15.37$ & $37.33$ & $-43.20$ & $-29.93$ & $35.18$\\
  \hline
@@
 Additionally, the unconstrained set of EoSs show similar, yet slightly larger EoS variation than was previously found in Ref.~\cite{Yagi:binLove} due to the random sampling taken into account in this analysis.
-Once again, the maximum EoS variability (in terms of fractional difference from the fit for comparison purposes) is tabulated in Tab.~\ref{tab:maxVar} for each value of mass ratio.
+Once again, the maximum EoS variability (in terms of both absolute and fractional differences from the fit) is tabulated in Tab.~\ref{tab:maxVar} for each value of mass ratio considered here.
 
@@
 The maximal EoS variability (shown as a the fractional difference for comparison purposes) for each case is tabulated and compared in Tab.~\ref{tab:maxVar}.
-Additionally shown is the binary Love relations for the 10 hybrid star EoSs (dashed bright green curves), as well as the HS fits (dot-dashed blue curves) discussed in Sec.~\ref{sec:binLove-hybrid}.
+Additionally shown are the binary Love relations for the 10 hybrid star EoSs (dashed bright green curves).
 Observe the large deviations from the fit as the mass ratio $q$ increases, returning near the fit before the transitional pressure at large values of $\Lambda_s$.
-This is shown in the bottom three panels as the absolute difference from the NS fit for comparison, while the HS fits show similar EoS variability to the constrained EoSs.
 }
@@
 
+Additionally shown in Fig.~\ref{fig:binLove} are the binary Love relations for the 10 hybrid EoSs discussed in previous sections.
+As described in Sec.~\ref{sec:theory}, transitional quark-hadron matter stars undergo first-order phase transitions at pressure $P_{\text{tr}}$, where the hadronic branch departs into a quark-matter branch at the corresponding transitional mass $M_{\text{tr}}$.
+These transitions result in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq M_{\text{tr}}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote these as ``HS"), and (ii) low-mass ($M \leq M_{\text{tr}}$) hadronic stars with no internal transition to quark matter (we denote these as ``NS").
+Contrary to the single-star relations (I-Love-Q, C-Love, and R-Love) where the hybrid stars moderately agree with their nuclear matter counterparts, the binary-star relations show large disagreement, which can be seen in Fig.~\ref{fig:binLove}.
+Observe how the agreement with the fit is quite good at low pressures (large $\Lambda_s$) where the the binaries consist of NS/NS combinations (here, both stars' EoSs consist of the same class of nuclear matter as the constrained EoSs).
+Once the critical pressure is reached, one or both stars transition into the hybrid branches, resulting in large reductions in tidal deformability as shown in Fig.~\ref{fig:hybridML}.
+When one star lies on the hadronic-matter branch while the other is on the quark-matter branch, 
+the difference between tidal deformabilities becomes larger than expected for pure hadronic-matter stars.
+This results in a large deviation in the sums and differences of tidal deformabilities $(\Lambda_1 \pm \Lambda_2)$, disrupting the overall universality and generating the large ``bump" in the binary love relations for hybrid stars\footnote{This discrepancy is not present in the I-Love-Q and C-Love relations due to their singular nature.} seen in Fig~\ref{fig:binLove}.
+
+Due to the inconsistencies in the sums and differences of tidal deformabilities for binary hybrid star systems, we conclude that hybrid stars do \emph{not} agree with the traditional nuclear matter binary Love relations.
+A number of attempts were made to reconcile these differences, such as performing separate ``HS" binary Love relations fitted directly to the hybrid star branches of the EoSs.
+This analysis quickly left the scope of the paper due to the large number of parameters required to control the varying transitional pressures through different EoSs.
+Therefore, we leave this analysis on the hybrid star binary Love relations to be discussed in future works.
+There, we anticipate generating large numbers of hybrid star EoSs with varying transition masses to be taken into account as an additional fitting parameter in a piece-wise fitting function designed to take into account the ``bumps" in the binary Love relations.
+
+\iffalse%%%%%%%%%%%%%%%%%%% COMMENTED OUT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Hybrid quark-hadron stars}\label{sec:binLove-hybrid}
@@
 To determine how each of class of binary NS systems obey our improved binary Love relations, we pick a representative set of 10 binary pairs from each class from the ACB5 hybrid EoS, with a transition at $M_{\text{tr}} \approx 1.4 \text{ M}_{\odot}$.
-Binary Love values are computed for each pair, and fractional residuals from the binary Love curve found in Sec.~\ref{sec:binLove-nuclear} are determined and compared to the values from the constrained set of EoSs.
+Binary Love values are computed for each pair, and fractional residuals from the binary Love curve found in Sec.~\ref{sec:binary} are determined and compared to the values from the constrained set of EoSs.
 The results are shown in Fig.~\ref{fig:hybrid}.
@@
 To compensate for these differences, we separate the two branches into the NS (hadronic matter) and HS (hybrid matter) branches.
-We first observe that the NS branches obey the ``hadronic" binary Love relations derived in Sec.~\ref{sec:binLove-nuclear} within the same EoS variability, indicating no further need for additional fits.
+We first observe that the NS branches obey the ``hadronic" binary Love relations derived in Sec.~\ref{sec:binary} within the same EoS variability, indicating no further need for additional fits.
 However, the HS branches do not follow the same relations, suggesting the need for a new ``hybrid binary love fit" pertaining to this branch alone.
@@
 Similar to the previous section, the fractional difference from the fit for each HS branch is computed, resulting in a maximum EoS variability of $18.49$\% for $q=0.90$.
-This result is strongly consistent with the results found for the nuclear matter fits of Sec.~\ref{sec:binLove-nuclear}.
+This result is strongly consistent with the results found for the nuclear matter fits of Sec.~\ref{sec:binary}.
 
@@
 By separating the two branches of the hybrid EoSs, we find a new ``hybrid" branch binary Love fit which gives consistent results to that found for the nuclear matter fits. 
+\fi%%%%%%%%%%%%%%%%%%% COMMENTED OUT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 In particular, we restrict our focus to only the constrained set of EoSs.
-Residuals in $\Lambda_a$ are computed as $\Lambda_a^{\text{relation}}(\Lambda_s,q)-\Lambda_a^{\text{true}}$, where $\Lambda_a^{\text{true}}$ corresponds to the true value predicted by the sample EoSs, and $\Lambda_a^{\text{relation}}(\Lambda_s,q)$ corresponds to the value obtained through the EoS-insensitive relations found in Sec.~\ref{sec:binLove-nuclear}.
+Residuals in $\Lambda_a$ are computed as $\Lambda_a^{\text{relation}}(\Lambda_s,q)-\Lambda_a^{\text{true}}$, where $\Lambda_a^{\text{true}}$ corresponds to the true value predicted by the sample EoSs, and $\Lambda_a^{\text{relation}}(\Lambda_s,q)$ corresponds to the value obtained through the EoS-insensitive relations found in Sec.~\ref{sec:binary}.
 We follow this up by converting the $\Lambda_a$ residuals into $\lambda_0$, allowing us to approximate the overall systematic errors on $\lambda_0$ from using the improved binary Love relations.
@@
 \caption{
-Residuals on $\lambda_0$ computed as $\lambda_0^{\text{fit}}-\lambda_0^{\text{true}}$ for the binary Love relations modeled in Sec.~\ref{sec:binLove-nuclear} for both constrained and unconstrained sets of EoSs.
+Residuals on $\lambda_0$ computed as $\lambda_0^{\text{fit}}-\lambda_0^{\text{true}}$ for the binary Love relations modeled in Sec.~\ref{sec:binary} for both constrained and unconstrained sets of EoSs.
 These residuals obey Gaussian distributions centered at $\mu=-0.1530$ and $\mu=0.2710$ with standard deviations of $\sigma=9.764$ and $\sigma=78.28$ for the constrained and unconstrained sets of EoSs, respectively.
@@
 The improvement in the multipole love relations can then be used to increase the accuracy of surrogate models.
+Additionally, we plan on a more comprehensive analysis into the intricacies of new hybrid star binary Love relations, as discussed in Sec.~\ref{sec:binary}.
 

### 2019-02-10 paper/bin-love-after-gw170817.tex
implemented comments from teleconference

@@
 \caption{
-Comparison between the $I-\Lambda$ maximal EoS variability for the constrained EoSs and the hybrid EoSs for three different cases of fitting data to Eq.~\ref{eq:ILQfitNew}: (1) fit to the combined data of constrained and hybrid EoS, (2) fit to the constrained EoS data alone, and (3) fit to the hybrid EoS data alone.
+Comparison between the $I-\Lambda$ maximal EoS variability (fractional difference from the fit) for the constrained EoSs and the hybrid EoSs for three different cases of fitting data to Eq.~\ref{eq:ILQfitNew}: (1) fit to the combined data of constrained and hybrid EoS, (2) fit to the constrained EoS data alone, and (3) fit to the hybrid EoS data alone.
 Observe how for all 3 cases, the hybrid EoSs are only universal up to a minimum of $\sim1$\%, while in each case the constrained EoSs outperform the hybrid ones.
@@
 We also present the uncertainty on a NS radius measurement using the C-Love relations in the bottom panel of Fig.~\ref{fig:rlove}, defined as the absolute difference from the fits.
-We observe a large suppression in the radius measurement accuracy from the unconstrained set of EoSs to the constrained set, tabulated in Tab.~\ref{tab:maxVar} as the maximal EoS measurement uncertainty.
+This indicates that one can reliably measure the NS radius within $\sim 180 \text{ m} -350$ m, using the C-Love relations computed using the constrained set of EoSs.
+We further observe a large suppression in the radius measurement accuracy from the unconstrained set of EoSs to the constrained set, tabulated in Tab.~\ref{tab:maxVar} as the maximal EoS measurement uncertainty.
 
@@
 Similar to Tab.~\ref{tab:hybridCompare} but for the C-Love relation.
-Observe how for all 3 cases, the hybrid EoSs are only universal up to a minimum of $\sim1$\%, while in each case the constrained EoSs outperform the hybrid ones.
+Observe how for all 3 cases, the hybrid EoSs are only universal up to a minimum of $\sim1$\% (fractional difference from the fit), while in each case the constrained EoSs outperform the hybrid ones.
 The second case is demonstrated in Fig.~\ref{fig:clove}.
@@
 Here, q is the mass ratio $q \equiv m_1/m_2$ with $m_1 \leq m_2$, and $F_n(q)$ is the Newtonian-limiting control factor given by:
-\begin{equation}
+\begin{equation}\label{eq:control}
 F_n(q) \equiv \frac{1-q^{10/(3-n)}}{1+q^{10/(3-n)}}.
@@
 Once again, the maximum EoS variability (in terms of both absolute and fractional differences from the fit) is tabulated in Tab.~\ref{tab:maxVar} for each value of mass ratio considered here.
+We take note that while the fractional errors increase rapidly with increasing mass ratio $q$, the absolute errors remain consistent, with a subtle maximum at $q=0.75$. 
+This can be explained by the control factor $F_n(q)$ given by Eq.~\ref{eq:control}, which similarly observes a peak for central mass ratio values of $q\approx0.75$.
+We additionally make two observations about the effective ranges of $\Lambda_s$ seen in Fig.~\ref{fig:binLove}: (i) as the constituent masses in the binary system become further separated, the range of $\Lambda_s$ values shrinks; and (ii) the constrained set of EoSs typically display smaller values of $\Lambda_s$ than the unconstrained set do.
+The former observation can be explained by the following reasoning: as the masses further separate, there is a limited range of tidal deformabilities $\Lambda_{1,2}$ in the M-L relationships which satisfy the mass ratio constraint.
+From this we suggest the reader take note that as the mass ratio decreases, the allowable paramreter space for the binary Love relations shrinks.
+The latter observation originates from the EoS generation process: the unconstrained EoSs are randomly generated -- resulting in various EoSs which are both stiffer and softer than those constrained by GW170817.
+This results in the unconstrained EoSs containing a larger range of tidal deformabilities $\Lambda$ (both above and below) than the constrained ones, which ultimately gives \emph{larger} values of $\Lambda_s=\frac{1}{2}(\Lambda_1+\Lambda_2)$.
 
@@
 Observe how this figure shows similar results on $\tilde\Lambda$ to that found on $\lambda_0$ for the case of one event - that is, future detectors ET and CE both observe statistical errors on $\tilde\Lambda$ dropping below the systematic binary Love errors for a single event.
+\red{We note that in Figs.~\ref{fig:stackedFisher} and~\ref{fig:singleFisherLt}, the single-event measurement uncertainty is slightly higher for CE than ET despite observing a larger SNR, due to the frequency-dependant detector sensitivities seen in Fig.~\ref{fig:sensitivities}.}
+
 \begin{figure}

### 2019-02-11 paper/bin-love-after-gw170817.tex
implemented comments from teleconference, and also did a thourough read through to fix flow, grammer, english, spelling,, and general issues

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Begin Abstract %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%
+%%%% ABSTRACT %%%%
+%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%
+
 \begin{abstract}
@@
 % What universal relations do
-Such EoS-insensitive relations allow the elimination of some tidal parameters from the list of model parameters, thus breaking degeneracies and ultimately reducing parameter extraction uncertainties.
+Such EoS-insensitive relations allow the elimination of some tidal parameters from the list of model parameters, thus breaking degeneracies and ultimately reducing the parameter extraction uncertainties.
 % What we will do
-However, even the most precise of EoS insensitive relations carry EoS variation which inject systematic errors into the parameter extraction process.
-In this document, we explain how one can reduce equation of state variation for I-Love-Q, C-Love, and binary Love relations, which helps to reduce systematic errors on the tidal measurement of binary neutron star mergers.
-However, we show that the systematic effects of these relations is very small until next-generation detectors. 
+However, even the most precise of EoS-insensitive relations carry EoS variation uncertainties which inject systematic errors into the parameter extraction process.
+In this document, we explain how one can reduce the equation of state variation for the I-Love-Q, C-Love, and binary Love relations, which helps to reduce the systematic errors on the tidal measurement of binary neutron star mergers.
+However, we show that the systematic effects of these relations are negligible until next-generation detector sensitivities. 
 We achieve this  by restricting to only equations of state drawn from the 90\% posterior constraint on pressure as a function of density, as derived by the LIGO Collaboration.
@@
 % Conclude
-We end by comparing systematic errors on tidal measurement due to the equation of state variation with statistical errors and comment on whether one can safely use these EoS-insensitive relations with future gravitational wave observations.
-We conclude that the systematic errors injected from the use of improved EoS-insensitive relations become comparable to the statistical errors for future design upgrade Voyager.
+We end by comparing the systematic errors on tidal measurements due to the equation of state variation with statistical errors and comment on whether one can safely use these EoS-insensitive relations with future gravitational wave observations.
+We conclude that the systematic errors injected from the use of improved EoS-insensitive relations become comparable to the statistical errors for future detector upgrade Voyager.
 \end{abstract}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Begin Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%
+%%%% INTRODUCTION %%%%
+%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%
 
 \section{Introduction}\label{sec:intro}
-%Intro
 
@@
 }}
+%Intro
 The dependence of pressure on density for cold supranuclear matter found inside neutron stars (NSs) remains to be one of the largest mysteries in both nuclear physics and astrophysics.
-This internal structure of such stars, known as the equation of state (EoS), is exceedingly important, as it is the determining factor for many NS observables - such as the mass, the radius, and many more.
+This internal structure of such stars, known as the equation of state (EoS), is exceedingly important, as it is the determining factor for many NS observables - such as the mass and the radius.
 Unfortunately, terrestrial experiments can only study the EoS to around the nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy} (although some temperature-dependent heavy-ion collision experiments may probe higher densities~\cite{Danielewicz:2002pu}), making NSs ideal laboratories for constraining ultra dense nuclear matter.
@@
 Independent measurements of NS observables can be used to constrain the nuclear EoS.
-For example, electromagnetic observations of the mass-radius relationship of NSs have been used to place limits on the NS EoS~\cite{guver,ozel-baym-guver,steiner-lattimer-brown,Lattimer2014,Ozel:2016oaf}.
+For example, electromagnetic observations of the NS mass-radius relationship have been used to place limits on the EoS~\cite{guver,ozel-baym-guver,steiner-lattimer-brown,Lattimer2014,Ozel:2016oaf}.
 However, these implications potentially suffer from large systematic errors due to various x-ray burst astrophysical mismodeling uncertainties.
@@
 %reparameterization of the template
-In the case of binary NSs, each star becomes deformed via the process highlighted above, resulting in two highly correlated tidal parameters $\Lambda_1$ and $\Lambda_2$ entering in the gravitational waveform\cite{Flanagan2008,Vines:2011ud}.
+In the case of binary NSs, each star becomes deformed via the process highlighted above, resulting in two highly correlated tidal parameters $\Lambda_1$ and $\Lambda_2$ entering the gravitational waveform~\cite{Flanagan2008,Vines:2011ud}.
 Due to high correlations between between the two parameters, independent extraction becomes very difficult at current interferometer sensitivities~\cite{Wade:tidalCorrections}.
 Typically, these high correlations can be reduced by strategically reparameterizing the waveform template with new tidal parameters constructed from linear combinations of $\Lambda_1$ and $\Lambda_2$.
-For example, utilizing the parameters $\tilde{\Lambda}$ and $\delta \tilde{\Lambda}$~\cite{Favata:2013rwa,Wade:tidalCorrections} which enter the GW waveform at different post-Newtonian (PN) orders (powers of the ratio between the orbital speed and the speed of light $v/c^{2n}$) partially mitigates these correlations.
-Similarly, the waveform may be parameterized by mass-independent tidal parameters $\lambda_0$ and $\lambda_1$, derived through a Taylor expansion about $m_0=1.4 \text{ M}_{\odot}$ of tidal deformability $\Lambda \approx \lambda_0+\lambda+1(1-\frac{m}{m_0})$~\cite{delPozzo:TaylorTidal,Yagi:binLove}.
+For example, utilizing the parameters $\tilde{\Lambda}$ and $\delta \tilde{\Lambda}$~\cite{Favata:2013rwa,Wade:tidalCorrections} which enter the GW waveform at different post-Newtonian (pN) orders\footnote{n-pN order corrections enter the gravitational waveform at powers of the ratio between the orbital speed and the speed of light $v/c^{2n}$.} partially mitigates these correlations.
+Similarly, the waveform may be parameterized by mass-independent tidal parameters $\lambda_0$ and $\lambda_1$, derived through a Taylor expansion about $m_0=1.4 \text{ M}_{\odot}$ of tidal deformability $\Lambda \approx \lambda_0+\lambda_1(1-\frac{m}{m_0})$~\cite{delPozzo:TaylorTidal,Yagi:binLove}.
 Use of this set of tidal parameters allows one to effectively combine multiple events with varying mass and $\tilde\Lambda$ components, not possible in the former parameterization of $\tilde{\Lambda}$ and $\delta \tilde{\Lambda}$
@@
 %Universal relations
-Unfortunately, current detectors are only sensitive enough to accurately measure the dominant tidal parameter, $\lambda_0$ (also known as $\Lambda_{1.4}$, the tidal deformability at $1.4 \text{ M}_{\odot}$).
+Unfortunately, current detectors are not sensitive enough to accurately measure the dominant tidal parameter, $\lambda_0$ (also known as $\Lambda_{1.4}$, the tidal deformability at $1.4 \text{ M}_{\odot}$).
 Previous work by Yagi and Yunes~\cite{Yagi:binLove} resolved this issue by finding approximately EoS-insensitive ``binary Love relations" between symmetric and anti-symmetric combinations of tidal deformabilities $\Lambda_{s,a}=\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$.
-This allows one to further break degeneracies between tidal parameters, resulting in both (i) a decrease in uncertainty upon parameter extraction of $\Lambda_s$ on the removal of parameter $\Lambda_a$ from the model, and (ii) the ability to measure the secondary tidal parameter upon measurement of the first~\cite{Katerina:residuals}.
-Use of these relations leads to up to an order of magnitude improvement in parameter estimation of $\Lambda_s$ through a simple Fisher analysis~\cite{Yagi:binLove}, also confirmed with the detailed analysis of~\cite{Katerina:residuals}.
-Similar ``I-Love-Q" and ``C-Love" relations~\cite{Yagi:ILQ} have been found between individual NS observables: quadrupole moment , moment of inertia, tidal deformability, and compactness; similarly allowing the removal of tidal parameters from the model list, and allowing an automatic determination of one observable through the measurement of another.
-However, these relations have been tuned to a collection of EoS models, and each have intrinsic uncertainties associated with their use.
+This allows one to further break degeneracies between tidal parameters, resulting in both (i) a decrease in uncertainty upon parameter extraction of $\Lambda_s$ on the removal of parameter $\Lambda_a$ from the model; and (ii) the ability to measure the secondary tidal parameter upon measurement of the first~\cite{Katerina:residuals}.
+Use of these relations leads to up to an order of magnitude improvement in parameter estimation of $\Lambda_s$ through a simple Fisher analysis~\cite{Yagi:binLove}, also confirmed with the detailed analysis seen in Ref.~\cite{Katerina:residuals}.
+Similar ``I-Love-Q" and ``C-Love" relations~\cite{Yagi:ILQ} have been found between individual NS observables: quadrupole moment, moment of inertia, tidal deformability, and compactness; similarly allowing the removal of tidal parameters from the model list, and allowing an automatic determination of one observable through the measurement of another.
+However, these relations have been tuned to a specific collection of EoS models, and each have intrinsic uncertainties associated with their use.
 
@@
 In this analysis, we aim to improve this important work by imposing the restrictions found on the EoS~\cite{LIGO:posterior} derived from the recent binary NS merger observation, GW170817~\cite{TheLIGOScientific:2017qsa}.
-By restricting to only EoSs which lie within the the 90\% credible region on pressure as a function of density found in~\cite{LIGO:posterior}, we repeat the analyses done in~\cite{Yagi:binLove,Yagi:ILQ} and show an increase in universality for I-Love-Q, C-Love, and binary Love relations.
-We also investigate the relationship between the NS radius and its tidal deformability, or the R-Love relations, determining if the uncertainties can be reduced.
-In addition, we consider hybrid star EoSs seen in~\cite{Paschalidis2018}, which experience strong first-order transitions from hadronic matter to quark matter.
-These provide a departure from the nuclear matter relations considered here - providing valuable insight into them.
-Further, we estimate the viability of using improved EoS-insensitive relations on future GW detections by performing simple Fisher analyses to approximate when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in the relations.
-To estimate the effect of waveform mismodeling, we additionally consider two different tidal corrections to the injected PhenomD~\cite{PhenomDI,PhenomDII} waveform: 6PN~\cite{Wade:tidalCorrections} and NRTidal~\cite{Samajdar:NRTidal}
+By restricting to only EoSs which lie within the the 90\% credible region on pressure as a function of density found in Ref.~\cite{LIGO:posterior}, we repeat the analyses done in Refs.~\cite{Yagi:binLove,Yagi:ILQ} and show an increase in universality for the I-Love-Q, C-Love, and binary Love relations.
+We also investigate the relationship between the NS radius and its tidal deformability, or the R-Love relations, determining whether the NS radius uncertainties can be reduced.
+In addition, we consider hybrid star EoSs seen in Ref.~\cite{Paschalidis2018}, which experience strong first-order transitions from hadronic matter to quark matter in the core.
+These provide a departure from the nuclear matter relations considered here - providing valuable insight into such EoSs.
+Lastly, we estimate the viability of using the improved EoS-insensitive relations on future GW detections by performing simple Fisher analyses to approximate when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in the relations.
+To further estimate the effect of waveform mismodeling, we additionally consider two different tidal corrections to the injected PhenomD~\cite{PhenomDI,PhenomDII} waveform: 6PN~\cite{Wade:tidalCorrections} and NRTidal~\cite{Samajdar:NRTidal}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% EXECUTIVE SUMMARY %%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %What we did
-In this paper we attempt to improve I-Love-Q, C-Love, and binary Love relations by imposing constraints on the EoS found by GW170817~\cite{LIGO:posterior,TheLIGOScientific:2017qsa}.
-First, we generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, where we (i) impose the restriction that they must be drawn from GW170817s 90\% credible posterior in pressure as a function of density, and (ii) don't impose any restrictions for comparison purposes.
-Next, we follow the important works of~\cite{Yagi:binLove} and~\cite{Yagi:ILQ} to show how the ``constrained" set of EoSs show improved universality (binary Love, I-Love-Q, and C-Love) from both the previous works, and the ``unconstrained" sample, shown by Fig.~\ref{fig:ILQ}.
-In addition, we determine the degree to which hybrid star EoSs obey binary Love relations.
+In this paper we attempt to improve the I-Love-Q, C-Love, and binary Love relations by imposing constraints on the EoS found by GW170817~\cite{LIGO:posterior,TheLIGOScientific:2017qsa}.
+First, we generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, where we (i) impose the restriction that they must be drawn from GW170817s 90\% credible posterior in pressure as a function of density; and (ii) don't impose any restrictions for comparison purposes.
+Next, we follow the important works of Refs.~\cite{Yagi:binLove} and~\cite{Yagi:ILQ} to show how the ``constrained" set of EoSs show improved universality (binary Love, I-Love-Q, and C-Love) from both the previous works, and the ``unconstrained" sample, shown by Fig.~\ref{fig:ILQ}.
+In addition, we determine the degree to which hybrid star EoSs obey the various EoS-insensitive relations.
 Finally, through a simple Fisher analysis, we consider the value in improving EoS-insensitive relations by approximating when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in the relations.
@@
 We also present the relationship between the NS radius and tidal deformability, computed directly from the C-Love relations, showing maximum EoS variability of $358.9 \text{ km}$ from the fit discussed in Sec.~\ref{sec:clove}.
-Additionally, we find that hybrid quark-hadron stars do obey the I-Love-Q and C-Love relations, with sightly increased EoS variability.
-We also find that binaries consisting of one massive hybrid star, and one small-mass hadronic star do not agree with derived binary Love relations, due to the large separation in $\tilde{\Lambda}$ between the constituent stars.
-Due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the EoS-insensitive relations are far outweighed by the statistical errors accrued by extraction of high-order PN tidal parameters from GW waveforms.
-Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from the parameter extraction of $\lambda_0$ (the tidal deformability at $1.4 \text{ M}_{\odot}$) for GW170817 as if it had been observed by future detectors $A \equiv ($ O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, ET~\cite{ET}, CE~\cite{Ap_Voyager_CE}$)$.
-Here, $\sigma^A_{\text{GW170817}}$ and $\rho^A_{\text{GW170817}}$ correspond to the statistical error and signal-to-noise-ratio found from observing GW170817 on detector $A$, and $\sigma^A_N$ represents the combined uncertainty after the detection of $N_A$ events (corresponding to the binary NS merger rate associated interferometer $A$).
+Additionally, we find that the hybrid quark-hadron star EoSs do obey the I-Love-Q and C-Love relations, with sightly increased EoS variability.
+We also find that binaries consisting of one massive hybrid star, and one small-mass hadronic star do not agree with the derived binary Love relations, due to the large separation in $\tilde{\Lambda}$ between the constituent stars.
+
+Due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the EoS-insensitive relations are far outweighed by the statistical errors accrued by the extraction of high pN order tidal parameters from GW waveforms.
+Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from the parameter extraction of $\lambda_0$ (the tidal deformability at $1.4 \text{ M}_{\odot}$) for GW170817 as if it had been observed by various detectors $A \equiv ($ O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, ET~\cite{ET}, CE~\cite{Ap_Voyager_CE}$)$.
+Here, $\sigma^A_{\text{GW170817}}$ and $\rho^A_{\text{GW170817}}$ correspond to the statistical error and signal-to-noise-ratio found from observing GW170817 on detector $A$, and $\sigma^A_N$ represents the combined uncertainty after the detection of $N_A$ events (corresponding to the binary NS merger rate associated with interferometer $A$).
 These values are further tabulated in Table~\ref{tab:variances}.
-It can be seen from this figure that the statistical errors from parameter extraction become comparable the EoS-insensitive relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love relations will become necessary.
-Also shown in the figure is the same measurement uncertainties upon the injection of the PhenomD + NRTidal waveform, rather than the PhenomD + 6PN tidal correction to demonstrate the effect of waveform mismodeling.
+It can be seen from this figure that the statistical errors from parameter extraction become comparable the EoS-insensitive relation systematics (indicated by the magenta horizontal line) for the Voyager interferometer - indicating when the improved binary Love relations will become necessary.
+Also shown in the figure is the same measurement uncertainties upon the injection of the PhenomD + NRTidal~\cite{PhenomDI,PhenomDII,Samajdar:NRTidal} waveform, rather than the PhenomD + 6PN~\cite{PhenomDI,PhenomDII,Wade:tidalCorrections} tidal correction to demonstrate the effect of waveform mismodeling.
+
 \begin{figure}
@@
 \caption{
-Estimated statistical uncertainties on the extraction of the tidal deformability at $1.4 \text{ M}_{\odot}$, $\lambda_0$, observed from interferometers $A=$(O2, aLIGO, A\texttt{+}, Voyager, CE, ET-D$)$ as a function of the signal-to-noise-ratio.
-In this figure, the filled blue circles denote the single-event statistical uncertainties $\sigma^A_{\text{GW170817}}$ of GW170817 as if it were observed on detector $A$.
-Also shown by the turquoise shaded region is combined uncertainty $\sigma^A_N$  from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper and lower limits of the expected binary NS merger detection rates for O2, aLIGO, A\texttt{+}, Voyager, CE, and ET-D over 1 observation year.
-It can be seen that the statistical errors in the parameter extraction become comparable to the systematics from EoS variation in the improved binary Love relations (indicated by the horizontal indigo dashed line) for Voyager, CE, and ET.
+Estimated statistical uncertainties on the extraction of the tidal deformability at $1.4 \text{ M}_{\odot}$, $\lambda_0$, observed from interferometers $A=$(O2, aLIGO, A\texttt{+}, Voyager, CE, ET-D$)$ as a function of the signal-to-noise-ratio $\rho^{\text{A}}_{\text{GW170817}}$.
+%evaluated from $300 \text{ Hz} \leq f \leq 1649 \text{ Hz}$\footnote{This was done for demonstrative purposes, as computing the SNR with $1 \text{ Hz} \leq f \leq 1649 \text{ Hz}$ resulted in smaller statistical uncertainties for ET than CE, albeit having a smaller SNR - a relic originating from ET being more sensitive to the high frequency tidal effects than CE.}.
+In this figure, the filled blue circles denote the single-event statistical uncertainties $\sigma^A_{\text{GW170817}}$ of GW170817 as if it were observed on detector $A$\footnote{We note that ET more accurately measures single events than CE albeit having a smaller SNR - a relic originating from ET being more sensitive to the high frequency tidal effects than CE.
+See Sec.~\ref{sec:futureObservations} for a discussion on this.}.
+Also shown by the cyan shaded region is the combined uncertainty $\sigma^A_N$ from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper and lower limits of the expected binary NS merger detection rates for detector $A$ over 1 observation year.
+It can be seen that the statistical errors in the parameter extraction become comparable to the systematics from EoS variation in the improved binary Love relations (indicated by the horizontal indigo dashed line) for the Voyager, CE, and ET detectors.
 These results are further tabulated in Table~\ref{tab:variances}.
@@
 The organization of this paper is outlined below.
-We begin with a complementary background and theory material in Sec.~\ref{sec:theory}.
+We begin with complementary background and theory material in Sec.~\ref{sec:theory}.
 We continue in Sec.~\ref{sec:universal} by finding new and improved binary Love, I-Love-Q, and C-Love relations, and considering how well hybrid star EoSs agree with the EoS-insensitive relations.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Begin theory %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% BACKGROUND AND THEORY %%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Background and theory}\label{sec:theory}
@@
 \subsection{Spectral representations of neutron star equations of state}\label{sec:eos}
-The structure of a NS and its tidal interactions in a binary system rely heavily on the underlying state function (or equation of state) describing the relationship between pressure ($p$) and energy density ($\epsilon$) of nuclear matter.
+The structure of a NS and its tidal interactions in a binary system rely heavily on the underlying state function (or equation of state - EoS) describing the relationship between the pressure ($p$) and energy density ($\epsilon$) of nuclear matter.
 Given that all currently proposed EoSs utilize certain approximations~\cite{Oertel:Review,Baym:Review}, one method to study a wide range of physically realizable EoSs is to parameterize them such that any realistic EoS can be represented with a small number of parameters.
@@
 \end{equation}
-Using this formalism, any valid EoS can be approximated through the choice of 4 or more spectral coefficients $\gamma_k$, tabulated for several common EoSs in Table 1 of~\cite{Lindblom:2018rfr}.
+Using this formalism, any valid EoS can be approximated through the choice of 4 spectral coefficients $\gamma_k$, tabulated for several common EoSs in Table 1 of Ref.~\cite{Lindblom:2018rfr}.
 
 In the current analysis, we consider EoSs which have been constrained by the recent binary neutron star merger event, GW170817.
-Important recent work~\cite{LIGO:posterior,Carney:2018sdv} sampled EoS parameters in order to derive a marginalized posterior on the pressure as a function of mass density, as seen in Fig.
+Important recent work by the LIGO Collaboration~\cite{LIGO:posterior,Carney:2018sdv} sampled the EoS parameter space in order to derive a marginalized posterior on the pressure as a function of mass density, as seen in Fig.
 2 of~\cite{LIGO:posterior}.
-The spectral coefficients were sampled within the ranges: $\gamma_0 \in \lbrack 0.2,2 \rbrack$, $\gamma_1 \in \lbrack -1.6,1.7 \rbrack$, $\gamma_2 \in \lbrack -0.6,0.6 \rbrack$, $\gamma_0 \in \lbrack -0.02,0.02 \rbrack$, and further restricted the adiabatic index to be $\Gamma \in \lbrack 0.6,4.5 \rbrack$, ensuring the parameterization exposed a wide range of viable EoSs~\cite{Lindblom:parameters}.
+The spectral coefficients were sampled within the ranges: $\gamma_0 \in \lbrack 0.2,2 \rbrack$, $\gamma_1 \in \lbrack -1.6,1.7 \rbrack$, $\gamma_2 \in \lbrack -0.6,0.6 \rbrack$, $\gamma_3 \in \lbrack -0.02,0.02 \rbrack$, and further restricted the adiabatic index to be $\Gamma \in \lbrack 0.6,4.5 \rbrack$, ensuring the parameterization exposed a wide range of viable EoSs~\cite{Lindblom:parameters}.
 Additional constraints imposed upon the generated EoSs were as follows~\cite{LIGO:posterior}: (i) causality within 10\%, and (ii) EoS priors must support NS masses up to $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations~\cite{Zhao:massiveNS}.
 We utilize a random set of 100 of the above posterior samples defined by GW170817, furthermore referenced as the ``constrained EoSs", as shown in Fig.~\ref{fig:eos}.
-Following~\cite{Read2009}, the parameterized high-density core EoSs generated above are matched to the low-density crust EoS Sly~\cite{Douchin:2001sv} at about half of the nuclear saturation density, $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$.
 For comparison, we also include a second sample of 100 ``unconstrained" EoSs, randomly sampled in the pressure-density plane to be unrestricted by GW170817s posterior.
-
-In addition, we investigate 10 transitional quark-hadron matter stars, which undergo first-order phase transitions at pressure $P_{\text{tr}}$, where the hadronic branch departs into a quark-matter branch at a given mass transition~\cite{Paschalidis2018,Alford:2017qgh,1971SvA....15..347S,Zdunik:2012dj,Alford:2013aca}.
+Following~\cite{Read2009}, the parameterized high-density core EoSs generated above are matched to the low-density crust EoS of Sly~\cite{Douchin:2001sv} at about half of the nuclear saturation density, $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$.
+
+In addition, we investigate 10 transitional quark-hadron matter stars, which undergo first-order phase transitions at pressure $P_{\text{tr}}$, where the hadronic branch departs into a quark-matter branch at a given transitional mass~\cite{Paschalidis2018,Alford:2017qgh,1971SvA....15..347S,Zdunik:2012dj,Alford:2013aca}.
 In particular, we focus on the ACS and ACB models described in Ref.~\cite{Paschalidis2018}, shown in Fig.~\ref{fig:hybridML}.
@@
 Additionally, 100 unconstrained EoSs were generated by randomly sampling spectral coefficients of physically valid EoSs, with no further constraints applied.
-The following restrictions were also applied to both sets of EoSs: (i) the EoS must have a causal structure within 10\%, and (ii) the EoS must support maximum NS mass of at least $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations.
+The following restrictions were also applied to both sets of EoSs: (i) each EoS must have a causal structure within 10\%, and (ii) each EoS must support a maximum NS mass of at least $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations.
 Finally, the high density core EoSs generated above were stitched to the low-density crust EoS of SLy~\cite{Douchin:2001sv} at $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$.}
@@
 Observe the transitional points where the NS transitions from the hadronic branch into a quark-matter branch.
-As described in the text, HS/HS and NS/NS binaries have individual masses chosen such that both stars are contained within one branch -- resulting in high $q$ values.
-Constrastingly, HS/NS binaries have individual masses chosen from each branch resulting in small $q$-values.
 }
@@
 However, the waveform templates can be strategically reparameterized to instead include independent linear combinations of $\Lambda_1$ and $\Lambda_2$ to mitigate correlations between them. 
-Any set of two independent functions may be used, for example: tidal parameters $\tilde{\Lambda}=\tilde{\Lambda}(\Lambda_1,\Lambda_2)$ and $\delta \tilde{\Lambda}=\delta \tilde{\Lambda}(\Lambda_1,\Lambda_2)$~\cite{Wade:tidalCorrections} first enter the gravitational waveform at 5PN and 6PN orders respectively, thus partially breaking degeneracies.
+Any set of two independent functions may be used, for example: tidal parameters $\tilde{\Lambda}=\tilde{\Lambda}(\Lambda_1,\Lambda_2)$ and $\delta \tilde{\Lambda}=\delta \tilde{\Lambda}(\Lambda_1,\Lambda_2)$~\cite{Wade:tidalCorrections} first enter the gravitational waveform at 5pN and 6pN orders respectively, thus partially breaking degeneracies.
 Here, $\tilde{\Lambda}$ is known as the mass weighted tidal deformability and is the dominant tidal parameter in the waveform.
 
-\subsection{EoS insensitive relations}\label{sec:eosInsensitive}
+\subsection{EoS-insensitive relations}\label{sec:eosInsensitive}
 Current gravitational wave interferometry is not yet sensitive enough to accurately extract both tidal parameters $\tilde{\Lambda}$ and $\delta\tilde{\Lambda}$.
@@
 These ``binary Love relations" allow one to break degeneracies between coupled tidal parameters.
-This is important for two reasons: (i) they allow one to algebraically eliminate tidal parameters from the template parameter list, improving overall parameter estimation, and (ii) they allow the automatic measurement of a second tidal parameter given observation of the first.
-It was shown through a simple Fisher analysis that the use of binary Love relations improved parameter extraction on $\tilde{\Lambda}$ by up to an order of magnitude.
+This is important for two reasons: (i) they allow one to algebraically eliminate tidal parameters from the template parameter list, improving overall parameter estimation; and (ii) they allow the automatic measurement of a second tidal parameter given observation of the first.
+It was shown through a simple Fisher analysis that the use of the binary Love relations improved the parameter extraction of $\tilde{\Lambda}$ by up to an order of magnitude.
 
 Similar EoS-insensitive relations have been found to exist between individual NS observables: moment of inertia (I), tidal deformability (Love), quadrupole moment (Q), and compactness (C), known as the ``I-Love-Q" and ``C-Love" relations~\cite{Yagi:ILQ, Yagi:binLove}.
-These have been found to be EoS insensitive by up to 1\% and 6.5\% respectively.
-In this paper, we show improvement in all of these relations by restricting to EoSs sampled from GW170817s posterior on pressure as a function of density.
-%%%%%%%%%%%%%%%%%%%%%%%%% Begin universal relations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+These have been found to be EoS-insensitive by up to 1\% and 6.5\% respectively.
+In this paper, we show an improvement in all of these relations by restricting to EoSs sampled from GW170817s posterior on pressure as a function of density.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% UNIVERSAL RELATIONS %%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{EoS-insensitive relations}\label{sec:universal}
-In this section, we follow the analyses performed in~\cite{Yagi:binLove,Yagi:ILQ} with two new sets of 100 spectrally generated EoS: (i) posterior samples randomly selected from GW170817s 90\% posterior on on pressure as a function of density as shown by the solid green curves in Fig.~\ref{fig:eos}, and (ii) those unconstrained by any prior EoS information, as shown by the dotted maroon curves in Fig.~\ref{fig:eos}.
+In this section, we follow the analyses performed in Refs.~\cite{Yagi:binLove,Yagi:ILQ} with two new sets of 100 spectrally generated EoS: (i) posterior samples randomly selected from GW170817s 90\% posterior on the pressure as a function of density as shown by the solid green curves in Fig.~\ref{fig:eos}; and (ii) those unconstrained by any prior EoS information, as shown by the dotted maroon curves in Fig.~\ref{fig:eos}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% I-LOVE-Q RELATIONS %%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \subsection{I-Love-Q relations}\label{sec:ilq}
-Here we present our results on I-Love-Q universality as compared to Fig. 1 of Ref.~\cite{Yagi:ILQ}.
+Here we present our results on the I-Love-Q universality as compared to Fig. 1 of Ref.~\cite{Yagi:ILQ}.
 In particular, we consider two distinct classes of NSs: nuclear matter EoSs and hybrid quark-hadron star EoSs as described in Sec.~\ref{sec:theory}.
 We begin in Sec.~\ref{sec:ilq-nuc} by fitting the new I-Love-Q relations using the constrained set of EoSs.
-This is followed in Sec.~\ref{sec:ilq-hyb} by an analysis and discussion into how well hybrid stars agree with the improved binary Love relations.
+This is followed in Sec.~\ref{sec:ilq-hyb} by an analysis and discussion into how well the hybrid star EoSs agree with the improved binary Love relations.
 
@@
 The new fitting coefficients are presented in Table~\ref{tab:ILQfitNew}.
-While the two above curves both result in fits with similar $R^2$ values (Coefficient of determination, defined as $R^2=\sum_i(f_i-\bar{y})^2/\sum_i(y_i-\bar{y})^2$, where $\bar{y}$ is the mean data value, and $f_i$, $y_i$ are the modeled and actual data values) of $\sim 0.9999995$ for the data presented, the latter has the advantage that it properly limits to the Newtonian case as $\Lambda \rightarrow \infty$~\cite{Yagi:binLove}.
+While the two above curves both result in fits with similar $R^2$ values\footnote{$R^2$ is the coefficient of determination, defined as $\sum_i(f_i-\bar{y})^2/\sum_i(y_i-\bar{y})^2$, where $\bar{y}$ is the mean data value, and $f_i$, $y_i$ are the modeled and actual data values} of $\sim 0.999995$ for the data presented, the latter has the advantage that it properly limits to the Newtonian case as $\Lambda \rightarrow \infty$~\cite{Yagi:binLove}.
 
@@
 
-Figure~\ref{fig:ILQ} shows the improved I-Love relations between the dimensionless moment of inertia $\bar{I} \equiv I/M^3$, the dimensionless quadrupole moment $\bar{Q} \equiv Q/M^3$, and the dimensionless tidal deformability $\Lambda$ for both the constrained and unconstrained sets of EoSs.
+Figure~\ref{fig:ILQ} shows the improved I-Love-Q relations between the dimensionless moment of inertia $\bar{I} \equiv I/M^3$, the dimensionless quadrupole moment $\bar{Q} \equiv Q/M^3$, and the dimensionless tidal deformability $\Lambda$ for both the constrained and unconstrained sets of EoSs.
 Here, each category of EoS are fit individually using the curve found in Eq.~\ref{eq:ILQfitNew}.
 We observe that the constrained EoSs show considerable improvement from the unconstrained EoSs.
-Additionally, we note a large improvement from the results of previous works~\cite{Yagi:ILQ}, validated in Tab.~\ref{tab:maxVar}, where the maximal EoS variation from each fit is tabulated; comparing the results of previous works to the unconstrained and constrained sets of EoSs.
+Additionally, we note a large improvement from the results of previous works~\cite{Yagi:ILQ}.
+This is validated in Tab.~\ref{tab:maxVar}, where the maximal EoS variation from each fit is tabulated; comparing the results of previous works to the unconstrained and constrained sets of EoSs.
 Observe how the constrained EoSs outperform both other cases by a considerable amount for each I-Love-Q relation.
@@
 \caption{
-Individual I-Love relations $\bar{I}-\Lambda$ (left), $\bar{Q}-\Lambda$ (center), and $\bar{I}-\bar{Q}$ (right), shown for both the constrained EoSs (solid green) and unconstrained EoSs (dotted maroon).
-In these figures, the black dashed lines corresponds to the fits given by Eq.~\ref{eq:ILQfitNew} (note: each panel contains individual fits for the constrained and unconstrained EoSs, indistinguishable on such a large scale).
+Individual I-Love-Q relations $\bar{I}-\Lambda$ (left), $\bar{Q}-\Lambda$ (center), and $\bar{I}-\bar{Q}$ (right), shown for both the constrained EoSs (solid green) and unconstrained EoSs (dotted maroon).
+In these figures, the black dashed lines corresponds to the fits given by Eq.~\ref{eq:ILQfitNew}.
 Observe how the fractional difference from the fits, shown in the bottom panels, is greatly suppressed for the constrained case, compared to both the unconstrained case, and results from previous works~\cite{Yagi:ILQ}.
@@
 These results indicate that EoS-insensitive relations can indeed be greatly improved upon by restricting to EoSs in agreeance with physical observations.
-In addition, we confirm the validity of this method by noting that the unconstrained EoSs observe more EoS variability than that found in Ref.~\cite{Yagi:ILQ} due to the nature of large random sampling taking into account more sources of uncertainty than previously studied.
+In addition, we confirm the validity of this method by noting that the unconstrained EoSs observe more EoS variability than that found in Ref.~\cite{Yagi:ILQ} due to the nature of large random sampling taking into account more sources of uncertainty than was previously studied.
 On the other hand, the constrained set of EoSs show significant improvement from that found in previous works.
@@
 \begin{enumerate}
-\item Complete set of 100 constrained EoSs combined with the 10 hybrid star EoSs,
-\item Complete set of 100 constrained EoSs alone,
-\item Complete set of 10 hybrid star EoSs alone.
+\item the complete set of 100 constrained EoSs combined with the 10 hybrid star EoSs,
+\item the complete set of 100 constrained EoSs alone,
+\item the complete set of 10 hybrid star EoSs alone.
 \end{enumerate}
@@
 The fractional differences for the second case (fit to only the constrained EoSs) is shown by the dashed green lines in Fig.~\ref{fig:ILQ} for example.
-To compare the three different fits, Tab.~\ref{tab:hybridCompare} displays the maximal EoS variation in the $I-\Lambda$ relation for both the constrained and hybrid star EoSs in each case.
+For comparison purposes, Tab.~\ref{tab:hybridCompare} displays the maximal EoS variation in the $I-\Lambda$ relation for both the constrained and hybrid star EoSs in each case.
 
@@
 Observe how the hybrid star EoSs obey the I-Love-Q relations in each case by up to $\sim1.7$\%, slightly higher than that found for nuclear matter EoSs in previous works~\cite{Yagi:ILQ}.
-Further, we observe that the universality can not be improved by much through the introduction of new fits, only bringing the max EoS variation down to $\sim1$\% for the fits constructed with only hybrid star EoSs.
-Concluding, we claim that hybrid star EoSs \emph{do} obey the I-Love-Q relations computed through nuclear EoS data, with a decrease in universality to $\sim1.7$\%.
+Further, we observe that the universality can not be improved by much through the introduction of new fits, only bringing the maximal EoS variation down to $\sim1$\% for the fits constructed with only hybrid star EoSs.
+Concluding, we claim that hybrid star EoSs \emph{do} obey the traditional nuclear I-Love-Q relations computed through nuclear EoS data, with a slight decrease in universality to $\sim1.7$\%.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% C-LOVE RELATIONS %%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \subsection{C-Love Relations}\label{sec:clove}
-In this section we consider approximately EoS-insensitive C-Love relations between NS compactness $C \equiv M/R$ and unitless tidal deformability $\Lambda$, as discussed by Yagi and Yunes~\cite{Yagi:binLove}.
+In this section we consider approximately EoS-insensitive C-Love relations between the NS compactness $C \equiv M/R$ and the unitless tidal deformability $\Lambda$, as discussed by Yagi and Yunes in ref.~\cite{Yagi:binLove}.
 Additionally in this section, we compute the relationship between the NS radius and tidal deformability from the C-Love relations.
-This allows one to compare the approximate uncertainty on NS radius computed from the C-Love relations for both the constrained and unconstrained sets of EoSs. 
+This allows one to compare the approximate uncertainty on the NS radius computed from the C-Love relations for both the constrained and unconstrained sets of EoSs. 
 Similar to the previous section, we consider two classes of stars in this section: nuclear matter EoSs and hybrid quark-hadron star EoSs.
@@
 
-Figure~\ref{fig:clove} presents the C-Love relations for both the constrained and unconstrained sets of EoSs, along with the relative fractional difference from the fits. 
+Figure~\ref{fig:clove} presents the C-Love relations for both the constrained and unconstrained sets of EoSs, along with the corresponding absolute differences from the fits. 
 Observe how the constrained EoSs show a large suppression in EoS variability compared to the unconstrained EoSs, as well as to that found in previous works~\cite{Yagi:binLove}.
@@
 \caption{
-Similar to Fig.~\ref{fig:ILQ} but for C-Love relations.
+Similar to Fig.~\ref{fig:ILQ} but for the C-Love relations, and the absolute differences (rather than fractional) from the fit.
 In this figure, we similarly construct fits to  Eq.~\ref{eq:ILQfitNew}, properly limiting to the Newtonian case $C \sim \Lambda^{-1/5}$.
-Observe how, as before, the fractional difference from the fits is greatly suppressed for the constrained case, compared to both the unconstrained case, and results from previous works~\cite{Yagi:binLove}.
-The maximal EoS variation from the fits for the unconstrained and constrained sets of EoSs are compared in Tab.~\ref{tab:maxVar}.
-Additionally shown in this figure is the hybrid star C-Love relations along with their fractional difference from the constrained EoS fits (dashed green).
+Observe how, as before, the absolute difference from the fits is greatly suppressed for the constrained case, compared to both the unconstrained case, and results from previous works~\cite{Yagi:binLove}.
+The maximal EoS variation from the fits for the unconstrained and constrained sets of EoSs are compared in Tab.~\ref{tab:maxVar} for both fractional and absolute differences.
+Additionally shown in this figure is the hybrid star C-Love relations along with their absolute differences from the constrained EoS fits (dashed green).
 }
@@
 
-The results for the C-Love and R-Love relations, similar to that found in Sec.~\ref{sec:ilq}, show the considerable improvement found in using constrained EoSs over any unconstrained set.
+The results for the C-Love and R-Love relations, similar to that found in Sec.~\ref{sec:ilq}, shows considerable improvement in using the constrained EoSs over any unconstrained set.
 We also note that the unconstrained EoSs display slightly larger EoS variability than found in Ref.~\cite{Yagi:binLove}, due to the large random sampling as discussed previously in Sec.~\ref{sec:ilq}.
@@
 In this section, we consider the effect of hybrid star EoSs on the C-Love relation.
-Much like Sec.~\ref{sec:ilq-hyb}, we perform 3 separate fits (constrained and hybrid EoSs combined, constrained EoSs only, and hybrid EoSs only) and compare the maximal EoS variation for each class of EoSs.
+Much like Sec.~\ref{sec:ilq-hyb}, we perform 3 separate fits (constrained and hybrid EoSs combined, constrained EoSs only, and hybrid EoSs only) and compare the maximal EoS variation for each set of EoSs.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% BINARY LOVE RELATIONS %%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Binary love relations}\label{sec:binary}
@@
 The updated fit parameters for the constrained set of EoSs can be found in Table~\ref{tab:binLovefit}.
-Notice how, unlike the individual NS I-Love-Q relations, these relations also depend on the ratio of constituent masses in the binary system.
+Notice how, unlike the individual NS I-Love-Q relations, these relations additionally depend on the ratio of constituent masses in the binary system.
+
 \begin{table*}
@@
 The former observation can be explained by the following reasoning: as the masses further separate, there is a limited range of tidal deformabilities $\Lambda_{1,2}$ in the M-L relationships which satisfy the mass ratio constraint.
-From this we suggest the reader take note that as the mass ratio decreases, the allowable paramreter space for the binary Love relations shrinks.
+From this we suggest the reader take note that as the mass ratio decreases, the allowable parameter space for the binary Love relations shrinks.
 The latter observation originates from the EoS generation process: the unconstrained EoSs are randomly generated -- resulting in various EoSs which are both stiffer and softer than those constrained by GW170817.
@@
 \begin{center} 
-\includegraphics[width=\linewidth]{binLoveAbsolute.eps}%{binLove.eps}
+\includegraphics[width=\linewidth]{binLoveAbsolute.eps}
 \end{center}
@@
 Observe how the constrained set of EoSs show a reduction in EoS variation for both the unconstrained set, and from the results shown in Ref.~\cite{Yagi:binLove}.
-The maximal EoS variability (shown as a the fractional difference for comparison purposes) for each case is tabulated and compared in Tab.~\ref{tab:maxVar}.
+The maximal EoS variability (shown as both the fractional and absolute differences) for each case is tabulated and compared in Tab.~\ref{tab:maxVar}.
 Additionally shown are the binary Love relations for the 10 hybrid star EoSs (dashed bright green curves).
@@
 
-Additionally shown in Fig.~\ref{fig:binLove} are the binary Love relations for the 10 hybrid EoSs discussed in previous sections.
+Additionally shown in Fig.~\ref{fig:binLove} are the binary Love relations for the 10 hybrid star EoSs discussed in previous sections.
 As described in Sec.~\ref{sec:theory}, transitional quark-hadron matter stars undergo first-order phase transitions at pressure $P_{\text{tr}}$, where the hadronic branch departs into a quark-matter branch at the corresponding transitional mass $M_{\text{tr}}$.
-These transitions result in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq M_{\text{tr}}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote these as ``HS"), and (ii) low-mass ($M \leq M_{\text{tr}}$) hadronic stars with no internal transition to quark matter (we denote these as ``NS").
+These transitions result in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq M_{\text{tr}}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote these as ``HS"); and (ii) low-mass ($M \leq M_{\text{tr}}$) hadronic stars with no internal transition to quark matter (we denote these as ``NS").
 Contrary to the single-star relations (I-Love-Q, C-Love, and R-Love) where the hybrid stars moderately agree with their nuclear matter counterparts, the binary-star relations show large disagreement, which can be seen in Fig.~\ref{fig:binLove}.
@@
 the difference between tidal deformabilities becomes larger than expected for pure hadronic-matter stars.
-This results in a large deviation in the sums and differences of tidal deformabilities $(\Lambda_1 \pm \Lambda_2)$, disrupting the overall universality and generating the large ``bump" in the binary love relations for hybrid stars\footnote{This discrepancy is not present in the I-Love-Q and C-Love relations due to their singular nature.} seen in Fig~\ref{fig:binLove}.
+This results in large deviations in the sums and differences of tidal deformabilities $(\Lambda_1 \pm \Lambda_2)$, disrupting the overall universality and generating the large ``bump" in the binary love relations for hybrid stars\footnote{This discrepancy is not present in the I-Love-Q and C-Love relations due to their single-star nature.} seen in Fig~\ref{fig:binLove}.
 
@@
 This analysis quickly left the scope of the paper due to the large number of parameters required to control the varying transitional pressures through different EoSs.
-Therefore, we leave this analysis on the hybrid star binary Love relations to be discussed in future works.
-There, we anticipate generating large numbers of hybrid star EoSs with varying transition masses to be taken into account as an additional fitting parameter in a piece-wise fitting function designed to take into account the ``bumps" in the binary Love relations.
-
-\iffalse%%%%%%%%%%%%%%%%%%% COMMENTED OUT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Hybrid quark-hadron stars}\label{sec:binLove-hybrid}
-As described in Sec.~\ref{sec:theory}, transitional quark-hadron matter stars undergo first-order phase transitions at pressure $P_{\text{tr}}$, where the hadronic branch departs into a quark-matter branch at the corresponding transitional mass $M_{\text{tr}}$.
-These transitions result in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq M_{\text{tr}}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote this as ``HS"), and (ii) low-mass ($M \leq M_{\text{tr}}$) hadronic stars with no internal transition to quark matter (we denote this as ``NS").
-We consider 3 classes of binary systems in this analysis:
-\begin{itemize}
-\item HS/NS binary: consists of one massive hybrid star, and one small hadronic neutron star,
-\item NS/NS binary: consists of two small-mass hadronic neutron stars,
-\item HS/HS binary: consists of two massive hybrid stars.
-\end{itemize}
-
-To determine how each of class of binary NS systems obey our improved binary Love relations, we pick a representative set of 10 binary pairs from each class from the ACB5 hybrid EoS, with a transition at $M_{\text{tr}} \approx 1.4 \text{ M}_{\odot}$.
-Binary Love values are computed for each pair, and fractional residuals from the binary Love curve found in Sec.~\ref{sec:binary} are determined and compared to the values from the constrained set of EoSs.
-The results are shown in Fig.~\ref{fig:hybrid}.
-First, we note that the NS/NS combination of stars gives consistent results to that found earlier -- as expected.
-Next, we observe that HS/HS combinations agree moderately with previous relations\footnote{Note that these EoSs do not fit within GW170817s 90\% posterior on EoS - so we expect deviations consistent with the ``unconstrained" set of EoSs, rather than the ``constrained" set.}, while HS/NS combinations disagree significantly.
-This can be explained by the large reduction in tidal deformability proceeding the transition pressure for hybrid stars, as shown in Fig.~\ref{fig:hybrid}.
-When one star lies on the hadronic-matter branch while the other is on the quark-matter branch, 
-the difference between tidal deformabilities becomes larger than expected for pure hadronic-matter stars.
-This results in a large deviation in the NS binary Love relations $\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$, disrupting the overall universality.
-
-\begin{figure}
-\begin{center} 
-\includegraphics[width=\columnwidth]{hybrid.eps}
-\end{center}
-\caption{
-Fractional difference from the improved binary Love relations fit for a representative set of constrained nuclear matter EoSs (gray circles), and 30 selected NS binaries from the ACB5 hybrid EoS.
-In particular, these binary pairs are selected from each of the following categories: (i) binaries with which one massive star has a quark matter core, while the other is pure hadronic matter (i.e.
+Therefore, we leave an analysis on the hybrid star binary Love relations to be discussed in future works.
+There, we anticipate the generation of large numbers of hybrid star EoSs with varying transition masses to be taken into account as an additional fitting parameter in a piece-wise fitting function designed to take into account the ``bumps" seen in the binary Love relations.
+
+%\iffalse%%%%%%%%%%%%%%%%%%% COMMENTED OUT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsubsection{Hybrid quark-hadron stars}\label{sec:binLove-hybrid}
+%As described in Sec.~\ref{sec:theory}, transitional quark-hadron matter stars undergo first-order phase transitions at pressure $P_{\text{tr}}$, where the hadronic branch departs into a quark-matter branch at the corresponding transitional mass $M_{\text{tr}}$.
+%These transitions result in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq M_{\text{tr}}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote this as ``HS"), and (ii) low-mass ($M \leq M_{\text{tr}}$) hadronic stars with no internal transition to quark matter (we denote this as ``NS").
+%We consider 3 classes of binary systems in this analysis:
+%\begin{itemize}
+%\item HS/NS binary: consists of one massive hybrid star, and one small hadronic neutron star,
+%\item NS/NS binary: consists of two small-mass hadronic neutron stars,
+%\item HS/HS binary: consists of two massive hybrid stars.
+%\end{itemize}
+
+%To determine how each of class of binary NS systems obey our improved binary Love relations, we pick a representative set of 10 binary pairs from each class from the ACB5 hybrid EoS, with a transition at $M_{\text{tr}} \approx 1.4 \text{ M}_{\odot}$.
+%Binary Love values are computed for each pair, and fractional residuals from the binary Love curve found in Sec.~\ref{sec:binary} are determined and compared to the values from the constrained set of EoSs.
+%The results are shown in Fig.~\ref{fig:hybrid}.
+%First, we note that the NS/NS combination of stars gives consistent results to that found earlier -- as expected.
+%Next, we observe that HS/HS combinations agree moderately with previous relations\footnote{Note that these EoSs do not fit within GW170817s 90\% posterior on EoS - so we expect deviations consistent with the ``unconstrained" set of EoSs, rather than the ``constrained" set.}, while HS/NS combinations disagree significantly.
+%This can be explained by the large reduction in tidal deformability proceeding the transition pressure for hybrid stars, as shown in Fig.~\ref{fig:hybrid}.
+%When one star lies on the hadronic-matter branch while the other is on the quark-matter branch, 
+%the difference between tidal deformabilities becomes larger than expected for pure hadronic-matter stars.
+%This results in a large deviation in the NS binary Love relations $\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$, disrupting the overall universality.
+
+%\begin{figure}
+%\begin{center} 
+%\includegraphics[width=\columnwidth]{hybrid.eps}
+%\end{center}
+%\caption{
+%Fractional difference from the improved binary Love relations fit for a representative set of constrained nuclear matter EoSs (gray circles), and 30 selected NS binaries from the ACB5 hybrid EoS.
+%In particular, these binary pairs are selected from each of the following categories: (i) binaries with which one massive star has a quark matter core, while the other is pure hadronic matter (i.e.
 small enough mass that the transition point has not yet been reached), denoted HS/NS (green triangles); (ii) binaries with two small-mass hadron stars, denoted NS/NS (red squares); and (iii) binaries with two large-mass stars with quark matter cores, denoted HS/HS (magenta diamonds).
-}
-\label{fig:hybrid}
-\end{figure}
-
-This discrepancy between the hybrid and hadronic matter EoSs can be seen in Fig.~\ref{fig:binLove}, where the binary Love relations for the 10 hybrid star EoSs are shown alongside the constrained and unconstrained nuclear matter EoSs.
-Observe how the residuals from the fit are quite good at low pressures (large $\Lambda_s$) where the the binaries consist of NS/NS combinations, before reaching the transitional pressure where the deviations become increasingly large ($\sim160$\% for $q=0.90$, $\sim37$\% for $q=0.75$, and $\sim6$\% for $q=0.50$) for HS/HS and HS/NS binaries.
-
-To further investigate this phenomena, we consider binary Love fits to the HS or NS branches \emph{individually}.
-It was found that the binary Love relations failed to properly fit to the collection of full hybrid star EoSs, due to the varying transitional masses $M_{\text{tr}}$ across the various EoSs.
-To compensate for these differences, we separate the two branches into the NS (hadronic matter) and HS (hybrid matter) branches.
-We first observe that the NS branches obey the ``hadronic" binary Love relations derived in Sec.~\ref{sec:binary} within the same EoS variability, indicating no further need for additional fits.
-However, the HS branches do not follow the same relations, suggesting the need for a new ``hybrid binary love fit" pertaining to this branch alone.
-We begin by fitting the binary Love curve in Eq.~\ref{eq:binLovefit} to the HS branches, resulting in the fit coefficients tabulated in the bottom row of Tab.~\ref{tab:binLovefit}.
-We note here that the Newtonian limit for this fit is not physical for quark-star matter, which does not reach low enough central densities.
-Attempts were made to remedy this by allowing the polytropic index $n$ to be either $0$ or a free fitting parameter, both of which failed.
-We instead leave the fits as they are, with the disclaimer that they do not properly limit to the Newtonian case.
-The fits are displayed in the top panel of Fig.~\ref{fig:binLove} as dot-dashed blue curves, showing a good relationship with the hybrid star branches used in the analysis.
-We urge caution with the use of these fits, as the limited sample size of 10 EoSs results in a less accurate fit than its nuclear-matter counterpart.
-Similar to the previous section, the fractional difference from the fit for each HS branch is computed, resulting in a maximum EoS variability of $18.49$\% for $q=0.90$.
-This result is strongly consistent with the results found for the nuclear matter fits of Sec.~\ref{sec:binary}.
-
-We conclude this section with the observation that the hybrid star EoSs do \emph{not} conform to the fits performed on nuclear matter EoSs.
-This is not surprising, as the hybrid branch of the EoSs forces inconsistent results between $\Lambda_1$ and $\Lambda_2$ with different masses; an issue not present for the single-star I-Love-Q relations.
-By separating the two branches of the hybrid EoSs, we find a new ``hybrid" branch binary Love fit which gives consistent results to that found for the nuclear matter fits. 
-\fi%%%%%%%%%%%%%%%%%%% COMMENTED OUT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%% Begin Future Observations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%}
+%\label{fig:hybrid}
+%\end{figure}
+
+%This discrepancy between the hybrid and hadronic matter EoSs can be seen in Fig.~\ref{fig:binLove}, where the binary Love relations for the 10 hybrid star EoSs are shown alongside the constrained and unconstrained nuclear matter EoSs.
+%Observe how the residuals from the fit are quite good at low pressures (large $\Lambda_s$) where the the binaries consist of NS/NS combinations, before reaching the transitional pressure where the deviations become increasingly large ($\sim160$\% for $q=0.90$, $\sim37$\% for $q=0.75$, and $\sim6$\% for $q=0.50$) for HS/HS and HS/NS binaries.
+
+%To further investigate this phenomena, we consider binary Love fits to the HS or NS branches \emph{individually}.
+%It was found that the binary Love relations failed to properly fit to the collection of full hybrid star EoSs, due to the varying transitional masses $M_{\text{tr}}$ across the various EoSs.
+%To compensate for these differences, we separate the two branches into the NS (hadronic matter) and HS (hybrid matter) branches.
+%We first observe that the NS branches obey the ``hadronic" binary Love relations derived in Sec.~\ref{sec:binary} within the same EoS variability, indicating no further need for additional fits.
+%However, the HS branches do not follow the same relations, suggesting the need for a new ``hybrid binary love fit" pertaining to this branch alone.
+%We begin by fitting the binary Love curve in Eq.~\ref{eq:binLovefit} to the HS branches, resulting in the fit coefficients tabulated in the bottom row of Tab.~\ref{tab:binLovefit}.
+%We note here that the Newtonian limit for this fit is not physical for quark-star matter, which does not reach low enough central densities.
+%Attempts were made to remedy this by allowing the polytropic index $n$ to be either $0$ or a free fitting parameter, both of which failed.
+%We instead leave the fits as they are, with the disclaimer that they do not properly limit to the Newtonian case.
+%The fits are displayed in the top panel of Fig.~\ref{fig:binLove} as dot-dashed blue curves, showing a good relationship with the hybrid star branches used in the analysis.
+%We urge caution with the use of these fits, as the limited sample size of 10 EoSs results in a less accurate fit than its nuclear-matter counterpart.
+%Similar to the previous section, the fractional difference from the fit for each HS branch is computed, resulting in a maximum EoS variability of $18.49$\% for $q=0.90$.
+%This result is strongly consistent with the results found for the nuclear matter fits of Sec.~\ref{sec:binary}.
+
+%We conclude this section with the observation that the hybrid star EoSs do \emph{not} conform to the fits performed on nuclear matter EoSs.
+%This is not surprising, as the hybrid branch of the EoSs forces inconsistent results between $\Lambda_1$ and $\Lambda_2$ with different masses; an issue not present for the single-star I-Love-Q relations.
+%By separating the two branches of the hybrid EoSs, we find a new ``hybrid" branch binary Love fit which gives consistent results to that found for the nuclear matter fits. 
+%\fi%%%%%%%%%%%%%%%%%%% COMMENTED OUT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% FUTURE OBSERVATIONS %%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Impact on future observations}\label{sec:observations}
 
-We have now shown that binary NS merger observations can help improve EoS-insensitive relations - the question is: is it worth it?
-Current interferometer sensitivities are not yet small enough to accurately constrain $\tilde{\Lambda}$.
-For example, GW170817 was detected by LIGO observing run 2 (``O2")~\cite{aLIGO} and was able to constrain $\tilde{\Lambda}$ to a $90\%$ confidence interval of 325 (or $\sigma_{\tilde{\Lambda}}=198$) centered at $\mu_{\tilde{\Lambda}}=395$.
-This corresponds to statistical uncertainties on the order of $\sim 82\%$, which vastly dominates the error budget compared to the small systematic errors picked up by EoS variation in the EoS-insensitive relations.
+We have now shown that binary NS merger observations can help improve the EoS-insensitive relations - the question is: is it worth it?
+Current interferometer sensitivities are not yet small enough to accurately constrain the dominant tidal parameter $\tilde{\Lambda}$.
+For example, GW170817 was detected by LIGO observing run 2 (``O2")~\cite{aLIGO} and was able to constrain $\tilde{\Lambda}$ to a $90\%$ confidence interval of 325 (or $\sigma_{\tilde{\Lambda}} \approx 198$) centered at $\mu_{\tilde{\Lambda}}=395$.
+This corresponds to statistical uncertainties on the order of $\sim 82\%$, which dominates the error budget compared to the small systematic errors picked up by EoS variation in the EoS-insensitive relations.
 This implies that currently, the use of improved EoS-insensitive relations will only make a negligible difference on the extraction of tidal parameters.
 
-In Sec.~\ref{sec:marginalization}, we first compute the systematic errors introduced by using the improved binary Love relations derived earlier.
-In Sec.~\ref{sec:futureObservations}, we compare the statistical errors on the parameter extraction of tidal parameters to the above-mentioned systematic errors.
+In Sec.~\ref{sec:marginalization}, we first estimate the systematic errors introduced by using the improved binary Love relations derived earlier.
+In Sec.~\ref{sec:futureObservations}, we estimate the statistical errors on the parameter extraction of tidal parameters, and compare them to the above-mentioned systematic errors.
 This is repeated for 5 future detectors, where multiple event detections become important.
@@
 \caption{
-Coefficients to the fits given by Eqs.(~\ref{eq:margFit1})-(\ref{eq:margFit4}) for the relative error on $\Lambda_a$ in the improved binary Love EoS-insensitive relations presented in this paper.
+Coefficients to the fits given by Eqs.~(\ref{eq:margFit1})-(\ref{eq:margFit4}) for the relative error on $\Lambda_a$ in the improved binary Love EoS-insensitive relations presented in this paper.
 }\label{tab:marginalized}
@@
 This means that, for the current ``O2" detector sensitivity, the use of improved binary Love relations will only make a negligible difference on the extraction of $\tilde\Lambda$.
-However, future detectors (for example aLIGO, A\texttt{+}, Voyager, CE, and ET) are planned with large reductions in sensitivity - both decreasing the statistical errors and allowing for a larger binary NS merger detection rate; further reducing the statistical uncertainties.
-In Sec.~\ref{sec:observations}, we analyze this further and discuss when the systematic errors from EoS-insensitive relations become comparable to the statistical errors.
+However, future detectors (for example aLIGO, A\texttt{+}, Voyager, CE, and ET) are planned with large reductions in sensitivity - both decreasing the statistical errors and allowing for larger binary NS merger detection rates; further reducing the statistical uncertainties.
+In Sec.~\ref{sec:futureObservations}, we analyze this further and discuss when the systematic errors from EoS-insensitive relations become comparable to the statistical errors.
 
@@
 \caption{$\lambda_0$ residuals binned in $q$ (top) and $\Lambda_s$ (bottom), highlighting the different error weights across the entire $(q,\Lambda_s)$ parameter space.
-In this figure, the violet circles indicate the standard deviation of each bin in $q$-space ($\Lambda_s$-space), while the black dashed lines represent the best fit given by Eqs.
+In this figure, the violet circles indicate the standard deviation of each bin in $q$-space ($\Lambda_s$-space), while the solid black lines represent the best fit given by Eqs.
 (\ref{eq:margFit3})-(\ref{eq:margFit4}).
@@
 In this section, we estimate the feasibility of utilizing the improved EoS-insensitive relations in future binary NS merger events.
-This estimate is acquired through a simple Fisher analysis~\cite{Finn:Fisher,Cutler:Fisher} which approximates the accuracy with which one can extract best-fit parameters $\theta^a$, given a prior template waveform.
+This estimate is acquired through a simple Fisher analysis~\cite{Finn:Fisher,Cutler:Fisher} which approximates the accuracy with which one can extract the best-fit parameters $\theta^a$, given a prior template waveform.
 For the remainder of the paper, we consider a template parameter vector consisting of:
@@
 \end{equation}
-where $A \equiv \sqrt{\frac{2 \eta}{3 \pi^{1/3}}}$ is a normalized amplitude factor, $\eta \equiv m_1 m_2/M^2$ is the symmetric mass ratio with $m_{1,2}$ and $M$ being the individual and total masses, $\mathcal{M}=M \eta^{3/5}$ is the chirp mass, and $\chi_{s,a}=\frac{1}{2}(\chi_1\pm\chi_2)$ are the symmetric and antisymmetric total spins, where $\chi_{1,2}$ are the NSs individual spins.
+where $\eta \equiv m_1 m_2/M^2$ is the symmetric mass ratio with $m_{1,2}$ and $M$ being the individual and total masses, $\mathcal{M}=M \eta^{3/5}$ is the chirp mass, $A \equiv \frac{\mathcal{M}^{5/6}}{\sqrt{30}\pi^{2/3}D_L}$ is a normalized amplitude factor with $D_L$ being the luminosity distance, and $\chi_{s,a}=\frac{1}{2}(\chi_1\pm\chi_2)$ are the symmetric and antisymmetric total spins, where $\chi_{1,2}$ are the NSs individual spins.
 Following Refs.~\cite{Cutler:Fisher,Berti:Fisher,Poisson:Fisher}, this method relies on the crude assumption of Gaussian prior distributions\footnote{Typically, the more valid assumption is a uniform prior distribution; an improvement made in a more detailed Bayesian analysis.}.
-The resulting posterior distribution is Gaussian with root-mean-square given by:
+The resulting posterior distribution is Gaussian with a root-mean-square given by:
 \begin{equation}
@@
 \end{equation}
-where $h$ is the waveform template, $\sigma_{\theta^a}$ is the parameters' prior root-mean-square estimate, and the inner product is defined by:
+where $h$ is the waveform template, $\sigma_{\theta^a}$ are the parameters' prior root-mean-square estimate, and the inner product is defined by:
 \begin{equation}
@@
 In this analysis, we consider the ``PhenomD" (IMRD) waveform template~\cite{PhenomDI,PhenomDII} modified by two different tidal corrections: the 6PN tidal correction shown in Ref.~\cite{Wade:tidalCorrections} (IMRD + 6PN), and the NRTidal correction shown in Ref.~\cite{Samajdar:NRTidal} (IMRD + NRTidal).
-Comparing the two tidal corrections to the IMRD waveform returns an estimate on the magnitude of waveform mismodeling systematics.
-Lastly, we consider the spectral noise density $S_n^A(f)$ for 6 different interferometer designs: $A \equiv ($O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, CE~\cite{ET}, ET-D~\cite{Ap_Voyager_CE}$)$ in order to compare the statistical errors accrued on parameter extraction using future upgraded detectors.
-
-We begin by authenticating this approach by applying a Fisher analysis (IMRD + 6PN waveform injection) to GW170817, as observed by LIGO with O2 detector sensitivity~\cite{aLIGO}.
+Comparing the two different tidal corrections to the IMRD waveform returns a rough estimate on the magnitude of waveform mismodeling systematics.
+Lastly, we consider the spectral noise densities $S_n^A(f)$ for 6 different interferometer designs: $A \equiv ($O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, CE~\cite{ET}, ET-D~\cite{Ap_Voyager_CE}$)$ in order to compare the statistical errors accrued on parameter extraction using future upgraded LIGO detectors as well as third generation detectors.
+
+We begin by authenticating this approach by applying a Fisher analysis (with an IMRD + 6PN waveform injection) to GW170817, as observed by LIGO with O2 detector sensitivity~\cite{aLIGO}.
 Because only 1 event was detected, we utilize $\tilde\Lambda$ and $\delta\tilde\Lambda$ as the tidal parameters for comparison purposes.
@@
 For reference, Fig.~\ref{fig:singleFisherLt} also displays the estimated $\tilde\Lambda$ extraction efficiency for \emph{one} event on each detector; as these events can not be combined like was done in the case of $\lambda_0$.
-Observe how this figure shows similar results on $\tilde\Lambda$ to that found on $\lambda_0$ for the case of one event - that is, future detectors ET and CE both observe statistical errors on $\tilde\Lambda$ dropping below the systematic binary Love errors for a single event.
-\red{We note that in Figs.~\ref{fig:stackedFisher} and~\ref{fig:singleFisherLt}, the single-event measurement uncertainty is slightly higher for CE than ET despite observing a larger SNR, due to the frequency-dependant detector sensitivities seen in Fig.~\ref{fig:sensitivities}.}
+Observe how this figure shows similar results on $\tilde\Lambda$ to that found on $\lambda_0$ for the case of one event - that is, future third-generation detectors ET and CE both observe statistical errors on $\tilde\Lambda$ (and $\lambda_0$) dropping below the systematic binary Love errors for a single event.
+This result is amplified when multiple events are combined as shown in Fig.~\ref{fig:stackedFisher}, further motivating the need to improve the systematic errors in the binary Love relations for upcoming detectors Voyager, CE and ET.
+We note that in Figs.~\ref{fig:stackedFisher} and~\ref{fig:singleFisherLt}, the single-event measurement uncertainties are slightly larger for CE than for ET despite having a larger SNR.
+This relic originates from the high-frequency dependence of CE and ETs detector sensitivities: due to the 3-detector geometry of ET, it is able to more accurately measure the tidal effects emergent at high frequencies.
+However, when computing the SNRs from $1 \text{ Hz} \leq f \leq 1649 \text{ Hz}$, CE dominates over ET and observes a larger SNR.
+When instead setting the minimum frequency to $f_{\text{min}} \geq 68$ Hz however, the SNR for ET instead dominates that for CE, validating our hypothesis on this effect.
 
@@
 This is repeated for 5 future detector sensitivities: aLIGO, A\texttt{+}, Voyager, CE, and ET.
-Below, $\rho^A_{\text{GW170817}}$ and $\sigma^A_{\text{GW170817}}$ correspond to the approximate SNR and $\sigma_{\lambda_0}$ of GW170817 had it been observed by the future interferometer, and $\sigma^A_N$ corresponds to the overall uncertainty on $\lambda_0$ after $N_A$ detections on interferometer $A$.
-It can be seen here that the statistical errors on $\lambda_0$ become comparable with the systematics (set to be $P_{90}=13.19$) from using improved binary Love relations from Voyager and on, indicating when it may be safe to utilize new EoS-insensitive relations.
+Below, $\rho^A_{\text{GW170817}}$ and $\sigma^A_{\text{GW170817}}$ correspond to the approximate SNR and $\sigma_{\lambda_0}$ of GW170817 had it been observed by future interferometer $A$, and $\sigma^A_N$ corresponds to the overall uncertainty on $\lambda_0$ after $N_A$ detections on interferometer $A$.
+It can be seen here that the statistical errors on $\lambda_0$ become comparable with the systematics (set to be $P_{90}=13.19$) from using improved binary Love relations for future detectors Voyager, ET, and CE, indicating when it will become important to improve the EoS-insensitive relations.
 Note that the approximation for $\sigma^A_N$ under the O2 detector sensitivity is left blank due to the singularity of the detected event.
@@
 Next, we repeat the process upon the injection of the IMRD + NRTidal waveform in order to demonstrate the effect of waveform mismodeling.
-The results are shown in Fig.~\ref{fig:stackedFisher} as blue outlined circles (single detection uncertainties) and the outlined dashed maroon region (combined uncertainties from multiple detections).
+The results are shown in Fig.~\ref{fig:stackedFisher} as maroon outlined circles (single detection uncertainties) and an outlined dashed maroon region (combined uncertainties from multiple detections).
 Observe the noticeable difference between the extraction efficiencies for the two different tidal corrections - highlighting the need for further waveform modeling for future interferometers.
 
-Concluding, we find that the Voyager, ET, and CE detectors all exhibit enough uncertainty reduction that the systematics on $\lambda_0$ introduced from using improved EoS-insensitive relations (found to be $13.19$) no longer become negligible in the error budget.
-This was also shown for the case of $\tilde\Lambda$, only taking into account single observed events, where ET and CE detectors both observe comparable statistical and systematic errors on $\tilde\Lambda$.
+Concluding, we find that the Voyager, ET, and CE detectors all exhibit enough statistical uncertainty reduction that the systematics on $\lambda_0$ and $\tilde\Lambda$ introduced from using improved EoS-insensitive relations (found to be $13.19$ and $12.01$, respectively) no longer become negligible in the error budget.
 This implies that the use and further improvement of EoS-insensitive relations is not only justified, but necessary, for future binary NS merger detections.
 Additionally, we find that the effect of waveform mismodeling is indeed important for future observations as the statistical errors continue to decrease.
-Further, we investigate the dependence of the measurement accuracy on $\tilde\Lambda$ on the binary NS mass ratio $q$ for fixed chirp mass $\mathcal{M}=1.88\text{ M}_{\odot}$ in Appendix~\ref{app:measurement}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%% Begin Discussion %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In Appendix~\ref{app:measurement}, we additionally investigate the dependence of the measurement accuracy on $\tilde\Lambda$ on the binary NS mass ratio $q$ for fixed chirp mass $\mathcal{M}=1.88\text{ M}_{\odot}$.
+
+%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%
+%%%% DISCUSSION %%%%
+%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%
+
 \section{Conclusion and Discussion}\label{sec:conclusion}
@@
 Similarly, we find an increase in C-Love and I-Love-Q universality by factors of $\sim 76$\% and $\sim 50$\%, respectively.
-We also show the relation between the NS radius and its tidal deformability, computed directly from the C-Love relations.
+We also show the relationship between the NS radius and its tidal deformability, computed directly from the C-Love relations.
 We find this relation to display a maximum error of $358.9\text{ m}$ from the fit discussed in Sec.~\ref{sec:clove}.
-Additionally, we find that hybrid quark-hadron star EoSs \emph{do} obey the I-Love-Q and C-Love universality, albeit with slightly higher maximum EoS variabilities as displayed in Tabs.~\ref{tab:hybridCompare} and ~\ref{tab:hybridCompareClove}.
-In addition, we find that binaries consisting of one massive hybrid quark-hadron star, and one small-mass hadron star do not obey the binary Love relations -- explained by the large difference in $\tilde{\Lambda}$ displayed between the constituent stars.
-To improve on this, we construct new ``hybrid matter binary Love relations", applied to only the hybrid branches of the transitional EoSs.
-This results in a maximal EoS variability similar to that found for the nuclear matter fits.
-Further, we analyze the impact of this improvement for future binary NS merger detections, as the current detectors are not yet sensitive enough to accurately constrain $\tilde{\Lambda}$ for the improved EoS-insensitive relations to make a difference.
-We find that future interferometers Voyager, CE, and ET-D all experience statistical uncertainties upon the extraction of $\tilde{\Lambda}$ small enough to become comparable to the systematic errors injected through the use of improved EoS-insensitive relations, as depicted in Fig.~\ref{fig:stackedFisher} and Table~\ref{tab:variances}.
+Additionally, we find that hybrid quark-hadron star EoSs \emph{do} obey the I-Love-Q and C-Love relations, albeit with slightly higher maximum EoS variabilities as displayed in Tabs.~\ref{tab:hybridCompare} and ~\ref{tab:hybridCompareClove}.
+We additionally find that binaries consisting of one massive hybrid quark-hadron star, and one small-mass hadron star do not obey the binary Love relations -- explained by the large difference in $\tilde{\Lambda}$ displayed between the constituent stars.
+From this we state that the hybrid star EoSs do \emph{not} obey the binary Love relations.
+Future work currently in progress will attempt to remedy this through a series of new piecewise hybrid star binary Love relations.
+
+In the second half of this paper, we analyze the impact of this improvement for future binary NS merger detections.
+Currently detectors are not yet sensitive enough to accurately constrain $\tilde{\Lambda}$ for the improved EoS-insensitive relations to make a difference.
+We find that future interferometers Voyager, CE, and ET-D all experience a reduction in the statistical uncertainties upon the extraction of $\tilde{\Lambda}$ enough to become comparable to the systematic errors injected through the use of improved EoS-insensitive relations, as depicted in Fig.~\ref{fig:stackedFisher} and Table~\ref{tab:variances}.
 Additionally, we considered the effect of waveform mismodeling by comparing Fisher analyses using two different tidal corrections to the PhenomD waveform: 6PN and NRTidal.
@@
 
-Future work on this subject entails an investigation into the improvement of alternative EoS insensitive relations, such as the multipole Love relations between various $l$-th order electric, magnetic, and shape tidal deformabilities as discussed in Ref.~\cite{Yagi:Multipole}.
+Future work on this subject entails an investigation into the improvement of alternative EoS-insensitive relations, such as the multipole Love relations between various $l$-th order electric, magnetic, and shape tidal deformabilities as discussed in Ref.~\cite{Yagi:Multipole}.
 Additionally, Lackey \emph{et al}. presented surrogate models of non-spinning effective-one-body waveform models with the the use of universal relations in Refs.~\cite{Lackey:Surrogate, Lackey:EOB}.
 By reducing the number of required waveform model parameters, surrogate models aid in the extraction of NS observables from GW detections.
-The improvement in the multipole love relations can then be used to increase the accuracy of surrogate models.
+The improvement in the multipole love relations can then be used to increase the accuracy of such surrogate models.
 Additionally, we plan on a more comprehensive analysis into the intricacies of new hybrid star binary Love relations, as discussed in Sec.~\ref{sec:binary}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%% Begin Acknowledgements %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Work along this direction is currently in progress.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% ACKNOWLEDGEMENTS %%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section*{Acknowledgments}\label{acknowledgments}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%% Begin Appendix A: Stacked events process %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% APPENDIX A: STACKED EVENTS PROCESS %%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \appendix
+
 \section{Computation of statistical uncertainties}\label{app:stackingProcedure}
@@
 This is accomplished with a simple Fisher analysis described in Sec.~\ref{sec:futureObservations}, where we first consider single-events identical to GW170817 as if they were detected on future detectors $A \equiv ($ O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, ET~\cite{ET}, CE~\cite{Ap_Voyager_CE}$)$.
-We conclude by simulating a population of $N_A$ events for each interferometer, approximating the number of events detected on detector $A$ over an observing period of one year.
+We conclude by simulating a population of $N_A$ events for each interferometer, approximating the number of events detected on interferometer $A$ over an observing period of one year.
 This is used to combine the statistical uncertainties, resulting in an approximation on the overall measurement accuracy of $\lambda_0$, which is compared to the systematic errors computed in Sec.~\ref{sec:marginalization}.
@@
 \item[(i)] Perform a Fisher analysis as outlined in Sec.~\ref{sec:futureObservations} using detector sensitivity $S_n^A(f)$, while restricting the luminosity distance $D_L$ such that an SNR of $\rho^{\text{O2}}_{\text{GW170817}}=32.4$ would be achieved on O2 sensitivity $S_n^{\text{O2}}(f)$.
-Here we assume low spin priors $|\chi| \leq 0.05$, as well as $0 \leq \lambda_0 \leq 3207$ and $-4490 \leq \lambda_1 \leq 0$~\cite{delPozzo:TaylorTidal} (These are converted from their corresponding dimensional forms).
-This results in a SNR $\rho^A_{\text{GW170817}}$ and a single-event statistical error $\sigma_\text{GW170817}^A$ accrued in the extraction of $\lambda_0$ on detector $A$.
+Here we assume low spin priors $|\chi_{1,2}| \leq 0.05$, as well as $0 \leq \lambda_0 \leq 3207$ and $-4490 \leq \lambda_1 \leq 0$~\cite{delPozzo:TaylorTidal} (these are converted from their corresponding dimensional forms).
+This results in an SNR $\rho^A_{\text{GW170817}}$ and a single-event statistical error $\sigma_\text{GW170817}^A$ accrued in the extraction of $\lambda_0$ on detector $A$.
 
@@
 with a network SNR threshold of $\rho_{\text{th}}=8$.
-The number of events $N_A$ is calculated by taking into account the BNS merger rate history throughout all redshift values within detector As' horizon distance $z_h$, as shown by Eq.
+The number of events $N_A$ is calculated by taking into account the BNS merger rate history throughout all redshift values within detector As' horizon redshift $z_h$, as shown by Eq.
 (10) of Ref.~\cite{Cutler:BNSmerger}:
@@
 where $H_0 = 70 \text{km s}^{-1}\text{Mpc}^{-1}$ is the local Hubble constant, and $\Omega_{\Lambda}=0.67$ is the universe's vacuum energy density.
-Here we choose an observing period $\Delta \tau_0 = 1$ year, and calculate the detection rate for the upper, central, and lower limits of the local binary NS coalescence rate density $\mathcal{R}=1540^{+3200}_{-1220} \text{ Gpc}^{-3}\text{yr}^{-1}$~\cite{Abbott2017}, giving the rates $N_A$ shown in the second column of Table~\ref{tab:variances}, as well as the turquoise shaded region in Fig.~\ref{fig:stackedFisher}.
+Here we choose an observing period of $\Delta \tau_0 = 1$ year, and calculate the detection rate for the upper, central, and lower limits of the local binary NS coalescence rate density $\mathcal{R}=1540^{+3200}_{-1220} \text{ Gpc}^{-3}\text{yr}^{-1}$~\cite{Abbott2017}, giving the rates $N_A$ shown in the second column of Table~\ref{tab:variances}.
 
@@
 \end{equation}
-where $\rho_i^A$ is the SNR of simulated event $i$ computed from Eq.~\ref{eq:population}, and $\rho_{\text{GW170817}}^A$ and $\sigma_{\text{GW170817}}^A$ are the known SNR and uncertainties of the GW170817 event from step (i).
+where $\rho_i^A$ is the SNR of simulated event $i$ computed from Eq.~\ref{eq:population}, and $\rho_{\text{GW170817}}^A$ and $\sigma_{\text{GW170817}}^A$ are the known SNRs and uncertainties of the GW170817 event from step (i).
+This results in the combined statistical errors for the lower, central, and upper limits of the local binary NS coalescence rate density $\mathcal{R}$, depicted by the cyan shaded region in Fig.~\ref{fig:stackedFisher}.
 \end{enumerate}
 
-%%%%%%%%%%%%%%%%%%%%%%%%% Begin Appendix A: measurement accuracy as a functino of q %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% APPENDIX B: MEASUREMENT ACCURACY AS A FUNCTION OF Q %%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Measurement accuracy as a function of binary mass ratio}\label{app:measurement}
+
 In this appendix, we discuss the effects of the binary NS mass ratio $q$ on the measurement accuracy of $\tilde\Lambda$ for various interferometers. 
 The top panel of Fig.~\ref{fig:massVariation} displays an approximation of the $\tilde\Lambda$ measurement accuracy as a function of increasing mass ratio $q$ (for a fixed chirp mass of $\mathcal{M}=1.188 \text{ M}_{\odot}$ corresponding to GW170817), using the Fisher analysis techniques described in Sec.~\ref{sec:observations}.
-We observe two points of interest about these trends: (i) the second generation detectors (O2, aLIGO, A\texttt{+}, and Voyager) typically become less accurate as the mass ratio approaches unity, and (ii) the third generation detectors (CE and ET) observe the opposite behavior-- a fast growth in accuracy as the mass ratio increases.
+We observe two points of interest about these trends: (i) the second generation detectors (O2, aLIGO, A\texttt{+}, and Voyager) typically become less accurate as the mass ratio approaches unity; and (ii) the third generation detectors (CE and ET) observe the opposite behavior-- a fast growth in accuracy as the mass ratio increases.
 For the remainder of this appendix, we attempt to explain the opposing behaviors of the second and third generation interferometers on the extraction of $\tilde\Lambda$.
@@
 Observe how the top panel shows strong disagreement between second and third generation detectors, while the bottom panel shows identical behavior.
-This indicates that parameter correlations between $\tilde\Lambda$ and higher PN order parameter $\delta\tilde\Lambda$ is the culprit in such a disagreement.
+This indicates that parameter correlations between $\tilde\Lambda$ and higher PN order parameter $\delta\tilde\Lambda$ are the culprit in such a disagreement.
 }
@@
 
-We begin by considering the correlations between individual template parameters and $\tilde\Lambda$, given in Eq.~\ref{eq:template}.
+We begin by considering the correlations between individual template parameters $\theta^a$ and $\tilde\Lambda$, given in Eq.~\ref{eq:template}.
 A simple approximation for the amplitude of these correlations can be performed by assuming that all of the other correlations are non-existing.
@@
 This figure, showing only the relative differences between correlations of different parameters $\theta^a$ and $\tilde\Lambda$, reveals a few things.
-First, the coalescence time $t_c$ is highly correlated with $\tilde\Lambda$ equally for each interferometer, an unsurprising fact due to the high 4PN order at which the parameter enters the waveform.
-Secondly, correlations with 6PN tidal parameter $\delta\tilde\Lambda$ shows high correlations with $\tilde\Lambda$ for only the third generation detectors.
-This can be explained by the high PN order at which $\delta\tilde\Lambda$ enters the waveform, an effect that only the most sensitive of detectors can probe.
+First, the coalescence time $t_c$ is highly correlated with $\tilde\Lambda$ equally for each interferometer, an unsurprising fact due to the high 4pN order at which the parameter enters the waveform.
+Secondly, correlations with 6pN tidal parameter $\delta\tilde\Lambda$ shows high correlations with $\tilde\Lambda$ for only the third generation detectors.
+This can be explained by the high pN order at which $\delta\tilde\Lambda$ enters the waveform, an effect that only the most sensitive of detectors can probe.
 
@@
 Following this conclusion on the difference of correlations between tidal parameters $\tilde\Lambda$ and $\delta\tilde\Lambda$ for second and third generation detectors, we attempt to describe the opposing behaviors of measurement accuracy between the two.
-Shown in the center panel of Fig.~\ref{fig:massVariation}, we approximate the measurement accuracy on $\tilde\Lambda$ with the correlations between $\delta\tilde\Lambda$ and $\tilde\Lambda$ removed, through a process similar to that described above.
+Shown in the central panel of Fig.~\ref{fig:massVariation}, we approximate the measurement accuracy on $\tilde\Lambda$ with the correlations between $\delta\tilde\Lambda$ and $\tilde\Lambda$ removed, through a process similar to that described above.
 Notice how the trends between detector generations become more similar -- implying that the correlations between tidal parameters may be the cause of the opposing behaviors.
 This is confirmed by the bottom panel of Fig.~\ref{fig:massVariation} where all parameter correlations have been removed from the Fisher matrix.
-We see that this results in identical behaviors between all 6 representative interferometers, leading us to conclude that the discrepancy between interferometers comes from the degeneracies between different parameters in the gravitational waveform, namely the 6PN tidal parameter $\delta\tilde\Lambda$ which is only detectable by the highly sensitive third generation detectors CE and ET.
-
-%%%%%%%%%%%%%%%%%%%%%%%%% Begin Bibliography  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+We see that this results in identical behaviors between all 6 representative interferometers, leading us to conclude that the discrepancy between the interferometers originates from the degeneracies between different parameters in the gravitational waveform, namely the 6pN tidal parameter $\delta\tilde\Lambda$ which is only detectable by the highly sensitive third generation detectors CE and ET.
+
+%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%
+%%%% BIBLIOGRAPHY %%%%
+%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%
+
 \clearpage

### 2019-02-14 paper/bin-love-after-gw170817.tex
added two references on I-Love-Q relation applicability and NS radius uncertainty from crust EoS, provided by Nico

@@
 Similar EoS-insensitive relations have been found to exist between individual NS observables: moment of inertia (I), tidal deformability (Love), quadrupole moment (Q), and compactness (C), known as the ``I-Love-Q" and ``C-Love" relations~\cite{Yagi:ILQ, Yagi:binLove}.
-These have been found to be EoS-insensitive by up to 1\% and 6.5\% respectively.
-In this paper, we show an improvement in all of these relations by restricting to EoSs sampled from GW170817s posterior on pressure as a function of density.
+These relations, found to be EoS-insensitive by up to 1\% and 6.5\% respectively, have been used for many important applications including deriving constraints on several stellar properties such as the moment of inertia (I), tidal deformability ($\Lambda$), compactness (C), spin ($\chi$), and radius (R)~\cite{Kumar:2019xgp}.
+Analyses such as that done in Ref.~\cite{Kumar:2019xgp} would benefit greatly from the improvement of such EoS-insensitive relations.
+In this paper, we show an improvement on these relations by restricting to EoSs sampled from GW170817s posterior on pressure as a function of density.
 
@@
 On the other hand, the constrained set of EoSs show significant improvement from that found in previous works.
+This improvement can be beneficial to many future analyses, such as improvements to the constraints found on the moment of inertia, tidal deformability, compactness, spin, and radius found in Ref.~\cite{Kumar:2019xgp}.
 
@@
 This indicates that one can reliably measure the NS radius within $\sim 180 \text{ m} -350$ m, using the C-Love relations computed using the constrained set of EoSs.
+The uncertainty quoted here is comparable to the $140\text{ m}$ error found in Ref.~\cite{Gamba:2019kwu}, which investigated the uncertainty owed to the choice of the SLy EoS model for the crust.
+The radius uncertainty for the unconstrained EoSs of $\sim1\text{ km}$ however, would dominate the corresponding error budget on stellar radius compared to the crust errors.
 We further observe a large suppression in the radius measurement accuracy from the unconstrained set of EoSs to the constrained set, tabulated in Tab.~\ref{tab:maxVar} as the maximal EoS measurement uncertainty.
@@
 \begin{equation}
-\lambda \approx \lambda_0 + \lambda_1 (1-\frac{m}{m_0}),
+\Lambda \approx \lambda_0 + \lambda_1 (1-\frac{m}{m_0}),
 \end{equation}
@@
 \caption{
-Square root of of the spectral noise densities $\sqrt{S_n^A(f)}$ plotted for detectors ($A$): LIGO O2 (orange), aLIGO (green), A\texttt{+} (purple), Voyager (magenta), CE (red), and ET-D (blue) as interpolated from publicly available data.
+Square root of of the spectral noise densities $\sqrt{S_n^A(f)}$ plotted for detectors ($A$): LIGO O2, aLIGO, A\texttt{+}, Voyager, CE, and ET-D as interpolated from publicly available data.
 Spectral noise densities are plotted from $f_{\text{min}}=(23,10,10,7,1,1) \text{ Hz}$, respectively, to $f_{\text{max}}=1649 \text{ Hz}$.
@@
 Similarly, we find an increase in C-Love and I-Love-Q universality by factors of $\sim 76$\% and $\sim 50$\%, respectively.
+These improvements on the I-Love-Q and C-Love relations can be very beneficial in many important analyses, including that done in Ref.~\cite{Kumar:2019xgp}, where constraints on the moment of inertia, tidal deformability, compactness, spin, and radius were found using such relations.
 We also show the relationship between the NS radius and its tidal deformability, computed directly from the C-Love relations.
@@
 
-\clearpage
+%\clearpage
 \bibliography{Zack}

### 2019-02-18 paper/bin-love-after-gw170817.tex
cleaned up title and abstract and minor other cleaning up

@@
 
-\title{EoS-insensitive relations after GW170817}
+\title{Equation-of-state insensitive relations after GW170817}
 
@@
 
-\author{Nicol\`as Yunes}
+\author{Nicol\'as Yunes}
 \affiliation{%
- Department of Physics, Montana State University, Bozeman, MT 59717, USA.
+eXtreme Gravity Institute, Department of Physics, Montana State University, Bozeman, MT 59717, USA.
 }%
@@
 % Intro
-The thermodynamic relationship between pressure and density (the equation of state, or EoS) of cold supranuclear matter, accessible in neutron stars, is critical to the study of such stars, and is one of the largest uncertainties in nuclear physics to date.
+The thermodynamic relation between pressure and density (i.e.~the equation of state) of cold supranuclear matter is critical to neutron stars, yet it remains one of the largest uncertainties in nuclear physics.
 % How to probe
-The extraction of tidal deformabilities from the gravitational waveforms of binary neutron star merger events, such as GW170817, is a promising method of probing the nuclear structure.
+The extraction of tidal deformabilities from the gravitational waves emitted in the coalescence of neutron star binaries, such as GW170817, is a promising tool to probe this thermodynamic relation.
 % What was done before - Binary Love
-Previous studies have shown that approximately EoS-insensitive ``binary Love relations" exist between symmetric and antisymmetric combinations of individual tidal deformabilities, which are difficult to be independently measured with second-generation gravitational wave interferometers.
+Equation-of-state insensitive relations between symmetric and antisymmetric combinations of individual tidal deformabilities, the so-called  ``binary Love relations", have proven important to infer the radius of neutron stars, and thus constrain the equation of state, from such gravitational waves.
 % What was done before - I-Love-Q
-Similarly, another set of EoS-insensitive relations exist between individual neutron star parameters: moment of inertia (I), tidal deformability (Love number), quadrupole moment (Q), and compactness (C) - known as the ``I-Love-Q" and ``C-Love" relations.
-% What universal relations do
-Such EoS-insensitive relations allow the elimination of some tidal parameters from the list of model parameters, thus breaking degeneracies and ultimately reducing the parameter extraction uncertainties.
+A similar set of relations between the moment of inertia, the tidal deformability, the quadrupole moment, and the compactness of neutron stars, the so-called ``I-Love-Q" and ``C-Love" relations, allow for future tests of General Relativity in the extreme gravity regime.
 % What we will do
-However, even the most precise of EoS-insensitive relations carry EoS variation uncertainties which inject systematic errors into the parameter extraction process.
-In this document, we explain how one can reduce the equation of state variation for the I-Love-Q, C-Love, and binary Love relations, which helps to reduce the systematic errors on the tidal measurement of binary neutron star mergers.
-However, we show that the systematic effects of these relations are negligible until next-generation detector sensitivities. 
-We achieve this  by restricting to only equations of state drawn from the 90\% posterior constraint on pressure as a function of density, as derived by the LIGO Collaboration.
-% What we found
-We find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with a mass ratio of 0.75, in C-Love universality by a factor of $\sim 67\%$, and in I-Love-Q universality by factors of $\sim 50$\%.
-% Conclude
-We end by comparing the systematic errors on tidal measurements due to the equation of state variation with statistical errors and comment on whether one can safely use these EoS-insensitive relations with future gravitational wave observations.
-We conclude that the systematic errors injected from the use of improved EoS-insensitive relations become comparable to the statistical errors for future detector upgrade Voyager.
+But even the most insensitive of such relations still presents some degree of equation-of-state variability that could introduce systematic error in parameter extraction and in model selection. 
+%
+We here reduce this variability by more than $50\%$ by imposing a prior on the allowed set of equations of state, derived from the posteriors generated from the analysis of GW170817.  
+%
+The resulting increase in insensitivity reduces systematic errors in the extraction of the tidal deformability from future gravitational wave observations, although statistical uncertainties currently dominate the error budget, and will continue to do so until the era of Voyager-class detectors.
 \end{abstract}
@@
 
-\section{Introduction}\label{sec:intro}
-
-{\ny{Just some general comments so that we don't forget:
-\begin{itemize}
-\item The EoS-insensitive relations are called ``binary Love'', ``I-Love-Q'', ``C-Love'' and ``R-Love.'' There is no need to call them ``binary Love EoS-insensitive relations.'' That's too verbose and not what they are called in the literature.
-I am ok with describing these relations as EoS-insensitive instead of approximately universal, but let's not change the names.
-\item There is some serious tidying up that needs to be done to all of the text.
-Specifically, there are missing prepositions, like ``the'', in lots of places that makes the reading a bit choppy and we can improve.
-Zack, when you have a chance, please do a detail read through and fix the flow as much as you can.
-\item Eventually, we need to discuss the abstract and the intro in more detail. 
-\item Let's not forget to check the acknowledgments for funding sources. 
-\item Let's do a spell check. 
-\item Let's remove all commented out text.  
-\end{itemize}
-}}
+\section{Introduction}
+\label{sec:intro}
+
 %Intro
@@
 Estimated statistical uncertainties on the extraction of the tidal deformability at $1.4 \text{ M}_{\odot}$, $\lambda_0$, observed from interferometers $A=$(O2, aLIGO, A\texttt{+}, Voyager, CE, ET-D$)$ as a function of the signal-to-noise-ratio $\rho^{\text{A}}_{\text{GW170817}}$.
-%evaluated from $300 \text{ Hz} \leq f \leq 1649 \text{ Hz}$\footnote{This was done for demonstrative purposes, as computing the SNR with $1 \text{ Hz} \leq f \leq 1649 \text{ Hz}$ resulted in smaller statistical uncertainties for ET than CE, albeit having a smaller SNR - a relic originating from ET being more sensitive to the high frequency tidal effects than CE.}.
 In this figure, the filled blue circles denote the single-event statistical uncertainties $\sigma^A_{\text{GW170817}}$ of GW170817 as if it were observed on detector $A$\footnote{We note that ET more accurately measures single events than CE albeit having a smaller SNR - a relic originating from ET being more sensitive to the high frequency tidal effects than CE.
@@
 
-\subsection{Spectral representations of neutron star equations of state}\label{sec:eos}
+\subsection{Spectral representations of neutron star equations of state}
+\label{sec:eos}
+
 The structure of a NS and its tidal interactions in a binary system rely heavily on the underlying state function (or equation of state - EoS) describing the relationship between the pressure ($p$) and energy density ($\epsilon$) of nuclear matter.
@@
 
-\section{EoS-insensitive relations}\label{sec:universal}
+\section{EoS-insensitive relations}
+\label{sec:universal}
+
 In this section, we follow the analyses performed in Refs.~\cite{Yagi:binLove,Yagi:ILQ} with two new sets of 100 spectrally generated EoS: (i) posterior samples randomly selected from GW170817s 90\% posterior on the pressure as a function of density as shown by the solid green curves in Fig.~\ref{fig:eos}; and (ii) those unconstrained by any prior EoS information, as shown by the dotted maroon curves in Fig.~\ref{fig:eos}.
@@
 
-\subsection{I-Love-Q relations}\label{sec:ilq}
+\subsection{I-Love-Q relations}
+\label{sec:ilq}
+
 Here we present our results on the I-Love-Q universality as compared to Fig. 1 of Ref.~\cite{Yagi:ILQ}.
@@
 
-\subsection{C-Love Relations}\label{sec:clove}
-In this section we consider approximately EoS-insensitive C-Love relations between the NS compactness $C \equiv M/R$ and the unitless tidal deformability $\Lambda$, as discussed by Yagi and Yunes in ref.~\cite{Yagi:binLove}.
+\subsection{C-Love Relations}
+\label{sec:clove}
+
+In this section we consider approximately EoS-insensitive C-Love relations between the NS compactness $C \equiv M/R$ and the unit-less tidal deformability $\Lambda$, as discussed by Yagi and Yunes in ref.~\cite{Yagi:binLove}.
 Additionally in this section, we compute the relationship between the NS radius and tidal deformability from the C-Love relations.
@@
 
-\subsubsection{Nuclear matter stars}\label{sec:clove-nuc}
+\subsubsection{Nuclear matter stars}
+\label{sec:clove-nuc}
+
 Following Ref.~\cite{Yagi:binLove}, we begin by fitting the data for each set of EoSs to the simple curve:
@@
 
-\subsubsection{Hybrid quark-hadron stars}\label{sec:clove-hyb}
+\subsubsection{Hybrid quark-hadron stars}
+\label{sec:clove-hyb}
+
 In this section, we consider the effect of hybrid star EoSs on the C-Love relation.
@@
 
-\subsection{Binary love relations}\label{sec:binary}
+\subsection{Binary love relations}
+\label{sec:binary}
+
 Next we consider improvements to the binary Love relations.
@@
 
-%\iffalse%%%%%%%%%%%%%%%%%%% COMMENTED OUT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsubsection{Hybrid quark-hadron stars}\label{sec:binLove-hybrid}
-%As described in Sec.~\ref{sec:theory}, transitional quark-hadron matter stars undergo first-order phase transitions at pressure $P_{\text{tr}}$, where the hadronic branch departs into a quark-matter branch at the corresponding transitional mass $M_{\text{tr}}$.
-%These transitions result in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq M_{\text{tr}}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote this as ``HS"), and (ii) low-mass ($M \leq M_{\text{tr}}$) hadronic stars with no internal transition to quark matter (we denote this as ``NS").
-%We consider 3 classes of binary systems in this analysis:
-%\begin{itemize}
-%\item HS/NS binary: consists of one massive hybrid star, and one small hadronic neutron star,
-%\item NS/NS binary: consists of two small-mass hadronic neutron stars,
-%\item HS/HS binary: consists of two massive hybrid stars.
-%\end{itemize}
-
-%To determine how each of class of binary NS systems obey our improved binary Love relations, we pick a representative set of 10 binary pairs from each class from the ACB5 hybrid EoS, with a transition at $M_{\text{tr}} \approx 1.4 \text{ M}_{\odot}$.
-%Binary Love values are computed for each pair, and fractional residuals from the binary Love curve found in Sec.~\ref{sec:binary} are determined and compared to the values from the constrained set of EoSs.
-%The results are shown in Fig.~\ref{fig:hybrid}.
-%First, we note that the NS/NS combination of stars gives consistent results to that found earlier -- as expected.
-%Next, we observe that HS/HS combinations agree moderately with previous relations\footnote{Note that these EoSs do not fit within GW170817s 90\% posterior on EoS - so we expect deviations consistent with the ``unconstrained" set of EoSs, rather than the ``constrained" set.}, while HS/NS combinations disagree significantly.
-%This can be explained by the large reduction in tidal deformability proceeding the transition pressure for hybrid stars, as shown in Fig.~\ref{fig:hybrid}.
-%When one star lies on the hadronic-matter branch while the other is on the quark-matter branch, 
-%the difference between tidal deformabilities becomes larger than expected for pure hadronic-matter stars.
-%This results in a large deviation in the NS binary Love relations $\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$, disrupting the overall universality.
-
-%\begin{figure}
-%\begin{center} 
-%\includegraphics[width=\columnwidth]{hybrid.eps}
-%\end{center}
-%\caption{
-%Fractional difference from the improved binary Love relations fit for a representative set of constrained nuclear matter EoSs (gray circles), and 30 selected NS binaries from the ACB5 hybrid EoS.
-%In particular, these binary pairs are selected from each of the following categories: (i) binaries with which one massive star has a quark matter core, while the other is pure hadronic matter (i.e.
-small enough mass that the transition point has not yet been reached), denoted HS/NS (green triangles); (ii) binaries with two small-mass hadron stars, denoted NS/NS (red squares); and (iii) binaries with two large-mass stars with quark matter cores, denoted HS/HS (magenta diamonds).
-%}
-%\label{fig:hybrid}
-%\end{figure}
-
-%This discrepancy between the hybrid and hadronic matter EoSs can be seen in Fig.~\ref{fig:binLove}, where the binary Love relations for the 10 hybrid star EoSs are shown alongside the constrained and unconstrained nuclear matter EoSs.
-%Observe how the residuals from the fit are quite good at low pressures (large $\Lambda_s$) where the the binaries consist of NS/NS combinations, before reaching the transitional pressure where the deviations become increasingly large ($\sim160$\% for $q=0.90$, $\sim37$\% for $q=0.75$, and $\sim6$\% for $q=0.50$) for HS/HS and HS/NS binaries.
-
-%To further investigate this phenomena, we consider binary Love fits to the HS or NS branches \emph{individually}.
-%It was found that the binary Love relations failed to properly fit to the collection of full hybrid star EoSs, due to the varying transitional masses $M_{\text{tr}}$ across the various EoSs.
-%To compensate for these differences, we separate the two branches into the NS (hadronic matter) and HS (hybrid matter) branches.
-%We first observe that the NS branches obey the ``hadronic" binary Love relations derived in Sec.~\ref{sec:binary} within the same EoS variability, indicating no further need for additional fits.
-%However, the HS branches do not follow the same relations, suggesting the need for a new ``hybrid binary love fit" pertaining to this branch alone.
-%We begin by fitting the binary Love curve in Eq.~\ref{eq:binLovefit} to the HS branches, resulting in the fit coefficients tabulated in the bottom row of Tab.~\ref{tab:binLovefit}.
-%We note here that the Newtonian limit for this fit is not physical for quark-star matter, which does not reach low enough central densities.
-%Attempts were made to remedy this by allowing the polytropic index $n$ to be either $0$ or a free fitting parameter, both of which failed.
-%We instead leave the fits as they are, with the disclaimer that they do not properly limit to the Newtonian case.
-%The fits are displayed in the top panel of Fig.~\ref{fig:binLove} as dot-dashed blue curves, showing a good relationship with the hybrid star branches used in the analysis.
-%We urge caution with the use of these fits, as the limited sample size of 10 EoSs results in a less accurate fit than its nuclear-matter counterpart.
-%Similar to the previous section, the fractional difference from the fit for each HS branch is computed, resulting in a maximum EoS variability of $18.49$\% for $q=0.90$.
-%This result is strongly consistent with the results found for the nuclear matter fits of Sec.~\ref{sec:binary}.
-
-%We conclude this section with the observation that the hybrid star EoSs do \emph{not} conform to the fits performed on nuclear matter EoSs.
-%This is not surprising, as the hybrid branch of the EoSs forces inconsistent results between $\Lambda_1$ and $\Lambda_2$ with different masses; an issue not present for the single-star I-Love-Q relations.
-%By separating the two branches of the hybrid EoSs, we find a new ``hybrid" branch binary Love fit which gives consistent results to that found for the nuclear matter fits. 
-%\fi%%%%%%%%%%%%%%%%%%% COMMENTED OUT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\section{Impact on future observations}\label{sec:observations}
+\section{Impact on future observations}
+\label{sec:observations}
 
@@
 
-\section{Conclusion and Discussion}\label{sec:conclusion}
+\section{Conclusion and Discussion}
+\label{sec:conclusion}
+
 The recent GW observation of binary NS merger GW170817 placed constraints on the supranuclear matter EoS for NSs.
@@
 \section*{Acknowledgments}\label{acknowledgments}
-K.Y. would like to acknowledge networking support by the COST Action GWverse CA16104.
+K.Y. acknowledge networking support by the COST Action GWverse CA16104.
+N.Y. acknowledges support from  NSF grant PHY-1759615 and NASA grants NNX16AB98G and 80NSSC17M0041.
 

### 2019-02-18 paper/bin-love-after-gw170817.tex
merge conflict

--- 2019-02-14 paper/bin-love-after-gw170817.tex
@@
 % What universal relations do
-Such EoS-insensitive relations allow the elimination of some tidal parameters from the list of model parameters, thus breaking degeneracies and ultimately reducing the parameter extraction uncertainties.
+Such EoS-insensitive relations allow the elimination of some tidal parameters from the list of model parameters, thus breaking degeneracies and ultimately reducing the parameter extraction uncertainties
 % What we will do

### 2019-02-18 paper/bin-love-after-gw170817.tex

--- 2019-02-18 paper/bin-love-after-gw170817.tex
@@
 % What we will do
-But even the most insensitive of such relations still presents some degree of equation-of-state variability that could introduce systematic error in parameter extraction and in model selection. 
+But even the most insensitive of such relations still presents some degree of equation-of-state variability that could introduce systematic uncertainties in parameter extraction and in model selection.
 %
@@
 %
-The resulting increase in insensitivity reduces systematic errors in the extraction of the tidal deformability from future gravitational wave observations, although statistical uncertainties currently dominate the error budget, and will continue to do so until the era of Voyager-class detectors.
+The resulting increase in insensitivity reduces systematic uncertainties in the extraction of the tidal deformability from future gravitational wave observations, although statistical uncertainties currently dominate the error budget, and will continue to do so until the era of Voyager-class detectors.
 \end{abstract}
@@
 %Intro
-The dependence of pressure on density for cold supranuclear matter found inside neutron stars (NSs) remains to be one of the largest mysteries in both nuclear physics and astrophysics.
-This internal structure of such stars, known as the equation of state (EoS), is exceedingly important, as it is the determining factor for many NS observables - such as the mass and the radius.
-Unfortunately, terrestrial experiments can only study the EoS to around the nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy} (although some temperature-dependent heavy-ion collision experiments may probe higher densities~\cite{Danielewicz:2002pu}), making NSs ideal laboratories for constraining ultra dense nuclear matter.
+The thermodynamic relation between pressure and density in cold, supranuclear matter, the so-called equation of state (EoS), remains an unsolved problem in nuclear physics.
+The EoS is critical to our understanding of neutron stars (NSs) because it determines many NS observables, such as their mass, radius, moment of inertia (I), quadrupole moment (Q) and tidal deformability (or Love number).
+Unfortunately, terrestrial experiments can only probe the EoS to around nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy}.
+Although some temperature-dependent heavy-ion collision experiments are beginning to probe higher densities~\cite{Danielewicz:2002pu}, astrophysical observations of NSs remain ideal for constraining the EoS of cold and ultra dense, nuclear matter.
 
@@
 Independent measurements of NS observables can be used to constrain the nuclear EoS.
-For example, electromagnetic observations of the NS mass-radius relationship have been used to place limits on the EoS~\cite{guver,ozel-baym-guver,steiner-lattimer-brown,Lattimer2014,Ozel:2016oaf}.
-However, these implications potentially suffer from large systematic errors due to various x-ray burst astrophysical mismodeling uncertainties.
-Alternatively, the emission of gravitational waves (GWs) from binary NS merger events have proven to be a unique method of probing nuclear physics.
-During the early inspiral portion of the merger, the orbital separation is large enough that the effect of companion tidal fields is negligible. 
-As the separation decreases through GW emission, tidal forces are magnified and the NSs deform from sphericity, altering the orbital trajectories; a relic which is directly imprinted on the GW signal.
-This deformation is characterized by the \textit{tidal deformability} $\Lambda$ as the linear response of the NSs quadrupole moment $Q_{ij}$ to the neighboring tidal field $\varepsilon_{ij}$~\cite{hinderer-love,Flanagan2008}.
+For example, electromagnetic observations of the mass and radius of certain NSs have been used to place confidence limits in the mass-radius plane, and thus constrain the EoS~\cite{guver,ozel-baym-guver,steiner-lattimer-brown,Lattimer2014,Ozel:2016oaf}.
+These observations, however, may potentially suffer from large systematic errors due to uncertainties in the astrophysical modeling of X-ray bursts.
+The gravitational waves (GWs) emitted in the coalesce of NS binaries may be a cleaner probe of nuclear physics.
+During the early inspiral, the orbital separation is large enough that the tidal fields are negligible; but as the orbital separation decreases due to GW emission, tidal forces grow and the NSs respond by developing deformations controlled by their nuclear EoS.
+These deformations affect the orbital trajectory of the binary, and thus the GWs emitted, encoding in the latter the NS EoS~\cite{hinderer-love,Flanagan2008}.
 
 %reparameterization of the template
-In the case of binary NSs, each star becomes deformed via the process highlighted above, resulting in two highly correlated tidal parameters $\Lambda_1$ and $\Lambda_2$ entering the gravitational waveform~\cite{Flanagan2008,Vines:2011ud}.
-Due to high correlations between between the two parameters, independent extraction becomes very difficult at current interferometer sensitivities~\cite{Wade:tidalCorrections}.
-Typically, these high correlations can be reduced by strategically reparameterizing the waveform template with new tidal parameters constructed from linear combinations of $\Lambda_1$ and $\Lambda_2$.
-For example, utilizing the parameters $\tilde{\Lambda}$ and $\delta \tilde{\Lambda}$~\cite{Favata:2013rwa,Wade:tidalCorrections} which enter the GW waveform at different post-Newtonian (pN) orders\footnote{n-pN order corrections enter the gravitational waveform at powers of the ratio between the orbital speed and the speed of light $v/c^{2n}$.} partially mitigates these correlations.
-Similarly, the waveform may be parameterized by mass-independent tidal parameters $\lambda_0$ and $\lambda_1$, derived through a Taylor expansion about $m_0=1.4 \text{ M}_{\odot}$ of tidal deformability $\Lambda \approx \lambda_0+\lambda_1(1-\frac{m}{m_0})$~\cite{delPozzo:TaylorTidal,Yagi:binLove}.
-Use of this set of tidal parameters allows one to effectively combine multiple events with varying mass and $\tilde\Lambda$ components, not possible in the former parameterization of $\tilde{\Lambda}$ and $\delta \tilde{\Lambda}$
+The gravitational waves emitted by binary neutron stars in the late inspiral must then depend on the \emph{tidal deformabilities} $\Lambda_1$ and $\Lambda_2$, which control the linear response of the star's quadrupole deformation to the (electric-type, quadrupole) tidal field of the companion (to leading order in a post-Newtonian expansion~\cite{Blanchet:2013haa})~\cite{Flanagan2008,Vines:2011ud}.
+These parameters, however, enter the GW Fourier model multiplied by the same function of the GW frequency (at leading post-Newtonian order), making them degenerate, and thus, very difficult to estimate independently with current GW data~\cite{Wade:tidalCorrections}.
+Instead, one can extract certain combinations of the tidal deformabilities, like the so-called \emph{chirp deformability} $\tilde{\Lambda}$~\cite{Favata:2013rwa,Wade:tidalCorrections}, or one can extract the (mass-independent) coefficients $(\lambda_{0},\lambda_{1},\ldots)$ of a Taylor expansion of the tidal deformabilities about some fiducial mass~\cite{delPozzo:TaylorTidal,Yagi:binLove}.
+Current detectors are not sensitive enough to accurately measure any of these coefficients, but future detectors will and the information from multiple events could then be combined, since the Taylor expansion coefficient should be common to all events.
 
 %Universal relations
-Unfortunately, current detectors are not sensitive enough to accurately measure the dominant tidal parameter, $\lambda_0$ (also known as $\Lambda_{1.4}$, the tidal deformability at $1.4 \text{ M}_{\odot}$).
-Previous work by Yagi and Yunes~\cite{Yagi:binLove} resolved this issue by finding approximately EoS-insensitive ``binary Love relations" between symmetric and anti-symmetric combinations of tidal deformabilities $\Lambda_{s,a}=\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$.
-This allows one to further break degeneracies between tidal parameters, resulting in both (i) a decrease in uncertainty upon parameter extraction of $\Lambda_s$ on the removal of parameter $\Lambda_a$ from the model; and (ii) the ability to measure the secondary tidal parameter upon measurement of the first~\cite{Katerina:residuals}.
-Use of these relations leads to up to an order of magnitude improvement in parameter estimation of $\Lambda_s$ through a simple Fisher analysis~\cite{Yagi:binLove}, also confirmed with the detailed analysis seen in Ref.~\cite{Katerina:residuals}.
-Similar ``I-Love-Q" and ``C-Love" relations~\cite{Yagi:ILQ} have been found between individual NS observables: quadrupole moment, moment of inertia, tidal deformability, and compactness; similarly allowing the removal of tidal parameters from the model list, and allowing an automatic determination of one observable through the measurement of another.
-However, these relations have been tuned to a specific collection of EoS models, and each have intrinsic uncertainties associated with their use.
-
-%How we improved this
-In this analysis, we aim to improve this important work by imposing the restrictions found on the EoS~\cite{LIGO:posterior} derived from the recent binary NS merger observation, GW170817~\cite{TheLIGOScientific:2017qsa}.
-By restricting to only EoSs which lie within the the 90\% credible region on pressure as a function of density found in Ref.~\cite{LIGO:posterior}, we repeat the analyses done in Refs.~\cite{Yagi:binLove,Yagi:ILQ} and show an increase in universality for the I-Love-Q, C-Love, and binary Love relations.
-We also investigate the relationship between the NS radius and its tidal deformability, or the R-Love relations, determining whether the NS radius uncertainties can be reduced.
-In addition, we consider hybrid star EoSs seen in Ref.~\cite{Paschalidis2018}, which experience strong first-order transitions from hadronic matter to quark matter in the core.
-These provide a departure from the nuclear matter relations considered here - providing valuable insight into such EoSs.
-Lastly, we estimate the viability of using the improved EoS-insensitive relations on future GW detections by performing simple Fisher analyses to approximate when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in the relations.
-To further estimate the effect of waveform mismodeling, we additionally consider two different tidal corrections to the injected PhenomD~\cite{PhenomDI,PhenomDII} waveform: 6PN~\cite{Wade:tidalCorrections} and NRTidal~\cite{Samajdar:NRTidal}.
+Lacking enough sensitivity in current GW observations, one is forced to only estimate the chirp deformability, but this prevents the independent extraction of $\Lambda_{1}$ and $\Lambda_{2}$.
+Yagi and Yunes~\cite{Yagi:binLove} solved this problem by finding EoS-insensitive relations between the symmetric and anti-symmetric combinations of the tidal deformabilities $\Lambda_{s,a}=\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$, the so-called ``binary Love relations." These relations can be used to analytically express $\Lambda_{s}$ in terms of $\Lambda_{a}$ (or vice-versa), making the chirp deformability a function of only $\Lambda_{a}$.
+A measurement of the chirp deformability then implies a measurement of $\Lambda_{a}$, and through the use of the binary Love relations, also a measurement of $\Lambda_{s}$, which then allows for the inference of the individual tidal deformabilities $\Lambda_{1}$ and $\Lambda_{2}$~\cite{Yagi:binLove}.
+With those at hand, one can further use EoS-insensitive relations between the tidal deformabilities and the compactness, the so-called ``C-Love relations''~\cite{Yagi:ILQ}, to infer the radii of the NSs, and thus, to place two constraints in the mass-radius plane, one for each star in the binary~\cite{Yagi:binLove}.
+This idea was recently implemented in GW170817, allowing for the first EoS-independent constraints on the mass-radius curve using GW data~\cite{LIGO:posterior}.
+
+EoS-insensitive relations can in fact be used for more than just measuring the nuclear EoS.
+For years, the theoretical physics community considered the possibility of using measurements of NS properties, like the mass, the radius and the moment of inertia, to constrain deviations from General Relativity in the strong-field regime.
+Certain modified theories of gravity, like scalar tensor theories with spontaneous scalarization~\cite{Damour:1996ke}, Einstein-Aether and Horava gravity~\cite{Eling:2007xh,Yagi:2013ava,Yagi:2013qpa}, dynamical Chern-Simons gravity~\cite{Yunes:2009ch}, beyond Horndesky theories~\cite{Sakstein:2016oel}, modify such NS observables, but unfortunately, these modifications are typically degenerate with the nuclear EoS.
+Yagi and Yunes solved this problem by finding EoS-insensitive relations between the moment of inertia, the tidal deformability (or Love number) and the quadrupole moment, the so-called ``I-Love-Q'' relations~\cite{Yagi:ILQ}.
+Given a measurement of the Love number for a given NS, for example through GW observations, the I-Love-Q relations can be used to infer the moment of inertia or the quadrupole moment.
+A second independent measurement of either of these two quantities, for example through binary pulsar observations~\cite{Lattimer:2004nj} or observations with the Neutron star Interior Composition ExploreR (NICER)~\cite{Ozel:2015ykl}, then allows an EoS-insensitive test of General Relativity in the strong field regime~\cite{Yagi:ILQ}.
+
+The implementation of the EoS-insensitive relations in data analysis has to somehow contend with the fact that these relations are in fact not exactly universal, but rather present different (albeit small) levels of EoS variability.
+In the case of the binary Love and C-Love relations to infer the radii of NSs with GW170817, the problem is solved by marginalizing over the EoS variability~\cite{Katerina:residuals}.
+Presumably, this same procedure can be applied in the future when carrying out tests of General Relativity with the I-Love-Q relations, using a combination of binary pulsar, NICER and GW data.
+But this marginalization procedure may not always be as important; as constraints in the mass-radius plane become more stringent with future GW observations, the allowed space of EoSs will shrink, which in turn must naturally decrease the degree of EoS variability in all EoS-insensitive relations.
+This is the main focus of this paper.
 
@@
 \subsection{Executive Summary}
-%What we did
-In this paper we attempt to improve the I-Love-Q, C-Love, and binary Love relations by imposing constraints on the EoS found by GW170817~\cite{LIGO:posterior,TheLIGOScientific:2017qsa}.
-First, we generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, where we (i) impose the restriction that they must be drawn from GW170817s 90\% credible posterior in pressure as a function of density; and (ii) don't impose any restrictions for comparison purposes.
-Next, we follow the important works of Refs.~\cite{Yagi:binLove} and~\cite{Yagi:ILQ} to show how the ``constrained" set of EoSs show improved universality (binary Love, I-Love-Q, and C-Love) from both the previous works, and the ``unconstrained" sample, shown by Fig.~\ref{fig:ILQ}.
-In addition, we determine the degree to which hybrid star EoSs obey the various EoS-insensitive relations.
-Finally, through a simple Fisher analysis, we consider the value in improving EoS-insensitive relations by approximating when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in the relations.
-
-%Final Results
-Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with mass ratios of $0.75$, in C-Love universality by a factor of $\sim 67\%$, and in I-Love-Q universality by factors of $\sim50$\%, tabulated in Tab.~\ref{tab:maxVar}.
-We also present the relationship between the NS radius and tidal deformability, computed directly from the C-Love relations, showing maximum EoS variability of $358.9 \text{ km}$ from the fit discussed in Sec.~\ref{sec:clove}.
-Additionally, we find that the hybrid quark-hadron star EoSs do obey the I-Love-Q and C-Love relations, with sightly increased EoS variability.
-We also find that binaries consisting of one massive hybrid star, and one small-mass hadronic star do not agree with the derived binary Love relations, due to the large separation in $\tilde{\Lambda}$ between the constituent stars.
-
-Due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the EoS-insensitive relations are far outweighed by the statistical errors accrued by the extraction of high pN order tidal parameters from GW waveforms.
-Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from the parameter extraction of $\lambda_0$ (the tidal deformability at $1.4 \text{ M}_{\odot}$) for GW170817 as if it had been observed by various detectors $A \equiv ($ O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, ET~\cite{ET}, CE~\cite{Ap_Voyager_CE}$)$.
-Here, $\sigma^A_{\text{GW170817}}$ and $\rho^A_{\text{GW170817}}$ correspond to the statistical error and signal-to-noise-ratio found from observing GW170817 on detector $A$, and $\sigma^A_N$ represents the combined uncertainty after the detection of $N_A$ events (corresponding to the binary NS merger rate associated with interferometer $A$).
-These values are further tabulated in Table~\ref{tab:variances}.
-It can be seen from this figure that the statistical errors from parameter extraction become comparable the EoS-insensitive relation systematics (indicated by the magenta horizontal line) for the Voyager interferometer - indicating when the improved binary Love relations will become necessary.
-Also shown in the figure is the same measurement uncertainties upon the injection of the PhenomD + NRTidal~\cite{PhenomDI,PhenomDII,Samajdar:NRTidal} waveform, rather than the PhenomD + 6PN~\cite{PhenomDI,PhenomDII,Wade:tidalCorrections} tidal correction to demonstrate the effect of waveform mismodeling.
+
+%How we improved this
+We begin by investigating the increase in EoS insensitivity due to the constraints placed by GW170817 on the allowed space of EoSs.
+We take the 90\% credible region constructed from the posterior probability distributions on the pressure-density plane~\cite{LIGO:posterior} obtained from GW170817~\cite{TheLIGOScientific:2017qsa} as a prior on the set of EoSs that is compatible with this observation.
+We then generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, one in which this prior is enforced (the ``constrained'' sample) and another in which the prior is not enforced (the ``unconstrained'' sample).
+We repeat the analysis done by Yagi and Yunes~\cite{Yagi:binLove,Yagi:ILQ} on both sets of EoSs and find that the EoS-insensitive relations present less EoS variability with the constrained set.
+In particular, the EoS-insensitivity increases by a factor of $\sim 60$\% in the binary Love relations (for stars with mass ratio larger than $0.75$), by a factor of $\sim 70\%$ in the C-Love relations, and by factors of $\sim 50$\% in the I-Love-Q relations (see Table~\ref{tab:maxVar} and Fig.~\ref{fig:ILQ} for more details).
+
+With this study at hand, we then carry out additional related studies on EoS-insensitive relations that go beyond the work in~\cite{Yagi:binLove,Yagi:ILQ}.
+First, we investigate the relation between the NS radius and its tidal deformability, the R-Love relations, for both sets of EoSs, because these are critical to place constraints on the radius from a measurement of the Love number.
+We use the C-Love relations to construct the R-Love relations and find that the maximum EoS variability drops from $\sim 880 {\rm{km}}$ in the unconstrained case to $\sim 360 {\rm{km}}$ in the constrained case (see Sec.~\ref{sec:clove} for more details).
+Second, we study the EoS-universality of hybrid stars, which experience strong first-order phase transitions from hadronic to quark matter in the core~\cite{Paschalidis2018}.
+We find that the I-Love-Q and C-Love relations remain EoS-insensitive for these hybrid stars, although the EoS variability increases slightly (see Sec.~\ref{sec:ilq-hyb} and~\ref{sec:clove-hyb} for more details).
+However, we also find that the binary Love relations are not EoS-insensitive for a mixed binary with a (massive) hybrid star and a (low-mass) hadronic star, due to the large separation in chirp deformability between the constituent stars (see Sec.~\ref{sec:binary} for more details).
+
+Last for not least, we study the importance of using the improved EoS-insensitive relations in future GW observations.
+The use of EoS-insensitive relations introduces systematic uncertainties in parameter estimation because of the intrinsic non-zero EoS-variability in these relations, which one must marginalize over.
+These uncertainties are currently irrelevant because statistical uncertainties in parameter estimation are much larger with current detectors.
+But as the detector sensitivity is improved, the signal-to-noise ratio and the number of events that will be detected will increase, therefore decreasing the statistical uncertainties below the systematic one due to EoS variability.
+We carry out a simple Fisher analyses to estimate when the statistical uncertainties become comparable to the systematic uncertainties due to EoS variability and find that this occurs for Voyager-class detectors.
+
+Figure~\ref{fig:stackedFisher} shows this result in more detail.
+We here present the (Fisher-estimated) statistical uncertainty in the measurement of $\lambda_{0}$ with various detectors (O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, ET~\cite{ET}, CE~\cite{Ap_Voyager_CE}) for an event identical to GW170817.
+The x-axis shows the signal-to-noise ratio for a GW170817 event detected with each of these detectors.
+We also present the combined statistical uncertainty $\sigma^A_N$ after $N$ detections with each of these instruments, with the top and bottom of the region representing the most optimistic and pessimistic expectation for the number of detections expected from the binary NS merger rate (see also Table~\ref{tab:variances}).
+These statistical uncertainties should be compared to the systematic uncertainty in $\lambda_{0}$ due to EoS-variability improved with the constrained set.
+Observe that the statistical and the systematic uncertainties cross for Voyager-class detectors.
+s
 
@@
 \end{center}
-\caption{
-Estimated statistical uncertainties on the extraction of the tidal deformability at $1.4 \text{ M}_{\odot}$, $\lambda_0$, observed from interferometers $A=$(O2, aLIGO, A\texttt{+}, Voyager, CE, ET-D$)$ as a function of the signal-to-noise-ratio $\rho^{\text{A}}_{\text{GW170817}}$.
-In this figure, the filled blue circles denote the single-event statistical uncertainties $\sigma^A_{\text{GW170817}}$ of GW170817 as if it were observed on detector $A$\footnote{We note that ET more accurately measures single events than CE albeit having a smaller SNR - a relic originating from ET being more sensitive to the high frequency tidal effects than CE.
-See Sec.~\ref{sec:futureObservations} for a discussion on this.}.
-Also shown by the cyan shaded region is the combined uncertainty $\sigma^A_N$ from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper and lower limits of the expected binary NS merger detection rates for detector $A$ over 1 observation year.
-It can be seen that the statistical errors in the parameter extraction become comparable to the systematics from EoS variation in the improved binary Love relations (indicated by the horizontal indigo dashed line) for the Voyager, CE, and ET detectors.
-These results are further tabulated in Table~\ref{tab:variances}.
-Additionally shown in the figure are the estimated statistical uncertainties on the extraction of $\lambda_0$ upon the injection of the PhenomD + NRTidal correction waveform (IMRD + NRTidal), rather than the PhenomD + 6PN tidal correction (IMRD + 6PN), in order to demonstrate the effect of waveform mismodeling uncertainties.
-The single-detection uncertainties are shown by unfilled maroon circles, while the combined detection uncertainties are outlined by dashed maroon.
-}
+\caption{(Color online) Fisher-estimated statistical uncertainties on the extraction of $\lambda_{0}$ with interferometer (O2, aLIGO, A\texttt{+}, Voyager, CE, ET-D) as a function of the signal-to-noise-ratio expected in each of these instruments, given a single GW170817 detection (circles).
+The statistical uncertainties with ET are lower than with CE in spite of a lower signal-to-noise ratio because the former is more sensitive above 300 Hz, where tidal effects matter the most (see Sec.~\ref{sec:futureObservations} for further discussion).
+We also plot the combined statistical uncertainty given $N$ observations consistent with the NS binary merger rate for a 1 year observation (regions), with the top and bottom edges of the regions corresponding to optimistic and pessimistic merger rates.
+These statistical uncertainties should be compared to the systematic uncertainty on the extraction of $\lambda_{0}$ due to EoS-variability (horizontal dashed line).
+Observe that the statistical and systematic uncertainties cross for Voyager-class detectors.
+We confirm this conclusion by repeating the statistical analysis with two different waveform models (PhenomD~\cite{PhenomDI,PhenomDII} plus NRTidal corrections~\cite{Samajdar:NRTidal} and PhenomD~\cite{PhenomDI,PhenomDII} plus 6PN tidal corrections~\cite{Wade:tidalCorrections}).}
 \label{fig:stackedFisher}
@@
 %outline
-The organization of this paper is outlined below.
+The remainder of this paper presents the details of the results summarized above and it is organized as follows. 
 We begin with complementary background and theory material in Sec.~\ref{sec:theory}.
@@
 We conclude in Sec.~\ref{sec:conclusion} by discussing our results and mentioning avenues of future work.
-Throughout this paper, we have adopted geometric units of $G=c=1$, unless otherwise stated.
+Throughout this paper, we have adopted geometric units of $G=1=c$, unless otherwise stated.
 
@@
 
-\subsubsection{Hybrid quark-hadron stars}\label{sec:ilq-hyb}
+\subsubsection{Hybrid quark-hadron stars}
+\label{sec:ilq-hyb}
+
 In this section, we investigate the I-Love-Q universality of hybrid stars, and their compatibility with their nuclear matter counterparts.
@@
 The uncertainty quoted here is comparable to the $140\text{ m}$ error found in Ref.~\cite{Gamba:2019kwu}, which investigated the uncertainty owed to the choice of the SLy EoS model for the crust.
-The radius uncertainty for the unconstrained EoSs of $\sim1\text{ km}$ however, would dominate the corresponding error budget on stellar radius compared to the crust errors.
+The radius uncertainty for the unconstrained EoSs of $\sim1\text{ km}$ however, would dominate the corresponding error budget on stellar radius compared to the crust uncertainties.
 We further observe a large suppression in the radius measurement accuracy from the unconstrained set of EoSs to the constrained set, tabulated in Tab.~\ref{tab:maxVar} as the maximal EoS measurement uncertainty.
@@
 For example, GW170817 was detected by LIGO observing run 2 (``O2")~\cite{aLIGO} and was able to constrain $\tilde{\Lambda}$ to a $90\%$ confidence interval of 325 (or $\sigma_{\tilde{\Lambda}} \approx 198$) centered at $\mu_{\tilde{\Lambda}}=395$.
-This corresponds to statistical uncertainties on the order of $\sim 82\%$, which dominates the error budget compared to the small systematic errors picked up by EoS variation in the EoS-insensitive relations.
+This corresponds to statistical uncertainties on the order of $\sim 82\%$, which dominates the error budget compared to the small systematic uncertainties picked up by EoS variation in the EoS-insensitive relations.
 This implies that currently, the use of improved EoS-insensitive relations will only make a negligible difference on the extraction of tidal parameters.
 
-In Sec.~\ref{sec:marginalization}, we first estimate the systematic errors introduced by using the improved binary Love relations derived earlier.
-In Sec.~\ref{sec:futureObservations}, we estimate the statistical errors on the parameter extraction of tidal parameters, and compare them to the above-mentioned systematic errors.
+In Sec.~\ref{sec:marginalization}, we first estimate the systematic uncertainties introduced by using the improved binary Love relations derived earlier.
+In Sec.~\ref{sec:futureObservations}, we estimate the statistical uncertainties on the parameter extraction of tidal parameters, and compare them to the above-mentioned systematic uncertainties.
 This is repeated for 5 future detectors, where multiple event detections become important.
@@
 
-\subsection{Error Marginalization}\label{sec:marginalization}
-
-In this section, we investigate the residuals on $\Lambda_a(\Lambda_s,q)$ in order to marginalize over the intrinsic error found in the binary Love EoS-insensitive relations.
+\subsection{Marginalization over Uncertainties}\label{sec:marginalization}
+
+In this section, we investigate the residuals on $\Lambda_a(\Lambda_s,q)$ in order to marginalize over the intrinsic uncertainty found in the binary Love EoS-insensitive relations.
 In particular, we restrict our focus to only the constrained set of EoSs.
 Residuals in $\Lambda_a$ are computed as $\Lambda_a^{\text{relation}}(\Lambda_s,q)-\Lambda_a^{\text{true}}$, where $\Lambda_a^{\text{true}}$ corresponds to the true value predicted by the sample EoSs, and $\Lambda_a^{\text{relation}}(\Lambda_s,q)$ corresponds to the value obtained through the EoS-insensitive relations found in Sec.~\ref{sec:binary}.
-We follow this up by converting the $\Lambda_a$ residuals into $\lambda_0$, allowing us to approximate the overall systematic errors on $\lambda_0$ from using the improved binary Love relations.
+We follow this up by converting the $\Lambda_a$ residuals into $\lambda_0$, allowing us to approximate the overall systematic uncertainties on $\lambda_0$ from using the improved binary Love relations.
 
@@
 
-Now that we have obtained the residuals on $\Lambda_a$, we must convert them into the new tidal parameter $\lambda_0$, in order to compute and easily compare the systematic errors to the statistical errors on $\lambda_0$, found in Sec.~\ref{sec:futureObservations}.
+Now that we have obtained the residuals on $\Lambda_a$, we must convert them into the new tidal parameter $\lambda_0$, in order to compute and easily compare the systematic uncertainties to the statistical uncertainties on $\lambda_0$, found in Sec.~\ref{sec:futureObservations}.
 Figure~\ref{fig:qLsResiduals} shows the standard deviations of these residuals (converted into $\lambda_0$) binned in both $q$ and $\Lambda_s$ as was done above. 
-To estimate the overall systematic errors on $\lambda_0$ accrued upon the use of the improved binary Love relations, we combine the errors in both $q$ and $\Lambda_s$.
+To estimate the overall systematic uncertainties on $\lambda_0$ accrued upon the use of the improved binary Love relations, we combine the uncertainties in both $q$ and $\Lambda_s$.
 Figure~\ref{fig:residuals} displays the un-binned Gaussian distribution of $\lambda_0$ residuals for both the constrained, and unconstrained sets of EoSs for comparison.
@@
 Additionally, we find the 90th, 99th, and 100th percentiles on $\lambda_0$ to be $P_{90}=13.19$, $P_{99}=42.38$, and $P_{100}=111.32$ for the constrained EoSs.
-Because the un-binned residuals seen in Fig.~\ref{fig:residuals} are dominated by the low-error regions of the parameter space ($\Lambda_s \rightarrow 0$, $\Lambda_s \rightarrow \infty$, $q \rightarrow 0$ and $q \rightarrow 1$) shown by Fig.~\ref{fig:qLsResiduals}, we consider the 90th percentile error (indicated by the dashed green line in Fig.~\ref{fig:qLsResiduals}) for the remainder of the analysis, in order to further take into account the high-error regions of the parameter space ($\Lambda_s \sim 2000$, $q\sim0.5$).
-We take this value of $P_{90}=13.19$ to be the systematic measurement error introduced by using the improved binary Love relations on the parameter extraction of $\lambda_0$, indicated by the dashed indigo line in Fig.~\ref{fig:stackedFisher}.
-Similarly, we derive the systematic measurement error on $\tilde\Lambda$ to be $12.01$, shown in Fig.~\ref{fig:singleFisherLt}.
-Currently, the statistical error of $170.1$ on $\lambda_0$ from GW170817 dominates the error budget compared to the systematic error of $13.19$, as seen in Fig.~\ref{fig:stackedFisher}.
+Because the un-binned residuals seen in Fig.~\ref{fig:residuals} are dominated by the low-error regions of the parameter space ($\Lambda_s \rightarrow 0$, $\Lambda_s \rightarrow \infty$, $q \rightarrow 0$ and $q \rightarrow 1$) shown by Fig.~\ref{fig:qLsResiduals}, we consider the 90th percentile uncertainty (indicated by the dashed green line in Fig.~\ref{fig:qLsResiduals}) for the remainder of the analysis, in order to further take into account the high-error regions of the parameter space ($\Lambda_s \sim 2000$, $q\sim0.5$).
+We take this value of $P_{90}=13.19$ to be the systematic measurement uncertainty introduced by using the improved binary Love relations on the parameter extraction of $\lambda_0$, indicated by the dashed indigo line in Fig.~\ref{fig:stackedFisher}.
+Similarly, we derive the systematic measurement uncertainty on $\tilde\Lambda$ to be $12.01$, shown in Fig.~\ref{fig:singleFisherLt}.
+Currently, the statistical uncertainty of $170.1$ on $\lambda_0$ from GW170817 dominates the error budget compared to the systematic uncertainty of $13.19$, as seen in Fig.~\ref{fig:stackedFisher}.
 This means that, for the current ``O2" detector sensitivity, the use of improved binary Love relations will only make a negligible difference on the extraction of $\tilde\Lambda$.
-However, future detectors (for example aLIGO, A\texttt{+}, Voyager, CE, and ET) are planned with large reductions in sensitivity - both decreasing the statistical errors and allowing for larger binary NS merger detection rates; further reducing the statistical uncertainties.
-In Sec.~\ref{sec:futureObservations}, we analyze this further and discuss when the systematic errors from EoS-insensitive relations become comparable to the statistical errors.
+However, future detectors (for example aLIGO, A\texttt{+}, Voyager, CE, and ET) are planned with large reductions in sensitivity - both decreasing the statistical uncertainties and allowing for larger binary NS merger detection rates; further reducing the statistical uncertainties.
+In Sec.~\ref{sec:futureObservations}, we analyze this further and discuss when the systematic uncertainties from EoS-insensitive relations become comparable to the statistical uncertainties.
 
@@
 (\ref{eq:margFit3})-(\ref{eq:margFit4}).
-Observe how the error is maximal for $q\sim0.5$ and $\Lambda_s\sim2000$, while it becomes minimal for both low and high values of $q$ and $\Lambda_s$.
+Observe how the uncertainty is maximal for $q\sim0.5$ and $\Lambda_s\sim2000$, while it becomes minimal for both low and high values of $q$ and $\Lambda_s$.
 Also shown in the figure is the 90th percentile of the un-binned residuals seen in Fig.~\ref{fig:residuals}, taken to be the overall systematic uncertainty introduced by using binary Love relations.
@@
 These residuals obey Gaussian distributions centered at $\mu=-0.1530$ and $\mu=0.2710$ with standard deviations of $\sigma=9.764$ and $\sigma=78.28$ for the constrained and unconstrained sets of EoSs, respectively.
-These uncertainties correspond roughly to the systematic errors introduced on the parameter extraction of $\lambda_0$ upon the use of binary Love relations.
-However, to take into account the systematic errors found in high-error regions of the parameter space, we instead set the systematic error to be the 90th percentile, $P_{90}=13.19$.
-Observe that the systematic errors from using the improved (constrained) binary Love relations are negligible compared to the statistical errors accrued on parameter extraction from GW170817, found to be $\sigma_{\lambda_0}=170.1$.
+These uncertainties correspond roughly to the systematic uncertainties introduced on the parameter extraction of $\lambda_0$ upon the use of binary Love relations.
+However, to take into account the systematic uncertainties found in high-error regions of the parameter space, we instead set the systematic uncertainty to be the 90th percentile, $P_{90}=13.19$.
+Observe that the systematic uncertainties from using the improved (constrained) binary Love relations are negligible compared to the statistical uncertainties accrued on parameter extraction from GW170817, found to be $\sigma_{\lambda_0}=170.1$.
 }
@@
 Comparing the two different tidal corrections to the IMRD waveform returns a rough estimate on the magnitude of waveform mismodeling systematics.
-Lastly, we consider the spectral noise densities $S_n^A(f)$ for 6 different interferometer designs: $A \equiv ($O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, CE~\cite{ET}, ET-D~\cite{Ap_Voyager_CE}$)$ in order to compare the statistical errors accrued on parameter extraction using future upgraded LIGO detectors as well as third generation detectors.
+Lastly, we consider the spectral noise densities $S_n^A(f)$ for 6 different interferometer designs: $A \equiv ($O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, CE~\cite{ET}, ET-D~\cite{Ap_Voyager_CE}$)$ in order to compare the statistical uncertainties accrued on parameter extraction using future upgraded LIGO detectors as well as third generation detectors.
 
@@
 The process we utilize to compute single and combined statistical uncertainties for each detector sensitivity $S_n^A(f)$ is detailed in App.~\ref{app:stackingProcedure}.
-From this, we determine if and when the statistical errors associated with the parameter extraction of $\lambda_0$ drop below the systematic EoS variation errors from using binary Love relations.
+From this, we determine if and when the statistical uncertainties associated with the parameter extraction of $\lambda_0$ drop below the systematic EoS variation errors from using binary Love relations.
 
@@
 For reference, Fig.~\ref{fig:singleFisherLt} also displays the estimated $\tilde\Lambda$ extraction efficiency for \emph{one} event on each detector; as these events can not be combined like was done in the case of $\lambda_0$.
-Observe how this figure shows similar results on $\tilde\Lambda$ to that found on $\lambda_0$ for the case of one event - that is, future third-generation detectors ET and CE both observe statistical errors on $\tilde\Lambda$ (and $\lambda_0$) dropping below the systematic binary Love errors for a single event.
-This result is amplified when multiple events are combined as shown in Fig.~\ref{fig:stackedFisher}, further motivating the need to improve the systematic errors in the binary Love relations for upcoming detectors Voyager, CE and ET.
+Observe how this figure shows similar results on $\tilde\Lambda$ to that found on $\lambda_0$ for the case of one event - that is, future third-generation detectors ET and CE both observe statistical uncertainties on $\tilde\Lambda$ (and $\lambda_0$) dropping below the systematic binary Love errors for a single event.
+This result is amplified when multiple events are combined as shown in Fig.~\ref{fig:stackedFisher}, further motivating the need to improve the systematic uncertainties in the binary Love relations for upcoming detectors Voyager, CE and ET.
 We note that in Figs.~\ref{fig:stackedFisher} and~\ref{fig:singleFisherLt}, the single-event measurement uncertainties are slightly larger for CE than for ET despite having a larger SNR.
@@
 Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ in the extraction of $\tilde\Lambda$ from GW170817 (O2) as if observed with future interferometers aLIGO, A\texttt{+}, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
-Also shown is the systematic error on $\tilde\Lambda$ derived using the same method used to compute the systematic error on $\lambda_0$.
+Also shown is the systematic uncertainty on $\tilde\Lambda$ derived using the same method used to compute the systematic uncertainty on $\lambda_0$.
 This is similar to Fig.~\ref{fig:stackedFisher} where the extraction efficiency of $\lambda_0$ was plotted, however, in this case multiple events can \emph{not} be combined due to the variation in mass and therefore $\tilde\Lambda$ among events.
@@
 \caption{
-Tabulated results for the estimated statistical errors on the tidal deformability at $1.4\text{ M}_{\odot}$, $\lambda_0$, for the combined results of $N_A$ detections corresponding to the estimated upper, central, and lower limits of the binary NS merger detection rate $\mathcal{R}$.
+Tabulated results for the estimated statistical uncertainties on the tidal deformability at $1.4\text{ M}_{\odot}$, $\lambda_0$, for the combined results of $N_A$ detections corresponding to the estimated upper, central, and lower limits of the binary NS merger detection rate $\mathcal{R}$.
 This is repeated for 5 future detector sensitivities: aLIGO, A\texttt{+}, Voyager, CE, and ET.
 Below, $\rho^A_{\text{GW170817}}$ and $\sigma^A_{\text{GW170817}}$ correspond to the approximate SNR and $\sigma_{\lambda_0}$ of GW170817 had it been observed by future interferometer $A$, and $\sigma^A_N$ corresponds to the overall uncertainty on $\lambda_0$ after $N_A$ detections on interferometer $A$.
-It can be seen here that the statistical errors on $\lambda_0$ become comparable with the systematics (set to be $P_{90}=13.19$) from using improved binary Love relations for future detectors Voyager, ET, and CE, indicating when it will become important to improve the EoS-insensitive relations.
+It can be seen here that the statistical uncertainties on $\lambda_0$ become comparable with the systematics (set to be $P_{90}=13.19$) from using improved binary Love relations for future detectors Voyager, ET, and CE, indicating when it will become important to improve the EoS-insensitive relations.
 Note that the approximation for $\sigma^A_N$ under the O2 detector sensitivity is left blank due to the singularity of the detected event.
@@
 This implies that the use and further improvement of EoS-insensitive relations is not only justified, but necessary, for future binary NS merger detections.
-Additionally, we find that the effect of waveform mismodeling is indeed important for future observations as the statistical errors continue to decrease.
+Additionally, we find that the effect of waveform mismodeling is indeed important for future observations as the statistical uncertainties continue to decrease.
 In Appendix~\ref{app:measurement}, we additionally investigate the dependence of the measurement accuracy on $\tilde\Lambda$ on the binary NS mass ratio $q$ for fixed chirp mass $\mathcal{M}=1.88\text{ M}_{\odot}$.
@@
 We also show the relationship between the NS radius and its tidal deformability, computed directly from the C-Love relations.
-We find this relation to display a maximum error of $358.9\text{ m}$ from the fit discussed in Sec.~\ref{sec:clove}.
+We find this relation to display a maximum uncertainty of $358.9\text{ m}$ from the fit discussed in Sec.~\ref{sec:clove}.
 Additionally, we find that hybrid quark-hadron star EoSs \emph{do} obey the I-Love-Q and C-Love relations, albeit with slightly higher maximum EoS variabilities as displayed in Tabs.~\ref{tab:hybridCompare} and ~\ref{tab:hybridCompareClove}.
@@
 Currently detectors are not yet sensitive enough to accurately constrain $\tilde{\Lambda}$ for the improved EoS-insensitive relations to make a difference.
-We find that future interferometers Voyager, CE, and ET-D all experience a reduction in the statistical uncertainties upon the extraction of $\tilde{\Lambda}$ enough to become comparable to the systematic errors injected through the use of improved EoS-insensitive relations, as depicted in Fig.~\ref{fig:stackedFisher} and Table~\ref{tab:variances}.
+We find that future interferometers Voyager, CE, and ET-D all experience a reduction in the statistical uncertainties upon the extraction of $\tilde{\Lambda}$ enough to become comparable to the systematic uncertainties injected through the use of improved EoS-insensitive relations, as depicted in Fig.~\ref{fig:stackedFisher} and Table~\ref{tab:variances}.
 Additionally, we considered the effect of waveform mismodeling by comparing Fisher analyses using two different tidal corrections to the PhenomD waveform: 6PN and NRTidal.
@@
 We conclude by simulating a population of $N_A$ events for each interferometer, approximating the number of events detected on interferometer $A$ over an observing period of one year.
-This is used to combine the statistical uncertainties, resulting in an approximation on the overall measurement accuracy of $\lambda_0$, which is compared to the systematic errors computed in Sec.~\ref{sec:marginalization}.
+This is used to combine the statistical uncertainties, resulting in an approximation on the overall measurement accuracy of $\lambda_0$, which is compared to the systematic uncertainties computed in Sec.~\ref{sec:marginalization}.
 The process used to achieve this is outlined below:
@@
 Here we assume low spin priors $|\chi_{1,2}| \leq 0.05$, as well as $0 \leq \lambda_0 \leq 3207$ and $-4490 \leq \lambda_1 \leq 0$~\cite{delPozzo:TaylorTidal} (these are converted from their corresponding dimensional forms).
-This results in an SNR $\rho^A_{\text{GW170817}}$ and a single-event statistical error $\sigma_\text{GW170817}^A$ accrued in the extraction of $\lambda_0$ on detector $A$.
+This results in an SNR $\rho^A_{\text{GW170817}}$ and a single-event statistical uncertainty $\sigma_\text{GW170817}^A$ accrued in the extraction of $\lambda_0$ on detector $A$.
 
@@
 where $\rho_i^A$ is the SNR of simulated event $i$ computed from Eq.~\ref{eq:population}, and $\rho_{\text{GW170817}}^A$ and $\sigma_{\text{GW170817}}^A$ are the known SNRs and uncertainties of the GW170817 event from step (i).
-This results in the combined statistical errors for the lower, central, and upper limits of the local binary NS coalescence rate density $\mathcal{R}$, depicted by the cyan shaded region in Fig.~\ref{fig:stackedFisher}.
+This results in the combined statistical uncertainties for the lower, central, and upper limits of the local binary NS coalescence rate density $\mathcal{R}$, depicted by the cyan shaded region in Fig.~\ref{fig:stackedFisher}.
 \end{enumerate}

### 2019-02-18 paper/bin-love-after-gw170817.tex
fixed Tab III R-Love row ordering :)
comments

@@
 Figure~\ref{fig:stackedFisher} shows this result in more detail.
-We here present the (Fisher-estimated) statistical uncertainty in the measurement of $\lambda_{0}$ with various detectors (O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, ET~\cite{ET}, CE~\cite{Ap_Voyager_CE}) for an event identical to GW170817.
+We here present the (Fisher-estimated) statistical uncertainty in the measurement of $\lambda_{0}$ with various detectors (O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, ET~\cite{ET}, CE~\cite{Ap_Voyager_CE}) \zc{Maybe these should be spelled out because it's the first time I mention them?
+a.k.a.
+(LIGO O2~\cite{aLIGO}, Advanced LIGO (aLIGO)~\cite{aLIGO}, LIGO A\texttt{+} (A\texttt{+})\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, the Einstein Telescope (ET)~\cite{ET}, and the Cosmic Explorer (CE)~\cite{Ap_Voyager_CE})} for an event identical to GW170817.
 The x-axis shows the signal-to-noise ratio for a GW170817 event detected with each of these detectors.
@@
 Observe that the statistical and the systematic uncertainties cross for Voyager-class detectors.
-s
 
@@
   \hline
- \multirow{2}{*}{$R-\Lambda$} & -- & $0.02172$ & $0.05649$\\
- & (--) & ($358.9 \text{ m}$) & ($881.4 \text{ m}$)\\
+ \multirow{2}{*}{$R-\Lambda$} & -- & $0.05649$ & $0.02172$\\
+ & (--) & ($881.4 \text{ m}$) & ($358.9 \text{ m}$) \\
  \hline

### 2019-02-19 paper/bin-love-after-gw170817.tex
up to Sec. 2A

--- 2019-02-18 paper/bin-love-after-gw170817.tex
@@
 
+In this section we review how the EoS can be represented analytically
+through a spectral decomposition, and how the observation of GW170817
+constrains the space of possible EoSs. We then proceed to discuss 
+how one computes the tidal deformabilities and the EoS-insensitive relations.
+
 \subsection{Spectral representations of neutron star equations of state}
@@
 Given that all currently proposed EoSs utilize certain approximations~\cite{Oertel:Review,Baym:Review}, one method to study a wide range of physically realizable EoSs is to parameterize them such that any realistic EoS can be represented with a small number of parameters.
-Spectral representations~\cite{Lindblom:2010bb,Lindblom:2012zi,Lindblom:2013kra,Lindblom:2018rfr,Abbott:2018exr} parameterize EoSs by performing spectral expansions on the adiabatic index $\Gamma(p)$\footnote{Another way of parameterizing EoSs is the piecewise polytropic formulation~\cite{Read2009,Lackey:2014fwa,Carney:2018sdv}.}:
-\begin{equation}
-\Gamma(x) = \exp{\sum_k\gamma_k x^k},
-\end{equation}
-where $x \equiv \log{p/p_0}$ for a minimum pressure $p_0$.
+Spectral representations~\cite{Lindblom:2010bb,Lindblom:2012zi,Lindblom:2013kra,Lindblom:2018rfr,Abbott:2018exr} parameterize EoSs by performing spectral expansions on the adiabatic index $\Gamma(p)$\footnote{Another way of parameterizing EoSs is through a piecewise polytropic formulation~\cite{Read2009,Lackey:2014fwa,Carney:2018sdv}.}:
+\begin{equation}
+\Gamma(x) = \exp{\sum_k^{N}\gamma_k x^k},
+\end{equation}
+where $x \equiv \log{(p/p_0)}$ for a minimum pressure $p_0$.
 The equation of state is then determined by an integration of the differential equation:
@@
 \end{equation}
-Using this formalism, any valid EoS can be approximated through the choice of 4 spectral coefficients $\gamma_k$, tabulated for several common EoSs in Table 1 of Ref.~\cite{Lindblom:2018rfr}.
-
-In the current analysis, we consider EoSs which have been constrained by the recent binary neutron star merger event, GW170817.
-Important recent work by the LIGO Collaboration~\cite{LIGO:posterior,Carney:2018sdv} sampled the EoS parameter space in order to derive a marginalized posterior on the pressure as a function of mass density, as seen in Fig.
+Using this formalism, any valid EoS can be approximated through the choice of $N$ spectral coefficients $\gamma_k$, and we here choose $N=4$, tabulated for several common EoSs in Table 1 of~\cite{Lindblom:2018rfr}.
+
+{\ny{Zack, I rewrote what's below, but please check.}}
+
+We here wish to consider EoS-insensitive relations using two sets of EoSs: a ``constrained set'' consistent with the observation of GW170817 and an ``unconstrained set'' that does not impose this prior.
+In \emph{both} cases, we model the EoS with a $C^{0}$-piecewise function that equals the low-density crust EoS of SLy~\cite{Douchin:2001sv} below half nuclear saturation density $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$~\cite{Read2009}, and equals the spectral decomposition described above outside the crust.
+For the latter, we restrict the spectral coefficients to the ranges $\gamma_0 \in \lbrack 0.2,2 \rbrack$, $\gamma_1 \in \lbrack -1.6,1.7 \rbrack$, $\gamma_2 \in \lbrack -0.6,0.6 \rbrack$, $\gamma_3 \in \lbrack -0.02,0.02 \rbrack$, and the adiabatic index is further restricted to $\Gamma \in \lbrack 0.6,4.5 \rbrack$~\cite{Lindblom:parameters}.
+Moreover, we impose the following two restrictions:  (i) causality within 10\%, i.e.
+that the speed of sound of the fluid be less than the speed of light to 10\%, and (ii) a high maximum mass, i.e.~that the resulting EoS supports NSs with masses at least as high as $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations~\cite{Zhao:massiveNS}.
+
+The unconstrained set is then defined by drawing random samples in the spectral coefficients (within their allowed prior ranges), and then eliminating any EoS that either leads to a polytropic index $\Gamma$ outside the allowed range, or breaks the causality restriction, or breaks the maximum mass restriction.
+The constrained set is defined in a similar way, with the addition of the restriction that the resulting EoS be inside the 90\% marginalized posterior distribution on the pressure-mass density plane derived from the GW170817 observation~\cite{LIGO:posterior,Carney:2018sdv}  (see Fig.~2 in~\cite{LIGO:posterior}).
+In both cases, each set consists of 100 members, with a subset of these shown in Fig.~\ref{fig:eos}.
+
+%In the current analysis, we consider EoSs which have been constrained by the recent binary neutron star merger event, GW170817.
+%Important recent work by the LIGO Collaboration~\cite{LIGO:posterior,Carney:2018sdv} sampled the EoS parameter space in order to derive a marginalized posterior on the pressure as a function of mass density, as seen in Fig.
 2 of~\cite{LIGO:posterior}.
-The spectral coefficients were sampled within the ranges: $\gamma_0 \in \lbrack 0.2,2 \rbrack$, $\gamma_1 \in \lbrack -1.6,1.7 \rbrack$, $\gamma_2 \in \lbrack -0.6,0.6 \rbrack$, $\gamma_3 \in \lbrack -0.02,0.02 \rbrack$, and further restricted the adiabatic index to be $\Gamma \in \lbrack 0.6,4.5 \rbrack$, ensuring the parameterization exposed a wide range of viable EoSs~\cite{Lindblom:parameters}.
-Additional constraints imposed upon the generated EoSs were as follows~\cite{LIGO:posterior}: (i) causality within 10\%, and (ii) EoS priors must support NS masses up to $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations~\cite{Zhao:massiveNS}.
-We utilize a random set of 100 of the above posterior samples defined by GW170817, furthermore referenced as the ``constrained EoSs", as shown in Fig.~\ref{fig:eos}.
-For comparison, we also include a second sample of 100 ``unconstrained" EoSs, randomly sampled in the pressure-density plane to be unrestricted by GW170817s posterior.
-Following~\cite{Read2009}, the parameterized high-density core EoSs generated above are matched to the low-density crust EoS of Sly~\cite{Douchin:2001sv} at about half of the nuclear saturation density, $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$.
-
-In addition, we investigate 10 transitional quark-hadron matter stars, which undergo first-order phase transitions at pressure $P_{\text{tr}}$, where the hadronic branch departs into a quark-matter branch at a given transitional mass~\cite{Paschalidis2018,Alford:2017qgh,1971SvA....15..347S,Zdunik:2012dj,Alford:2013aca}.
-In particular, we focus on the ACS and ACB models described in Ref.~\cite{Paschalidis2018}, shown in Fig.~\ref{fig:hybridML}.
-These result in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq \text{ M}_{\text{tr}}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote this as ``HS"), and (ii) low-mass ($M \leq \text{ M}_{\text{tr}}$) hadronic stars with no internal transition to quark matter (we denote this as ``NS").
+%The spectral coefficients were sampled within the ranges: $\gamma_0 \in \lbrack 0.2,2 \rbrack$, $\gamma_1 \in \lbrack -1.6,1.7 \rbrack$, $\gamma_2 \in \lbrack -0.6,0.6 \rbrack$, $\gamma_3 \in \lbrack -0.02,0.02 \rbrack$, and further restricted the adiabatic index to be $\Gamma \in \lbrack 0.6,4.5 \rbrack$, ensuring the parameterization exposed a wide range of viable EoSs~\cite{Lindblom:parameters}.
+%Additional constraints imposed upon the generated EoSs were as follows~\cite{LIGO:posterior}: (i) causality within 10\%, and (ii) EoS priors must support NS masses up to $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations~\cite{Zhao:massiveNS}.
+%We utilize a random set of 100 of the above posterior samples defined by GW170817, furthermore referenced as the ``constrained EoSs", as shown in Fig.~\ref{fig:eos}.
+%For comparison, we also include a second sample of 100 ``unconstrained" EoSs, randomly sampled in the pressure-density plane to be unrestricted by GW170817s posterior.
+%Following~\cite{Read2009}, the parameterized high-density core EoSs generated above are matched to the low-density crust EoS of Sly~\cite{Douchin:2001sv} at about half of the nuclear saturation density, $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$.
+
+{\ny{Zack, I think the description here was wrong because the hybrid stars do not just have hadronic matter in the crust, but also in the outer core, no? Please check.}}
+
+In addition, we investigate 10 transitional quark-hadron matter stars, which undergo strong first-order phase transitions at a pressure $P_{\text{tr}}$, leading to the hadronic branch departing into a quark-matter branch at a given transitional mass~\cite{Paschalidis2018,Alford:2017qgh,1971SvA....15..347S,Zdunik:2012dj,Alford:2013aca}.
+In particular, we focus on the ACS and ACB models described in~\cite{Paschalidis2018}, and also shown in Fig.~\ref{fig:hybridML}.
+These result in two distinct types of NSs, based on their mass: (i) massive ($M \geq \text{ M}_{\text{tr}}$) hybrid stars which have quark-matter inner cores and nuclear matter elsewhere (henceforth, we denote such stars as hybrid stars (HSs)), and (ii) low-mass ($M \leq \text{ M}_{\text{tr}}$) hadronic stars with no internal transition to quark matter (henceforth, we denote these stars as simply NSs).
 

### 2019-02-19 paper/bin-love-after-gw170817.tex
fixed caption of Fig. 2

--- 2019-02-19 paper/bin-love-after-gw170817.tex
@@
 Figure~\ref{fig:stackedFisher} shows this result in more detail.
-We here present the (Fisher-estimated) statistical uncertainty in the measurement of $\lambda_{0}$ with various detectors (O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, ET~\cite{ET}, CE~\cite{Ap_Voyager_CE}) for an event identical to GW170817.
+We here present the (Fisher-estimated) statistical uncertainty in the measurement of $\lambda_{0}$ with various detectors (LIGO O2~\cite{aLIGO}, Advanced LIGO (aLIGO)~\cite{aLIGO}, LIGO A\texttt{+} (A\texttt{+})\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, the Einstein Telescope (ET)~\cite{ET}, and the Cosmic Explorer (CE)~\cite{Ap_Voyager_CE}) for an event identical to GW170817.
 The x-axis shows the signal-to-noise ratio for a GW170817 event detected with each of these detectors.
@@
 \end{center}
-\caption{
-Small representative sets of the unconstrained (dotted) and constrained (solid) EoSs used in this analysis. 
-The constrained EoSs were populated by randomly selecting 100 posterior samples obtained from the GW170817 90\% credible level shown in cyan~\cite{LIGO:posterior}.
-Additionally, 100 unconstrained EoSs were generated by randomly sampling spectral coefficients of physically valid EoSs, with no further constraints applied.
-The following restrictions were also applied to both sets of EoSs: (i) each EoS must have a causal structure within 10\%, and (ii) each EoS must support a maximum NS mass of at least $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations.
-Finally, the high density core EoSs generated above were stitched to the low-density crust EoS of SLy~\cite{Douchin:2001sv} at $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$.}
+\caption{(Color Online) Small representative samples of the unconstrained (dotted) and constrained (solid) sets, together with the 90\% marginalized posterior distribution from the observation of GW170817 (cyan shaded region)~\cite{LIGO:posterior}.
+Observe that the there is significantly less variability in the constrained set of EoSs due to the requirement that they be consistent with the GW170817 observation.}
 \label{fig:eos}

### 2019-02-19 paper/bin-love-after-gw170817.tex
added small comment about figs.
up to Sec. III

@@
 %reparameterization of the template
-The gravitational waves emitted by binary neutron stars in the late inspiral must then depend on the \emph{tidal deformabilities} $\Lambda_1$ and $\Lambda_2$, which control the linear response of the star's quadrupole deformation to the (electric-type, quadrupole) tidal field of the companion (to leading order in a post-Newtonian expansion~\cite{Blanchet:2013haa})~\cite{Flanagan2008,Vines:2011ud}.
+The GWs emitted by binary NSs in the late inspiral must then depend on the \emph{tidal deformabilities} $\Lambda_1$ and $\Lambda_2$, which control the linear response of the star's quadrupole deformation to the (electric-type, quadrupole) tidal field of the companion (to leading order in a post-Newtonian expansion~\cite{Blanchet:2013haa})~\cite{Flanagan2008,Vines:2011ud}.
 These parameters, however, enter the GW Fourier model multiplied by the same function of the GW frequency (at leading post-Newtonian order), making them degenerate, and thus, very difficult to estimate independently with current GW data~\cite{Wade:tidalCorrections}.
@@
 Lacking enough sensitivity in current GW observations, one is forced to only estimate the chirp deformability, but this prevents the independent extraction of $\Lambda_{1}$ and $\Lambda_{2}$.
-Yagi and Yunes~\cite{Yagi:binLove} solved this problem by finding EoS-insensitive relations between the symmetric and anti-symmetric combinations of the tidal deformabilities $\Lambda_{s,a}=\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$, the so-called ``binary Love relations." These relations can be used to analytically express $\Lambda_{s}$ in terms of $\Lambda_{a}$ (or vice-versa), making the chirp deformability a function of only $\Lambda_{a}$.
+Yagi and Yunes~\cite{Yagi:binLove} solved this problem by finding ``approximately universal'' or ``EoS-insensitive'' relations between the symmetric and anti-symmetric combinations of the tidal deformabilities $\Lambda_{s,a}=\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$, the so-called ``binary Love relations." These relations can be used to analytically express $\Lambda_{s}$ in terms of $\Lambda_{a}$ (or vice-versa), making the chirp deformability a function of only $\Lambda_{a}$.
 A measurement of the chirp deformability then implies a measurement of $\Lambda_{a}$, and through the use of the binary Love relations, also a measurement of $\Lambda_{s}$, which then allows for the inference of the individual tidal deformabilities $\Lambda_{1}$ and $\Lambda_{2}$~\cite{Yagi:binLove}.
@@
 
-\subsection{Spectral representations of neutron star equations of state}
+\subsection{Spectral representations of NS equations of state}
 \label{sec:eos}
@@
 
-\subsection{Neutron Star Tidal deformability}\label{tidal}
-Binary neutron star mergers, such as GW170817, provide valuable insight into the internal structure of such stars. 
-Namely, tidal effects which enter the gravitational waveform depend strongly on the EoS defining the NSs structure. 
-The ($l=2$ electric type) \emph{tidal deformability}, denoted as $\lambda$, has the largest impact on the waveform phase. 
-Consider a NS of mass $M$ in the presence of the tidal field $\varepsilon_{ij}$ of a companion star.
-In response, the NS will deform away from sphericity under the acquisition of quadrupole moment $Q_{ij}$, characterized by $\lambda$ as the linear response to $\varepsilon_{ij}$~\cite{Flanagan2008,hinderer-love,Yagi2013}:
-\begin{equation}
-Q_{ij}=-\lambda \varepsilon_{ij}.
-\end{equation}
-One can extract $Q_{ij}$ and $\varepsilon_{ij}$ -- and thus $\lambda$, or its dimensionless form $\Lambda \equiv \lambda/M^5$ -- via different asymptotic limits of the gravitational potential:
+{\ny{Zack, it's a bit weird to show p-rho in Fig.
+2 (for the NSs) and then show M-Lambda in Fig.
+3 for the hybrid stars.
+Why not plot also p-rho here and make these two figures into widetext?
+I think this would make the comparison between them cleaner, specially considering that we haven't introduced Lambda yet.}}
+
+\subsection{NS Tidal deformability}\label{tidal}
+
+The GWs emitted in the coalescence of binary NSs, such as GW170817, provide valuable insight into their internal structure.
+As the stars spiral into each other, they tidally deform due to their companion's tidal field.
+The tidal field can be decomposed into multipole moments, with the leading-order field being even parity and quadrupolar, and thus leading to an even parity and quadrupolar deformation in response.
+The constant of proportionality that determines how quadrupolarly deformed a star becomes in the presence of a quadrupolar tidal field is called the \emph{tidal deformability} and denoted $\lambda$.
+Therefore, this parameter has the largest impact on the GW phase, and thus, it is encoded in GW observations of binary NS coalescence.
+
+Consider a NS of mass $M$ in the presence of the (spatial) tidal tensor $\varepsilon_{ij}$ of its companion.
+In response to this tidal field, the NS will deform away from sphericity and acquire a (spatial) quadrupole moment tensor $Q_{ij}$.
+The tidal deformability $\lambda$ quantifies this linear response via~\cite{Flanagan2008,hinderer-love,Yagi2013}:
+\begin{equation}
+Q_{ij}=-\lambda \; \varepsilon_{ij}.
+\end{equation}
+One can extract $Q_{ij}$ and $\varepsilon_{ij}$ -- and thus $\lambda$, or its dimensionless form $\Lambda \equiv \lambda/M^5$ -- via a double asymptotic expansion of the gravitational potential in a buffer zone, defined by ${\cal{L}} \gg r \gg R$ {\ny{This was inaccurate so I rewrote it}}:
 \begin{align}
-\begin{split}
-\Phi=\frac{1+g_{tt}}{2}&=-\frac{M}{r} - \frac{3}{2}\frac{Q_{ij}}{r^3} \Bigg(\frac{x^i}{r} \frac{x^j}{r}-\frac{1}{3}\delta_{ij} \Bigg) + \mathcal{O} \Bigg( \frac{M^4}{r^4} \Bigg)\\
-&+ \frac{1}{2} \varepsilon_{ij} x^i x^j + \mathcal{O} \Bigg( \frac{r^3}{M^3} \Bigg).
-\end{split}
+\Phi=\frac{1+g_{tt}}{2}&=-\frac{M}{r} - \frac{3}{2}\frac{Q_{ij}}{r^3} \Bigg(\frac{x^i}{r} \frac{x^j}{r}-\frac{1}{3}\delta_{ij} \Bigg) + \mathcal{O} \Bigg( \frac{{\cal{L}}^4}{r^4} \Bigg)
+\nonumber \\ &+ \frac{1}{2} \varepsilon_{ij} x^i x^j + \mathcal{O} \Bigg( \frac{r^3}{R^3} \Bigg),
 \end{align}
-The metric component $g_{tt}$ is determined by first constructing a spherically symmetric, non-spinning background solution, followed by the introduction of a perturbative tidal deformation.
-Next, the perturbed Einstein equations must be solved in the NSs interior given an EoS, then matched to the exterior Schwarzschild solution at the surface, modulo a constant.
-This process is described in more detail in Ref.~\cite{hinderer-love}.
-Further, the stellar mass and radius are determined from $p(R)=0$, and the above mentioned constant.
-Similarly, the moment of inertia is obtained from the asymptotic behavior of the $g_{t \phi}$ metric component.
-
-Next we consider binary NS systems, as was found in GW170817, where each star individually experiences a neighboring tidal field.
-Thus each star possesses tidal deformabilities $\Lambda_1$ and $\Lambda_2$ entering the gravitational waveform.
+where $R$ is the radius of the star and ${\cal{L}}$ is the length scale associated with the radius of curvature induced by the companion.
+
+The calculation of the tidal deformability therefore requires the calculation of the metric component $g_{tt}$.
+One typically stars by first constructing a spherically symmetric, non-spinning background solution, whose stellar mass and radius are determined from $p(R)=0$.
+One then perturbatively introduces a tidal deformation and solves the perturbed Einstein equations in the NS interior, and matches this solution to an exterior Schwarzschild solution at the surface, modulo a constant.
+The requirement that the metric be at least $C^{1}$ fixes all constants of integration, yielding the tidal deformability, as discussed in more detail in~\cite{hinderer-love}.
+One can similarly obtain the moment of inertia from the asymptotic behavior of the $g_{t \phi}$ metric component.
+
+{\ny{Wait, is $\tilde{\Lambda}$ the ``mass-weighted tidal deformability'' or is it the ``chirp deformability''? Is there a difference? Please look it up and correct the nomenclature.}}
+
+Consider now a binary NS systems, as that which produced the GW170817 event, where each star individually experiences the tidal field of the other star.
+Thus, each star possesses tidal deformabilities $\Lambda_1$ and $\Lambda_2$ that enter the GW phase and encode information about each star's EoS.
 Due to strong correlations between these parameters, individual extraction is very difficult with current interferometer sensitivity limitations.
-However, the waveform templates can be strategically reparameterized to instead include independent linear combinations of $\Lambda_1$ and $\Lambda_2$ to mitigate correlations between them. 
-Any set of two independent functions may be used, for example: tidal parameters $\tilde{\Lambda}=\tilde{\Lambda}(\Lambda_1,\Lambda_2)$ and $\delta \tilde{\Lambda}=\delta \tilde{\Lambda}(\Lambda_1,\Lambda_2)$~\cite{Wade:tidalCorrections} first enter the gravitational waveform at 5pN and 6pN orders respectively, thus partially breaking degeneracies.
-Here, $\tilde{\Lambda}$ is known as the mass weighted tidal deformability and is the dominant tidal parameter in the waveform.
+However, the waveform templates can be strategically reparameterized to instead include independent linear combinations of $\Lambda_1$ and $\Lambda_2$ that mitigate correlations.
+One common reparameterization is through the introduction of the chirp deformability $\tilde{\Lambda}=\tilde{\Lambda}(\Lambda_1,\Lambda_2)$ and the parameter $\delta \tilde{\Lambda}=\delta \tilde{\Lambda}(\Lambda_1,\Lambda_2)$~\cite{Wade:tidalCorrections}.
+Since these parameters enter the GW phase at 5 and 6PN orders respectively\footnote{A term of NPN order is proportional to $v^{2N}$ relative to the leading-order term in the expression.}, the partially break the degeneracies between $\Lambda_{1}$ and $\Lambda_{2}$.
 
 \subsection{EoS-insensitive relations}\label{sec:eosInsensitive}
-Current gravitational wave interferometry is not yet sensitive enough to accurately extract both tidal parameters $\tilde{\Lambda}$ and $\delta\tilde{\Lambda}$.
-In a search to remedy this, Yagi and Yunes~\cite{Yagi:binLove} found that symmetric and antisymmetric combinations of tidal deformabilities:
+Current GW interferometry is not yet sensitive enough to accurately extract both tidal parameters $\tilde{\Lambda}$ and $\delta\tilde{\Lambda}$.
+In a search to remedy this, Yagi and Yunes~\cite{Yagi:binLove} found that symmetric and antisymmetric combinations of the tidal deformabilities:
 \begin{equation}
@@
 \end{equation}
-display EoS-insensitive properties to a high degree, showing EoS variations up to 20\% for binaries with masses less than $1.7 \text{ M}_{\odot}$, for a representative set of 11 EoSs. 
-These ``binary Love relations" allow one to break degeneracies between coupled tidal parameters.
-This is important for two reasons: (i) they allow one to algebraically eliminate tidal parameters from the template parameter list, improving overall parameter estimation; and (ii) they allow the automatic measurement of a second tidal parameter given observation of the first.
-It was shown through a simple Fisher analysis that the use of the binary Love relations improved the parameter extraction of $\tilde{\Lambda}$ by up to an order of magnitude.
-
-Similar EoS-insensitive relations have been found to exist between individual NS observables: moment of inertia (I), tidal deformability (Love), quadrupole moment (Q), and compactness (C), known as the ``I-Love-Q" and ``C-Love" relations~\cite{Yagi:ILQ, Yagi:binLove}.
-These relations, found to be EoS-insensitive by up to 1\% and 6.5\% respectively, have been used for many important applications including deriving constraints on several stellar properties such as the moment of inertia (I), tidal deformability ($\Lambda$), compactness (C), spin ($\chi$), and radius (R)~\cite{Kumar:2019xgp}.
-Analyses such as that done in Ref.~\cite{Kumar:2019xgp} would benefit greatly from the improvement of such EoS-insensitive relations.
-In this paper, we show an improvement on these relations by restricting to EoSs sampled from GW170817s posterior on pressure as a function of density.
+display EoS-insensitive properties to a high degree, showing EoS variations of at most 20\% for binaries with masses less than $1.7 \text{ M}_{\odot}$ and using a representative sample of 11 EoSs. 
+These ``binary Love relations" allow one to analytically break degeneracies between the tidal parameters: one can substitute $\Lambda_{a}=\Lambda_{a}(\Lambda_{s})$ in the GW model, thus completing eliminating $\Lambda_{a}$ from the parameter list (or vice-versa).
+This is important for two reasons: (i) the new model allows for the more accurate extraction of $\Lambda_{s}$ (or $\Lambda_{a}$ if $\Lambda_{s}$ is eliminated), and (ii) the relations allow for the inference of $\Lambda_{a}$ given a measurement of $\Lambda_{s}$ (or vice-versa), and from this for the inference of the individual tidal deformabilities $\Lambda_{1}$ and $\Lambda_{2}$.
+A simple Fisher analysis has shown that the binary Love relations improve parameter estimation of $\tilde{\Lambda}$ by up to an order of magnitude~\cite{Yagi:binLove}.
+
+Similar EoS-insensitive relations have been found between individual NS observables: the moment of inertia (I), the tidal deformability (Love), the quadrupole moment (Q), and the compactness (C), known as the ``I-Love-Q" and ``C-Love" relations~\cite{Yagi:ILQ, Yagi:binLove}.
+These relations are EoS-insensitive to better than 1\% and 6\% respectively, and they have been important applications in both GW astrophysics and experimental relativity.
+For example, these relations and the measurement of the tidal deformabilities allow for the inference of several other stellar properties, such as the moment of inertia, the  compactness, the spin ($\chi$), and the radius of NSs~\cite{Kumar:2019xgp}.
+Analyses such as that of~\cite{Kumar:2019xgp} could benefit from the improvement of such EoS-insensitive relations, which we derive in this paper.
 

### 2019-02-19 paper/bin-love-after-gw170817.tex
Sec 2a

--- 2019-02-19 paper/bin-love-after-gw170817.tex
@@
 
-{\ny{Zack, I rewrote what's below, but please check.}}
-
 We here wish to consider EoS-insensitive relations using two sets of EoSs: a ``constrained set'' consistent with the observation of GW170817 and an ``unconstrained set'' that does not impose this prior.
@@
 
-The unconstrained set is then defined by drawing random samples in the spectral coefficients (within their allowed prior ranges), and then eliminating any EoS that either leads to a polytropic index $\Gamma$ outside the allowed range, or breaks the causality restriction, or breaks the maximum mass restriction.
+The unconstrained set is then defined by drawing random samples in the spectral coefficients (within their allowed prior ranges), and then eliminating any EoS that either leads to a polytropic index $\Gamma$ outside the allowed range, breaks the causality restriction, or breaks the maximum mass restriction.
 The constrained set is defined in a similar way, with the addition of the restriction that the resulting EoS be inside the 90\% marginalized posterior distribution on the pressure-mass density plane derived from the GW170817 observation~\cite{LIGO:posterior,Carney:2018sdv}  (see Fig.~2 in~\cite{LIGO:posterior}).
-In both cases, each set consists of 100 members, with a subset of these shown in Fig.~\ref{fig:eos}.
+In both cases, each set consists of 100 members, with a subset of these shown in the left panel of Fig.~\ref{fig:eos}.
 
@@
 
-{\ny{Zack, I think the description here was wrong because the hybrid stars do not just have hadronic matter in the crust, but also in the outer core, no? Please check.}}
-
 In addition, we investigate 10 transitional quark-hadron matter stars, which undergo strong first-order phase transitions at a pressure $P_{\text{tr}}$, leading to the hadronic branch departing into a quark-matter branch at a given transitional mass~\cite{Paschalidis2018,Alford:2017qgh,1971SvA....15..347S,Zdunik:2012dj,Alford:2013aca}.
-In particular, we focus on the ACS and ACB models described in~\cite{Paschalidis2018}, and also shown in Fig.~\ref{fig:hybridML}.
+In particular, we focus on the ACS and ACB models described in~\cite{Paschalidis2018}, and also shown in the right panel of Fig.~\ref{fig:eos}.
 These result in two distinct types of NSs, based on their mass: (i) massive ($M \geq \text{ M}_{\text{tr}}$) hybrid stars which have quark-matter inner cores and nuclear matter elsewhere (henceforth, we denote such stars as hybrid stars (HSs)), and (ii) low-mass ($M \leq \text{ M}_{\text{tr}}$) hadronic stars with no internal transition to quark matter (henceforth, we denote these stars as simply NSs).
 
-\begin{figure}
+\begin{figure*}
 \begin{center} 
 \includegraphics[width=\columnwidth]{EoSs.eps}
+\includegraphics[width=\columnwidth]{hybridEoSs.eps}
 \end{center}
-\caption{(Color Online) Small representative samples of the unconstrained (dotted) and constrained (solid) sets, together with the 90\% marginalized posterior distribution from the observation of GW170817 (cyan shaded region)~\cite{LIGO:posterior}.
-Observe that the there is significantly less variability in the constrained set of EoSs due to the requirement that they be consistent with the GW170817 observation.}
+\caption{(Color Online) (left) Small representative samples of the unconstrained (dotted) and constrained (solid) sets, together with the 90\% marginalized posterior distribution from the observation of GW170817 (cyan shaded region)~\cite{LIGO:posterior}.
+Observe that the there is significantly less variability in the constrained set of EoSs due to the requirement that they be consistent with the GW170817 observation.
+(right) ACS and ACB model hybrid stars investigated in our analysis, each transitioning from a hadronic branch (corresponging to a pure hadronic-matter NS) into a quark-matter branch (quark-matter inner core surrounded by hadronic matter) at various transition pressures $P_{\text{tr}}$.
+}
 \label{fig:eos}
-\end{figure}
-
-\begin{figure}
-\begin{center} 
-\includegraphics[width=\linewidth]{hybridML.eps}
-\end{center}
-\caption{
-$M-\Lambda$ relations for the ACS and ACB class model hybrid stars. 
-Observe the transitional points where the NS transitions from the hadronic branch into a quark-matter branch.
-}
-\label{fig:hybridML}
-\end{figure}
+\end{figure*}
 
@@
 Observe how the agreement with the fit is quite good at low pressures (large $\Lambda_s$) where the the binaries consist of NS/NS combinations (here, both stars' EoSs consist of the same class of nuclear matter as the constrained EoSs).
-Once the critical pressure is reached, one or both stars transition into the hybrid branches, resulting in large reductions in tidal deformability as shown in Fig.~\ref{fig:hybridML}.
+Once the critical pressure is reached, one or both stars transition into the hybrid branches, resulting in large reductions in tidal deformability as shown in the right panel of Fig.~\ref{fig:eos}.
 When one star lies on the hadronic-matter branch while the other is on the quark-matter branch, 

### 2019-02-19 paper/bin-love-after-gw170817.tex

--- 2019-02-19 paper/bin-love-after-gw170817.tex
@@
 
-{\ny{Zack, I think the description here was wrong because the hybrid stars do not just have hadronic matter in the crust, but also in the outer core, no? Please check.}}
-
 In addition, we investigate 10 transitional quark-hadron matter stars, which undergo strong first-order phase transitions at a pressure $P_{\text{tr}}$, leading to the hadronic branch departing into a quark-matter branch at a given transitional mass~\cite{Paschalidis2018,Alford:2017qgh,1971SvA....15..347S,Zdunik:2012dj,Alford:2013aca}.
-In particular, we focus on the ACS and ACB models described in~\cite{Paschalidis2018}, and also shown in Fig.~\ref{fig:hybridML}.
+In particular, we focus on the ACS and ACB models described in~\cite{Paschalidis2018}, and also shown in the right panel of Fig.~\ref{fig:eos}.
 These result in two distinct types of NSs, based on their mass: (i) massive ($M \geq \text{ M}_{\text{tr}}$) hybrid stars which have quark-matter inner cores and nuclear matter elsewhere (henceforth, we denote such stars as hybrid stars (HSs)), and (ii) low-mass ($M \leq \text{ M}_{\text{tr}}$) hadronic stars with no internal transition to quark matter (henceforth, we denote these stars as simply NSs).
 
-\begin{figure}
+\begin{figure*}
 \begin{center} 
 \includegraphics[width=\columnwidth]{EoSs.eps}
+\includegraphics[width=\columnwidth]{hybridEoSs.eps}
 \end{center}
-\caption{(Color Online) Small representative samples of the unconstrained (dotted) and constrained (solid) sets, together with the 90\% marginalized posterior distribution from the observation of GW170817 (cyan shaded region)~\cite{LIGO:posterior}.
-Observe that the there is significantly less variability in the constrained set of EoSs due to the requirement that they be consistent with the GW170817 observation.}
+\caption{(Color Online) (left) Small representative samples of the unconstrained (dotted) and constrained (solid) sets, together with the 90\% marginalized posterior distribution from the observation of GW170817 (cyan shaded region)~\cite{LIGO:posterior}.
+Observe that the there is significantly less variability in the constrained set of EoSs due to the requirement that they be consistent with the GW170817 observation.
+(right) ACS and ACB model hybrid stars investigated in our analysis, each transitioning from a hadronic branch (corresponging to a pure hadronic-matter NS) into a quark-matter branch (quark-matter inner core surrounded by hadronic matter) at various transition pressures $P_{\text{tr}}$.
+}
 \label{fig:eos}
-\end{figure}
-
-\begin{figure}
-\begin{center} 
-\includegraphics[width=\linewidth]{hybridML.eps}
-\end{center}
-\caption{
-$M-\Lambda$ relations for the ACS and ACB class model hybrid stars. 
-Observe the transitional points where the NS transitions from the hadronic branch into a quark-matter branch.
-}
-\label{fig:hybridML}
-\end{figure}
-
-{\ny{Zack, it's a bit weird to show p-rho in Fig.
-2 (for the NSs) and then show M-Lambda in Fig.
-3 for the hybrid stars.
-Why not plot also p-rho here and make these two figures into widetext?
-I think this would make the comparison between them cleaner, specially considering that we haven't introduced Lambda yet.}}
+\end{figure*}
 

### 2019-02-19 paper/bin-love-after-gw170817.tex
merged Figs 2 and 3, addressed some of Nicos comments

@@
 \end{equation}
-One can extract $Q_{ij}$ and $\varepsilon_{ij}$ -- and thus $\lambda$, or its dimensionless form $\Lambda \equiv \lambda/M^5$ -- via a double asymptotic expansion of the gravitational potential in a buffer zone, defined by ${\cal{L}} \gg r \gg R$ {\ny{This was inaccurate so I rewrote it}}:
+One can extract $Q_{ij}$ and $\varepsilon_{ij}$ -- and thus $\lambda$, or its dimensionless form $\Lambda \equiv \lambda/M^5$ -- via a double asymptotic expansion of the gravitational potential in a buffer zone, defined by ${\cal{L}} \gg r \gg R$:
 \begin{align}
@@
 The calculation of the tidal deformability therefore requires the calculation of the metric component $g_{tt}$.
-One typically stars by first constructing a spherically symmetric, non-spinning background solution, whose stellar mass and radius are determined from $p(R)=0$.
+One typically starts by first constructing a spherically symmetric, non-spinning background solution, whose stellar mass and radius are determined from $p(R)=0$.
 One then perturbatively introduces a tidal deformation and solves the perturbed Einstein equations in the NS interior, and matches this solution to an exterior Schwarzschild solution at the surface, modulo a constant.
@@
 
-{\ny{Wait, is $\tilde{\Lambda}$ the ``mass-weighted tidal deformability'' or is it the ``chirp deformability''? Is there a difference? Please look it up and correct the nomenclature.}}
-
-Consider now a binary NS systems, as that which produced the GW170817 event, where each star individually experiences the tidal field of the other star.
+Consider now a binary NS system, as that which produced the GW170817 event, where each star individually experiences the tidal field of the other star.
 Thus, each star possesses tidal deformabilities $\Lambda_1$ and $\Lambda_2$ that enter the GW phase and encode information about each star's EoS.
@@
 One common reparameterization is through the introduction of the chirp deformability $\tilde{\Lambda}=\tilde{\Lambda}(\Lambda_1,\Lambda_2)$ and the parameter $\delta \tilde{\Lambda}=\delta \tilde{\Lambda}(\Lambda_1,\Lambda_2)$~\cite{Wade:tidalCorrections}.
-Since these parameters enter the GW phase at 5 and 6PN orders respectively\footnote{A term of NPN order is proportional to $v^{2N}$ relative to the leading-order term in the expression.}, the partially break the degeneracies between $\Lambda_{1}$ and $\Lambda_{2}$.
+Since these parameters enter the GW phase at 5 and 6PN orders respectively\footnote{A term of NPN order is proportional to $v^{2N}$ relative to the leading-order term in the expression.}, they partially break the degeneracies between $\Lambda_{1}$ and $\Lambda_{2}$.
 
@@
 This is repeated for 5 future detectors, where multiple event detections become important.
-Because future events occur with weighted tidal parameters $\tilde\Lambda$ which are unknown at this time, we can not accurately combine the uncertainties on $\tilde\Lambda$ for multiple events.
+Because future events occur with chirp tidal parameter $\tilde\Lambda$ which are unknown at this time, we can not accurately combine the uncertainties on $\tilde\Lambda$ for multiple events.
 To remedy this, we re-parameterize the waveform and instead consider the $\lambda_0$ and $\lambda_1$ tidal coefficients produced by Taylor expanding the dimensionless tidal deformability $\Lambda$ about the ``canonical" reference mass of $m_0=1.4\text{ M}_{\odot}$~\cite{delPozzo:TaylorTidal,Yagi:binLove}:

### 2019-02-19 paper/bin-love-after-gw170817.tex
minor changes to Sec. III

--- 2019-02-19 paper/bin-love-after-gw170817.tex
@@
 
+{\ny{Zack, I rewrote what's below, but please check.}}
+
 We here wish to consider EoS-insensitive relations using two sets of EoSs: a ``constrained set'' consistent with the observation of GW170817 and an ``unconstrained set'' that does not impose this prior.
@@
 
-The unconstrained set is then defined by drawing random samples in the spectral coefficients (within their allowed prior ranges), and then eliminating any EoS that either leads to a polytropic index $\Gamma$ outside the allowed range, breaks the causality restriction, or breaks the maximum mass restriction.
+The unconstrained set is then defined by drawing random samples in the spectral coefficients (within their allowed prior ranges), and then eliminating any EoS that either leads to a polytropic index $\Gamma$ outside the allowed range, or breaks the causality restriction, or breaks the maximum mass restriction.
 The constrained set is defined in a similar way, with the addition of the restriction that the resulting EoS be inside the 90\% marginalized posterior distribution on the pressure-mass density plane derived from the GW170817 observation~\cite{LIGO:posterior,Carney:2018sdv}  (see Fig.~2 in~\cite{LIGO:posterior}).
-In both cases, each set consists of 100 members, with a subset of these shown in the left panel of Fig.~\ref{fig:eos}.
+In both cases, each set consists of 100 members, with a subset of these shown in Fig.~\ref{fig:eos}.
 
@@
 
+{\ny{Zack, I think the description here was wrong because the hybrid stars do not just have hadronic matter in the crust, but also in the outer core, no? Please check.}}
+
 In addition, we investigate 10 transitional quark-hadron matter stars, which undergo strong first-order phase transitions at a pressure $P_{\text{tr}}$, leading to the hadronic branch departing into a quark-matter branch at a given transitional mass~\cite{Paschalidis2018,Alford:2017qgh,1971SvA....15..347S,Zdunik:2012dj,Alford:2013aca}.
-In particular, we focus on the ACS and ACB models described in~\cite{Paschalidis2018}, and also shown in the right panel of Fig.~\ref{fig:eos}.
+In particular, we focus on the ACS and ACB models described in~\cite{Paschalidis2018}, and also shown in Fig.~\ref{fig:hybridML}.
 These result in two distinct types of NSs, based on their mass: (i) massive ($M \geq \text{ M}_{\text{tr}}$) hybrid stars which have quark-matter inner cores and nuclear matter elsewhere (henceforth, we denote such stars as hybrid stars (HSs)), and (ii) low-mass ($M \leq \text{ M}_{\text{tr}}$) hadronic stars with no internal transition to quark matter (henceforth, we denote these stars as simply NSs).
 
-\begin{figure*}
+\begin{figure}
 \begin{center} 
 \includegraphics[width=\columnwidth]{EoSs.eps}
-\includegraphics[width=\columnwidth]{hybridEoSs.eps}
-\end{center}
-\caption{(Color Online) (left) Small representative samples of the unconstrained (dotted) and constrained (solid) sets, together with the 90\% marginalized posterior distribution from the observation of GW170817 (cyan shaded region)~\cite{LIGO:posterior}.
-Observe that the there is significantly less variability in the constrained set of EoSs due to the requirement that they be consistent with the GW170817 observation.
-(right) ACS and ACB model hybrid stars investigated in our analysis, each transitioning from a hadronic branch (corresponging to a pure hadronic-matter NS) into a quark-matter branch (quark-matter inner core surrounded by hadronic matter) at various transition pressures $P_{\text{tr}}$.
+\end{center}
+\caption{(Color Online) Small representative samples of the unconstrained (dotted) and constrained (solid) sets, together with the 90\% marginalized posterior distribution from the observation of GW170817 (cyan shaded region)~\cite{LIGO:posterior}.
+Observe that the there is significantly less variability in the constrained set of EoSs due to the requirement that they be consistent with the GW170817 observation.}
+\label{fig:eos}
+\end{figure}
+
+\begin{figure}
+\begin{center} 
+\includegraphics[width=\linewidth]{hybridML.eps}
+\end{center}
+\caption{
+$M-\Lambda$ relations for the ACS and ACB class model hybrid stars. 
+Observe the transitional points where the NS transitions from the hadronic branch into a quark-matter branch.
 }
-\label{fig:eos}
-\end{figure*}
+\label{fig:hybridML}
+\end{figure}
+
+{\ny{Zack, it's a bit weird to show p-rho in Fig.
+2 (for the NSs) and then show M-Lambda in Fig.
+3 for the hybrid stars.
+Why not plot also p-rho here and make these two figures into widetext?
+I think this would make the comparison between them cleaner, specially considering that we haven't introduced Lambda yet.}}
 
@@
 
-In this section, we follow the analyses performed in Refs.~\cite{Yagi:binLove,Yagi:ILQ} with two new sets of 100 spectrally generated EoS: (i) posterior samples randomly selected from GW170817s 90\% posterior on the pressure as a function of density as shown by the solid green curves in Fig.~\ref{fig:eos}; and (ii) those unconstrained by any prior EoS information, as shown by the dotted maroon curves in Fig.~\ref{fig:eos}.
+In this section, we repeat and improve the analyses of~\cite{Yagi:binLove,Yagi:ILQ} through the use of the two sets of EoSs (the constrained and the unconstrained set) and through new fitting functions that properly limit Newtonian results.
 
@@
 
-Here we present our results on the I-Love-Q universality as compared to Fig. 1 of Ref.~\cite{Yagi:ILQ}.
+Here we present our results on the I-Love-Q universality, comparing when possible to Fig.~1 of~\cite{Yagi:ILQ}.
 In particular, we consider two distinct classes of NSs: nuclear matter EoSs and hybrid quark-hadron star EoSs as described in Sec.~\ref{sec:theory}.
 We begin in Sec.~\ref{sec:ilq-nuc} by fitting the new I-Love-Q relations using the constrained set of EoSs.
-This is followed in Sec.~\ref{sec:ilq-hyb} by an analysis and discussion into how well the hybrid star EoSs agree with the improved binary Love relations.
-
-\subsubsection{Nuclear matter stars}\label{sec:ilq-nuc}
-Following the work of Ref.~\cite{Yagi:ILQ}, the data for each EoS-insensitive relation is first fit to the following curve:
+This is followed in Sec.~\ref{sec:ilq-hyb} by an analysis and discussion of how well the hybrid star EoSs agree with the improved binary Love relations.
+
+\subsubsection{Nuclear matter stars}
+\label{sec:ilq-nuc}
+
+Following~\cite{Yagi:ILQ}, we first fit the data for each EoS-insensitive relation to the following function:
 \begin{equation}\label{eq:ILQfit}
@@
 \end{equation}
-where the updated coefficients are given in Table~\ref{tab:ILQfit}.
-Additionally, we offer an improvement to the functional form of the I-Love-Q fitting curve. 
-Namely, we use the Newtonian relationships between various observables as a controlling factor in the fit~\cite{Yagi:ILQ}:
+where $y$ and $x$ correspond to NS observables $\bar{I}$, $\bar{Q}$, and $\Lambda$, and the updated coefficients are given in Table~\ref{tab:ILQfit}.
+This fitting function, however, does not limit properly to the Newtonian results~\cite{Yagi:ILQ}:
 \begin{equation}\label{eq:Newtonian}
-\bar{I}^{\text{N}} = K_{\bar{I}\Lambda}\Lambda^{2/5}, \hspace{3mm} \bar{Q}^{\text{N}} = K_{\bar{Q}\Lambda}\Lambda^{1/5}, \hspace{3mm} \bar{I}^{\text{N}} = K_{\bar{I}\bar{Q}}\bar{Q}^{2}.
-\end{equation}
-This is appended to an expansion in $\Lambda^{-1/5} \propto C$, where $C=M/R$ is the compactness of the star.
-This results in the following overall fitting relation:
+\bar{I}^{\text{N}} = K_{\bar{I}\Lambda}\Lambda^{2/5}, \hspace{3mm} \bar{Q}^{\text{N}} = K_{\bar{Q}\Lambda}\Lambda^{1/5}, \hspace{3mm} \bar{I}^{\text{N}} = K_{\bar{I}\bar{Q}}\bar{Q}^{2},
+\end{equation}
+where $\Lambda^{-1/5} \sim C$ when $C \ll 1$. One can thus improve the fitting function to 
 \begin{equation}\label{eq:ILQfitNew}
@@
 \end{equation}
-where $y$ and $x$ correspond to NS observables $\bar{I}$, $\bar{Q}$, and $\Lambda$, and $\alpha$ is given by $2/5$, $1/5$, and $2$ for the $\bar{I}-\Lambda$, $\bar{Q}-\Lambda$, and $\bar{I}-\bar{Q}$ relations, respectively.
-The new fitting coefficients are presented in Table~\ref{tab:ILQfitNew}.
-While the two above curves both result in fits with similar $R^2$ values\footnote{$R^2$ is the coefficient of determination, defined as $\sum_i(f_i-\bar{y})^2/\sum_i(y_i-\bar{y})^2$, where $\bar{y}$ is the mean data value, and $f_i$, $y_i$ are the modeled and actual data values} of $\sim 0.999995$ for the data presented, the latter has the advantage that it properly limits to the Newtonian case as $\Lambda \rightarrow \infty$~\cite{Yagi:binLove}.
-
+where $\alpha$ is either $2/5$, $1/5$, or $2$ for the $\bar{I}-\Lambda$, $\bar{Q}-\Lambda$, and $\bar{I}-\bar{Q}$ relations respectively, and where the new fitting coefficients are presented in Table~\ref{tab:ILQfitNew}.
+While the two fits result in similar $R^2$ values\footnote{$R^2$ is the coefficient of determination, defined as $\sum_i(f_i-\bar{y})^2/\sum_i(y_i-\bar{y})^2$, where $\bar{y}$ is the mean data value, and $f_i$, $y_i$ are the modeled and actual data values} of $\sim 0.999995$, the fit in Eq.~\eqref{eq:ILQfitNew} has the advantage that it properly limits to the Newtonian result as $\Lambda \gg 1$~\cite{Yagi:binLove}.
+
+{\ny{Too many tables. Please combine Tables 1 and 2 into a single table and change the notation of the fits appropriately.}}
 \begin{table*}
@@
 Observe how the agreement with the fit is quite good at low pressures (large $\Lambda_s$) where the the binaries consist of NS/NS combinations (here, both stars' EoSs consist of the same class of nuclear matter as the constrained EoSs).
-Once the critical pressure is reached, one or both stars transition into the hybrid branches, resulting in large reductions in tidal deformability as shown in the right panel of Fig.~\ref{fig:eos}.
+Once the critical pressure is reached, one or both stars transition into the hybrid branches, resulting in large reductions in tidal deformability as shown in Fig.~\ref{fig:hybridML}.
 When one star lies on the hadronic-matter branch while the other is on the quark-matter branch, 

### 2019-02-19 paper/bin-love-after-gw170817.tex
merged changes

@@
 These parameters, however, enter the GW Fourier model multiplied by the same function of the GW frequency (at leading post-Newtonian order), making them degenerate, and thus, very difficult to estimate independently with current GW data~\cite{Wade:tidalCorrections}.
-Instead, one can extract certain combinations of the tidal deformabilities, like the so-called \emph{chirp deformability} $\tilde{\Lambda}$~\cite{Favata:2013rwa,Wade:tidalCorrections}, or one can extract the (mass-independent) coefficients $(\lambda_{0},\lambda_{1},\ldots)$ of a Taylor expansion of the tidal deformabilities about some fiducial mass~\cite{delPozzo:TaylorTidal,Yagi:binLove}.
+Instead, one can extract certain combinations of the tidal deformabilities, like a certain mass-weighted tidal deformability $\tilde{\Lambda}$~\cite{Favata:2013rwa,Wade:tidalCorrections}, or one can extract the (mass-independent) coefficients $(\lambda_{0},\lambda_{1},\ldots)$ of a Taylor expansion of the tidal deformabilities about some fiducial mass~\cite{delPozzo:TaylorTidal,Yagi:binLove}.
 Current detectors are not sensitive enough to accurately measure any of these coefficients, but future detectors will and the information from multiple events could then be combined, since the Taylor expansion coefficient should be common to all events.
@@
 %Universal relations
-Lacking enough sensitivity in current GW observations, one is forced to only estimate the chirp deformability, but this prevents the independent extraction of $\Lambda_{1}$ and $\Lambda_{2}$.
-Yagi and Yunes~\cite{Yagi:binLove} solved this problem by finding ``approximately universal'' or ``EoS-insensitive'' relations between the symmetric and anti-symmetric combinations of the tidal deformabilities $\Lambda_{s,a}=\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$, the so-called ``binary Love relations." These relations can be used to analytically express $\Lambda_{s}$ in terms of $\Lambda_{a}$ (or vice-versa), making the chirp deformability a function of only $\Lambda_{a}$.
-A measurement of the chirp deformability then implies a measurement of $\Lambda_{a}$, and through the use of the binary Love relations, also a measurement of $\Lambda_{s}$, which then allows for the inference of the individual tidal deformabilities $\Lambda_{1}$ and $\Lambda_{2}$~\cite{Yagi:binLove}.
+Lacking enough sensitivity in current GW observations, one is forced to only estimate the mass-weighted tidal deformability, but this prevents the independent extraction of $\Lambda_{1}$ and $\Lambda_{2}$.
+Yagi and Yunes~\cite{Yagi:binLove} solved this problem by finding ``approximately universal'' or ``EoS-insensitive'' relations between the symmetric and anti-symmetric combinations of the tidal deformabilities $\Lambda_{s,a}=\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$, the so-called ``binary Love relations." These relations can be used to analytically express $\Lambda_{s}$ in terms of $\Lambda_{a}$ (or vice-versa), making the mass-weighted tidal deformability a function of only $\Lambda_{a}$.
+A measurement of the mass-weighted tidal deformability then implies a measurement of $\Lambda_{a}$, and through the use of the binary Love relations, also a measurement of $\Lambda_{s}$, which then allows for the inference of the individual tidal deformabilities $\Lambda_{1}$ and $\Lambda_{2}$~\cite{Yagi:binLove}.
 With those at hand, one can further use EoS-insensitive relations between the tidal deformabilities and the compactness, the so-called ``C-Love relations''~\cite{Yagi:ILQ}, to infer the radii of the NSs, and thus, to place two constraints in the mass-radius plane, one for each star in the binary~\cite{Yagi:binLove}.
@@
 We find that the I-Love-Q and C-Love relations remain EoS-insensitive for these hybrid stars, although the EoS variability increases slightly (see Sec.~\ref{sec:ilq-hyb} and~\ref{sec:clove-hyb} for more details).
-However, we also find that the binary Love relations are not EoS-insensitive for a mixed binary with a (massive) hybrid star and a (low-mass) hadronic star, due to the large separation in chirp deformability between the constituent stars (see Sec.~\ref{sec:binary} for more details).
+However, we also find that the binary Love relations are not EoS-insensitive for a mixed binary with a (massive) hybrid star and a (low-mass) hadronic star, due to the large separation in mass-weighted tidal deformability between the constituent stars (see Sec.~\ref{sec:binary} for more details).
 
@@
 
+\begin{figure*}
+\begin{center} 
+\includegraphics[width=\columnwidth]{EoSs.eps}
+\includegraphics[width=\columnwidth]{hybridEoSs.eps}
+\end{center}
+\caption{(Color Online) Left: Small representative samples of the unconstrained (dotted) and constrained (solid) sets, together with the 90\% marginalized posterior distribution from the observation of GW170817 (cyan shaded region)~\cite{LIGO:posterior}.
+Observe that the there is significantly less variability in the constrained set of EoSs due to the requirement that they be consistent with the GW170817 observation.
+Right: EoSs for ACS and ACB hybrid stars, each transitioning from a hadronic branch (corresponding to a pure hadronic-matter NS) into a quark-matter branch (quark-matter inner core surrounded by hadronic matter) at various transition pressures $P_{\text{tr}}$.
+}
+\label{fig:eos}
+\end{figure*}
+
 We here wish to consider EoS-insensitive relations using two sets of EoSs: a ``constrained set'' consistent with the observation of GW170817 and an ``unconstrained set'' that does not impose this prior.
@@
 
-\begin{figure*}
-\begin{center} 
-\includegraphics[width=\columnwidth]{EoSs.eps}
-\includegraphics[width=\columnwidth]{hybridEoSs.eps}
-\end{center}
-\caption{(Color Online) (left) Small representative samples of the unconstrained (dotted) and constrained (solid) sets, together with the 90\% marginalized posterior distribution from the observation of GW170817 (cyan shaded region)~\cite{LIGO:posterior}.
-Observe that the there is significantly less variability in the constrained set of EoSs due to the requirement that they be consistent with the GW170817 observation.
-(right) ACS and ACB model hybrid stars investigated in our analysis, each transitioning from a hadronic branch (corresponging to a pure hadronic-matter NS) into a quark-matter branch (quark-matter inner core surrounded by hadronic matter) at various transition pressures $P_{\text{tr}}$.
-}
-\label{fig:eos}
-\end{figure*}
-
 \subsection{NS Tidal deformability}\label{tidal}
@@
 However, the waveform templates can be strategically reparameterized to instead include independent linear combinations of $\Lambda_1$ and $\Lambda_2$ that mitigate correlations.
-One common reparameterization is through the introduction of the chirp deformability $\tilde{\Lambda}=\tilde{\Lambda}(\Lambda_1,\Lambda_2)$ and the parameter $\delta \tilde{\Lambda}=\delta \tilde{\Lambda}(\Lambda_1,\Lambda_2)$~\cite{Wade:tidalCorrections}.
+One common reparameterization is through the introduction of the mass-weighted tidal deformability $\tilde{\Lambda}=\tilde{\Lambda}(\Lambda_1,\Lambda_2)$ and the parameter $\delta \tilde{\Lambda}=\delta \tilde{\Lambda}(\Lambda_1,\Lambda_2)$~\cite{Wade:tidalCorrections}.
 Since these parameters enter the GW phase at 5 and 6PN orders respectively\footnote{A term of NPN order is proportional to $v^{2N}$ relative to the leading-order term in the expression.}, they partially break the degeneracies between $\Lambda_{1}$ and $\Lambda_{2}$.
@@
 This is repeated for 5 future detectors, where multiple event detections become important.
-Because future events occur with chirp tidal parameter $\tilde\Lambda$ which are unknown at this time, we can not accurately combine the uncertainties on $\tilde\Lambda$ for multiple events.
+Because future events occur with mass-weighted tidal deformability $\tilde\Lambda$ which are unknown at this time, we can not accurately combine the uncertainties on $\tilde\Lambda$ for multiple events.
 To remedy this, we re-parameterize the waveform and instead consider the $\lambda_0$ and $\lambda_1$ tidal coefficients produced by Taylor expanding the dimensionless tidal deformability $\Lambda$ about the ``canonical" reference mass of $m_0=1.4\text{ M}_{\odot}$~\cite{delPozzo:TaylorTidal,Yagi:binLove}:

### 2019-02-19 paper/bin-love-after-gw170817.tex
up to Sec. IIIB

@@
 Given a measurement of the Love number for a given NS, for example through GW observations, the I-Love-Q relations can be used to infer the moment of inertia or the quadrupole moment.
-A second independent measurement of either of these two quantities, for example through binary pulsar observations~\cite{Lattimer:2004nj} or observations with the Neutron star Interior Composition ExploreR (NICER)~\cite{Ozel:2015ykl}, then allows an EoS-insensitive test of General Relativity in the strong field regime~\cite{Yagi:ILQ}.
+A second independent measurement of either of these two quantities, for example through binary pulsar observations~\cite{Lattimer:2004nj} or observations with the Neutron star Interior Composition ExploreR (NICER)~\cite{Ozel:2015ykl}, then allows an EoS-insensitive test of General Relativity in the strong field regime~\cite{Yagi:ILQ,Gupta:2017vsl}.
 
@@
 Similar EoS-insensitive relations have been found between individual NS observables: the moment of inertia (I), the tidal deformability (Love), the quadrupole moment (Q), and the compactness (C), known as the ``I-Love-Q" and ``C-Love" relations~\cite{Yagi:ILQ, Yagi:binLove}.
-These relations are EoS-insensitive to better than 1\% and 6\% respectively, and they have been important applications in both GW astrophysics and experimental relativity.
+These relations are EoS-insensitive to better than 1\% and 6\% respectively, and they have been important applications in both GW astrophysics~\cite{Kumar:2019xgp} and experimental relativity~\cite{Gupta:2017vsl}.
 For example, these relations and the measurement of the tidal deformabilities allow for the inference of several other stellar properties, such as the moment of inertia, the  compactness, the spin ($\chi$), and the radius of NSs~\cite{Kumar:2019xgp}.
@@
 
+\begin{table*}[htb]
+\centering
+\begin{tabular}{ c  c  | c c c c c c c c c c} 
+ \hline
+ \hline
+ $y$ & $x$ & $\alpha$ & $K_{yx}$ & $a_1$ & $a_2$ & $a_3$ & $a_{4}$ & $a_{5}$ & $b_1$ & $b_2$ & $b_3$ \\
+ \hline
+  $\bar{I}$ & $\Lambda$ & (--) & (--) & $1.493$ & $0.06410$ & $0.02085$ & $-5.018 \times 10^{-4}$ & $3.16 \times 10^{-7}$ & (--) & (--) & (--)  \\
+ $\bar{Q}$ & $\Lambda$ & (--) & (--) & $0.2093$ & $0.07404$ & $-0.05382$ & $-5.018 \times 10^{-3}$ & $1.576 \times 10^{-4}$ & (--)  &(--)  & (--) \\ 
+  $\bar{I}$ & $\bar{Q}$ & (--) & (--) & $1.383$ & $0.5931$ & $-0.02161$ & $0.04190$ & $-2.968 \times 10^{-3}$ &(--)  &(--) & (--) \\
+ \hline 
+ $\bar{I}$ & $\Lambda$ & $2/5$ & $0.5313$ & $1.287$ & $0.09888$ & $-2.300$ & (--) & (--) & $-1.347$ & $0.3857$ & $-0.02870$\\
+ $\bar{Q}$ & $\Lambda$ & $1/5$ & $3.555$ & $-2.122$ & $2.72$ & $-1.491$ & (--) & (--) & $0.8644$ & $-0.1428$ & $-1.397$\\
+ $\bar{I}$ & $\bar{Q}$ & $2$ & $0.008921$ & $10.59$ & $-37.46$ & $43.18$ &(--)  &(--)  & $-2.361$ & $1.967$ & $-0.5678$\\
+ $C$ & $\Lambda$ & $-1/5$ & $0.2496$ & $-919.6$ & $330.3$ & $-857.2$ & (--) & (--) & $-383.5$ & $192.5$ & $-811.1$\\
+\hline
+\hline
+\end{tabular}
+\caption{
+Fit parameters for the I-Love-Q and C-Love relations using the constrained set and the fitting functions in Eq.~\eqref{eq:ILQfit} (top) and in Eq.~\eqref{eq:ILQfitNew} (bottom).
+}\label{tab:ILQfitNew}
+\end{table*}
+
 \section{EoS-insensitive relations}
@@
 \begin{equation}\label{eq:ILQfit}
-\ln{y_i}=a_i+b_i \ln{x_i} + c_i (\ln{x_i})^2 + d_i (\ln{x_i})^3 + e_i (\ln{x_i})^4,
-\end{equation}
-where $y$ and $x$ correspond to NS observables $\bar{I}$, $\bar{Q}$, and $\Lambda$, and the updated coefficients are given in Table~\ref{tab:ILQfit}.
+\ln{y}=a_{1}+a_{2} \ln{x} + a_{3} (\ln{x})^2 + a_{4} (\ln{x})^3 + a_{5} (\ln{x})^4,
+\end{equation}
+where $y$ and $x$ correspond to NS observables $\bar{I}$, $\bar{Q}$, and $\Lambda$, and the updated coefficients are given in the top of Table~\ref{tab:ILQfitNew}.
 This fitting function, however, does not limit properly to the Newtonian results~\cite{Yagi:ILQ}:
@@
 \end{equation}
-where $\alpha$ is either $2/5$, $1/5$, or $2$ for the $\bar{I}-\Lambda$, $\bar{Q}-\Lambda$, and $\bar{I}-\bar{Q}$ relations respectively, and where the new fitting coefficients are presented in Table~\ref{tab:ILQfitNew}.
+where $\alpha$ is either $2/5$, $1/5$, or $2$ for the $\bar{I}-\Lambda$, $\bar{Q}-\Lambda$, and $\bar{I}-\bar{Q}$ relations respectively, and where the new fitting coefficients are presented in the bottom of Table~\ref{tab:ILQfitNew}.
 While the two fits result in similar $R^2$ values\footnote{$R^2$ is the coefficient of determination, defined as $\sum_i(f_i-\bar{y})^2/\sum_i(y_i-\bar{y})^2$, where $\bar{y}$ is the mean data value, and $f_i$, $y_i$ are the modeled and actual data values} of $\sim 0.999995$, the fit in Eq.~\eqref{eq:ILQfitNew} has the advantage that it properly limits to the Newtonian result as $\Lambda \gg 1$~\cite{Yagi:binLove}.
 
-{\ny{Too many tables. Please combine Tables 1 and 2 into a single table and change the notation of the fits appropriately.}}
-\begin{table*}
-\centering
-\caption{
-Updated fit parameters for the I-Love-Q relations, fitted to the constrained EoS data by the curve found in Eq.~\ref{eq:ILQfit}.
-}\label{tab:ILQfit}
-\begin{tabular}{ c  c | c c c c c } 
- \hline
- \hline
- $y_i$ & $x_i$ & $a_i$ & $b_i$ & $c_i$ & $d_i$ & $e_i$ \\
- \hline
- $\bar{I}$ & $\Lambda$ & $1.493$ & $0.06410$ & $0.02085$ & $-5.018 \times 10^{-4}$ & $3.16 \times 10^{-7}$ \\
- $\bar{Q}$ & $\Lambda$ & $0.2093$ & $0.07404$ & $-0.05382$ & $-5.018 \times 10^{-3}$ & $1.576 \times 10^{-4}$ \\ 
-  $\bar{I}$ & $\bar{Q}$ & $1.383$ & $0.5931$ & $-0.02161$ & $0.04190$ & $-2.968 \times 10^{-3}$ \\
- \hline
- \hline
-\end{tabular}
-\end{table*}
-
-\begin{table*}
-\centering
-\caption{
-I-Love-Q and C-Love, relations fit parameters for the constrained EoS data using the improved fitting relations found in Eq.~\ref{eq:ILQfitNew}.
-This fitting relation, unlike previous versions, properly limits to the Newtonian case as $\Lambda \rightarrow \infty$.
-}\label{tab:ILQfitNew}
-\begin{tabular}{ c  c  | c c c c c c c c} 
- \hline
- \hline
- $y$ & $x$ & $\alpha$ & $K_{yx}$ & $a_1$ & $a_2$ & $a_3$ & $b_1$ & $b_2$ & $b_3$ \\
- \hline
- $\bar{I}$ & $\Lambda$ & $2/5$ & $0.5313$ & $1.287$ & $0.09888$ & $-2.300$ & $-1.347$ & $0.3857$ & $-0.02870$\\
- $\bar{Q}$ & $\Lambda$ & $1/5$ & $3.555$ & $-2.122$ & $2.72$ & $-1.491$ & $0.8644$ & $-0.1428$ & $-1.397$\\
- $\bar{I}$ & $\bar{Q}$ & $2$ & $0.008921$ & $10.59$ & $-37.46$ & $43.18$ & $-2.361$ & $1.967$ & $-0.5678$\\
- $C$ & $\Lambda$ & $-1/5$ & $0.2496$ & $-919.6$ & $330.3$ & $-857.2$ & $-383.5$ & $192.5$ & $-811.1$\\
-\hline
-\hline
-\end{tabular}
-\end{table*}
-
-Figure~\ref{fig:ILQ} shows the improved I-Love-Q relations between the dimensionless moment of inertia $\bar{I} \equiv I/M^3$, the dimensionless quadrupole moment $\bar{Q} \equiv Q/M^3$, and the dimensionless tidal deformability $\Lambda$ for both the constrained and unconstrained sets of EoSs.
-Here, each category of EoS are fit individually using the curve found in Eq.~\ref{eq:ILQfitNew}.
-We observe that the constrained EoSs show considerable improvement from the unconstrained EoSs.
-Additionally, we note a large improvement from the results of previous works~\cite{Yagi:ILQ}.
-This is validated in Tab.~\ref{tab:maxVar}, where the maximal EoS variation from each fit is tabulated; comparing the results of previous works to the unconstrained and constrained sets of EoSs.
-Observe how the constrained EoSs outperform both other cases by a considerable amount for each I-Love-Q relation.
-
-\begin{figure*}
+Figure~\ref{fig:ILQ} shows the improved I-Love-Q relations between the dimensionless moment of inertia $\bar{I} \equiv I/M^3$, the dimensionless quadrupole moment $\bar{Q} \equiv Q/M^3$, and the dimensionless tidal deformability $\Lambda$.
+The fits are done using the new fitting function in Eq.~\eqref{eq:ILQfitNew} and over either the constrained set or the unconstrained set separately.
+The bottom panels show the relative fractional difference between the fit and the data for each set of EoSs.
+Observe that the new fits to the constrained set shows considerable more EoS-insensitivity than that fit to the unconstrained set.
+These results are summarized in Table~\ref{tab:maxVar}, which tabulates the maximum EoS variation in each fit.
+Clearly then, the EoS-insensitive relations can be made more universal by restricting the EoSs through the use of observations.
+Such improvements can be beneficial to future studies in GW astrophysics, such as those of~\cite{Kumar:2019xgp}, and in experimental relativity, such as those of~\cite{Gupta:2017vsl}.
+
+\begin{figure*}[htb]
 \begin{center} 
@@
 
-\begin{table}
+\begin{table}[htb]
 \centering
-\caption{
-Comparison between the EoS-insensitive relations (I-Love-Q, C-Love, R-Love, and binary Love) maximal EoS variability for the results of previous works~\cite{Yagi:ILQ,Yagi:binLove}, and the unconstrained and constrained sets of EoSs analyzed here.
-The maximum EoS variation, given by the largest fractional difference (the absolute difference is also shown in parenthesis for the C-Love, R-Love, and binary Love fits) from the fits as shown in Figs.~\ref{fig:ILQ},~\ref{fig:clove},~\ref{fig:rlove} and~\ref{fig:binLove}, observes a considerable improvement for the constrained set of EoSs, compared to the unconstrained set as well as that found in previous works.
-Additionally, note how the maximal EoS variation for the unconstrained set of EoSs is slightly larger than that found in Refs.~\cite{Yagi:ILQ,Yagi:binLove} - due to the effects of large random sampling taking into account more sources of uncertainty.
-}\label{tab:maxVar}
 \begin{tabular}{ c  || c c c } 
@@
  $\bar{I}-\bar{Q}$ & $0.012$ & $0.01490$ & $0.005716$\\
- \hline
- \noalign{\smallskip}
-\noalign{\smallskip}
- \noalign{\smallskip}
-\noalign{\smallskip}
-\hline
- \hline
- \textbf{EoS-insensitive} & \multicolumn{3}{c}{\textbf{Maximal EoS Variability}} \\
- \cline{2-4}
- \textbf{Relation} & \multicolumn{1}{c|}{\emph{Previous}} & \multicolumn{1}{c|}{\emph{Unconstrained}} & \emph{Constrained}\\
  \hline
@@
 \end{tabular}
+\caption{Maximum relative and fractional EoS variation in the I-Love-Q, C-Love, R-Love, and binary Love relations using the unconstrained set, the constrained set and variations reported in previous work~\cite{Yagi:ILQ,Yagi:binLove}.
+The maximum absolute EoS variation is also reported in the C-Love, R-Love and binary Love cases in parenthesis.
+Observe that the maximum variation in the constrained set case is better than a factor of two smaller than the variability in the unconstrained case and in previous work.
+The maximum EoS variation in the unconstrained set is slightly larger than that found in previous work because the former is built from a large random sampling of EoSs.
+{\ny{Do we really need these many significant digits?}}
+}\label{tab:maxVar}
 \end{table}
-
-These results indicate that EoS-insensitive relations can indeed be greatly improved upon by restricting to EoSs in agreeance with physical observations.
-In addition, we confirm the validity of this method by noting that the unconstrained EoSs observe more EoS variability than that found in Ref.~\cite{Yagi:ILQ} due to the nature of large random sampling taking into account more sources of uncertainty than was previously studied.
-On the other hand, the constrained set of EoSs show significant improvement from that found in previous works.
-This improvement can be beneficial to many future analyses, such as improvements to the constraints found on the moment of inertia, tidal deformability, compactness, spin, and radius found in Ref.~\cite{Kumar:2019xgp}.
 
@@
 
-In this section, we investigate the I-Love-Q universality of hybrid stars, and their compatibility with their nuclear matter counterparts.
-We consider three different sets of data to be fit by Eq.~\ref{eq:ILQfitNew}:
+Let us now focus on the I-Love-Q relations of hybrid stars, and their compatibility with their nuclear matter counterparts.
+For concreteness, we consider three different sets of EoSs in the hybrid case:
 \begin{enumerate}
@@
 \end{enumerate}
-Following this, we compute the fractional difference from the fits for all three cases for the 10 hybrid star EoSs.
-The fractional differences for the second case (fit to only the constrained EoSs) is shown by the dashed green lines in Fig.~\ref{fig:ILQ} for example.
-For comparison purposes, Tab.~\ref{tab:hybridCompare} displays the maximal EoS variation in the $I-\Lambda$ relation for both the constrained and hybrid star EoSs in each case.
-
-\begin{table}
+For each of these cases, we compute the I-Love-Q relations, we fit the data to Eq.~\eqref{eq:ILQfitNew} and we compute the relative fractional difference.
+
+\begin{table}[htb]
 \centering
-\caption{
-Comparison between the $I-\Lambda$ maximal EoS variability (fractional difference from the fit) for the constrained EoSs and the hybrid EoSs for three different cases of fitting data to Eq.~\ref{eq:ILQfitNew}: (1) fit to the combined data of constrained and hybrid EoS, (2) fit to the constrained EoS data alone, and (3) fit to the hybrid EoS data alone.
-Observe how for all 3 cases, the hybrid EoSs are only universal up to a minimum of $\sim1$\%, while in each case the constrained EoSs outperform the hybrid ones.
-The second case is demonstrated in Fig.~\ref{fig:ILQ}.
-}\label{tab:hybridCompare}
 \begin{tabular}{ c  || c c } 
@@
 \end{tabular}
+\caption{
+Maximum relative and fractional EoS variation in the I-Love relation, fitting to three different sets of data: using the constrained set plus hybrid EoSs, using the constrained set alone, EoS data alone, and using only the hybrid EoSs.
+In all 3 cases the hybrid EoSs are EoS-insensitive to $\sim1$\%, which is a slight decrease in universality relative to the hadronic only EoSs.
+{\ny{Do we really need these many significant digits?}}
+}\label{tab:hybridCompare}
 \end{table}
 
-Observe how the hybrid star EoSs obey the I-Love-Q relations in each case by up to $\sim1.7$\%, slightly higher than that found for nuclear matter EoSs in previous works~\cite{Yagi:ILQ}.
-Further, we observe that the universality can not be improved by much through the introduction of new fits, only bringing the maximal EoS variation down to $\sim1$\% for the fits constructed with only hybrid star EoSs.
-Concluding, we claim that hybrid star EoSs \emph{do} obey the traditional nuclear I-Love-Q relations computed through nuclear EoS data, with a slight decrease in universality to $\sim1.7$\%.
+The fractional differences for the second case (fit to only the constrained EoSs) is shown with dashed green lines in Fig.~\ref{fig:ILQ}, while the maximum EoS variation for the I-Love relation is shown in Table~\ref{tab:hybridCompare} for both the constrained and hybrid star cases.
+Observe how the hybrid star EoSs obey the I-Love-Q relations in each case to better than $\sim1.7$\%, a variability that is slightly higher than that found when using only nuclear matter EoSs in previous works~\cite{Yagi:ILQ}.
+Observe also that the universality cannot be improved much through the introduction of new fits, only bringing the maximal EoS variation down to $\sim1$\% for the fits constructed with only hybrid star EoSs.
+From this study, we conclude that hybrid star EoSs \emph{do} obey the traditional nuclear I-Love-Q relations computed with nuclear EoS data, albeit with a slight decrease in universality to $\sim1.7$\%.
 

### 2019-02-20 paper/bin-love-after-gw170817.tex
added hybrid star eoss
changed sig figs on errors
merging

@@
 
+\zc{Just adding a note here so I don't forget to decide/change the sig figs we use throughout the paper.}
 %Intro
@@
 Right: EoSs for ACS and ACB hybrid stars, each transitioning from a hadronic branch (corresponding to a pure hadronic-matter NS) into a quark-matter branch (quark-matter inner core surrounded by hadronic matter) at various transition pressures $P_{\text{tr}}$.
+{\ny{There shouldn't be a title in the figures, no?}}
 }
@@
 The maximum EoS variation in the unconstrained set is slightly larger than that found in previous work because the former is built from a large random sampling of EoSs.
-{\ny{Do we really need these many significant digits?}}
 }\label{tab:maxVar}
@@
 In all 3 cases the hybrid EoSs are EoS-insensitive to $\sim1$\%, which is a slight decrease in universality relative to the hadronic only EoSs.
-{\ny{Do we really need these many significant digits?}}
 }\label{tab:hybridCompare}
@@
 
-In this section we consider approximately EoS-insensitive C-Love relations between the NS compactness $C \equiv M/R$ and the unit-less tidal deformability $\Lambda$, as discussed by Yagi and Yunes in ref.~\cite{Yagi:binLove}.
-Additionally in this section, we compute the relationship between the NS radius and tidal deformability from the C-Love relations.
-This allows one to compare the approximate uncertainty on the NS radius computed from the C-Love relations for both the constrained and unconstrained sets of EoSs. 
-Similar to the previous section, we consider two classes of stars in this section: nuclear matter EoSs and hybrid quark-hadron star EoSs.
+In this subsection we focus on the EoS-insensitive C-Love relations, as introduced by Yagi and Yunes in~\cite{Yagi:binLove}, as well as on the R-Love relations, since these play a key role in GW data analysis for the extraction of M-R credible intervals.
+As in the previous subsection, we consider both nuclear matter EoSs, as well as hybrid quark-hadron star EoSs.
 
@@
 
-Following Ref.~\cite{Yagi:binLove}, we begin by fitting the data for each set of EoSs to the simple curve:
+Following Ref.~\cite{Yagi:binLove}, we begin by fitting the data for each set of EoSs to the simple curve
 \begin{equation}
@@
 \end{equation}
-Doing so yields $a_0 = 0.3617$, $a_1 = -0.03548$, and $a_2 = 0.0006194$, similar to that found in Ref.~\cite{Yagi:binLove}.
-Additionally we offer an improvement to the fits as was done in Sec.~\ref{sec:ilq}, by considering the fitting function found in Eq.~\ref{eq:ILQfitNew}, with the controlling factor given by:
+Doing so, yields $a_0 = 0.3617$, $a_1 = -0.03548$, and $a_2 = 0.0006194$, similar to what was found in~\cite{Yagi:binLove} {\ny{Wait, this is for the constrained set or the unconstrained set?
+I'm guessing you used the constrained set, but we should say so here.}}.
+As in the I-Love-Q case, however, the above fitting function does not limit properly to the Newtonian result
 \begin{equation}
@@
 \end{equation}
-The new fitting coefficients are displayed in Tab.~\ref{tab:ILQfitNew}, alongside the previously found I-Love-Q relations.
+We thus repeat the fit using Eq.~\ref{eq:ILQfitNew} as the fitting function, with the new fitting coefficients presented in Table~\ref{tab:ILQfitNew}.
 

### 2019-02-20 paper/bin-love-after-gw170817.tex
done with Sec. III

@@
 
-\zc{Just adding a note here so I don't forget to decide/change the sig figs we use throughout the paper.}
 %Intro
@@
  \hline
- $\bar{I}-\Lambda$ &  $0.0059$ & $0.007673$ & $0.003138$\\
- $\bar{Q}-\Lambda$ & $0.010$ & $0.01262$ & $0.004661$\\
- $\bar{I}-\bar{Q}$ & $0.012$ & $0.01490$ & $0.005716$\\
- \hline
- \multirow{2}{*}{$C-\Lambda$} & $0.065$ & $0.07198$ & $0.02169$\\
- & (--) & ($0.01837$) & ($0.006582$)\\
-  \hline
- \multirow{2}{*}{$R-\Lambda$} & -- & $0.05649$ & $0.02172$\\
- & (--) & ($881.4 \text{ m}$) & ($358.9 \text{ m}$) \\
- \hline
- $\Lambda_a-\Lambda_s$ & $\sim0.50$ & $0.5724$ & $0.2140$\\
- $q=0.90$ & (--) & ($190.1$) & ($37.23$) \\
+ $\bar{I}-\Lambda$ &  $0.0059$ & $0.0077$ & $0.0031$\\
+ $\bar{Q}-\Lambda$ & $0.010$ & $0.013$ & $0.0047$\\
+ $\bar{I}-\bar{Q}$ & $0.012$ & $0.015$ & $0.0057$\\
+ \hline
+ \multirow{2}{*}{$C-\Lambda$} & $0.065$ & $0.072$ & $0.022$\\
+ & (--) & ($0.018$) & ($0.0066$)\\
+  \hline
+ \multirow{2}{*}{$R-\Lambda$} & -- & $0.056$ & $0.022$\\
+ & (--) & ($880 \text{ m}$) & ($360 \text{ m}$) \\
+ \hline
+ $\Lambda_a-\Lambda_s$ & $\sim0.50$ & $0.57$ & $0.21$\\
+ $q=0.90$ & (--) & ($190$) & ($37$) \\
  \cline{1-1}
- $\Lambda_a-\Lambda_s$ & $\sim0.20$ & $0.2447$ & $0.08284$\\
-  $q=0.7$ & (--) & ($320.4$) & ($51.62$) \\
+ $\Lambda_a-\Lambda_s$ & $\sim0.20$ & $0.25$ & $0.083$\\
+  $q=0.7$ & (--) & ($320$) & ($52$) \\
   \cline{1-1}
- $\Lambda_a-\Lambda_s$ & $\sim0.025$ & $0.03841$ & $0.01823$\\
-  $q=0.50$ & (--) & ($244.1$) & ($28.96$) \\
+ $\Lambda_a-\Lambda_s$ & $\sim0.025$ & $0.038$ & $0.018$\\
+  $q=0.50$ & (--) & ($240$) & ($29$) \\
   \cline{1-1}
@@
  \hline
- \emph{Combined} &  \multirow{2}{*}{$0.004407$} & \multirow{2}{*}{$0.01363$}\\
+ \emph{Combined} &  \multirow{2}{*}{$0.0044$} & \multirow{2}{*}{$0.014$}\\
  \emph{(Case 1)} & &\\
  \cline{1-1}
- \emph{Constrained only} & \multirow{2}{*}{$0.003138$} & \multirow{2}{*}{$0.01736$}\\
+ \emph{Constrained only} & \multirow{2}{*}{$0.0031$} & \multirow{2}{*}{$0.017$}\\
   \emph{(Case 2)} & &\\
   \cline{1-1}
- \emph{Hybrid only} & \multirow{2}{*}{$0.008400$} & \multirow{2}{*}{$0.01017$}\\
+ \emph{Hybrid only} & \multirow{2}{*}{$0.0084$} & \multirow{2}{*}{$0.010$}\\
   \emph{(Case 3)} & &\\
@@
 
+\begin{figure*}
+\begin{center} 
+\includegraphics[width=\columnwidth]{CL.eps}
+\includegraphics[width=\columnwidth]{RL.eps}
+\end{center}
+\caption{
+Similar to Fig.~\ref{fig:ILQ} but for the C-Love (left) and the R-Love relations (right), with the bottom panels showing the \emph{absolute differences} (rather than fractional difference as in Fig.~\ref{fig:ILQ}) from the fit.
+Observe how the absolute difference is suppressed in the constrained set case relative to the unconstrained set, and results from previous work~\cite{Yagi:binLove}.
+In the left panel, we also present the C-Love relations in the hybrid star cases (dashed green) for comparison, where observe that, although still EoS-insensitive, the degree of universality decreases.
+{\ny{Why is the size of the right panel larger than the left panel?}}
+}
+\label{fig:clove}
+\end{figure*}
+
 \subsection{C-Love Relations}
@@
 
-Figure~\ref{fig:clove} presents the C-Love relations for both the constrained and unconstrained sets of EoSs, along with the corresponding absolute differences from the fits. 
-Observe how the constrained EoSs show a large suppression in EoS variability compared to the unconstrained EoSs, as well as to that found in previous works~\cite{Yagi:binLove}.
-The maximal EoS variation is compared between the above three cases in Tab.~\ref{tab:maxVar}.
-\begin{figure}
-\begin{center} 
-\includegraphics[width=\columnwidth]{CL.eps}
-\end{center}
-\caption{
-Similar to Fig.~\ref{fig:ILQ} but for the C-Love relations, and the absolute differences (rather than fractional) from the fit.
-In this figure, we similarly construct fits to  Eq.~\ref{eq:ILQfitNew}, properly limiting to the Newtonian case $C \sim \Lambda^{-1/5}$.
-Observe how, as before, the absolute difference from the fits is greatly suppressed for the constrained case, compared to both the unconstrained case, and results from previous works~\cite{Yagi:binLove}.
-The maximal EoS variation from the fits for the unconstrained and constrained sets of EoSs are compared in Tab.~\ref{tab:maxVar} for both fractional and absolute differences.
-Additionally shown in this figure is the hybrid star C-Love relations along with their absolute differences from the constrained EoS fits (dashed green).
-}
-\label{fig:clove}
-\end{figure}
-
-In addition, Fig.~\ref{fig:rlove} displays the relationship between the NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
-This relationship is computed directly from the C-Love relations discussed above as $R(\Lambda)=m/C(\Lambda)$ for observed mass $m=1.48\text{ M}_{\odot}$ from GW170817.
-We also present the uncertainty on a NS radius measurement using the C-Love relations in the bottom panel of Fig.~\ref{fig:rlove}, defined as the absolute difference from the fits.
-This indicates that one can reliably measure the NS radius within $\sim 180 \text{ m} -350$ m, using the C-Love relations computed using the constrained set of EoSs.
-The uncertainty quoted here is comparable to the $140\text{ m}$ error found in Ref.~\cite{Gamba:2019kwu}, which investigated the uncertainty owed to the choice of the SLy EoS model for the crust.
-The radius uncertainty for the unconstrained EoSs of $\sim1\text{ km}$ however, would dominate the corresponding error budget on stellar radius compared to the crust uncertainties.
-We further observe a large suppression in the radius measurement accuracy from the unconstrained set of EoSs to the constrained set, tabulated in Tab.~\ref{tab:maxVar} as the maximal EoS measurement uncertainty.
-
-\begin{figure}
-\begin{center} 
-\includegraphics[width=\columnwidth]{RL.eps}
-\end{center}
-\caption{
-Similar to Fig.~\ref{fig:clove} but for the R-Love relationship between the NS radius and tidal deformability.
-This relationship is computed directly from the C-Love relations, and estimates the uncertainty on the NS radius as computed through the C-Love relations.
-Observe how the absolute difference from the fit is reduced significantly between the unconstrained and constrained sets of EoSs, shown by the comparisons in Tab.~\ref{tab:maxVar}.
-}
-\label{fig:rlove}
-\end{figure}
-
-The results for the C-Love and R-Love relations, similar to that found in Sec.~\ref{sec:ilq}, shows considerable improvement in using the constrained EoSs over any unconstrained set.
-We also note that the unconstrained EoSs display slightly larger EoS variability than found in Ref.~\cite{Yagi:binLove}, due to the large random sampling as discussed previously in Sec.~\ref{sec:ilq}.
+The left panel of Fig.~\ref{fig:clove} shows the C-Love relations for both the constrained and unconstrained sets, along with the corresponding \emph{absolute differences} from the fits (instead of the fractional differences as done back in Fig.~\ref{fig:ILQ}).
+Observe how the fit to the constrained EoSs suppresses the EoS variability compared to the fit to the unconstrained set, as well as that of previous works~\cite{Yagi:binLove}.
+The maximal EoS variation is compared between these three cases in Table~\ref{tab:maxVar}.
+
+From the C-Love relations, we can also compute directly the R-Love relation using $R(\Lambda)=M/C(\Lambda)$ and for a fixed NS mass $M$.
+The right panel of Fig.~\ref{fig:clove} shows the R-Love relation for the constrained and unconstrained sets fixing $M=1.48\text{ M}_{\odot}$ at the observed value for one of the NSs in the GW170817 event, with the bottom panel showing the absolute difference of the data and the fits.
+Observe that the C-Love relations allow us to infer the NS radius to better than $\sim 350 \textrm{m} $ in the constrained case, while the error goes up to $1,000 \textrm{m}$ in the unconstrained case, as also tabulated in Table~\ref{tab:maxVar}.
+The systematic uncertainty in the radius using the constrained fit is thus comparable to the $\sim 140\textrm{m}$ systematic uncertainty in the radius due to the choice of EoS to model the crust~\cite{Gamba:2019kwu}.
 
@@
 
-In this section, we consider the effect of hybrid star EoSs on the C-Love relation.
-Much like Sec.~\ref{sec:ilq-hyb}, we perform 3 separate fits (constrained and hybrid EoSs combined, constrained EoSs only, and hybrid EoSs only) and compare the maximal EoS variation for each set of EoSs.
-
-Table~\ref{tab:hybridCompareClove} compares the maximal EoS variability for the constrained and hybrid star EoSs under the fitting conditions for each case described above. 
-We observe very similar behavior to that described in Sec.~\ref{sec:ilq-hyb}, in which the maximal EoS variation for hybrid stars only fluctuate slightly ($\sim 4.5\% - 7\%$) for each case.
-From this, we similarly conclude that hybrid stars do obey the C-Love relation derived with nuclear matter stars, with the caveat that the maximum universality increases to $\sim 7.1\%$.
-This is exemplified in Fig.~\ref{fig:clove} by the dashed green curves.
+Let us now focus on whether the C-Love relations hold for hybrid stars.
+Much like in Sec.~\ref{sec:ilq-hyb}, we perform 3 separate fits: one to the constrained set plus 10 hybrid EoSs, another to the constrained set only, and a third to the 10 hybrid EoSs only.
+We then compare the EoS insensitivity in each case.
+
+The left panel of Fig.~\ref{fig:clove} shows the C-Love relation when fitting only to the constrained set (dashed green curves).
+Observe how the C-Love relation for hybrid star remains EoS-insensitive, but the degree of universality is not as high as in the case of hadronic NSs.
+Table~\ref{tab:hybridCompareClove} compares the maximal EoS variability for the constrained and hybrid star EoSs fitting to the three data sets described above.
+As in Sec.~\ref{sec:ilq-hyb}, observe how the maximal EoS variation for hybrid stars fluctuates only slightly ($\sim 4.5\% - 7\%$) in each case.ÊFrom this, we conclude that hybrid stars do obey the C-Love relation derived for nuclear matter stars, with the caveat that the maximum universality increases to $\sim 7.1\%$.
 
@@
 \centering
-\caption{
-Similar to Tab.~\ref{tab:hybridCompare} but for the C-Love relation.
-Observe how for all 3 cases, the hybrid EoSs are only universal up to a minimum of $\sim1$\% (fractional difference from the fit), while in each case the constrained EoSs outperform the hybrid ones.
-The second case is demonstrated in Fig.~\ref{fig:clove}.
-}\label{tab:hybridCompareClove}
 \begin{tabular}{ c  || c c } 
@@
  \hline
- \emph{Combined} &  \multirow{2}{*}{$0.03686$} & \multirow{2}{*}{$0.05533$}\\
+ \emph{Combined} &  \multirow{2}{*}{$0.037$} & \multirow{2}{*}{$0.055$}\\
  \emph{(Case 1)} & &\\
  \cline{1-1}
- \emph{Constrained only} & \multirow{2}{*}{$0.02169$} & \multirow{2}{*}{$0.07191$}\\
+ \emph{Constrained only} & \multirow{2}{*}{$0.022$} & \multirow{2}{*}{$0.072$}\\
   \emph{(Case 2)} & &\\
   \cline{1-1}
- \emph{Hybrid only} & \multirow{2}{*}{$0.05788$} & \multirow{2}{*}{$0.04478$}\\
+ \emph{Hybrid only} & \multirow{2}{*}{$0.058$} & \multirow{2}{*}{$0.045$}\\
   \emph{(Case 3)} & &\\
@@
 \end{tabular}
+\caption{
+Similar to Tab.~\ref{tab:hybridCompare} but for the C-Love relation.
+Observe how for all 3 cases, the hybrid EoSs are only universal up to a minimum of $\sim1$\% (fractional difference from the fit), while in each case the constrained EoSs outperform the hybrid ones.
+The second case is also shown in Fig.~\ref{fig:clove}.
+}\label{tab:hybridCompareClove}
 \end{table}
@@
 
-Next we consider improvements to the binary Love relations.
-Similar to Sec.~\ref{sec:ilq}, we consider two distinct classes of NSs: nuclear matter EoSs and hybrid quark-hadron star EoSs~\cite{Paschalidis2018,Alford:2017qgh,1971SvA....15..347S,Zdunik:2012dj,Alford:2013aca}.
-Following Ref.~\cite{Yagi:binLove}, we begin by fitting the binary Love relations to the constrained and unconstrained sets of EoSs using the two-dimensional curve:
-\begin{equation}\label{eq:binLovefit}
-\Lambda_a=F_n(q) \frac{1+ \sum_{i=1}^3 \sum_{j=1}^2 b_{ij}q^j x^{i/5}}{1 + \sum_{i=1}^3 \sum_{j=1}^2 c_{ij}q^j x^{i/5}} \Lambda_s^{\alpha}.
-\end{equation}
-Here, q is the mass ratio $q \equiv m_1/m_2$ with $m_1 \leq m_2$, and $F_n(q)$ is the Newtonian-limiting control factor given by:
-\begin{equation}\label{eq:control}
-F_n(q) \equiv \frac{1-q^{10/(3-n)}}{1+q^{10/(3-n)}}.
-\end{equation}
-The updated fit parameters for the constrained set of EoSs can be found in Table~\ref{tab:binLovefit}.
-Notice how, unlike the individual NS I-Love-Q relations, these relations additionally depend on the ratio of constituent masses in the binary system.
-
-\begin{table*}
-\centering
-\caption{
-Updated fit parameters for the binary Love relations, as given by the curve found in Eq.~\ref{eq:binLovefit}.
-}\label{tab:binLovefit}
-\addtolength{\tabcolsep}{1pt} 
-\begin{tabular}{c  c  c  c  c  c  c  c c c c c c c} 
- \hline
- \hline
-$n$ & $\alpha$ & $b_{11}$ & $b_{12}$ & $b_{21}$ & $b_{22}$ & $b_{31}$ & $b_{32}$ & $c_{11}$ & $c_{12}$ & $c_{21}$ & $c_{22}$ & $c_{31}$ & $c_{32}$\\
-\hline
-$0.743$ & $-1$ & $-14.40$ & $14.45$ & $31.36$ & $-32.25$ & $-22.44$ & $20.35$ & $-15.25$ & $15.37$ & $37.33$ & $-43.20$ & $-29.93$ & $35.18$\\
- \hline
- \hline
-\end{tabular}
-\addtolength{\tabcolsep}{-1pt}
-\end{table*}
-
-Figure~\ref{fig:binLove} shows the improved binary Love relation for 3 different mass ratios: $q=0.9$, $q=0.75$, and $q=0.5$ for both the constrained and unconstrained sets of EoSs.
-Observe how once again, the constrained set of EoSs show a considerable improvement upon both the unconstrained set of EoSs, as well as the results found in previous works~\cite{Yagi:binLove}.
-Additionally, the unconstrained set of EoSs show similar, yet slightly larger EoS variation than was previously found in Ref.~\cite{Yagi:binLove} due to the random sampling taken into account in this analysis.
-Once again, the maximum EoS variability (in terms of both absolute and fractional differences from the fit) is tabulated in Tab.~\ref{tab:maxVar} for each value of mass ratio considered here.
-We take note that while the fractional errors increase rapidly with increasing mass ratio $q$, the absolute errors remain consistent, with a subtle maximum at $q=0.75$. 
-This can be explained by the control factor $F_n(q)$ given by Eq.~\ref{eq:control}, which similarly observes a peak for central mass ratio values of $q\approx0.75$.
-We additionally make two observations about the effective ranges of $\Lambda_s$ seen in Fig.~\ref{fig:binLove}: (i) as the constituent masses in the binary system become further separated, the range of $\Lambda_s$ values shrinks; and (ii) the constrained set of EoSs typically display smaller values of $\Lambda_s$ than the unconstrained set do.
-The former observation can be explained by the following reasoning: as the masses further separate, there is a limited range of tidal deformabilities $\Lambda_{1,2}$ in the M-L relationships which satisfy the mass ratio constraint.
-From this we suggest the reader take note that as the mass ratio decreases, the allowable parameter space for the binary Love relations shrinks.
-The latter observation originates from the EoS generation process: the unconstrained EoSs are randomly generated -- resulting in various EoSs which are both stiffer and softer than those constrained by GW170817.
-This results in the unconstrained EoSs containing a larger range of tidal deformabilities $\Lambda$ (both above and below) than the constrained ones, which ultimately gives \emph{larger} values of $\Lambda_s=\frac{1}{2}(\Lambda_1+\Lambda_2)$.
-
-\begin{figure}
+\begin{figure}[htb]
 \begin{center} 
-\includegraphics[width=\linewidth]{binLoveAbsolute.eps}
+\includegraphics[width=\columnwidth]{binLoveAbsolute.eps}
 \end{center}
-\caption{
-Binary Love relations shown for the constrained EoSs (dotted maroon) and unconstrained EoSs (solid green) for various values of mass ratio: $q=0.9$, $q=0.75$, and $q=0.50$.
-In this figure, the top panel displays the EoS-insensitive relations with fits given by Eq.~\ref{eq:binLovefit} shown by dashed black lines (note there are 2 fits for each mass ratio, corresponding to the constrained and unconstrained sets of EoSs), while the bottom 3 panels correspond to the absolute EoS variation for each mass ratio.
-Observe how the constrained set of EoSs show a reduction in EoS variation for both the unconstrained set, and from the results shown in Ref.~\cite{Yagi:binLove}.
-The maximal EoS variability (shown as both the fractional and absolute differences) for each case is tabulated and compared in Tab.~\ref{tab:maxVar}.
-Additionally shown are the binary Love relations for the 10 hybrid star EoSs (dashed bright green curves).
-Observe the large deviations from the fit as the mass ratio $q$ increases, returning near the fit before the transitional pressure at large values of $\Lambda_s$.
+\caption{(Color online) Binary Love relations using Eq.~\ref{eq:binLovefit} fitted to the constrained (dotted maroon) and unconstrained sets (solid green), fixing $q=0.9$, $q=0.75$, and $q=0.50$.
+The bottom panels show the absolute difference (not the relative difference as in Fig.~\ref{fig:ILQ}) of the fit and the data.
+The fit to the constrained set shows a reduction in EoS variation relative to both the fit to the unconstrained set and previous work~\cite{Yagi:binLove}.
+For comparison, we also show the binary Love relations for the 10 hybrid star EoSs (dashed bright green curves), which present much larger EoS variation.
 }
@@
 
-Additionally shown in Fig.~\ref{fig:binLove} are the binary Love relations for the 10 hybrid star EoSs discussed in previous sections.
-As described in Sec.~\ref{sec:theory}, transitional quark-hadron matter stars undergo first-order phase transitions at pressure $P_{\text{tr}}$, where the hadronic branch departs into a quark-matter branch at the corresponding transitional mass $M_{\text{tr}}$.
-These transitions result in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq M_{\text{tr}}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote these as ``HS"); and (ii) low-mass ($M \leq M_{\text{tr}}$) hadronic stars with no internal transition to quark matter (we denote these as ``NS").
-Contrary to the single-star relations (I-Love-Q, C-Love, and R-Love) where the hybrid stars moderately agree with their nuclear matter counterparts, the binary-star relations show large disagreement, which can be seen in Fig.~\ref{fig:binLove}.
-Observe how the agreement with the fit is quite good at low pressures (large $\Lambda_s$) where the the binaries consist of NS/NS combinations (here, both stars' EoSs consist of the same class of nuclear matter as the constrained EoSs).
-Once the critical pressure is reached, one or both stars transition into the hybrid branches, resulting in large reductions in tidal deformability as shown in the right panel of Fig.~\ref{fig:eos}.
-When one star lies on the hadronic-matter branch while the other is on the quark-matter branch, 
-the difference between tidal deformabilities becomes larger than expected for pure hadronic-matter stars.
-This results in large deviations in the sums and differences of tidal deformabilities $(\Lambda_1 \pm \Lambda_2)$, disrupting the overall universality and generating the large ``bump" in the binary love relations for hybrid stars\footnote{This discrepancy is not present in the I-Love-Q and C-Love relations due to their single-star nature.} seen in Fig~\ref{fig:binLove}.
-
-Due to the inconsistencies in the sums and differences of tidal deformabilities for binary hybrid star systems, we conclude that hybrid stars do \emph{not} agree with the traditional nuclear matter binary Love relations.
-A number of attempts were made to reconcile these differences, such as performing separate ``HS" binary Love relations fitted directly to the hybrid star branches of the EoSs.
-This analysis quickly left the scope of the paper due to the large number of parameters required to control the varying transitional pressures through different EoSs.
-Therefore, we leave an analysis on the hybrid star binary Love relations to be discussed in future works.
-There, we anticipate the generation of large numbers of hybrid star EoSs with varying transition masses to be taken into account as an additional fitting parameter in a piece-wise fitting function designed to take into account the ``bumps" seen in the binary Love relations.
+Let us now consider the binary Love relations.
+Following Ref.~\cite{Yagi:binLove}, we begin by fitting the binary Love relations to the constrained and unconstrained sets using the two-dimensional curve:
+\begin{equation}\label{eq:binLovefit}
+\Lambda_a=F_n(q) \frac{1+ \sum_{i=1}^3 \sum_{j=1}^2 b_{ij}q^j x^{i/5}}{1 + \sum_{i=1}^3 \sum_{j=1}^2 c_{ij}q^j x^{i/5}} \Lambda_s^{\alpha},
+\end{equation}
+where $q\equiv m_{1}/m_{2}$ is the mass ratio with $m_1 \leq m_2$, and $F_n(q)$ is the Newtonian-limiting controlling factor, given by
+\begin{equation}\label{eq:control}
+F_n(q) \equiv \frac{1-q^{10/(3-n)}}{1+q^{10/(3-n)}}.
+\end{equation}
+The coefficients of the fit to the constrained set are 
+\begin{align}
+b_{ij} = \begin{bmatrix}
+    -14.40 & 14.45   \\
+    31.36 & -32.25   \\
+    -22.44 & 20.35   
+\end{bmatrix}
+\quad
+c_{ij} = \begin{bmatrix}
+    -15.25 & 15.37   \\
+    37.33 & -43.20   \\
+    -29.93 & 35.18   
+\end{bmatrix},
+\end{align}
+{\ny{Zack, why did you pick a non-square matrix of coefficients to fit to? Typically, fits are better behaved when you stay with square matrices}}
+and $n = 0.743$, where we set $\alpha = 1$ {\ny{Zack, is this right?
+I think you didn't fit for $\alpha$, but rather you set it to unity, but you did fit to $n$.
+Please confirm.}} Unlike the individual I-Love-Q relations, the binary Love relations depend also depend on the mass ratio.
+
+Figure~\ref{fig:binLove} shows the improved binary Love relation for 3 different mass ratios ($q=0.9$, $q=0.75$, and $q=0.5$) for both the constrained and unconstrained sets of EoSs.
+Observe how, once again, the constrained set shows a considerable increase in EoS-insensitivity relative to both the unconstrained set and previous works~\cite{Yagi:binLove}.
+As before, the fit to the unconstrained set shows similar, yet slightly larger EoS variation than that found in previous work~\cite{Yagi:binLove} due to the random sampling used in our analysis.
+Observe that absolute error between the fit and the data is approximately independent of the mass ratio $q$, with a subtle maximum at $q=0.75$, which mimics the behavior of the controlling factor $F_n(q)$.
+As before, maximum EoS variation is tabulated in Tab.~\ref{tab:maxVar} for each value of mass ratio considered here.
+
+We can extract two additional conclusions from from this Fig.~\ref{fig:binLove}.
+First, as the mass ratio becomes more extreme (i.e.~away from unity), the ranges of values that $\Lambda_s$ and $\Lambda_a$ can take decrease.
+This is because as $q$ decreases, there is a limited range of tidal deformabilities $\Lambda_{1,2}$ in the M-L relationships that satisfy the mass ratio constraint {\ny{What?
+I didn't understand the previous clause enough to rewrite it.}}, and thus, the allowed parameter space shrinks.
+Second, the fit to the constrained set does not extend to as high values of $\Lambda_s$ as the fit to the unconstrained set does.
+This is because of how the sets of EoSs were generated in our analysis, with the unconstrained set including some EoSs that are stiffer and and others that are softer than those constrained by the GW170817 event.
+This results in the unconstrained set  containing a larger range of tidal deformabilities $\Lambda_{1,2}$ (from both above and below) than the constrained set, which ultimately leads to a \emph{larger} range of $\Lambda_s=\frac{1}{2}(\Lambda_1+\Lambda_2)$ values.
+
+Let us now consider the binary Love relations for hybrid stars.
+As described in Sec.~\ref{sec:theory}, transitional quark-hadron matter stars undergo strong first-order phase transitions at a transitional pressure $P_{\text{tr}}$, where the hadronic branch departs into a quark-matter branch at the corresponding transitional mass $M_{\text{tr}}$.
+These transitions result in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq M_{\text{tr}}$) hybrid stars that have quark-matter inner cores and nuclear matter elsewhere (which recall we denote ``HS"); and (ii) low-mass ($M \leq M_{\text{tr}}$) hadronic stars with no internal transition to quark matter (which recall we denote ``NS").
+We therefore expect the binary Love relations for hybrid stars to present behavior identical to their purely hadronic counterparts below the transitional mass (or correspondingly above a transitional $\Lambda_{s,\textrm{tr}}$), and very different behavior for higher masses (or correspondingly for smaller $\Lambda_{s,\textrm{tr}}$).
+
+This behavior is exactly what we observe in Fig.~\ref{fig:binLove} for the binary Love relations of hybrid stars.
+Indeed, contrary to the case of EoS-insensitive relations for isolated hadronic stars (I-Love-Q, C-Love, and R-Love) which remain moderately EoS-insensitive for all hybrid stars, the binary Love relations depart from their hadronic counterparts below some transitional $\Lambda_{s}$.
+This is because at low pressures ($\Lambda_s>\Lambda_{s,\textrm{tr}}$) the binary is purely of NS/NS type (with the EoS for both stars a member of the constrained set), but once the critical pressure is reached ($\Lambda_{s}<\Lambda_{s,\textrm{tr}}$), one or both stars transition into the hybrid branch, resulting in large reductions in tidal deformability, as shown in the left panel of Fig.~\ref{fig:clove}.
+When one star lies on the hadronic-matter branch while the other is on the quark-matter branch, the difference between tidal deformabilities becomes larger than expected for pure hadronic-matter stars.
+This results in large deviations in the sums and differences of tidal deformabilities $(\Lambda_1 \pm \Lambda_2)$, disrupting the overall universality and generating the large ``bump" in the binary Love relations for hybrid stars\footnote{This discrepancy is not present in the I-Love-Q and C-Love relations due to their single-star nature.} seen in Fig~\ref{fig:binLove}.
+
+From this analysis, we conclude that binaries containing one or more hybrid stars do \emph{not} satisfy the same binary Love relations as binaries that contain only traditional nuclear matter stars.
+This does not imply, however, that more sophisticated binary Love relations cannot be constructed that will remain EoS-insensitive and able to model both types of binary systems.
+Such relations, however, would necessarily have to include (at least) one new parameter that determines the transition between the hadronic and the quark branches, such that the ``bump'' in the binary Love relations can be properly modeled.
+Work along these lines is outside the scope of this paper.
 

### 2019-02-20 paper/bin-love-after-gw170817.tex
hate git

@@
 
-We have now shown that binary NS merger observations can help improve the EoS-insensitive relations - the question is: is it worth it?
-Current interferometer sensitivities are not yet small enough to accurately constrain the dominant tidal parameter $\tilde{\Lambda}$.
-For example, GW170817 was detected by LIGO observing run 2 (``O2")~\cite{aLIGO} and was able to constrain $\tilde{\Lambda}$ to a $90\%$ confidence interval of 325 (or $\sigma_{\tilde{\Lambda}} \approx 198$) centered at $\mu_{\tilde{\Lambda}}=395$.
-This corresponds to statistical uncertainties on the order of $\sim 82\%$, which dominates the error budget compared to the small systematic uncertainties picked up by EoS variation in the EoS-insensitive relations.
+We have now shown that binary NS merger observations can help improve the EoS-insensitive relations, but the question remains: is it worth it?
+Current interferometer sensitivities are not yet high enough to accurately constrain the dominant tidal parameter $\tilde{\Lambda}$.
+For example, GW170817 was detected by LIGO observing run 2 (``O2")~\cite{aLIGO} and was able to constrain $\tilde{\Lambda}$ to a $90\%$ confidence interval centered at $\mu_{\tilde{\Lambda}}=395$ and with a width of 325 (or $\sigma_{\tilde{\Lambda}} \approx 198$).
+This corresponds to statistical uncertainties of ${\cal{O}}(80\%)$, which dominates the error budget compared to the small systematic uncertainties picked up by EoS variation in the EoS-insensitive relations.
 This implies that currently, the use of improved EoS-insensitive relations will only make a negligible difference on the extraction of tidal parameters.
 
-In Sec.~\ref{sec:marginalization}, we first estimate the systematic uncertainties introduced by using the improved binary Love relations derived earlier.
-In Sec.~\ref{sec:futureObservations}, we estimate the statistical uncertainties on the parameter extraction of tidal parameters, and compare them to the above-mentioned systematic uncertainties.
-This is repeated for 5 future detectors, where multiple event detections become important.
-Because future events occur with mass-weighted tidal deformability $\tilde\Lambda$ which are unknown at this time, we can not accurately combine the uncertainties on $\tilde\Lambda$ for multiple events.
-To remedy this, we re-parameterize the waveform and instead consider the $\lambda_0$ and $\lambda_1$ tidal coefficients produced by Taylor expanding the dimensionless tidal deformability $\Lambda$ about the ``canonical" reference mass of $m_0=1.4\text{ M}_{\odot}$~\cite{delPozzo:TaylorTidal,Yagi:binLove}:
-\begin{equation}
-\Lambda \approx \lambda_0 + \lambda_1 (1-\frac{m}{m_0}),
-\end{equation}
-where $\lambda_0$ and $\lambda_1$ are the tidal deformability and its slope at $1.4 \text{ M}_{\odot}$\footnote{$\lambda_0$ is commonly known as $\Lambda_{1.4}$.}. 
-The new tidal parameters $\lambda_0$ and $\lambda_1$ do not depend on mass, thus are identical for every future binary NS merger, and may be combined in uncertainty.
-Under this reasoning, we consider the new tidal parameters $\lambda_0$ and $\lambda_1$ for the remainder of the investigation.
+In this section, we further explore this question and study when in the future the new set of improved relations will become important as current detectors are improved and new ones are built.
+In Sec.~\ref{sec:marginalization}, we first estimate the systematic uncertainties introduced by using the improved binary Love relations.
+In Sec.~\ref{sec:futureObservations}, we estimate the statistical uncertainties on the extraction of tidal parameters, and compare them to the above-mentioned systematic uncertainties.
+This is repeated for 5 future detectors, where multiple detections become important, but to combine constraints from multiple events we cannot use the $\tilde\Lambda$ parameterization, as this depends on the masses of the binary constituents.
+To remedy this, we re-parameterize the waveform in terms of the coefficients $\lambda_0$ (sometimes called $\Lambda_{1.4}$) and $\lambda_1$, obtained from a Taylor expansion of the dimensionless tidal deformability $\Lambda$ about a ``canonical" reference mass $M_0=1.4\text{ M}_{\odot}$~\cite{delPozzo:TaylorTidal,Yagi:binLove}:
+\begin{equation}
+\Lambda = \lambda_0 + \lambda_1 \left(1-\frac{M}{M_0}\right) + {\cal{O}}\left[\left(1-\frac{M_{0}}{M}\right)^{2}\right].
+\end{equation}
+The Taylor coefficients $\lambda_0$ and $\lambda_1$ are mass independent, and thus they are identical in all binary NS observations, and their posteriors may be combined.
 
@@
 
-In this section, we investigate the residuals on $\Lambda_a(\Lambda_s,q)$ in order to marginalize over the intrinsic uncertainty found in the binary Love EoS-insensitive relations.
+Let us begin by investigating the residuals on $\Lambda_a(\Lambda_s,q)$ and the induced residuals on $\lambda_{0}$, in order to marginalize over the intrinsic uncertainty found in the binary Love relations.
 In particular, we restrict our focus to only the constrained set of EoSs.
-Residuals in $\Lambda_a$ are computed as $\Lambda_a^{\text{relation}}(\Lambda_s,q)-\Lambda_a^{\text{true}}$, where $\Lambda_a^{\text{true}}$ corresponds to the true value predicted by the sample EoSs, and $\Lambda_a^{\text{relation}}(\Lambda_s,q)$ corresponds to the value obtained through the EoS-insensitive relations found in Sec.~\ref{sec:binary}.
-We follow this up by converting the $\Lambda_a$ residuals into $\lambda_0$, allowing us to approximate the overall systematic uncertainties on $\lambda_0$ from using the improved binary Love relations.
-
+Residuals in $\Lambda_a$ are computed as $\Lambda_a^{\text{relation}}(\Lambda_s,q)-\Lambda_a^{\text{true}}$, where $\Lambda_a^{\text{true}}$ corresponds to the true value predicted by the sampled EoSs, and $\Lambda_a^{\text{relation}}(\Lambda_s,q)$ corresponds to the fit found in Sec.~\ref{sec:binary}.
+We then convert the $\Lambda_a$ residuals into $\lambda_0$ residuals, as we describe below.
+
+{\ny{Please rewrite everything from here to Subsection B. It is not clear at all what you've done, why you've done it, and what you got.}}
 Following Ref.~\cite{Katerina:residuals}, we assume the residuals on $\Lambda_a$ observe a Gaussian distribution with mean and standard deviation given by:
@@
 \end{align}
-Similar to Ref.~\cite{Katerina:residuals}, we fit the individual components to the following power functions:
+%The mean and standard deviation of the Gaussian distribution of the residuals on 
+We then fit the individual components using the following power functions {\ny{to what data? This is confusing}}:
 \begin{align}
@@
 \centering
-\caption{
-Coefficients to the fits given by Eqs.~(\ref{eq:margFit1})-(\ref{eq:margFit4}) for the relative error on $\Lambda_a$ in the improved binary Love EoS-insensitive relations presented in this paper.
-}\label{tab:marginalized}
 \addtolength{\tabcolsep}{1pt} 
@@
 \end{tabular}
+\caption{
+Coefficients to the fits given by Eqs.~(\ref{eq:margFit1})-(\ref{eq:margFit4}) for the relative error on $\Lambda_a$ in the improved binary Love EoS-insensitive relations presented in this paper.
+}\label{tab:marginalized}
 \addtolength{\tabcolsep}{-1pt}
@@
 
-Now that we have obtained the residuals on $\Lambda_a$, we must convert them into the new tidal parameter $\lambda_0$, in order to compute and easily compare the systematic uncertainties to the statistical uncertainties on $\lambda_0$, found in Sec.~\ref{sec:futureObservations}.
-Figure~\ref{fig:qLsResiduals} shows the standard deviations of these residuals (converted into $\lambda_0$) binned in both $q$ and $\Lambda_s$ as was done above. 
+Now that we have obtained the residuals on $\Lambda_a$, we must convert them into residuals on the new tidal parameter $\lambda_0$, in order to compute and easily compare the systematic uncertainties to the statistical uncertainties on $\lambda_0$.
+{\ny{You need to say explicitly how you did this.}}
+Figure~\ref{fig:qLsResiduals} shows the standard deviations of these residuals (converted into $\lambda_0$) binned in both $q$ and $\Lambda_s$. 
 To estimate the overall systematic uncertainties on $\lambda_0$ accrued upon the use of the improved binary Love relations, we combine the uncertainties in both $q$ and $\Lambda_s$.
@@
 \subsection{Future Observations}\label{sec:futureObservations}
-In this section, we estimate the feasibility of utilizing the improved EoS-insensitive relations in future binary NS merger events.
-This estimate is acquired through a simple Fisher analysis~\cite{Finn:Fisher,Cutler:Fisher} which approximates the accuracy with which one can extract the best-fit parameters $\theta^a$, given a prior template waveform.
-For the remainder of the paper, we consider a template parameter vector consisting of:
+
+We now estimate the feasibility of using the improved EoS-insensitive relations in future GW observations of the coalescence of binary NSs.
+We estimate the statistical accuracy to which parameters can be extracted through a simple Fisher analysis~\cite{Finn:Fisher,Cutler:Fisher}, assuming sufficiently high signal-to-noise ratio and Gaussian noise~\cite{Cutler:Fisher,Berti:Fisher,Poisson:Fisher}.
+Henceforth, we consider a waveform template parametrized in terms of
 \begin{equation}\label{eq:template}
@@
 \end{equation}
-where $\eta \equiv m_1 m_2/M^2$ is the symmetric mass ratio with $m_{1,2}$ and $M$ being the individual and total masses, $\mathcal{M}=M \eta^{3/5}$ is the chirp mass, $A \equiv \frac{\mathcal{M}^{5/6}}{\sqrt{30}\pi^{2/3}D_L}$ is a normalized amplitude factor with $D_L$ being the luminosity distance, and $\chi_{s,a}=\frac{1}{2}(\chi_1\pm\chi_2)$ are the symmetric and antisymmetric total spins, where $\chi_{1,2}$ are the NSs individual spins.
-Following Refs.~\cite{Cutler:Fisher,Berti:Fisher,Poisson:Fisher}, this method relies on the crude assumption of Gaussian prior distributions\footnote{Typically, the more valid assumption is a uniform prior distribution; an improvement made in a more detailed Bayesian analysis.}.
+where $\eta \equiv m_1 m_2/m^2$ is the symmetric mass ratio with $m_{1,2}$ and $m$ being the individual and total masses, $\mathcal{M}=m \eta^{3/5}$ is the chirp mass, $A \equiv {\mathcal{M}^{5/6}}/({\sqrt{30}\pi^{2/3}D_L})$ is a normalized amplitude factor with $D_L$ the luminosity distance, and $\chi_{s,a}=\frac{1}{2}(\chi_1\pm\chi_2)$ are the symmetric and antisymmetric dimensionless spin parameters.
 The resulting posterior distribution is Gaussian with a root-mean-square given by:

### 2019-02-20 paper/bin-love-after-gw170817.tex
done with Sec. IV

@@
 Figure~\ref{fig:stackedFisher} shows this result in more detail.
-We here present the (Fisher-estimated) statistical uncertainty in the measurement of $\lambda_{0}$ with various detectors (LIGO O2~\cite{aLIGO}, Advanced LIGO (aLIGO)~\cite{aLIGO}, LIGO A\texttt{+} (A\texttt{+})\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, the Einstein Telescope (ET)~\cite{ET}, and the Cosmic Explorer (CE)~\cite{Ap_Voyager_CE}) for an event identical to GW170817.
+We here present the (Fisher-estimated) statistical uncertainty in the measurement of $\lambda_{0}$ with various detectors (LIGO O2~\cite{aLIGO}, Advanced LIGO at design sensitivity (aLIGO)~\cite{aLIGO}, LIGO A\texttt{+} (A\texttt{+})\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, the Einstein Telescope (ET)~\cite{ET}, and the Cosmic Explorer (CE)~\cite{Ap_Voyager_CE}) for an event identical to GW170817.
 The x-axis shows the signal-to-noise ratio for a GW170817 event detected with each of these detectors.
@@
 This means that, for the current ``O2" detector sensitivity, the use of improved binary Love relations will only make a negligible difference on the extraction of $\tilde\Lambda$.
-However, future detectors (for example aLIGO, A\texttt{+}, Voyager, CE, and ET) are planned with large reductions in sensitivity - both decreasing the statistical uncertainties and allowing for larger binary NS merger detection rates; further reducing the statistical uncertainties.
+However, future detectors (for example aLIGO at design sensitivity, A\texttt{+}, Voyager, CE, and ET) are planned with large reductions in sensitivity - both decreasing the statistical uncertainties and allowing for larger binary NS merger detection rates; further reducing the statistical uncertainties.
 In Sec.~\ref{sec:futureObservations}, we analyze this further and discuss when the systematic uncertainties from EoS-insensitive relations become comparable to the statistical uncertainties.
@@
 We estimate the statistical accuracy to which parameters can be extracted through a simple Fisher analysis~\cite{Finn:Fisher,Cutler:Fisher}, assuming sufficiently high signal-to-noise ratio and Gaussian noise~\cite{Cutler:Fisher,Berti:Fisher,Poisson:Fisher}.
-Henceforth, we consider a waveform template parametrized in terms of
+
+Consider then a waveform template $h$ parametrized in terms of
 \begin{equation}\label{eq:template}
@@
 where $\eta \equiv m_1 m_2/m^2$ is the symmetric mass ratio with $m_{1,2}$ and $m$ being the individual and total masses, $\mathcal{M}=m \eta^{3/5}$ is the chirp mass, $A \equiv {\mathcal{M}^{5/6}}/({\sqrt{30}\pi^{2/3}D_L})$ is a normalized amplitude factor with $D_L$ the luminosity distance, and $\chi_{s,a}=\frac{1}{2}(\chi_1\pm\chi_2)$ are the symmetric and antisymmetric dimensionless spin parameters.
-The resulting posterior distribution is Gaussian with a root-mean-square given by:
-\begin{equation}
-\Delta \theta^a=\sqrt{\Big( \tilde{\Gamma}^{-1}\Big)^{aa}}.
-\end{equation}
-Here, the Fisher matrix $\tilde{\Gamma}$ is defined by:
-\begin{equation}
-\tilde{\Gamma}_{ab} \equiv \Big( \frac{\partial h}{\partial \theta^a} \Big| \frac{\partial h}{\partial \theta^a}\Big) + \frac{1}{\sigma_{\theta^a}^2} \delta_{ab}
-\end{equation}
-where $h$ is the waveform template, $\sigma_{\theta^a}$ are the parameters' prior root-mean-square estimate, and the inner product is defined by:
-\begin{equation}
-(a|b) \equiv 2 \int^{\infty}_0\frac{\tilde{a}^*\tilde{b}+\tilde{b}^*\tilde{a}}{S_n(f)}df.
-\end{equation}
-
-In this analysis, we consider the ``PhenomD" (IMRD) waveform template~\cite{PhenomDI,PhenomDII} modified by two different tidal corrections: the 6PN tidal correction shown in Ref.~\cite{Wade:tidalCorrections} (IMRD + 6PN), and the NRTidal correction shown in Ref.~\cite{Samajdar:NRTidal} (IMRD + NRTidal).
-Comparing the two different tidal corrections to the IMRD waveform returns a rough estimate on the magnitude of waveform mismodeling systematics.
-Lastly, we consider the spectral noise densities $S_n^A(f)$ for 6 different interferometer designs: $A \equiv ($O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, CE~\cite{ET}, ET-D~\cite{Ap_Voyager_CE}$)$ in order to compare the statistical uncertainties accrued on parameter extraction using future upgraded LIGO detectors as well as third generation detectors.
-
-We begin by authenticating this approach by applying a Fisher analysis (with an IMRD + 6PN waveform injection) to GW170817, as observed by LIGO with O2 detector sensitivity~\cite{aLIGO}.
-Because only 1 event was detected, we utilize $\tilde\Lambda$ and $\delta\tilde\Lambda$ as the tidal parameters for comparison purposes.
-Further, we scale the luminosity distance such that the signal-to-noise-ratio ($SNR \equiv \rho$) is fixed to be $\rho=32.4$, as was found in GW170817.
+Given a sufficiently loud observation and Gaussian noise, the resulting posterior distribution on the estimated parameters is Gaussian with a root-mean-square given by
+\begin{equation}
+\Delta \theta^a=\sqrt{\Big( \tilde{\Gamma}^{-1}\Big)^{aa}},
+\end{equation}
+where the Fisher information matrix $\tilde{\Gamma}$ is
+\begin{equation}
+\tilde{\Gamma}_{ab} \equiv \Big( \frac{\partial h}{\partial \theta^b} \Big| \frac{\partial h}{\partial \theta^a}\Big) + \frac{1}{\sigma_{\theta^a}^2} \delta_{ab}
+\end{equation}
+$\sigma_{\theta^a}$ are the parameters' prior root-mean-square estimate, and the inner product is defined by:
+\begin{equation}
+(a|b) \equiv 2 \int^{\infty}_0\frac{\tilde{a}^*\tilde{b}+\tilde{b}^*\tilde{a}}{S_n(f)}df,
+\end{equation}
+with the overhead tilde and the star standing for the Fourier transform and complex conjugation respectively.
+
+The inner product, and thus the root-mean-square error, depends on the spectral noise density $S_{n}(f)$ and the waveform template $\tilde{h}$.
+We consider here 6 different interferometer designs, O2~\cite{aLIGO}, aLIGO at design sensitivity~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, CE~\cite{ET}, ET-D~\cite{Ap_Voyager_CE} shown in Fig.~\ref{fig:sensitivities}, in order to compare the statistical uncertainties accrued on parameter extraction using future upgraded LIGO detectors, as well as third generation detectors.
+The inner product also depends on the particular waveform model we use for the template.
+We here consider a ``PhenomD" (IMRD) waveform template~\cite{PhenomDI,PhenomDII} modified by a 6PN tidal correction~\cite{Wade:tidalCorrections} (IMRD + 6PN), as well as a ``PhenomD'' template modified with a NRTidal correction~\cite{Samajdar:NRTidal} (IMRD + NRTidal).
+Considering two template models will allow us to estimate systematic uncertainties due to mismodeling.
+
+We begin by testing our Fisher analysis (with an IMRD + 6PN waveform injection) against a simulated event identical to GW170817 with O2 detector sensitivity~\cite{aLIGO}.
+Because only 1 event was detected, we use $\tilde\Lambda$ and $\delta\tilde\Lambda$ as the tidal parameters for comparison purposes.
+Further, we scale the luminosity distance such that the signal-to-noise-ratio ($SNR \equiv \rho$) is fixed to $\rho=32.4$, as found in GW170817.
 We also assume low spin priors $|\chi| \leq 0.05$, as well as $\tilde{\Lambda} \leq 3000$ and $|\delta \tilde{\Lambda}| \leq 500$~\cite{Wade:LambdaPriors}.
-The resulting posterior distribution on $\tilde{\Lambda}$ has a range of $\pm 276.99$ encompassing the $90\%$ credible levels.
-We compare these results with the Bayesian analysis performed in Ref.~\cite{TheLIGOScientific:2017qsa,Abbott2018}, finding close agreement with the resulting $90\%$ credible region of $70 \leq \tilde{\Lambda} \leq 720$.
-This confirms the approximate validity of this method, allowing a continuation of this analysis for future detectors.
+The resulting $90\%$ credible region of the posterior distribution on $\tilde{\Lambda}$ has a range of $\pm 276.99$, which is in close agreement to that found by LIGO with a Bayesian analysis~\cite{TheLIGOScientific:2017qsa,Abbott2018}
+
 \begin{figure}
@@
 \end{center}
-\caption{
-Square root of of the spectral noise densities $\sqrt{S_n^A(f)}$ plotted for detectors ($A$): LIGO O2, aLIGO, A\texttt{+}, Voyager, CE, and ET-D as interpolated from publicly available data.
+\caption{(Color online)
+Square root of of the spectral noise densities $\sqrt{S_n^A(f)}$ plotted for LIGO O2, aLIGO at design sensitivity, A\texttt{+}, Voyager, CE, and ET-D as interpolated from publicly available data.
 Spectral noise densities are plotted from $f_{\text{min}}=(23,10,10,7,1,1) \text{ Hz}$, respectively, to $f_{\text{max}}=1649 \text{ Hz}$.
@@
 
-Next, we consider events identical to GW170817 detected on future design sensitivity upgrades and detectors $A \equiv ($O2, aLIGO, A\texttt{+}, Voyager, CE, ET-D$)$, shown in Fig.~\ref{fig:sensitivities}.
-Further, we consider the combined statistical uncertainties of $N_A$ events detected over 1 year on detector $A$, determined by integrating the local binary NS (BNS) merger rate over redshifts up to the horizon redshift of each detector.
-Here we assume low spin priors $|\chi| \leq 0.05$, as well as $0 \leq \lambda_0 \leq 3207$ and $-4490 \leq \lambda_1 \leq 0$~\cite{delPozzo:TaylorTidal}\footnote{These are converted from the dimensional forms found in Ref.~\cite{delPozzo:TaylorTidal} into their corresponding dimensionless forms.}.
-The process we utilize to compute single and combined statistical uncertainties for each detector sensitivity $S_n^A(f)$ is detailed in App.~\ref{app:stackingProcedure}.
-From this, we determine if and when the statistical uncertainties associated with the parameter extraction of $\lambda_0$ drop below the systematic EoS variation errors from using binary Love relations.
-
-The results for this process upon the injection of the IMRD + 6PN waveform are compiled in Table~\ref{tab:variances}, and shown graphically in Fig.~\ref{fig:stackedFisher} where $\sigma^A_{\text{GW170817}}$ and $\sigma^A_N$ are plotted as a function of $\rho^A_{\text{GW170817}}$ (the SNR as if GW170817 were detected on future detector $A$) for 5 future detector sensitivities.
-For reference, Fig.~\ref{fig:singleFisherLt} also displays the estimated $\tilde\Lambda$ extraction efficiency for \emph{one} event on each detector; as these events can not be combined like was done in the case of $\lambda_0$.
-Observe how this figure shows similar results on $\tilde\Lambda$ to that found on $\lambda_0$ for the case of one event - that is, future third-generation detectors ET and CE both observe statistical uncertainties on $\tilde\Lambda$ (and $\lambda_0$) dropping below the systematic binary Love errors for a single event.
-This result is amplified when multiple events are combined as shown in Fig.~\ref{fig:stackedFisher}, further motivating the need to improve the systematic uncertainties in the binary Love relations for upcoming detectors Voyager, CE and ET.
-We note that in Figs.~\ref{fig:stackedFisher} and~\ref{fig:singleFisherLt}, the single-event measurement uncertainties are slightly larger for CE than for ET despite having a larger SNR.
-This relic originates from the high-frequency dependence of CE and ETs detector sensitivities: due to the 3-detector geometry of ET, it is able to more accurately measure the tidal effects emergent at high frequencies.
-However, when computing the SNRs from $1 \text{ Hz} \leq f \leq 1649 \text{ Hz}$, CE dominates over ET and observes a larger SNR.
-When instead setting the minimum frequency to $f_{\text{min}} \geq 68$ Hz however, the SNR for ET instead dominates that for CE, validating our hypothesis on this effect.
+Next, we consider events identical to GW170817 detected on upgraded detectors and future detectors, as well as the combined statistical uncertainties of $N_A$ events detected over a 1 year observation with each detector.
+The later is calculated by integrating the local binary NS merger rate over redshifts up to the horizon redshift of each detector.
+As before, for each Fisher calculation we assume low spin priors $|\chi| \leq 0.05$, as well as $0 \leq \lambda_0 \leq 3207$ and $-4490 \leq \lambda_1 \leq 0$~\cite{delPozzo:TaylorTidal}\footnote{These are converted from the dimensional forms found in~\cite{delPozzo:TaylorTidal} into their corresponding dimensionless forms.}.
+The process we use to compute single and combined statistical uncertainties for each detector sensitivity $S_n^A(f)$ is detailed in App.~\ref{app:stackingProcedure}.
+From this, we determine if and when the statistical uncertainties associated with the parameter extraction of $\lambda_0$ drop below the systematic EoS variation errors from using the binary Love relations.
+
+Figures~\ref{fig:singleFisherLt} and~\ref{fig:stackedFisher}, and Table~\ref{tab:variances} summarize our results graphically using an IMRD + 6PN template.
+In the latter, you can see the statistical accuracy to which $\tilde{\Lambda}$ can be estimated as a function of $\rho^A_{\text{GW170817}}$ for single GW170817-like events, i.e.~the signal-to-noise ratio that future detector $A$ would have measured for a GW170817 event.
+Observe that the systematic uncertainty in $\tilde{\Lambda}$ (the horizontal dashed line) becomes comparable to the statistical uncertainty for Voyager-class detectors or better.
+Figure~\ref{fig:singleFisherLt} presents similar results but for the parameter $\lambda_{0}$, for which one can combine posteriors and obtained a reduced combined statistical error.
+This figure also shows that the statistical and systematic uncertainties become comparable for Voyager-class detectors or better.
+The careful reader will notice that Figs.~\ref{fig:stackedFisher} and~\ref{fig:singleFisherLt} show that the single-event statistical uncertainties using CE is higher than using ET despite the later having a larger SNR for a GW170817-like event.
+This is because the 3-detector geometry of ET enables it to have higher sensitivity than ET at frequencies above 300Hz, which is precisely where the tidal deformabilities is encoded, but ET has lower sensitivity at lower frequencies, where a lot of the signal-to-noise ratio accumulates.
 
@@
 \end{center}
-\caption{
-Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ in the extraction of $\tilde\Lambda$ from GW170817 (O2) as if observed with future interferometers aLIGO, A\texttt{+}, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
-Also shown is the systematic uncertainty on $\tilde\Lambda$ derived using the same method used to compute the systematic uncertainty on $\lambda_0$.
-This is similar to Fig.~\ref{fig:stackedFisher} where the extraction efficiency of $\lambda_0$ was plotted, however, in this case multiple events can \emph{not} be combined due to the variation in mass and therefore $\tilde\Lambda$ among events.
+\caption{(Color Online) Estimated statistical uncertainty $\sigma^A_{\text{GW170817}}$ in the extraction of $\tilde\Lambda$ from a single GW170817-like event as if observed with aLIGO at design sensitivity, A\texttt{+}, Voyager, CE, and ET-D, plotted as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$ that those detectors would measure for such an event.
+For comparison, we also plot the systematic uncertainty on $\tilde\Lambda$ due to the use of the binary Love relations.
+Observe that the statistical and the systematic errors become comparable for Voyager-class detectors or better.
 }
@@
 \centering
-\caption{
-Tabulated results for the estimated statistical uncertainties on the tidal deformability at $1.4\text{ M}_{\odot}$, $\lambda_0$, for the combined results of $N_A$ detections corresponding to the estimated upper, central, and lower limits of the binary NS merger detection rate $\mathcal{R}$.
-This is repeated for 5 future detector sensitivities: aLIGO, A\texttt{+}, Voyager, CE, and ET.
-Below, $\rho^A_{\text{GW170817}}$ and $\sigma^A_{\text{GW170817}}$ correspond to the approximate SNR and $\sigma_{\lambda_0}$ of GW170817 had it been observed by future interferometer $A$, and $\sigma^A_N$ corresponds to the overall uncertainty on $\lambda_0$ after $N_A$ detections on interferometer $A$.
-It can be seen here that the statistical uncertainties on $\lambda_0$ become comparable with the systematics (set to be $P_{90}=13.19$) from using improved binary Love relations for future detectors Voyager, ET, and CE, indicating when it will become important to improve the EoS-insensitive relations.
-Note that the approximation for $\sigma^A_N$ under the O2 detector sensitivity is left blank due to the singularity of the detected event.
-These results are also shown graphically in Fig.~\ref{fig:stackedFisher}.
-}\label{tab:variances}
 \begin{tabular}{|c|@{\extracolsep{4pt}}c@{\extracolsep{0pt}}|c|@{\extracolsep{4pt}}C{1.7cm}@{\extracolsep{-2pt}}|C{1.7cm}|@{\extracolsep{-2pt}}C{1.7cm}@{\extracolsep{2pt}}|c|@{\extracolsep{0pt}}c@{\extracolsep{0pt}}|c|}
@@
 \end{tabular}
+\caption{
+Approximate signal-to-noise ratio $\rho^A_{\text{GW170817}}$ and ($1\sigma$ {\ny{Zack, 1 sigma or $90\%$?}}) statistical uncertainty on the extraction of $\lambda_{0}$ had a single event like GW170817 been observed by future interferometer $A$ and had interferometer $A$ observed $N_{A}$ events in a 1 year observation, using aLIGO, A\texttt{+}, Voyager, CE, and ET.
+The number of events $N_{A}$, and the combined statistical uncertainty depends on the binary NS merger detection rate, and thus we include results assuming an upper, a central and a lower limit on this rate.
+The statistical uncertainties on $\lambda_0$ becomes comparable with the systematic uncertainty (set to be $P_{90}=13.19$) from using the improved binary Love relations with detectors of Voyager-class or better.
+}\label{tab:variances}
 \end{table*}
 
-Next, we repeat the process upon the injection of the IMRD + NRTidal waveform in order to demonstrate the effect of waveform mismodeling.
-The results are shown in Fig.~\ref{fig:stackedFisher} as maroon outlined circles (single detection uncertainties) and an outlined dashed maroon region (combined uncertainties from multiple detections).
-Observe the noticeable difference between the extraction efficiencies for the two different tidal corrections - highlighting the need for further waveform modeling for future interferometers.
-
-Concluding, we find that the Voyager, ET, and CE detectors all exhibit enough statistical uncertainty reduction that the systematics on $\lambda_0$ and $\tilde\Lambda$ introduced from using improved EoS-insensitive relations (found to be $13.19$ and $12.01$, respectively) no longer become negligible in the error budget.
-This implies that the use and further improvement of EoS-insensitive relations is not only justified, but necessary, for future binary NS merger detections.
-Additionally, we find that the effect of waveform mismodeling is indeed important for future observations as the statistical uncertainties continue to decrease.
-In Appendix~\ref{app:measurement}, we additionally investigate the dependence of the measurement accuracy on $\tilde\Lambda$ on the binary NS mass ratio $q$ for fixed chirp mass $\mathcal{M}=1.88\text{ M}_{\odot}$.
+But is the statistical error calculated here robust to mismodeling systematics in the template?
+We repeat the analysis above using an IMRD + NRTidal template model  and find results consistent with those presented above.
+Indeed, Fig.~\ref{fig:stackedFisher} shows the individual and combined statistical error on $\lambda_{0}$ when using this template model (maroon circles and dashed region).
+Observe that the accuracy to which $\lambda_{0}$ can be measured with this template model is systematically better than when using the IMRD+6PN model (by roughly a factor of two).
+This implies that more accurate template models will indeed be required in the third-generation detector era, as previously pointed out in~\cite{XXX} {\ny{CITE SOMEBODY}}.
+However, our conclusion that for Voyager-class detectors or better the statistical and binary Love systematic uncertainties become comparable seems robust.
 

### 2019-02-20 paper/bin-love-after-gw170817.tex
done

@@
 
-The recent GW observation of binary NS merger GW170817 placed constraints on the supranuclear matter EoS for NSs.
-We take advantage of this by generating a restricted set of spectral EoSs which agree with this observation in order to reduce the uncertainties upon the extraction of tidal parameters from future GW events.
-Important previous work by Yagi and Yunes~\cite{Yagi:ILQ,Yagi:binLove} found EoS-insensitive relations between symmetric and antisymmetric combinations of NS tidal deformabilities, which aid in the extraction of said tidal parameters.
-We find an improvement upon these EoS-insensitive relations by a factor of $\sim 59$\% for stars with mass ratios of $0.75$ by restricting to the EoS posterior samples from GW170817s 90\% credible region on pressure as a function of density.
-Similarly, we find an increase in C-Love and I-Love-Q universality by factors of $\sim 76$\% and $\sim 50$\%, respectively.
-These improvements on the I-Love-Q and C-Love relations can be very beneficial in many important analyses, including that done in Ref.~\cite{Kumar:2019xgp}, where constraints on the moment of inertia, tidal deformability, compactness, spin, and radius were found using such relations.
-We also show the relationship between the NS radius and its tidal deformability, computed directly from the C-Love relations.
-We find this relation to display a maximum uncertainty of $358.9\text{ m}$ from the fit discussed in Sec.~\ref{sec:clove}.
-Additionally, we find that hybrid quark-hadron star EoSs \emph{do} obey the I-Love-Q and C-Love relations, albeit with slightly higher maximum EoS variabilities as displayed in Tabs.~\ref{tab:hybridCompare} and ~\ref{tab:hybridCompareClove}.
-We additionally find that binaries consisting of one massive hybrid quark-hadron star, and one small-mass hadron star do not obey the binary Love relations -- explained by the large difference in $\tilde{\Lambda}$ displayed between the constituent stars.
-From this we state that the hybrid star EoSs do \emph{not} obey the binary Love relations.
-Future work currently in progress will attempt to remedy this through a series of new piecewise hybrid star binary Love relations.
-
-In the second half of this paper, we analyze the impact of this improvement for future binary NS merger detections.
-Currently detectors are not yet sensitive enough to accurately constrain $\tilde{\Lambda}$ for the improved EoS-insensitive relations to make a difference.
-We find that future interferometers Voyager, CE, and ET-D all experience a reduction in the statistical uncertainties upon the extraction of $\tilde{\Lambda}$ enough to become comparable to the systematic uncertainties injected through the use of improved EoS-insensitive relations, as depicted in Fig.~\ref{fig:stackedFisher} and Table~\ref{tab:variances}.
-Additionally, we considered the effect of waveform mismodeling by comparing Fisher analyses using two different tidal corrections to the PhenomD waveform: 6PN and NRTidal.
-Doing so revealed a noticeable difference between the extraction uncertainties derived under injection of each waveform - indicating the need for further waveform modeling.
-Finally, in Appendix~\ref{app:measurement} we investigate the effect of NS binary mass ratio q on the measurement accuracy of $\tilde\Lambda$.
-We find that the second generation interferometers lose accuracy as one increases the mass ratio, while the third generation detectors observe a large increase in accuracy due to the correlations between $\tilde\Lambda$ and $\delta\tilde\Lambda$.
-This indicates that the use and further improvement of EoS-insensitive relations is justified for future GW observations of binary NS merger events.
-
-Future work on this subject entails an investigation into the improvement of alternative EoS-insensitive relations, such as the multipole Love relations between various $l$-th order electric, magnetic, and shape tidal deformabilities as discussed in Ref.~\cite{Yagi:Multipole}.
-Additionally, Lackey \emph{et al}. presented surrogate models of non-spinning effective-one-body waveform models with the the use of universal relations in Refs.~\cite{Lackey:Surrogate, Lackey:EOB}.
-By reducing the number of required waveform model parameters, surrogate models aid in the extraction of NS observables from GW detections.
+The recent GW observation of a binary NS coalescence, GW170817, placed constraints on the supranuclear matter EoS for NSs.
+We used this observation to generate a restricted set of spectral EoSs that agree with it, in order to reduce the uncertainties upon the extraction of tidal parameters from future GW events.
+Previous work by Yagi and Yunes~\cite{Yagi:ILQ,Yagi:binLove} had found EoS-insensitive relations between symmetric and antisymmetric combinations of NS tidal deformabilities, which aid in the extraction of said tidal parameters.
+We here found that the GW170817-constrained set of EoSs are more EoS-insensitive by a factor of $\sim 60$\% for stars with mass ratios of $0.75$ relative to previous work.
+Similarly, we find an increase in EoS-insensitivity in the C-Love and I-Love-Q  relations by factors of $\sim 75$\% and $\sim 50$\% respectively.
+The former further allowed us to improve the R-Love relation leading to uncertainties below $400$ meters in the entire parameter space.
+We also studied the EoS-insensitive relations of hybrid stars and found that for the most part the relations remain insensitive for isolated stars, albeit with slightly higher EoS variability.
+The binary Love relations, however, do not satisfy the same EoS-insensitive relations as in the case of purely hadronic star, when the binary contains at least one hybrid star.
+
+The second half of this paper focused on when the improvements in the EoS-insensitive relations would become necessary in future detectors.
+Current detectors are not yet sensitive enough that the systematic uncertainties in the EoS-insensitive relations make a large difference.
+However, we did find that for Voyager-class detectors or better, the systematic uncertainties in the EoS-insensitive relations due to EoS variability become comparable to statistical uncertainties in the estimation of $\tilde{\Lambda}$ and $\lambda_{0}$.
+We also considered the effect of waveform mismodeling and found that the above conclusion remains robust, but that more accurate waveform models will be necessary to take full advantage of the improved sensitivity of future detectors.
+
+Future work on this subject could entail an investigation into the improvement of alternative EoS-insensitive relations, such as the multipole Love relations between various $\ell$-th order electric, magnetic, and shape tidal deformabilities, as discussed in~\cite{Yagi:Multipole}.
+Additionally, Lackey \emph{et al}~\cite{Lackey:Surrogate, Lackey:EOB} presented surrogate models of non-spinning effective-one-body waveforms with the the use of universal relations.
+By reducing the number of waveform model parameters, surrogate models aid in the extraction of NS observables from GW detections.
 The improvement in the multipole love relations can then be used to increase the accuracy of such surrogate models.
-Additionally, we plan on a more comprehensive analysis into the intricacies of new hybrid star binary Love relations, as discussed in Sec.~\ref{sec:binary}.
-Work along this direction is currently in progress.
+Another possible avenue for future research includes a more comprehensive analysis into the intricacies of new hybrid star binary Love relations.
 

### 2019-02-20 paper/bin-love-after-gw170817.tex
working on the error marg. section

--- 2019-02-20 paper/bin-love-after-gw170817.tex
@@
 \includegraphics[width=\columnwidth]{CL.eps}
-\includegraphics[width=\columnwidth]{RL.eps}
+\includegraphics[width=.96\columnwidth]{RL.eps}
 \end{center}
@@
 In the left panel, we also present the C-Love relations in the hybrid star cases (dashed green) for comparison, where observe that, although still EoS-insensitive, the degree of universality decreases.
-{\ny{Why is the size of the right panel larger than the left panel?}}
 }
@@
 \end{equation}
-Doing so, yields $a_0 = 0.3617$, $a_1 = -0.03548$, and $a_2 = 0.0006194$, similar to what was found in~\cite{Yagi:binLove} {\ny{Wait, this is for the constrained set or the unconstrained set?
-I'm guessing you used the constrained set, but we should say so here.}}.
+Doing so, yields $a_0 = 0.3617$, $a_1 = -0.03548$, and $a_2 = 0.0006194$ for the constrained set of EoSs, similar to what was found in~\cite{Yagi:binLove}.
 As in the I-Love-Q case, however, the above fitting function does not limit properly to the Newtonian result
@@
 
-\subsection{Marginalization over Uncertainties}\label{sec:marginalization}
-
-Let us begin by investigating the residuals on $\Lambda_a(\Lambda_s,q)$ and the induced residuals on $\lambda_{0}$, in order to marginalize over the intrinsic uncertainty found in the binary Love relations.
-In particular, we restrict our focus to only the constrained set of EoSs.
-Residuals in $\Lambda_a$ are computed as $\Lambda_a^{\text{relation}}(\Lambda_s,q)-\Lambda_a^{\text{true}}$, where $\Lambda_a^{\text{true}}$ corresponds to the true value predicted by the sampled EoSs, and $\Lambda_a^{\text{relation}}(\Lambda_s,q)$ corresponds to the fit found in Sec.~\ref{sec:binary}.
-We then convert the $\Lambda_a$ residuals into $\lambda_0$ residuals, as we describe below.
-
-{\ny{Please rewrite everything from here to Subsection B. It is not clear at all what you've done, why you've done it, and what you got.}}
-Following Ref.~\cite{Katerina:residuals}, we assume the residuals on $\Lambda_a$ observe a Gaussian distribution with mean and standard deviation given by:
+\subsection{Error Marginalization}\label{sec:marginalization}
+
+Although the improved binary Love relation $\Lambda_a^{\text{relation}}(\Lambda_s,q)$ shows high levels of accuracy, any residual errors in the relation could confuse deduction about the correct EoS.
+In this section, we offer a method for which readers can marginalize over the binary Love relations' intrinsic errors.
+This is done by investigating its residuals, which are defined to be $\Lambda_a^{\text{relation}}(\Lambda_s,q)-\Lambda_a^{\text{true}}$.
+Given sampled parameters $q$ and $\Lambda_s$, $\Lambda_a^{\text{relation}}(\Lambda_s,q)$ corresponds to the value found from the binary Love fit found in Sec.~\ref{sec:binary}, and $\Lambda_a^{\text{true}}$ corresponds to the true value predicted by the various sampled EoSs for the same values of $q$ and $\Lambda_s$
+
+Following the analysis done in Ref.~\cite{Katerina:residuals}, we assume that such residuals in $\Lambda_a$ observe a Gaussian distribution with mean and standard deviation given by:
 \begin{align}
@@
 \end{align}
-%The mean and standard deviation of the Gaussian distribution of the residuals on 
-We then fit the individual components using the following power functions {\ny{to what data? This is confusing}}:
+In order to find such relations, we generate data by sampling through various values of mass ratio $q\in \lbrack0.36,1\rbrack$.
+For each value of $q$ and $\Lambda_s$ sampled, the corresponding $\Lambda_a^{\text{true}}$ values for each of the 100 constrained EoS used in our analysis are computed, as well as the values of $\Lambda_a^{\text{relation}}$ from the binary Love fit.
+Lastly, we compute the residuals between the two as $\Lambda_a^{\text{relation}}(\Lambda_s,q)-\Lambda_a^{\text{true}}$.
+We then proceed to bin such residuals in both $q$ and $\Lambda_s$, computing the means $\mu(x)$ and standard deviations $\sigma(x)$ within each individual bin.
+The resulting distributions $\mu_{\Lambda_s}(\Lambda_s)$, $\mu_q(q)$, $\sigma_{\Lambda_s}(\Lambda_s)$, and $\sigma_q(q)$ can then be fit by the following power functions, as was done in Ref.~\cite{Katerina:residuals}:
 \begin{align}
@@
 \end{align}
-The fitting parameters $\mu_i$ and $\sigma_i$ are tabulated in Table~\ref{tab:marginalized}.
+The fitting parameters $\mu_i$ and $\sigma_i$ for these distributions are tabulated in Table~\ref{tab:marginalized}.
 
@@
 
-Now that we have obtained the residuals on $\Lambda_a$, we must convert them into residuals on the new tidal parameter $\lambda_0$, in order to compute and easily compare the systematic uncertainties to the statistical uncertainties on $\lambda_0$.
-{\ny{You need to say explicitly how you did this.}}
-Figure~\ref{fig:qLsResiduals} shows the standard deviations of these residuals (converted into $\lambda_0$) binned in both $q$ and $\Lambda_s$. 
-To estimate the overall systematic uncertainties on $\lambda_0$ accrued upon the use of the improved binary Love relations, we combine the uncertainties in both $q$ and $\Lambda_s$.
-Figure~\ref{fig:residuals} displays the un-binned Gaussian distribution of $\lambda_0$ residuals for both the constrained, and unconstrained sets of EoSs for comparison.
+Finally, in order to marginalize over such errors, one would compute $\Lambda_a$ given selected values of $q$ and $\Lambda_s$ like so:
+\begin{equation}
+\Lambda_a=\Lambda_a^{\text{relation}}(\Lambda_s,q)+\mathcal{N}(\mu(\Lambda_s,q),\sigma(\Lambda_s,q)),
+\end{equation}
+where $\mathcal{N}(\mu,\sigma)$ is a normal distribution with mean and variance $\mu$ and $\sigma^2$.
+
+However, for the extent of this analysis we are interested in obtaining an estimate for the amount of systematic uncertainties in $\lambda_0$ accrued upon the use of the improved binary Love relations.
+Such an approximation would allow us to compare the systematic and statistical uncertaintes in order to determine when the former will dominate the latter.
+Similar to what was previously done, we sample $q$ and $\Lambda_s$ in order compute the residuals from the binary Love fits in $\lambda_0$ as $\lambda_0^{\text{relation}}(\Lambda_s,q)-\lambda_0^{\text{true}}$.
+Figure~\ref{fig:residuals} displays the probability distribution of such $\lambda_0$ residuals (for both the constrained and unconstrained EoSs for comparison), which is observed to approximately obey a Gaussian distribution, as assumed.
 Observe how the standard deviations $\sigma=9.764$ and $\sigma=78.28$ show a large decrease from the unconstrained to the constrained sets of EoSs.
 Additionally, we find the 90th, 99th, and 100th percentiles on $\lambda_0$ to be $P_{90}=13.19$, $P_{99}=42.38$, and $P_{100}=111.32$ for the constrained EoSs.
-Because the un-binned residuals seen in Fig.~\ref{fig:residuals} are dominated by the low-error regions of the parameter space ($\Lambda_s \rightarrow 0$, $\Lambda_s \rightarrow \infty$, $q \rightarrow 0$ and $q \rightarrow 1$) shown by Fig.~\ref{fig:qLsResiduals}, we consider the 90th percentile uncertainty (indicated by the dashed green line in Fig.~\ref{fig:qLsResiduals}) for the remainder of the analysis, in order to further take into account the high-error regions of the parameter space ($\Lambda_s \sim 2000$, $q\sim0.5$).
-We take this value of $P_{90}=13.19$ to be the systematic measurement uncertainty introduced by using the improved binary Love relations on the parameter extraction of $\lambda_0$, indicated by the dashed indigo line in Fig.~\ref{fig:stackedFisher}.
+
+For demonstration purposes, Fig.~\ref{fig:qLsResiduals} displays the standard deviations of $\lambda_0$ residuals binned in $q$ and $\Lambda_s$, as was done previously for $\Lambda_s$ residuals.
+Observe how the uncertainties in $\lambda_0$ are dominated by the low-error regions of the parameter space ($\Lambda_s \rightarrow 0$, $\Lambda_s \rightarrow \infty$, $q \rightarrow 0$ and $q \rightarrow 1$).
+in order to take into account the high-error regions of the parameter space ($\Lambda_s \sim 2000$, $q\sim0.5$), we conservatively approximate the systematic error in the binary Love relations to be the 90th percentile uncertainty $P_{90}=13.19$ (indicated by the dashed green line in Fig.~\ref{fig:qLsResiduals} and the dashed indigo line in Fig.~\ref{fig:stackedFisher}) for the remainder of the analysis.
 Similarly, we derive the systematic measurement uncertainty on $\tilde\Lambda$ to be $12.01$, shown in Fig.~\ref{fig:singleFisherLt}.
@@
 In Sec.~\ref{sec:futureObservations}, we analyze this further and discuss when the systematic uncertainties from EoS-insensitive relations become comparable to the statistical uncertainties.
+
+\begin{figure}
+\begin{center} 
+\includegraphics[width=\columnwidth]{residuals.pdf}
+\end{center}
+\caption{
+Residuals on $\lambda_0$ computed as $\lambda_0^{\text{fit}}-\lambda_0^{\text{true}}$ for the binary Love relations modeled in Sec.~\ref{sec:binary} for both constrained and unconstrained sets of EoSs.
+These residuals obey Gaussian distributions centered at $\mu=-0.1530$ and $\mu=0.2710$ with standard deviations of $\sigma=9.764$ and $\sigma=78.28$ for the constrained and unconstrained sets of EoSs, respectively.
+These uncertainties correspond roughly to the systematic uncertainties introduced on the parameter extraction of $\lambda_0$ upon the use of binary Love relations.
+However, to take into account the systematic uncertainties found in high-error regions of the parameter space, we instead set the systematic uncertainty to be the 90th percentile, $P_{90}=13.19$.
+Observe that the systematic uncertainties from using the improved (constrained) binary Love relations are negligible compared to the statistical uncertainties accrued on parameter extraction from GW170817, found to be $\sigma_{\lambda_0}=170.1$.
+}
+\label{fig:residuals}
+\end{figure}
 
@@
 \label{fig:qLsResiduals}
-\end{figure}
-
-\begin{figure}
-\begin{center} 
-\includegraphics[width=\columnwidth]{residuals.pdf}
-\end{center}
-\caption{
-Residuals on $\lambda_0$ computed as $\lambda_0^{\text{fit}}-\lambda_0^{\text{true}}$ for the binary Love relations modeled in Sec.~\ref{sec:binary} for both constrained and unconstrained sets of EoSs.
-These residuals obey Gaussian distributions centered at $\mu=-0.1530$ and $\mu=0.2710$ with standard deviations of $\sigma=9.764$ and $\sigma=78.28$ for the constrained and unconstrained sets of EoSs, respectively.
-These uncertainties correspond roughly to the systematic uncertainties introduced on the parameter extraction of $\lambda_0$ upon the use of binary Love relations.
-However, to take into account the systematic uncertainties found in high-error regions of the parameter space, we instead set the systematic uncertainty to be the 90th percentile, $P_{90}=13.19$.
-Observe that the systematic uncertainties from using the improved (constrained) binary Love relations are negligible compared to the statistical uncertainties accrued on parameter extraction from GW170817, found to be $\sigma_{\lambda_0}=170.1$.
-}
-\label{fig:residuals}
 \end{figure}

### 2019-02-20 paper/bin-love-after-gw170817.tex
rewrote error marginalization section

@@
 \begin{center} 
-\includegraphics[width=\columnwidth]{EoSs.eps}
+\includegraphics[width=.97\columnwidth]{EoSs.eps}
 \includegraphics[width=\columnwidth]{hybridEoSs.eps}
@@
 Right: EoSs for ACS and ACB hybrid stars, each transitioning from a hadronic branch (corresponding to a pure hadronic-matter NS) into a quark-matter branch (quark-matter inner core surrounded by hadronic matter) at various transition pressures $P_{\text{tr}}$.
-{\ny{There shouldn't be a title in the figures, no?}}
 }
@@
 \end{align}
-{\ny{Zack, why did you pick a non-square matrix of coefficients to fit to? Typically, fits are better behaved when you stay with square matrices}}
-and $n = 0.743$, where we set $\alpha = 1$ {\ny{Zack, is this right?
-I think you didn't fit for $\alpha$, but rather you set it to unity, but you did fit to $n$.
-Please confirm.}} Unlike the individual I-Love-Q relations, the binary Love relations depend also depend on the mass ratio.
+{\zc{I'll Decide whether to use 3x3 or 3x2 coefficient matrices and change this (or not) later.}}
+where we set $n = 0.743$ and $\alpha = 1$ as was done in Ref.~\cite{Yagi:binLove}.
+Unlike the individual I-Love-Q relations, the binary Love relations depend also depend on the mass ratio.
 
@@
 
-We can extract two additional conclusions from from this Fig.~\ref{fig:binLove}.
+We can extract two additional conclusions from from Fig.~\ref{fig:binLove}.
 First, as the mass ratio becomes more extreme (i.e.~away from unity), the ranges of values that $\Lambda_s$ and $\Lambda_a$ can take decrease.
-This is because as $q$ decreases, there is a limited range of tidal deformabilities $\Lambda_{1,2}$ in the M-L relationships that satisfy the mass ratio constraint {\ny{What?
-I didn't understand the previous clause enough to rewrite it.}}, and thus, the allowed parameter space shrinks.
+This is because \textbf{as the separation between $m_1$ and $m_2$ increases, the effective number of possible $\Lambda_1(m_1)$-$\Lambda_2(m_2)$ configurations decrease}, and thus, the allowed parameter space shrinks.
 Second, the fit to the constrained set does not extend to as high values of $\Lambda_s$ as the fit to the unconstrained set does.
@@
 This is done by investigating its residuals, which are defined to be $\Lambda_a^{\text{relation}}(\Lambda_s,q)-\Lambda_a^{\text{true}}$.
-Given sampled parameters $q$ and $\Lambda_s$, $\Lambda_a^{\text{relation}}(\Lambda_s,q)$ corresponds to the value found from the binary Love fit found in Sec.~\ref{sec:binary}, and $\Lambda_a^{\text{true}}$ corresponds to the true value predicted by the various sampled EoSs for the same values of $q$ and $\Lambda_s$
+Given sampled parameters $\Lambda_s$ and $q$, $\Lambda_a^{\text{relation}}(\Lambda_s,q)$ corresponds to the value found from the binary Love fit found in Sec.~\ref{sec:binary}, and $\Lambda_a^{\text{true}}$ corresponds to the true value predicted by the various sampled EoSs for the same values of $q$ and $\Lambda_s$
 
@@
 However, for the extent of this analysis we are interested in obtaining an estimate for the amount of systematic uncertainties in $\lambda_0$ accrued upon the use of the improved binary Love relations.
-Such an approximation would allow us to compare the systematic and statistical uncertaintes in order to determine when the former will dominate the latter.
+Such an approximation would allow us to compare the systematic and statistical uncertainties in order to determine when the former will dominate the latter.
 Similar to what was previously done, we sample $q$ and $\Lambda_s$ in order compute the residuals from the binary Love fits in $\lambda_0$ as $\lambda_0^{\text{relation}}(\Lambda_s,q)-\lambda_0^{\text{true}}$.
@@
 Observe how the uncertainties in $\lambda_0$ are dominated by the low-error regions of the parameter space ($\Lambda_s \rightarrow 0$, $\Lambda_s \rightarrow \infty$, $q \rightarrow 0$ and $q \rightarrow 1$).
-in order to take into account the high-error regions of the parameter space ($\Lambda_s \sim 2000$, $q\sim0.5$), we conservatively approximate the systematic error in the binary Love relations to be the 90th percentile uncertainty $P_{90}=13.19$ (indicated by the dashed green line in Fig.~\ref{fig:qLsResiduals} and the dashed indigo line in Fig.~\ref{fig:stackedFisher}) for the remainder of the analysis.
+In order to take into account the high-error regions of the parameter space ($\Lambda_s \sim 2000$, $q\sim0.5$), we conservatively approximate the systematic error in the binary Love relations to be the 90th percentile uncertainty $P_{90}=13.19$ (indicated by the dashed green line in Fig.~\ref{fig:qLsResiduals} and the dashed indigo line in Fig.~\ref{fig:stackedFisher}) for the remainder of the analysis.
 Similarly, we derive the systematic measurement uncertainty on $\tilde\Lambda$ to be $12.01$, shown in Fig.~\ref{fig:singleFisherLt}.
@@
 
-Consider then a waveform template $h$ parametrized in terms of
+Consider then a waveform template $h$ parameterized in terms of
 \begin{equation}\label{eq:template}
@@
 \caption{
-Approximate signal-to-noise ratio $\rho^A_{\text{GW170817}}$ and ($1\sigma$ {\ny{Zack, 1 sigma or $90\%$?}}) statistical uncertainty on the extraction of $\lambda_{0}$ had a single event like GW170817 been observed by future interferometer $A$ and had interferometer $A$ observed $N_{A}$ events in a 1 year observation, using aLIGO, A\texttt{+}, Voyager, CE, and ET.
+Approximate signal-to-noise ratio $\rho^A_{\text{GW170817}}$ and ($1\sigma$) statistical uncertainty on the extraction of $\lambda_{0}$ had a single event like GW170817 been observed by future interferometer $A$ and had interferometer $A$ observed $N_{A}$ events in a 1 year observation, using aLIGO, A\texttt{+}, Voyager, CE, and ET.
 The number of events $N_{A}$, and the combined statistical uncertainty depends on the binary NS merger detection rate, and thus we include results assuming an upper, a central and a lower limit on this rate.
@@
 Observe that the accuracy to which $\lambda_{0}$ can be measured with this template model is systematically better than when using the IMRD+6PN model (by roughly a factor of two).
-This implies that more accurate template models will indeed be required in the third-generation detector era, as previously pointed out in~\cite{XXX} {\ny{CITE SOMEBODY}}.
+This implies that more accurate template models will indeed be required in the third-generation detector era, as previously pointed out in~\cite{Samajdar:NRTidal}.
 However, our conclusion that for Voyager-class detectors or better the statistical and binary Love systematic uncertainties become comparable seems robust.

### 2019-02-21 paper/bin-love-after-gw170817.tex
minor addition
rewrote confusing subsections

@@
 \end{align}
-{\zc{I'll Decide whether to use 3x3 or 3x2 coefficient matrices and change this (or not) later.}}
 where we set $n = 0.743$ and $\alpha = 1$ as was done in Ref.~\cite{Yagi:binLove}.
@@
 First, as the mass ratio becomes more extreme (i.e.~away from unity), the ranges of values that $\Lambda_s$ and $\Lambda_a$ can take decrease.
-This is because \textbf{as the separation between $m_1$ and $m_2$ increases, the effective number of possible $\Lambda_1(m_1)$-$\Lambda_2(m_2)$ configurations decrease}, and thus, the allowed parameter space shrinks.
+This is because as the separation between $m_1$ and $m_2$ increases, the effective number of possible $\Lambda_1(m_1)$-$\Lambda_2(m_2)$ configurations decrease, and thus, the allowed parameter space shrinks.
 Second, the fit to the constrained set does not extend to as high values of $\Lambda_s$ as the fit to the unconstrained set does.
@@
 
-Although the improved binary Love relation $\Lambda_a^{\text{relation}}(\Lambda_s,q)$ shows high levels of accuracy, any residual errors in the relation could confuse deduction about the correct EoS.
-In this section, we offer a method for which readers can marginalize over the binary Love relations' intrinsic errors.
-This is done by investigating its residuals, which are defined to be $\Lambda_a^{\text{relation}}(\Lambda_s,q)-\Lambda_a^{\text{true}}$.
-Given sampled parameters $\Lambda_s$ and $q$, $\Lambda_a^{\text{relation}}(\Lambda_s,q)$ corresponds to the value found from the binary Love fit found in Sec.~\ref{sec:binary}, and $\Lambda_a^{\text{true}}$ corresponds to the true value predicted by the various sampled EoSs for the same values of $q$ and $\Lambda_s$
-
-Following the analysis done in Ref.~\cite{Katerina:residuals}, we assume that such residuals in $\Lambda_a$ observe a Gaussian distribution with mean and standard deviation given by:
+Although the improved binary Love relation $\Lambda_a^{\text{relation}}(\Lambda_s,q)$ shows a high degree of universality, any residual EoS dependance in the relation could introduce a systematic bias and lead to incorrect inferences about the correct EoS.
+Let us then discuss a method to marginalize over the residual EoS-dependence of the binary Love relations.
+The residual is here defined as
+\begin{equation}
+\label{eq:residual}
+r(\Lambda_{s},q) \equiv \Lambda_a^{\text{relation}}(\Lambda_s,q)-\Lambda_a^{\text{true}}\,,
+\end{equation}
+where $\Lambda_a^{\text{relation}}(\Lambda_s,q)$ is given by the binary Love fit found in Sec.~\ref{sec:binary}, while $\Lambda_a^{\text{true}}$ is the true value predicted by choosing a particular EoS in the constrained set and solving for the tidal deformabilities numerically.
+
+Following the proposal in~\cite{Katerina:residuals}, one can model the residual EoS-sensitivity by enhancing the binary Love relations through 
+\begin{equation}
+\Lambda_a^{{\textrm{new relation}}}=\Lambda_a^{\text{relation}}(\Lambda_s,q)+\mathcal{N}(\mu_{r}(\Lambda_s,q),\sigma_{r}(\Lambda_s,q)),
+\end{equation}
+where $\mathcal{N}(\mu,\sigma)$ is a normal distribution with mean and variance $\mu_{r}$ and $\sigma_{r}^2$.
+Let us further assume that the residuals $r$ obey a Gaussian distribution with mean and standard deviation that can be decomposed as
 \begin{align}
-\mu_{\Lambda_a}(\Lambda_s,q) &=\frac{\mu_{\Lambda_s}(\Lambda_s)+\mu_{q}(q)}{2},\\ 
-\sigma_{\Lambda_a} &=\sqrt{\sigma_{\Lambda_s}^2(\Lambda_s) + \sigma_{q}^2(q)}. 
+\mu_{r}(\Lambda_s,q) &=\frac{\mu_{r}(\Lambda_s)+\mu_{r}(q)}{2},\\ 
+\sigma_{r}(\Lambda_s,q) &=\sqrt{\sigma_{r}^2(\Lambda_s) + \sigma_{r}^2(q)},
 \end{align}
-In order to find such relations, we generate data by sampling through various values of mass ratio $q\in \lbrack0.36,1\rbrack$.
-For each value of $q$ and $\Lambda_s$ sampled, the corresponding $\Lambda_a^{\text{true}}$ values for each of the 100 constrained EoS used in our analysis are computed, as well as the values of $\Lambda_a^{\text{relation}}$ from the binary Love fit.
-Lastly, we compute the residuals between the two as $\Lambda_a^{\text{relation}}(\Lambda_s,q)-\Lambda_a^{\text{true}}$.
-We then proceed to bin such residuals in both $q$ and $\Lambda_s$, computing the means $\mu(x)$ and standard deviations $\sigma(x)$ within each individual bin.
-The resulting distributions $\mu_{\Lambda_s}(\Lambda_s)$, $\mu_q(q)$, $\sigma_{\Lambda_s}(\Lambda_s)$, and $\sigma_q(q)$ can then be fit by the following power functions, as was done in Ref.~\cite{Katerina:residuals}:
+where $\mu_{r}(q)$ and $\mu_{r}(\Lambda_{s})$ are the means marginalized over $\Lambda_{s}$ and $q$ respectively, while $\sigma_{r}(q)$ and $\sigma_{r}(\Lambda_{s})$ are the standard deviations marginalized over $\Lambda_{s}$ and $q$ respectively.
+
+Clearly then, to account for the residual EoS-sensitivity, we must first find the marginalized mean and standard deviation of the residual function, which we accomplish as follows.
+We first generate $\Lambda_{s}^{\textrm{true}}$ data by sampling through various values of mass ratio $q\in \lbrack0.36,1\rbrack$ and symmetric tidal deformability $\Lambda_{s} \in \lbrack XXX,XXX\rbrack$ {\ny{Please complete}} over all 100 elements of the constrained set of EoSs.
+For each value of $(q,\Lambda_{s})$ we then compute $\Lambda_{a}^{\textrm{relation}}$ from the binary Love relation, and then compute the residuals through Eq.~\eqref{eq:residual}.
+We then proceed to marginalize over $q$ by binning the residuals in $\Lambda_{s}$, which returns a distribution of residuals that is only a function of the binned $\Lambda_{s}$, and from which we can compute the mean $\mu_{s}(\Lambda_{s})$ and the standard deviation $\sigma_{r}(\Lambda_{s})$.
+Repeating this procedure by marginalizing over $\Lambda_{s}$ then allows us to compute the mean $\mu_{s}(q)$ and the standard deviation $\sigma_{r}(q)$.
+Finally, we fit the means and standard deviations to the functions~\cite{Katerina:residuals}
 \begin{align}
-\mu_{\Lambda_s}(x) &= \mu_1 x + \mu_2, \label{eq:margFit1}\\ 
-\mu_{q}(x) &= \mu_3 x^2 + \mu_4 x + \mu_5, \label{eq:margFit2}\\ 
-\sigma_{\Lambda_s}(x) &= \sigma_1 x^{5/2} + \sigma_2 x^{3/2} + \sigma_3 x \sigma_4 x^{1/2} + \sigma_5, \label{eq:margFit3}\\ 
-\sigma_{q}(x) &= \sigma_6 x^3 + \sigma_7 x^2 + \sigma_8 x + \sigma_9. \label{eq:margFit4}
+\mu_{r}(\Lambda_s) &= \mu_1 \Lambda_s + \mu_2, \label{eq:margFit1}\\ 
+\mu_{r}(q) &= \mu_3 q^2 + \mu_4 q + \mu_5, \label{eq:margFit2}\\ 
+\sigma_{r}(\Lambda_s) &= \sigma_1 \Lambda_s^{5/2} + \sigma_2 \Lambda_s^{3/2} + \sigma_3 \Lambda_s +  \sigma_4 \Lambda_s^{1/2} + \sigma_5, \label{eq:margFit3}\\ 
+\sigma_{r}(q) &= \sigma_6 q^3 + \sigma_7 q^2 + \sigma_8 q + \sigma_9, 
+\label{eq:margFit4}
 \end{align}
-The fitting parameters $\mu_i$ and $\sigma_i$ for these distributions are tabulated in Table~\ref{tab:marginalized}.
+where the fitting parameters $\mu_i$ and $\sigma_i$ are tabulated in Table~\ref{tab:marginalized}.
 
@@
 
-Finally, in order to marginalize over such errors, one would compute $\Lambda_a$ given selected values of $q$ and $\Lambda_s$ like so:
-\begin{equation}
-\Lambda_a=\Lambda_a^{\text{relation}}(\Lambda_s,q)+\mathcal{N}(\mu(\Lambda_s,q),\sigma(\Lambda_s,q)),
-\end{equation}
-where $\mathcal{N}(\mu,\sigma)$ is a normal distribution with mean and variance $\mu$ and $\sigma^2$.
-
-However, for the extent of this analysis we are interested in obtaining an estimate for the amount of systematic uncertainties in $\lambda_0$ accrued upon the use of the improved binary Love relations.
-Such an approximation would allow us to compare the systematic and statistical uncertainties in order to determine when the former will dominate the latter.
-Similar to what was previously done, we sample $q$ and $\Lambda_s$ in order compute the residuals from the binary Love fits in $\lambda_0$ as $\lambda_0^{\text{relation}}(\Lambda_s,q)-\lambda_0^{\text{true}}$.
-Figure~\ref{fig:residuals} displays the probability distribution of such $\lambda_0$ residuals (for both the constrained and unconstrained EoSs for comparison), which is observed to approximately obey a Gaussian distribution, as assumed.
-Observe how the standard deviations $\sigma=9.764$ and $\sigma=78.28$ show a large decrease from the unconstrained to the constrained sets of EoSs.
-Additionally, we find the 90th, 99th, and 100th percentiles on $\lambda_0$ to be $P_{90}=13.19$, $P_{99}=42.38$, and $P_{100}=111.32$ for the constrained EoSs.
-
-For demonstration purposes, Fig.~\ref{fig:qLsResiduals} displays the standard deviations of $\lambda_0$ residuals binned in $q$ and $\Lambda_s$, as was done previously for $\Lambda_s$ residuals.
-Observe how the uncertainties in $\lambda_0$ are dominated by the low-error regions of the parameter space ($\Lambda_s \rightarrow 0$, $\Lambda_s \rightarrow \infty$, $q \rightarrow 0$ and $q \rightarrow 1$).
-In order to take into account the high-error regions of the parameter space ($\Lambda_s \sim 2000$, $q\sim0.5$), we conservatively approximate the systematic error in the binary Love relations to be the 90th percentile uncertainty $P_{90}=13.19$ (indicated by the dashed green line in Fig.~\ref{fig:qLsResiduals} and the dashed indigo line in Fig.~\ref{fig:stackedFisher}) for the remainder of the analysis.
-Similarly, we derive the systematic measurement uncertainty on $\tilde\Lambda$ to be $12.01$, shown in Fig.~\ref{fig:singleFisherLt}.
-Currently, the statistical uncertainty of $170.1$ on $\lambda_0$ from GW170817 dominates the error budget compared to the systematic uncertainty of $13.19$, as seen in Fig.~\ref{fig:stackedFisher}.
-This means that, for the current ``O2" detector sensitivity, the use of improved binary Love relations will only make a negligible difference on the extraction of $\tilde\Lambda$.
-However, future detectors (for example aLIGO at design sensitivity, A\texttt{+}, Voyager, CE, and ET) are planned with large reductions in sensitivity - both decreasing the statistical uncertainties and allowing for larger binary NS merger detection rates; further reducing the statistical uncertainties.
-In Sec.~\ref{sec:futureObservations}, we analyze this further and discuss when the systematic uncertainties from EoS-insensitive relations become comparable to the statistical uncertainties.
+In what follows, however, we will be interested in comparing an estimate of the systematic uncertainties in $\lambda_0$ due to the residual EoS-sensitivity in the binary Love relations to the statistical error in the extraction of this parameter.
+To estimate the former, we first numerically calculate $\lambda_{0}^{\textrm{true}}$ by sampling again in $(q,\Lambda_{s})$ within the same ranges as before and over all 100 elements of the constrained and the unconstrained sets of EoSs.
+We then use the binary Love relation to calculate $\lambda_0^{\text{relation}}$ over the $(q,\Lambda_{s})$ sampled points, and from this we compute the residual.
+\begin{equation}
+{\cal{R}}(\Lambda_{s},q) = \lambda_0^{\text{relation}}(\Lambda_s,q)-\lambda_0^{\text{true}}.
+\end{equation}
+Figure~\ref{fig:residuals} shows a histogram of ${\cal{R}}$ for both the constrained and unconstrained set of EoSs, which approximately obeys a Gaussian distribution.
+The standard deviations of the two histograms, $\sigma=9.764$ and $\sigma=78.28$, show a large decrease in EoS-variability from the unconstrained to the constrained sets of EoSs.
+From this distribution, we can additionally find the 90\%, 99\%, and 100\% credible interval on $\lambda_0$, namely $P_{90}=13.19$, $P_{99}=42.38$, and $P_{100}=111.32$ for the constrained EoSs.
+
+Figure~\ref{fig:qLsResiduals} shows the standard deviations of the $\lambda_0$ residuals binned in $q$ (top panel) and $\Lambda_{s}$ (bottom panel), as was done previously for the $\Lambda_a$ residuals.
+Observe how the EoS-variability in $\lambda_0$ is dominated by the region around $q \sim 0.5$ and $\Lambda_{s} \sim 2,000$.
+Henceforth, we approximate the EoS-variability in the binary Love relations with the 90\% credible interval, which for the $\lambda_{0}$ parameter is $P_{90}=13.19$ (indicated by the dashed green line in Fig.~\ref{fig:qLsResiduals} and the dashed indigo line in Fig.~\ref{fig:stackedFisher}).
+We can similarly derive a conservative estimate of the systematic uncertainty due to EoS-variability in the binary Love relations in terms of $\tilde\Lambda_{a}$ to find $12.01$, which is what we use later in Fig.~\ref{fig:singleFisherLt}.
 

### 2019-02-21 paper/bin-love-after-gw170817.tex
replying to Nicos comments

@@
 
-%In the current analysis, we consider EoSs which have been constrained by the recent binary neutron star merger event, GW170817.
-%Important recent work by the LIGO Collaboration~\cite{LIGO:posterior,Carney:2018sdv} sampled the EoS parameter space in order to derive a marginalized posterior on the pressure as a function of mass density, as seen in Fig.
-2 of~\cite{LIGO:posterior}.
-%The spectral coefficients were sampled within the ranges: $\gamma_0 \in \lbrack 0.2,2 \rbrack$, $\gamma_1 \in \lbrack -1.6,1.7 \rbrack$, $\gamma_2 \in \lbrack -0.6,0.6 \rbrack$, $\gamma_3 \in \lbrack -0.02,0.02 \rbrack$, and further restricted the adiabatic index to be $\Gamma \in \lbrack 0.6,4.5 \rbrack$, ensuring the parameterization exposed a wide range of viable EoSs~\cite{Lindblom:parameters}.
-%Additional constraints imposed upon the generated EoSs were as follows~\cite{LIGO:posterior}: (i) causality within 10\%, and (ii) EoS priors must support NS masses up to $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations~\cite{Zhao:massiveNS}.
-%We utilize a random set of 100 of the above posterior samples defined by GW170817, furthermore referenced as the ``constrained EoSs", as shown in Fig.~\ref{fig:eos}.
-%For comparison, we also include a second sample of 100 ``unconstrained" EoSs, randomly sampled in the pressure-density plane to be unrestricted by GW170817s posterior.
-%Following~\cite{Read2009}, the parameterized high-density core EoSs generated above are matched to the low-density crust EoS of Sly~\cite{Douchin:2001sv} at about half of the nuclear saturation density, $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$.
-
 In addition, we investigate 10 transitional quark-hadron matter stars, which undergo strong first-order phase transitions at a pressure $P_{\text{tr}}$, leading to the hadronic branch departing into a quark-matter branch at a given transitional mass~\cite{Paschalidis2018,Alford:2017qgh,1971SvA....15..347S,Zdunik:2012dj,Alford:2013aca}.
@@
 
-Although the improved binary Love relation $\Lambda_a^{\text{relation}}(\Lambda_s,q)$ shows a high degree of universality, any residual EoS dependance in the relation could introduce a systematic bias and lead to incorrect inferences about the correct EoS.
+Although the improved binary Love relation $\Lambda_a^{\text{relation}}(\Lambda_s,q)$ shows a high degree of universality, any residual EoS dependence in the relation could introduce a systematic bias and lead to incorrect inferences about the correct EoS.
 Let us then discuss a method to marginalize over the residual EoS-dependence of the binary Love relations.
@@
 Clearly then, to account for the residual EoS-sensitivity, we must first find the marginalized mean and standard deviation of the residual function, which we accomplish as follows.
-We first generate $\Lambda_{s}^{\textrm{true}}$ data by sampling through various values of mass ratio $q\in \lbrack0.36,1\rbrack$ and symmetric tidal deformability $\Lambda_{s} \in \lbrack XXX,XXX\rbrack$ {\ny{Please complete}} over all 100 elements of the constrained set of EoSs.
+We first generate $\Lambda_{s}^{\textrm{true}}$ data by sampling through various values of mass ratio $q\in \lbrack0.36,1\rbrack$ and symmetric tidal deformability $\Lambda_{s} \in \lbrack 4,4600 \rbrack$ over all 100 elements of the constrained set of EoSs.
 For each value of $(q,\Lambda_{s})$ we then compute $\Lambda_{a}^{\textrm{relation}}$ from the binary Love relation, and then compute the residuals through Eq.~\eqref{eq:residual}.

### 2019-02-22 paper/bin-love-after-gw170817.tex
relabeled figs 6 and 7 to Nicos new residual formalism

@@
 \caption{
-Residuals on $\lambda_0$ computed as $\lambda_0^{\text{fit}}-\lambda_0^{\text{true}}$ for the binary Love relations modeled in Sec.~\ref{sec:binary} for both constrained and unconstrained sets of EoSs.
+Residuals on $\lambda_0$ computed as $\mathcal{R}=\lambda_0^{\text{relation}}-\lambda_0^{\text{true}}$ for the binary Love relations modeled in Sec.~\ref{sec:binary} for both constrained and unconstrained sets of EoSs.
 These residuals obey Gaussian distributions centered at $\mu=-0.1530$ and $\mu=0.2710$ with standard deviations of $\sigma=9.764$ and $\sigma=78.28$ for the constrained and unconstrained sets of EoSs, respectively.
@@
 \begin{center} 
-\includegraphics[width=\columnwidth]{qResiduals.eps}
-\includegraphics[width=\columnwidth]{LsResiduals.eps}
+\begin{overpic}[width=\columnwidth]{qResiduals.eps}
+\put(7,94){\tiny\rotatebox{90}{$\mathcal{R}$}}
+\end{overpic}
+\begin{overpic}[width=\columnwidth]{LsResiduals.eps}
+\put(7,95){\tiny\rotatebox{90}{$\mathcal{R}$}}
+\end{overpic}
 \end{center}
-\caption{$\lambda_0$ residuals binned in $q$ (top) and $\Lambda_s$ (bottom), highlighting the different error weights across the entire $(q,\Lambda_s)$ parameter space.
+\caption{Standard deviations of the $\lambda_0$ residuals $\mathcal{R}$ binned in $q$ (top) and $\Lambda_s$ (bottom), highlighting the different error weights across the entire $(q,\Lambda_s)$ parameter space.
 In this figure, the violet circles indicate the standard deviation of each bin in $q$-space ($\Lambda_s$-space), while the solid black lines represent the best fit given by Eqs.

### 2019-02-23 paper/bin-love-after-gw170817.tex
katerina comments intro

@@
 Unfortunately, terrestrial experiments can only probe the EoS to around nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy}.
-Although some temperature-dependent heavy-ion collision experiments are beginning to probe higher densities~\cite{Danielewicz:2002pu}, astrophysical observations of NSs remain ideal for constraining the EoS of cold and ultra dense, nuclear matter.
+Although some temperature-dependent heavy-ion collision experiments can probe higher densities~\cite{Danielewicz:2002pu}, astrophysical observations of NSs remain ideal for constraining the EoS of cold and ultra dense, nuclear matter.
 
@@
 The GWs emitted by binary NSs in the late inspiral must then depend on the \emph{tidal deformabilities} $\Lambda_1$ and $\Lambda_2$, which control the linear response of the star's quadrupole deformation to the (electric-type, quadrupole) tidal field of the companion (to leading order in a post-Newtonian expansion~\cite{Blanchet:2013haa})~\cite{Flanagan2008,Vines:2011ud}.
-These parameters, however, enter the GW Fourier model multiplied by the same function of the GW frequency (at leading post-Newtonian order), making them degenerate, and thus, very difficult to estimate independently with current GW data~\cite{Wade:tidalCorrections}.
-Instead, one can extract certain combinations of the tidal deformabilities, like a certain mass-weighted tidal deformability $\tilde{\Lambda}$~\cite{Favata:2013rwa,Wade:tidalCorrections}, or one can extract the (mass-independent) coefficients $(\lambda_{0},\lambda_{1},\ldots)$ of a Taylor expansion of the tidal deformabilities about some fiducial mass~\cite{delPozzo:TaylorTidal,Yagi:binLove}.
+\sout{These parameters, however, enter the GW Fourier model multiplied by the same function of the GW frequency} \kc{that's not correct, the "function" depends on the mass ratio} These parameters, however, enter the GW Fourier model at the same post-Newtonian order, making them degenerate, and thus, very difficult to estimate independently with current GW data~\cite{Wade:tidalCorrections}.
+Instead, one can extract certain combinations of the tidal deformabilities, such as a certain mass-weighted tidal deformability $\tilde{\Lambda}$~\cite{Favata:2013rwa,Wade:tidalCorrections}, or one can extract the (mass-independent) coefficients $(\lambda_{0},\lambda_{1},\ldots)$ of a Taylor expansion of the tidal deformabilities about some fiducial mass~\cite{delPozzo:TaylorTidal,Yagi:binLove}.
 Current detectors are not sensitive enough to accurately measure any of these coefficients, but future detectors will and the information from multiple events could then be combined, since the Taylor expansion coefficient should be common to all events.
@@
 Lacking enough sensitivity in current GW observations, one is forced to only estimate the mass-weighted tidal deformability, but this prevents the independent extraction of $\Lambda_{1}$ and $\Lambda_{2}$.
-Yagi and Yunes~\cite{Yagi:binLove} solved this problem by finding ``approximately universal'' or ``EoS-insensitive'' relations between the symmetric and anti-symmetric combinations of the tidal deformabilities $\Lambda_{s,a}=\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$, the so-called ``binary Love relations." These relations can be used to analytically express $\Lambda_{s}$ in terms of $\Lambda_{a}$ (or vice-versa), making the mass-weighted tidal deformability a function of only $\Lambda_{a}$.
+Yagi and Yunes~\cite{Yagi:binLove} \sout{solved} \kc{proposed a solution to this problem} this problem by finding ``approximately universal'' or ``EoS-insensitive'' relations between the symmetric and anti-symmetric combinations of the tidal deformabilities $\Lambda_{s,a}=\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$, the so-called ``binary Love relations." These relations can be used to analytically express $\Lambda_{s}$ in terms of $\Lambda_{a}$ (or vice-versa), making the mass-weighted tidal deformability a function of only $\Lambda_{a}$.
 A measurement of the mass-weighted tidal deformability then implies a measurement of $\Lambda_{a}$, and through the use of the binary Love relations, also a measurement of $\Lambda_{s}$, which then allows for the inference of the individual tidal deformabilities $\Lambda_{1}$ and $\Lambda_{2}$~\cite{Yagi:binLove}.
 With those at hand, one can further use EoS-insensitive relations between the tidal deformabilities and the compactness, the so-called ``C-Love relations''~\cite{Yagi:ILQ}, to infer the radii of the NSs, and thus, to place two constraints in the mass-radius plane, one for each star in the binary~\cite{Yagi:binLove}.
-This idea was recently implemented in GW170817, allowing for the first EoS-independent constraints on the mass-radius curve using GW data~\cite{LIGO:posterior}.
+This idea was recently implemented in GW170817, allowing for an EoS-independent constraints on the mass-radius curve using GW data~\cite{Katerina:residuals,LIGO:posterior}.
 
 EoS-insensitive relations can in fact be used for more than just measuring the nuclear EoS.
-For years, the theoretical physics community considered the possibility of using measurements of NS properties, like the mass, the radius and the moment of inertia, to constrain deviations from General Relativity in the strong-field regime.
-Certain modified theories of gravity, like scalar tensor theories with spontaneous scalarization~\cite{Damour:1996ke}, Einstein-Aether and Horava gravity~\cite{Eling:2007xh,Yagi:2013ava,Yagi:2013qpa}, dynamical Chern-Simons gravity~\cite{Yunes:2009ch}, beyond Horndesky theories~\cite{Sakstein:2016oel}, modify such NS observables, but unfortunately, these modifications are typically degenerate with the nuclear EoS.
-Yagi and Yunes solved this problem by finding EoS-insensitive relations between the moment of inertia, the tidal deformability (or Love number) and the quadrupole moment, the so-called ``I-Love-Q'' relations~\cite{Yagi:ILQ}.
+For years, the theoretical physics community considered the possibility of using measurements of NS properties, such as the mass, the radius and the moment of inertia, to constrain deviations from General Relativity in the strong-field regime.
+Certain modified theories of gravity, such as scalar tensor theories with spontaneous scalarization~\cite{Damour:1996ke}, Einstein-Aether and Horava gravity~\cite{Eling:2007xh,Yagi:2013ava,Yagi:2013qpa}, dynamical Chern-Simons gravity~\cite{Yunes:2009ch}, beyond Horndesky theories~\cite{Sakstein:2016oel}, modify such NS observables, but unfortunately, these modifications are typically degenerate with the nuclear EoS.
+Yagi and Yunes \sout{solved} \kc{proposed to solve} this problem by finding EoS-insensitive relations between the moment of inertia, the tidal deformability (or Love number) and the quadrupole moment, the so-called ``I-Love-Q'' relations~\cite{Yagi:ILQ}.
 Given a measurement of the Love number for a given NS, for example through GW observations, the I-Love-Q relations can be used to infer the moment of inertia or the quadrupole moment.
@@
 We begin by investigating the increase in EoS insensitivity due to the constraints placed by GW170817 on the allowed space of EoSs.
-We take the 90\% credible region constructed from the posterior probability distributions on the pressure-density plane~\cite{LIGO:posterior} obtained from GW170817~\cite{TheLIGOScientific:2017qsa} as a prior on the set of EoSs that is compatible with this observation.
+We take the 90\% credible region constructed from the posterior probability distributions on the pressure-density plane~\cite{Carney:2018sdv,LIGO:posterior} obtained from GW170817~\cite{TheLIGOScientific:2017qsa} as a prior on the set of EoSs that is compatible with this observation.
 We then generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, one in which this prior is enforced (the ``constrained'' sample) and another in which the prior is not enforced (the ``unconstrained'' sample).
@@
 
-Last for not least, we study the importance of using the improved EoS-insensitive relations in future GW observations.
+Last but not least, we study the importance of using the improved EoS-insensitive relations in future GW observations.
 The use of EoS-insensitive relations introduces systematic uncertainties in parameter estimation because of the intrinsic non-zero EoS-variability in these relations, which one must marginalize over.
@@
 But as the detector sensitivity is improved, the signal-to-noise ratio and the number of events that will be detected will increase, therefore decreasing the statistical uncertainties below the systematic one due to EoS variability.
-We carry out a simple Fisher analyses to estimate when the statistical uncertainties become comparable to the systematic uncertainties due to EoS variability and find that this occurs for Voyager-class detectors.
+We carry out a \sout{simple} Fisher analyses to estimate when the statistical uncertainties become comparable to the systematic uncertainties due to EoS variability and find that this occurs for Voyager-class detectors.
 
 Figure~\ref{fig:stackedFisher} shows this result in more detail.
-We here present the (Fisher-estimated) statistical uncertainty in the measurement of $\lambda_{0}$ with various detectors (LIGO O2~\cite{aLIGO}, Advanced LIGO at design sensitivity (aLIGO)~\cite{aLIGO}, LIGO A\texttt{+} (A\texttt{+})\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, the Einstein Telescope (ET)~\cite{ET}, and the Cosmic Explorer (CE)~\cite{Ap_Voyager_CE}) for an event identical to GW170817.
+We present the (Fisher-estimated) statistical uncertainty in the measurement of $\lambda_{0}$ with various detectors (LIGO O2~\cite{aLIGO}, Advanced LIGO at design sensitivity (aLIGO)~\cite{aLIGO}, LIGO A\texttt{+} (A\texttt{+})\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, the Einstein Telescope (ET)~\cite{ET}, and the Cosmic Explorer (CE)~\cite{Ap_Voyager_CE}) for an event \sout{identical to} similar to GW170817.
 The x-axis shows the signal-to-noise ratio for a GW170817 event detected with each of these detectors.
-We also present the combined statistical uncertainty $\sigma^A_N$ after $N$ detections with each of these instruments, with the top and bottom of the region representing the most optimistic and pessimistic expectation for the number of detections expected from the binary NS merger rate (see also Table~\ref{tab:variances}).
+We also present the combined statistical uncertainty $\sigma^A_N$ after $N$ detections with each of these instruments, with the top and bottom of the region representing the most optimistic and pessimistic expectation for the number of detections expected from the binary NS merger rate \kc{add citation for the merger rate} (see also Table~\ref{tab:variances}).
 These statistical uncertainties should be compared to the systematic uncertainty in $\lambda_{0}$ due to EoS-variability improved with the constrained set.
-Observe that the statistical and the systematic uncertainties cross for Voyager-class detectors.
+We find that the statistical and the systematic uncertainties cross for Voyager-class detectors.
 

### 2019-02-23 paper/bin-love-after-gw170817.tex
katerina comments sec 2

@@
 \caption{(Color Online) Left: Small representative samples of the unconstrained (dotted) and constrained (solid) sets, together with the 90\% marginalized posterior distribution from the observation of GW170817 (cyan shaded region)~\cite{LIGO:posterior}.
-Observe that the there is significantly less variability in the constrained set of EoSs due to the requirement that they be consistent with the GW170817 observation.
+There is significantly less variability in the constrained set of EoSs due to the requirement that they be consistent with the GW170817 observation.
 Right: EoSs for ACS and ACB hybrid stars, each transitioning from a hadronic branch (corresponding to a pure hadronic-matter NS) into a quark-matter branch (quark-matter inner core surrounded by hadronic matter) at various transition pressures $P_{\text{tr}}$.
@@
 The constrained set is defined in a similar way, with the addition of the restriction that the resulting EoS be inside the 90\% marginalized posterior distribution on the pressure-mass density plane derived from the GW170817 observation~\cite{LIGO:posterior,Carney:2018sdv}  (see Fig.~2 in~\cite{LIGO:posterior}).
-In both cases, each set consists of 100 members, with a subset of these shown in the left panel of Fig.~\ref{fig:eos}.
+In both cases, each set consists of 100 members, with a subset of these shown in the left panel of Fig.~\ref{fig:eos}.\kc{wait, aren't you using the samples that Calr sent you directly?
+If yes we need to describe how they were computed and add the appropriate citations to code and data.
+But that's not what you are describing here}
 

### 2019-02-24 paper/bin-love-after-gw170817.tex
katerina comments sec 3

@@
 The bottom panels show the relative fractional difference between the fit and the data for each set of EoSs.
-Observe that the new fits to the constrained set shows considerable more EoS-insensitivity than that fit to the unconstrained set.
+The new fits to the constrained set shows considerable more EoS-insensitivity than that fit to the unconstrained set.
 These results are summarized in Table~\ref{tab:maxVar}, which tabulates the maximum EoS variation in each fit.
@@
 In these figures, the black dashed lines corresponds to the fits given by Eq.~\ref{eq:ILQfitNew}.
-Observe how the fractional difference from the fits, shown in the bottom panels, is greatly suppressed for the constrained case, compared to both the unconstrained case, and results from previous works~\cite{Yagi:ILQ}.
+The fractional difference from the fits, shown in the bottom panels, is greatly suppressed for the constrained case, compared to both the unconstrained case, and results from previous works~\cite{Yagi:ILQ}.
 The maximal EoS variation from the fits for the unconstrained and constrained sets of EoSs are compared in Tab.~\ref{tab:maxVar}.
@@
 The maximum absolute EoS variation is also reported in the C-Love, R-Love and binary Love cases in parenthesis.
-Observe that the maximum variation in the constrained set case is better than a factor of two smaller than the variability in the unconstrained case and in previous work.
+The maximum variation in the constrained set case is better than a factor of two smaller than the variability in the unconstrained case and in previous work.
 The maximum EoS variation in the unconstrained set is slightly larger than that found in previous work because the former is built from a large random sampling of EoSs.
@@
 The fractional differences for the second case (fit to only the constrained EoSs) is shown with dashed green lines in Fig.~\ref{fig:ILQ}, while the maximum EoS variation for the I-Love relation is shown in Table~\ref{tab:hybridCompare} for both the constrained and hybrid star cases.
-Observe how the hybrid star EoSs obey the I-Love-Q relations in each case to better than $\sim1.7$\%, a variability that is slightly higher than that found when using only nuclear matter EoSs in previous works~\cite{Yagi:ILQ}.
-Observe also that the universality cannot be improved much through the introduction of new fits, only bringing the maximal EoS variation down to $\sim1$\% for the fits constructed with only hybrid star EoSs.
+The hybrid star EoSs obey the I-Love-Q relations in each case to better than $\sim1.7$\%, a variability that is slightly higher than that found when using only nuclear matter EoSs in previous works~\cite{Yagi:ILQ}.
+The universality cannot be improved much through the introduction of new fits, only bringing the maximal EoS variation down to $\sim1$\% for the fits constructed with only hybrid star EoSs.
 From this study, we conclude that hybrid star EoSs \emph{do} obey the traditional nuclear I-Love-Q relations computed with nuclear EoS data, albeit with a slight decrease in universality to $\sim1.7$\%.
@@
 Similar to Fig.~\ref{fig:ILQ} but for the C-Love (left) and the R-Love relations (right), with the bottom panels showing the \emph{absolute differences} (rather than fractional difference as in Fig.~\ref{fig:ILQ}) from the fit.
-Observe how the absolute difference is suppressed in the constrained set case relative to the unconstrained set, and results from previous work~\cite{Yagi:binLove}.
-In the left panel, we also present the C-Love relations in the hybrid star cases (dashed green) for comparison, where observe that, although still EoS-insensitive, the degree of universality decreases.
+The absolute difference is suppressed in the constrained set case relative to the unconstrained set, and results from previous work~\cite{Yagi:binLove}.
+In the left panel, we also present the C-Love relations in the hybrid star cases (dashed green) for comparison, where, although still EoS-insensitive, the degree of universality decreases.
 }
@@
 
-From the C-Love relations, we can also compute directly the R-Love relation using $R(\Lambda)=M/C(\Lambda)$ and for a fixed NS mass $M$.
-The right panel of Fig.~\ref{fig:clove} shows the R-Love relation for the constrained and unconstrained sets fixing $M=1.48\text{ M}_{\odot}$ at the observed value for one of the NSs in the GW170817 event, with the bottom panel showing the absolute difference of the data and the fits.
-Observe that the C-Love relations allow us to infer the NS radius to better than $\sim 350 \textrm{m} $ in the constrained case, while the error goes up to $1,000 \textrm{m}$ in the unconstrained case, as also tabulated in Table~\ref{tab:maxVar}.
+From the C-Love relations, we can also compute directly the R-Love relation using $R(\Lambda)=M/C(\Lambda)$ and for a fixed\kc{fixed in what sense?} NS mass $M$.
+The right panel of Fig.~\ref{fig:clove} shows the R-Love relation for the constrained and unconstrained sets fixing $M=1.48\text{ M}_{\odot}$\kc{??????} at the observed value for one of the NSs in the GW170817 event, with the bottom panel showing the absolute difference of the data and the fits.
+The C-Love relations allow us to infer the NS radius to better than $\sim 350 \textrm{m} $ in the constrained case, while the error goes up to $1,000 \textrm{m}$ in the unconstrained case, as also tabulated in Table~\ref{tab:maxVar}.
 The systematic uncertainty in the radius using the constrained fit is thus comparable to the $\sim 140\textrm{m}$ systematic uncertainty in the radius due to the choice of EoS to model the crust~\cite{Gamba:2019kwu}.
@@
 The left panel of Fig.~\ref{fig:clove} shows the C-Love relation when fitting only to the constrained set (dashed green curves).
-Observe how the C-Love relation for hybrid star remains EoS-insensitive, but the degree of universality is not as high as in the case of hadronic NSs.
+The C-Love relation for hybrid star remains EoS-insensitive, but the degree of universality is not as high as in the case of hadronic NSs.
 Table~\ref{tab:hybridCompareClove} compares the maximal EoS variability for the constrained and hybrid star EoSs fitting to the three data sets described above.
-As in Sec.~\ref{sec:ilq-hyb}, observe how the maximal EoS variation for hybrid stars fluctuates only slightly ($\sim 4.5\% - 7\%$) in each case.ÊFrom this, we conclude that hybrid stars do obey the C-Love relation derived for nuclear matter stars, with the caveat that the maximum universality increases to $\sim 7.1\%$.
+As in Sec.~\ref{sec:ilq-hyb}, the maximal EoS variation for hybrid stars fluctuates only slightly ($\sim 4.5\% - 7\%$) in each case.
+From this, we conclude that hybrid stars do obey the C-Love relation derived for nuclear matter stars, with the caveat that the maximum universality increases to $\sim 7.1\%$.
 
@@
 Similar to Tab.~\ref{tab:hybridCompare} but for the C-Love relation.
-Observe how for all 3 cases, the hybrid EoSs are only universal up to a minimum of $\sim1$\% (fractional difference from the fit), while in each case the constrained EoSs outperform the hybrid ones.
+For all 3 cases, the hybrid EoSs are only universal up to a minimum of $\sim1$\% (fractional difference from the fit), while in each case the constrained EoSs outperform the hybrid ones.
 The second case is also shown in Fig.~\ref{fig:clove}.
@@
 Figure~\ref{fig:binLove} shows the improved binary Love relation for 3 different mass ratios ($q=0.9$, $q=0.75$, and $q=0.5$) for both the constrained and unconstrained sets of EoSs.
-Observe how, once again, the constrained set shows a considerable increase in EoS-insensitivity relative to both the unconstrained set and previous works~\cite{Yagi:binLove}.
+Once again we find that the constrained set shows a considerable increase in EoS-insensitivity relative to both the unconstrained set and previous works~\cite{Yagi:binLove}.
 As before, the fit to the unconstrained set shows similar, yet slightly larger EoS variation than that found in previous work~\cite{Yagi:binLove} due to the random sampling used in our analysis.
-Observe that absolute error between the fit and the data is approximately independent of the mass ratio $q$, with a subtle maximum at $q=0.75$, which mimics the behavior of the controlling factor $F_n(q)$.
+The absolute error between the fit and the data is approximately independent of the mass ratio $q$, with a subtle maximum at $q=0.75$, which mimics the behavior of the controlling factor $F_n(q)$.
 As before, maximum EoS variation is tabulated in Tab.~\ref{tab:maxVar} for each value of mass ratio considered here.
 
-We can extract two additional conclusions from from Fig.~\ref{fig:binLove}.
+We can extract two additional conclusions from Fig.~\ref{fig:binLove}.
 First, as the mass ratio becomes more extreme (i.e.~away from unity), the ranges of values that $\Lambda_s$ and $\Lambda_a$ can take decrease.

### 2019-02-24 paper/bin-love-after-gw170817.tex
katerina comments sec 4

@@
 Current interferometer sensitivities are not yet high enough to accurately constrain the dominant tidal parameter $\tilde{\Lambda}$.
-For example, GW170817 was detected by LIGO observing run 2 (``O2")~\cite{aLIGO} and was able to constrain $\tilde{\Lambda}$ to a $90\%$ confidence interval centered at $\mu_{\tilde{\Lambda}}=395$ and with a width of 325 (or $\sigma_{\tilde{\Lambda}} \approx 198$).
+For example, GW170817 was detected by LIGO observing run 2 (``O2")~\cite{aLIGO} and VIRGO~\cite{TheVirgo:2014hva} and was able to constrain $\tilde{\Lambda}$ to a $90\%$ credible interval centered at $\mu_{\tilde{\Lambda}}=395$ and with a width of 325 (or $\sigma_{\tilde{\Lambda}} \approx 198$).
 This corresponds to statistical uncertainties of ${\cal{O}}(80\%)$, which dominates the error budget compared to the small systematic uncertainties picked up by EoS variation in the EoS-insensitive relations.
@@
 \end{equation}
-Figure~\ref{fig:residuals} shows a histogram of ${\cal{R}}$ for both the constrained and unconstrained set of EoSs, which approximately obeys a Gaussian distribution.
+Figure~\ref{fig:residuals} shows a histogram of ${\cal{R}}$ for both the constrained and unconstrained set of EoSs, \sout{which approximately obeys a Gaussian distribution}\kc{it does not}.
 The standard deviations of the two histograms, $\sigma=9.764$ and $\sigma=78.28$, show a large decrease in EoS-variability from the unconstrained to the constrained sets of EoSs.
@@
 Figure~\ref{fig:qLsResiduals} shows the standard deviations of the $\lambda_0$ residuals binned in $q$ (top panel) and $\Lambda_{s}$ (bottom panel), as was done previously for the $\Lambda_a$ residuals.
-Observe how the EoS-variability in $\lambda_0$ is dominated by the region around $q \sim 0.5$ and $\Lambda_{s} \sim 2,000$.
+The EoS-variability in $\lambda_0$ is dominated by the region around $q \sim 0.5$ and $\Lambda_{s} \sim 2,000$.
 Henceforth, we approximate the EoS-variability in the binary Love relations with the 90\% credible interval, which for the $\lambda_{0}$ parameter is $P_{90}=13.19$ (indicated by the dashed green line in Fig.~\ref{fig:qLsResiduals} and the dashed indigo line in Fig.~\ref{fig:stackedFisher}).
@@
 Residuals on $\lambda_0$ computed as $\mathcal{R}=\lambda_0^{\text{relation}}-\lambda_0^{\text{true}}$ for the binary Love relations modeled in Sec.~\ref{sec:binary} for both constrained and unconstrained sets of EoSs.
-These residuals obey Gaussian distributions centered at $\mu=-0.1530$ and $\mu=0.2710$ with standard deviations of $\sigma=9.764$ and $\sigma=78.28$ for the constrained and unconstrained sets of EoSs, respectively.
+\sout{These residuals obey} \kc{We fit these residuals with} Gaussian distributions centered at $\mu=-0.1530$ and $\mu=0.2710$ with standard deviations of $\sigma=9.764$ and $\sigma=78.28$ for the constrained and unconstrained sets of EoSs, respectively.
 These uncertainties correspond roughly to the systematic uncertainties introduced on the parameter extraction of $\lambda_0$ upon the use of binary Love relations.
 However, to take into account the systematic uncertainties found in high-error regions of the parameter space, we instead set the systematic uncertainty to be the 90th percentile, $P_{90}=13.19$.
-Observe that the systematic uncertainties from using the improved (constrained) binary Love relations are negligible compared to the statistical uncertainties accrued on parameter extraction from GW170817, found to be $\sigma_{\lambda_0}=170.1$.
+The systematic uncertainties from using the improved (constrained) binary Love relations are negligible compared to the statistical uncertainties accrued on parameter extraction from GW170817, found to be $\sigma_{\lambda_0}=170.1$.
 }
@@
 (\ref{eq:margFit3})-(\ref{eq:margFit4}).
-Observe how the uncertainty is maximal for $q\sim0.5$ and $\Lambda_s\sim2000$, while it becomes minimal for both low and high values of $q$ and $\Lambda_s$.
+The uncertainty is maximal for $q\sim0.5$ and $\Lambda_s\sim2000$, while it becomes minimal for both low and high values of $q$ and $\Lambda_s$.
 Also shown in the figure is the 90th percentile of the un-binned residuals seen in Fig.~\ref{fig:residuals}, taken to be the overall systematic uncertainty introduced by using binary Love relations.
@@
 We also assume low spin priors $|\chi| \leq 0.05$, as well as $\tilde{\Lambda} \leq 3000$ and $|\delta \tilde{\Lambda}| \leq 500$~\cite{Wade:LambdaPriors}.
-The resulting $90\%$ credible region of the posterior distribution on $\tilde{\Lambda}$ has a range of $\pm 276.99$, which is in close agreement to that found by LIGO with a Bayesian analysis~\cite{TheLIGOScientific:2017qsa,Abbott2018}
+The resulting $90\%$ credible region of the posterior distribution on $\tilde{\Lambda}$ has a range of $\pm 276.99$, which is in close agreement to that found by LIGO~\cite{TheLIGOScientific:2017qsa,Abbott2018}
 
@@
 \caption{(Color online)
-Square root of of the spectral noise densities $\sqrt{S_n^A(f)}$ plotted for LIGO O2, aLIGO at design sensitivity, A\texttt{+}, Voyager, CE, and ET-D as interpolated from publicly available data.
+Amplitude spectral noise densities $\sqrt{S_n^A(f)}$ plotted for LIGO O2, aLIGO at design sensitivity, A\texttt{+}, Voyager, CE, and ET-D as interpolated from publicly available data.
 Spectral noise densities are plotted from $f_{\text{min}}=(23,10,10,7,1,1) \text{ Hz}$, respectively, to $f_{\text{max}}=1649 \text{ Hz}$.
@@
 
-Next, we consider events identical to GW170817 detected on upgraded detectors and future detectors, as well as the combined statistical uncertainties of $N_A$ events detected over a 1 year observation with each detector.
+Next, we consider events similar to GW170817 detected on upgraded detectors and future detectors, as well as the combined statistical uncertainties of $N_A$ events detected over a 1 year observation with each detector.
 The later is calculated by integrating the local binary NS merger rate over redshifts up to the horizon redshift of each detector.

### 2019-02-24 paper/bin-love-after-gw170817.tex
katerina comments conclusions

@@
 In this appendix, we detail the process used to compute the statistical uncertainties on the extraction of $\lambda_0$ from the gravitational waveform.
-This is accomplished with a simple Fisher analysis described in Sec.~\ref{sec:futureObservations}, where we first consider single-events identical to GW170817 as if they were detected on future detectors $A \equiv ($ O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, ET~\cite{ET}, CE~\cite{Ap_Voyager_CE}$)$.
+This is accomplished with a simple Fisher analysis described in Sec.~\ref{sec:futureObservations}, where we first consider single-events similar to GW170817 as if they were detected on future detectors $A \equiv ($ O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, ET~\cite{ET}, CE~\cite{Ap_Voyager_CE}$)$.
 We conclude by simulating a population of $N_A$ events for each interferometer, approximating the number of events detected on interferometer $A$ over an observing period of one year.
@@
 \section{Measurement accuracy as a function of binary mass ratio}\label{app:measurement}
-
+\kc{I am not sure how this appendix fits with the rest of the paper. I don't even see it referenced in the text. Remove?}
 In this appendix, we discuss the effects of the binary NS mass ratio $q$ on the measurement accuracy of $\tilde\Lambda$ for various interferometers. 

### 2019-02-24 paper/bin-love-after-gw170817.tex
katerina comments conclusions

@@
 These statistical uncertainties should be compared to the systematic uncertainty on the extraction of $\lambda_{0}$ due to EoS-variability (horizontal dashed line).
-Observe that the statistical and systematic uncertainties cross for Voyager-class detectors.
+The statistical and systematic uncertainties cross for Voyager-class detectors.
 We confirm this conclusion by repeating the statistical analysis with two different waveform models (PhenomD~\cite{PhenomDI,PhenomDII} plus NRTidal corrections~\cite{Samajdar:NRTidal} and PhenomD~\cite{PhenomDI,PhenomDII} plus 6PN tidal corrections~\cite{Wade:tidalCorrections}).}
@@
 The left panel of Fig.~\ref{fig:clove} shows the C-Love relations for both the constrained and unconstrained sets, along with the corresponding \emph{absolute differences} from the fits (instead of the fractional differences as done back in Fig.~\ref{fig:ILQ}).
-Observe how the fit to the constrained EoSs suppresses the EoS variability compared to the fit to the unconstrained set, as well as that of previous works~\cite{Yagi:binLove}.
+The fit to the constrained EoSs suppresses the EoS variability compared to the fit to the unconstrained set, as well as that of previous works~\cite{Yagi:binLove}.
 The maximal EoS variation is compared between these three cases in Table~\ref{tab:maxVar}.
@@
 In the latter, you can see the statistical accuracy to which $\tilde{\Lambda}$ can be estimated as a function of $\rho^A_{\text{GW170817}}$ for single GW170817-like events, i.e.~the signal-to-noise ratio that future detector $A$ would have measured for a GW170817 event.
-Observe that the systematic uncertainty in $\tilde{\Lambda}$ (the horizontal dashed line) becomes comparable to the statistical uncertainty for Voyager-class detectors or better.
+The systematic uncertainty in $\tilde{\Lambda}$ (the horizontal dashed line) becomes comparable to the statistical uncertainty for Voyager-class detectors or better.
 Figure~\ref{fig:singleFisherLt} presents similar results but for the parameter $\lambda_{0}$, for which one can combine posteriors and obtained a reduced combined statistical error.
@@
 For comparison, we also plot the systematic uncertainty on $\tilde\Lambda$ due to the use of the binary Love relations.
-Observe that the statistical and the systematic errors become comparable for Voyager-class detectors or better.
+The statistical and the systematic errors become comparable for Voyager-class detectors or better.
 }
@@
 Indeed, Fig.~\ref{fig:stackedFisher} shows the individual and combined statistical error on $\lambda_{0}$ when using this template model (maroon circles and dashed region).
-Observe that the accuracy to which $\lambda_{0}$ can be measured with this template model is systematically better than when using the IMRD+6PN model (by roughly a factor of two).
+The accuracy to which $\lambda_{0}$ can be measured with this template model is systematically better than when using the IMRD+6PN model (by roughly a factor of two).
 This implies that more accurate template models will indeed be required in the third-generation detector era, as previously pointed out in~\cite{Samajdar:NRTidal}.

### 2019-02-24 paper/bin-love-after-gw170817.tex
add sentences about GWOSC and LI

@@
 
-The unconstrained set is then defined by drawing random samples in the spectral coefficients (within their allowed prior ranges), and then eliminating any EoS that either leads to a polytropic index $\Gamma$ outside the allowed range, breaks the causality restriction, or breaks the maximum mass restriction.
-The constrained set is defined in a similar way, with the addition of the restriction that the resulting EoS be inside the 90\% marginalized posterior distribution on the pressure-mass density plane derived from the GW170817 observation~\cite{LIGO:posterior,Carney:2018sdv}  (see Fig.~2 in~\cite{LIGO:posterior}).
+The unconstrained set is then defined by drawing random samples in the spectral coefficients within their allowed prior ranges, and then eliminating any EoS that either leads to a polytropic index $\Gamma$ outside the allowed range, breaks the causality restriction, or breaks the maximum mass restriction.
+To obtain the constrained set of EoSs we analyze the publicly available data for GW170817 from the Gravitational Wave Open Science Center~\cite{GWOSC,Vallisneri:2014vxa}.
+We use the publicly available software library {\tt LALInference}~\cite{Veitch:2014wba,lalinference_o2} to obtain samples from the EoS posterior.
+Our anaysis uses the same settings and prior choice as those of~\cite{LIGO:posterior,Carney:2018sdv}.
+In both cases, each set consists of 100 members, with a subset of these shown in the left panel of Fig.~\ref{fig:eos}.
+
+%The constrained set is defined in a similar way, with the addition of the restriction that the resulting EoS be inside the 90\% marginalized posterior distribution on the pressure-mass density plane derived from the GW170817 observation~\cite{LIGO:posterior,Carney:2018sdv}  (see Fig.~2 in~\cite{LIGO:posterior}).
 In both cases, each set consists of 100 members, with a subset of these shown in the left panel of Fig.~\ref{fig:eos}.\kc{wait, aren't you using the samples that Calr sent you directly?
@@
 N.Y. acknowledges support from  NSF grant PHY-1759615 and NASA grants NNX16AB98G and 80NSSC17M0041.
+%
+This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center (https://www.gw-openscience.org), a service of LIGO Laboratory, the LIGO Scientific Collaboration and the Virgo Collaboration.
+LIGO is funded by the U.S.
+National Science Foundation.
+Virgo is funded by the French Centre National de Recherche Scientifique (CNRS), the Italian Istituto Nazionale della Fisica Nucleare (INFN) and the Dutch Nikhef, with contributions by Polish and Hungarian institutes.
+%
+The authors are grateful for computational resources provided by the LIGO Laboratory and supported by National Science Foundation Grants PHY-0757058 and PHY-0823459.
 

### 2019-02-24 paper/bin-love-after-gw170817.tex
repliying to Katerinas comments

--- 2019-02-24 paper/bin-love-after-gw170817.tex
@@
 The GWs emitted by binary NSs in the late inspiral must then depend on the \emph{tidal deformabilities} $\Lambda_1$ and $\Lambda_2$, which control the linear response of the star's quadrupole deformation to the (electric-type, quadrupole) tidal field of the companion (to leading order in a post-Newtonian expansion~\cite{Blanchet:2013haa})~\cite{Flanagan2008,Vines:2011ud}.
-\sout{These parameters, however, enter the GW Fourier model multiplied by the same function of the GW frequency} \kc{that's not correct, the "function" depends on the mass ratio} These parameters, however, enter the GW Fourier model at the same post-Newtonian order, making them degenerate, and thus, very difficult to estimate independently with current GW data~\cite{Wade:tidalCorrections}.
+These parameters, however, enter the GW Fourier model at the same post-Newtonian order, making them degenerate, and thus, very difficult to estimate independently with current GW data~\cite{Wade:tidalCorrections}.
 Instead, one can extract certain combinations of the tidal deformabilities, such as a certain mass-weighted tidal deformability $\tilde{\Lambda}$~\cite{Favata:2013rwa,Wade:tidalCorrections}, or one can extract the (mass-independent) coefficients $(\lambda_{0},\lambda_{1},\ldots)$ of a Taylor expansion of the tidal deformabilities about some fiducial mass~\cite{delPozzo:TaylorTidal,Yagi:binLove}.
@@
 Lacking enough sensitivity in current GW observations, one is forced to only estimate the mass-weighted tidal deformability, but this prevents the independent extraction of $\Lambda_{1}$ and $\Lambda_{2}$.
-Yagi and Yunes~\cite{Yagi:binLove} \sout{solved} \kc{proposed a solution to this problem} this problem by finding ``approximately universal'' or ``EoS-insensitive'' relations between the symmetric and anti-symmetric combinations of the tidal deformabilities $\Lambda_{s,a}=\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$, the so-called ``binary Love relations." These relations can be used to analytically express $\Lambda_{s}$ in terms of $\Lambda_{a}$ (or vice-versa), making the mass-weighted tidal deformability a function of only $\Lambda_{a}$.
+Yagi and Yunes~\cite{Yagi:binLove} proposed a solution to this problem by finding ``approximately universal'' or ``EoS-insensitive'' relations between the symmetric and anti-symmetric combinations of the tidal deformabilities $\Lambda_{s,a}=\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$, the so-called ``binary Love relations." These relations can be used to analytically express $\Lambda_{s}$ in terms of $\Lambda_{a}$ (or vice-versa), making the mass-weighted tidal deformability a function of only $\Lambda_{a}$.
 A measurement of the mass-weighted tidal deformability then implies a measurement of $\Lambda_{a}$, and through the use of the binary Love relations, also a measurement of $\Lambda_{s}$, which then allows for the inference of the individual tidal deformabilities $\Lambda_{1}$ and $\Lambda_{2}$~\cite{Yagi:binLove}.
@@
 Certain modified theories of gravity, such as scalar tensor theories with spontaneous scalarization~\cite{Damour:1996ke}, Einstein-Aether and Horava gravity~\cite{Eling:2007xh,Yagi:2013ava,Yagi:2013qpa}, dynamical Chern-Simons gravity~\cite{Yunes:2009ch}, beyond Horndesky theories~\cite{Sakstein:2016oel}, modify such NS observables, but unfortunately, these modifications are typically degenerate with the nuclear EoS.
-Yagi and Yunes \sout{solved} \kc{proposed to solve} this problem by finding EoS-insensitive relations between the moment of inertia, the tidal deformability (or Love number) and the quadrupole moment, the so-called ``I-Love-Q'' relations~\cite{Yagi:ILQ}.
+Yagi and Yunes proposed to solve this problem by finding EoS-insensitive relations between the moment of inertia, the tidal deformability (or Love number) and the quadrupole moment, the so-called ``I-Love-Q'' relations~\cite{Yagi:ILQ}.
 Given a measurement of the Love number for a given NS, for example through GW observations, the I-Love-Q relations can be used to infer the moment of inertia or the quadrupole moment.
@@
 But as the detector sensitivity is improved, the signal-to-noise ratio and the number of events that will be detected will increase, therefore decreasing the statistical uncertainties below the systematic one due to EoS variability.
-We carry out a \sout{simple} Fisher analyses to estimate when the statistical uncertainties become comparable to the systematic uncertainties due to EoS variability and find that this occurs for Voyager-class detectors.
+We carry out a Fisher analyses to estimate when the statistical uncertainties become comparable to the systematic uncertainties due to EoS variability and find that this occurs for Voyager-class detectors.
 
 Figure~\ref{fig:stackedFisher} shows this result in more detail.
-We present the (Fisher-estimated) statistical uncertainty in the measurement of $\lambda_{0}$ with various detectors (LIGO O2~\cite{aLIGO}, Advanced LIGO at design sensitivity (aLIGO)~\cite{aLIGO}, LIGO A\texttt{+} (A\texttt{+})\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, the Einstein Telescope (ET)~\cite{ET}, and the Cosmic Explorer (CE)~\cite{Ap_Voyager_CE}) for an event \sout{identical to} similar to GW170817.
+We present the (Fisher-estimated) statistical uncertainty in the measurement of $\lambda_{0}$ with various detectors (LIGO O2~\cite{aLIGO}, Advanced LIGO at design sensitivity (aLIGO)~\cite{aLIGO}, LIGO A\texttt{+} (A\texttt{+})\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, the Einstein Telescope (ET)~\cite{ET}, and the Cosmic Explorer (CE)~\cite{Ap_Voyager_CE}) for an event similar to GW170817.
 The x-axis shows the signal-to-noise ratio for a GW170817 event detected with each of these detectors.
-We also present the combined statistical uncertainty $\sigma^A_N$ after $N$ detections with each of these instruments, with the top and bottom of the region representing the most optimistic and pessimistic expectation for the number of detections expected from the binary NS merger rate \kc{add citation for the merger rate} (see also Table~\ref{tab:variances}).
+We also present the combined statistical uncertainty $\sigma^A_N$ after $N$ detections with each of these instruments, with the top and bottom of the region representing the most optimistic and pessimistic expectation for the number of detections expected from the binary NS merger rate~\cite{Abbott2017} (see also Tab.~\ref{tab:variances}).
 These statistical uncertainties should be compared to the systematic uncertainty in $\lambda_{0}$ due to EoS-variability improved with the constrained set.
@@
 The constrained set is defined in a similar way, with the addition of the restriction that the resulting EoS be inside the 90\% marginalized posterior distribution on the pressure-mass density plane derived from the GW170817 observation~\cite{LIGO:posterior,Carney:2018sdv}  (see Fig.~2 in~\cite{LIGO:posterior}).
-In both cases, each set consists of 100 members, with a subset of these shown in the left panel of Fig.~\ref{fig:eos}.\kc{wait, aren't you using the samples that Calr sent you directly?
-If yes we need to describe how they were computed and add the appropriate citations to code and data.
-But that's not what you are describing here}
+In both cases, each set consists of 100 members, with a subset of these shown in the left panel of Fig.~\ref{fig:eos}.
 
@@
 
-From the C-Love relations, we can also compute directly the R-Love relation using $R(\Lambda)=M/C(\Lambda)$ and for a fixed\kc{fixed in what sense?} NS mass $M$.
-The right panel of Fig.~\ref{fig:clove} shows the R-Love relation for the constrained and unconstrained sets fixing $M=1.48\text{ M}_{\odot}$\kc{??????} at the observed value for one of the NSs in the GW170817 event, with the bottom panel showing the absolute difference of the data and the fits.
+From the C-Love relations, we can also compute directly the R-Love relation using $R(\Lambda)=M/C(\Lambda)$ for NSs of mass $M$.
+The right panel of Fig.~\ref{fig:clove} shows the R-Love relation for the constrained and unconstrained sets, with the bottom panel showing the absolute difference of the data and the fits.
 The C-Love relations allow us to infer the NS radius to better than $\sim 350 \textrm{m} $ in the constrained case, while the error goes up to $1,000 \textrm{m}$ in the unconstrained case, as also tabulated in Table~\ref{tab:maxVar}.
@@
 \end{equation}
-Figure~\ref{fig:residuals} shows a histogram of ${\cal{R}}$ for both the constrained and unconstrained set of EoSs, \sout{which approximately obeys a Gaussian distribution}\kc{it does not}.
+Figure~\ref{fig:residuals} shows a histogram of ${\cal{R}}$ for both the constrained and unconstrained set of EoSs.
 The standard deviations of the two histograms, $\sigma=9.764$ and $\sigma=78.28$, show a large decrease in EoS-variability from the unconstrained to the constrained sets of EoSs.
@@
 Residuals on $\lambda_0$ computed as $\mathcal{R}=\lambda_0^{\text{relation}}-\lambda_0^{\text{true}}$ for the binary Love relations modeled in Sec.~\ref{sec:binary} for both constrained and unconstrained sets of EoSs.
-\sout{These residuals obey} \kc{We fit these residuals with} Gaussian distributions centered at $\mu=-0.1530$ and $\mu=0.2710$ with standard deviations of $\sigma=9.764$ and $\sigma=78.28$ for the constrained and unconstrained sets of EoSs, respectively.
+We fit these residuals with Gaussian distributions centered at $\mu=-0.1530$ and $\mu=0.2710$ with standard deviations of $\sigma=9.764$ and $\sigma=78.28$ for the constrained and unconstrained sets of EoSs, respectively.
 These uncertainties correspond roughly to the systematic uncertainties introduced on the parameter extraction of $\lambda_0$ upon the use of binary Love relations.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\iffalse
 \section{Measurement accuracy as a function of binary mass ratio}\label{app:measurement}
-\kc{I am not sure how this appendix fits with the rest of the paper. I don't even see it referenced in the text. Remove?}
 In this appendix, we discuss the effects of the binary NS mass ratio $q$ on the measurement accuracy of $\tilde\Lambda$ for various interferometers. 
@@
 We see that this results in identical behaviors between all 6 representative interferometers, leading us to conclude that the discrepancy between the interferometers originates from the degeneracies between different parameters in the gravitational waveform, namely the 6pN tidal parameter $\delta\tilde\Lambda$ which is only detectable by the highly sensitive third generation detectors CE and ET.
-
+\fi
 %%%%%%%%%%%%%%%%%%%%%%

### 2019-02-24 paper/bin-love-after-gw170817.tex

@@
 
-The unconstrained set is then defined by drawing random samples in the spectral coefficients (within their allowed prior ranges), and then eliminating any EoS that either leads to a polytropic index $\Gamma$ outside the allowed range, breaks the causality restriction, or breaks the maximum mass restriction.
-The constrained set is defined in a similar way, with the addition of the restriction that the resulting EoS be inside the 90\% marginalized posterior distribution on the pressure-mass density plane derived from the GW170817 observation~\cite{LIGO:posterior,Carney:2018sdv}  (see Fig.~2 in~\cite{LIGO:posterior}).
+The unconstrained set is then defined by drawing random samples in the spectral coefficients within their allowed prior ranges, and then eliminating any EoS that either leads to a polytropic index $\Gamma$ outside the allowed range, breaks the causality restriction, or breaks the maximum mass restriction.
+To obtain the constrained set of EoSs we analyze the publicly available data for GW170817 from the Gravitational Wave Open Science Center~\cite{GWOSC,Vallisneri:2014vxa}.
+We use the publicly available software library {\tt LALInference}~\cite{Veitch:2014wba,lalinference_o2} to obtain samples from the EoS posterior.
+Our anaysis uses the same settings and prior choice as those of~\cite{LIGO:posterior,Carney:2018sdv}.
 In both cases, each set consists of 100 members, with a subset of these shown in the left panel of Fig.~\ref{fig:eos}.

### 2019-02-26 paper/bin-love-after-gw170817.tex
Fixed Carl's affiliation

@@
 \affiliation{%
- Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY 10010
+ Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY 10010, USA
 }%
@@
 \affiliation{%
- Canadian Institute for Theoretical Astrophysics, 60 St. George Street, Toronto, Ontario, M5S 3H8, Canada
+ LIGO Laboratory and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, Massachusetts 02139, USA
 }%
-\affiliation{%
- Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY 10010
-}%
-
 \author{Nicol\'as Yunes}

### 2019-02-26 paper/bin-love-after-gw170817.tex
going over the first half of the draft

--- 2019-02-24 paper/bin-love-after-gw170817.tex
@@
 
+\author{Kent Yagi}
+\affiliation{%
+ Department of Physics, University of Virginia, Charlottesville, Virginia 22904, USA
+}%
+
 \author{Nicol\'as Yunes}
@@
 
-\author{Kent Yagi}
-\affiliation{%
- Department of Physics, University of Virginia, Charlottesville, Virginia 22904, USA
-}%
-
 \date{\today}
@@
 % Intro
+\ky{I think some of the affiliations are messed up. For example, the MIT Kavli one (Is this Carl's?) is incomplete.}
 The thermodynamic relation between pressure and density (i.e.~the equation of state) of cold supranuclear matter is critical to neutron stars, yet it remains one of the largest uncertainties in nuclear physics.
@@
 The thermodynamic relation between pressure and density in cold, supranuclear matter, the so-called equation of state (EoS), remains an unsolved problem in nuclear physics.
-The EoS is critical to our understanding of neutron stars (NSs) because it determines many NS observables, such as their mass, radius, moment of inertia (I), quadrupole moment (Q) and tidal deformability (or Love number).
+The EoS is critical to our understanding of neutron stars (NSs) because it determines many NS observables, such as their mass, radius, moment of inertia ($I$), quadrupole moment ($Q$) and tidal deformability (or Love number).
 Unfortunately, terrestrial experiments can only probe the EoS to around nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy}.
@@
 For example, electromagnetic observations of the mass and radius of certain NSs have been used to place confidence limits in the mass-radius plane, and thus constrain the EoS~\cite{guver,ozel-baym-guver,steiner-lattimer-brown,Lattimer2014,Ozel:2016oaf}.
-These observations, however, may potentially suffer from large systematic errors due to uncertainties in the astrophysical modeling of X-ray bursts.
+These observations, however, may potentially suffer from large systematic errors~\cite{Miller2013} due to uncertainties in the astrophysical modeling of X-ray bursts.
 The gravitational waves (GWs) emitted in the coalesce of NS binaries may be a cleaner probe of nuclear physics.
@@
 These parameters, however, enter the GW Fourier model at the same post-Newtonian order, making them degenerate, and thus, very difficult to estimate independently with current GW data~\cite{Wade:tidalCorrections}.
-Instead, one can extract certain combinations of the tidal deformabilities, such as a certain mass-weighted tidal deformability $\tilde{\Lambda}$~\cite{Favata:2013rwa,Wade:tidalCorrections}, or one can extract the (mass-independent) coefficients $(\lambda_{0},\lambda_{1},\ldots)$ of a Taylor expansion of the tidal deformabilities about some fiducial mass~\cite{delPozzo:TaylorTidal,Yagi:binLove}.
+Instead, one can extract certain combinations of the tidal deformabilities, such as a certain mass-weighted tidal deformability $\tilde{\Lambda}$~\cite{Favata:2013rwa,Wade:tidalCorrections}, or one can extract the (mass-independent) coefficients $(\lambda_{0},\lambda_{1},\ldots)$ of a Taylor expansion of the tidal deformabilities about some fiducial mass~\cite{Messenger:2011gi,delPozzo:TaylorTidal,Yagi:binLove}.
 Current detectors are not sensitive enough to accurately measure any of these coefficients, but future detectors will and the information from multiple events could then be combined, since the Taylor expansion coefficient should be common to all events.
@@
 Lacking enough sensitivity in current GW observations, one is forced to only estimate the mass-weighted tidal deformability, but this prevents the independent extraction of $\Lambda_{1}$ and $\Lambda_{2}$.
-Yagi and Yunes~\cite{Yagi:binLove} proposed a solution to this problem by finding ``approximately universal'' or ``EoS-insensitive'' relations between the symmetric and anti-symmetric combinations of the tidal deformabilities $\Lambda_{s,a}=\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$, the so-called ``binary Love relations." These relations can be used to analytically express $\Lambda_{s}$ in terms of $\Lambda_{a}$ (or vice-versa), making the mass-weighted tidal deformability a function of only $\Lambda_{a}$.
-A measurement of the mass-weighted tidal deformability then implies a measurement of $\Lambda_{a}$, and through the use of the binary Love relations, also a measurement of $\Lambda_{s}$, which then allows for the inference of the individual tidal deformabilities $\Lambda_{1}$ and $\Lambda_{2}$~\cite{Yagi:binLove}.
-With those at hand, one can further use EoS-insensitive relations between the tidal deformabilities and the compactness, the so-called ``C-Love relations''~\cite{Yagi:ILQ}, to infer the radii of the NSs, and thus, to place two constraints in the mass-radius plane, one for each star in the binary~\cite{Yagi:binLove}.
-This idea was recently implemented in GW170817, allowing for an EoS-independent constraints on the mass-radius curve using GW data~\cite{Katerina:residuals,LIGO:posterior}.
+Yagi and Yunes~\cite{Yagi:2015pkc,Yagi:binLove} proposed a solution to this problem by finding ``approximately universal'' or ``EoS-insensitive'' relations between the symmetric and anti-symmetric combinations of the tidal deformabilities $\Lambda_{s,a}=\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$, the so-called ``binary Love relations." These relations can be used to analytically express $\Lambda_{s}$ in terms of $\Lambda_{a}$ (or vice-versa), making the mass-weighted tidal deformability a function of only $\Lambda_{a}$.
+A measurement of the mass-weighted tidal deformability then implies a measurement of $\Lambda_{a}$, and through the use of the binary Love relations, also a measurement of $\Lambda_{s}$, which then allows for the inference of the individual tidal deformabilities $\Lambda_{1}$ and $\Lambda_{2}$~\cite{Yagi:2015pkc,Yagi:binLove}.
+With those at hand, one can further use EoS-insensitive relations between the tidal deformabilities and the compactness, the so-called ``C-Love relations''~\cite{Yagi:2013bca,Yagi:ILQ,Maselli:2013mva,Yagi:2016bkt}, to infer the radii of the NSs, and thus, to place two constraints in the mass-radius plane, one for each star in the binary.
+This idea was recently implemented in GW170817~\cite{TheLIGOScientific:2017qsa}, allowing for an EoS-independent constraints on the mass-radius curve using GW data~\cite{Katerina:residuals,LIGO:posterior}.
 
@@
 For years, the theoretical physics community considered the possibility of using measurements of NS properties, such as the mass, the radius and the moment of inertia, to constrain deviations from General Relativity in the strong-field regime.
-Certain modified theories of gravity, such as scalar tensor theories with spontaneous scalarization~\cite{Damour:1996ke}, Einstein-Aether and Horava gravity~\cite{Eling:2007xh,Yagi:2013ava,Yagi:2013qpa}, dynamical Chern-Simons gravity~\cite{Yunes:2009ch}, beyond Horndesky theories~\cite{Sakstein:2016oel}, modify such NS observables, but unfortunately, these modifications are typically degenerate with the nuclear EoS.
-Yagi and Yunes proposed to solve this problem by finding EoS-insensitive relations between the moment of inertia, the tidal deformability (or Love number) and the quadrupole moment, the so-called ``I-Love-Q'' relations~\cite{Yagi:ILQ}.
+Certain modified theories of gravity, such as scalar tensor theories with spontaneous scalarization~\cite{Damour:1996ke}, Einstein-\AE ther and Ho\v rava gravity~\cite{Eling:2007xh,Yagi:2013ava,Yagi:2013qpa}, dynamical Chern-Simons gravity~\cite{Yunes:2009ch,Yagi:2013mbt,Gupta:2017vsl}, beyond Horndesky theories~\cite{Babichev:2016jom,Sakstein:2016oel}, modify such NS observables, but unfortunately, these modifications are typically degenerate with the nuclear EoS.
+Yagi and Yunes proposed to solve this problem by finding EoS-insensitive relations between the moment of inertia, the tidal deformability (or Love number) and the quadrupole moment, the so-called ``I-Love-Q'' relations~\cite{Yagi:2013bca,Yagi:ILQ}.
 Given a measurement of the Love number for a given NS, for example through GW observations, the I-Love-Q relations can be used to infer the moment of inertia or the quadrupole moment.
-A second independent measurement of either of these two quantities, for example through binary pulsar observations~\cite{Lattimer:2004nj} or observations with the Neutron star Interior Composition ExploreR (NICER)~\cite{Ozel:2015ykl}, then allows an EoS-insensitive test of General Relativity in the strong field regime~\cite{Yagi:ILQ,Gupta:2017vsl}.
+A second independent measurement of either of these two quantities, for example through binary pulsar observations~\cite{Lattimer:2004nj} or observations with the Neutron star Interior Composition ExploreR (NICER)~\cite{Ozel:2015ykl}, then allows an EoS-insensitive test of General Relativity in the strong field regime~\cite{Yagi:2013bca,Yagi:ILQ,Gupta:2017vsl,Doneva:2017jop}.
 
@@
 We use the C-Love relations to construct the R-Love relations and find that the maximum EoS variability drops from $\sim 880 {\rm{km}}$ in the unconstrained case to $\sim 360 {\rm{km}}$ in the constrained case (see Sec.~\ref{sec:clove} for more details).
-Second, we study the EoS-universality of hybrid stars, which experience strong first-order phase transitions from hadronic to quark matter in the core~\cite{Paschalidis2018}.
+Second, we study the EoS-universality of hybrid stars, which experience strong first-order phase transitions from hadronic to quark matter in the core~\cite{Paschalidis2018,Most:2018eaw,Burgio:2018yix,Montana:2018bkb}.
 We find that the I-Love-Q and C-Love relations remain EoS-insensitive for these hybrid stars, although the EoS variability increases slightly (see Sec.~\ref{sec:ilq-hyb} and~\ref{sec:clove-hyb} for more details).
@@
 But as the detector sensitivity is improved, the signal-to-noise ratio and the number of events that will be detected will increase, therefore decreasing the statistical uncertainties below the systematic one due to EoS variability.
-We carry out a Fisher analyses to estimate when the statistical uncertainties become comparable to the systematic uncertainties due to EoS variability and find that this occurs for Voyager-class detectors.
+We carry out Fisher analyses to estimate when the statistical uncertainties become comparable to the systematic uncertainties due to EoS variability and find that this occurs for Voyager-class detectors.
 
@@
 The x-axis shows the signal-to-noise ratio for a GW170817 event detected with each of these detectors.
-We also present the combined statistical uncertainty $\sigma^A_N$ after $N$ detections with each of these instruments, with the top and bottom of the region representing the most optimistic and pessimistic expectation for the number of detections expected from the binary NS merger rate~\cite{Abbott2017} (see also Tab.~\ref{tab:variances}).
+We also present the combined statistical uncertainty $\sigma^A_N$ after $N$ detections with each of these instruments, with the top and bottom of the region representing the most optimistic and pessimistic expectation for the number of detections expected from the binary NS merger rate~\cite{Abbott2017} (see also Table~\ref{tab:variances}).
 These statistical uncertainties should be compared to the systematic uncertainty in $\lambda_{0}$ due to EoS-variability improved with the constrained set.
@@
 The statistical uncertainties with ET are lower than with CE in spite of a lower signal-to-noise ratio because the former is more sensitive above 300 Hz, where tidal effects matter the most (see Sec.~\ref{sec:futureObservations} for further discussion).
-We also plot the combined statistical uncertainty given $N$ observations consistent with the NS binary merger rate for a 1 year observation (regions), with the top and bottom edges of the regions corresponding to optimistic and pessimistic merger rates.
+We also plot the combined statistical uncertainty given $N$ observations consistent with the NS binary merger rate for a 1 year observation (regions), with the top and bottom edges of the regions corresponding to optimistic and pessimistic \ky{``pessimistic and optimistic'' fits better with ``top and bottom''?} merger rates.
 These statistical uncertainties should be compared to the systematic uncertainty on the extraction of $\lambda_{0}$ due to EoS-variability (horizontal dashed line).
 The statistical and systematic uncertainties cross for Voyager-class detectors.
-We confirm this conclusion by repeating the statistical analysis with two different waveform models (PhenomD~\cite{PhenomDI,PhenomDII} plus NRTidal corrections~\cite{Samajdar:NRTidal} and PhenomD~\cite{PhenomDI,PhenomDII} plus 6PN tidal corrections~\cite{Wade:tidalCorrections}).}
+We confirm this conclusion by repeating the statistical analysis with two different waveform models (PhenomD~\cite{PhenomDI,PhenomDII} plus NRTidal corrections~\cite{Dietrich:2017aum,Samajdar:NRTidal} and PhenomD~\cite{PhenomDI,PhenomDII} plus 6PN tidal corrections~\cite{Vines:2011ud,Wade:tidalCorrections}).}
 \label{fig:stackedFisher}
@@
 
-\subsection{Spectral representations of NS equations of state}
+\subsection{Spectral representations of NS EoSs}
 \label{sec:eos}
@@
 There is significantly less variability in the constrained set of EoSs due to the requirement that they be consistent with the GW170817 observation.
-Right: EoSs for ACS and ACB hybrid stars, each transitioning from a hadronic branch (corresponding to a pure hadronic-matter NS) into a quark-matter branch (quark-matter inner core surrounded by hadronic matter) at various transition pressures $P_{\text{tr}}$.
+Right: EoSs for ACS and ACB hybrid stars~\cite{Paschalidis2018}, each transitioning from a hadronic branch (corresponding to a pure hadronic-matter NS) into a quark-matter branch (quark-matter inner core surrounded by hadronic matter) at various transition pressures $P_{\text{tr}}$.
 }
@@
 Moreover, we impose the following two restrictions:  (i) causality within 10\%, i.e.
-that the speed of sound of the fluid be less than the speed of light to 10\%, and (ii) a high maximum mass, i.e.~that the resulting EoS supports NSs with masses at least as high as $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations~\cite{Zhao:massiveNS}.
+that the speed of sound of the fluid be less than the speed of light to 10\%, and (ii) a high maximum mass, i.e.~that the resulting EoS supports NSs with masses at least as high as $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations~\cite{1.97NS,2.01NS,Zhao:massiveNS}.
 
@@
 In response to this tidal field, the NS will deform away from sphericity and acquire a (spatial) quadrupole moment tensor $Q_{ij}$.
-The tidal deformability $\lambda$ quantifies this linear response via~\cite{Flanagan2008,hinderer-love,Yagi2013}:
+The tidal deformability $\lambda$ quantifies this linear response via~\cite{Flanagan2008,hinderer-love,Yagi:ILQ}:
 \begin{equation}
@@
 \end{equation}
-One can extract $Q_{ij}$ and $\varepsilon_{ij}$ -- and thus $\lambda$, or its dimensionless form $\Lambda \equiv \lambda/M^5$ -- via a double asymptotic expansion of the gravitational potential in a buffer zone, defined by ${\cal{L}} \gg r \gg R$:
+One can extract $Q_{ij}$ and $\varepsilon_{ij}$ -- and thus $\lambda$, or its dimensionless form $\Lambda \equiv \lambda/M^5$ -- via a double asymptotic expansion of the gravitational potential in a buffer zone, defined by ${\cal{L}} \gg r \gg R$: \ky{Added a minus sign in front of $\frac{1+g_{tt}}{2}$.}
 \begin{align}
-\Phi=\frac{1+g_{tt}}{2}&=-\frac{M}{r} - \frac{3}{2}\frac{Q_{ij}}{r^3} \Bigg(\frac{x^i}{r} \frac{x^j}{r}-\frac{1}{3}\delta_{ij} \Bigg) + \mathcal{O} \Bigg( \frac{{\cal{L}}^4}{r^4} \Bigg)
+\Phi=- \frac{1+g_{tt}}{2}&=-\frac{M}{r} - \frac{3}{2}\frac{Q_{ij}}{r^3} \Bigg(\frac{x^i}{r} \frac{x^j}{r}-\frac{1}{3}\delta_{ij} \Bigg) + \mathcal{O} \Bigg( \frac{{\cal{L}}^4}{r^4} \Bigg)
 \nonumber \\ &+ \frac{1}{2} \varepsilon_{ij} x^i x^j + \mathcal{O} \Bigg( \frac{r^3}{R^3} \Bigg),
@@
 The calculation of the tidal deformability therefore requires the calculation of the metric component $g_{tt}$.
-One typically starts by first constructing a spherically symmetric, non-spinning background solution, whose stellar mass and radius are determined from $p(R)=0$.
-One then perturbatively introduces a tidal deformation and solves the perturbed Einstein equations in the NS interior, and matches this solution to an exterior Schwarzschild solution at the surface, modulo a constant.
-The requirement that the metric be at least $C^{1}$ fixes all constants of integration, yielding the tidal deformability, as discussed in more detail in~\cite{hinderer-love}.
-One can similarly obtain the moment of inertia from the asymptotic behavior of the $g_{t \phi}$ metric component.
+One typically starts by first constructing a spherically symmetric, non-spinning background solution, whose stellar radius and mass are determined from $p(R)=0$ and \kent{$M=(1-g_{rr}(R)^{-1})R/2$}.
+One then perturbatively introduces a tidal deformation and solves the perturbed Einstein equations in the NS interior, and matches this solution to an exterior \sout{Schwarzschild} \ky{The exterior solution is not Schwarzschild.} solution at the surface, modulo \sout{a constant} \kent{two integration constants}.
+The requirement that the metric be at least $C^{1}$ fixes \sout{all} \kent{the ratio between the two} constants of integration, yielding the tidal deformability, as discussed in more detail in~\cite{hinderer-love}.
+
+\ky{I created this new paragraph. Please check.}
+Similar to tidal perturbations, one can consider rotational perturbations.
+At first order in rotation, the stellar moment of inertia can be extracted by looking at the asymptotic behavior of the $g_{t \phi}$ metric component.
+At second order in rotation, the quadrupole moment can be extracted by studying the asymptotic behavior of the $g_{t t}$ metric component.
+%One can similarly obtain the moment of inertia from the asymptotic behavior of the $g_{t \phi}$ metric component.
 
@@
 However, the waveform templates can be strategically reparameterized to instead include independent linear combinations of $\Lambda_1$ and $\Lambda_2$ that mitigate correlations.
-One common reparameterization is through the introduction of the mass-weighted tidal deformability $\tilde{\Lambda}=\tilde{\Lambda}(\Lambda_1,\Lambda_2)$ and the parameter $\delta \tilde{\Lambda}=\delta \tilde{\Lambda}(\Lambda_1,\Lambda_2)$~\cite{Wade:tidalCorrections}.
-Since these parameters enter the GW phase at 5 and 6PN orders respectively\footnote{A term of NPN order is proportional to $v^{2N}$ relative to the leading-order term in the expression.}, they partially break the degeneracies between $\Lambda_{1}$ and $\Lambda_{2}$.
+One common reparameterization is through the introduction of the mass-weighted tidal deformability $\tilde{\Lambda}=\tilde{\Lambda}(\Lambda_1,\Lambda_2)$ and the parameter $\delta \tilde{\Lambda}=\delta \tilde{\Lambda}(\Lambda_1,\Lambda_2)$~\cite{Favata:2013rwa,Wade:tidalCorrections}.
+Since these parameters enter the GW phase at 5 and 6PN orders respectively\footnote{A term of $N$PN order is proportional to $v^{2N}$ relative to the leading-order term in the expression, \kent{where $v$ represents the relative velocity of binary constituents}.}, they partially break the degeneracies between $\Lambda_{1}$ and $\Lambda_{2}$.
 
@@
 Current GW interferometry is not yet sensitive enough to accurately extract both tidal parameters $\tilde{\Lambda}$ and $\delta\tilde{\Lambda}$.
-In a search to remedy this, Yagi and Yunes~\cite{Yagi:binLove} found that symmetric and antisymmetric combinations of the tidal deformabilities:
+In a search to remedy this, Yagi and Yunes~\cite{Yagi:binLove} found that symmetric and antisymmetric combinations of the tidal deformabilities
 \begin{equation}
@@
 display EoS-insensitive properties to a high degree, showing EoS variations of at most 20\% for binaries with masses less than $1.7 \text{ M}_{\odot}$ and using a representative sample of 11 EoSs. 
-These ``binary Love relations" allow one to analytically break degeneracies between the tidal parameters: one can substitute $\Lambda_{a}=\Lambda_{a}(\Lambda_{s})$ in the GW model, thus completing eliminating $\Lambda_{a}$ from the parameter list (or vice-versa).
+These ``binary Love relations" allow one to analytically break degeneracies between the tidal parameters: one can substitute $\Lambda_{a}=\Lambda_{a}(\Lambda_{s})$ in the GW model, thus completly eliminating $\Lambda_{a}$ from the parameter list (or vice-versa).
 This is important for two reasons: (i) the new model allows for the more accurate extraction of $\Lambda_{s}$ (or $\Lambda_{a}$ if $\Lambda_{s}$ is eliminated), and (ii) the relations allow for the inference of $\Lambda_{a}$ given a measurement of $\Lambda_{s}$ (or vice-versa), and from this for the inference of the individual tidal deformabilities $\Lambda_{1}$ and $\Lambda_{2}$.
-A simple Fisher analysis has shown that the binary Love relations improve parameter estimation of $\tilde{\Lambda}$ by up to an order of magnitude~\cite{Yagi:binLove}.
-
-Similar EoS-insensitive relations have been found between individual NS observables: the moment of inertia (I), the tidal deformability (Love), the quadrupole moment (Q), and the compactness (C), known as the ``I-Love-Q" and ``C-Love" relations~\cite{Yagi:ILQ, Yagi:binLove}.
-These relations are EoS-insensitive to better than 1\% and 6\% respectively, and they have been important applications in both GW astrophysics~\cite{Kumar:2019xgp} and experimental relativity~\cite{Gupta:2017vsl}.
+A simple Fisher analysis has shown that the binary Love relations improve parameter estimation of $\tilde{\Lambda}$ by up to an order of magnitude~\cite{Yagi:2015pkc,Yagi:binLove}.
+
+Similar EoS-insensitive relations have been found between individual NS observables: the moment of inertia ($I$), the tidal deformability (Love), the quadrupole moment ($Q$), and the compactness ($C$), known as the ``I-Love-Q" and ``C-Love" relations~\cite{Yagi:2013bca,Yagi:ILQ, Maselli:2013mva}.
+These relations are EoS-insensitive to better than 1\% and 6\% respectively, and they have been important applications in both GW astrophysics~\cite{Kumar:2019xgp} and experimental relativity~\cite{Yagi:2013bca,Yagi:ILQ,Gupta:2017vsl,Doneva:2017jop}.
 For example, these relations and the measurement of the tidal deformabilities allow for the inference of several other stellar properties, such as the moment of inertia, the  compactness, the spin ($\chi$), and the radius of NSs~\cite{Kumar:2019xgp}.
@@
 The bottom panels show the relative fractional difference between the fit and the data for each set of EoSs.
-The new fits to the constrained set shows considerable more EoS-insensitivity than that fit to the unconstrained set.
+The new fits to the constrained set shows considerably more EoS-insensitivity than the fit to the unconstrained set.
 These results are summarized in Table~\ref{tab:maxVar}, which tabulates the maximum EoS variation in each fit.
@@
 Individual I-Love-Q relations $\bar{I}-\Lambda$ (left), $\bar{Q}-\Lambda$ (center), and $\bar{I}-\bar{Q}$ (right), shown for both the constrained EoSs (solid green) and unconstrained EoSs (dotted maroon).
-In these figures, the black dashed lines corresponds to the fits given by Eq.~\ref{eq:ILQfitNew}.
-The fractional difference from the fits, shown in the bottom panels, is greatly suppressed for the constrained case, compared to both the unconstrained case, and results from previous works~\cite{Yagi:ILQ}.
-The maximal EoS variation from the fits for the unconstrained and constrained sets of EoSs are compared in Tab.~\ref{tab:maxVar}.
+In these figures, the black dashed lines correspond to the fits given by Eq.~\eqref{eq:ILQfitNew}.
+The fractional difference from the fits, shown in the bottom panels, is greatly suppressed for the constrained case, compared to both the unconstrained case, and results from previous works~\cite{Yagi:2013bca,Yagi:ILQ}.
+The maximal EoS variation from the fits for the unconstrained and constrained sets of EoSs are compared in Table~\ref{tab:maxVar}.
 Additionally shown in this figure is the fractional difference from the nuclear matter fits for the 10 hybrid star EoSs (dashed green).
@@
  $\Lambda_a-\Lambda_s$ & $\sim0.20$ & $0.25$ & $0.083$\\
-  $q=0.7$ & (--) & ($320$) & ($52$) \\
+  $q=0.75$ & (--) & ($320$) & ($52$) \\
   \cline{1-1}
@@
 \caption{Maximum relative and fractional EoS variation in the I-Love-Q, C-Love, R-Love, and binary Love relations using the unconstrained set, the constrained set and variations reported in previous work~\cite{Yagi:ILQ,Yagi:binLove}.
-The maximum absolute EoS variation is also reported in the C-Love, R-Love and binary Love cases in parenthesis.
+The maximum absolute EoS variation is also reported in the C-Love, R-Love and binary Love cases in parentheses.
 The maximum variation in the constrained set case is better than a factor of two smaller than the variability in the unconstrained case and in previous work.
 The maximum EoS variation in the unconstrained set is slightly larger than that found in previous work because the former is built from a large random sampling of EoSs.
-}\label{tab:maxVar}
+}
+\label{tab:maxVar}
 \end{table}
@@
 \caption{
-Maximum relative and fractional EoS variation in the I-Love relation, fitting to three different sets of data: using the constrained set plus hybrid EoSs, using the constrained set alone, EoS data alone, and using only the hybrid EoSs.
+Maximum relative and fractional EoS variation in the I-Love relation, fitting to three different sets of data: using the constrained set plus hybrid EoSs, using the constrained set alone, and using only the hybrid EoSs.
 In all 3 cases the hybrid EoSs are EoS-insensitive to $\sim1$\%, which is a slight decrease in universality relative to the hadronic only EoSs.
@@
 
-The fractional differences for the second case (fit to only the constrained EoSs) is shown with dashed green lines in Fig.~\ref{fig:ILQ}, while the maximum EoS variation for the I-Love relation is shown in Table~\ref{tab:hybridCompare} for both the constrained and hybrid star cases.
-The hybrid star EoSs obey the I-Love-Q relations in each case to better than $\sim1.7$\%, a variability that is slightly higher than that found when using only nuclear matter EoSs in previous works~\cite{Yagi:ILQ}.
+The fractional differences \ky{of hybrid stars from the fit} for the second case (fit to only the constrained EoSs) is shown with dashed green lines in Fig.~\ref{fig:ILQ}, while the maximum EoS variation for the I-Love relation is shown in Table~\ref{tab:hybridCompare} for both the constrained and hybrid star cases.
+The hybrid star EoSs obey the I-Love-Q relations in each case to better than $\sim1.7$\%, a variability that is slightly higher than that found when using only nuclear matter EoSs in previous works~\cite{Yagi:2013bca,Yagi:ILQ} \kent{and is consistent with~\cite{Paschalidis2018}}.
 The universality cannot be improved much through the introduction of new fits, only bringing the maximal EoS variation down to $\sim1$\% for the fits constructed with only hybrid star EoSs.
@@
 \caption{
-Similar to Fig.~\ref{fig:ILQ} but for the C-Love (left) and the R-Love relations (right), with the bottom panels showing the \emph{absolute differences} (rather than fractional difference as in Fig.~\ref{fig:ILQ}) from the fit.
-The absolute difference is suppressed in the constrained set case relative to the unconstrained set, and results from previous work~\cite{Yagi:binLove}.
+Similar to Fig.~\ref{fig:ILQ} but for the C-Love (left) and the R-Love relations (right).
+\kent{In the top panels, we show two different fits, one for the unconstrained set and one for the constrained set of EoSs.} The bottom panels show the \emph{absolute differences} (rather than fractional difference as in Fig.~\ref{fig:ILQ}) from the fit.
+The absolute difference is suppressed in the constrained set case relative to the unconstrained set, and results from previous work~\cite{Maselli:2013mva}.
 In the left panel, we also present the C-Love relations in the hybrid star cases (dashed green) for comparison, where, although still EoS-insensitive, the degree of universality decreases.
+\ky{Zack, can you please make the ordering of legends as consistent as possible among different plots?
+For example, ``Fits'' is mentioned last in the left panel while it's at the beginning on the right panel.}
 }
@@
 
-In this subsection we focus on the EoS-insensitive C-Love relations, as introduced by Yagi and Yunes in~\cite{Yagi:binLove}, as well as on the R-Love relations, since these play a key role in GW data analysis for the extraction of M-R credible intervals.
+In this subsection we focus on the EoS-insensitive C-Love relations, as introduced in~\cite{Yagi:2013bca,Yagi:ILQ,Maselli:2013mva}, as well as on the R-Love relations, since these play a key role in GW data analysis for the extraction of M-R credible intervals.
 As in the previous subsection, we consider both nuclear matter EoSs, as well as hybrid quark-hadron star EoSs.
@@
 
-Following Ref.~\cite{Yagi:binLove}, we begin by fitting the data for each set of EoSs to the simple curve
+\ky{Somehow we've been citing~\cite{Yagi:binLove} for the C-Love relation, but I think this should really be~\cite{Maselli:2013mva} so I've modified throughout.}
+
+Following Ref.~\cite{Maselli:2013mva}, we begin by fitting the data for each set of EoSs to the simple curve
 \begin{equation}
@@
 \end{equation}
-Doing so, yields $a_0 = 0.3617$, $a_1 = -0.03548$, and $a_2 = 0.0006194$ for the constrained set of EoSs, similar to what was found in~\cite{Yagi:binLove}.
+Doing so, yields $a_0 = 0.3617$, $a_1 = -0.03548$, and $a_2 = 0.0006194$ for the constrained set of EoSs, similar to what was found in~\cite{Maselli:2013mva}.
 As in the I-Love-Q case, however, the above fitting function does not limit properly to the Newtonian result
@@
 \end{equation}
-We thus repeat the fit using Eq.~\ref{eq:ILQfitNew} as the fitting function, with the new fitting coefficients presented in Table~\ref{tab:ILQfitNew}.
-
-The left panel of Fig.~\ref{fig:clove} shows the C-Love relations for both the constrained and unconstrained sets, along with the corresponding \emph{absolute differences} from the fits (instead of the fractional differences as done back in Fig.~\ref{fig:ILQ}).
-The fit to the constrained EoSs suppresses the EoS variability compared to the fit to the unconstrained set, as well as that of previous works~\cite{Yagi:binLove}.
+We thus repeat the fit using Eq.~\eqref{eq:ILQfitNew} as the fitting function, with the new fitting coefficients presented in Table~\ref{tab:ILQfitNew}.
+
+The left panel of Fig.~\ref{fig:clove} shows the C-Love relations for both the constrained and unconstrained sets, along with the corresponding \emph{absolute differences}\footnote{\kent{We present absolute differences instead of fractional differences since the former is what matters directly to the GW data analysis.}} from the fits (instead of the fractional differences as done back in Fig.~\ref{fig:ILQ}).
+The fit to the constrained EoSs suppresses the EoS variability compared to the fit to the unconstrained set, as well as that of previous work~\cite{Maselli:2013mva}.
 The maximal EoS variation is compared between these three cases in Table~\ref{tab:maxVar}.
 
-From the C-Love relations, we can also compute directly the R-Love relation using $R(\Lambda)=M/C(\Lambda)$ for NSs of mass $M$.
-The right panel of Fig.~\ref{fig:clove} shows the R-Love relation for the constrained and unconstrained sets, with the bottom panel showing the absolute difference of the data and the fits.
+From the C-Love relations, we can also compute directly the R-Love relation using $R(\Lambda)=M/C(\Lambda)$ for NSs of mass $M$ \ky{Did you use $M(\Lambda)$ to find $R(\Lambda)$, or did you fix the mass to be something when plotting Fig.~4?}.
+The right panel of Fig.~\ref{fig:clove} shows the R-Love relations for the constrained and unconstrained sets, with the bottom panel showing the absolute difference of the data and the fits.
 The C-Love relations allow us to infer the NS radius to better than $\sim 350 \textrm{m} $ in the constrained case, while the error goes up to $1,000 \textrm{m}$ in the unconstrained case, as also tabulated in Table~\ref{tab:maxVar}.
@@
 
-The left panel of Fig.~\ref{fig:clove} shows the C-Love relation when fitting only to the constrained set (dashed green curves).
-The C-Love relation for hybrid star remains EoS-insensitive, but the degree of universality is not as high as in the case of hadronic NSs.
+\kent{In the top} left panel of Fig.~\ref{fig:clove}, we show the C-Love relations \kent{for hybrid stars (dashed green curves), while in the bottom panel, we show the absolute difference of the relations for such stars from the fit constructed only from} the constrained set (dashed green curves).
+The C-Love relations for hybrid stars remain EoS-insensitive, but the degree of universality is not as high as in the case of hadronic NSs.
 Table~\ref{tab:hybridCompareClove} compares the maximal EoS variability for the constrained and hybrid star EoSs fitting to the three data sets described above.
@@
 From this, we conclude that hybrid stars do obey the C-Love relation derived for nuclear matter stars, with the caveat that the maximum universality increases to $\sim 7.1\%$.
+
+\ky{Why don't we show R-Love for hybrid stars?}
 
@@
 \caption{
-Similar to Tab.~\ref{tab:hybridCompare} but for the C-Love relation.
-For all 3 cases, the hybrid EoSs are only universal up to a minimum of $\sim1$\% (fractional difference from the fit), while in each case the constrained EoSs outperform the hybrid ones.
+Similar to Table~\ref{tab:hybridCompare} but for the C-Love relation.
+For all 3 cases, the hybrid EoSs are only universal up to a minimum of $\sim1$\% (fractional difference from the fit), while in each case the constrained EoSs outperform the hybrid ones \ky{Is this true?
+For case 3, hybrid one has smaller number than the constrained one.}.
 The second case is also shown in Fig.~\ref{fig:clove}.
@@
 \end{center}
-\caption{(Color online) Binary Love relations using Eq.~\ref{eq:binLovefit} fitted to the constrained (dotted maroon) and unconstrained sets (solid green), fixing $q=0.9$, $q=0.75$, and $q=0.50$.
+\caption{(Color online) Binary Love relations using Eq.~\eqref{eq:binLovefit} fitted to the constrained (dotted maroon) and unconstrained sets (solid green), fixing $q=0.90$, 0.75 and 0.50.
 The bottom panels show the absolute difference (not the relative difference as in Fig.~\ref{fig:ILQ}) of the fit and the data.
 The fit to the constrained set shows a reduction in EoS variation relative to both the fit to the unconstrained set and previous work~\cite{Yagi:binLove}.
-For comparison, we also show the binary Love relations for the 10 hybrid star EoSs (dashed bright green curves), which present much larger EoS variation.
+For comparison, we also show the binary Love relations for the 10 hybrid star EoSs (dashed green curves), which present much larger EoS variation.
 }
@@
 
-Let us now consider the binary Love relations.
+Let us now consider the binary Love relations. \kent{As for other relations, we consider nuclear matter stars and hybrid stars separately.}
+
+\subsubsection{Nuclear matter stars}
+
 Following Ref.~\cite{Yagi:binLove}, we begin by fitting the binary Love relations to the constrained and unconstrained sets using the two-dimensional curve:
@@
 where we set $n = 0.743$ and $\alpha = 1$ as was done in Ref.~\cite{Yagi:binLove}.
-Unlike the individual I-Love-Q relations, the binary Love relations depend also depend on the mass ratio.
-
-Figure~\ref{fig:binLove} shows the improved binary Love relation for 3 different mass ratios ($q=0.9$, $q=0.75$, and $q=0.5$) for both the constrained and unconstrained sets of EoSs.
+Unlike the individual I-Love-Q relations, the binary Love relations depend also on the mass ratio.
+
+Figure~\ref{fig:binLove} shows the improved binary Love relation for 3 different mass ratios ($q=0.9$, 0.75 and 0.5) for both the constrained and unconstrained sets of EoSs.
 Once again we find that the constrained set shows a considerable increase in EoS-insensitivity relative to both the unconstrained set and previous works~\cite{Yagi:binLove}.
@@
 The absolute error between the fit and the data is approximately independent of the mass ratio $q$, with a subtle maximum at $q=0.75$, which mimics the behavior of the controlling factor $F_n(q)$.
-As before, maximum EoS variation is tabulated in Tab.~\ref{tab:maxVar} for each value of mass ratio considered here.
+As before, maximum EoS variation is tabulated in Table~\ref{tab:maxVar} for each value of mass ratio considered here.
 
@@
 Second, the fit to the constrained set does not extend to as high values of $\Lambda_s$ as the fit to the unconstrained set does.
-This is because of how the sets of EoSs were generated in our analysis, with the unconstrained set including some EoSs that are stiffer and and others that are softer than those constrained by the GW170817 event.
+This is because of how the sets of EoSs were generated in our analysis, with the unconstrained set including some EoSs that are stiffer and others that are softer than those constrained by the GW170817 event.
 This results in the unconstrained set  containing a larger range of tidal deformabilities $\Lambda_{1,2}$ (from both above and below) than the constrained set, which ultimately leads to a \emph{larger} range of $\Lambda_s=\frac{1}{2}(\Lambda_1+\Lambda_2)$ values.
+
+\subsubsection{Hybrid quark-hadron stars}
 
@@
 Work along these lines is outside the scope of this paper.
+
+\ky{UP TO HERE}
 
@@
 Future work on this subject could entail an investigation into the improvement of alternative EoS-insensitive relations, such as the multipole Love relations between various $\ell$-th order electric, magnetic, and shape tidal deformabilities, as discussed in~\cite{Yagi:Multipole}.
-Additionally, Lackey \emph{et al}~\cite{Lackey:Surrogate, Lackey:EOB} presented surrogate models of non-spinning effective-one-body waveforms with the the use of universal relations.
+Additionally, Lackey \emph{et al}~\cite{Lackey:Surrogate, Lackey:EOB} presented surrogate models of non-spinning effective-one-body waveforms with the use of universal relations.
 By reducing the number of waveform model parameters, surrogate models aid in the extraction of NS observables from GW detections.
@@
 \section*{Acknowledgments}\label{acknowledgments}
-K.Y. acknowledge networking support by the COST Action GWverse CA16104.
+KY acknowledges support from NSF Award PHY-1806776. 
+K.Y. would like to also acknowledge networking support by the COST Action GWverse CA16104.
 N.Y. acknowledges support from  NSF grant PHY-1759615 and NASA grants NNX16AB98G and 80NSSC17M0041.

### 2019-02-26 paper/bin-love-after-gw170817.tex

@@
 \affiliation{%
- Canadian Institute for Theoretical Astrophysics, 60 St. George Street, Toronto, Ontario, M5S 3H8, Canada
+ LIGO Laboratory and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, Massachusetts 02139, USA
 }%
-\affiliation{%
- Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY 10010
-}%
+%\affiliation{%
+% Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY 10010
+%}%
 
@@
 }%
-\affiliation{%
- Department of Physics and MIT Kavli Institute,
-}%
+%\affiliation{%
+% Department of Physics and MIT Kavli Institute,
+%}%
 

### 2019-02-26 paper/bin-love-after-gw170817.tex
removing one comments

@@
 % Intro
-\ky{I think some of the affiliations are messed up. For example, the MIT Kavli one (Is this Carl's?) is incomplete.}
 The thermodynamic relation between pressure and density (i.e.~the equation of state) of cold supranuclear matter is critical to neutron stars, yet it remains one of the largest uncertainties in nuclear physics.

### 2019-02-26 paper/bin-love-after-gw170817.tex
going over the second half

@@
 
-\ky{UP TO HERE}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{equation}
-where $\mathcal{N}(\mu,\sigma)$ is a normal distribution with mean and variance $\mu_{r}$ and $\sigma_{r}^2$.
-Let us further assume that the residuals $r$ obey a Gaussian distribution with mean and standard deviation that can be decomposed as
+where $\mathcal{N}(\mu_r,\sigma_r)$ is a normal distribution with mean and variance $\mu_{r}$ and $\sigma_{r}^2$.
+Let us further assume that the residuals $r$ obey a Gaussian distribution with mean and standard deviation that can be decomposed as \ky{Are you }
 \begin{align}
@@
 Figure~\ref{fig:qLsResiduals} shows the standard deviations of the $\lambda_0$ residuals binned in $q$ (top panel) and $\Lambda_{s}$ (bottom panel), as was done previously for the $\Lambda_a$ residuals.
-The EoS-variability in $\lambda_0$ is dominated by the region around $q \sim 0.5$ and $\Lambda_{s} \sim 2,000$.
-Henceforth, we approximate the EoS-variability in the binary Love relations with the 90\% credible interval, which for the $\lambda_{0}$ parameter is $P_{90}=13.19$ (indicated by the dashed green line in Fig.~\ref{fig:qLsResiduals} and the dashed indigo line in Fig.~\ref{fig:stackedFisher}).
+The EoS-variability in $\lambda_0$ is dominated by the region around $q \sim 0.5$ and $\Lambda_{s} \sim 2000$.
+\ky{I don't see the connection between this sentence and the previous one.
+(How did we arrive at using $P_{90}=13.19$ from the fact that the EoS variability peaks around $q \sim 0.5$ and $\Lambda_{s} \sim 2000$?)} Henceforth, we approximate the EoS-variability in the binary Love relations with the 90\% credible interval, which for the $\lambda_{0}$ parameter is $P_{90}=13.19$ (indicated by the dashed green line in Fig.~\ref{fig:qLsResiduals} and the dashed indigo line in Fig.~\ref{fig:stackedFisher}).
 We can similarly derive a conservative estimate of the systematic uncertainty due to EoS-variability in the binary Love relations in terms of $\tilde\Lambda_{a}$ to find $12.01$, which is what we use later in Fig.~\ref{fig:singleFisherLt}.
@@
 \caption{
+\ky{What are $\Lambda_s$ and $q$ used to produce this plot?}
 Residuals on $\lambda_0$ computed as $\mathcal{R}=\lambda_0^{\text{relation}}-\lambda_0^{\text{true}}$ for the binary Love relations modeled in Sec.~\ref{sec:binary} for both constrained and unconstrained sets of EoSs.
@@
 Also shown in the figure is the 90th percentile of the un-binned residuals seen in Fig.~\ref{fig:residuals}, taken to be the overall systematic uncertainty introduced by using binary Love relations.
+\ky{Can we have 4 small ticks between large ticks instead of 3?}
 }
@@
 where $\eta \equiv m_1 m_2/m^2$ is the symmetric mass ratio with $m_{1,2}$ and $m$ being the individual and total masses, $\mathcal{M}=m \eta^{3/5}$ is the chirp mass, $A \equiv {\mathcal{M}^{5/6}}/({\sqrt{30}\pi^{2/3}D_L})$ is a normalized amplitude factor with $D_L$ the luminosity distance, and $\chi_{s,a}=\frac{1}{2}(\chi_1\pm\chi_2)$ are the symmetric and antisymmetric dimensionless spin parameters.
-Given a sufficiently loud observation and Gaussian noise, the resulting posterior distribution on the estimated parameters is Gaussian with a root-mean-square given by
+Given a sufficiently loud observation and Gaussian noise, the resulting posterior distribution on the estimated parameters is Gaussian with a root-mean-square error given by
 \begin{equation}
@@
 \begin{equation}
-\tilde{\Gamma}_{ab} \equiv \Big( \frac{\partial h}{\partial \theta^b} \Big| \frac{\partial h}{\partial \theta^a}\Big) + \frac{1}{\sigma_{\theta^a}^2} \delta_{ab}
-\end{equation}
-$\sigma_{\theta^a}$ are the parameters' prior root-mean-square estimate, and the inner product is defined by:
+\tilde{\Gamma}_{ab} \equiv \Big( \frac{\partial h}{\partial \theta^b} \Big| \frac{\partial h}{\partial \theta^a}\Big) + \frac{1}{\sigma_{\theta^a}^2} \delta_{ab}\,.
+\end{equation}
+Here $\sigma_{\theta^a}$ are the parameters' prior root-mean-square estimate, and the inner product is defined by:
 \begin{equation}
@@
 Further, we scale the luminosity distance such that the signal-to-noise-ratio ($SNR \equiv \rho$) is fixed to $\rho=32.4$, as found in GW170817.
-We also assume low spin priors $|\chi| \leq 0.05$, as well as $\tilde{\Lambda} \leq 3000$ and $|\delta \tilde{\Lambda}| \leq 500$~\cite{Wade:LambdaPriors}.
+\ky{I think we should also explain what fiducial values we used for all the other parameters, like masses and $\tilde \Lambda$.} We also assume low spin priors $|\chi| \leq 0.05$, as well as $\tilde{\Lambda} \leq 3000$ and $|\delta \tilde{\Lambda}| \leq 500$~\cite{Wade:LambdaPriors}.
 The resulting $90\%$ credible region of the posterior distribution on $\tilde{\Lambda}$ has a range of $\pm 276.99$, which is in close agreement to that found by LIGO~\cite{TheLIGOScientific:2017qsa,Abbott2018}
@@
 Also shown is $2 \sqrt{f}$ multiplied by the amplitude of the PhenomD~\cite{PhenomDI,PhenomDII} waveform template.
+\ky{Please change ``a++'' to ``A+'' in the legend. Same comment applies to Fig.~9.}
 }
@@
 Next, we consider events similar to GW170817 detected on upgraded detectors and future detectors, as well as the combined statistical uncertainties of $N_A$ events detected over a 1 year observation with each detector.
-The later is calculated by integrating the local binary NS merger rate over redshifts up to the horizon redshift of each detector.
+The latter is calculated by integrating the local binary NS merger rate over redshifts up to the horizon redshift of each detector.
 As before, for each Fisher calculation we assume low spin priors $|\chi| \leq 0.05$, as well as $0 \leq \lambda_0 \leq 3207$ and $-4490 \leq \lambda_1 \leq 0$~\cite{delPozzo:TaylorTidal}\footnote{These are converted from the dimensional forms found in~\cite{delPozzo:TaylorTidal} into their corresponding dimensionless forms.}.
@@
 
-Figures~\ref{fig:singleFisherLt} and~\ref{fig:stackedFisher}, and Table~\ref{tab:variances} summarize our results graphically using an IMRD + 6PN template.
-In the latter, you can see the statistical accuracy to which $\tilde{\Lambda}$ can be estimated as a function of $\rho^A_{\text{GW170817}}$ for single GW170817-like events, i.e.~the signal-to-noise ratio that future detector $A$ would have measured for a GW170817 event.
+Figures~\ref{fig:stackedFisher} and~\ref{fig:singleFisherLt}, and Table~\ref{tab:variances} summarize our results graphically using an IMRD + 6PN template.
+In Fig.~\ref{fig:singleFisherLt}, one can see the statistical accuracy to which $\tilde{\Lambda}$ can be estimated as a function of $\rho^A_{\text{GW170817}}$ for single GW170817-like events, i.e.~the signal-to-noise ratio that future detector $A$ would have measured for a GW170817 event.
 The systematic uncertainty in $\tilde{\Lambda}$ (the horizontal dashed line) becomes comparable to the statistical uncertainty for Voyager-class detectors or better.
-Figure~\ref{fig:singleFisherLt} presents similar results but for the parameter $\lambda_{0}$, for which one can combine posteriors and obtained a reduced combined statistical error.
+Figure~\ref{fig:stackedFisher} presents similar results but for the parameter $\lambda_{0}$, for which one can combine posteriors and obtained a reduced combined statistical error.
 This figure also shows that the statistical and systematic uncertainties become comparable for Voyager-class detectors or better.
-The careful reader will notice that Figs.~\ref{fig:stackedFisher} and~\ref{fig:singleFisherLt} show that the single-event statistical uncertainties using CE is higher than using ET despite the later having a larger SNR for a GW170817-like event.
+The careful reader will notice that Figs.~\ref{fig:stackedFisher} and~\ref{fig:singleFisherLt} show that the single-event statistical uncertainties using CE is higher than using ET despite the latter having a larger SNR for a GW170817-like event.
 This is because the 3-detector geometry of ET enables it to have higher sensitivity than ET at frequencies above 300Hz, which is precisely where the tidal deformabilities is encoded, but ET has lower sensitivity at lower frequencies, where a lot of the signal-to-noise ratio accumulates.
@@
 The statistical and the systematic errors become comparable for Voyager-class detectors or better.
+\ky{I sort of feel that we only need to show $\sigma > 1$.
+}
 }
@@
 The statistical uncertainties on $\lambda_0$ becomes comparable with the systematic uncertainty (set to be $P_{90}=13.19$) from using the improved binary Love relations with detectors of Voyager-class or better.
+\ky{Do we really need to show numbers with 7 digits...? I think it's enough to just show the first few digits in a form $a.b \times 10^X$ in each cell.}
 }\label{tab:variances}
@@
 We used this observation to generate a restricted set of spectral EoSs that agree with it, in order to reduce the uncertainties upon the extraction of tidal parameters from future GW events.
-Previous work by Yagi and Yunes~\cite{Yagi:ILQ,Yagi:binLove} had found EoS-insensitive relations between symmetric and antisymmetric combinations of NS tidal deformabilities, which aid in the extraction of said tidal parameters.
+Previous work by Yagi and Yunes~\cite{Yagi:2013bca,Yagi:ILQ,Yagi:2015pkc,Yagi:binLove} had found EoS-insensitive relations between symmetric and antisymmetric combinations of NS tidal deformabilities, which aid in the extraction of said tidal parameters.
 We here found that the GW170817-constrained set of EoSs are more EoS-insensitive by a factor of $\sim 60$\% for stars with mass ratios of $0.75$ relative to previous work.
@@
 Future work on this subject could entail an investigation into the improvement of alternative EoS-insensitive relations, such as the multipole Love relations between various $\ell$-th order electric, magnetic, and shape tidal deformabilities, as discussed in~\cite{Yagi:Multipole}.
-Additionally, Lackey \emph{et al}~\cite{Lackey:Surrogate, Lackey:EOB} presented surrogate models of non-spinning effective-one-body waveforms with the use of universal relations.
+Lackey \emph{et al}~\cite{Lackey:Surrogate, Lackey:EOB} presented surrogate models of non-spinning effective-one-body waveforms with the use of universal relations.
 By reducing the number of waveform model parameters, surrogate models aid in the extraction of NS observables from GW detections.
-The improvement in the multipole love relations can then be used to increase the accuracy of such surrogate models.
+The improvement in the multipole Love relations can then be used to increase the accuracy of such surrogate models.
 Another possible avenue for future research includes a more comprehensive analysis into the intricacies of new hybrid star binary Love relations.
@@
       0 & z\geq 5\\ 
-\end{array} 
+\end{array}\,, 
 \right.
@@
 
-where $H_0 = 70 \text{km s}^{-1}\text{Mpc}^{-1}$ is the local Hubble constant, and $\Omega_{\Lambda}=0.67$ is the universe's vacuum energy density.
+where $H_0 = 70 \text{km s}^{-1}\text{Mpc}^{-1}$ is the local Hubble constant and $\Omega_{\Lambda}=0.67$ is the universe's vacuum energy density.
 Here we choose an observing period of $\Delta \tau_0 = 1$ year, and calculate the detection rate for the upper, central, and lower limits of the local binary NS coalescence rate density $\mathcal{R}=1540^{+3200}_{-1220} \text{ Gpc}^{-3}\text{yr}^{-1}$~\cite{Abbott2017}, giving the rates $N_A$ shown in the second column of Table~\ref{tab:variances}.
@@
 \end{equation}
-where $\rho_i^A$ is the SNR of simulated event $i$ computed from Eq.~\ref{eq:population}, and $\rho_{\text{GW170817}}^A$ and $\sigma_{\text{GW170817}}^A$ are the known SNRs and uncertainties of the GW170817 event from step (i).
+where $\rho_i^A$ is the SNR of simulated event $i$ computed from Eq.~\eqref{eq:population}, and $\rho_{\text{GW170817}}^A$ and $\sigma_{\text{GW170817}}^A$ are the known SNRs and uncertainties of the GW170817 event from step (i).
 This results in the combined statistical uncertainties for the lower, central, and upper limits of the local binary NS coalescence rate density $\mathcal{R}$, depicted by the cyan shaded region in Fig.~\ref{fig:stackedFisher}.

### 2019-02-27 paper/bin-love-after-gw170817.tex
responding to Kents comments

@@
 The statistical uncertainties with ET are lower than with CE in spite of a lower signal-to-noise ratio because the former is more sensitive above 300 Hz, where tidal effects matter the most (see Sec.~\ref{sec:futureObservations} for further discussion).
-We also plot the combined statistical uncertainty given $N$ observations consistent with the NS binary merger rate for a 1 year observation (regions), with the top and bottom edges of the regions corresponding to optimistic and pessimistic \ky{``pessimistic and optimistic'' fits better with ``top and bottom''?} merger rates.
+We also plot the combined statistical uncertainty given $N$ observations consistent with the NS binary merger rate for a 1 year observation (regions), with the top and bottom edges of the regions corresponding to pessimistic and optimistic merger rates.
 These statistical uncertainties should be compared to the systematic uncertainty on the extraction of $\lambda_{0}$ due to EoS-variability (horizontal dashed line).
@@
 \end{equation}
-One can extract $Q_{ij}$ and $\varepsilon_{ij}$ -- and thus $\lambda$, or its dimensionless form $\Lambda \equiv \lambda/M^5$ -- via a double asymptotic expansion of the gravitational potential in a buffer zone, defined by ${\cal{L}} \gg r \gg R$: \ky{Added a minus sign in front of $\frac{1+g_{tt}}{2}$.}
+One can extract $Q_{ij}$ and $\varepsilon_{ij}$ -- and thus $\lambda$, or its dimensionless form $\Lambda \equiv \lambda/M^5$ -- via a double asymptotic expansion of the gravitational potential in a buffer zone, defined by ${\cal{L}} \gg r \gg R$:
 \begin{align}
@@
 The calculation of the tidal deformability therefore requires the calculation of the metric component $g_{tt}$.
-One typically starts by first constructing a spherically symmetric, non-spinning background solution, whose stellar radius and mass are determined from $p(R)=0$ and \kent{$M=(1-g_{rr}(R)^{-1})R/2$}.
-One then perturbatively introduces a tidal deformation and solves the perturbed Einstein equations in the NS interior, and matches this solution to an exterior \sout{Schwarzschild} \ky{The exterior solution is not Schwarzschild.} solution at the surface, modulo \sout{a constant} \kent{two integration constants}.
-The requirement that the metric be at least $C^{1}$ fixes \sout{all} \kent{the ratio between the two} constants of integration, yielding the tidal deformability, as discussed in more detail in~\cite{hinderer-love}.
-
-\ky{I created this new paragraph. Please check.}
+One typically starts by first constructing a spherically symmetric, non-spinning background solution, whose stellar radius and mass are determined from $p(R)=0$ and $M=(1-g_{rr}(R)^{-1})R/2$.
+One then perturbatively introduces a tidal deformation and solves the perturbed Einstein equations in the NS interior, and matches this solution to an exterior solution at the surface, modulo two integration constants.
+The requirement that the metric be at least $C^{1}$ fixes the ratio between the two constants of integration, yielding the tidal deformability, as discussed in more detail in~\cite{hinderer-love}.
+
 Similar to tidal perturbations, one can consider rotational perturbations.
@@
 At second order in rotation, the quadrupole moment can be extracted by studying the asymptotic behavior of the $g_{t t}$ metric component.
-%One can similarly obtain the moment of inertia from the asymptotic behavior of the $g_{t \phi}$ metric component.
 
@@
 display EoS-insensitive properties to a high degree, showing EoS variations of at most 20\% for binaries with masses less than $1.7 \text{ M}_{\odot}$ and using a representative sample of 11 EoSs. 
-These ``binary Love relations" allow one to analytically break degeneracies between the tidal parameters: one can substitute $\Lambda_{a}=\Lambda_{a}(\Lambda_{s})$ in the GW model, thus completly eliminating $\Lambda_{a}$ from the parameter list (or vice-versa).
+These ``binary Love relations" allow one to analytically break degeneracies between the tidal parameters: one can substitute $\Lambda_{a}=\Lambda_{a}(\Lambda_{s})$ in the GW model, thus completely eliminating $\Lambda_{a}$ from the parameter list (or vice-versa).
 This is important for two reasons: (i) the new model allows for the more accurate extraction of $\Lambda_{s}$ (or $\Lambda_{a}$ if $\Lambda_{s}$ is eliminated), and (ii) the relations allow for the inference of $\Lambda_{a}$ given a measurement of $\Lambda_{s}$ (or vice-versa), and from this for the inference of the individual tidal deformabilities $\Lambda_{1}$ and $\Lambda_{2}$.
@@
 \caption{
-Individual I-Love-Q relations $\bar{I}-\Lambda$ (left), $\bar{Q}-\Lambda$ (center), and $\bar{I}-\bar{Q}$ (right), shown for both the constrained EoSs (solid green) and unconstrained EoSs (dotted maroon).
+(Color Online) Individual I-Love-Q relations $\bar{I}-\Lambda$ (left), $\bar{Q}-\Lambda$ (center), and $\bar{I}-\bar{Q}$ (right), shown for both the constrained EoSs (solid green) and unconstrained EoSs (dotted maroon).
 In these figures, the black dashed lines correspond to the fits given by Eq.~\eqref{eq:ILQfitNew}.
@@
 
-The fractional differences \ky{of hybrid stars from the fit} for the second case (fit to only the constrained EoSs) is shown with dashed green lines in Fig.~\ref{fig:ILQ}, while the maximum EoS variation for the I-Love relation is shown in Table~\ref{tab:hybridCompare} for both the constrained and hybrid star cases.
-The hybrid star EoSs obey the I-Love-Q relations in each case to better than $\sim1.7$\%, a variability that is slightly higher than that found when using only nuclear matter EoSs in previous works~\cite{Yagi:2013bca,Yagi:ILQ} \kent{and is consistent with~\cite{Paschalidis2018}}.
+The fractional differences of hybrid stars from the fit for the second case (fit to only the constrained EoSs) is shown with dashed green lines in Fig.~\ref{fig:ILQ}, while the maximum EoS variation for the I-Love relation is shown in Table~\ref{tab:hybridCompare} for both the constrained and hybrid star cases.
+The hybrid star EoSs obey the I-Love-Q relations in each case to better than $\sim1.7$\%, a variability that is slightly higher than that found when using only nuclear matter EoSs in previous works~\cite{Yagi:2013bca,Yagi:ILQ}, and is consistent with~\cite{Paschalidis2018}.
 The universality cannot be improved much through the introduction of new fits, only bringing the maximal EoS variation down to $\sim1$\% for the fits constructed with only hybrid star EoSs.
@@
 \caption{
-Similar to Fig.~\ref{fig:ILQ} but for the C-Love (left) and the R-Love relations (right).
-\kent{In the top panels, we show two different fits, one for the unconstrained set and one for the constrained set of EoSs.} The bottom panels show the \emph{absolute differences} (rather than fractional difference as in Fig.~\ref{fig:ILQ}) from the fit.
+(Color online) Similar to Fig.~\ref{fig:ILQ} but for the C-Love (left) and the R-Love relations (right).
+In the top panels, we show two different fits, one for the unconstrained set and one for the constrained set of EoSs.
+The bottom panels show the \emph{absolute differences} (rather than fractional difference as in Fig.~\ref{fig:ILQ}) from the fit.
 The absolute difference is suppressed in the constrained set case relative to the unconstrained set, and results from previous work~\cite{Maselli:2013mva}.
-In the left panel, we also present the C-Love relations in the hybrid star cases (dashed green) for comparison, where, although still EoS-insensitive, the degree of universality decreases.
-\ky{Zack, can you please make the ordering of legends as consistent as possible among different plots?
-For example, ``Fits'' is mentioned last in the left panel while it's at the beginning on the right panel.}
+In the left panel, we also present the corresponding relations in the hybrid star cases (dashed green) for comparison, where, although still EoS-insensitive, the degree of universality decreases.
 }
@@
 
-\ky{Somehow we've been citing~\cite{Yagi:binLove} for the C-Love relation, but I think this should really be~\cite{Maselli:2013mva} so I've modified throughout.}
-
 Following Ref.~\cite{Maselli:2013mva}, we begin by fitting the data for each set of EoSs to the simple curve
@@
 
-The left panel of Fig.~\ref{fig:clove} shows the C-Love relations for both the constrained and unconstrained sets, along with the corresponding \emph{absolute differences}\footnote{\kent{We present absolute differences instead of fractional differences since the former is what matters directly to the GW data analysis.}} from the fits (instead of the fractional differences as done back in Fig.~\ref{fig:ILQ}).
+The left panel of Fig.~\ref{fig:clove} shows the C-Love relations for both the constrained and unconstrained sets, along with the corresponding \emph{absolute differences}\footnote{We present absolute differences instead of fractional differences since the former is what matters directly to the GW data analysis.} from the fits (instead of the fractional differences as done back in Fig.~\ref{fig:ILQ}).
 The fit to the constrained EoSs suppresses the EoS variability compared to the fit to the unconstrained set, as well as that of previous work~\cite{Maselli:2013mva}.
@@
 
-From the C-Love relations, we can also compute directly the R-Love relation using $R(\Lambda)=M/C(\Lambda)$ for NSs of mass $M$ \ky{Did you use $M(\Lambda)$ to find $R(\Lambda)$, or did you fix the mass to be something when plotting Fig.~4?}.
+From the C-Love relations, we can also compute directly the R-Love relation using $R(\Lambda)=M/C(\Lambda)$ for NSs of mass $M$.
 The right panel of Fig.~\ref{fig:clove} shows the R-Love relations for the constrained and unconstrained sets, with the bottom panel showing the absolute difference of the data and the fits.
@@
 
-\kent{In the top} left panel of Fig.~\ref{fig:clove}, we show the C-Love relations \kent{for hybrid stars (dashed green curves), while in the bottom panel, we show the absolute difference of the relations for such stars from the fit constructed only from} the constrained set (dashed green curves).
+In the top left panel of Fig.~\ref{fig:clove}, we show the C-Love relations for hybrid stars (dashed green curves), while in the bottom panel, we show the absolute difference of the relations for such stars from the fit constructed only from the constrained set of EoSs (dashed green curves).
 The C-Love relations for hybrid stars remain EoS-insensitive, but the degree of universality is not as high as in the case of hadronic NSs.
@@
 From this, we conclude that hybrid stars do obey the C-Love relation derived for nuclear matter stars, with the caveat that the maximum universality increases to $\sim 7.1\%$.
-
-\ky{Why don't we show R-Love for hybrid stars?}
+For completeness, we also show the R-Love relations for hybrid stars in Fig.~\ref{fig:clove}.
+The absolute differences from the (constrained EoS) fit are similarly displayed in the bottom panel, showing a maximum eos variability of $\sim50\text{ m}$, consistent with the uncertainties found in the unconstrained relations.
 
@@
 Similar to Table~\ref{tab:hybridCompare} but for the C-Love relation.
-For all 3 cases, the hybrid EoSs are only universal up to a minimum of $\sim1$\% (fractional difference from the fit), while in each case the constrained EoSs outperform the hybrid ones \ky{Is this true?
-For case 3, hybrid one has smaller number than the constrained one.}.
+For all 3 cases, the hybrid EoSs are only universal up to a minimum of $\sim1$\% (fractional difference from the fit), and the constrained EoSs typically outperform the hybrid ones (other than the third case where the hybrid stars show slightly better agreement to the fit).
 The second case is also shown in Fig.~\ref{fig:clove}.
@@
 
-Let us now consider the binary Love relations. \kent{As for other relations, we consider nuclear matter stars and hybrid stars separately.}
+Let us now consider the binary Love relations. As for other relations, we consider nuclear matter stars and hybrid stars separately.
 
@@
 where $\mathcal{N}(\mu_r,\sigma_r)$ is a normal distribution with mean and variance $\mu_{r}$ and $\sigma_{r}^2$.
-Let us further assume that the residuals $r$ obey a Gaussian distribution with mean and standard deviation that can be decomposed as \ky{Are you }
+Let us further assume that the residuals $r$ obey a Gaussian distribution with mean and standard deviation that can be decomposed as
 \begin{align}
@@
 The EoS-variability in $\lambda_0$ is dominated by the region around $q \sim 0.5$ and $\Lambda_{s} \sim 2000$.
-\ky{I don't see the connection between this sentence and the previous one.
-(How did we arrive at using $P_{90}=13.19$ from the fact that the EoS variability peaks around $q \sim 0.5$ and $\Lambda_{s} \sim 2000$?)} Henceforth, we approximate the EoS-variability in the binary Love relations with the 90\% credible interval, which for the $\lambda_{0}$ parameter is $P_{90}=13.19$ (indicated by the dashed green line in Fig.~\ref{fig:qLsResiduals} and the dashed indigo line in Fig.~\ref{fig:stackedFisher}).
+Henceforth, in order to take into account these high-error regions of parameter space which may get averaged out, we approximate the EoS-variability in the binary Love relations with the 90\% credible interval (rather than the $1\sigma$ uncertainty), which for the $\lambda_{0}$ parameter is $P_{90}=13.19$ (indicated by the dashed green line in Fig.~\ref{fig:qLsResiduals} and the dashed indigo line in Fig.~\ref{fig:stackedFisher}).
 We can similarly derive a conservative estimate of the systematic uncertainty due to EoS-variability in the binary Love relations in terms of $\tilde\Lambda_{a}$ to find $12.01$, which is what we use later in Fig.~\ref{fig:singleFisherLt}.
@@
 \caption{
-\ky{What are $\Lambda_s$ and $q$ used to produce this plot?}
-Residuals on $\lambda_0$ computed as $\mathcal{R}=\lambda_0^{\text{relation}}-\lambda_0^{\text{true}}$ for the binary Love relations modeled in Sec.~\ref{sec:binary} for both constrained and unconstrained sets of EoSs.
+Residuals on $\lambda_0$ computed as $\mathcal{R}=\lambda_0^{\text{relation}}-\lambda_0^{\text{true}}$ (computed by sampling $q\in \lbrack0.36,1\rbrack$ and $\Lambda_{s} \in \lbrack 4,4600 \rbrack$ for each of the 100 EoS samples) for the binary Love relations modeled in Sec.~\ref{sec:binary} for both constrained and unconstrained sets of EoSs.
 We fit these residuals with Gaussian distributions centered at $\mu=-0.1530$ and $\mu=0.2710$ with standard deviations of $\sigma=9.764$ and $\sigma=78.28$ for the constrained and unconstrained sets of EoSs, respectively.
@@
 Also shown in the figure is the 90th percentile of the un-binned residuals seen in Fig.~\ref{fig:residuals}, taken to be the overall systematic uncertainty introduced by using binary Love relations.
-\ky{Can we have 4 small ticks between large ticks instead of 3?}
 }
@@
 Further, we scale the luminosity distance such that the signal-to-noise-ratio ($SNR \equiv \rho$) is fixed to $\rho=32.4$, as found in GW170817.
-\ky{I think we should also explain what fiducial values we used for all the other parameters, like masses and $\tilde \Lambda$.} We also assume low spin priors $|\chi| \leq 0.05$, as well as $\tilde{\Lambda} \leq 3000$ and $|\delta \tilde{\Lambda}| \leq 500$~\cite{Wade:LambdaPriors}.
+We used fiducial template parameter values of $D_L=21.7$ Mpc for the luminosity distance, $\mathcal{M}=1.22\text{ M}_\odot$ for the chirp mass, $\eta=0.249$ for the symmetric mass ratio, $\tilde\Lambda=395$ (Corresponding to GW170817), and $0$ for the remaining parameters.
+We also assume low spin priors $|\chi| \leq 0.05$, as well as $\tilde{\Lambda} \leq 3000$ and $|\delta \tilde{\Lambda}| \leq 500$~\cite{Wade:LambdaPriors}.
 The resulting $90\%$ credible region of the posterior distribution on $\tilde{\Lambda}$ has a range of $\pm 276.99$, which is in close agreement to that found by LIGO~\cite{TheLIGOScientific:2017qsa,Abbott2018}
@@
 Also shown is $2 \sqrt{f}$ multiplied by the amplitude of the PhenomD~\cite{PhenomDI,PhenomDII} waveform template.
-\ky{Please change ``a++'' to ``A+'' in the legend. Same comment applies to Fig.~9.}
 }
@@
 The latter is calculated by integrating the local binary NS merger rate over redshifts up to the horizon redshift of each detector.
-As before, for each Fisher calculation we assume low spin priors $|\chi| \leq 0.05$, as well as $0 \leq \lambda_0 \leq 3207$ and $-4490 \leq \lambda_1 \leq 0$~\cite{delPozzo:TaylorTidal}\footnote{These are converted from the dimensional forms found in~\cite{delPozzo:TaylorTidal} into their corresponding dimensionless forms.}.
+Similar to before, we used fiducial template parameter values of $D_L=21.7$ Mpc for the luminosity distance, $\mathcal{M}=1.22\text{ M}_\odot$ for the chirp mass, $\eta=0.249$ for the symmetric mass ratio, $\lambda_0=150$, $\lambda_1=-213$ (corresponding to the GW170817), and $0$ for the remaining parameters.
+Also as before, for each Fisher calculation we assume low spin priors $|\chi| \leq 0.05$, as well as $0 \leq \lambda_0 \leq 3207$ and $-4490 \leq \lambda_1 \leq 0$~\cite{delPozzo:TaylorTidal}\footnote{These are converted from the dimensional forms found in~\cite{delPozzo:TaylorTidal} into their corresponding dimensionless forms.}.
 The process we use to compute single and combined statistical uncertainties for each detector sensitivity $S_n^A(f)$ is detailed in App.~\ref{app:stackingProcedure}.
@@
 The statistical and the systematic errors become comparable for Voyager-class detectors or better.
-\ky{I sort of feel that we only need to show $\sigma > 1$.
-}
 }
@@
 \centering
-\begin{tabular}{|c|@{\extracolsep{4pt}}c@{\extracolsep{0pt}}|c|@{\extracolsep{4pt}}C{1.7cm}@{\extracolsep{-2pt}}|C{1.7cm}|@{\extracolsep{-2pt}}C{1.7cm}@{\extracolsep{2pt}}|c|@{\extracolsep{0pt}}c@{\extracolsep{0pt}}|c|}
+\begin{tabular}{|c|@{\extracolsep{4pt}}C{1.7cm}@{\extracolsep{0pt}}|C{1.7cm}|@{\extracolsep{4pt}}C{1.7cm}@{\extracolsep{-2pt}}|C{1.7cm}|@{\extracolsep{-2pt}}C{1.7cm}@{\extracolsep{2pt}}|C{1.7cm}|@{\extracolsep{0pt}}C{1.7cm}@{\extracolsep{0pt}}|C{1.7cm}|}
 \cline{1-1}\cline{2-3}\cline{4-9}
@@
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
- O2  & \multicolumn{1}{|c|}{$32.40$}  & $170.13$ &  \multicolumn{1}{|c|}{--} & -- & -- & \multicolumn{1}{|c|}{--} & -- & --\\
+&\multicolumn{1}{|c|}{}&&\multicolumn{1}{|c|}{}&&&\multicolumn{1}{|c|}{}&&\\[-1em]
+ O2  & \multicolumn{1}{|c|}{$\sci{3.2}{1}$}  & $\sci{1.7}{2}$ &  \multicolumn{1}{|c|}{--} & -- & -- & \multicolumn{1}{|c|}{--} & -- & --\\
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
- aLIGO  & \multicolumn{1}{|c|}{$90.74$}  & $109.7$ &  \multicolumn{1}{|c|}{$20$} & $98$ & $304$ & \multicolumn{1}{|c|}{$182.8$} & $83.31$ & $46.95$\\
+&\multicolumn{1}{|c|}{}&&\multicolumn{1}{|c|}{}&&&\multicolumn{1}{|c|}{}&&\\[-1em]
+ aLIGO  & \multicolumn{1}{|c|}{$\sci{9.1}{1}$}  & $\sci{1.1}{2}$ &  \multicolumn{1}{|c|}{$\sci{2.0}{1}$} & $\sci{9.8}{1}$ & $\sci{3.0}{2}$ & \multicolumn{1}{|c|}{$\sci{1.8}{2}$} & $\sci{8.3}{1}$ & $\sci{4.7}{1}$\\
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
- A\texttt{+}  & \multicolumn{1}{|c|}{$180.95$}  & $45.64$ &  \multicolumn{1}{|c|}{163} & 786 & 2,419 & \multicolumn{1}{|c|}{$58.94$} & $24.69$ & $13.66$\\
+&\multicolumn{1}{|c|}{}&&\multicolumn{1}{|c|}{}&&&\multicolumn{1}{|c|}{}&&\\[-1em]
+ A\texttt{+}  & \multicolumn{1}{|c|}{$\sci{1.8}{2}$}  & $\sci{4.6}{1}$ &  \multicolumn{1}{|c|}{$\sci{1.6}{2}$} & $\sci{7.9}{2}$ & $\sci{2.4}{3}$ & \multicolumn{1}{|c|}{$\sci{5.9}{1}$} & $\sci{2.5}{1}$ & $\sci{1.4}{1}$\\
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
@@
 \\[-1em]
-
- Voyager  & \multicolumn{1}{|c|}{$428.89$}  & $25.26$ &  \multicolumn{1}{|c|}{2,191} & 10,544 & 32,454 & \multicolumn{1}{|c|}{$20.97$} & $9.556$ & $5.323$\\
+&\multicolumn{1}{|c|}{}&&\multicolumn{1}{|c|}{}&&&\multicolumn{1}{|c|}{}&&\\[-1em]
+ Voyager  & \multicolumn{1}{|c|}{$\sci{4.3}{2}$}  & $\sci{2.5}{1}$ &  \multicolumn{1}{|c|}{$\sci{2.2}{3}$} & $\sci{1.1}{4}$ & $\sci{3.2}{4}$ & \multicolumn{1}{|c|}{$\sci{2.1}{1}$} & $\sci{9.6}{0}$ & $\sci{5.3}{0}$\\
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
@@
 \\[-1em]
-
- ET-D  & \multicolumn{1}{|c|}{$1398.03$}  & $6.871$ &  \multicolumn{1}{|c|}{71,536} & 344,270 & 1,059,638 & \multicolumn{1}{|c|}{$3.848$} & $1.732$ & $0.9621$\\
+&\multicolumn{1}{|c|}{}&&\multicolumn{1}{|c|}{}&&&\multicolumn{1}{|c|}{}&&\\[-1em]
+ ET-D  & \multicolumn{1}{|c|}{$\sci{1.4}{3}$}  & $\sci{6.9}{0}$ &  \multicolumn{1}{|c|}{$\sci{7.2}{4}$} & $\sci{3.4}{5}$ & $\sci{1.1}{6}$ & \multicolumn{1}{|c|}{$\sci{3.8}{0}$} & $\sci{1.7}{0}$ & $\sci{9.6}{-1}$\\
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
@@
 \\[-1em]
-
- CE  & \multicolumn{1}{|c|}{$2807.45$}  & $7.664$ &  \multicolumn{1}{|c|}{295,200} & 1,420,650 & 4,372,653 & \multicolumn{1}{|c|}{$3.720$} & $1.668$ & $0.8979$\\
+&\multicolumn{1}{|c|}{}&&\multicolumn{1}{|c|}{}&&&\multicolumn{1}{|c|}{}&&\\[-1em]
+ CE  & \multicolumn{1}{|c|}{$\sci{2.8}{3}$}  & $\sci{7.7}{0}$ &  \multicolumn{1}{|c|}{$\sci{3.0}{5}$} & $\sci{1.4}{6}$ & $\sci{4.4}{6}$ & \multicolumn{1}{|c|}{$\sci{3.7}{0}$} & $\sci{1.7}{0}$ & $\sci{9.0}{-1}$\\
 \cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
@@
 The statistical uncertainties on $\lambda_0$ becomes comparable with the systematic uncertainty (set to be $P_{90}=13.19$) from using the improved binary Love relations with detectors of Voyager-class or better.
-\ky{Do we really need to show numbers with 7 digits...? I think it's enough to just show the first few digits in a form $a.b \times 10^X$ in each cell.}
 }\label{tab:variances}

### 2019-02-27 paper/bin-love-after-gw170817.tex
minor

@@
 For completeness, we also show the R-Love relations for hybrid stars in Fig.~\ref{fig:clove}.
-The absolute differences from the (constrained EoS) fit are similarly displayed in the bottom panel, showing a maximum eos variability of $\sim50\text{ m}$, consistent with the uncertainties found in the unconstrained relations.
+The absolute differences from the (constrained EoS) fit are similarly displayed in the bottom panel, showing a maximum EoS variability of $\sim50\text{ m}$, consistent with the uncertainties found in the unconstrained relations.
 

### 2019-02-27 paper/bin-love-after-gw170817.tex
minor change

@@
 Further, we scale the luminosity distance such that the signal-to-noise-ratio ($SNR \equiv \rho$) is fixed to $\rho=32.4$, as found in GW170817.
-We used fiducial template parameter values of $D_L=21.7$ Mpc for the luminosity distance, $\mathcal{M}=1.22\text{ M}_\odot$ for the chirp mass, $\eta=0.249$ for the symmetric mass ratio, $\tilde\Lambda=395$ (Corresponding to GW170817), and $0$ for the remaining parameters.
+We used fiducial template parameter values of $\mathcal{M}=1.22\text{ M}_\odot$ for the chirp mass, $\eta=0.249$ for the symmetric mass ratio, $\tilde\Lambda=395$ (Corresponding to GW170817), and $0$ for the remaining parameters.
 We also assume low spin priors $|\chi| \leq 0.05$, as well as $\tilde{\Lambda} \leq 3000$ and $|\delta \tilde{\Lambda}| \leq 500$~\cite{Wade:LambdaPriors}.
@@
 The latter is calculated by integrating the local binary NS merger rate over redshifts up to the horizon redshift of each detector.
-Similar to before, we used fiducial template parameter values of $D_L=21.7$ Mpc for the luminosity distance, $\mathcal{M}=1.22\text{ M}_\odot$ for the chirp mass, $\eta=0.249$ for the symmetric mass ratio, $\lambda_0=150$, $\lambda_1=-213$ (corresponding to the GW170817), and $0$ for the remaining parameters.
+Similar to before, we used fiducial template parameter values of $\mathcal{M}=1.22\text{ M}_\odot$ for the chirp mass, $\eta=0.249$ for the symmetric mass ratio, $\lambda_0=150$, $\lambda_1=-213$ (corresponding to the GW170817), and $0$ for the remaining parameters.
 Also as before, for each Fisher calculation we assume low spin priors $|\chi| \leq 0.05$, as well as $0 \leq \lambda_0 \leq 3207$ and $-4490 \leq \lambda_1 \leq 0$~\cite{delPozzo:TaylorTidal}\footnote{These are converted from the dimensional forms found in~\cite{delPozzo:TaylorTidal} into their corresponding dimensionless forms.}.

### 2019-02-28 paper/bin-love-after-gw170817.tex
comments from Carl

@@
  LIGO Laboratory and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, Massachusetts 02139, USA
-}%
-%\affiliation{%
-% Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY 10010
-%}%
+}
 
@@
 % Intro
-The thermodynamic relation between pressure and density (i.e.~the equation of state) of cold supranuclear matter is critical to neutron stars, yet it remains one of the largest uncertainties in nuclear physics.
+The thermodynamic relation between pressure and density (i.e.~the equation of state) of cold supranuclear matter is critical \chs{to} \ch{in describing} neutron stars, yet it remains one of the largest uncertainties in nuclear physics.
 % How to probe
@@
 These observations, however, may potentially suffer from large systematic errors~\cite{Miller2013} due to uncertainties in the astrophysical modeling of X-ray bursts.
-The gravitational waves (GWs) emitted in the coalesce of NS binaries may be a cleaner probe of nuclear physics.
-During the early inspiral, the orbital separation is large enough that the tidal fields are negligible; but as the orbital separation decreases due to GW emission, tidal forces grow and the NSs respond by developing deformations controlled by their nuclear EoS.
+The gravitational waves (GWs) emitted in the coalescence of NS binaries may be a cleaner probe of nuclear physics.
+During the early inspiral, the orbital separation is large enough that the tidal fields are negligible; but as the orbital separation decreases due to GW emission, tidal forces grow and the NSs respond by developing deformations \chs{controlled}\ch{determined} by their nuclear EoS.
 These deformations affect the orbital trajectory of the binary, and thus the GWs emitted, encoding in the latter the NS EoS~\cite{hinderer-love,Flanagan2008}.
@@
 %reparameterization of the template
-The GWs emitted by binary NSs in the late inspiral must then depend on the \emph{tidal deformabilities} $\Lambda_1$ and $\Lambda_2$, which control the linear response of the star's quadrupole deformation to the (electric-type, quadrupole) tidal field of the companion (to leading order in a post-Newtonian expansion~\cite{Blanchet:2013haa})~\cite{Flanagan2008,Vines:2011ud}.
-These parameters, however, enter the GW Fourier model at the same post-Newtonian order, making them degenerate, and thus, very difficult to estimate independently with current GW data~\cite{Wade:tidalCorrections}.
+The GWs emitted by binary NSs in the late inspiral must then depend on the \emph{tidal deformabilities} $\Lambda_1$ and $\Lambda_2$\footnote{\ch{Throughout this work we use the convention that binary quantities are indexed as $1,2$ where 1 always correspond to the less massive object.}}, which control the linear response of the star's quadrupole deformation to the (electric-type, quadrupole) tidal field of the companion (to leading order in a post-Newtonian expansion~\cite{Blanchet:2013haa})~\cite{Flanagan2008,Vines:2011ud}.
+These parameters, however, enter the GW Fourier model \ch{'I think GW Fourier model isn't immediately clear, switch to "GW waveform model"?'} at the same post-Newtonian order, making them degenerate, and thus, very difficult to estimate independently with current GW data~\cite{Wade:tidalCorrections}.
 Instead, one can extract certain combinations of the tidal deformabilities, such as a certain mass-weighted tidal deformability $\tilde{\Lambda}$~\cite{Favata:2013rwa,Wade:tidalCorrections}, or one can extract the (mass-independent) coefficients $(\lambda_{0},\lambda_{1},\ldots)$ of a Taylor expansion of the tidal deformabilities about some fiducial mass~\cite{Messenger:2011gi,delPozzo:TaylorTidal,Yagi:binLove}.
-Current detectors are not sensitive enough to accurately measure any of these coefficients, but future detectors will and the information from multiple events could then be combined, since the Taylor expansion coefficient should be common to all events.
+Current detectors are not sensitive enough to accurately measure any of these coefficients, but future detectors will, and the information from multiple events could then be combined, since the Taylor expansion coefficients should be common to all events.
 
@@
 With those at hand, one can further use EoS-insensitive relations between the tidal deformabilities and the compactness, the so-called ``C-Love relations''~\cite{Yagi:2013bca,Yagi:ILQ,Maselli:2013mva,Yagi:2016bkt}, to infer the radii of the NSs, and thus, to place two constraints in the mass-radius plane, one for each star in the binary.
-This idea was recently implemented in GW170817~\cite{TheLIGOScientific:2017qsa}, allowing for an EoS-independent constraints on the mass-radius curve using GW data~\cite{Katerina:residuals,LIGO:posterior}.
+This idea was recently implemented for GW170817~\cite{TheLIGOScientific:2017qsa}, allowing \chs{for an} EoS-independent constraints on the mass-radius curve using GW data~\cite{Katerina:residuals,LIGO:posterior}.
 
@@
 With this study at hand, we then carry out additional related studies on EoS-insensitive relations that go beyond the work in~\cite{Yagi:binLove,Yagi:ILQ}.
-First, we investigate the relation between the NS radius and its tidal deformability, the R-Love relations, for both sets of EoSs, because these are critical to place constraints on the radius from a measurement of the Love number.
+First, we investigate the relation between the NS radius and its tidal deformability, the R-Love relations, for both sets of EoSs, as these are critical in order to place constraints on the radius from a measurement of the Love number.
 We use the C-Love relations to construct the R-Love relations and find that the maximum EoS variability drops from $\sim 880 {\rm{km}}$ in the unconstrained case to $\sim 360 {\rm{km}}$ in the constrained case (see Sec.~\ref{sec:clove} for more details).
@@
 \end{equation}
-where $q\equiv m_{1}/m_{2}$ is the mass ratio with $m_1 \leq m_2$, and $F_n(q)$ is the Newtonian-limiting controlling factor, given by
+where $q\equiv m_{1}/m_{2}$ is the mass ratio with $m_1 \leq m_2$ \ch{in LIGO we use the convention where $m_2 \leq m_1$ and $q\equiv m_{2}/m_{1}$.
+It doesn't make any real difference, but might cause less confusion.
+If the change is made here, please also change the footnote about indeces I added earlier}, and $F_n(q)$ is the Newtonian-limiting controlling factor, given by
 \begin{equation}\label{eq:control}
@@
 Second, the fit to the constrained set does not extend to as high values of $\Lambda_s$ as the fit to the unconstrained set does.
-This is because of how the sets of EoSs were generated in our analysis, with the unconstrained set including some EoSs that are stiffer and others that are softer than those constrained by the GW170817 event.
+This is because of how the sets of EoSs were generated in our analysis, with the unconstrained set including some EoSs that are stiffer \ch{this is the only place where EoS "stiffness" is discussed, might want to clarify that a bit} and others that are softer than those constrained by the GW170817 event.
 This results in the unconstrained set  containing a larger range of tidal deformabilities $\Lambda_{1,2}$ (from both above and below) than the constrained set, which ultimately leads to a \emph{larger} range of $\Lambda_s=\frac{1}{2}(\Lambda_1+\Lambda_2)$ values.
@@
 Current interferometer sensitivities are not yet high enough to accurately constrain the dominant tidal parameter $\tilde{\Lambda}$.
-For example, GW170817 was detected by LIGO observing run 2 (``O2")~\cite{aLIGO} and VIRGO~\cite{TheVirgo:2014hva} and was able to constrain $\tilde{\Lambda}$ to a $90\%$ credible interval centered at $\mu_{\tilde{\Lambda}}=395$ and with a width of 325 (or $\sigma_{\tilde{\Lambda}} \approx 198$).
+For example, GW170817 was detected by \chs{LIGO observing run 2} \ch{the second LIGO observing run} (``O2")~\cite{aLIGO} and Virgo~\cite{TheVirgo:2014hva} \ch{Virgo is not formally an abbreviation,  so it's not all capitalized} and was able to constrain $\tilde{\Lambda}$ to a $90\%$ credible interval centered at $\mu_{\tilde{\Lambda}}=395$ and with a width of 325 (or $\sigma_{\tilde{\Lambda}} \approx 198$).
 This corresponds to statistical uncertainties of ${\cal{O}}(80\%)$, which dominates the error budget compared to the small systematic uncertainties picked up by EoS variation in the EoS-insensitive relations.
@@
 \end{equation}
-where $\eta \equiv m_1 m_2/m^2$ is the symmetric mass ratio with $m_{1,2}$ and $m$ being the individual and total masses, $\mathcal{M}=m \eta^{3/5}$ is the chirp mass, $A \equiv {\mathcal{M}^{5/6}}/({\sqrt{30}\pi^{2/3}D_L})$ is a normalized amplitude factor with $D_L$ the luminosity distance, and $\chi_{s,a}=\frac{1}{2}(\chi_1\pm\chi_2)$ are the symmetric and antisymmetric dimensionless spin parameters.
+where $\eta \equiv m_1 m_2/m^2$ is the symmetric mass ratio with $m_{1,2}$ and $m$ being the individual and total masses, $\mathcal{M}=m \eta^{3/5}$ is the chirp mass, $A \equiv {\mathcal{M}^{5/6}}/({\sqrt{30}\pi^{2/3}D_L})$ is a normalized amplitude factor with $D_L$ the luminosity distance, and $\chi_{s,a}=\frac{1}{2}(\chi_1\pm\chi_2)$ are the symmetric and antisymmetric dimensionless \ch{non-precessing} spin parameters.
 Given a sufficiently loud observation and Gaussian noise, the resulting posterior distribution on the estimated parameters is Gaussian with a root-mean-square error given by
@@
 \end{equation}
-with the overhead tilde and the star standing for the Fourier transform and complex conjugation respectively.
+with the overhead tilde and the star representing the Fourier transform and complex conjugation respectively.
 
@@
 We here consider a ``PhenomD" (IMRD) waveform template~\cite{PhenomDI,PhenomDII} modified by a 6PN tidal correction~\cite{Wade:tidalCorrections} (IMRD + 6PN), as well as a ``PhenomD'' template modified with a NRTidal correction~\cite{Samajdar:NRTidal} (IMRD + NRTidal).
-Considering two template models will allow us to estimate systematic uncertainties due to mismodeling.
+Considering two template models will allow us to estimate systematic uncertainties due to mismodeling \ch{of the GW signal}.
 
@@
 The careful reader will notice that Figs.~\ref{fig:stackedFisher} and~\ref{fig:singleFisherLt} show that the single-event statistical uncertainties using CE is higher than using ET despite the latter having a larger SNR for a GW170817-like event.
-This is because the 3-detector geometry of ET enables it to have higher sensitivity than ET at frequencies above 300Hz, which is precisely where the tidal deformabilities is encoded, but ET has lower sensitivity at lower frequencies, where a lot of the signal-to-noise ratio accumulates.
+This is because the 3-detector geometry of ET enables it to have higher sensitivity than ET at frequencies above 300Hz, which is precisely where the tidal deformabilities is encoded, but ET has lower sensitivity at lower frequencies, where a lot of the signal-to-noise ratio accumulates \ch{confusion about ET and CE in this sentence}.
 
@@
 
-But is the statistical error calculated here robust to mismodeling systematics in the template?
+\chs{But is the statistical error calculated here}\ch{Is the statistical error calculated here however} robust to mismodeling systematics in the template?
 We repeat the analysis above using an IMRD + NRTidal template model  and find results consistent with those presented above.
@@
 Future work on this subject could entail an investigation into the improvement of alternative EoS-insensitive relations, such as the multipole Love relations between various $\ell$-th order electric, magnetic, and shape tidal deformabilities, as discussed in~\cite{Yagi:Multipole}.
-Lackey \emph{et al}~\cite{Lackey:Surrogate, Lackey:EOB} presented surrogate models of non-spinning effective-one-body waveforms with the use of universal relations.
+Lackey \emph{et al.}~\cite{Lackey:Surrogate, Lackey:EOB} presented surrogate models of non-spinning effective-one-body waveforms with the use of universal relations.
 By reducing the number of waveform model parameters, surrogate models aid in the extraction of NS observables from GW detections.

### 2019-02-28 paper/bin-love-after-gw170817.tex
addressing Carls comments

@@
 % Intro
-The thermodynamic relation between pressure and density (i.e.~the equation of state) of cold supranuclear matter is critical \chs{to} \ch{in describing} neutron stars, yet it remains one of the largest uncertainties in nuclear physics.
+The thermodynamic relation between pressure and density (i.e.~the equation of state) of cold supranuclear matter is critical in describing neutron stars, yet it remains one of the largest uncertainties in nuclear physics.
 % How to probe
@@
 The gravitational waves (GWs) emitted in the coalescence of NS binaries may be a cleaner probe of nuclear physics.
-During the early inspiral, the orbital separation is large enough that the tidal fields are negligible; but as the orbital separation decreases due to GW emission, tidal forces grow and the NSs respond by developing deformations \chs{controlled}\ch{determined} by their nuclear EoS.
+During the early inspiral, the orbital separation is large enough that the tidal fields are negligible; but as the orbital separation decreases due to GW emission, tidal forces grow and the NSs respond by developing deformations determined by their nuclear EoS.
 These deformations affect the orbital trajectory of the binary, and thus the GWs emitted, encoding in the latter the NS EoS~\cite{hinderer-love,Flanagan2008}.
@@
 %reparameterization of the template
-The GWs emitted by binary NSs in the late inspiral must then depend on the \emph{tidal deformabilities} $\Lambda_1$ and $\Lambda_2$\footnote{\ch{Throughout this work we use the convention that binary quantities are indexed as $1,2$ where 1 always correspond to the less massive object.}}, which control the linear response of the star's quadrupole deformation to the (electric-type, quadrupole) tidal field of the companion (to leading order in a post-Newtonian expansion~\cite{Blanchet:2013haa})~\cite{Flanagan2008,Vines:2011ud}.
-These parameters, however, enter the GW Fourier model \ch{'I think GW Fourier model isn't immediately clear, switch to "GW waveform model"?'} at the same post-Newtonian order, making them degenerate, and thus, very difficult to estimate independently with current GW data~\cite{Wade:tidalCorrections}.
+The GWs emitted by binary NSs in the late inspiral must then depend on the \emph{tidal deformabilities} $\Lambda_1$ and $\Lambda_2$\footnote{Throughout this work we use the convention that binary quantities are indexed as $1,2$ where 1 always correspond to the more massive object.}, which control the linear response of the star's quadrupole deformation to the (electric-type, quadrupole) tidal field of the companion (to leading order in a post-Newtonian expansion~\cite{Blanchet:2013haa})~\cite{Flanagan2008,Vines:2011ud}.
+These parameters, however, enter the GW waveform model at the same post-Newtonian order, making them degenerate, and thus, very difficult to estimate independently with current GW data~\cite{Wade:tidalCorrections}.
 Instead, one can extract certain combinations of the tidal deformabilities, such as a certain mass-weighted tidal deformability $\tilde{\Lambda}$~\cite{Favata:2013rwa,Wade:tidalCorrections}, or one can extract the (mass-independent) coefficients $(\lambda_{0},\lambda_{1},\ldots)$ of a Taylor expansion of the tidal deformabilities about some fiducial mass~\cite{Messenger:2011gi,delPozzo:TaylorTidal,Yagi:binLove}.
@@
 With those at hand, one can further use EoS-insensitive relations between the tidal deformabilities and the compactness, the so-called ``C-Love relations''~\cite{Yagi:2013bca,Yagi:ILQ,Maselli:2013mva,Yagi:2016bkt}, to infer the radii of the NSs, and thus, to place two constraints in the mass-radius plane, one for each star in the binary.
-This idea was recently implemented for GW170817~\cite{TheLIGOScientific:2017qsa}, allowing \chs{for an} EoS-independent constraints on the mass-radius curve using GW data~\cite{Katerina:residuals,LIGO:posterior}.
+This idea was recently implemented for GW170817~\cite{TheLIGOScientific:2017qsa}, allowing EoS-independent constraints on the mass-radius curve using GW data~\cite{Katerina:residuals,LIGO:posterior}.
 
@@
 One common reparameterization is through the introduction of the mass-weighted tidal deformability $\tilde{\Lambda}=\tilde{\Lambda}(\Lambda_1,\Lambda_2)$ and the parameter $\delta \tilde{\Lambda}=\delta \tilde{\Lambda}(\Lambda_1,\Lambda_2)$~\cite{Favata:2013rwa,Wade:tidalCorrections}.
-Since these parameters enter the GW phase at 5 and 6PN orders respectively\footnote{A term of $N$PN order is proportional to $v^{2N}$ relative to the leading-order term in the expression, \kent{where $v$ represents the relative velocity of binary constituents}.}, they partially break the degeneracies between $\Lambda_{1}$ and $\Lambda_{2}$.
+Since these parameters enter the GW phase at 5 and 6PN orders respectively\footnote{A term of $N$PN order is proportional to $v^{2N}$ relative to the leading-order term in the expression, where $v$ represents the relative velocity of binary constituents.}, they partially break the degeneracies between $\Lambda_{1}$ and $\Lambda_{2}$.
 
@@
 \end{equation}
-where $q\equiv m_{1}/m_{2}$ is the mass ratio with $m_1 \leq m_2$ \ch{in LIGO we use the convention where $m_2 \leq m_1$ and $q\equiv m_{2}/m_{1}$.
-It doesn't make any real difference, but might cause less confusion.
-If the change is made here, please also change the footnote about indeces I added earlier}, and $F_n(q)$ is the Newtonian-limiting controlling factor, given by
+where $q\equiv m_{2}/m_{1}$ is the mass ratio with $m_2 \leq m_1$, and $F_n(q)$ is the Newtonian-limiting controlling factor, given by
 \begin{equation}\label{eq:control}
@@
 Second, the fit to the constrained set does not extend to as high values of $\Lambda_s$ as the fit to the unconstrained set does.
-This is because of how the sets of EoSs were generated in our analysis, with the unconstrained set including some EoSs that are stiffer \ch{this is the only place where EoS "stiffness" is discussed, might want to clarify that a bit} and others that are softer than those constrained by the GW170817 event.
+This is because of how the sets of EoSs were generated in our analysis, with the unconstrained set including some EoSs that are stiffer\footnote{Typically, the ``stiffness" of an EoS is determined by the amount of pressure gained given an increase in density.
+Stiff EoSs have steep pressures and predict more massive NSs, while soft EoSs have shallow pressures and predict smaller mass NSs.} and others that are softer than those constrained by the GW170817 event.
 This results in the unconstrained set  containing a larger range of tidal deformabilities $\Lambda_{1,2}$ (from both above and below) than the constrained set, which ultimately leads to a \emph{larger} range of $\Lambda_s=\frac{1}{2}(\Lambda_1+\Lambda_2)$ values.
@@
 Current interferometer sensitivities are not yet high enough to accurately constrain the dominant tidal parameter $\tilde{\Lambda}$.
-For example, GW170817 was detected by \chs{LIGO observing run 2} \ch{the second LIGO observing run} (``O2")~\cite{aLIGO} and Virgo~\cite{TheVirgo:2014hva} \ch{Virgo is not formally an abbreviation,  so it's not all capitalized} and was able to constrain $\tilde{\Lambda}$ to a $90\%$ credible interval centered at $\mu_{\tilde{\Lambda}}=395$ and with a width of 325 (or $\sigma_{\tilde{\Lambda}} \approx 198$).
+For example, GW170817 was detected by the second LIGO observing run (``O2")~\cite{aLIGO} and Virgo~\cite{TheVirgo:2014hva} Virgo is not formally an abbreviation,  so it's not all capitalized and was able to constrain $\tilde{\Lambda}$ to a $90\%$ credible interval centered at $\mu_{\tilde{\Lambda}}=395$ and with a width of 325 (or $\sigma_{\tilde{\Lambda}} \approx 198$).
 This corresponds to statistical uncertainties of ${\cal{O}}(80\%)$, which dominates the error budget compared to the small systematic uncertainties picked up by EoS variation in the EoS-insensitive relations.
@@
 \end{equation}
-where $\eta \equiv m_1 m_2/m^2$ is the symmetric mass ratio with $m_{1,2}$ and $m$ being the individual and total masses, $\mathcal{M}=m \eta^{3/5}$ is the chirp mass, $A \equiv {\mathcal{M}^{5/6}}/({\sqrt{30}\pi^{2/3}D_L})$ is a normalized amplitude factor with $D_L$ the luminosity distance, and $\chi_{s,a}=\frac{1}{2}(\chi_1\pm\chi_2)$ are the symmetric and antisymmetric dimensionless \ch{non-precessing} spin parameters.
+where $\eta \equiv m_1 m_2/m^2$ is the symmetric mass ratio with $m_{1,2}$ and $m$ being the individual and total masses, $\mathcal{M}=m \eta^{3/5}$ is the chirp mass, $A \equiv {\mathcal{M}^{5/6}}/({\sqrt{30}\pi^{2/3}D_L})$ is a normalized amplitude factor with $D_L$ the luminosity distance, and $\chi_{s,a}=\frac{1}{2}(\chi_1\pm\chi_2)$ are the symmetric and antisymmetric dimensionless non-precessing spin parameters.
 Given a sufficiently loud observation and Gaussian noise, the resulting posterior distribution on the estimated parameters is Gaussian with a root-mean-square error given by
@@
 We here consider a ``PhenomD" (IMRD) waveform template~\cite{PhenomDI,PhenomDII} modified by a 6PN tidal correction~\cite{Wade:tidalCorrections} (IMRD + 6PN), as well as a ``PhenomD'' template modified with a NRTidal correction~\cite{Samajdar:NRTidal} (IMRD + NRTidal).
-Considering two template models will allow us to estimate systematic uncertainties due to mismodeling \ch{of the GW signal}.
+Considering two template models will allow us to estimate systematic uncertainties due to mismodeling of the GW signal.
 
@@
 The careful reader will notice that Figs.~\ref{fig:stackedFisher} and~\ref{fig:singleFisherLt} show that the single-event statistical uncertainties using CE is higher than using ET despite the latter having a larger SNR for a GW170817-like event.
-This is because the 3-detector geometry of ET enables it to have higher sensitivity than ET at frequencies above 300Hz, which is precisely where the tidal deformabilities is encoded, but ET has lower sensitivity at lower frequencies, where a lot of the signal-to-noise ratio accumulates \ch{confusion about ET and CE in this sentence}.
+This is because the 3-detector geometry of ET enables it to have higher sensitivity than CE at frequencies above 300Hz, which is precisely where the tidal deformabilities are encoded, but ET has lower sensitivity at lower frequencies, where a lot of the signal-to-noise ratio accumulates.
 
@@
 
-\chs{But is the statistical error calculated here}\ch{Is the statistical error calculated here however} robust to mismodeling systematics in the template?
+Is the statistical error calculated here robust to mismodeling systematics in the template?
 We repeat the analysis above using an IMRD + NRTidal template model  and find results consistent with those presented above.

### 2019-02-28 paper/bin-love-after-gw170817.tex
minor modification and final readthrough-spellcheck

@@
 We use the publicly available software library {\tt LALInference}~\cite{Veitch:2014wba,lalinference_o2} to obtain samples from the EoS posterior.
-Our anaysis uses the same settings and prior choice as those of~\cite{LIGO:posterior,Carney:2018sdv}.
+Our analysis uses the same settings and prior choice as those of~\cite{LIGO:posterior,Carney:2018sdv}.
 In both cases, each set consists of 100 members, with a subset of these shown in the left panel of Fig.~\ref{fig:eos}.
@@
 \begin{equation}
-\Lambda_s \equiv \frac{\Lambda_1 + \Lambda_2}{2}, \hspace{6mm} \Lambda_a \equiv \frac{\Lambda_1 - \Lambda_2}{2},
+\Lambda_s \equiv \frac{\Lambda_2 + \Lambda_1}{2}, \hspace{6mm} \Lambda_a \equiv \frac{\Lambda_2 - \Lambda_1}{2},
 \end{equation}
@@
 This is because of how the sets of EoSs were generated in our analysis, with the unconstrained set including some EoSs that are stiffer\footnote{Typically, the ``stiffness" of an EoS is determined by the amount of pressure gained given an increase in density.
-Stiff EoSs have steep pressures and predict more massive NSs, while soft EoSs have shallow pressures and predict smaller mass NSs.} and others that are softer than those constrained by the GW170817 event.
+Stiff EoSs have steep pressures and predict larger maximum mass NSs, while soft EoSs have shallow pressures and predict smaller maximum mass NSs.} and others that are softer than those constrained by the GW170817 event.
 This results in the unconstrained set  containing a larger range of tidal deformabilities $\Lambda_{1,2}$ (from both above and below) than the constrained set, which ultimately leads to a \emph{larger} range of $\Lambda_s=\frac{1}{2}(\Lambda_1+\Lambda_2)$ values.
@@
 When one star lies on the hadronic-matter branch while the other is on the quark-matter branch, the difference between tidal deformabilities becomes larger than expected for pure hadronic-matter stars.
-This results in large deviations in the sums and differences of tidal deformabilities $(\Lambda_1 \pm \Lambda_2)$, disrupting the overall universality and generating the large ``bump" in the binary Love relations for hybrid stars\footnote{This discrepancy is not present in the I-Love-Q and C-Love relations due to their single-star nature.} seen in Fig~\ref{fig:binLove}.
+This results in large deviations in the sums and differences of tidal deformabilities $(\Lambda_2 \pm \Lambda_1)$, disrupting the overall universality and generating the large ``bump" in the binary Love relations for hybrid stars\footnote{This discrepancy is not present in the I-Love-Q and C-Love relations due to their single-star nature.} seen in Fig~\ref{fig:binLove}.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%% APPENDIX B: MEASUREMENT ACCURACY AS A FUNCTION OF Q %%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\iffalse
-\section{Measurement accuracy as a function of binary mass ratio}\label{app:measurement}
-In this appendix, we discuss the effects of the binary NS mass ratio $q$ on the measurement accuracy of $\tilde\Lambda$ for various interferometers. 
-The top panel of Fig.~\ref{fig:massVariation} displays an approximation of the $\tilde\Lambda$ measurement accuracy as a function of increasing mass ratio $q$ (for a fixed chirp mass of $\mathcal{M}=1.188 \text{ M}_{\odot}$ corresponding to GW170817), using the Fisher analysis techniques described in Sec.~\ref{sec:observations}.
-We observe two points of interest about these trends: (i) the second generation detectors (O2, aLIGO, A\texttt{+}, and Voyager) typically become less accurate as the mass ratio approaches unity; and (ii) the third generation detectors (CE and ET) observe the opposite behavior-- a fast growth in accuracy as the mass ratio increases.
-For the remainder of this appendix, we attempt to explain the opposing behaviors of the second and third generation interferometers on the extraction of $\tilde\Lambda$.
-
-\begin{figure}
-\begin{center} 
-\includegraphics[width=.3\textwidth]{massVariation1.eps}
-\includegraphics[width=.3\textwidth]{massVariation2.eps}
-\includegraphics[width=.3\textwidth]{massVariation3.eps}
-\end{center}
-\caption{
-Measurement accuracy of $\tilde\Lambda$ as a function of increasing mass ratio $q$ for interferometer sensitivities O2, aLIGO, A\texttt{+}, Voyager, CE, and ET.
-Evaluated at a fixed chirp mass of $\mathcal{M}=1.188\text{ M}_{\odot}$ corresponding to GW170817, this is repeated for three cases: (i) (top) with correlations between all template waveform parameters $\theta^a$ intact; (ii) (center) with the correlations between $\tilde\Lambda$ and $\delta\tilde\Lambda$ removed; and (iii) (bottom) with correlations between all parameters removed.
-The removal of parameter correlations is approximated by setting certain Fisher matrix elements to 0, as described in Appendix.~\ref{app:measurement}.
-Observe how the top panel shows strong disagreement between second and third generation detectors, while the bottom panel shows identical behavior.
-This indicates that parameter correlations between $\tilde\Lambda$ and higher PN order parameter $\delta\tilde\Lambda$ are the culprit in such a disagreement.
-}
-\label{fig:massVariation}
-\end{figure}
-
-We begin by considering the correlations between individual template parameters $\theta^a$ and $\tilde\Lambda$, given in Eq.~\ref{eq:template}.
-A simple approximation for the amplitude of these correlations can be performed by assuming that all of the other correlations are non-existing.
-Individual correlations between parameters $\tilde\Lambda$ and $\theta^a$ is achieved by setting all of the off-diagonal Fisher matrix elements to $0$, except for the $(i,j)$ components such that both $i$ and $j$ correspond to the $\tilde\Lambda$ and $\theta^a$ parameters.
-We follow this process for each parameter in turn, and display the results in Fig.~\ref{fig:correlations} for each interferometer.
-This figure, showing only the relative differences between correlations of different parameters $\theta^a$ and $\tilde\Lambda$, reveals a few things.
-First, the coalescence time $t_c$ is highly correlated with $\tilde\Lambda$ equally for each interferometer, an unsurprising fact due to the high 4pN order at which the parameter enters the waveform.
-Secondly, correlations with 6pN tidal parameter $\delta\tilde\Lambda$ shows high correlations with $\tilde\Lambda$ for only the third generation detectors.
-This can be explained by the high pN order at which $\delta\tilde\Lambda$ enters the waveform, an effect that only the most sensitive of detectors can probe.
-
-\begin{figure}
-\begin{center} 
-\begin{overpic}[width=\columnwidth]{correlations.eps}
-\put(121,13){\fontsize{7pt}{7pt}\selectfont $\mathcal{M}$}
-\end{overpic}
-\end{center}
-\caption{
-Measurement accuracy of $\tilde\Lambda$ upon the consideration of correlations between \emph{only} $\tilde\Lambda$ and other individual template parameters $\theta^a$ shown in Eq.~\ref{eq:template}.
-This process, repeated for 6 interferometer design sensitivities O2, aLIGO, A\texttt{+}, Voyager, CE, and ET, is approximated by setting all off-diagonal Fisher matrix elements to 0 except for the $(i,j)$ components such that both $i$ and $j$ correspond to the $\tilde\Lambda$ and $\theta^a$ parameters.
-Observe how correlations with 4PN parameter $t_c$ (coalescence time) remain to be highly correlated with $\tilde\Lambda$ among all 6 interferometers.
-However, correlations between 6PN tidal parameter $\delta\tilde\Lambda$ and $\tilde\Lambda$ only begin to make a strong impact for third generation detectors.
-This is due to the small effect that $\delta\tilde\Lambda$ has on the waveform, only to be distinguished by the most sensitive detectors.
-}
-\label{fig:correlations}
-\end{figure}
-
-Following this conclusion on the difference of correlations between tidal parameters $\tilde\Lambda$ and $\delta\tilde\Lambda$ for second and third generation detectors, we attempt to describe the opposing behaviors of measurement accuracy between the two.
-Shown in the central panel of Fig.~\ref{fig:massVariation}, we approximate the measurement accuracy on $\tilde\Lambda$ with the correlations between $\delta\tilde\Lambda$ and $\tilde\Lambda$ removed, through a process similar to that described above.
-Notice how the trends between detector generations become more similar -- implying that the correlations between tidal parameters may be the cause of the opposing behaviors.
-This is confirmed by the bottom panel of Fig.~\ref{fig:massVariation} where all parameter correlations have been removed from the Fisher matrix.
-We see that this results in identical behaviors between all 6 representative interferometers, leading us to conclude that the discrepancy between the interferometers originates from the degeneracies between different parameters in the gravitational waveform, namely the 6pN tidal parameter $\delta\tilde\Lambda$ which is only detectable by the highly sensitive third generation detectors CE and ET.
-\fi
 %%%%%%%%%%%%%%%%%%%%%%

### 2019-03-17 paper/Submit/bin-love-after-gw170817.tex
arxive/prd version ready for submission
Added R-Love citations
adding Hectors references

--- 2019-02-28 paper/bin-love-after-gw170817.tex
@@
 
-\author{Zachary Carson}
+\author{Zack Carson}
 \affiliation{%
@@
 \author{Katerina Chatziioannou}
-%\affiliation{%
-% Canadian Institute for Theoretical Astrophysics, 60 St. George Street, Toronto, Ontario, M5S 3H8, Canada
-%}%
 \affiliation{%
@@
 For years, the theoretical physics community considered the possibility of using measurements of NS properties, such as the mass, the radius and the moment of inertia, to constrain deviations from General Relativity in the strong-field regime.
-Certain modified theories of gravity, such as scalar tensor theories with spontaneous scalarization~\cite{Damour:1996ke}, Einstein-\AE ther and Ho\v rava gravity~\cite{Eling:2007xh,Yagi:2013ava,Yagi:2013qpa}, dynamical Chern-Simons gravity~\cite{Yunes:2009ch,Yagi:2013mbt,Gupta:2017vsl}, beyond Horndesky theories~\cite{Babichev:2016jom,Sakstein:2016oel}, modify such NS observables, but unfortunately, these modifications are typically degenerate with the nuclear EoS.
+Certain modified theories of gravity, such as scalar tensor theories with spontaneous scalarization~\cite{Damour:1996ke}, Einstein-\AE ther and Ho\v rava gravity~\cite{Eling:2007xh,Yagi:2013ava,Yagi:2013qpa}, dynamical Chern-Simons gravity~\cite{Yunes:2009ch,Yagi:2013mbt,Gupta:2017vsl}, beyond Horndesky theories~\cite{Babichev:2016jom,Sakstein:2016oel}, modify such NS observables, but unfortunately, these modifications are typically degenerate with the nuclear EoS~\cite{Pani:2014jra,Minamitsuji:2016hkk,Maselli:2016gxk}.
 Yagi and Yunes proposed to solve this problem by finding EoS-insensitive relations between the moment of inertia, the tidal deformability (or Love number) and the quadrupole moment, the so-called ``I-Love-Q'' relations~\cite{Yagi:2013bca,Yagi:ILQ}.
@@
 \begin{center} 
-\includegraphics[width=\columnwidth]{stackedFisher.eps}
+\includegraphics[width=\columnwidth]{stackedFisher.pdf}
 \end{center}
@@
 \begin{center} 
-\includegraphics[width=.97\columnwidth]{EoSs.eps}
-\includegraphics[width=\columnwidth]{hybridEoSs.eps}
+\includegraphics[width=.97\columnwidth]{EoSs.pdf}
+\includegraphics[width=\columnwidth]{hybridEoSs.pdf}
 \end{center}
@@
 \begin{center} 
-\includegraphics[width=\columnwidth]{CL.eps}
-\includegraphics[width=.96\columnwidth]{RL.eps}
+\includegraphics[width=\columnwidth]{CL.pdf}
+\includegraphics[width=.96\columnwidth]{RL.pdf}
 \end{center}
@@
 The systematic uncertainty in the radius using the constrained fit is thus comparable to the $\sim 140\textrm{m}$ systematic uncertainty in the radius due to the choice of EoS to model the crust~\cite{Gamba:2019kwu}.
+See also Refs.~\cite{Annala:2017llu,Raithel:2018ncd} for related work on the R-Love relations.
 
@@
 \begin{center} 
-\includegraphics[width=\columnwidth]{binLoveAbsolute.eps}
+\includegraphics[width=\columnwidth]{binLoveAbsolute.pdf}
 \end{center}
@@
 \begin{center} 
-\begin{overpic}[width=\columnwidth]{qResiduals.eps}
+\begin{overpic}[width=\columnwidth]{qResiduals.pdf}
 \put(7,94){\tiny\rotatebox{90}{$\mathcal{R}$}}
 \end{overpic}
-\begin{overpic}[width=\columnwidth]{LsResiduals.eps}
+\begin{overpic}[width=\columnwidth]{LsResiduals.pdf}
 \put(7,95){\tiny\rotatebox{90}{$\mathcal{R}$}}
@@
 \begin{center} 
-\includegraphics[width=\columnwidth]{sensitivities.eps}
+\includegraphics[width=\columnwidth]{sensitivities.pdf}
 \end{center}
@@
 \begin{center} 
-\includegraphics[width=\columnwidth]{singleFisherLt.eps}
+\includegraphics[width=\columnwidth]{singleFisherLt.pdf}
 \end{center}

### 2019-03-17 paper/go.sh

@@ -9,6 +9,7 @@ echo "~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~" >> out
 pdflatex --shell-escape bin-love-after-gw170817.tex >> output.text
 echo "~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~" >> output.text
 pdflatex --shell-escape bin-love-after-gw170817.tex >> output.text
-#rm *blg *log *aux *Notes* *bbl output.text *out
+rm *blg *log *aux *Notes*  output.text *out
+mv bin-love-after-gw170817.pdf ../
 echo "Done. Enjoy your PDF!"
-evince bin-love-after-gw170817.pdf &
+evince ../bin-love-after-gw170817.pdf &

### 2019-04-09 paper/Response.txt
writing response to referee, as well as editing the paper

Dear Editor,

We would like to thank the referee for carefully reading our manuscript 
and providing valuable comments which have helped us improve the quality 
of our paper. For ease, we have highlighted all of our newest updates in 
boldface black. Additionally, we have outlined all of the comments
below, with "R:" and "A:" corresponding to the referee's comments and
the authors' replies, respectively.

We hope you reconsider publication of our manuscript in your journal.

Sincerely,

Zack Carson, Katerina Chatziioannou, Carl-Johan Haster, Kent Yagi, and 
Nicolás Yunes

---------------------------------------
Comments from the Referee
---------------------------------------

R: 1. I find the description of the “constrained” prior and its relation
to the “unconstrained” one slightly confusing. Sec. I A suggests that
it is constructed by sampling a large number of spectral EOSs and then
discarding those lying outside the 90% credible region of the EOS
posterior from GW170817. On the other hand, Sec. II A says that it is
built up from EOSs sampled directly from the EOS posterior (itself
derived from the unconstrained prior?), with no mention of the 90%
credible region. Naively, I would think that one would simply take the
unconstrained prior and reweight it by the GW170817 EOS likelihood to
get the constrained prior. Please explain more clearly which procedure
was adopted, and emphasize how the constrained and unconstrained
priors are related.

A: We apologize for the loss in translation between the descriptions of 
the constrained EoSs in the executive summary and Sec IIa. Ultimately, 
the "constrained" EoSs were computed identically to how the 90% 
posterior EoS were found in the paper by Abbott et al. So essentially we
are sampling the actual 90% posterior given by LIGO (the exact 
posterior EoSs from the paper are not publicly available, so the 
computation had to be re-done). Then, the unconstrained EoSs were 
generated completely randomly, with no relation to the constrained EoS
or the posterior PDF. We have modified our descriptions of this in both 
Sec. Ia and IIa.

R: 2. To quantify the error in the tidal deformability introduced by the
approximately universal nature of the binary Love relations, Sec. IV
adopts a representation for the error about the best-fit relation. The
error model is fitted to data from the constrained prior. Does this
prior include any hybrid EOSs, the models that deviate the most from
the binary Love relations? If not, do the projections in Sec. IV rely
on an implicit assumption that the EOS is purely hadronic?

A: Yes, you are correct that our results for the systematic errors from
the binary Love relations rely on the assumption of hadronic stars. Our 
set of constrained EoSs do not contain any hybrid star EoSs, following
from the calculations of Abbott et al on the EoS posterior probability 
distribution, which also assumed purely hadronic EoSs. If included these
results may change slightly, and could be a possible avenue of future
work. We have added a couple of sentences to the end of Sec. IVa 
noting this.

R:  3. Several papers have claimed that EOSs with sharp phase transitions
can violate I-Love-Q universality, e.g. Han & Steiner,
arXiv:1810.10967; Bandyopadhyay et al., Eur. Phys. J. A (2018) 54: 26;
Lau et al., Phys. Rev. D 95, 101302 (2017). Here, in Sec. III, hybrid
hadron-quark EOSs are found to obey the standard I-Love-Q relations.
Is this finding compatible with the existing claims in the literature?
The paper would benefit from a brief discussion of this point.

A: Upon reading over the papers by Han & Steiner, Bandyopadhyay et al, 
and Lau et al, we find that our results are indeed consistent with what
they present. 
The paper by Han & Steiner claims that "for typical neutron
stars > 1.0 M_sun, discrepancies are negligible", which can also be seen
in the bottom left panel of Fig. 11. In fact, the fits are only valid in
the M>1M_sun regime as can be seen in the top panel of Fig. 11, a relic 
fixed in our paper by using improved fits which limit to the Newtonian
case.
In the paper by Lau et al,  they claim that the "I-Love 
relation for hybrid stars still agrees with the universal relation for 
fluid stars to about 1% level for hybrid stars with a quark-matter core
surrounded by a fluid [hadronic] envelope", similar to what we investigate. 
They find that solid quark-matter stars (not studied by us) violate the 
relations proportionally to the value of the gap parameter. 
Finally, in the paper by Bandyopadhyay et al, there is no claim to *how* 
strongly the "HQ" EoSs violate the I-Love relation. However, by looking 
at Fig. we see that the departure from the "np" EoSs is not noticeably 
large, and seems to be somewhat consistent with what we see with our 
hybrid star EoSs. 
We also see in Paschalidis2018 (10.1103/physrevd.97.084038) that it was 
shown that the I-Love-Q universality is preserved for the hybrid stars
considered, which are identical to the ones used here.
As so, we have added a couple of sentences at the end of Sec.
IIIA2 discussing the consistency, as well as the additional references.

R:  4. In Fig. 5, the departure of the hybrid EOSs from the best-fit
binary Love relation appears to become more pronounced as q tends to
1. Is there an intuitive explanation for this behavior?

A: This behavior is caused for the same reason as the (fractional) error 
increases for hadronic stars with increasing mass ratio. This is because 
as the mass ratio decreases, the universal relation becomes more exact 
as Lambda_s -> Lambda_a (exactly equal in the q=0 limit). Therefore, as 
the mass ratio increases to 1, Lambda_a and Lambda_s become maximally 
different, and the fractional error becomes maximal. We have added a 
comment on this at the end of the caption on Fig. 5, as well as added 
the absolute differences for hybrid stars in the bottom three panels.

R:  * Sec. I: A more up-to-date reference about systematic errors in
neutron star mass-radius measurements is Miller & Lamb, F. Eur. Phys.
J. A (2016) 52: 63.

A: We thank the referee for the updated citation on M-R systematics. In 
response, we have added the Miller & Lamb 2016 citation in the first 
paragraph of Sec. I.

R: * Sec. I: The last sentence of the second paragraph seems to attribute
the tidal signature in the waveform solely to the modified orbital
dynamics, but there is an equally important dissipative contribution
due to the extra multipole radiation sourced by the tidal bulges.

A: We have modified the sentence in question to include this additional
GW modification effect: "These deformations source additional multipole radiation 
as well as affect the orbital trajectory of the binary, thus altering the
 GWs emitted, encoding within the latter the NS EoS."

R: * Sec. I A: Surely the variability in the R-Love relation is on the
order of hundreds of meters, not hundreds of kilometers.

A: We thank the referee for finding this typo! It is indeed errors of
~880 m and ~360 m, not km. This has been adjusted accordingly.

R: * Sec. II A: Why is causality only required to within 10% in the
prior? It does not appear to be explained in the text. (Also, Gamma is
incorrectly called the polytropic index instead of the adabiatic index
in this discussion.)

A: We chose causality to 10% to be consistent with the analysis of 
Abbott et al. 2018 (10.1103/PhysRevLett.121.161101), from which they 
choose to adhere to causality up to 10% upon deriving the EoS 
posterior probability distribution. We have added a short note to Sec. 
IIa. commenting on this. We have also fixed the incorrect naming of Gamma.

R: * Sec. IV: The sentence reporting the GW170817 Lambda_tilde
measurement does not cite the reference from which it was taken.
(Also, there appears to be an extraneous comment embedded in the same
sentence.)

A: We thank the referee for finding the missing citation and extraneous 
comment that somehow made it into the final draft. The citation has been
added, and comment removed.

---------------------------------------
Other Modifications
---------------------------------------

- We have included additional citations regarding the sentence 
"...but unfortunately, these [modified theories of gravity] are 
typically degenerate with the nuclear EoS. These are Pani & Berti 2014, 
Arxiv:1405.4547, Minamitsuji & Silva 2016, Arxviv:1604.07742, and 
Maselli & Silva 2016, Arxiv:1603.04876

### 2019-04-09 paper/Submit/bin-love-after-gw170817.tex
writing response to referee, as well as editing the paper

@@
 For example, electromagnetic observations of the mass and radius of certain NSs have been used to place confidence limits in the mass-radius plane, and thus constrain the EoS~\cite{guver,ozel-baym-guver,steiner-lattimer-brown,Lattimer2014,Ozel:2016oaf}.
-These observations, however, may potentially suffer from large systematic errors~\cite{Miller2013} due to uncertainties in the astrophysical modeling of X-ray bursts.
+These observations, however, may potentially suffer from large systematic errors~\cite{Miller:2016pom, Miller2013} due to uncertainties in the astrophysical modeling of X-ray bursts.
 The gravitational waves (GWs) emitted in the coalescence of NS binaries may be a cleaner probe of nuclear physics.
 During the early inspiral, the orbital separation is large enough that the tidal fields are negligible; but as the orbital separation decreases due to GW emission, tidal forces grow and the NSs respond by developing deformations determined by their nuclear EoS.
-These deformations affect the orbital trajectory of the binary, and thus the GWs emitted, encoding in the latter the NS EoS~\cite{hinderer-love,Flanagan2008}.
+These deformations \textbf{source additional multipole radiation as well as} affect the orbital trajectory of the binary, \textbf{thus altering} the GWs emitted, encoding \textbf{within} the latter the NS EoS~\cite{hinderer-love,Flanagan2008}.
 
@@
 We take the 90\% credible region constructed from the posterior probability distributions on the pressure-density plane~\cite{Carney:2018sdv,LIGO:posterior} obtained from GW170817~\cite{TheLIGOScientific:2017qsa} as a prior on the set of EoSs that is compatible with this observation.
-We then generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, one in which this prior is enforced (the ``constrained'' sample) and another in which the prior is not enforced (the ``unconstrained'' sample).
+We then generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, one in which \textbf{the EoSs are directly sampled from the posterior probability distribution} (the ``constrained'' sample) and another in which the prior is not enforced (the ``unconstrained'' sample).
 We repeat the analysis done by Yagi and Yunes~\cite{Yagi:binLove,Yagi:ILQ} on both sets of EoSs and find that the EoS-insensitive relations present less EoS variability with the constrained set. 
@@
 First, we investigate the relation between the NS radius and its tidal deformability, the R-Love relations, for both sets of EoSs, as these are critical in order to place constraints on the radius from a measurement of the Love number.
-We use the C-Love relations to construct the R-Love relations and find that the maximum EoS variability drops from $\sim 880 {\rm{km}}$ in the unconstrained case to $\sim 360 {\rm{km}}$ in the constrained case (see Sec.~\ref{sec:clove} for more details).
+We use the C-Love relations to construct the R-Love relations and find that the maximum EoS variability drops from $\sim 880$ \textbf{m} in the unconstrained case to $\sim 360$ \textbf{m} in the constrained case (see Sec.~\ref{sec:clove} for more details).
 Second, we study the EoS-universality of hybrid stars, which experience strong first-order phase transitions from hadronic to quark matter in the core~\cite{Paschalidis2018,Most:2018eaw,Burgio:2018yix,Montana:2018bkb}.
@@
 Moreover, we impose the following two restrictions:  (i) causality within 10\%, i.e.
-that the speed of sound of the fluid be less than the speed of light to 10\%, and (ii) a high maximum mass, i.e.~that the resulting EoS supports NSs with masses at least as high as $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations~\cite{1.97NS,2.01NS,Zhao:massiveNS}.
-
-The unconstrained set is then defined by drawing random samples in the spectral coefficients within their allowed prior ranges, and then eliminating any EoS that either leads to a polytropic index $\Gamma$ outside the allowed range, breaks the causality restriction, or breaks the maximum mass restriction.
+that the speed of sound of the fluid be less than the speed of light to 10\% \textbf{(following the analysis of Ref.~\cite{LIGO:posterior})}, and (ii) a high maximum mass, i.e.~that the resulting EoS supports NSs with masses at least as high as $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations~\cite{1.97NS,2.01NS,Zhao:massiveNS}.
+
+The unconstrained set is then defined by drawing random samples in the spectral coefficients within their allowed prior ranges, and then eliminating any EoS that either leads to \textbf{an adiabatic index} $\Gamma$ outside the allowed range, breaks the causality restriction, or breaks the maximum mass restriction.
 To obtain the constrained set of EoSs we analyze the publicly available data for GW170817 from the Gravitational Wave Open Science Center~\cite{GWOSC,Vallisneri:2014vxa}. 
-We use the publicly available software library {\tt LALInference}~\cite{Veitch:2014wba,lalinference_o2} to obtain samples from the EoS posterior.
+We use the publicly available software library {\tt LALInference}~\cite{Veitch:2014wba,lalinference_o2} to \textbf{directly} obtain samples from the EoS \textbf{90\% posterior provided by Ref~\cite{LIGO:posterior}.}
 Our analysis uses the same settings and prior choice as those of~\cite{LIGO:posterior,Carney:2018sdv}. 
@@
 From this study, we conclude that hybrid star EoSs \emph{do} obey the traditional nuclear I-Love-Q relations computed with nuclear EoS data, albeit with a slight decrease in universality to $\sim1.7$\%.
+\textbf{We find this decrease in universality to be somewhat consistent with similar works~\cite{Paschalidis2018,Bandyopadhyay2018,PhysRevD.95.101302,Han:2018mtj}.
+In such investigations, departures from universality of up to $\sim1\%-2\%$ were found with various hybrid star EoSs, compatible with our result of $\sim1.7$\%.}
 
@@
 For comparison, we also show the binary Love relations for the 10 hybrid star EoSs (dashed green curves), which present much larger EoS variation.
+Observe here how both hadronic and hybrid star EoSs alike seemingly observe increasingly small distinction from the fits as the mass ratio $q$ approaches 0.
+While the absolute errors remain somewhat consistent with mass ratio, the fractional differences from the fit approach $0$ as $q\rightarrow0$ as the universal relation becomes exact ($\Lambda_s\rightarrow\Lambda_a$).
 }
@@
 Current interferometer sensitivities are not yet high enough to accurately constrain the dominant tidal parameter $\tilde{\Lambda}$.
-For example, GW170817 was detected by the second LIGO observing run (``O2")~\cite{aLIGO} and Virgo~\cite{TheVirgo:2014hva} Virgo is not formally an abbreviation,  so it's not all capitalized and was able to constrain $\tilde{\Lambda}$ to a $90\%$ credible interval centered at $\mu_{\tilde{\Lambda}}=395$ and with a width of 325 (or $\sigma_{\tilde{\Lambda}} \approx 198$).
+For example, GW170817 was detected by the second LIGO observing run (``O2")~\cite{aLIGO} and Virgo~\cite{TheVirgo:2014hva}, and was able to constrain $\tilde{\Lambda}$ to a $90\%$ credible interval centered at $\mu_{\tilde{\Lambda}}=395$ and with a width of 325~\cite{Abbott2018} (or $\sigma_{\tilde{\Lambda}} \approx 198$).
 This corresponds to statistical uncertainties of ${\cal{O}}(80\%)$, which dominates the error budget compared to the small systematic uncertainties picked up by EoS variation in the EoS-insensitive relations.
@@
 We can similarly derive a conservative estimate of the systematic uncertainty due to EoS-variability in the binary Love relations in terms of $\tilde\Lambda_{a}$ to find $12.01$, which is what we use later in Fig.~\ref{fig:singleFisherLt}.
+\textbf{Here we note that these results rely on the assumption of a purely hadronic EoS, as the constrained set of EoSs do not contain any hybrid stars.
+This assumption was also made in Ref.~\cite{LIGO:posterior} upon the derivation of the posterior probability distribution.}
 

### 2019-04-10 paper/Response.txt
implementing Katerina and Kents comments on response to Ref.

@@
 the authors' replies, respectively.
-
-We hope you reconsider publication of our manuscript in your journal.
 
@@
 the constrained EoSs in the executive summary and Sec IIa. Ultimately, 
-the "constrained" EoSs were computed identically to how the 90% 
-posterior EoS were found in the paper by Abbott et al. So essentially we
-are sampling the actual 90% posterior given by LIGO (the exact 
-posterior EoSs from the paper are not publicly available, so the 
-computation had to be re-done). Then, the unconstrained EoSs were 
-generated completely randomly, with no relation to the constrained EoS
-or the posterior PDF. We have modified our descriptions of this in both 
-Sec. Ia and IIa.
+the "constrained" EoSs were computed identically to how the
+posterior for the EoS was computed in the paper by Abbott et al. So 
+essentially we are sampling the actual posterior given by LIGO (the exact 
+posterior EoSs from the paper were not publicly available at the time we 
+started this work, so the computation had to be re-done). Then, the 
+unconstrained EoSs were generated completely randomly, with no relation 
+to the constrained EoS or the posterior PDF. We have modified our 
+descriptions of this in both Sec. Ia and IIa.
 
@@
 strongly the "HQ" EoSs violate the I-Love relation. However, by looking 
-at Fig. we see that the departure from the "np" EoSs is not noticeably 
+at Fig. 6 we see that the departure from the "np" EoSs is not noticeably 
 large, and seems to be somewhat consistent with what we see with our 
 hybrid star EoSs. 
-We also see in Paschalidis2018 (10.1103/physrevd.97.084038) that it was 
+We also see in Paschalidis et al. 2018 (10.1103/physrevd.97.084038) that it was 
 shown that the I-Love-Q universality is preserved for the hybrid stars

### 2019-04-10 paper/Submit/bin-love-after-gw170817.tex
implementing Katerina and Kents comments on response to Ref.

@@
 We begin by investigating the increase in EoS insensitivity due to the constraints placed by GW170817 on the allowed space of EoSs. 
-We take the 90\% credible region constructed from the posterior probability distributions on the pressure-density plane~\cite{Carney:2018sdv,LIGO:posterior} obtained from GW170817~\cite{TheLIGOScientific:2017qsa} as a prior on the set of EoSs that is compatible with this observation.
-We then generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, one in which \textbf{the EoSs are directly sampled from the posterior probability distribution} (the ``constrained'' sample) and another in which the prior is not enforced (the ``unconstrained'' sample).
+\textbf{We use the posterior probability distribution on the pressure-density plane~\cite{Carney:2018sdv,LIGO:posterior} obtained from GW170817~\cite{TheLIGOScientific:2017qsa} to inform the set of EoSs that is compatible with this observation.
+We then generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, one in which the EoSs are directly sampled from the posterior probability distribution (the ``constrained" sample) and another in which this constraint not enforced (the ``unconstrained" sample).}
 We repeat the analysis done by Yagi and Yunes~\cite{Yagi:binLove,Yagi:ILQ} on both sets of EoSs and find that the EoS-insensitive relations present less EoS variability with the constrained set. 
@@
 To obtain the constrained set of EoSs we analyze the publicly available data for GW170817 from the Gravitational Wave Open Science Center~\cite{GWOSC,Vallisneri:2014vxa}. 
-We use the publicly available software library {\tt LALInference}~\cite{Veitch:2014wba,lalinference_o2} to \textbf{directly} obtain samples from the EoS \textbf{90\% posterior provided by Ref~\cite{LIGO:posterior}.}
+We use the publicly available software library {\tt LALInference}~\cite{Veitch:2014wba,lalinference_o2} to sample the EoS \textbf{posterior, similar to Ref~\cite{LIGO:posterior}.}
 Our analysis uses the same settings and prior choice as those of~\cite{LIGO:posterior,Carney:2018sdv}. 

### 2019-04-15 paper/Submit/bin-love-after-gw170817.tex
final revision from peer review

--- 2019-04-09 paper/Submit/bin-love-after-gw170817.tex
@@
 During the early inspiral, the orbital separation is large enough that the tidal fields are negligible; but as the orbital separation decreases due to GW emission, tidal forces grow and the NSs respond by developing deformations determined by their nuclear EoS.
-These deformations \textbf{source additional multipole radiation as well as} affect the orbital trajectory of the binary, \textbf{thus altering} the GWs emitted, encoding \textbf{within} the latter the NS EoS~\cite{hinderer-love,Flanagan2008}.
+These deformations source additional multipole radiation as well as affect the orbital trajectory of the binary, thus altering the GWs emitted, encoding within the latter the NS EoS~\cite{hinderer-love,Flanagan2008}.
 
@@
 We begin by investigating the increase in EoS insensitivity due to the constraints placed by GW170817 on the allowed space of EoSs. 
-We take the 90\% credible region constructed from the posterior probability distributions on the pressure-density plane~\cite{Carney:2018sdv,LIGO:posterior} obtained from GW170817~\cite{TheLIGOScientific:2017qsa} as a prior on the set of EoSs that is compatible with this observation.
-We then generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, one in which \textbf{the EoSs are directly sampled from the posterior probability distribution} (the ``constrained'' sample) and another in which the prior is not enforced (the ``unconstrained'' sample).
+We use the posterior probability distribution on the pressure-density plane~\cite{Carney:2018sdv,LIGO:posterior} obtained from GW170817~\cite{TheLIGOScientific:2017qsa} to inform the set of EoSs that is compatible with this observation.
+We then generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, one in which the EoSs are directly sampled from the posterior probability distribution (the ``constrained" sample) and another in which this constraint not enforced (the ``unconstrained" sample).
 We repeat the analysis done by Yagi and Yunes~\cite{Yagi:binLove,Yagi:ILQ} on both sets of EoSs and find that the EoS-insensitive relations present less EoS variability with the constrained set. 
@@
 First, we investigate the relation between the NS radius and its tidal deformability, the R-Love relations, for both sets of EoSs, as these are critical in order to place constraints on the radius from a measurement of the Love number.
-We use the C-Love relations to construct the R-Love relations and find that the maximum EoS variability drops from $\sim 880$ \textbf{m} in the unconstrained case to $\sim 360$ \textbf{m} in the constrained case (see Sec.~\ref{sec:clove} for more details).
+We use the C-Love relations to construct the R-Love relations and find that the maximum EoS variability drops from $\sim 880$ m in the unconstrained case to $\sim 360$ m in the constrained case (see Sec.~\ref{sec:clove} for more details).
 Second, we study the EoS-universality of hybrid stars, which experience strong first-order phase transitions from hadronic to quark matter in the core~\cite{Paschalidis2018,Most:2018eaw,Burgio:2018yix,Montana:2018bkb}.
@@
 Moreover, we impose the following two restrictions:  (i) causality within 10\%, i.e.
-that the speed of sound of the fluid be less than the speed of light to 10\% \textbf{(following the analysis of Ref.~\cite{LIGO:posterior})}, and (ii) a high maximum mass, i.e.~that the resulting EoS supports NSs with masses at least as high as $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations~\cite{1.97NS,2.01NS,Zhao:massiveNS}.
-
-The unconstrained set is then defined by drawing random samples in the spectral coefficients within their allowed prior ranges, and then eliminating any EoS that either leads to \textbf{an adiabatic index} $\Gamma$ outside the allowed range, breaks the causality restriction, or breaks the maximum mass restriction.
+that the speed of sound of the fluid be less than the speed of light to 10\% (following the analysis of Ref.~\cite{LIGO:posterior}), and (ii) a high maximum mass, i.e.~that the resulting EoS supports NSs with masses at least as high as $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations~\cite{1.97NS,2.01NS,Zhao:massiveNS}.
+
+The unconstrained set is then defined by drawing random samples in the spectral coefficients within their allowed prior ranges, and then eliminating any EoS that either leads to an adiabatic index $\Gamma$ outside the allowed range, breaks the causality restriction, or breaks the maximum mass restriction.
 To obtain the constrained set of EoSs we analyze the publicly available data for GW170817 from the Gravitational Wave Open Science Center~\cite{GWOSC,Vallisneri:2014vxa}. 
-We use the publicly available software library {\tt LALInference}~\cite{Veitch:2014wba,lalinference_o2} to \textbf{directly} obtain samples from the EoS \textbf{90\% posterior provided by Ref~\cite{LIGO:posterior}.}
+We use the publicly available software library {\tt LALInference}~\cite{Veitch:2014wba,lalinference_o2} to sample the EoS posterior, similar to Ref~\cite{LIGO:posterior}.
 Our analysis uses the same settings and prior choice as those of~\cite{LIGO:posterior,Carney:2018sdv}. 
@@
 From this study, we conclude that hybrid star EoSs \emph{do} obey the traditional nuclear I-Love-Q relations computed with nuclear EoS data, albeit with a slight decrease in universality to $\sim1.7$\%.
-\textbf{We find this decrease in universality to be somewhat consistent with similar works~\cite{Paschalidis2018,Bandyopadhyay2018,PhysRevD.95.101302,Han:2018mtj}.
-In such investigations, departures from universality of up to $\sim1\%-2\%$ were found with various hybrid star EoSs, compatible with our result of $\sim1.7$\%.}
+We find this decrease in universality to be somewhat consistent with similar works~\cite{Paschalidis2018,Bandyopadhyay2018,PhysRevD.95.101302,Han:2018mtj}.
+In such investigations, departures from universality of up to $\sim1\%-2\%$ were found with various hybrid star EoSs, compatible with our result of $\sim1.7$\%.
 
@@
 We can similarly derive a conservative estimate of the systematic uncertainty due to EoS-variability in the binary Love relations in terms of $\tilde\Lambda_{a}$ to find $12.01$, which is what we use later in Fig.~\ref{fig:singleFisherLt}.
-\textbf{Here we note that these results rely on the assumption of a purely hadronic EoS, as the constrained set of EoSs do not contain any hybrid stars.
-This assumption was also made in Ref.~\cite{LIGO:posterior} upon the derivation of the posterior probability distribution.}
+Here we note that these results rely on the assumption of a purely hadronic EoS, as the constrained set of EoSs do not contain any hybrid stars.
+This assumption was also made in Ref.~\cite{LIGO:posterior} upon the derivation of the posterior probability distribution.
 

### 2019-04-25 paper/Submit/bin-love-after-gw170817.tex
PRD corrections for publishing

@@
 We here wish to consider EoS-insensitive relations using two sets of EoSs: a ``constrained set'' consistent with the observation of GW170817 and an ``unconstrained set'' that does not impose this prior.
-In \emph{both} cases, we model the EoS with a $C^{0}$-piecewise function that equals the low-density crust EoS of SLy~\cite{Douchin:2001sv} below half nuclear saturation density $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$~\cite{Read2009}, and equals the spectral decomposition described above outside the crust.
+In \emph{both} cases, we model the EoS with a $C^{0}$-piecewise function that equals the low-density crust EoS of SLy\footnote{SLy represents the unified equation of state based on the effective Skyrme Lyon nucleon-nucleon interactions, developed by Douchin and Haensel, 2001~\cite{Douchin:2001sv}.}~\cite{Douchin:2001sv} below half nuclear saturation density $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$~\cite{Read2009}, and equals the spectral decomposition described above outside the crust.
 For the latter, we restrict the spectral coefficients to the ranges $\gamma_0 \in \lbrack 0.2,2 \rbrack$, $\gamma_1 \in \lbrack -1.6,1.7 \rbrack$, $\gamma_2 \in \lbrack -0.6,0.6 \rbrack$, $\gamma_3 \in \lbrack -0.02,0.02 \rbrack$, and the adiabatic index is further restricted to $\Gamma \in \lbrack 0.6,4.5 \rbrack$~\cite{Lindblom:parameters}.
@@
 In addition, we investigate 10 transitional quark-hadron matter stars, which undergo strong first-order phase transitions at a pressure $P_{\text{tr}}$, leading to the hadronic branch departing into a quark-matter branch at a given transitional mass~\cite{Paschalidis2018,Alford:2017qgh,1971SvA....15..347S,Zdunik:2012dj,Alford:2013aca}.
-In particular, we focus on the ACS and ACB models described in~\cite{Paschalidis2018}, and also shown in the right panel of Fig.~\ref{fig:eos}.
+In particular, we focus on the ACS and ACB models (corresponding to speed of sound, and piecewise polytropic representations of the EoS beyond the phase transition, respectively) described in~\cite{Paschalidis2018}, and also shown in the right panel of Fig.~\ref{fig:eos}.
 These result in two distinct types of NSs, based on their mass: (i) massive ($M \geq \text{ M}_{\text{tr}}$) hybrid stars which have quark-matter inner cores and nuclear matter elsewhere (henceforth, we denote such stars as hybrid stars (HSs)), and (ii) low-mass ($M \leq \text{ M}_{\text{tr}}$) hadronic stars with no internal transition to quark matter (henceforth, we denote these stars as simply NSs).
@@
 The constant of proportionality that determines how quadrupolarly deformed a star becomes in the presence of a quadrupolar tidal field is called the \emph{tidal deformability} and denoted $\lambda$.
+The magnitude of $\lambda$ depends strongly on the underlying structure, as well as the fluid nature of the NS~\cite{PhysRevD.98.084010}.
 Therefore, this parameter has the largest impact on the GW phase, and thus, it is encoded in GW observations of binary NS coalescence.
